### 2018-12-13 manuscript/reply_to_referees.tex
adding code and ms

\documentclass[12pt]{letter}

\usepackage[britdate]{LiU-letter}
\usepackage{times}
\usepackage{letterbib}
\usepackage{geometry}
\usepackage[round]{natbib}
\usepackage{graphicx}
\geometry{a4paper}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage[running]{lineno}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage[margin=10pt,font=small,labelfont=bf]{caption}

%\usepackage{natbib}
% \bibpunct[; ]{(}{)}{;}{a}{,}{;}

\newenvironment{refquote}{\bigskip \begin{it}}{\end{it}\smallskip}

\newenvironment{figure}{}

\begin{document}

\newpage

\setcounter{page}{1}

% -----------------------------------------------------------------------------
% -----------------------------------------------------------------------------
{\Large \bf Reply to Referee \#1}
% ---------------------------------------

  Referee 1 focused their critique entirely on our methods. They were concerned that our novel approach had not been properly validated or compared to previous methods, and that we did not have within-family resolution for our tree. We respond (preceded by \textbf{R:}) to each of these concerns in detail below.

  1. Request for statistical validation

    \begin{refquote}

      I think that the introduction of a new method should be validated in terms of statistical power (type I and II error) ... For example, how the new method accounts for the non-independent use of the same species in different pairwise interactions?

    \end{refquote}

    \textbf{R:} Solution was something to do with making >100 simulations of each empirical network and then >100 simulations of each simulation...

  2. Request for comparison with other methods

    \begin{refquote}

      I think that the introduction of a new method should be ... compared with existing methods.  Does the new method outperforms  those of Ives \& Godfray (2006, Am Nat 168),  Rafferty and Ives (2013, Ecology 94) or Hadfield et al (2014, Am Nat 183)? The latter method identifies three sources of phylogenetic signal: host/parasite specialism-generalism, host/parasite evolutionary interactions, and the coevolutionary interaction. Can the new method identify these sources of phylogenetic signal between plants and animals (pollinators or herbivores)?

    \end{refquote}

    \textbf{R:} I need to re-read these papers. As I recall, they were asking slightly different questions but I didn't fully understand their methodologies.

      %     Our study and those that the author mention are designed to answer different
      % questions. Ives \& Godfray (2006) developed their method to ask whether a
      % plant (or the majority of plants in a community) is visited by a related set of 
      % pollinators (and vice versa). We are interested in whether related plants are 
      % visited by similar sets of pollinators, regardless of whether or not the 
      % pollinators are related. It is not obvious how to translate the results of their 
      % method (e.g., individual species of pollinators tend to visit related sets of plants) 
      % to our question, as two closely-related plants might be visited by non-overlapping 
      % sets of pollinators which nevertheless tend to visit related plants. This could 
      % occur, for example, if plants within a particular genus grow either in the 
      % understory or in more open microhabitats and each pollinator visits only plants of 
      % this genus that grow within its preferred microhabitat.

      % Similarly, Rafferty \& Ives (2013) used two phylogenetic linear
      % mixed models (PLMM's) to model the strength of plant-pollinator
      % interactions as a function of 1) plant traits and pollinator
      % phylogeny; and 2) plant and pollinator phylogenies. We were instead
      % interested in modelling plants' traits (i.e., their interaction
      % partners) over their phylogeny. In our case, we did not have pollinator
      % phylogenies and our `trait' of interest was the set of animals with
      % which a plant interacts. In Rafferty \& Ives' first PLMM, then, we
      % would need to include network structure as both a dependent and the
      % independent variable, while in the second we would be obliged to assume
      % that the pollinator phylogenies were completely uninformative. This is
      % almost certainly not the case. More importantly, even if we accept this
      % limitation and model the strength (or in our case, binary presence or 
      % absence) of interactions purely based on the plant phylogeny, it is not
      % clear how this model would allow us to assess whether or not plants 
      % tend to interact with similar \emph{sets} of animals. That is, we are not
      % interested in whether each particular animal has similar probabilities
      % of interacting with closely-related plants but rather in the amount of
      % overlap in the sets of animals that visit related and unrelated plants.

      % Hadfield \emph{et. al.}'s 2014 study addresses questions that are even
      % further from our study's focus. The authors of that study are mainly
      % interested in the interplay of two phylogenies (also a focus of
      % Rafferty \& Ives, 2013, but to a lesser degree). In our datset, we
      % had access to phylogenies for the plants but not their animal interaction
      % partners. As such, the referee is correct in noting that we do not 
      % identify sources of phylogenetic signal \emph{a la} Hadfield \emph{et. al.}.
      % In our study, we cannot test for co-evolution of plants and their 
      % partners or for other forms of evolutionary interaction between them. 
      % Without being able to eliminate these possibilities, testing for an 
      % effect of animal or plant specialism on interaction patterns tells us
      % little about the effect of plants' evolutionary histories.

      % [[We have edited the main text to make our question of interest (and
      % the ways in which it differs from the questions asked by other 
      % researchers) clearer. We have also added tests for type I and type II
      % statistical errors, as described below. We hope that this will provide
      % a sufficient indication of the quality of our method, as we cannot 
      % in good concience compare our results to those of methods asking different
      % questions.]]

  3. Between-family resolution is not sufficient

    \begin{refquote}

      Regarding the phylogenetic patterns within plant families, I am afraid that the authors do not have neither topological nor cronological resolution in the phylogenetic tree to run these analyses. The topology provided by phylomatic is resolved at the family level, and then it may produce a lot of polytomies at the genus and species level. Similarly, Wilkstrom et al's calibration points are not enough to calibrate divergence points within families. Instead, the authors use the bladj algorithm, which distribute the undated nodes following a mathematical function which is strongly dependent on the number of tips in that particular clade.  Bladj + Wikstrom ages may work well to detect patterns at the community level where phylogenetic distances among species from different clades are averaged.  However, when phylogenetic distances within lower taxonomic entities (families, genera) are needed, a more accurate calibration is needed. Otherwise, phylogenetic distance is confounded with species richness within clades (i.e. the phylogenetic distance between two species of a family will depend on the  number of species in that family and not on the true phylogenetic distance among them). For that reason, I have serious doubts about the phylogenetic patterns within families shown by the authors. Accurate chronograms at genus and species level would be necessary to extract robust conclusions.

      \end{refquote}

      \textbf{R:} We accept the author's reluctance to accept conclusions based on Bladj + Wikstrom age dates. As none of the authors of this manuscript has any expertise relevant to constructing chronograms, however, we are strictly limited to using published dates of divergence between taxa. Fortunately, while this manuscript was being revised a recent dated tree (that of Zanne \emph{et al.}, 2014) has been incorporated into the Phylomatic web tool. We have rebuilt our dated trees using this phlogeny, which incorporates within-family divisions. We hope that this additional detail will satisfy the reviewer.

\section*{Referee 2}

  Referee 2 was very positive about our manuscript and only had a few minor suggestions. We thank the Referee for her thoughtful input.

  1. Expand the title

    \begin{refquote}

      I think the title could be improved to bring a "bigger message" (which is in the manuscript), such as stressing the great spatial extent of the study. E.g. Global assessment of plant-pollinator-herbivore evolutionary interactions reveals great variation across communities and plant families, etc.

    \end{refquote}

    \textbf{R:} Assuming this still fits after re-analysis, seems like a good idea.

  2. Add more evolutionary/community-ecology context

    \begin{refquote}

      I also think it would be very interesting to put this work in a context of evolutionary community ecology, in order to potentially understand the evolutionary development of the traits in the plant families studied in this work. Specifically, it would be worth testing the study system in the framework of specialist vs. generalist herbivores and specialist vs. generalist pollinators. Taking into consideration that herbivores and pollinators have an evolutionary contrasting impact on plants: plants want to escape herbivores but want to be pollinated. So we can guess that being a specialist herbivore might have an opposite effect than being a specialist pollinator: we might find more distantly related species co-existing in plant communities where specialist herbivores dominate; and more closely related co-existing plant species when generalist herbivores dominate. Contrastingly, in the presence of specialist pollinators, co-existing plants are closely related. Whereas plant are distantly related when generalist pollinators dominate. These community-levels works might be interesting:

      \smallskip

      Yguel, B., Bailey, R., Tosh, N. D., Vialatte, A., Vasseur, C., Vitrac, X., ... \& Prinzing, A. (2011). Phytophagy on phylogenetically isolated trees: why hosts should escape their relatives. Ecology Letters, 14(11), 1117-1124.
      \smallskip
      Castagneyrol, B., Jactel, H., Vacher, C., Brockerhoff, E. G., \& Koricheva, J. (2014). Effects of plant phylogenetic diversity on  herbivory depend on herbivore specialization. Journal of Applied Ecology, 51(1), 134-141.
      \smallskip
      Yguel, B., Bailey, R. I., Villemant, C., Brault, A., Jactel, H., \& Prinzing, A. (2014). Insect herbivores should follow plants escaping their relatives. Oecologia, 176(2), 521-532.

      \end{refquote}

    \textbf{R:}

\section*{Referee 3}

  Referee 3 saw "the potential [[for our study]] to become a significant contribution to the field of ecological networks" if a number of significant issues are addressed. Specifically, the Referee found several sections to be unclear, the discussion to be shallow, and lacked confidence in our statistical analyses. We address each point below and hope that our responses (preceded by \textbf{R:}) will satisfy the Referee.

  1. Use randomization tests to address non-independence of pairs of species

    \begin{refquote}

      If I understood right the authors used the paired niche overlap and the shared evolutionary history of each pair of species as data points in their analyses. However, pairs of species are not independent. I am not here worried about the evolutionary dependence of pairs of species. Rather, I am worried that in a network with P plant species, each plant species will participate of P-1 data points. These data points, as a consequence, are not independent and the authors need to incorporate this dependency in their analysis. A simple way of circumvent this problem is to use randomization tests to build up an empirical distribution for the metric of interest in the presence of the dependency of data points.

      \end{refquote}

      \textbf{R:}

  2. Demand for more detailed discussion of system-specific biology

    \begin{refquote}

      One of the main weaknesses of the manuscript is that the huge amount of information we know about plant-insect interactions in the wild is ignored in the methods section and the discussion of the paper. Examples include:

      \begin{itemize}

      \item Line 77. The authors carefully restricted their herbivore dataset to only those insects that feed on leaves. Having said that, inspecting their dataset it is possible to notice that distinct herbivory networks are formed by distinct groups of insects such as grasshoppers, lepidopterans, and leaf beetles. We know for a long time these herbivores markedly vary in the way they interact with plants. As a result, networks formed by these herbivores and their host plants are very distinct, varying in many network structural patterns (Pires and Guimares 2013. Interface). I missed a deeper discussion on the role of biological traits (often mentioned in the vague "traits" way) in shaping network patterns. For example, physical and physiological integration associated with interaction intimacy might explain the stronger "phylogenetic effect" observed in herbivory networks that involve leaf beetles and lepidopterans.

      \item There is a lot of information on plant families that are known to have secondary metabolites that deter multiple herbivores. Along the same lines, there is a lot of information on flower morphology that constrains or favors particular types of pollinators. Flower morphology, in turn, is often a family-level attribute. Nevertheless, there is no attempt of relate the patterns the authors observe with the solid body of information on the biology of plant-insect interactions.

      \item Lines 238-248 and 339-341. Which is the biological meaning of the fact the families associated to networks with steepest relationships between niche overlap and shared evolutionary history did not show steep relationships between niche overlap and shared evolutionary history? It is not clear to me.

      \item In the discussion the authors hypothesize that pollinator syndromes would be more common within families with weaker evidence of effects of shared evolutionary history. However, twenty years ago Jordano (1995. AmNat) showed that syndromes – at least in seed dispersal systems – are associated with shared evolutionary history. Thus, there is no reason to assume that syndromes are more likely to occur in interactions in which shared evolutionary history has an weaker association on patterns of interaction.

    \end{itemize}
    \end{refquote}

    \textbf{R:} We hope that the Referee appreciates the fact that length restrictions limit our ability to go into too much detail in the Discussion without severely compromising our explanation of the methods. Nevertheless, where possible we have added biological details throughout the manuscript. We have taken particular care to address the specific points the Referee has highlighted above.

  3. Request to provide more detail about specialist pollinators

    \begin{refquote}

      It is puzzling that pollinators show smaller number of interactions than herbivores. It is the opposite of all we know about herbivory and plant-pollinator interactions. It might be a consequence of lumped grasshoppers with other herbivores, the effect of analyzing occasional flower visitors as specialists in pollinator networks, or a consequence of poor sampling in pollinator networks. I would like the authors to provide more information on which are those "pollinator specialists" and on how exhaustive is the sampling of the networks they analyze.

    \end{refquote}

    \textbf{R:} As we used published networks rather than collecting data ourselves, we cannot provide information on the exhaustiveness of sampling other than that given in the original sources (detailed in the SI). In particular, we cannot say which apparently specialist pollinators appear specialized because of rarity and which are genuinely specialized as data on abundances were not published together with the bulk of the metworks we used. The questions the Referee asks about the adequacy of sampling and specialization in plant-pollinator networks are very important, but we respectfully suggest that they are best addressed by encouraging empirical researchers to publish abundance data as well as interaction networks. There is very little we can do to address these questions when re-analysing the limited data that have been made available.

   One thing we can do, however, is investigate the effects of lumping grasshoppers in with other herbivores. To that end, we have repeated our analyses excluding the plant-herbivore networks which contained grasshoppers. As removing these networks substantially reduces our already small collection of plant-herbivore networks, we retain these networks in the main text and present the re-analysis in the SI. [[What changed?]]

 4. Demand for further clarification of the methods

    \begin{refquote}

      Some methodological approaches are not clear and becase of that it would be impossible to replicate this study.

        \begin{itemize}
          \item Line 113-115. Why? Please explain.
          \item Line 122-125. How this difference is incorporated in the analysis? It is not clear. Differences between the two cases would not lead to an undesirable effect of generalism on your metric?
        \end{itemize}

      \end{refquote}

      \textbf{R:} We appreciate the Referee's frankness.

  5. The null model approach is confusing

    \begin{refquote}

      The null model approach (Lines 163-170) makes no sense for me. The authors permutate species between networks of a given type but not between networks of different types. Why? Plants that are animal-pollinated can be attacked by herbivores and animals pollinate many plants attacked by herbivores. In contrast, the authors randomize species from pollinator networks that are occuring in distinct biogeographical regions. I understand that in such kind of broad scale study we need to simplify the use of biological information, but a really robust approach would control for non-sense geographical swaps (e.g., among distinct continents) and to prevent the swap that place plants that are not pollinated by animals in pollinator networks but otherwise would allow that plant species to be swaped between network types.

      \end{refquote}

      \textbf{R:}

  6. Request for dated clades

    \begin{refquote}

      Lines 94-96. "These dates included divergence times in millions of years (My) between families and within some families, but did not give dates for divergences within genera". Please provide the dated clades.

      \end{refquote}

      \textbf{R:} The dated clades used in our original analyses are those given by Wikstrom \emph{et al.} ([[year]]). We have since re-created our analyses using the dated tree given in Zanne \emph{et al.} (2014) as found in the Phylomatic web application. We do not have separate dated clades for specific taxa. As both of these clades have already been published, repeating them in our manuscript would be purely redundant.

  7. The Referee is confused

    \begin{refquote}

      Some sentences are just hard to follow and/or are puzzling. Exemples include but are not limited to: "These relationships were also significantly related to the composition of the network’s plant component", "plants that produce noxious secondary metabolites may suffer fewer herbivores", "Interestingly, in our analyses the plant families associated with the steepest relationships between niche overlap and phylogenetic distance at the network level did not show particularly steep relationships within themselves".

    \end{refquote}

    \textbf{R:} We do not understand why the Referee finds some of the above examples confusing, particularly "plants that produce noxious secondary metabolites may suffer fewer herbivores". We have nevertheless rephrased the cited examples and revised our manuscript for clarity. This request for simpler phrasing often comes at the cost of brevity, which unfortanately makes it very difficult to comply with the Referee's demand for more biological detail (point 2). We hope that we have struck a reasonable balance between these two criticisms.

  8. The Referee hates our conclusion

    \begin{refquote}

      Line 331. "This may be because pairing antagonistic and mutualistic interactions balances the indirect effects of these interactions, leading to a more stable community (Sauve et al., 2014)". The attempt of explain patterns of interaction that are mold by selection acting on individuals and shaping populations in terms of advantages for the community makes no sense in the light of what we known about evolutionary biology and ecological communities, which are transient aggregations of coexisting species that show no clear boundaries in either space or time and from which there is little evidence of heritability in traits.

      \end{refquote}

      \textbf{R:} We are confused by the Referee's argument that communities show no clear boundaries in either space or time and that there is little evidence of heritability in traits within a community. This seems to suggest that the Referee does not believe in ecological communities or networks as viable units of study or in evolution (which requires heritability of traits). If this is so, then the Referee is not an appropriate reviewer for this manuscript. We instead hope that the Referee is attempting to make the point that communities are not shaped for the benefit of the species within them and simply doing so in an unclear way. That being the case, of course we are aware of this and agree 100\%. We did not intend to suggest that either species are selected to stabilize their communities or that communities are selected to maintain the species within them. We are well aware of spatial and temporal turnover, and of the fact that most communities are not at equilibrium and therefore we should not expect network structure to remain constant. Our point was rather that a more stable community is likely to persist longer than a less stable community and, therefore, more likely to be observed. We therefore expect communities with patterns of interactions condusive to long-term persistence to be over-represented in the empirical networks available to us. We have revised and expanded our conclusion to explicitly state that we are \textbf{not} suggesting any kind of community-level selection process, only the disproportionate change of unstable communities to more stable ones. We hope that this revision is less objectionable to the Referee.

\end{document}

### 2018-12-13 manuscript/coverletter.tex
adding code and ms

\documentclass[12pt]{letter}

% \usepackage[britdate]{canterbury-letter}
\usepackage[britdate,alyssa-signature]{canterbury-letter}
\usepackage{times}
% \usepackage{letterbib}
\usepackage{geometry}
% \usepackage[round]{natbib}
\usepackage{graphicx}
\geometry{a4paper}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage[running]{lineno}
\usepackage{amsmath,amsfonts,amssymb}
% \usepackage[margin=10pt,font=small,labelfont=bf]{caption}

%\usepackage{natbib}
% \bibpunct[; ]{(}{)}{;}{a}{,}{;}

\newenvironment{refquote}{\bigskip \begin{it}}{\end{it}\smallskip}

\newenvironment{figure}{}

\position{PhD Candidate}
\department{School of Biological Sciences}
\location{Private Bag 4800}
\telephone{+64 3 364 2729}
\fax{+64 3 364 2590}
\email{alyssa.cirtwill@pg.canterbury.ac.nz}
\url{http://stoufferlab.org}
\name{Alyssa R. Cirtwill}

% \position{PhD student}
% \department{School of Biological Sciences}
% \location{Private Bag 4800}
% \telephone{+64 3 364 2729}
% \fax{+64 3 364 2590}
% \email{alyssa.cirtwill@pg.canterbury.ac.nz}
% \url{http://stoufferlab.org}
% \name{Ms. Alyssa R. Cirtwill}

\newcommand{\mytitle}{\emph{Conservation of interaction partners between related plants varies widely across communities and between plant families.}}
\newcommand{\myjournal}{\emph{New Phytologist}}

\begin{document}

\begin{letter}{\bf Professor Alistair M. Hetherington\\
               Editor-in-Chief, New Phytologist\\
               Bailrigg House, Lancaster University\\
               Lancaster, UK\\
               LA1 4YE\\
                }

\opening{Dear Prof. Hetherington:}

We are happy to invite you to consider our manuscript 
``\mytitle'' for publication in the Interaction section of \myjournal. 
As detailed below, we believe that our study represents an important contribution
to plant science that will be of key interest to general readers of \myjournal.

\begin{enumerate}

\item What hypotheses or questions does this work address?

\smallskip 
Broadly, we test whether closely-related plants tend to share more
pollinators and/or herbivores. We test this hypothesis at the community level
and across plant families. Moreover, we link the two scales by investigating
whether the plant families in a community predict the community-level
relationship between relatedness and shared interaction partners. 
\smallskip

\item How does this work advance our current understanding of plant science?

\smallskip 
By taking a fine-scale approach to the conservation of interaction
partners, we gain a richer picture of the ways in which plant-animal
interactions are structured with respect to evolutionary history. In
particular, we demonstrate the variety of patterns of conservation across
families and propose potential mechanisms underlying these different
relationships. 
\smallskip

\item Why is this work important and timely?

\smallskip 
Plants' interactions with animals can significantly affect their
fitness for better and for worse. By comparing plant families displaying
different patterns of conservation of these interactions, we can predict which
families may experience different types of selection pressures. Thus, we can
use ecological data to guide future evolutionary research.

\end{enumerate}

We hope you will agree that the novelty of our approach and the significance
of our results justify consideration of our manuscript for \myjournal.

Thank you again for your consideration.

\closing{Regards,}

\end{letter}

% \newpage

% \setcounter{page}{1}

\end{document}

### 2018-12-13 manuscript/newphy_submitted.tex
adding code and ms

\documentclass[12pt]{article}  
\usepackage{amsmath}
\usepackage{url}
\usepackage[dvips]{graphicx}
\usepackage{multirow}
\usepackage{geometry}
\usepackage{pdflscape}
\usepackage{gensymb}
% \usepackage{rotating}
% make Figure 1 etc bold
\usepackage[labelfont=bf]{caption}
\usepackage{setspace}

\usepackage[running]{lineno}

\usepackage{dcolumn}
\newcolumntype{d}[1]{D{.}{.}{#1}}

%\usepackage{overcite}
\usepackage[round]{natbib}

\newcommand{\expect}[1]{\left\langle #1 \right\rangle}
\newcommand{\etal}{\textit{et al.\ }}

\newcommand{\beginsupplement}{%
        \setcounter{table}{0}
        \renewcommand{\thetable}{S\arabic{table}}%
        \setcounter{figure}{0}
        \renewcommand{\thefigure}{S\arabic{figure}}%
     }

% the abstract formatting
\newenvironment{sciabstract}{%
\begin{quote} \bf}
{\end{quote}}
\renewcommand\refname{References}

% margin sizes`
\topmargin 0.0cm
\oddsidemargin 0.2cm

\textwidth 16cm 
\textheight 21cm
\footskip 1.0cm

\title{Conservation of interaction partners between related plants varies widely across communities and between plant families.}

\author{Alyssa R. Cirtwill$^{1}$, Giulio V. Dalla Riva$^{2}$, Nick J. Baker$^{1}$,\\
 Joshua A. Thia$^{1,3}$, Christie J. Webber$^{1}$, Daniel B. Stouffer$^{1}$}
\date{\small$^1$Centre for Integrative Ecology, School of Biological Sciences\\
    \medskip$^2$Biomathematics Research Centre, School of Mathematics and Statistics\\
            University of Canterbury\\Private Bag 4800\\
Christchurch 8140, New Zealand\\
\medskip$^3$Present Address: School of Biological Sciences\\
University of Queensland\\Brisbane, QLD 4072, Australia }

\begin{document}
\maketitle
\baselineskip=8.5mm
\begin{spacing}{1.0}

\section*{Word Counts}

Main text: 4522

\begin{itemize}
  \item Introduction: 805 
  \item Materials and Methods: 1831 
  \item Results: 665
  \item Discussion: 1139 
  \item Acknowledgements: 83
\end{itemize}

Figures: 3

Tables: 2

Supporting information: 1 file containing 4 sections.

\vspace{0.4 in}

\section*{Summary}

  \begin{itemize}
    \item Related plants are often hypothesised to interact with similar sets of 
          pollinators and herbivores, but empirical support for this idea is mixed.
          Here we argue that this may be because some plant families vary in their 
          tendency to share interaction partners.

    \item We introduce a novel approach with which to quantify
          overlap of interaction
          partners for each pair of plants in 59 pollination and 11 herbivory
          networks.  We then tested for relationships between phylogenetic 
          distance and overlap within each network, and whether these 
          relationships varied with the composition of the plant community.
          Finally, we tested for different relationships within well-represented
          plant families.

    \item Across all networks, more closely-related plants tended to have 
          greater overlap, and this tendency was stronger in herbivory 
          networks than pollination networks. These relationships were also significantly related 
          to the composition of the network's plant component. Within plant families, 
          relationships varied greatly in both network types.

    \item The variety of relationships between phylogenetic distance and
          interaction partners in different plant families likely
          reflects a variety of ecological and evolutionary processes. To 
          understand the distribution of interactions within a community, 
          it is therefore important to consider factors affecting particular 
          plant families.

  \end{itemize}

\section*{Keywords}

defensive syndrome, ecological networks, herbivory, niche overlap, phylogenetic signal, pollination, pollination syndrome, specialisation

\end{spacing}
\begin{spacing}{1.5}

\section*{Introduction}
\linenumbers

  Interactions with animals affect plants' life cycles in several critical
  ways~\citep{Mayr2001,Sauve2015}. On one hand,
  pollination and other mutualistic interactions contribute
  to the reproductive success of many angiosperms~\citep{Ollerton2011}. 
  On the other, herbivores consume plant tissues~\citep{McCall2006} which
  costs plants energy and likely lowers their fitness.
  In both cases, these interactions do not occur randomly but
  are strongly influenced by plants' phenotypes. For example, plants that produce
  abundant or high-quality nectar may receive more visits from
  pollinators~\citep{Robertson1999} whereas plants that produce noxious secondary metabolites
  may suffer fewer herbivores~\citep{Johnson2014}. A plant's traits are also 
  likely to determine which specific pollinators and herbivores interact with that plant.
  Plants with different defences (e.g., thorns vs. chemical defences) may deter 
  different groups of herbivores~\citep{Ehrlich1964,Johnson2014}, and the concept
  of pollination syndromes has often been used to group plants into phenotypic
  classes believed to attract certain groups of pollinators~\citep{Waser1996,Fenster2004,Ollerton2009}.

  If attractive and/or defensive traits are heritable,
  then we can reasonably expect that related plants will have similar 
  patterns of interactions with animals~\citep{Schemske1999}.
  Recent studies that have investigated this question at the level of whole
  communities, however, have yielded mixed results~\citep{Rezende2007a,Gomez2010,Rohr2014a,Fontaine2015,Lind2015}.
  In particular, significant phylogenetic signal in plants' interaction partners
  ---the tendency for more closely-related plants to have more similar interactions---
  tends to be rare in empirical networks (\citealp{Rezende2007a,Lind2015}; but see~\citealp{Elias2013,Fontaine2015}).
  Further, plants' roles within networks tend to be less phylogenetically constrained than those of 
  animals~\citep{Rezende2007a,Chamberlain2014,Rohr2014,Vamosi2014,Lind2015}.

  Several mechanisms that might weaken the conservation of interactions
  have been identified in the literature. Pollination and herbivory may be affected
  by a wide variety of traits, and not all of these are likely to be
  phylogenetically conserved~\citep{Rezende2007,Kursar2009}. If, for example,
  floral displays are strongly affected by environmental conditions~\citep{Canto2004}, 
  then pollinators may not be predicted by plants' phylogenies.
  Even if the traits affecting pollination and herbivory are
  heritable, plants may experience conflicting selection pressures that
  weaken the overall association between plant phylogeny and interaction
  partners~\citep{Armbruster1997,Lankau2007,Siepielski2010,Wise2013}. 
  For instance, floral traits that
  are attractive to pollinators can also increase 
  herbivory~\citep{Strauss2002,Adler2004,Theis2006}. 
  Conversely, herbivory can reduce pollination by inducing chemical 
  defences~\citep{Adler2006} or altering floral display or nectar 
  availability~\citep{Strauss1997}. Observed patterns
  of similarity in plants' interaction partners therefore represent
  a mixture of environmental effects and various selection pressures as
  well as plants' shared phylogenetic history.

  A further complication is the possibility that the relationship between
  plants' relatedness and the similarity of their interaction partners is
  not constant across plant clades. Closely-related plants
  in one clade might be under strong selection to favour dissimilar
  sets of pollinators to avoid exchanging pollen with other
  species~\citep{Levin1970,Bell2005,Mitchell2009}. Similar pressures 
  could also affect related plants' defences against herbivores if 
  congeners tend to grow in the same places such that herbivores 
  could easily move between them.  Unrelated plants might also 
  converge upon similar phenotypes, attracting a particularly 
  efficient or abundant pollinator~\citep{Ollerton1996,Ollerton2009}. 
  Likewise, herbivores may be able to depredate sets of unrelated 
  plants if they have evolved similar defences~\citep{Pichersky2000}. 
  In either case, dissimilarity of interactions among related species 
  or similarity of interactions among unrelated species could result 
  in low apparent phylogenetic signal across an entire plant community. 
  Moreover, all of the aforementioned hypotheses 
  are non-exclusive; different processes likely affect different
  clades, and these processes might be associated with different 
  pressures imposed by pollination and herbivory.

  Here we use a novel approach to investigate how the patterns of
  overlap in interaction partners between pairs of plants (henceforth
  ``niche overlap'') vary over phylogenetic distance. Whereas previous
  studies have focused on the presence or absence of phylogenetic
  signal across entire networks, we are able to investigate the
  relationship between niche overlap and phylogenetic distance in
  within networks as well as different plant families. Specifically,
  we test whether niche overlap decreases over increasing phylogenetic
  distance in a large dataset of pollination and herbivory networks, 
  whether the plant family composition of a community affects the
  relationship between niche overlap and phylogenetic distance in that community,
  and whether the relationship between niche overlap and phylogenetic
  distance differs across plant families.

\section*{Materials and Methods}

\subsection*{Network data}

  We studied phylogenetic conservation of interactions within a 
  set of 59 pollination and 11 herbivory networks. 
  These networks span a range of biomes 
  (desert to scrub forest to grassland) and countries (Sweden to 
  Australia), and range in size between 18 and 996 total species 
  (mean 160.93, median 96) with seven to 131 plant species (mean 38.06, 
  median 28).
  To ensure that we were analysing interactions influenced by similar
  sets of traits across networks, we restricted our herbivory 
  networks to insects consuming leaves. This excluded sap-sucking, 
  leaf-mining, and galling insects as well as seed predators and
  xylophagous insects; all of these interactions involve different 
  plant tissues and means of feeding
  than leaf consumption and so may be influenced by different
  plant and insect traits. We also excluded networks which focused on
  plants from a single genus as these did not contain sufficient
  variation in phylogenetic distance between plants.
  See \emph{Table S1, Supporting Information} for details on the original 
  sources of all networks.

\subsection*{Phylogenetic data}

  In order to fit the plant species in all networks to a common phylogeny, 
  we first compared all species and genus names with the 
  National Center for Biotechnology Information
  and Taxonomic Name Resolution Service databases to ensure
  correctness. This was done using the function `get\_tsn' in the R~\citep{R}
  package taxize~\citep{taxize1,taxize2}. Species which could not 
  be assigned to an accepted taxonomic name (e.g., `Unknown Forb') were 
  discarded, as were those with non-unique common names and no binomial 
  name given (e.g., `Ragwort) or binomial names that could not be definitively 
  linked to  higher taxa (e.g., \emph{`Salpiglossus sp.'}). We were left with 
  2341 unique species in 1027 genera and 195 families. On average, 11.43\% of 
  plants were removed from each network (median 4.60\%, range 0-55.10\%).

  We then estimated phylogenetic distances between species. To accomplish 
  this, we constructed a phylogenetic tree for our dataset based on the 
  phylomatic `mega-tree' of higher plants (version 20120829)~\citep{APG2009}. 
  Where possible, we dated nodes on the mega-tree according to~\citet{Wikstrom2001}. 
  These dates included divergence times in millions of years (My) between families and 
  within some families, but did not give dates for divergences within genera. For those
  nodes that were not included in the mega-tree, we used the branch length adjustment
  algorithm bladj~\citep{Webb2008} to estimate the ages of all undated nodes. This 
  means that the ages in our phylogenies are approximations, but the presence of 
  even a subset of properly dated nodes within a phylogeny improves upon undated, purely
  taxonomic approaches~\citep{Webb2000}. To obtain trees for each network, we 
  pruned the dated mega-tree to include only species in that network.

\subsection*{Calculating niche overlap within communities}

  To fully describe the extent to which two plants' niches overlap,
  we defined the overlap between two plants' sets of interaction partners
  by recording the frequencies with which pairs of animals (where each animal 
  interacted with at least one plant) fall into three unique patterns
  (Fig.~\ref{overlap_patterns}). In the first pattern, both plants interact 
  with both animals, indicating total overlap for that quartet. In the second pattern, one plant
  interacts with both animal partners while the other
  interacts with only one animal, indicating partial overlap. In the third pattern,
  each animal interacts with only one plant, indicating no overlap. 
  Taken together, the frequencies of these three patterns of
  overlap can be used to describe the degree to which two plants have
  similar interaction partners. %

  Using the three patterns defined above provides more detail than other measures of overlap,
  such as the proportion of one species' partners that are shared with
  another as given by Jaccard similarity. In particular, comparing the probability of observing each pattern
  rather than one of the other two provides a measure of indirect
  interactions between plants by considering pairs of animal partners rather
  than each animal separately. For example, a pair of plants which share 
  two interaction partners are more likely to influence each other via these partners
  than two plants which do not share interaction partners. Moreover, our measure
  of overlap has greater statistical power than Jaccard dissimilarity because
  it includes information on the \emph{number} of shared interaction partners as
  well as the proportion. For instance, a pair of plants which together interact
  with 100 animals provides more information about shared overlap than a pair of
  plants which together interact with only one animal whereas the Jaccard similarity
  of both would simply be one.

\subsection*{Statistical analysis}

  To determine how overlap of interaction partners
  breaks down over phylogenetic distance,
  we modelled the probabilities of observing each pattern
  of overlap relative to the other two patterns.
  We expected that the frequency of the high- and moderate-overlap 
  patterns would decrease with increasing phylogenetic distance
  between two plants while the frequency of the low-overlap pattern would
  increase. As we expect pollination and herbivory networks could 
  show different patterns of overlap, we included effects of network 
  type and the interaction between network type and distance. Lastly, to
  account for the possibility that different communities show different
  characteristic relationships, we also included random effects of network ID on the slope 
  and intercept, giving a mixed-effects logistic regression of the form
  \begin{equation}
  logit(\omega_{pnij}) \propto \delta_{ij} + \rho_{n} + \delta_{ij}\rho_{n} + N_{n} + \delta_{ij}N_{n} ,
  \label{networklevel}
  \end{equation}

  \noindent where $\omega_{pnij}$ is the probability of overlap pattern $p$ occurring between
  species $i$ and $j$ in network $n$, $\delta_{ij}$ is the phylogenetic distance between 
  plants $i$ and $j$, $\rho_{n}$ is the network type (one in pollination networks,
  zero in herbivory networks), and $N_n$ and $\delta_{ij}N_{n}$ are random slope and intercepts 
  for network $n$. All models were fit using R function glmer from package lme4~\citep{lme4}.
  Sample size for these models was the sum (over all pairs of plants) of the number of pairs 
  of animals where each plant and each animal has at least one interaction partner. Over all 
  networks, there were 43,288,090 such sets of plants and animals, with a median of 72 (mean 
  671 +/- 2247) pairs of animals per pair of plants and median 58,528 (mean 636,590)
  plant-animal sets per network.

\subsection*{Linking network-level trends and community composition}

  Next, we examined the connection between our network-level observations
  and the plant families present in each community.
  Specifically, we tested the hypothesis that
  varying relationships between phylogenetic distance and
  pairwise niche overlap are due to the different distributions 
  of families across networks. To do this, we performed a non-parametric
  permutational multi-variate analysis of variance
  (PERMANOVA;~\citealp{Anderson2001}) using the change in log
  odds of observing each pattern of overlap to 
  predict the Bray-Curtis dissimilarity of networks
  based on the composition of their plant component
  (defined as the proportions of the plant community
  made up by each plant family present in the entire dataset).
  We used Bray-Curtis dissimilarity because, for a given
  pair of networks, only those plant families that appear
  in at least one network are considered~\citep{Anderson2001,Cirtwill2015}; 
  that is, the absence of rare plant families will not make 
  two networks appear more similar than they actually are.

  Note that a PERMANOVA does not assume that the data are 
  normally distributed, but rather compares the pseudo-$F$ 
  statistic calculated from the observed data to a null 
  distribution obtained by permuting the raw data. As 
  pollination and herbivory networks might have different
  community composition and the change in log odds of observing
  different patterns of overlap, we stratified these permutations
  by network type. That is, the change in log odds for a pollination
  network could only be exchanged for that of another pollination
  network. Stratifying the permutations in this way ensures that 
  the null distribution used to calculate the $P$-value is not 
  biased by including combinations of changes in log odds and 
  community composition that would not occur because of inherent 
  differences in the two network types (e.g., \emph{Pinaceae} 
  only appeared in herbivory networks and should not be assigned 
  to pollination networks). We used 9999 such stratified permutations 
  to obtain the null distribution and obtain a $P$-value.

  The PERMANOVA tests whether there is an association between
  community composition and network-level patterns but does not
  give any information on \emph{which} plant families have the
  greatest effects. To address this, we supplemented the 
  PERMANOVA with three constrained correspondence analyses (CCAs)
  which placed plant families along an axis representing the
  change in log odds of observing each pattern of overlap.
  A correspondence 
  analysis (CA) is similar to other multivariate
  analyses such as principal components analysis in that it
  reduces multivariate data to a set of orthogonal axes. A
  subset of axes that explain the majority of variation in 
  the data can then be interpreted to elucidate trends that
  were difficult to interpret in the full multivariate space.
  A constrained correspondence analysis (CCA) creates an extra
  axis based on some constraint - in this case, the change in
  log odds of observing each pattern of overlap.

\subsection*{Calculating niche overlap within families}

  Finally, we wished to compare the breakdown of overlap of interactions in
  different plant families. To do this, we used the same definitions of overlap
  and phylogenetic distance as in the within-network analysis but restricted
  our regressions to pairs of plants from the same family and the same network.
  In order to fit our regression models, we had to eliminate any family-network
  combination where there was no variation in the probabilities of any pattern of
  overlap or in phylogenetic distance.  This occurred, for example, when all 
  plant pairs in a given family in a given network were taken from the same genus
  (as divergence times in our dataset were not resolved within genera;~\citealp{Wikstrom2001}).
  Unlike in our previous analysis, we analysed data from pollination and
  herbivory networks separately as most well-represented plant families appeared
  in only one network type. For those families which appeared in both network types, 
  we ran separate analyses on each subset of data.

  For each plant family, within each network type, we then fit one of two similar 
  sets of models. First, when family $f$ was found in several networks of network
  type $t$, we fit mixed-effects logistic regressions for each pattern of overlap $\omega_{pntfij}$ of the form
  \begin{equation}
    logit(\omega_{pntfij}) \propto \delta_{ij} + N_{n} ,
    \label{full}
  \end{equation}

  \noindent where $\omega_{ptnfij}$ is the probability of overlap pattern $p$
  in network $n$ of network type $t$ for plants $i$ and $j$ in plant family $f$,
  $\delta_{ij}$ is the phylogenetic distance between plants $i$ and $j$, and
  $N_{n}$ is a random effect of network $n$.
  Second, if a plant family was represented in only one network 
  and therefore necessarily in only one network type, we omitted the 
  network-level random effect giving mixed-effects logistic regressions of the form
 \begin{equation}
    logit(\omega_{pntfij}) \propto \delta_{ij} .
    \label{minimal}
  \end{equation}

  \noindent We fit Eq.~\ref{full} using the function `glmer' from the
  R package lme4~\citep{lme4} and fit Eq.~\ref{minimal} in R using the
  function `glm' from the same package.

\section*{Results}

  \subsection*{Within-network conservation of niche overlap}

    Overlap of interaction partners decreased significantly with 
    increasing phylogenetic distance in pollination networks
    ($\beta_{\delta + \delta\rho}$ = -17.14 My$^{-1}$, $P$\textless0.001 
    for total overlap; $\beta_{\delta + \delta\rho}$ = -9.47 My$^{-1}$, 
    $P$\textless0.001 for partial overlap). In herbivory networks,
    these negative relationships were even stronger
    ($\beta_{\delta}$=-40.81 My$^{-1}$, $P$\textless0.001; 
    $\beta_{\delta}$=-16.47 My$^{-1}$, $P$=0.003 for total and 
    partial overlap, respectively). In both cases, the trends 
    for the no-overlap pattern were opposite to those described above, 
    as expected (see \emph{Notes S1, Supporting Information} for details).
    That is, a pair of plants in the same genus was more likely to share 
    interaction partners than a pair of plants in the same family in both types 
    of networks, but a pair of congeners would be less likely to share pollinators
    than to share herbivores.

    Further, plants were slightly less likely to share pollinators than herbivores 
    regardless of their phylogenetic distance ($\beta_{\rho}$=-0.94, 
    $P$=0.014 and $\beta_{\rho}$=-0.40, $P$=0.110 for total and partial 
    overlap, respectively). This may be due to the greater proportion of
    specialist pollinators than specialist herbivores. In our dataset, an
    average of 48\% (+/- 14) of pollinators in a given web were extreme 
    specialists (i.e., visited only one plant species) compared to 29\% 
    (+/- 29) of herbivores ($z$=5.62, df=68, $P$\textless0.001 
    for a binomial regression of specialists and generalists over network
    type).

    Despite these general trends, there was substantial variation between 
    pollination networks, with overlap of interaction partners decreasing 
    with increasing phylogenetic distance in some networks and increasing in 
    others (Fig.~\ref{within_network_regression}). For example, the 
    probability of observing the no-overlap pattern ranged from approximately 
    0.3 to over 0.95 over the entire range of divergence times observed in 
    our dataset. Herbivory networks were less variable in the directions of
    relationships between overlap and phylogenetic distance, but there was
    nevertheless a great deal of variation in probabilities across networks.
    In one network, for instance, the probability of observing the no-overlap
    pattern increased from 0.1 to 0.7 over 800 My of divergence time while
    in other networks the probability was much more constant. Overall, overlap 
    of interaction partners decreased with increasing phylogenetic distance in 
    77\% of pollination networks ($\beta_{\delta+\delta\rho+\delta N} $\textless0 
    in 46 of 59 networks for total overlap and in 45 of 59 networks for partial 
    overlap). All herbivory networks, on the other hand, showed decreasing overlap 
    with increasing  phylogenetic distance ($\beta_{\delta + \delta N}$\textless0 
    in 11 of 11 networks for total and partial overlap).

  \subsection*{Linking network-level trends and community composition}

    In each PERMANOVA, the change in log odds of observing a given 
    pattern of overlap in a given network was significantly associated 
    with the composition of the plant community in that network
    ($F_{1,68}$=1.79, $P$=0.019; $F_{1,68}$=1.92, 
    $P$=0.010; and $F_{1,68}$=1.81, $p$=0.015 for total
    overlap, partial overlap, and no overlap, respectively). 
    In the CCAs of community composition constrained by the change in
    log odds of observing each pattern of overlap, the largest decreases 
    in partial overlap with increasing phylogenetic distance were associated 
    with \emph{Begoniaceae}, \emph{Gleicheniaceae}, \emph{Myricaceae}, 
    \emph{Siparunaceae}, and \emph{Apocynaceae} (the ordering of plant
    families was qualitatively similar for total overlap and no overlap--
    see \emph{Notes S2, Supporting Information}). The largest increases
    in partial overlap with increasing phylogenetic distance were 
    associated with \emph{Surianaceae}, \emph{Malpighiaceae},
    \emph{Goodeniaceae}, \emph{Plumbaginaceae}, and \emph{Resedaceae}.

  \subsection*{Within-family conservation of niche overlap}

    The relationship between within-family niche overlap and phylogenetic distance
    varied widely in both pollination and herbivory networks. For the families
    that were well represented in pollination networks, overlap decreased
    with increasing phylogenetic distance in 18 (Table~\ref{family_slopes_pp}).
    There was no significant relationship between overlap and phylogenetic distance in
    a further 15 plant families. Finally, the overlap between pairs of \emph{Polygonaceae}
    increased with increasing phylogenetic distance. 
    Of the seven plant families that were sufficiently well represented in herbivory 
    networks, overlap decreased with increasing phylogenetic distance in four 
    (Table~\ref{family_slopes_ph}; Fig.~\ref{within_family_regression}). Two
    families did not show significant relationships between phylogenetic distance and overlap,
    and in one family, \emph{Fabaceae}, overlap of interaction partners increased with 
    increasing phylogenetic distance.

\section*{Discussion}

  We found broad support for the hypothesis that more
  closely-related pairs of plants have a higher degree
  of niche overlap. Using a novel method which considers
  all pairs of plants together, 
  the probability of two plants sharing the same animal 
  interaction partners decreased with increasing 
  phylogenetic distance. Considering networks separately,
  $\approx$78\%  of the pollination and all of the 
  herbivory networks exhibited the expected trend of decreasing 
  overlap with increasing distance.

  Within families, however, there was much greater variability. 
  More than half of the plant families in each network type
  behaved as we hypothesised, with more 
  closely-related plants having greater niche overlap than 
  distantly related plants. This relationship between overlap and 
  phylogenetic distance is consistent with the idea that traits affecting 
  interactions are heritable~\citep{Schemske1999} and changing gradually
  such that closely related plants resemble their common ancestor--- and
  each other ---more than they do distantly related plants. In some families, 
  such as \emph{Asteraceae} in pollination networks, the positive slope of 
  this relationship was very shallow while in others, such as 
  \emph{Melastomataceae} in herbivory networks, the positive slope was 
  extremely steep. This could indicate different rates of phenotypic drift 
  or evolution in different families.

  In contrast, \emph{Polygonaceae} in pollination networks and 
  \emph{Fabaceae} in herbivory networks showed the opposite 
  pattern. In these families, closely-related plants had 
  \emph{lower} overlap than more distantly-related pairs of plants. 
  There are several possible reasons a plant family might
  display this pattern. First, part of the family may have recently 
  undergone a period of rapid diversification with closely-related species 
  developing novel phenotypes that attract different animal 
  interaction partners~\citep{Linder2008,Breitkopf2015}. It is also possible that the
  animals have undergone an adaptive radiation to 
  specialise on their most profitable partner~\citep{Janz2006}. Second, this pattern 
  could be the result of ecological or environmental filtering~\citep{Mayfield2009,Ackerly2010}. 
  Closely-related species which have high degrees of overlap in their interaction 
  partners might compete too severely to coexist. This is especially likely
  for plants sharing pollinators, where the loss of pollen to related species 
  might severely limit reproductive success~\citep{Levin1970,Bell2005,Mitchell2009}.
  Indeed, animal pollination and seed dispersal have been shown to act
  as filters for several plant clades~\citep{Mayfield2009}.
  Distantly-related plants with similar interaction partners,
  on the other hand, may differ in some other aspect of their niches
  and so be able to coexist. Plants sharing herbivores are unlikely to
  compete for these interaction partners, but the presence of both
  plants in a community could support higher herbivore populations
  than could one species alone~\citep{Russell2007}. If the plants 
  compete for some other resource, the combined impact of herbivory
  and competition could eliminate the rarer plant species. Distantly-related
  plants sharing herbivores, conversely, would be less likely to compete
  for vital resources and more likely to persist.

  The remaining families did not show significant relationships 
  in either direction. That is, the niche overlap between two 
  plants did not vary linearly over phylogenetic distance. Once again, there 
  are several possible drivers for this trend (or lack thereof). These plants might 
  be highly specialised on different interaction partners and therefore
  have low overlap at all levels of relatedness. In other plant families
  with more moderate levels of specialisation, it is possible 
  that pollination and/or herbivory do not exert large
  selection pressures on the plants. If traits affecting pollination
  or herbivory are not heritable in these groups~\citep{Kursar2009}
  and that their phenotypes are constrained by other factors (e.g., 
  drought tolerance), then we should not expect a relationship 
  between phylogenetic distance and overlap of interaction partners.
  Alternatively, pollination and/or herbivory might exert large 
  pressures that maintain the clade within a pollination or 
  defensive syndrome. These syndromes are commonly believed to
  predict the pollinators or herbivores with which a plant will 
  interact~\citep{Waser1996,Fenster2004,Ollerton2009,Johnson2014}.
  As some recent studies have suggested that pollination syndromes
  do not accurately predict plants' visitors in all plant 
  families~\citep{Ollerton2009},
  it may be of interest for future researchers to test whether 
  syndromes are better predictors in families with weak 
  relationships between overlap and phylogenetic distance.
  Lastly, it is possible that the absence of a linear relationship 
  between niche overlap and phylogenetic distance is because the data
  actually exhibit a strongly non-linear one. This could result, for 
  example, from an early burst of diversification followed by a period
  of stasis~\citep{Davis2014}.

  For those families which were well-represented in both pollination
  and herbivory networks, we can also contrast the 
  trends in the two network types. In all five such cases, there was
  a significant relationship between overlap and phylogenetic 
  distance in only one network type (counting the singular 
  relationships in \emph{Rubiaceae} in pollination networks as 
  non-significant). This may indicate that one type of interaction
  places greater constraints upon these families than the other. Plants
  may not be able to respond to selection on both types of interaction
  simultaneously because traits affecting pollination can also affect herbivory, and vice
  versa~\citep{Strauss1997,Strauss2002,Adler2004,Adler2006,Theis2006}.
  Associations with pollinators and herbivores may also be constrained by the
  larger structure of the community. In one recent study, plants which are 
  visited by many pollinators are also consumed by many herbivores~\citep{Sauve2015}.
  This may be because pairing antagonistic and mutualistic interactions
  balances the indirect effects of these interactions, leading to a
  more stable community~\citep{Sauve2014}. As more networks describing 
  pollination and herbivory in the same community become available, it 
  will be interesting to test this hypothesis more thoroughly.

  Altogether, our study has revealed a wide variety of relationships 
  between overlap of interaction partners and phylogenetic distance 
  between plants in the same family. Regardless of the precise mechanisms
  behind these relationships, it is clear
  that the differences between families can affect the relationship
  between overlap and phylogenetic distance at the network level. 
  Interestingly, in our analyses the plant families associated with
  the steepest relationships between niche overlap and phylogenetic
  distance at the network level did not show particularly steep
  relationships within themselves. This result suggests
  that it is not just which plant families are present but the additional 
  relationships between the families that affects conservation of
  interactions at the network level and is consistent with previous
  work showing that the shape of phylogenetic tress, as well as the
  phylogenetic distances between species, can affect the strength
  of phylogenetic signal~\citep{Chamberlain2014a}. Our results 
  emphasise the importance of considering conservation of interactions at multiple scales.
  We hope that these results will help to guide future work investigating
  the genetic and environmental drivers underpinning these relationships.

\section*{Acknowledgements}

  We would like to thank the authors of the published networks used in this study. 
  We are grateful for the use of the Edward Percival field station in Kaikoura, 
  New Zealand in May, 2014. This research was supported by an NSERC PGS-D 
  graduate scholarship (to ARC), a Marsden Fund Fast-Start grant (UOC-1101) and a 
  Rutherford Discovery Fellowship, both administered by the Royal Society of New 
  Zealand (to DBS), a BlueFern HPC PhD scholarship (to NJB), and by
  the Allan Wilson Centre (to GVDR).

\section*{Author Contribution}

  ARC, DBS, GVDR, and NJB designed the research. ARC, JAT, and CJW collected published data.
  ARC and GVDR performed the analyses. All authors contributed to the manuscript.

\end{spacing}

\newpage
\bibliographystyle{newphy}
\renewcommand*{\bibfont}{\raggedright}
\bibliography{noisn}

\newpage
\section*{Tables}

  \begin{table}[!h]
  \caption{\small Change in log odds (per million years of phylogenetic distance) of observing total, partial, or
  no overlap in herbivores between a pair of plants in the same family. }
  \label{family_slopes_ph}
  \begin{tabular}{|l  rrr rrr|}
  \hline
  \multicolumn{1}{|c}{\multirow{2}{*}{Family}}
  & \multicolumn{2}{|c}{Total overlap} & \multicolumn{2}{|c}{Partial overlap} & \multicolumn{2}{|c|}{No overlap} \\
  \cline{2-7}
   & \multicolumn{1}{|c}{Odds ratio} & \multicolumn{1}{|c}{$P$-value} & \multicolumn{1}{|c}{Odds ratio} & \multicolumn{1}{|c}{$P$-value} & \multicolumn{1}{|c}{Odds ratio} & \multicolumn{1}{|c|}{$P$-value} \\
    \hline
  \emph{Asteraceae}      &  42.96 & \textbf{0.013}          &   2.04 & 0.820                   & -27.95 & \textbf{0.004} \\
  \emph{Rubiaceae}       & -66.12 & \textbf{\textless0.001} & -24.24 & \textbf{\textless0.001} &  55.60 & \textbf{\textless0.001} \\
  \emph{Melastomataceae} &-528.51 & 0.190                   &-923.08 & \textbf{\textless0.001} & 905.82 & \textbf{\textless0.001} \\
  \emph{Euphorbiaceae}   & -20.29 & \textbf{\textless0.001} &  -7.92 & \textbf{\textless0.001} &  17.60 & \textbf{\textless0.001} \\
  \emph{Fabaceae}        &  71.05 & \textbf{0.021}          &  32.33 & \textbf{\textless0.001} & -38.87 & \textbf{\textless0.001} \\
  \emph{Poaceae}         &  -5.91 & \textbf{\textless0.001} &  -3.97 & \textbf{\textless0.001} &   6.01 & \textbf{\textless0.001} \\
  \emph{Pinaceae}        & -47.11 & 0.351                   & -13.22 & 0.340                   &  16.95 & 0.215 \\
  \hline
  \end{tabular}
  \smallskip
  \footnotesize

  Only seven plant families were sufficiently diverse in our  dataset to permit this analysis
  (see \emph{Materials \\and Methods} for details). For each pattern of overlap, we show the change
  in log odds per million years \\and the associated $P$-value. Statistically significant values are
  indicated in bold. \\

  \end{table}

  \begin{table}[!h]
  \caption{\small Change in log odds (per million years of phylogenetic distance) of observing total, partial, or no overlap in pollinators between a pair of plants in the same family.}
  \small
  \label{family_slopes_pp}
  \begin{tabular}{|l  rrr rrr|}
  \hline
  \multicolumn{1}{|c}{\multirow{2}{*}{Family}}
  & \multicolumn{2}{|c}{Total overlap} & \multicolumn{2}{|c}{Partial overlap} & \multicolumn{2}{|c|}{No overlap} \\
  \cline{2-7}
   & \multicolumn{1}{|c}{Odds ratio} & \multicolumn{1}{|c}{$P$-value} & \multicolumn{1}{|c}{Odds ratio} & \multicolumn{1}{|c}{$P$-value} & \multicolumn{1}{|c}{Odds ratio} & \multicolumn{1}{|c|}{$P$-value} \\
    \hline
    \emph{Adoxaceae}        &   -    & -                       &  -33.37 & \textbf{\textless0.001} &  33.87 & \textbf{\textless0.001} \\
    \emph{Caprifoliaceae}   &   -    & -                       &    1.04 & 0.588                   &  -1.23 & 0.522 \\
    \emph{Apiaceae}         &  11.02 & \textbf{\textless0.001} &  -53.50 & \textbf{\textless0.001} &  59.57 & \textbf{\textless0.001} \\ 
    \emph{Asteraceae}*      &  -4.74 & \textbf{\textless0.001} &   -2.00 & \textbf{\textless0.001} &   2.38 & \textbf{\textless0.001} \\
    \emph{Apocynaceae}      &  -8.26 & \textbf{\textless0.001} &   -4.48 & \textbf{\textless0.001} &   5.67 & \textbf{\textless0.001} \\
    \emph{Rubiaceae}        & - & - & - & - & - & - \\
    \emph{Boraginaceae}     &  26.40 & 0.470                   &  -24.67 & \textbf{\textless0.001} &  23.85 & \textbf{\textless0.001} \\
    \emph{Lamiaceae}        &   5.81 & 0.528                   &    1.90 & 0.255                   &  -2.10 & 0.205 \\
    \emph{Orobanchaceae}    & 241.20 & 0.998                   &  261.90 & 0.995                   &-262.55 & 0.995 \\
    \emph{Plantaginaceae}   &-529.93 & 0.940                   &  -53.81 & \textbf{\textless0.001} &  58.36 & \textbf{\textless0.001} \\
    \emph{Oleaceae}         & -11.01 & 0.367                   &  -14.95 & \textbf{\textless0.001} &  14.90 & \textbf{\textless0.001} \\
    \emph{Solanaceae}       &  -     & -                       &   12.33 & 0.743                   & -25.57 & 0.484 \\
    \emph{Ericaceae}        &  -5.32 & \textbf{\textless0.001} &   -4.48 & \textbf{\textless0.001} &   5.02 & \textbf{\textless0.001} \\
    \emph{Primulaceae}      & -49.15 & \textbf{\textless0.001} &  -21.46 & \textbf{\textless0.001} &  23.22 & \textbf{\textless0.001} \\
    \emph{Hydrangeaceae}    &  -7.14 & \textbf{0.002}          &   -1.16 & \textbf{0.027}          &   1.47 & \textbf{0.004} \\
    \emph{Loasaceae}        & 482.42 & 0.998                   &  478.88 & 0.995                   &-485.71 & 0.995 \\
    \emph{Caryophyllaceae}  &  -3.42 & 0.167                   &   -3.63 & \textbf{\textless0.001} &   4.09 & \textbf{\textless0.001} \\
    \emph{Montiaceae}       & 346.61 & 0.999                   &  406.10 & 0.998                   &-406.90 & 0.998 \\
    \emph{Polygonaceae}     &  18.37 & \textbf{\textless0.001} &   14.63 & \textbf{\textless0.001} & -14.99 & \textbf{\textless0.001} \\
    \emph{Brassicaceae}     &  -6.04 & 0.260                   &   -1.34 & 0.302                   &   1.57 & 0.218 \\
    \emph{Cistaceae}        & -26.90 & \textbf{\textless0.001} &  -10.81 & \textbf{\textless0.001} &  13.33 & \textbf{\textless0.001} \\
    \emph{Malvaceae}        &  -1.29 & 0.558                   &   -4.59 & \textbf{\textless0.001} &   5.02 & \textbf{\textless0.001} \\
    \emph{Geraniaceae}      & -11.17 & \textbf{0.014}          &   -1.25 & 0.730                   &   9.96 & \textbf{0.013} \\
    \emph{Melastomataceae}* &  47.20 & 0.998                   &   52.97 & 0.993                   & -53.08 & 0.993 \\
    \emph{Myrtaceae}        & -70.37 & \textbf{\textless0.001} &  -44.38 & \textbf{\textless0.001} &  51.83 & \textbf{\textless0.001} \\
    \emph{Malpighiaceae}    &  -0.83 & 0.610                   &   -0.26 & 0.850                   &   0.99 & 0.513 \\
    \emph{Phyllanthaceae}   &-389.36 & 0.995                   &  -24.36 & \textbf{\textless0.001} &  24.88 & \textbf{\textless0.001} \\
    \emph{Fabaceae}*        &  14.19 & \textbf{0.011}          &    3.18 & 0.091                   &  -4.60 & \textbf{0.012} \\
    \emph{Rosaceae}         & -21.45 & \textbf{\textless0.001} &  -20.31 & \textbf{\textless0.001} &  21.50 & \textbf{\textless0.001} \\
    \emph{Saxifragaceae}    &  -4.00 & 0.053                   &    0.40 & 0.722                   &   0.79 & 0.474 \\
    \emph{Papaveraceae}     & -27.67 & \textbf{0.003}          &  -16.16 & \textbf{\textless0.001} &  16.80 & \textbf{\textless0.001} \\
    \emph{Ranunculaceae}    &  69.01 & 0.996                   &  -11.70 & \textbf{0.003}          &  10.73 & \textbf{0.006} \\
    \emph{Amaryllidaceae}   &   0.65 & 0.933                   &   -1.01 & 0.465                   &   0.97 & 0.480 \\
    \emph{Asparagaceae}     & -73.15 & \textbf{0.003}          &  -33.10 & \textbf{\textless0.001} &  35.56 & \textbf{\textless0.001} \\
    \emph{Iridaceae}        & 253.09 & 0.998                   &    1.68 & 0.773                   &  -2.30 & 0.691 \\
    \emph{Poaceae}*         & 343.63 & 0.996                   &  343.55 & 0.990                   &-344.97 & 0.990 \\
  \hline
  \end{tabular}
  \smallskip
  \footnotesize

    We were able to fit these models to 35 plant families (see \emph{Materials and Methods} for     details). 
    Families \\ marked with an asterisk were also highly diverse in herbivory networks. 
    Statistically significant values \\ are indicated in bold. Dashes indicate 
    plant families where the corresponding overlap 
    pattern was\\either extremely rare or omnipresent and the relevant model was uninformative.

    \end{table}

\clearpage

\section*{Figures}

  \begin{figure}[!h]
    \begin{center}
      % \centerline{\includegraphics*[width=.75\textwidth]{Figures/Sketches/methods_breakdown.eps}}
    \end{center}
     \caption{Visual depiction of our decomposition of pairwise niche overlap of plants' interaction
     partners. \textbf{(a)} First, consider the representation of any pollination or herbivory network
     as an adjacency matrix. Here, filled cells indicate an interaction between a particular plant 
     (letters on rows) and an animal (numbers on columns). \textbf{(b)} For a given pair of plants (e.g., plants 
     A and B), we then considered the set of animals that interact with at least one of the focal
     plants. Taking each pair of animals in this set in turn, we assigned the resulting quartet (the
     two focal plants plus two animals) to one of three patterns of overlap.
     In the \textbf{total overlap} pattern, both plants interact with both animals. 
     In the \textbf{partial overlap} pattern, one plant interacts with both animals and the other plant
     interacts with only one.
     Finally, in the \textbf{no overlap} pattern each animal interacts with only one plant; note that 
     this includes cases where both animals interact with the same plant (e.g., animals 1 and 5 and plant A)
     as well as cases where each animal interacts with a different plant (e.g., animals 1 with plant A and animal
     4 with plant B). \textbf{(c-e)} The number of times each pattern occurred was used to summarise the pairwise niche 
     overlap between the two plants and then related to their phylogenetic distance.}
    \label{overlap_patterns}
  \end{figure}

  \begin{figure}[!h]
    \begin{center}
      % \centerline{\includegraphics*[width=.75\textwidth]{Figures/dataplots/scaled_regression_lines_full_color.eps}}
    \end{center}
     \caption{Results of a mixed-effects logistic regression of pairwise niche overlap
     against phylogenetic distance for plants in 11
     herbivory networks (left; green) and 59 pollination
     networks (right; purple). In both network types, the probability of
     observing the total and partial overlap patterns tended to
     decrease as phylogenetic distance increased while the 
     probability of the no-overlap pattern tended to increase
     (thick, dark lines). There was also substantial variation
     between individual networks (thin, pale lines) of both types.
     The model is described in Eq. 1.}
    \label{within_network_regression}
  \end{figure}

  \begin{figure}[!h]
    \begin{center}
      % \centerline{\includegraphics*[height=.62\textheight]{Figures/dataplots/Family/allfams_full.eps}}
    \end{center}
     \caption{Change in log odds of observing different 
     patterns of pairwise niche overlap per million
     years of divergence time between a pair of plants
     in 38 separate plant families.
     Families in pollination networks are indicated
     by dark purple diamonds while families in herbivory
     networks are indicated by pale green circles.
     Note that changes in log odds are analogous to the 
     slopes of the regression lines from Eq. 2-3
     in logit-transformed space and represent
     the change in the probability of observing a pattern
     of overlap per million years of divergence time. We also
     show the slope of the relationship between the
     log-odds of observing each overlap pattern and 
     phylogenetic distance across all plant families
     in herbivory (pale, green horizontal line) and
     pollination (dark, purple horizontal line) networks.
     Arrows indicate significant values for~\emph{Melastomataceae} in
     herbivory networks which fell outside the plot margins.
     See~\emph{Figure S1; Supporting Information} for more details.
     The phylogenetic tree below the plots indicates the
     relatedness between plant families. Error bars represent 95\% confidence
     intervals.}
    \label{within_family_regression}
  \end{figure}

\end{document}

### 2018-12-13 manuscript/phylogenetic_signal_manuscript.tex
adding code and ms

--- 2018-12-13 manuscript/newphy_submitted.tex
@@
   than leaf consumption and so may be influenced by different
-  plant and insect traits. We also excluded networks which focused on
+  plant and insect traits. The bulk of our herbivory networks 
+  included only leaf-chewing insects. Where a network contained other
+  types of herbivores we removed the non-leaf-chewing insects. Any
+  plants which had no interaction partners after removing other types
+  of herbivores were also removed. We also excluded networks which focused on
   plants from a single genus as these did not contain sufficient
-  variation in phylogenetic distance between plants.
+  variation in phylogenetic distance between plants. This left us
+  with a final data set of 54 pollination and 11 herbivory networks.
   See \emph{Table S1, Supporting Information} for details on the original 
@@
   We then estimated phylogenetic distances between species. To accomplish 
-  this, we constructed a phylogenetic tree for our dataset based on the 
-  phylomatic `mega-tree' of higher plants (version 20120829)~\citep{APG2009}. 
-  Where possible, we dated nodes on the mega-tree according to~\citet{Wikstrom2001}. 
-  These dates included divergence times in millions of years (My) between families and 
-  within some families, but did not give dates for divergences within genera. For those
-  nodes that were not included in the mega-tree, we used the branch length adjustment
-  algorithm bladj~\citep{Webb2008} to estimate the ages of all undated nodes. This 
-  means that the ages in our phylogenies are approximations, but the presence of 
-  even a subset of properly dated nodes within a phylogeny improves upon undated, purely
-  taxonomic approaches~\citep{Webb2000}. To obtain trees for each network, we 
+  this, we constructed a phylogenetic tree for our dataset based on a dated
+  `mega-tree' of angiosperms~\citep{Zanne2014}. Some species were not included
+  in the angiosperm mega-tree (largely ferns and tree ferns). For angiosperms,
+  a sister taxon was identified using~\citet{APW} and the species added manually.
+  Ferns, tree ferns, and a single club moss were added to the base of the tree.
+  This means that closely-related non-angiosperm species appear to have very long 
+  phylogenetic distances between them. For this reason, we excluded comparisons 
+  between pairs of non-angiosperms from our analyses. As only two networks (both 
+  plant-herbivore networks) included more than one such species and non-angiosperms
+  were always a small minority of any network, we do not 
+  believe that omitting these comparisons has greatly affected our results.
+  To obtain trees for each network, we 
   pruned the dated mega-tree to include only species in that network.
@@
 
-  To fully describe the extent to which two plants' niches overlap,
-  we defined the overlap between two plants' sets of interaction partners
-  by recording the frequencies with which pairs of animals (where each animal 
-  interacted with at least one plant) fall into three unique patterns
-  (Fig.~\ref{overlap_patterns}). In the first pattern, both plants interact 
-  with both animals, indicating total overlap for that quartet. In the second pattern, one plant
-  interacts with both animal partners while the other
-  interacts with only one animal, indicating partial overlap. In the third pattern,
-  each animal interacts with only one plant, indicating no overlap. 
-  Taken together, the frequencies of these three patterns of
-  overlap can be used to describe the degree to which two plants have
-  similar interaction partners. %
+  We calculated niche overlap for each pair of species within
+  a community using a modified Jaccard index. The 
+  Jaccard index $J_{ij}$ describes the proportion of shared interaction 
+  partners for for species $i$ and $j$ and is defined as:
 
-  Using the three patterns defined above provides more detail than other measures of overlap,
-  such as the proportion of one species' partners that are shared with
-  another as given by Jaccard similarity. In particular, comparing the probability of observing each pattern
-  rather than one of the other two provides a measure of indirect
-  interactions between plants by considering pairs of animal partners rather
-  than each animal separately. For example, a pair of plants which share 
-  two interaction partners are more likely to influence each other via these partners
-  than two plants which do not share interaction partners. Moreover, our measure
-  of overlap has greater statistical power than Jaccard dissimilarity because
-  it includes information on the \emph{number} of shared interaction partners as
-  well as the proportion. For instance, a pair of plants which together interact
-  with 100 animals provides more information about shared overlap than a pair of
-  plants which together interact with only one animal whereas the Jaccard similarity
-  of both would simply be one.
+  \begin{equation}
+    J_{ij} = \frac{M_{ij}}{P_i+P_j-M_ij} ,,
+  \end{equation}
+
+  where $M_{ij}$ is the set of \emph{mutual} (shared) interaction partners of 
+  species $i$ and $j$ and $P_i$ and $P_j$ are the sets of interaction 
+  \emph{partners} for species $i$ and $j$ respectively. We wished to give more 
+  weight to species sharing a large number of interaction partners as well as 
+  those sharing a large proportion (i.e., to emphasize pairs of generalists 
+  sharing most of their interaction partners over specialists sharing a single 
+  interaction partner). We therefore recorded, for each species, the number of 
+  shared interaction partners $M_{ij}$ and the number of interaction partners 
+  that were not shared ($U_{ij}$ = $P_{i}$+$P_{j}$-2$M_{ij}$). Instead of a 
+  single index $J_{ij}$ we therefore defined niche overlap between species
+  $i$ and $j$ as a tuple: ($M_{ij}$, $U_{ij}$).
+
+  % To fully describe the extent to which two plants' niches overlap,
+  % we defined the overlap between two plants' sets of interaction partners
+  % by recording the frequencies with which pairs of animals (where each animal 
+  % interacted with at least one plant) fall into three unique patterns
+  % (Fig.~\ref{overlap_patterns}). In the first pattern, both plants interact 
+  % with both animals, indicating total overlap for that quartet. In the second pattern, one plant
+  % interacts with both animal partners while the other
+  % interacts with only one animal, indicating partial overlap. In the third pattern,
+  % each animal interacts with only one plant, indicating no overlap. 
+  % Taken together, the frequencies of these three patterns of
+  % overlap can be used to describe the degree to which two plants have
+  % similar interaction partners. %
+
+  % Using the three patterns defined above provides more detail than other measures of overlap,
+  % such as the proportion of one species' partners that are shared with
+  % another as given by Jaccard similarity. In particular, comparing the probability of observing each pattern
+  % rather than one of the other two provides a measure of indirect
+  % interactions between plants by considering pairs of animal partners rather
+  % than each animal separately. For example, a pair of plants which share 
+  % two interaction partners are more likely to influence each other via these partners
+  % than two plants which do not share interaction partners. Moreover, our measure
+  % of overlap has greater statistical power than Jaccard dissimilarity because
+  % it includes information on the \emph{number} of shared interaction partners as
+  % well as the proportion. For instance, a pair of plants which together interact
+  % with 100 animals provides more information about shared overlap than a pair of
+  % plants which together interact with only one animal whereas the Jaccard similarity
+  % of both would simply be one.
+
+  % [[It appears we switched to Jaccard and Sorenson dissimilarities - number of shared partners and number of shared partners*2/notshared.]]
 
@@
 
-  To determine how overlap of interaction partners
-  breaks down over phylogenetic distance,
-  we modelled the probabilities of observing each pattern
-  of overlap relative to the other two patterns.
-  We expected that the frequency of the high- and moderate-overlap 
-  patterns would decrease with increasing phylogenetic distance
-  between two plants while the frequency of the low-overlap pattern would
-  increase. As we expect pollination and herbivory networks could 
-  show different patterns of overlap, we included effects of network 
-  type and the interaction between network type and distance. Lastly, to
-  account for the possibility that different communities show different
-  characteristic relationships, we also included random effects of network ID on the slope 
-  and intercept, giving a mixed-effects logistic regression of the form
-  \begin{equation}
-  logit(\omega_{pnij}) \propto \delta_{ij} + \rho_{n} + \delta_{ij}\rho_{n} + N_{n} + \delta_{ij}N_{n} ,
-  \label{networklevel}
-  \end{equation}
+  We modelled the relationship between niche overlap and phylogenetic distance
+  using a logistic regression. We used both the numbers of shared and 
+  non-shared partners as dependent variables and centred, scaled phylogenetic 
+  distance as the independent variable. This is conceptually similar to 
+  modelling successes and failures in a binomial-distributed process. 
+  Accordingly, we assumed a binomial distribution for residuals. All regressions were fit using the R~\citep{R} function 
+  ``glm'' from package \emph{lme4}~\citep{lme4}. To avoid potential 
+  confounding effects of different relationships in different networks, we 
+  modelled the relationship between overlap and phylogenetic distance within 
+  each network separately.
 
-  \noindent where $\omega_{pnij}$ is the probability of overlap pattern $p$ occurring between
-  species $i$ and $j$ in network $n$, $\delta_{ij}$ is the phylogenetic distance between 
-  plants $i$ and $j$, $\rho_{n}$ is the network type (one in pollination networks,
-  zero in herbivory networks), and $N_n$ and $\delta_{ij}N_{n}$ are random slope and intercepts 
-  for network $n$. All models were fit using R function glmer from package lme4~\citep{lme4}.
-  Sample size for these models was the sum (over all pairs of plants) of the number of pairs 
-  of animals where each plant and each animal has at least one interaction partner. Over all 
-  networks, there were 43,288,090 such sets of plants and animals, with a median of 72 (mean 
-  671 +/- 2247) pairs of animals per pair of plants and median 58,528 (mean 636,590)
-  plant-animal sets per network.
+  Note that pairs of plants are not always independent: the same plant will
+  appear in many pairs. This violates the assumption of independence used when 
+  calculating the significance of logistic regressions within the R~\citep{R} 
+  package \emph{lme4}~\citep{lme4}. To calculate significance of the 
+  relationships we observed, it was therefore necessary to compare the 
+  observed relationships to those in a suite of random networks. To create 
+  these networks, we shuffled interactions among species while preserving row 
+  and column totals. That is, each species retained the same number of 
+  interaction partners as in the observed network but the exact set of 
+  partners (and therefore niche overlaps with all other species) varied across 
+  random networks. We preserved the observed phylogenetic relationships 
+  between species in all cases. For each observed network, we created 999 such 
+  random networks and calculated the relationship between niche overlap and 
+  phylogenetic distance. This gave us a null distribution for each observed 
+  network with which to determine the significance of the observed 
+  relationship.
+
+  This randomization approach also allows us to estimate type I and type II 
+  error for our analysis. To do this, we created 500 randomizations of each 
+  random network and, again keeping the observed phylogenetic distances 
+  between plant species, repeated our analyses. We can then determine the 
+  number of randomized networks which appear to have significant 
+  overlap-phylogenetic distance relationships relative to the randomizations 
+  of these random networks (type I error). [[How does this get at type II error?]]
+
+  % To determine how overlap of interaction partners
+  % breaks down over phylogenetic distance,
+  % we modelled the probabilities of observing each pattern
+  % of overlap relative to the other two patterns.
+  % We expected that the frequency of the high- and moderate-overlap 
+  % patterns would decrease with increasing phylogenetic distance
+  % between two plants while the frequency of the low-overlap pattern would
+  % increase. As we expect pollination and herbivory networks could 
+  % show different patterns of overlap, we included effects of network 
+  % type and the interaction between network type and distance. Lastly, to
+  % account for the possibility that different communities show different
+  % characteristic relationships, we also included random effects of network ID on the slope 
+  % and intercept, giving a mixed-effects logistic regression of the form
+  % \begin{equation}
+  % logit(\omega_{pnij}) \propto \delta_{ij} + \rho_{n} + \delta_{ij}\rho_{n} + N_{n} + \delta_{ij}N_{n} ,
+  % \label{networklevel}
+  % \end{equation}
+
+  % \noindent where $\omega_{pnij}$ is the probability of overlap pattern $p$ occurring between
+  % species $i$ and $j$ in network $n$, $\delta_{ij}$ is the phylogenetic distance between 
+  % plants $i$ and $j$, $\rho_{n}$ is the network type (one in pollination networks,
+  % zero in herbivory networks), and $N_n$ and $\delta_{ij}N_{n}$ are random slope and intercepts 
+  % for network $n$. All models were fit using R function glmer from package lme4~\citep{lme4}.
+  % Sample size for these models was the sum (over all pairs of plants) of the number of pairs 
+  % of animals where each plant and each animal has at least one interaction partner. Over all 
+  % networks, there were 43,288,090 such sets of plants and animals, with a median of 72 (mean 
+  % 671 +/- 2247) pairs of animals per pair of plants and median 58,528 (mean 636,590)
+  % plant-animal sets per network.
 
@@
   (PERMANOVA;~\citealp{Anderson2001}) using the change in log
-  odds of observing each pattern of overlap to 
+  odds of two plants sharing an interaction partner to 
   predict the Bray-Curtis dissimilarity of networks
@@
   pollination and herbivory networks might have different
-  community composition and the change in log odds of observing
-  different patterns of overlap, we stratified these permutations
+  community composition, we stratified these permutations
   by network type. That is, the change in log odds for a pollination
@@
   which placed plant families along an axis representing the
-  change in log odds of observing each pattern of overlap.
+  change in log odds of sharing an interaction partner.
   A correspondence 
@@
   axis based on some constraint - in this case, the change in
-  log odds of observing each pattern of overlap.
+  log odds of sharing an interaction partner.
 
@@
   our regressions to pairs of plants from the same family and the same network.
-  In order to fit our regression models, we had to eliminate any family-network
-  combination where there was no variation in the probabilities of any pattern of
-  overlap or in phylogenetic distance.  This occurred, for example, when all 
-  plant pairs in a given family in a given network were taken from the same genus
-  (as divergence times in our dataset were not resolved within genera;~\citealp{Wikstrom2001}).
   Unlike in our previous analysis, we analysed data from pollination and
@@
   sets of models. First, when family $f$ was found in several networks of network
-  type $t$, we fit mixed-effects logistic regressions for each pattern of overlap $\omega_{pntfij}$ of the form
+  type $t$, we fit mixed-effects logistic regressions for the probability of sharing an interaction partner $\omega_{ntfij}$ of the form
   \begin{equation}
-    logit(\omega_{pntfij}) \propto \delta_{ij} + N_{n} ,
+    logit(\omega_{ntfij}) \propto \delta_{ij} + N_{n} ,
     \label{full}
@@
 
-  \noindent where $\omega_{ptnfij}$ is the probability of overlap pattern $p$
+  \noindent where $\omega_{tnfij}$ is the probability of sharing a partner 
   in network $n$ of network type $t$ for plants $i$ and $j$ in plant family $f$,
@@
 
-    Overlap of interaction partners decreased significantly with 
-    increasing phylogenetic distance in pollination networks
-    ($\beta_{\delta + \delta\rho}$ = -17.14 My$^{-1}$, $P$\textless0.001 
-    for total overlap; $\beta_{\delta + \delta\rho}$ = -9.47 My$^{-1}$, 
-    $P$\textless0.001 for partial overlap). In herbivory networks,
-    these negative relationships were even stronger
-    ($\beta_{\delta}$=-40.81 My$^{-1}$, $P$\textless0.001; 
-    $\beta_{\delta}$=-16.47 My$^{-1}$, $P$=0.003 for total and 
-    partial overlap, respectively). In both cases, the trends 
-    for the no-overlap pattern were opposite to those described above, 
-    as expected (see \emph{Notes S1, Supporting Information} for details).
-    That is, a pair of plants in the same genus was more likely to share 
-    interaction partners than a pair of plants in the same family in both types 
-    of networks, but a pair of congeners would be less likely to share pollinators
-    than to share herbivores.
-
-    Further, plants were slightly less likely to share pollinators than herbivores 
-    regardless of their phylogenetic distance ($\beta_{\rho}$=-0.94, 
-    $P$=0.014 and $\beta_{\rho}$=-0.40, $P$=0.110 for total and partial 
-    overlap, respectively). This may be due to the greater proportion of
+    Across all networks, overlap of interaction partners decreased with increasing phylogenetic distance and the decrease in overlap of pollinators was steeper than that in herbivores ($\beta_{distance}$=-6.82, $p$\textless0.001 and $\beta_{distance:PP}$=-18.5, $p$\textless0.001, respectively).
+That is, a pair of plants in the same genus was more likely to share interaction partners than a pair of plants in the same family in both types of networks, but a pair of congeners would be less likely to share pollinators than to share herbivores.
+Regardless of phylogenetic distance, a pair of plants were also less likely to share pollinators than herbivores ($\beta_{PP}$=-1.44, $p$\textless0.001).
+This may be due to the greater proportion of
     specialist pollinators than specialist herbivores. In our dataset, an
@@
     for a binomial regression of specialists and generalists over network
-    type).
+    type). % Are the above betas un-scaled?
 
@@
     with increasing phylogenetic distance in some networks and increasing in 
-    others (Fig.~\ref{within_network_regression}). For example, the 
-    probability of observing the no-overlap pattern ranged from approximately 
-    0.3 to over 0.95 over the entire range of divergence times observed in 
-    our dataset. Herbivory networks were less variable in the directions of
-    relationships between overlap and phylogenetic distance, but there was
-    nevertheless a great deal of variation in probabilities across networks.
-    In one network, for instance, the probability of observing the no-overlap
-    pattern increased from 0.1 to 0.7 over 800 My of divergence time while
-    in other networks the probability was much more constant. Overall, overlap 
-    of interaction partners decreased with increasing phylogenetic distance in 
-    77\% of pollination networks ($\beta_{\delta+\delta\rho+\delta N} $\textless0 
-    in 46 of 59 networks for total overlap and in 45 of 59 networks for partial 
-    overlap). All herbivory networks, on the other hand, showed decreasing overlap 
-    with increasing  phylogenetic distance ($\beta_{\delta + \delta N}$\textless0 
-    in 11 of 11 networks for total and partial overlap).
+    others (Fig.~\ref{within_network_regression}).
+Overlap of interaction partners decreased significantly with increasing phylogenetic distance in 7/11 plant-herbivore networks and 33/59 plant-pollinator networks.
+In the remaining four plant-herbivore networks and 25 of the 26 remaining plant-pollinator networks, overlap of interaction partners was not related to phylogenetic distance.
+Overlap of interaction partners increased with increasing phylogenetic distance in only a single plant-pollinator network.
+% (M_PL_026).
+
+    [[Reviewers demanded this - it seems very boring]]
+    Comparing the results in the observed networks to those obtained after randomising phylogenetic distances across pairs of plants, the observed slope of the relationship between phylogenetic distance and interaction partner overlap was always more extreme (i.e., always lesser or always greater) than that obtained in the random networks.
+Observed networks with a negative relationship between phylogenetic distance and overlap always had a more negative slope than that obtained from the random networks, while the 10 networks with positive relationships between phylogenetic distance and overlap always had more positive relationships than the random networks.
+
+    Comparing the random networks to randomizations of the random networks, the slope obtained from the initial random network was quite variable with respect to the slopes obtained from 500 randomizations of the random network.
+Averaged over the 1000 randomizations of each observed network, the slope of the random network was more extreme than 48.1-51.3\% of the randomizations of the random network.
+This confirms that shuffling phylogenetic distances between plant pairs destroys the relationship between distance and interaction partner overlap, and that further shuffling distances does not have a predictable effect.
 
@@
 
-    In each PERMANOVA, the change in log odds of observing a given 
-    pattern of overlap in a given network was significantly associated 
-    with the composition of the plant community in that network
-    ($F_{1,68}$=1.79, $P$=0.019; $F_{1,68}$=1.92, 
-    $P$=0.010; and $F_{1,68}$=1.81, $p$=0.015 for total
-    overlap, partial overlap, and no overlap, respectively). 
-    In the CCAs of community composition constrained by the change in
-    log odds of observing each pattern of overlap, the largest decreases 
-    in partial overlap with increasing phylogenetic distance were associated 
-    with \emph{Begoniaceae}, \emph{Gleicheniaceae}, \emph{Myricaceae}, 
-    \emph{Siparunaceae}, and \emph{Apocynaceae} (the ordering of plant
-    families was qualitatively similar for total overlap and no overlap--
-    see \emph{Notes S2, Supporting Information}). The largest increases
-    in partial overlap with increasing phylogenetic distance were 
-    associated with \emph{Surianaceae}, \emph{Malpighiaceae},
-    \emph{Goodeniaceae}, \emph{Plumbaginaceae}, and \emph{Resedaceae}.
+    We were interested in whether the slope of the relationship between phylogenetic distance varied with community composition.
+In a PERMANOVA of slope against community composition, stratified by network type, we did not find a significant relationship between slope and community composition ($F_{1,68}$=1.06, $p$=0.493).
+Of the 200 families in our dataset, only 29 were represented by more than 20 species.
+Lumping all other families into an "other" category and repeating the PERMANOVA, we still did not find a significant relationship between slope and community composition ($F_{1,68}$=1.12, $p$=0.409).
+    % Also performed a CCA to see which fams had most positive/negative associations, but with non-sig results I don't think it's interesting.
 
-  \subsection*{Within-family conservation of niche overlap}
+  \subsection*{Within-family conservation of niche overlap} [[Still of interest given negative result above?]]
+
+    Taking all families together, the probability of species in the same family sharing interaction partners decreased wiht increasing phylogenetic distance in both plant-pollinator and plant-herbivore networks and the strength of this relationship did not differ significantly between network types ($\beta_{distance}$=-4.75, $p$=0.012; $\beta_{distance:PH}$=-1.73, $p$=0.681).
+Plants in plant-herbivore networks had a higher probability of sharing interaction partners with a member of the same family ($\beta_{PH}$=0.78, $p$=0.007).
 
     The relationship between within-family niche overlap and phylogenetic distance
-    varied widely in both pollination and herbivory networks. For the families
+    varied widely in both pollination and herbivory networks. 
+    % Gotta separate plant-herb and plant-poll networks.
+
+    For the families
     that were well represented in pollination networks, overlap decreased
@@
 
-\section*{Discussion}
+    Models for two families did not converge.
+In both the \emph{Lauraceae}, (represented by four species in one pollination network) and the \emph{Sapindaceae} in plant-herbivore networks (represented by five species in one network), one pair of species shared a single interaction partner while all other pairs did not share any interaction partners.
+The model for \emph{Sapindaceae} in plant-pollinator networks did converge.
+
+\section*{Discussion} [[not updated post new results]]
 
@@
   \begin{table}[!h]
-  \caption{\small Change in log odds (per million years of phylogenetic distance) of observing total, partial, or
-  no overlap in herbivores between a pair of plants in the same family. }
+  \caption{\small Change in log odds (per million years of phylogenetic distance) of a pair of plants in the same family sharing a herbivore.}
   \label{family_slopes_ph}
-  \begin{tabular}{|l  rrr rrr|}
+  \begin{tabular}{|l  rr|}
   \hline
-  \multicolumn{1}{|c}{\multirow{2}{*}{Family}}
-  & \multicolumn{2}{|c}{Total overlap} & \multicolumn{2}{|c}{Partial overlap} & \multicolumn{2}{|c|}{No overlap} \\
-  \cline{2-7}
-   & \multicolumn{1}{|c}{Odds ratio} & \multicolumn{1}{|c}{$P$-value} & \multicolumn{1}{|c}{Odds ratio} & \multicolumn{1}{|c}{$P$-value} & \multicolumn{1}{|c}{Odds ratio} & \multicolumn{1}{|c|}{$P$-value} \\
+    Family & Change in log odds & $P$-value \\
     \hline
-  \emph{Asteraceae}      &  42.96 & \textbf{0.013}          &   2.04 & 0.820                   & -27.95 & \textbf{0.004} \\
-  \emph{Rubiaceae}       & -66.12 & \textbf{\textless0.001} & -24.24 & \textbf{\textless0.001} &  55.60 & \textbf{\textless0.001} \\
-  \emph{Melastomataceae} &-528.51 & 0.190                   &-923.08 & \textbf{\textless0.001} & 905.82 & \textbf{\textless0.001} \\
-  \emph{Euphorbiaceae}   & -20.29 & \textbf{\textless0.001} &  -7.92 & \textbf{\textless0.001} &  17.60 & \textbf{\textless0.001} \\
-  \emph{Fabaceae}        &  71.05 & \textbf{0.021}          &  32.33 & \textbf{\textless0.001} & -38.87 & \textbf{\textless0.001} \\
-  \emph{Poaceae}         &  -5.91 & \textbf{\textless0.001} &  -3.97 & \textbf{\textless0.001} &   6.01 & \textbf{\textless0.001} \\
-  \emph{Pinaceae}        & -47.11 & 0.351                   & -13.22 & 0.340                   &  16.95 & 0.215 \\
+    \emph{Asteraceae} & -1.73 &  0.550 \\
+    \emph{Euphorbiaceae} & -19.2 & \textbf{\textless0.001} \\
+    \emph{Fabaceae} & 18.7 &  \textbf{0.046} \\
+    \emph{Melastomataceae} & -13.2 & \textbf{0.022} \\
+    \emph{Moraceae} & -2.13 & 0.092 \\
+    \emph{Nothofagaceae} & -595 & \textgreater{0.999} \\
+    \emph{Pinaceae} &  -25.8 & 0.733 \\
+    \emph{Poaceae} & -4.50 & \textbf{0.020} \\
+    \emph{Rubiaceae} & -8.16 &  \textbf{0.006} \\
   \hline
@@
 
-  Only seven plant families were sufficiently diverse in our  dataset to permit this analysis
+  Nine plant families were sufficiently diverse in our  dataset to permit this analysis
   (see \emph{Materials \\and Methods} for details). For each pattern of overlap, we show the change
@@
   \begin{table}[!h]
-  \caption{\small Change in log odds (per million years of phylogenetic distance) of observing total, partial, or no overlap in pollinators between a pair of plants in the same family.}
+  \caption{
+  \small Change in log odds (per million years of phylogenetic distance) of a pair of plants in the same family sharing a pollinator.}
   \small
   \label{family_slopes_pp}
-  \begin{tabular}{|l  rrr rrr|}
+  \begin{tabular}{|l  rr|}
     \hline
-  \multicolumn{1}{|c}{\multirow{2}{*}{Family}}
-  & \multicolumn{2}{|c}{Total overlap} & \multicolumn{2}{|c}{Partial overlap} & \multicolumn{2}{|c|}{No overlap} \\
-  \cline{2-7}
-   & \multicolumn{1}{|c}{Odds ratio} & \multicolumn{1}{|c}{$P$-value} & \multicolumn{1}{|c}{Odds ratio} & \multicolumn{1}{|c}{$P$-value} & \multicolumn{1}{|c}{Odds ratio} & \multicolumn{1}{|c|}{$P$-value} \\
+    Family  & Change in log odds & $P$-value \\
     \hline
-    \emph{Adoxaceae}        &   -    & -                       &  -33.37 & \textbf{\textless0.001} &  33.87 & \textbf{\textless0.001} \\
-    \emph{Caprifoliaceae}   &   -    & -                       &    1.04 & 0.588                   &  -1.23 & 0.522 \\
-    \emph{Apiaceae}         &  11.02 & \textbf{\textless0.001} &  -53.50 & \textbf{\textless0.001} &  59.57 & \textbf{\textless0.001} \\ 
-    \emph{Asteraceae}*      &  -4.74 & \textbf{\textless0.001} &   -2.00 & \textbf{\textless0.001} &   2.38 & \textbf{\textless0.001} \\
-    \emph{Apocynaceae}      &  -8.26 & \textbf{\textless0.001} &   -4.48 & \textbf{\textless0.001} &   5.67 & \textbf{\textless0.001} \\
-    \emph{Rubiaceae}        & - & - & - & - & - & - \\
-    \emph{Boraginaceae}     &  26.40 & 0.470                   &  -24.67 & \textbf{\textless0.001} &  23.85 & \textbf{\textless0.001} \\
-    \emph{Lamiaceae}        &   5.81 & 0.528                   &    1.90 & 0.255                   &  -2.10 & 0.205 \\
-    \emph{Orobanchaceae}    & 241.20 & 0.998                   &  261.90 & 0.995                   &-262.55 & 0.995 \\
-    \emph{Plantaginaceae}   &-529.93 & 0.940                   &  -53.81 & \textbf{\textless0.001} &  58.36 & \textbf{\textless0.001} \\
-    \emph{Oleaceae}         & -11.01 & 0.367                   &  -14.95 & \textbf{\textless0.001} &  14.90 & \textbf{\textless0.001} \\
-    \emph{Solanaceae}       &  -     & -                       &   12.33 & 0.743                   & -25.57 & 0.484 \\
-    \emph{Ericaceae}        &  -5.32 & \textbf{\textless0.001} &   -4.48 & \textbf{\textless0.001} &   5.02 & \textbf{\textless0.001} \\
-    \emph{Primulaceae}      & -49.15 & \textbf{\textless0.001} &  -21.46 & \textbf{\textless0.001} &  23.22 & \textbf{\textless0.001} \\
-    \emph{Hydrangeaceae}    &  -7.14 & \textbf{0.002}          &   -1.16 & \textbf{0.027}          &   1.47 & \textbf{0.004} \\
-    \emph{Loasaceae}        & 482.42 & 0.998                   &  478.88 & 0.995                   &-485.71 & 0.995 \\
-    \emph{Caryophyllaceae}  &  -3.42 & 0.167                   &   -3.63 & \textbf{\textless0.001} &   4.09 & \textbf{\textless0.001} \\
-    \emph{Montiaceae}       & 346.61 & 0.999                   &  406.10 & 0.998                   &-406.90 & 0.998 \\
-    \emph{Polygonaceae}     &  18.37 & \textbf{\textless0.001} &   14.63 & \textbf{\textless0.001} & -14.99 & \textbf{\textless0.001} \\
-    \emph{Brassicaceae}     &  -6.04 & 0.260                   &   -1.34 & 0.302                   &   1.57 & 0.218 \\
-    \emph{Cistaceae}        & -26.90 & \textbf{\textless0.001} &  -10.81 & \textbf{\textless0.001} &  13.33 & \textbf{\textless0.001} \\
-    \emph{Malvaceae}        &  -1.29 & 0.558                   &   -4.59 & \textbf{\textless0.001} &   5.02 & \textbf{\textless0.001} \\
-    \emph{Geraniaceae}      & -11.17 & \textbf{0.014}          &   -1.25 & 0.730                   &   9.96 & \textbf{0.013} \\
-    \emph{Melastomataceae}* &  47.20 & 0.998                   &   52.97 & 0.993                   & -53.08 & 0.993 \\
-    \emph{Myrtaceae}        & -70.37 & \textbf{\textless0.001} &  -44.38 & \textbf{\textless0.001} &  51.83 & \textbf{\textless0.001} \\
-    \emph{Malpighiaceae}    &  -0.83 & 0.610                   &   -0.26 & 0.850                   &   0.99 & 0.513 \\
-    \emph{Phyllanthaceae}   &-389.36 & 0.995                   &  -24.36 & \textbf{\textless0.001} &  24.88 & \textbf{\textless0.001} \\
-    \emph{Fabaceae}*        &  14.19 & \textbf{0.011}          &    3.18 & 0.091                   &  -4.60 & \textbf{0.012} \\
-    \emph{Rosaceae}         & -21.45 & \textbf{\textless0.001} &  -20.31 & \textbf{\textless0.001} &  21.50 & \textbf{\textless0.001} \\
-    \emph{Saxifragaceae}    &  -4.00 & 0.053                   &    0.40 & 0.722                   &   0.79 & 0.474 \\
-    \emph{Papaveraceae}     & -27.67 & \textbf{0.003}          &  -16.16 & \textbf{\textless0.001} &  16.80 & \textbf{\textless0.001} \\
-    \emph{Ranunculaceae}    &  69.01 & 0.996                   &  -11.70 & \textbf{0.003}          &  10.73 & \textbf{0.006} \\
-    \emph{Amaryllidaceae}   &   0.65 & 0.933                   &   -1.01 & 0.465                   &   0.97 & 0.480 \\
-    \emph{Asparagaceae}     & -73.15 & \textbf{0.003}          &  -33.10 & \textbf{\textless0.001} &  35.56 & \textbf{\textless0.001} \\
-    \emph{Iridaceae}        & 253.09 & 0.998                   &    1.68 & 0.773                   &  -2.30 & 0.691 \\
-    \emph{Poaceae}*         & 343.63 & 0.996                   &  343.55 & 0.990                   &-344.97 & 0.990 \\
+    \emph{Adoxaceae} &  -65.8 & 0.163 \\
+    \emph{Amaryllidaceae} &  -17.9 & \textbf{0.015} \\
+    \emph{Apiaceae} &  10.9  & \textbf{0.006} \\
+    \emph{Apocynaceae} &  -6.96  & \textbf{0.037} \\
+    \emph{Asparagaceae} &  -6.23  & 0.189 \\
+    \emph{Asteraceae}* &  -1.47  & \textbf{\textless0.001} \\
+    \emph{Berberidaceae} &  -1.48$\times10^3$ & \textgreater0.999 \\
+    \emph{Boraginaceae} &  -5.15  & \textbf{\textless0.001} \\
+    \emph{Brassicaceae} &  -11.2 & 0.072 \\
+    \emph{Calceolariaceae} &  156 & 0.998 \\
+    \emph{Campanulaceae} &  334 & 0.999 \\
+    \emph{Caprifoliaceae} &  0.310 & 0.959 \\
+    \emph{Caryophyllaceae} &  2.09 & 0.644 \\
+    \emph{Cistaceae} &  -11.4 & \textbf{\textless0.001} \\
+    \emph{Convolvulaceae} &  -1.84  & 0.837 \\
+    \emph{Ericaceae} &  4.61 & 0.116 \\
+    \emph{Fabaceae}* &  -12.9 & \textbf{\textless0.001} \\
+    \emph{Geraniaceae} &  -3.31  & 0.624 \\
+    \emph{Hydrangeaceae} &  0.057 & 0.982 \\
+    \emph{Iridaceae} &  -27.9 & 0.078 \\
+    \emph{Lamiaceae} &  -5.01  & \textbf{\textless0.001} \\
+    \emph{Loasaceae} &  -865  & \textgreater0.999 \\
+    \emph{Malpighiaceae} &  2.80 & 0.168 \\
+    \emph{Malvaceae} &  -5.56  & 0.363 \\
+    \emph{Melastomataceae}* &  5.19 & 0.577 \\
+    \emph{Montiaceae} &  -1.12  & 0.870 \\
+    \emph{Myrtaceae} &  8.55 & 0.071 \\
+    \emph{Oleaceae} &  0.995 & 0.855 \\
+    \emph{Onagraceae} &  -556  & \textgreater0.999 \\
+    \emph{Orchidaceae} &  -14.5 & 0.145 \\
+    \emph{Orobanchaceae} &  24.2  & 0.326 \\
+    \emph{Papaveraceae} &  -11.2 & 0.511 \\
+    \emph{Phyllanthaceae} &  9.99 & 0.433 \\
+    \emph{Plantaginaceae} &  -8.48  & \textbf{0.001} \\
+    \emph{Poaceae}* &  69.2  & \textbf{0.003} \\
+    \emph{Polygonaceae} &  -14.8 & \textbf{\textless0.001} \\
+    \emph{Primulaceae} &  14.9  & 0.343 \\
+    \emph{Ranunculaceae} &  -38.0 & \textbf{\textless0.001} \\
+    \emph{Rosaceae} &  0.759 & 0.735 \\
+    \emph{Rubiaceae}* &  -13.0 & \textbf{0.026} \\
+    \emph{Salicaceae} &  -1.90  & 0.545 \\
+    \emph{Sapindaceae} &  821 & 0.999 \\
+    \emph{Saxifragaceae} &  -0.092  & 0.992 \\
+    \emph{Solanaceae} &  -21.9 & 0.189 \\
+    \emph{Tropaeolaceae} &  192 & 0.997 \\
+    \emph{Verbenaceae} &  -9.03  & 0.627 \\
+    \emph{Violaceae} &  -0.487  & 0.974 \\
   \hline
@@
 
-    We were able to fit these models to 35 plant families (see \emph{Materials and Methods} for     details). 
-    Families \\ marked with an asterisk were also highly diverse in herbivory networks. 
-    Statistically significant values \\ are indicated in bold. Dashes indicate 
-    plant families where the corresponding overlap 
-    pattern was\\either extremely rare or omnipresent and the relevant model was uninformative.
+    We were able to fit these models to 47 plant families (see \emph{Materials and Methods} for     details). 
+    Families \\ marked with an asterisk were also sufficiently diverse in herbivory networks. 
+    Statistically significant values \\ are indicated in bold.
 
@@
 
-  \begin{figure}[!h]
-    \begin{center}
+  % \begin{figure}[!h]
+  %   \begin{center}
   %     \centerline{\includegraphics*[width=.75\textwidth]{Figures/Sketches/methods_breakdown.eps}}
-    \end{center}
-     \caption{Visual depiction of our decomposition of pairwise niche overlap of plants' interaction
-     partners. \textbf{(a)} First, consider the representation of any pollination or herbivory network
-     as an adjacency matrix. Here, filled cells indicate an interaction between a particular plant 
-     (letters on rows) and an animal (numbers on columns). \textbf{(b)} For a given pair of plants (e.g., plants 
-     A and B), we then considered the set of animals that interact with at least one of the focal
-     plants. Taking each pair of animals in this set in turn, we assigned the resulting quartet (the
-     two focal plants plus two animals) to one of three patterns of overlap.
-     In the \textbf{total overlap} pattern, both plants interact with both animals. 
-     In the \textbf{partial overlap} pattern, one plant interacts with both animals and the other plant
-     interacts with only one.
-     Finally, in the \textbf{no overlap} pattern each animal interacts with only one plant; note that 
-     this includes cases where both animals interact with the same plant (e.g., animals 1 and 5 and plant A)
-     as well as cases where each animal interacts with a different plant (e.g., animals 1 with plant A and animal
-     4 with plant B). \textbf{(c-e)} The number of times each pattern occurred was used to summarise the pairwise niche 
-     overlap between the two plants and then related to their phylogenetic distance.}
-    \label{overlap_patterns}
-  \end{figure}
+  %   \end{center}
+  %    \caption{Visual depiction of our decomposition of pairwise niche overlap of plants' interaction
+  %    partners. \textbf{(a)} First, consider the representation of any pollination or herbivory network
+  %    as an adjacency matrix. Here, filled cells indicate an interaction between a particular plant 
+  %    (letters on rows) and an animal (numbers on columns). \textbf{(b)} For a given pair of plants (e.g., plants 
+  %    A and B), we then considered the set of animals that interact with at least one of the focal
+  %    plants. Taking each pair of animals in this set in turn, we assigned the resulting quartet (the
+  %    two focal plants plus two animals) to one of three patterns of overlap.
+  %    In the \textbf{total overlap} pattern, both plants interact with both animals. 
+  %    In the \textbf{partial overlap} pattern, one plant interacts with both animals and the other plant
+  %    interacts with only one.
+  %    Finally, in the \textbf{no overlap} pattern each animal interacts with only one plant; note that 
+  %    this includes cases where both animals interact with the same plant (e.g., animals 1 and 5 and plant A)
+  %    as well as cases where each animal interacts with a different plant (e.g., animals 1 with plant A and animal
+  %    4 with plant B). \textbf{(c-e)} The number of times each pattern occurred was used to summarise the pairwise niche 
+  %    overlap between the two plants and then related to their phylogenetic distance.}
+  %   \label{overlap_patterns}
+  % \end{figure}
 
@@
     \begin{center}
-      % \centerline{\includegraphics*[width=.75\textwidth]{Figures/dataplots/scaled_regression_lines_full_color.eps}}
+      \centerline{\includegraphics*[width=.75\textwidth]{Figures/dataplots/scaled_regression_lines_full_color.eps}}
     \end{center}
@@
      against phylogenetic distance for plants in 11
-     herbivory networks (left; green) and 59 pollination
-     networks (right; purple). In both network types, the probability of
-     observing the total and partial overlap patterns tended to
-     decrease as phylogenetic distance increased while the 
-     probability of the no-overlap pattern tended to increase
-     (thick, dark lines). There was also substantial variation
-     between individual networks (thin, pale lines) of both types.
-     The model is described in Eq. 1.}
+     herbivory networks (top; green) and 59 pollination
+     networks (bottom; purple). In both network types, the probability of a pair of plants
+     sharing an interaction partner increased with increasing phylogenetic distance (thick,
+     dark lines). There was substantial variation among networks (thin, pale lines) of both types.}
     \label{within_network_regression} 
@@
     \begin{center}
-      % \centerline{\includegraphics*[height=.62\textheight]{Figures/dataplots/Family/allfams_full.eps}}
+      \centerline{\includegraphics*[height=.62\textheight]{Figures/dataplots/Family/allfams_full.eps}}
     \end{center}
-     \caption{Change in log odds of observing different 
-     patterns of pairwise niche overlap per million
+     \caption{Change in log odds of observing pairwise niche overlap per million
      years of divergence time between a pair of plants
-     in 38 separate plant families.
+     in the 14 plant families where there was a significant
+     relationship between log odds of sharing interaction
+     partners and phylogenetic distance.
      Families in pollination networks are indicated
@@
      in logit-transformed space and represent
-     the change in the probability of observing a pattern
-     of overlap per million years of divergence time. We also
+     the change in the probability of observing shared 
+     interaction partners per million years of divergence time. We also
      show the slope of the relationship between the
@@
      pollination (dark, purple horizontal line) networks.
-     Arrows indicate significant values for~\emph{Melastomataceae} in
-     herbivory networks which fell outside the plot margins.
-     See~\emph{Figure S1; Supporting Information} for more details.
+     % See~\emph{Figure S1; Supporting Information} for more details.
      The phylogenetic tree below the plots indicates the

### 2018-12-13 code/Jaccard_overlap_vs_distance.R

@@ -1,0 +1,142 @@
+library(ape)
+library(geiger)
+library(nlme)
+library(phytools)
+
+source('helper_functions.R') 
+# Contains functions for turning networks into binary matrices,
+###########################################################################################################
+
+# Read in the file that has the correct families
+taxinfo=read.table('../data/plant_phylogeny/inputs_to_outputs.tsv',header=TRUE,sep='\t')
+taxinfo=as.data.frame(taxinfo)
+taxonomy=taxinfo
+taxonomy$Input<-NULL
+taxonomy$family=1
+taxonomy$genus=1
+taxonomy$tipname=1
+famjunk=strsplit(as.character(taxonomy$Output),split='/')
+for(i in 1:nrow(taxonomy)){
+  taxonomy$family[i]=famjunk[[i]][1]
+  taxonomy$genus[i]=famjunk[[i]][2]
+  taxonomy$tipname[i]=paste0(famjunk[[i]][2],'_',famjunk[[i]][3])
+}
+taxonomy<-taxonomy[which(duplicated(taxonomy)==FALSE),]
+row.names(taxonomy)=taxonomy$tipname
+# Can't have the rownames since c. 50 species are in more than one web.
+
+###########################################################################################################
+phfiles<-as.character(list.files(path="../data/Corrected_Matrices/Plant_herbivore_matrices", full.names=TRUE, pattern="*.csv"))
+ppfiles<-as.character(list.files(path="../data/Corrected_Matrices/Stouffer_Ecology_Matrices", full.names=TRUE, pattern="*.csv"))
+
+# Here I'll count up how many species we're getting in each family.
+families=levels(as.factor(taxonomy$family))
+families_by_network=matrix(nrow=length(c(phfiles,ppfiles)),ncol=length(families))
+colnames(families_by_network)=families
+rownames(families_by_network)=c(phfiles,ppfiles)
+
+for(n in 1:length(c(phfiles,ppfiles))){
+  file=c(phfiles,ppfiles)[n]
+  net=gsub("../data/Corrected_Matrices/","",file) # Type of network, network name
+  netname=gsub("_corrected.csv","",net)                     # same without .csv
+  if(file %in% phfiles){
+    planttree=read.newick(paste0('../data/plant_phylogeny/trees/',gsub('Plant_herbivore_matrices/','',netname),'.new'))
+  } else {
[…]

### 2018-12-13 code/Jaccard_random_regressions.R

@@ -1,0 +1,91 @@
+library(car)
+require(lme4)
+
+
+networks<-as.character(list.files(path="../data/Jaccard/Random_Matrices/test", full.names=TRUE, pattern="*"))
+# Distance from the observed, overlaps from the randoms
+for(network in networks){
+# out_table_single_J<-matrix(nrow=length(networks),ncol=999)
+# out_table_single_S<-matrix(nrow=length(networks),ncol=999)
+# n=1
+  netname=gsub('../data/Jaccard/Random_Matrices/test',"",network)
+  if(network %in% networks[1:59]){
+    obsfile=paste0('../data/Jaccard/Overlap_dist/Stouffer_Ecology_Matrices/',netname,'_dist.csv',sep='')
+  } else {
+    obsfile=paste0('../data/Jaccard/Overlap_dist/Plant_herbivore_matrices/',netname,'_dist.csv',sep='')    
+  }
+  obsdata=read.csv(obsfile,header=TRUE,row.names=1,check.names=FALSE,sep=',')
+  out_table_J<-matrix(nrow=99,ncol=1)
+  out_table_S<-matrix(nrow=99,ncol=1)
+  print(network)
+  for(i in 1:99){
+#      tryCatch({
+#       unshared=read.csv(paste0(network,'/',netname,'_',i,'_notshared.csv',sep=''),header=TRUE,row.names=1,sep=',')
+#       animals=read.csv(paste0(network,'/',netname,'_',i,'_animals.csv',sep=''),header=TRUE,row.names=1,sep=',')
+#       interactions=read.csv(paste0(network,'/',netname,'_',i,'_interactions.csv',sep=''),header=TRUE,row.names=1,sep=',')
+#       # print(c(nrows(unshared)==nrows(animals),nrows(unshared)==nrows(interactions),nrows(animals)==nrows(interactions)))
+#       if(!nrow(unshared)==nrow(animals)){
+#         print(i)
+#       }
+#       },
+#               error = function(e) {print(i);NaN})
+# }}
+    print(i)
+    animals=read.csv(paste0(network,'/',netname,'_',i,'_animals.csv',sep=''),header=TRUE,row.names=1,sep=',')
+    interactions=read.csv(paste0(network,'/',netname,'_',i,'_interactions.csv',sep=''),header=TRUE,row.names=1,sep=',')
+    unshared=read.csv(paste0(network,'/',netname,'_',i,'_notshared.csv',sep=''),header=TRUE,row.names=1,sep=',')
+
[…]

### 2018-12-13 code/Jaccard_regressions.R

@@ -1,0 +1,54 @@
+library(car)
+require(lme4)
+
+files1<-as.character(list.files(path="../data/Jaccard/Overlap_dist/Plant_herbivore_matrices", full.names=TRUE, pattern="*.csv"))
+files2<-as.character(list.files(path="../data/Jaccard/Overlap_dist/Stouffer_Ecology_Matrices", full.names=TRUE, pattern="*.csv"))
+
+files=c(files1,files2)
+
+outtab=matrix(nrow=length(files),ncol=5)
+colnames(outtab)=c('network','Jaccard_slope','Jaccard_p','Sorenson_slope','Sorenson_p')
+combi=matrix(nrow=0,ncol=6)
+
+for(n in 1:length(files)){
+  network=files[n]
+  netname=gsub('../data/Jaccard/Overlap_dist/',"",network)
+  net=gsub('_dist.csv',"",netname)
+  netdata=read.csv(network,header=TRUE,row.names=1,check.names=FALSE,sep=',')
+  Jaccard=glm(cbind(n_shared_animals,n_notshared)~scale(distance),data=netdata,family="binomial")
+  Sorenson=glm(cbind(n_shared_interactions,n_notshared)~scale(distance),data=netdata,family="binomial")
+
+  obs_slopes=c(Jaccard$coefficients['scale(distance)'],summary(Jaccard)$coefficients['scale(distance)',4],Sorenson$coefficients['scale(distance)'],summary(Sorenson)$coefficients['scale(distance)',4])
+  outtab[n,]=c(net,obs_slopes)
+
+  if(n<12){
+  	netdata$nettype='ph'
+  } else {
+  	netdata$nettype='pp'
+  }
+  print(n)
+  netdata$network=netname
+  combi=rbind(combi,netdata)
+
+}
+
+combi$nettype=as.factor(combi$nettype)
+fullreg=glm(cbind(n_shared_animals,n_notshared)~scale(distance)*nettype,data=combi,family="binomial")
+
+outfile=paste0('../data/Jaccard/Observed_Regression/observed_coefficients.tsv')
+write.table(outtab,file=outfile,sep='\t')
+message("Done observed")
+
+fullreg_bynetwork=glmer(cbind(n_shared_animals,n_notshared)~scale(distance)*nettype+(1+scale(distance)|network),data=combi,family="binomial")
+fixes=summary(fullreg_bynetwork)$coefficients
+ranes=ranef(fullreg_bynetwork)$network
[…]

### 2018-12-13 code/Mantel_randomiser.R

@@ -1,0 +1,53 @@
+# 1. Observed shared/notshared for each network - Done
+# 2. Generate 999 random shuffles for each network - Done.
+# 3. Calculate shared/notshared for each random network
+# 4. Generate 500 random shuffles for each 999 random shuffle - Done.
+# 5. Calculate shared/notshared for each randomized random network
+# 6. Calculate observed p-value
+# 7. Calculate distribution of random p-values for each matrix
+
+source('helper_functions.R')
+###########################################################################################################
+phfiles<-as.character(list.files(path="../data/Corrected_Matrices/Plant_herbivore_matrices", full.names=TRUE, pattern="*.csv"))
+ppfiles<-as.character(list.files(path="../data/Corrected_Matrices/Stouffer_Ecology_Matrices", full.names=TRUE, pattern="*.csv"))
+
+# for(n in 1:70){
+for(n in 1:2){
+  # file=c(phfiles,ppfiles)[n]
+  file=ppfiles[n]
+  print(file)
+
+  network_matrix=read.csv(file,header=TRUE,sep=',',row.names=1)
+  numeric_matrix=make_numeric_matrix(network_matrix)
+  plantnames=colnames(numeric_matrix)
+
+  net=gsub("../data/Corrected_Matrices/","",file)
+  netname=gsub("_corrected.csv","",net)
+  shortname=strsplit(netname,'/')[[1]][2]
+
+  dir.create(paste0('../data/Random_Matrices/test/',shortname))
+  # dir.create(paste0('../data/Random_Random_Matrices/',shortname))
+  # Shuffle the plant names and write a new matrix
+  for(z in 1:99){
+    print(z)
+    shuffnames=sample(plantnames)
+    modmat=numeric_matrix
+    colnames(modmat)=shuffnames
+
+    outFileName=paste0('../data/Random_Matrices/test/',shortname,'/',shortname,'_',z,'_rand.csv')
+    write.table(modmat,file=outFileName,sep=',',append=FALSE)
+
+    #Make a directory for the 500 sub-randomisations
+    # subdir=gsub('_rand.csv',"",outFileName)
+    # subsubdir=gsub("Random_Matrices","Random_Random_Matrices",subdir)
+    # dir.create(subsubdir)
+    # for(q in 1:500){
+    #     shuffnames=sample(plantnames)
+    #     modmat2=numeric_matrix
+    #     colnames(modmat2)=shuffnames
+
[…]

### 2018-12-13 code/Random_Jaccard_overlap_vs_distance.R

@@ -1,0 +1,99 @@
+library(ape)
+library(geiger)
+library(nlme)
+library(phytools)
+
+source('helper_functions.R') 
+
+# Don't need the trees, just want to corral all the overlaps in the random and random-random matrices.
+
+###########################################################################################################
+
+dirs<-as.character(list.files(path="../data/Random_Matrices/test", full.names=TRUE, pattern="*"))
+# print(dirs)
+
+for(n in 1:length(dirs)){
+  subdir=dirs[n]
+  print(subdir)
+  files <- as.character(list.files(path=subdir,full.names=TRUE,pattern="*.csv"))
+
+  # if(length(files)==999){
+
+  # print(length(files))
+  # Make sure there's a receptacle directory
+  altdir=gsub("../data/Random_Matrices/test/","",subdir) # Type of network, network name
+  dir.create(paste0('../data/Jaccard/Random_Matrices/test/',altdir))
+ 
+  for(z in 1:length(files)){
+    netfile=files[z]
+    # netfile=paste0('../data/Random_Matrices/M_PL_057/M_PL_057_',z,'_rand.csv')
+    print(netfile)   
+    # Read in network matrix, convert it to a numeric one
+    network_matrix=read.csv(netfile,header=TRUE,sep=',',row.names=1)
+    numeric_matrix=make_numeric_matrix(network_matrix)
+
+    # make a list of all plant pairs in the community
+    plantpairs=combn(colnames(numeric_matrix),2)
+    # Fuck it, I'll shrink the pairs to the good list for Peralta and Bodner later.
+
+    #build the results container for the network
+    colls <- c("n_shared_animals","n_shared_interactions","n_notshared")
+    # shared animals/not shared is Jaccard, shared interactions (shared aimals x2)/not shared is Sorenson
+    # Going to want separate files for each of shared_animals, shared_interactions, notshared
+    animals=matrix(data=0,nrow=ncol(plantpairs),ncol=501) # observed plus all randoms
+    rownames(animals)=interaction(plantpairs[1,],plantpairs[2,],sep=':')
+    interactions=matrix(data=0,nrow=ncol(plantpairs),ncol=501)
+    rownames(interactions)=interaction(plantpairs[1,],plantpairs[2,],sep=':')
+    notshared=matrix(data=0,nrow=ncol(plantpairs),ncol=501)
[…]

### 2018-12-13 code/chitest.R

@@ -1,0 +1,116 @@
+library(nlme)
+library(geiger)
+require(phytools)
+
+# Read in the overlap data files (made by overlap_vs_distance.R)
+phfiles<-as.character(list.files(path="../data/Corrected_Matrices/Plant_herbivore_matrices", full.names=TRUE, pattern="*.csv"))
+ppfiles<-as.character(list.files(path="../data/Corrected_Matrices/Stouffer_Ecology_Matrices", full.names=TRUE, pattern="*.csv"))
+
+files=c(phfiles,ppfiles)
+
+files1<-as.character(list.files(path="../data/Overlap_dist/Plant_herbivore_matrices", full.names=TRUE, pattern="*.csv"))
+files2<-as.character(list.files(path="../data/Overlap_dist/Stouffer_Ecology_Matrices", full.names=TRUE, pattern="*.csv"))
+
+altfiles=c(files1,files2)
+overlap_data <- list()
+for(network in altfiles){
+  netname=gsub('../data/Corrected/',"",network)
+  subfolder=strsplit(strsplit(netname,'-')[[1]][1],'/')[[1]][1]
+  if(subfolder=='Stouffer_Ecology_Matrices'){
+    nettype='pp'  } else {
+      nettype='ph'   }
+
+  message(paste0("Processing '",netname,"' "),appendLF=FALSE)
+
+  overlap_data[[netname]]=read.csv(network,header=TRUE,row.names=1,check.names=FALSE,sep=',')
+  overlap_data[[netname]]$network <- netname
+  overlap_data[[netname]]$nettype <- nettype
+
+  message("Done")
+}
+
+all_data <- do.call("rbind", overlap_data)
+
+#### Build the tree
+planttree=read.newick("../data/plant_phylogeny/dated_tree.new")
+collapsed_tree=collapse.singles(planttree)   #Collapses non-branching nodes (i.e., internal nodes on lines leading to only 1 species)
+
+#### Directory of species names and networks
+speciesnames=read.table('../data/plant_phylogeny/corrected_names.tsv',header=TRUE,sep=',')
+speciesnames$new_lower=tolower(speciesnames$new_names)
+speciesnames$original_lower=tolower(speciesnames$original_name)
+# Remove all problematic characters
+speciesnames$original_lower=gsub('  ', ' ', speciesnames$original_lower)
+speciesnames$original_lower=gsub('_', ' ', speciesnames$original_lower)
[…]

### 2018-12-13 code/cladewise_distance_sorter.R

@@ -1,0 +1,114 @@
+library(ape)
+library(geiger)
+library(nlme)
+library(phytools)
+library(lme4)
+
+# This code takes the files describing overlap in interaction partners for each network, 
+# stitches them together, and returns a file with overlap between species in the same clade
+# (taken from the same network) across all networks
+
+###########################################################################################################
+
+# Read in the overlap data files (made by overlap_vs_distance.R)
+files1<-as.character(list.files(path="../data/Jaccard/Overlap_dist/Plant_herbivore_matrices", full.names=TRUE, pattern="*.csv"))
+files2<-as.character(list.files(path="../data/Jaccard/Overlap_dist/Stouffer_Ecology_Matrices", full.names=TRUE, pattern="*.csv"))
+
+files=c(files1,files2)
+
+overlap_data <- list()
+for(network in files){
+  netname=gsub('../data/Jaccard/Overlap_dist/',"",network)
+  subfolder=strsplit(strsplit(netname,'-')[[1]][1],'/')[[1]][1]
+  if(subfolder=='Stouffer_Ecology_Matrices'){
+    nettype='pp'  } else {
+      nettype='ph'   }
+
+  message(paste0("Processing '",netname,"' "),appendLF=FALSE)
+
+  overlap_data[[netname]]=read.csv(network,header=TRUE,row.names=1,check.names=FALSE,sep=',')
+  overlap_data[[netname]]$network <- netname
+  overlap_data[[netname]]$nettype <- nettype
+
+  message("Done")
+}
+
+all_data <- do.call("rbind", overlap_data)
+
+###########################################################################################################
+
+taxinfo=read.table('../data/plant_phylogeny/inputs_to_outputs.tsv',header=TRUE,sep='\t')
+taxinfo=as.data.frame(taxinfo)
+taxonomy=taxinfo
+taxonomy$Input<-NULL
+taxonomy$family=1
+taxonomy$genus=1
+taxonomy$tipname=1
+famjunk=strsplit(as.character(taxonomy$Output),split='/')
+for(i in 1:nrow(taxonomy)){
+  taxonomy$family[i]=famjunk[[i]][1]
+  taxonomy$genus[i]=famjunk[[i]][2]
+  taxonomy$tipname[i]=paste0(famjunk[[i]][2],'_',famjunk[[i]][3])
+}
+taxonomy<-taxonomy[which(duplicated(taxonomy)==FALSE),]
[…]

### 2018-12-13 code/cladewise_regressions.R

@@ -1,0 +1,269 @@
+library(ape)
+library(geiger)
+library(nlme)
+library(phytools)
+library(lme4)
+library(lmerTest)
+library(car)
+
+rm(list=ls(all=TRUE))
+
+options(warn=2)
+
+# From cladewise_distance_sorter.R
+samefam=read.table('../data/cladewise_overlap_dist.csv',sep=',',header=TRUE)
+
+which_test=matrix(nrow=1000,ncol=3)
+what_scale=matrix(nrow=1000,ncol=3)
+
+frankendata=matrix(nrow=0,ncol=ncol(samefam))
+colnames(frankendata)=c("n_shared_animals","n_shared_interactions","n_notshared",
+    "distance","network","nettype","family")
+
+p_test=function(model){
+  p_est=deltaMethod(model,"b1+b3",parameterNames=paste("b",0:3,sep=''))
+  p_z=p_est$Estimate/p_est$SE
+  p_p=2*pnorm(-abs(p_z))
+  result=c(p_est,p_p)
+  return(result)  
+}
+
+check_dataset=function(dataset){
+  if(nrow(dataset)>1){ # Must have multiple rows, checking n per row seperately for multi-network families
+      if(max(dataset$distance)-min(dataset$distance)>0.001){ # If there's range in distance
+        if(max(dataset$n_shared_animals)-min(dataset$n_shared_animals)>=1){        # If there's a range in no-overlap motifs
+          if(max(dataset$n_shared_interactions)-min(dataset$n_shared_interactions)>=1){              # If there's a range in partial-overlap motifs
+            if(max(dataset$n_notshared)-min(dataset$n_notshared)>=1){        # If there's a range in total-overlap motifs
+              return('ok')} else {
+            return('reject') }
+          } else {
+            return('reject') }
+        } else {
+          return('reject') }
+      } else {
+        return('reject') }
+  } else {
+    return('reject')
+  }
+}
+
+# If there's only one network, R refuses to fit NAs for nettype
+print_glm_outputs=function(dataset,family,nettype){
+  # print(c(family,'glm'))
+  reg=glm(cbind(n_shared_animals,n_notshared)~scale(distance),data=dataset,family="binomial",maxit=1000)
+  write.table(summary(reg)$coef,
+    file=paste0('../data/Jaccard/families_to_networks/Regressions/',family,'_',nettype,'_reg_fixef.tsv'),sep='\t')
+}
+
[…]

### 2018-12-13 code/collate_randoms.R

@@ -1,0 +1,55 @@
+
+files1<-as.character(list.files(path="../data/Jaccard/Overlap_dist/Plant_herbivore_matrices", full.names=TRUE, pattern="*.csv"))
+files2<-as.character(list.files(path="../data/Jaccard/Overlap_dist/Stouffer_Ecology_Matrices", full.names=TRUE, pattern="*.csv"))
+
+files=c(files1,files2)
+
+
+obs_vs_random=matrix(nrow=length(files),ncol=1000)
+obsdata=read.table('../data/Jaccard/Observed_Regression/observed_coefficients.tsv')
+# I think I will just do Jaccards for now - not 100% sure why I cared about Sorenson
+obs_vs_random[,1]=obsdata$Jaccard_slope
+
+# And let's collect the p-values for ran vs ran-ran here
+ran_vs_ranran=matrix(nrow=length(files),ncol=999)
+
+netnames=c()
+for(n in 1:length(files)){
+	print obsdata
+  network=files[n]
+  netname=strsplit(network,'/')[[1]][6]
+  net=gsub('_dist.csv',"",netname)
+  print(net)
+  netnames=cbind(netnames,net)
+	randdata=read.table(paste0('../data/Jaccard/Random_Regressions/',net,'_randomCoeffs_Jaccard.tsv'))
+	obs_vs_random[n,2:1000]=t(randdata[,1])
+
+	for(j in 1:999){
+		ranrans=randdata[j,2:500]
+		ran=randdata[j,1]
+		p=length(ranrans[which(ranrans>ran)])/500
+		ran_vs_ranran[n,j]=p
+	}
+
+}
+obs_vs_random=as.data.frame(obs_vs_random)
+colnames(obs_vs_random)[1]=c("Observed")
+rownames(obs_vs_random)=netnames
+write.table(obs_vs_random,file='../data/Jaccard/Observed_Regression/observed_vs_random.tsv')
+
+ran_vs_ranran=as.data.frame(ran_vs_ranran)
+rownames(ran_vs_ranran)=netnames
+write.table(ran_vs_ranran,file='../data/Jaccard/Observed_Regression/random_vs_randomrandom.tsv')
+
+obs_ps=matrix(nrow=length(files),ncol=2)
+for(n in 1:length(files)){
+	obs=obs_vs_random[n,1]
+	rans=obs_vs_random[n,2:1000]
[…]

### 2018-12-13 code/comparing_observed_random_matrices.R

@@ -1,0 +1,15 @@
+# Comparing with random matrices
+
+# Slopes in observed, random networks
+obsran=read.table('../data/Jaccard/Observed_Regression/observed_vs_random.tsv')
+# P-values in random vs. ranran
+ranran=read.table('../data/Jaccard/Observed_Regression/random_vs_randomrandom.tsv')
+
+obs_p=matrix(nrow=70,ncol=2)
+for(i in 1:70){
+	obs_p[i,1]=obsran[i,1]
+	obs_p[i,2]=length(which(obsran[i,2:1000]<obsran[i,1]))
+}
+
+ranran$summary=rowMeans(ranran)
+

### 2018-12-13 code/create_figures/cladewise_barplot.py

@@ -1,0 +1,356 @@
+import sys 
+import os 
+import re 
+import random 
+from decimal import *
+import math
+
+from PyGrace.grace import Grace
+from PyGrace.colors import RandomColorScheme, MarkovChainColorScheme, ColorBrewerScheme
+from PyGrace.dataset import SYMBOLS
+from PyGrace.Extensions.panel import Panel,MultiPanelGrace, TreePanel
+from PyGrace.drawing_objects import DrawText, DrawLine
+
+from PyGrace.Extensions.distribution import CDFGraph, PDFGraph
+from PyGrace.Extensions.latex_string import LatexString, CONVERT
+
+# Update the scale dict, update the scales for each plot.
+scaledict={
+  "adoxaceae":(109.005904,72.33798048),
+  "amaranthaceae_ph":(63.31440233,25.6747469),
+  "amaryllidaceae":(124.3113023,23.22845123),
+  "apiaceae":(97.08918062,49.51149577),
+  "apocynaceae":(67.32058251,19.57696024),
+  "araliaceae_ph":(99.42261375,29.52333939),
+  "asparagaceae":(126.7490068,34.97861194),
+  "asteraceae_pp":(80.27592,20.89695),
+  "asteraceae_ph":(81.03086142,22.84774091),
+  "berberidaceae":(170.1549313,111.5126936),
+  "boraginaceae":(104.3294132,19.93357802),
+  "brassicaceae":(86.85651906,50.0135176),
+  "cactaceae_ph":(29.48932,11.53711841),
+  "calceolariaceae":(39.951931,14.58840519),
+  "campanulaceae":(88.27866667,30.58062718),
+  "caprifoliaceae":(123.2603062,25.03345494),
+  "caryophyllaceae":(81.10386123,32.17269234),
+  "cistaceae":(54.06062086,25.37135909),
+  "convolvulaceae":(74.26640822,42.3053962),
+  "cornaceae_ph":(113.032486,39.81259219),
+  "ericaceae":(90.05900849,36.05961842),
+  "euphorbiaceae":(172.4392253,43.00556316),
+  "fabaceae_pp":(101.9271,43.96578),
+  "fabaceae_ph":(85.61470337,40.71417068),
+  "gentianaceae_ph":(37.2132315,31.22748797),
+  "geraniaceae":(61.21654733,29.18579945),
+  "hydrangeaceae":(101.5381486,26.70867942),
+  "iridaceae":(126.447704,42.84244667),
[…]

### 2018-12-13 code/create_figures/explain_methods.py

@@ -1,0 +1,371 @@
+import sys
+import os
+import re
+import random
+from decimal import *
+import math
+
+from PyGrace.grace import Grace
+from PyGrace.colors import RandomColorScheme, MarkovChainColorScheme, ColorBrewerScheme
+from PyGrace.dataset import SYMBOLS
+from PyGrace.Extensions.panel import Panel,MultiPanelGrace
+from PyGrace.drawing_objects import DrawText, DrawLine, DrawBox
+from PyGrace.axis import LINEAR_SCALE, LOGARITHMIC_SCALE
+
+from PyGrace.Extensions.distribution import CDFGraph, PDFGraph
+from PyGrace.Extensions.latex_string import LatexString, CONVERT
+from PyGrace.Extensions.colorbar import SolidRectangle, ColorBar
+from PyGrace.Styles.el import ElGraph, ElLinColorBar, ElLogColorBar
+
+def grapher(grace,graph):
+  names=["A","B","C","D","E","F"]
+  polnames=[1,2,3,4,5]
+
+  specials=graph.yaxis.tick.set_spec_ticks([6,5,4,3,2,1],[],tick_labels=names)
+  specials2=graph.xaxis.tick.set_spec_ticks([1,2,3,4,5],[],tick_labels=polnames)
+
+  graph.world.xmax=5.5
+  graph.world.ymax=6.5
+
+  graph.world.xmin=0.5
+  graph.world.ymin=0.5
+
+  boxes=[(1,1),(1,2),(1,3),(1,4),(1,6),(2,3),(2,4),(2,5),(2,6),(3,5),(3,6),(4,3),(4,4),(4,5),(5,6)]
+
+  boxed=graph.add_dataset(boxes)
+  boxed.line.linestyle=0
+  boxed.symbol.configure(shape=2,size=4,fill_color=8)
+
+  graph.xaxis.tick.configure(major=1,minor_size=0,major_size=0)
+  graph.yaxis.tick.configure(major=1,minor_size=0,major_size=0)
+
+  graph.yaxis.ticklabel.configure(char_size=1)
+  graph.xaxis.ticklabel.configure(char_size=1,place='opposite')
+
+  graph.yaxis.tick.configure(major=1,minor_ticks=1,minor_grid='off')
+  graph.xaxis.tick.configure(major=1,minor_ticks=1,minor_grid='off')
+
+  graph.frame.color=1
+  graph.xaxis.bar.linewidth=0
+  graph.yaxis.bar.linewidth=0
[…]

### 2018-12-13 code/create_figures/explain_methods_breakdown.py

@@ -1,0 +1,656 @@
+import sys
+import os
+import re
+import random
+from decimal import *
+import math
+
+from PyGrace.grace import Grace
+from PyGrace.colors import RandomColorScheme, MarkovChainColorScheme, ColorBrewerScheme
+from PyGrace.dataset import SYMBOLS
+from PyGrace.Extensions.panel import Panel,MultiPanelGrace
+from PyGrace.drawing_objects import DrawText, DrawLine, DrawBox
+from PyGrace.axis import LINEAR_SCALE, LOGARITHMIC_SCALE
+
+from PyGrace.Extensions.distribution import CDFGraph, PDFGraph
+from PyGrace.Extensions.latex_string import LatexString, CONVERT
+from PyGrace.Extensions.colorbar import SolidRectangle, ColorBar
+from PyGrace.Styles.el import ElGraph, ElLinColorBar, ElLogColorBar
+
+# The idea here is to use the interaction matrix for MPL033 to make a heat map like in the island project
+# Just be aware that apparently the row names don't match the tip names?
+
+def panel_a(graph): 
+
+  intmatrix={
+    "A":[1,1,1,0,1],
+    "B":[0,1,1,1,0],
+    "C":[1,1,0,1,0],
+    "D":[1,1,0,1,0],
+    "E":[1,0,0,0,0],
+    "F":[1,0,0,0,0]
+    }
+
+  specieslist=["A","B","C","D","E","F"]
+
+  datadict={}
+
+  i=1
+  j=6
+  for species in specieslist:
+    datadict[species]={}
+    for value in intmatrix[species]:
+      datadict[species][(i,j)]=value
+      i=i+1
+    j=j-1
+    i=1
+
+  return datadict
+
+def quaddict_maker(quad):
+  specieslist=["A","B"]
+
+  datadict={}
+
+  i=1
+  j=7
+  for species in specieslist:
+    datadict[species]={}
+    for value in quad[species]:
+      datadict[species][(i,j)]=value
+      i=i+1
+    j=j-1
+    i=1
+
+  return datadict
+
+def grapher(grace,graph):
+  xwidth=1
+  ywidth=1
+
+  names=["A","B","C","D","E","F"]
[…]

### 2018-12-13 code/create_figures/explain_methods_vectorseries.py

@@ -1,0 +1,347 @@
+import sys
+import os
+import re
+import random
+from decimal import *
+import math
+
+from PyGrace.grace import Grace
+from PyGrace.colors import RandomColorScheme, MarkovChainColorScheme, ColorBrewerScheme
+from PyGrace.dataset import SYMBOLS
+from PyGrace.Extensions.panel import Panel,MultiPanelGrace
+from PyGrace.drawing_objects import DrawText, DrawLine, DrawBox
+from PyGrace.axis import LINEAR_SCALE, LOGARITHMIC_SCALE
+
+from PyGrace.Extensions.distribution import CDFGraph, PDFGraph
+from PyGrace.Extensions.latex_string import LatexString, CONVERT
+from PyGrace.Extensions.colorbar import SolidRectangle, ColorBar
+from PyGrace.Styles.el import ElGraph, ElLinColorBar, ElLogColorBar
+
+# The idea here is to use the interaction matrix for MPL033 to make a heat map like in the island project
+# Just be aware that apparently the row names don't match the tip names?
+
+def panel_a(graph): 
+
+  intmatrix={
+    "A":[1,1,1,0,1],
+    "B":[0,1,1,1,0],
+    "C":[1,1,0,1,0],
+    "D":[1,1,0,1,0],
+    "E":[1,0,0,0,0],
+    "F":[1,0,0,0,0]
+    }
+
+  specieslist=["A","B","C","D","E","F"]
+
+  datadict={}
+
+  i=1
+  j=6
+  for species in specieslist:
+    datadict[species]={}
+    for value in intmatrix[species]:
+      datadict[species][(i,j)]=value
+      i=i+1
+    j=j-1
+    i=1
+
+  return datadict
+
+
+def vectorgrapher(grace,graph):
+  xwidth=1
+  ywidth=1
+
+  names=["A","B","A","E","C","D","E","F"]
+  polnames=[1,2,3,4,5]
+
+  specials=graph.yaxis.tick.set_spec_ticks([12,11,9,8,6,5,3,2],[],tick_labels=names)
+  # specials2=graph.xaxis.tick.set_spec_ticks([1,2,3,4,5],[],tick_labels=polnames)
+
+  graph.world.xmax=9.5
+  graph.world.ymax=12.5
+
[…]

### 2018-12-13 code/create_figures/family_network_CCA.py

@@ -1,0 +1,130 @@
+import sys
+import math
+import random
+from decimal import *
+
+
+#Giulio says there's something wrong with the cca that explains the wierd shape?
+# I think I would like two panels, for early and late, please.
+
+#Pygrace libraries
+from PyGrace.grace import Grace
+from PyGrace.colors import RandomColorScheme, MarkovChainColorScheme, ColorBrewerScheme
+from PyGrace.dataset import SYMBOLS
+from PyGrace.Extensions.panel import Panel,MultiPanelGrace
+from PyGrace.drawing_objects import DrawText, DrawLine
+
+from PyGrace.Extensions.distribution import CDFGraph, PDFGraph
+from PyGrace.Extensions.latex_string import LatexString, CONVERT
+
+colors=ColorBrewerScheme('Spectral')#,reverse=True)  # The blue is very beautiful but maybe harder to see.
+
+pointsize=1
+
+def pointreader(netfile):
+
+  pointdict={'ph':[],'pp':[]}
+
+  f=open(netfile,'r')
+  for line in f:
+    if line.split()[0] not in ['"V1"','""','"MDS1"','"CCA1"','"CA1"']:
+      rownum=line.split()[0][1:-1]
+      if rownum < 9: 
+        nettype='ph'
+      else:
+        nettype='pp'
+      x=float(line.split()[1])#[1:-1])
+      y=float(line.split()[2])#[1:-1])
+
+      pointdict[nettype].append((x,y))
+
+  f.close()
+  return pointdict
+
+def famreader(famfile):
+  points={}
+  f=open(famfile,'r')
+  i=1
+  for line in f:
+    if line.split()[0] not in ['"CCA1"','"CA1"','"MDS1"']:
+      family=line.split()[0][1:-1]
+      print family
+      x=float(line.split()[1])
+      y=float(line.split()[2])
+      points[family]=[(x,y)]
+      i=i+1
+  f.close()
+
+  return points
+
+def points(graph,pointdict):
+  for group in pointdict:
+    points=pointdict[group]
+    pointy=graph.add_dataset(points)
+    pointy.line.linestyle=0
+    if group=='ph':
+      col=12
+    else:
+      col=2
+    pointy.symbol.configure(shape=1,fill_color=col,linewidth=1,size=pointsize*.5)
+  return graph
+
+
+def legendary(graph,group):
+  if group=='early':
[…]

### 2018-12-13 code/create_figures/logodds_tree.py

@@ -1,0 +1,207 @@
+import os
+import sys
+from user import pygracePackagePath
+sys.path.append(pygracePackagePath)
+
+from math import log, fabs
+
+from PyGrace.grace import Grace
+from PyGrace.colors import ColorBrewerScheme
+from PyGrace.drawing_objects import DrawText
+from PyGrace.Extensions.panel import MultiPanelGrace,Panel,TreePanel
+from PyGrace.Extensions.colorbar import ColorBar
+from PyGrace.axis import LINEAR_SCALE, LOGARITHMIC_SCALE
+
+# ---------------------------------- functions to read the data
+
+def read_species_data(filename,web):
+    inFile = open(filename,'r')
+    inFile.readline()
+    data = inFile.readlines()
+    inFile.close()
+
+    species_data = {}
+    for line in data:
+        sline = line.strip().split(',')
+        if sline[0] == web:
+            n_prey = int(sline[11])
+            g_predator = float(sline[13])
+            z_predator = float(sline[15])
+            species_data[sline[-1]] = [n_prey, g_predator, z_predator]
+
+    return species_data
+
+def read_tree(filename):
+    inFile = open(filename,'r')
+    data = inFile.readline()
+    inFile.close()
+    return data
+
+# ---------------------------------- this is the part where YOU do the analysis
+
+# make a Grace instance with the "Set1" color scheme
+colors = ColorBrewerScheme("Greys",n=253) # this is the maximum number of colors
+colors = ColorBrewerScheme("Greens",n=253) # this is the maximum number of colors
+grace = MultiPanelGrace(colors=colors)#ColorBrewerScheme('Paired'))
+grace.set_label_scheme("latin",)
+
+# create graphs and set locations on page
+graph1 = grace.add_graph(TreePanel,orientation='down')
+graph2 = grace.add_graph(Panel,)#type="chart",)
+#graph3 = grace.add_graph(Panel,)#type="chart",)
+graph4 = grace.add_graph(Panel,)#type="chart",)
+
+web = 'Caricaie_Lakes'
+
+tree = graph1.add_tree(read_tree('../../../data/'+web+'/Calculations/tree.newick'))
+tip_labels = dict(zip([i.replace(" ","_") for i in graph1.xaxis.tick.spec_ticklabels],
+                      graph1.xaxis.tick.spec_ticks))
+
[…]

### 2018-12-13 code/create_figures/pval_test_observed.py

@@ -1,0 +1,27 @@
+def pval_getter(netdir):
+  Jaccard_pvals=[]
+  Sorenson_pvals=[]
+  for file in netdir:
+    f=open(file,'r')
+    for line in f: 
+
+
+
+def main():
+
+  bigdir='../../data/Jaccard/Observed_Regression/'
+  grace=MultiPanelGrace(colors='RdBu')
+
+  for nettype in os.listdir(bigdir):
+    for network in os.listdir(bigdir+nettype+'/'):
+      graph=grace.add_graph(Panel)    
+
+      pvals=pval_getter(bigdir+nettype+'/'+network)
+
+
+  grace.multi(rows=10,cols=7,vgap=.03,hgap=.03)
+
+
+
+if __name__ == '__main__':
+  main()

### 2018-12-13 code/create_figures/regression_line_plot.py

@@ -1,0 +1,210 @@
+import sys
+import os
+import re
+import random
+from decimal import *
+import math
+
+from PyGrace.grace import Grace
+from PyGrace.colors import RandomColorScheme, MarkovChainColorScheme, ColorBrewerScheme
+from PyGrace.dataset import SYMBOLS
+from PyGrace.Extensions.panel import Panel,MultiPanelGrace
+from PyGrace.drawing_objects import DrawText, DrawLine
+
+from PyGrace.Extensions.distribution import CDFGraph, PDFGraph
+from PyGrace.Extensions.latex_string import LatexString, CONVERT
+
+scaledict={'centre':251.7093,'scale':91.05211}
+
+def signalreader(datapath,suffix):
+  databank={'fixef':{},'ranef':{}}
+  f=open(datapath+suffix+'_fixef.tsv','r')
+  for line in f:
+    if line.split()[0]!='"Estimate"':
+      name=line.split()[0][1:-1]
+      effect=float(line.split()[1][1:-1])
+      databank['fixef'][name]=effect
+  f.close()
+
+  ran=open(datapath+suffix+'_ranef.tsv','r')
+  for line in ran:
+    if len(line.split())==3:
+      network=line.split()[0][1:-1]
+      intercept=float(line.split()[1])
+      slope=float(line.split()[2])
+      databank['ranef'][network]=(intercept,slope)
+  ran.close()
+
+  print databank['fixef'].keys()
+  return databank
+
+def simlines(inter,beta):
+  simdata=[]
+  for i in range(0,101):
+    x=float(i)/100
+    y=inter+x*beta
+    logity=1/(1+math.exp(0-y))
+    simdata.append((x,logity))
+  return simdata
+
+def simlines_scaled(inter,beta):
+  simdata=[]
+  for i in range(0,80):
+    dist=10*i
+    scaledist=(dist-scaledict['centre'])/scaledict['scale']
+    y=inter+scaledist*beta
+    logity=1/(1+math.exp(0-y))
+    simdata.append((dist,logity))
+  return simdata
+
+def lineplotter(datapath,modeltype,colormode):
+  # dummy=[r"\| \|",r"\|\\\|",r"\|,X\|"]
+  dummy=['Plant-herbivore networks','Plant-pollinator networks','','','','']
+  # dummy=['Total overlap','Partial overlap','No overlap','','','']
+  if modeltype=='scaled':
+    suffix='_reg_unranked_scaled'
+  else:
+    suffix='_reg'
+
+  graphtype='full'
[…]

### 2018-12-13 code/create_figures/talk_interaction_matrix.py

@@ -1,0 +1,115 @@
+import sys
+import os
+import re
+import random
+from decimal import *
+import math
+
+from PyGrace.grace import Grace
+from PyGrace.colors import RandomColorScheme, MarkovChainColorScheme, ColorBrewerScheme
+from PyGrace.dataset import SYMBOLS
+from PyGrace.Extensions.panel import Panel,MultiPanelGrace
+from PyGrace.drawing_objects import DrawText, DrawLine
+from PyGrace.axis import LINEAR_SCALE, LOGARITHMIC_SCALE
+
+from PyGrace.Extensions.distribution import CDFGraph, PDFGraph
+from PyGrace.Extensions.latex_string import LatexString, CONVERT
+from PyGrace.Extensions.colorbar import SolidRectangle, ColorBar
+from PyGrace.Styles.el import ElGraph, ElLinColorBar, ElLogColorBar
+
+# The idea here is to use the interaction matrix for MPL033 to make a heat map like in the island project
+# Just be aware that apparently the row names don't match the tip names?
+
+def panel_a(graph): 
+
+  intmatrix={
+    "smilacina_trifolia_m_pl_033.csv":[0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,1,0,0,0,1,0,0,1,0,0,0,0,0,1,0,0],
+    "aronia_melanocarpa_m_pl_033.csv":[0,1,0,1,1,1,0,0,1,0,0,1,0,1,1,1,1,0,0,1,0,1,0,1,0,1,0,1,0,1,0],
+    "spiraea_alba_m_pl_033.csv":[0,0,1,0,0,1,0,0,1,0,1,0,0,1,0,1,1,0,1,0,0,0,0,0,1,0,0,0,1,1,1],
+    "kalmia_polifolia_m_pl_033.csv":[0,1,0,0,1,1,1,1,1,1,1,0,1,1,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0],
+    "andromeda_glaucophylla_m_pl_033.csv":[0,0,0,0,0,1,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0],
+    "gaylussacia_baccata_m_pl_033.csv":[0,1,1,0,1,1,1,0,1,1,1,0,1,0,1,0,1,1,0,0,1,0,0,0,0,0,0,1,0,0,0],
[…]

### 2018-12-13 code/create_figures/talk_regression_plot.py

@@ -1,0 +1,386 @@
+import sys
+import os
+import re
+import random
+from decimal import *
+import math
+
+from PyGrace.grace import Grace
+from PyGrace.colors import RandomColorScheme, MarkovChainColorScheme, ColorBrewerScheme
+from PyGrace.dataset import SYMBOLS
+from PyGrace.Extensions.panel import Panel,MultiPanelGrace
+from PyGrace.drawing_objects import DrawText, DrawLine
+
+from PyGrace.Extensions.distribution import CDFGraph, PDFGraph
+from PyGrace.Extensions.latex_string import LatexString, CONVERT
+
+scaledict={'centre':441.5587,'scale':115.3807}
+
+def signalreader(datapath,motif,suffix):
+  databank={'fixef':{},'ranef':{}}
+  f=open(datapath+motif+suffix+'_fixef.tsv','r')
+  for line in f:
+    if len(line.split())==2:
+      name=line.split()[0][1:-1]
+      effect=float(line.split()[1])
+      databank['fixef'][name]=effect
+  f.close()
+
+  ran=open(datapath+motif+suffix+'_ranef.tsv','r')
+  for line in ran:
+    if len(line.split())==3:
+      network=line.split()[0][1:-1]
+      intercept=float(line.split()[1])
+      slope=float(line.split()[2])
+      databank['ranef'][network]=(intercept,slope)
+  ran.close()
+
+  return databank
+
+def simlines(inter,beta):
+  simdata=[]
+  for i in range(0,101):
+    x=float(i)/100
+    y=inter+x*beta
+    logity=1/(1+math.exp(0-y))
+    simdata.append((x,logity))
+  return simdata
+
+def simlines_scaled(inter,beta):
+  simdata=[]
+  for i in range(2,80):
+    dist=10*i
+    scaledist=(dist-scaledict['centre'])/scaledict['scale']
+    y=inter+scaledist*beta
+    logity=1/(1+math.exp(0-y))
+    simdata.append((dist,logity))
+  return simdata
+
+def lineplotter(datapath,modeltype,colormode):
+  # dummy=[r"\| \|",r"\|\\\|",r"\|,X\|"]
+  # dummy=['Plant-herbivore networks','Plant-pollinator networks','','','','']
+  dummy=['Total overlap','Partial overlap','No overlap','','','']
+  if modeltype=='scaled':
+    suffix='_reg_unranked_scaled'
+  else:
+    suffix='_reg'
+
[…]

### 2018-12-13 code/families_to_networks.R

@@ -1,0 +1,52 @@
+library(Hmisc)
+library(lme4)
+library(vegan)
+
+phfiles<-as.character(list.files(path="../data/Corrected_Matrices/Plant_herbivore_matrices", full.names=TRUE, pattern="*.csv"))
+ppfiles<-as.character(list.files(path="../data/Corrected_Matrices/Stouffer_Ecology_Matrices", full.names=TRUE, pattern="*.csv"))
+
+netslopes=matrix(nrow=length(c(phfiles,ppfiles)),ncol=3)
+colnames(netslopes)=c("nettype","slope","p")
+
+families_by_network=read.table('../data/Jaccard/families_to_networks/families_by_network.csv',header=TRUE,sep=',')
+# Remove family-less species
+families_by_network$'X..'<-NULL
+# families with >20 species in all the dataset...
+goodfams=families_by_network[,which(colSums(families_by_network)>20)]
+goodfams$'Other'=rowSums(families_by_network)-rowSums(goodfams)
+
+#Gather the observed slopes
+fixeffs=read.table(paste('../data/Jaccard/Observed_Regression/observed_coefficients.tsv',sep=''))
+rownames(netslopes)=fixeffs[,1]
+netslopes[,1]=c(rep('ph',11),rep('pp',59))
+netslopes[,2]=fixeffs[,2]
+netslopes[,3]=fixeffs[,3]
+netslopes=as.data.frame(netslopes)
+netslopes[,2]=as.numeric(as.character(netslopes[,2]))
+netslopes[,3]=as.numeric(as.character(netslopes[,3]))
+
+fams=as.matrix(families_by_network)/rowSums(as.matrix(families_by_network))
+famdist=vegdist(fams,method="bray")
+
+goodnorm=as.matrix(goodfams)/rowSums(as.matrix(goodfams))
+gooddist=vegdist(goodnorm,method="bray")
+
+perm=adonis(famdist~netslopes[,2],strata=netslopes[,1],permutations=9999)
+perm2=adonis(gooddist~netslopes[,2],strata=netslopes[,1],permutations=9999)
+
+famassoc=cca(fams~netslopes[,2])
+famassoc2=cca(goodnorm~netslopes[,2])
+# Now see which of the goodfams are associated with the constraint axis.
+
+familyconts=summary(famassoc)$species[,1] # correlation with slope = -1
+familyconts=familyconts[order(familyconts)]
[…]

### 2018-12-13 code/helper_functions.R

@@ -1,0 +1,43 @@
+make_numeric_matrix <- function(network_matrix){
+
+  if('X'%in%colnames(network_matrix)){          # Trim any superfluous columns
+    network_matrix$X=NULL    }
+  if('X.1'%in%colnames(network_matrix)){          
+    network_matrix$X.1=NULL    }
+
+  numeric_matrix=matrix(nrow=nrow(network_matrix),ncol=ncol(network_matrix))
+  #Ensure all columns are numeric
+  for(i in 1:nrow(network_matrix)){
+    for(j in 1:ncol(network_matrix)){
+      if(as.numeric(as.character(network_matrix[i,j]))>0){
+        numeric_matrix[i,j]=1      }
+      if(as.numeric(as.character(network_matrix[i,j]))==0){
+        numeric_matrix[i,j]=0      }
+        }}
+
+  rownames(numeric_matrix)=rownames(network_matrix)
+  colnames(numeric_matrix)=colnames(network_matrix)
+
+
+	return(numeric_matrix)
+}
+
+
+calculate_overlap <- function(numeric_matrix,plantpair){
+
+	subnetwork=t(numeric_matrix[,plantpair,drop=FALSE])                 # select just the columns of interest
+	subnetwork=subnetwork[,which(colSums(subnetwork)>0),drop=FALSE]     # get rid of animals that don't have interactions
+	if(ncol(subnetwork) > 0){                                           # make sure there are at least some animals left
+	  intersection=length(which(colSums(subnetwork)==2))      
+	  union=ncol(subnetwork)
+	  notshared=length(which(colSums(subnetwork)==1))
+	  } else {
+	  	intersection=0
+	  	union=0
+	  	notshared=0
+	  }
+
+	result=c(intersection,union,notshared)
+	return(result)
+}
+

### 2018-12-13 code/how_many_extreme_specialists.R

@@ -1,0 +1,109 @@
+library(nlme)
+library(geiger)
+require(phytools)
+library(MASS)
+
+phfiles<-as.character(list.files(path="../data/Corrected_Matrices/Plant_herbivore_matrices", full.names=TRUE, pattern="*.csv"))
+ppfiles<-as.character(list.files(path="../data/Corrected_Matrices/Stouffer_Ecology_Matrices", full.names=TRUE, pattern="*.csv"))
+planttree=read.newick("../data/plant_phylogeny/dated_tree.new")
+
+#### Directory of species names and networks
+speciesnames=read.table('../data/plant_phylogeny/corrected_names.tsv',header=TRUE,sep=',')
+
+# Set up the results storage table
+result_table=matrix(nrow=length(c(phfiles,ppfiles)),ncol=9,data=1000)
+colnames(result_table)=c("network","network_type","spec_plants","spec_animals","gen_plants","gen_animals","n_plants","n_animals","plants_in_tree")
+
+for(n in 1:length(c(phfiles,ppfiles))){
+  file=c(phfiles,ppfiles)[n]
+  print(file)
+  netname=gsub('../data/Corrected_Matrices/','',file)
+
+  if(file%in%phfiles){
+    nettype='ph'} else {
+    nettype='pp'}
+
+  network_matrix=read.csv(file,header=TRUE,sep=',',row.names=1)
+  if('X'%in%colnames(network_matrix)){          # Trim any superfluous columns
+    network_matrix$X=NULL    }
+
+  numeric_matrix=matrix(nrow=nrow(network_matrix),ncol=ncol(network_matrix))
+  #Ensure all columns are numeric
+  for(i in 1:nrow(network_matrix)){
+    for(j in 1:ncol(network_matrix)){
+      if(as.numeric(as.character(network_matrix[i,j]))>0){
+        numeric_matrix[i,j]=1      }
+      if(as.numeric(as.character(network_matrix[i,j]))==0){
+        numeric_matrix[i,j]=0      }
+        }}
+
+  rownames(numeric_matrix)=rownames(network_matrix)
+  colnames(numeric_matrix)=colnames(network_matrix)
+
+  pdeg=colSums(numeric_matrix)
+  adeg=rowSums(numeric_matrix)
+
+  n_in_tree=length(which(colnames(network_matrix) %in% planttree$tip.label))
+
+  special_plants=as.numeric(length(which(pdeg==1)))
[…]

### 2018-12-13 code/outfile_checker.R

@@ -1,0 +1,22 @@
+source('helper_functions.R') 
+
+# Checking to make sure each file has the requisite 3 output files
+
+dirs<-as.character(list.files(path="../data/Jaccard/Random_Matrices", full.names=TRUE, pattern="*"))
+# print(dirs)
+for(n in 1:length(dirs)){
+
+  subdir=dirs[n]
+  print(subdir)
+  files <- as.character(list.files(path=subdir,full.names=TRUE,pattern="*.csv"))
+  if(length(files)!=3*999){
+    print('not done')
+    for(i in 900:999){
+      outfiles=grep(paste0('_',i,'_',sep=''),files)      
+      if(length(outfiles)!=3){
+        print(i)
+      }
+    }
+  }
+}
+

### 2018-12-13 code/randomisation_counter.py

@@ -1,0 +1,80 @@
+import os
+import sys
+
+def random_checker(RM):
+	notdone=[]
+	ranwebs=os.listdir(RM)
+	for web in sorted(ranwebs):
+		n_random=len(os.listdir(RM+'/'+web))
+		if n_random!=999:
+			print web, 999-n_random, "randomisations to go"
+			notdone.append(web)
+	return notdone
+
+def doubleran_checker(RRM,notdone):
+	orig=os.listdir(RRM)
+	for web in orig:
+		if web not in notdone:
+			ranwebs=os.listdir(RRM+'/'+web)
+			# if len(ranwebs)!=999:
+			# 	print web, len(ranwebs), 'missing a few head folders'
+			for rando in ranwebs:
+				dubs=os.listdir(RRM+'/'+web+'/'+rando)
+				if len(dubs)!=500:
+					print web, rando, len(dubs), 'missing double randomisations'
+
+def counter_checker(JD):
+	dirs=sorted(os.listdir(JD))
+	if len(dirs)<70:
+		print 'not all webs are done yet'
+	else:
+		print 'all webs present and accounted for'
+	for dire in dirs:
+		if dire!='.gitattributes' and '.zip' not in dire:
+			if len(os.listdir(JD+'/'+dire))!=3*999:
+				dones=set()
+				for outfile in os.listdir(JD+'/'+dire):
+					if outfile!='.gitattributes':
+						key=outfile.split('_')[-2]
+						dones.add(key)
+				print len(os.listdir(JD+'/'+dire))/3, dire
+				print 999-len(dones), 'to go'
+
+def regression_checker(RD):
+	files=os.listdir(RD)
+	for i in range(1,60):
+		outs=[]
+		for fil in files:
+			if 'M_PL_0'+str(i)+'_' in fil:
+				outs.append(fil)
+			if 'M_PL_00'+str(i)+'_' in fil:
+				outs.append(fil)
+		if len(outs)==2:
+			print i,'done'
+		else:
+			print len(outs), i, 'has more or less'
+	phouts=[]
+	for fil in files:
+		if 'ph' in fil:
+			phouts.append(fil)
+	if len(phouts)==22:
+		print 'all phs done'
+	else:
+		print phouts
+
+def main():
+
+	RM='../data/Random_Matrices'
+	RRM='../data/Random_Random_Matrices'
+	JD='../data/Jaccard/Random_Matrices'
[…]

### 2018-12-13 code/refine_matrices/auto_taxize.R

@@ -1,0 +1,248 @@
+library(taxize)
+
+data=read.table('../../data/plant_phylogeny/original_names.tsv',row.names=NULL,sep='\t')
+colnames(data)=c("original_name","original_genus","web","shortened_name")
+data<-data[2:nrow(data),]
+for (c in 1:ncol(data)){
+  data[,c]=as.character(data[,c])
+  print(str(data[,c]))
+}
+
+data<-data[order(data$shortened_name),]
+data$new_name<-NA
+data$source<-NA
+rownames(data)=paste0(data$original_name,data$web)
+
+names=levels(as.factor(data$shortened_name))
+n_unique=length(names) #2259 unique species
+
+dumb_names=c("Arthropod parts", "Unidentified sp.", "Unidentified sp13_MPL040",
+      "Unidentified sp14_MPL040", "Unidentified sp15_MPL040", "Unidentified sp16_MPL040",
+      "Unidentified sp17_MPL040", "Unidentified sp18_MPL040", "Unidentified sp19_MPL040",
+      "Unidentified sp20_MPL040", "Unidentified sp21_MPL040",  "Unidentified sp21_MPL041", 
+      "Unidentified sp22_MPL040", "Unidentified sp23_MPL040", "Unidentified sp27_MPL046",
+      "Unknown", "Unknown Forb_a", "Unknown Forb_b", "Unknown Forb_c", 
+      "Unknown Forb_d","Unknown Forb_e","Unknown Forb_f",                
+      "Unknown Forb_g","Unknown Forb_h","Unknown Forb_i",                
+      "Unknown Forb_j","Unknown Forb_k","Unknown Forb_l",                
+      "Unknown Forb_m","Unknown Forb_n","Unknown Forb_o",                
+      "Unknown Forb_p","Unknown Forb_q","Unknown Forb_r",                
+      "Unknown Forb_s","Unknown Voucher_no._1","Unknown lichen",
+      "Unidentified Voucher_no.28",
+      "Phasuba","Ceballosia fruticosa","Dalea spp.1","Dalea spp.2","Tyttnera scabra")
+
+daleas=c("Dalea spp.1","Dalea spp.2")
+# Dalea is ok but the spp. throws TNRS off
+
+good_names=names[!names %in% dumb_names]
+n_good=length(good_names)
+
+# Note: tnrs does NOT preserve order of query lists. Fun.
[…]

### 2018-12-13 code/refine_matrices/create_corrected_matrices.py

@@ -1,0 +1,235 @@
+import csv
+import sys
+import os
+import re
+
+# Gymnosperms: PH (13 plants)
+# Adding unmatched species manually using Mat's R code (bottom)
+# Peralta has 11 of the unmatched.
+# Coley has 1 unmatched, bodner has 3, bluthgen has 2
+webs_with_unmatched=['ph-peralta-2014-marlborough-metaweb.new','ph_bluthgen_2006_borneo_handmade.new','ph_coley_2006_panama_handmade.new','ph_bodner_2010_handmade.new']
+
+def create_name_dict(namefile):
+  namedict={}
+  f=open(namefile,'r')
+  for line in f:
+    if len(line.split('\t'))!=2:
+      print line.split('\t')
+      sys.exit()
+    if line.split('\t')[0]!='Input':
+      namedict[line.split('\t')[0]]=line.split('\t')[1].split('\n')[0]
+  f.close()
+  return namedict
+
+def rowlist_builder(matfile,directory):
+  g=open(directory+matfile,'r')
+  rows=csv.DictReader(g)
+
+  rowslist=[]
+  for row in rows:
+    rowslist.append(row)
+  g.close()
+  return rowslist
+
+def slashdelim_builder(namedict,matfile,directory,slashdelims): # Also makes little phylogenies
+  if 'M_PL' in matfile:
+    filenum=int(matfile.split('_')[-1].split('.')[0])
+  else:
+    filenum=0
+  rowslist=rowlist_builder(matfile,directory)
+  for plant in rowslist[0].keys():
+    if plant not in [None,"''",' ','']:
+      if plant not in namedict.keys():
+        print plant, matfile
+        sys.exit()
+      mscname=namedict[plant]
+      modname='/'.join(mscname.split('/')[:2])+'/'+'_'.join(mscname.split('/')[1:])
+      slashdelims.append(modname)        
+  return slashdelims
+
+def slashdelim_printer(slashdelims,phylofile): # Makes one enormous phylogeny
+  if 'ph' not in phylofile:
+    outfile=open('../../data/plant_phylogeny/PP_webs/'+phylofile.split('.csv')[0]+'_tree.tsv','w')
+  else:
[…]

### 2018-12-13 code/refine_matrices/ensure_plants_columns.py

@@ -1,0 +1,123 @@
+import csv
+import sys
+import os
+import re
+
+### known genera/species of plants and insects to confirm orientation of matrices
+
+common_bugs=set(['Apis','Bombus','Culex','Papilio','Xylocopa','Ichneumonidae',
+                'Acarina','Peremptor','Aedes', 'Xanthia','Abraxas','Melanopus',
+                'Bootettix','Phalera','Gomphocerus','Opeia','Melanoplus','Diptera',
+                'Cleora.sp','Holocola.sp','Neolepta_34','Acacus_sarawacus','Bryoptera',
+                'Udranomia_sp','CURC012'])
+
+common_plants=set(['Artemisia','Carolus','Quercus','Avicenna','Lantana',
+                    'Opuntia','Epilobium','Vaccinium','Cassinia','Pedicularis',
+                    'Prunus','Aristida','Erigonum','Bromus','Lotus','Mentha','Acaena',
+                    'Oxalis','Astragalus','Passiflora','Adenocarpus','Asclepias','Thymus',
+                    'Viola','Trillium','Mimosa','Claytonia','Myrteola','Angelica','Allium','Ribes',
+                    'coprosma_robusta','Cordia_dichotoma','Liana_unidentified','Hyptis_sp',
+                    'Cordia_bicolor','Ficus_copiosa'
+                    ])
+
+def are_plants_columns(filename,inverted_matrices):
+  row_genera=set()
+  column_genera=set()
+
+  f=open(filename,'r')
+  filebase=csv.DictReader(f)
+
+  for row in filebase:
+    for key in row:
+      if key=='':
+        row_genera.add(row[key].split(' ')[0])
+      else:
+        column_genera.add(str(key).split(' ')[0])
+
+  f.close()
+  # print row_genera
+  if column_genera&common_bugs!=set([]):
+    print 'It appears that file ', filename, ' has pollinators as columns'
+    inverted_matrices.append(filename)
+
+    if row_genera&common_plants!=set([]):
+      print 'Indeed, plants are on the rows.' 
+
+  else:
+
+    if row_genera&common_bugs==set([]):
+      print 'Add more insects', filename
+    if column_genera&common_plants==set([]):
+      print 'Add more plants', filename
+
+
+def flip_the_matrix(matfile):
+  f=open(matfile,'r')
+  filebase=csv.DictReader(f)
+
+  reversedict={}
+
+  plantnames=set()
+
+  for row in filebase:
+    plantname=row['']
+    plantnames.add(plantname)
[…]

### 2018-12-13 code/refine_matrices/plant_name_extractor.py

@@ -1,0 +1,76 @@
+import csv
+import sys
+import os
+import re
+
+
+def extract_plant_names(filename,plant_names):
+
+  f=open(filename,'r')
+  filebase=csv.DictReader(f)
+
+  for row in filebase:
+    for key in row:
+      if key not in ['','None',None]:
+        plant_names.add((key,filename))
+  f.close()
+
+  return plant_names
+
+def print_name_list(plant_names):
+  outfile=open('../../data/plant_phylogeny/original_names.tsv','w')
+  outfile.write('original_name\toriginal_genus\tweb\tshortened_name\n')
+  for (item,web) in plant_names:
+    webname=web.split('/')[-1]
+    if '_' in item:
+      splitname=item.split('_')
+    else:
+      splitname=item.split()
+    if item=="Cuphea o'donellii": # Dat apostrophe though
+      item="Cuphea odonellii"
+      splitname=['Cuphea','odonellii']
+
+    if len(splitname) in [1,2]: # Regular genus, species case or just genus. Nothing fancy.
+      outfile.write(item+'\t'+splitname[0].capitalize()+'\t'+webname+'\t'+' '.join(splitname).capitalize()+'\n')
+    elif 'var.' in splitname or 'subsp.' in splitname: # Don't care about subspecies, varieties.
+      outfile.write(item+'\t'+splitname[0].capitalize()+'\t'+webname+'\t'+' '.join(splitname[:2]).capitalize()+'\n')
+    elif 'PL' in splitname:  # Unknown numbered species with web IDs to ensure distinctness
+      species=splitname[0].split()
+      other=splitname[1:]
+      webtag=species[-2]+'_'+species[-1]+''.join(other)
+      outfile.write(item+'\t'+species[0]+'\t'+webname+'\t'+species[0].capitalize()+' '+webtag+'\n')
+    elif 'Unknown' in splitname or 'Unidentified' in splitname or 'Other' in splitname:
+      outfile.write(item+'\t'+splitname[0].capitalize()+'\t'+webname+'\t'+splitname[0]+' '+'_'.join(splitname[1:]).capitalize()+'\n')
+    else:
+      if 'sp.' in splitname or 'sp' in splitname:
+        modname=[bit for bit in splitname if bit not in ['sp','sp.']]
+        outfile.write(item+'\t'+splitname[0].capitalize()+'\t'+webname+'\t'+' '.join(modname).capitalize()+'\n')
+      elif 'unidentified' in splitname or 'subgen.' in splitname:
[…]

### 2018-12-13 code/sorting_tips_to_families.R

@@ -1,0 +1,87 @@
+# Read in the overlap data files (made by overlap_vs_distance.R)
+files1<-as.character(list.files(path="../data/Jaccard/Overlap_dist/Plant_herbivore_matrices", full.names=TRUE, pattern="*.csv"))
+files2<-as.character(list.files(path="../data/Jaccard/Overlap_dist/Stouffer_Ecology_Matrices", full.names=TRUE, pattern="*.csv"))
+
+files=c(files1,files2)
+
+overlap_data <- list()
+for(network in files){
+  netname=gsub('../data/Jaccard/Overlap_dist/',"",network)
+  subfolder=strsplit(strsplit(netname,'-')[[1]][1],'/')[[1]][1]
+  if(subfolder=='Stouffer_Ecology_Matrices'){
+    nettype='pp'  } else {
+      nettype='ph'   }
+
+  message(paste0("Processing '",netname,"' "),appendLF=FALSE)
+
+  overlap_data[[netname]]=read.csv(network,header=TRUE,row.names=1,check.names=FALSE,sep=',')
+  overlap_data[[netname]]$network <- netname
+  overlap_data[[netname]]$nettype <- nettype
+
+  message("Done")
+}
+
+all_data <- do.call("rbind", overlap_data)
+for(r in 1:nrow(all_data)){
+  sp=strsplit(rownames(all_data)[r],'.csv.')[[1]][2]
+  all_data$sp1[r]=strsplit(sp,':')[[1]][1]
+  all_data$sp2[r]=strsplit(sp,':')[[1]][2]
+}
+all_data$fam1="quirk"
+all_data$fam2="quirk"
+
+# Read in the file that has the correct families
+taxonomy=read.table('../data/plant_phylogeny/inputs_to_outputs.tsv',header=TRUE,sep='\t')
+for(r in 1:nrow(taxonomy)){
+  taxonomy$family[r]=strsplit(as.character(taxonomy$Output[r]),'/')[[1]][1]
+  taxonomy$genus[r]=strsplit(as.character(taxonomy$Output[r]),'/')[[1]][2]
+  taxonomy$species[r]=strsplit(as.character(taxonomy$Output[r]),'/')[[1]][3]
+  taxonomy$name[r]=paste0(taxonomy$genus[r],'_',taxonomy$species[r])
+
+}
+
+for(sp in levels(as.factor(all_data$sp1))){
+  for(r in 1:nrow(taxonomy)){
[…]

### 2019-02-09 code/create_figures/cladewise_barplot.py
edits to Fig. 1

@@ -88,6 +88,7 @@ scaledict={
 
 # Two families didn't converge (small samples with one odd value)
 non_convergent={'pp':'lauraceae','ph':'sapindaceae'}
+legenddict={'pp':'Plant-pollinator','ph':'Plant-herbivore'}
 
 def read_tree(filename):
     inFile = open(filename,'r')
@@ -112,6 +113,7 @@ def signalreader(datapath,family,nettype):
   return databank
 
 def overall_signalreader(datafile):
+  print datafile
   databank={}
   f=open(datafile,'r')
   for line in f:
@@ -126,6 +128,10 @@ def overall_signalreader(datafile):
   return phslope, ppslope
 
 def lineplotter(datapath,family,grace,graph,x,graphtype,supertype,nettype,summarydict):
+  if nettype=='pp':
+    shap=3
+  else:
+    shap=2
   databank=signalreader(datapath,family,nettype)
   if family not in non_convergent[nettype] and databank!={'fixef':{},'ranef':{}}:
     try:
@@ -163,10 +169,11 @@ def lineplotter(datapath,family,grace,graph,x,graphtype,supertype,nettype,summar
         else:
           col=10
 
-      dat.symbol.configure(color=1,fill_color=col,size=.6,linewidth=.3,shape=3)
+      dat.symbol.configure(color=1,fill_color=col,size=.6,linewidth=.3,shape=shap)
       dat.line.linestyle=0
       dat.errorbar.configure(riser_linewidth=1,linewidth=1.25,size=.75)
-
+      if family=='rubiaceae':
+        dat.legend=legenddict[nettype]
       if y>150:
         graph.add_drawing_object(DrawLine,arrow=2,start=(60,y),end=(85,y),loctype='world')
         # if y-err > 0:
@@ -195,7 +202,7 @@ def overall_lineplotter(graph,grace,supertype,graphtype):
   if supertype=='paper':
     Hline=graph.add_dataset([(0,phslope),(60,phslope)])
     Hline.symbol.size=0
-    Hline.line.configure(linewidth=1.25,color=col1)
+    Hline.line.configure(linewidth=1.25,linestyle=3,color=col1)
 
   # print phslope, ppslope
[…]

### 2019-02-09 manuscript/phylogenetic_signal_manuscript.tex
made a figure to show significance of slopes

@@
 \author{Alyssa R. Cirtwill$^{1}$, Giulio V. Dalla Riva$^{2}$, Nick J. Baker$^{1}$,\\
- Joshua A. Thia$^{1,3}$, Christie J. Webber$^{1}$, Daniel B. Stouffer$^{1}$}
+ Joshua A. Thia$^{1,3}$, Christie J. Webber$^{1}$, Daniel B. Stouffer$^{1}$, MSC helpers from Linkoping}
 \date{\small$^1$Centre for Integrative Ecology, School of Biological Sciences\\
@@
 In the remaining four plant-herbivore networks and 25 of the 26 remaining plant-pollinator networks, overlap of interaction partners was not related to phylogenetic distance.
-Overlap of interaction partners increased with increasing phylogenetic distance in only a single plant-pollinator network.
-% (M_PL_026).
+Overlap of interaction partners increased with increasing phylogenetic distance in only a single plant-pollinator network.% (M_PL_026).
 
     [[Reviewers demanded this - it seems very boring]]
-    Comparing the results in the observed networks to those obtained after randomising phylogenetic distances across pairs of plants, the observed slope of the relationship between phylogenetic distance and interaction partner overlap was always more extreme (i.e., always lesser or always greater) than that obtained in the random networks.
+    Comparing the results in the observed networks to those obtained after randomising phylogenetic distances across pairs of plants, the observed slope of the relationship between phylogenetic distance and interaction partner overlap was always more extreme (i.e., always lesser or always greater) than that obtained in the random networks (Fig.~\ref{obs_vs_random}).
 Observed networks with a negative relationship between phylogenetic distance and overlap always had a more negative slope than that obtained from the random networks, while the 10 networks with positive relationships between phylogenetic distance and overlap always had more positive relationships than the random networks.
@@
 
-  ARC, DBS, GVDR, and NJB designed the research. ARC, JAT, and CJW collected published data.
+  ARC, DBS, GVDR, and NJB designed the research. ARC, JAT, and CJW collected published data. [[Add MSC helpers!]]
   ARC and GVDR performed the analyses. All authors contributed to the manuscript.
@@
      sharing an interaction partner increased with increasing phylogenetic distance (thick,
-     dark lines). There was substantial variation among networks (thin, pale lines) of both types.}
+     dark lines).
+There was substantial variation among networks (thin, pale lines) of both types.
+The slope of the regression for each network was significantly more extreme than that obtained from 999 permutatations of that network (slopes obtained from the permuted networks ranged between -1.34$\times10^{-12}$ and 9.19$\times10*{-13}$).}
     \label{within_network_regression} 
+  \end{figure}
+
+  \begin{figure}[!h]
+    \begin{center}
+      \centerline{\includegraphics*[width=.75\textwidth]{Figures/dataplots/observed_vs_random.eps}}
+    \end{center}
+     \caption{The slopes of the mixed-effect logistic regression of pairwise niche overlap against phylogenetic distance was signficantly different from 0 for each network.
+Here we show, for plant-herbivore (PH) and plant-pollinator (PP) networks, the observed slopes (depicted by green squares or purple diamonds, respectively).
+The maximum and minimum slopes obtained from 999 permutations of each network are depicted by thin, black lines.
+For both network types, the slopes obtained from permuted networks were always very close to 0.}
+    \label{obs_vs_random} 
   \end{figure}

### 2019-02-09 code/create_figures/observed_vs_random_slopes.py

@@ -1,0 +1,181 @@
+import sys
+import os
+import re
+import random
+from decimal import *
+import math
+
+from PyGrace.grace import Grace
+from PyGrace.colors import RandomColorScheme, MarkovChainColorScheme, ColorBrewerScheme
+from PyGrace.dataset import SYMBOLS
+from PyGrace.Extensions.panel import Panel,MultiPanelGrace
+from PyGrace.drawing_objects import DrawText, DrawLine
+
+from PyGrace.Extensions.distribution import CDFGraph, PDFGraph
+from PyGrace.Extensions.latex_string import LatexString, CONVERT
+
+
+def read_regfile(regfile):
+  obslopes={'pp':[],'ph':[]}
+  ranslopes={'pp':[],'ph':[]}
+  f=open(regfile,'r')
+  for line in f:
+    if line.split()[0]!='"Observed"':
+      netname=line.split()[0][1:-1]
+      if netname[:2]=='ph':
+        nettype='ph'
+      elif netname[:4]=='M_PL':
+        nettype='pp'
+      if nettype not in ['pp','ph']:
+        print line.split()[:3]
+        sys.exit()
+      obs=float(line.split()[1])
+      rans=line.split()[2:]
+      obslopes[nettype].append(obs)
+      for ran in rans:
+        ranslopes[nettype].append(float(ran))
+  f.close()
+
+  return obslopes, ranslopes
+
+def format_graph(graph,nettype):
+
+  graph.world.ymin=-.600000000001
+  graph.world.ymax=.2
+  graph.yaxis.tick.configure(place='both',major_size=.4,minor_ticks=1,minor_size=.2,major=.2,major_linewidth=1,minor_linewidth=1)
+  graph.yaxis.ticklabel.configure(char_size=.75,format='decimal',prec=1)
+  graph.yaxis.bar.linewidth=1
+
+  graph.world.xmin=0.45
+  graph.world.xmax=.55
+  graph.xaxis.tick.configure(place='both',major_size=.4,minor_ticks=1,minor_size=.2,major=2,major_linewidth=1,minor_linewidth=1)
+  graph.xaxis.ticklabel.configure(char_size=0,format='decimal',prec=0)
+
+  graph.frame.linewidth=1
+  graph.xaxis.bar.linewidth=1
+  
+  graph.panel_label.configure(char_size=.85,placement='ouc',dy=0.01,dx=0,just=2)
+
+  return graph
+
[…]

### 2019-02-09 code/create_figures/signal_barplots.py

@@ -1,0 +1,123 @@
+import sys
+import os
+import re
+import random
+from decimal import *
+import math
+
+from PyGrace.grace import Grace
+from PyGrace.colors import RandomColorScheme, MarkovChainColorScheme, ColorBrewerScheme
+from PyGrace.dataset import SYMBOLS
+from PyGrace.Extensions.panel import Panel,MultiPanelGrace
+from PyGrace.drawing_objects import DrawText, DrawLine
+
+from PyGrace.Extensions.distribution import CDFGraph, PDFGraph
+from PyGrace.Extensions.latex_string import LatexString, CONVERT
+
+def signalreader(datapath,sig):
+  databank={'ph':{},'pp':{}}
+  f=open(datapath,'r')
+  for line in f:
+    line2=line.split('\n')[0]
+    newline=line2.split(',')
+    if len(newline)==5 or len(newline)==7:
+      x=int(newline[0][1:-1])
+      netname=newline[1][1:-1]
+      nettype=newline[2][1:-1]
+      if sig!='degree':
+        K=float(newline[3][1:-1])
+        p=float(newline[4][1:-1])
+      else:
+        K=float(newline[5][1:-1])
+        p=float(newline[6][1:-1])
+      databank[nettype][x]=((K,p,netname))
+  f.close()
+  return databank
+
+def indiv_plot(sig,plottype,datapath):
+
+  grace=Grace(colors=ColorBrewerScheme('PRGn'))
+  graph=grace.add_graph()
+
+  ppset=[]
+  phset=[]
+  ys=[]
+  if plottype!='axis':
+    databank=signalreader(datapath,sig)
+
+    if plottype=='one':
+      net=65
+      ppset.append((70-net,1-databank['pp'][net][1]))
+    else:
+      for net in databank['pp']:
+        ys.append((1-databank['pp'][net][1],'pp'))
+
+    if plottype=='full':
+      for net in databank['ph']:
+        ys.append((1-databank['ph'][net][1],'ph'))
+
+    for i in range(0,len(sorted(ys))):
+      if sorted(ys,reverse=True)[i][1]=='pp':
+        ppset.append((i+2,sorted(ys,reverse=True)[i][0]))
+      elif sorted(ys,reverse=True)[i][1]=='ph':
+        phset.append((i+2,sorted(ys,reverse=True)[i][0]))
[…]

### 2019-02-13 manuscript/phylogenetic_signal_manuscript.tex
working on DBS comments

@@
 
+  [[update refs, add definition of plant roles]]
   If attractive and/or defensive traits are heritable,
@@
   tends to be rare in empirical networks (\citealp{Rezende2007a,Lind2015}; but see~\citealp{Elias2013,Fontaine2015}).
-  Further, plants' roles within networks tend to be less phylogenetically constrained than those of 
-  animals~\citep{Rezende2007a,Chamberlain2014,Rohr2014,Vamosi2014,Lind2015}.
+  Further, plants' roles [[how defined?]] within networks tend to be less phylogenetically constrained than those of 
+  animals~\citep{Rezende2007a,Chamberlain2014,Rohr2014,Vamosi2014,Lind2015}. [[GVDR is skeptical of this - check partiteness, size, type of role and add more detail to support.]]
 
@@
   Likewise, herbivores may be able to depredate sets of unrelated 
-  plants if they have evolved similar defences~\citep{Pichersky2000}. 
+  plants if the plants have evolved similar defences~\citep{Pichersky2000}. 
   In either case, dissimilarity of interactions among related species 
   or similarity of interactions among unrelated species could result 
-  in low apparent phylogenetic signal across an entire plant community. 
+  in weaker phylogenetic signal across an entire plant community. 
   Moreover, all of the aforementioned hypotheses 
@@
 
-  Here we use a novel approach to investigate how the patterns of
-  overlap in interaction partners between pairs of plants (henceforth
-  ``niche overlap'') vary over phylogenetic distance. Whereas previous
+  Here we use a novel approach to investigate how overlap in 
+  interaction partners between pairs of plants (henceforth ``niche 
+  overlap'') varies over phylogenetic distance. Whereas previous 
   studies have focused on the presence or absence of phylogenetic
@@
   whether the plant family composition of a community affects the
-  relationship between niche overlap and phylogenetic distance in that community,
-  and whether the relationship between niche overlap and phylogenetic
-  distance differs across plant families.
+  relationship between niche overlap and phylogenetic distance in that 
+  community, and whether the relationship between niche overlap and 
+  phylogenetic distance differs across plant families.
 
@@
 
-  We studied phylogenetic conservation of interactions within a 
-  set of 59 pollination and 11 herbivory networks. 
-  These networks span a range of biomes 
-  (desert to scrub forest to grassland) and countries (Sweden to 
-  Australia), and range in size between 18 and 996 total species 
-  (mean 160.93, median 96) with seven to 131 plant species (mean 38.06, 
-  median 28).
-  To ensure that we were analysing interactions influenced by similar
-  sets of traits across networks, we restricted our herbivory 
-  networks to insects consuming leaves. This excluded sap-sucking, 
-  leaf-mining, and galling insects as well as seed predators and
-  xylophagous insects; all of these interactions involve different 
-  plant tissues and means of feeding
-  than leaf consumption and so may be influenced by different
-  plant and insect traits. The bulk of our herbivory networks 
-  included only leaf-chewing insects. Where a network contained other
-  types of herbivores we removed the non-leaf-chewing insects. Any
+  We studied tested for phylogenetic signal in niche overlap within a 
+  set of 59 pollination and 11 herbivory networks. These networks span 
+  a range of biomes (desert to scrub forest to grassland) and 
+  countries (Sweden to Australia). The herbivory networks included a 
+  variety of types of herbivores but were dominated by insects 
+  consuming leaves. To ensure that we were analysing interactions 
+  influenced by similar sets of traits across networks, we restricted 
+  our herbivory networks to insects consuming leaves and excluded 
+  sap-sucking, leaf-mining, and galling insects as well as seed 
+  predators and xylophagous insects; all of these interactions involve 
+  different plant tissues and means of feeding than leaf consumption 
+  and so may be influenced by different plant and insect traits. 
+  Specifically, we removed any non-leaf consuming insects and any 
   plants which had no interaction partners after removing other types  
-  of herbivores were also removed. We also excluded networks which focused on
-  plants from a single genus as these did not contain sufficient
-  variation in phylogenetic distance between plants. This left us
-  with a final data set of 54 pollination and 11 herbivory networks.
-  See \emph{Table S1, Supporting Information} for details on the original 
-  sources of all networks.
+  of herbivores. The adjusted networks range in size between 19 and 
+  997 total species (mean=162, median=97) with  between 8 and 132 
+  plant species (mean=39.1, median=29.5). See \emph{Table S1, 
+  Supporting Information} [[NOT DONE!]]for details on the original sources of all 
+  networks.
 

### 2019-02-13 code/network_sizes.R

@@ -1,0 +1,41 @@
+# library(ape)
+# library(geiger)
+# library(nlme)
+# library(phytools)
+
+source('helper_functions.R') 
+# Contains functions for turning networks into binary matrices,
+###########################################################################################################
+
+phfiles<-as.character(list.files(path="../data/Corrected_Matrices/Plant_herbivore_matrices", full.names=TRUE, pattern="*.csv"))
+ppfiles<-as.character(list.files(path="../data/Corrected_Matrices/Stouffer_Ecology_Matrices", full.names=TRUE, pattern="*.csv"))
+
+# Here I'll count up how many species we're getting in each family.
+network_sizes=matrix(nrow=length(phfiles)+length(ppfiles),ncol=3)
+
+for(n in 1:length(c(phfiles,ppfiles))){
+  file=c(phfiles,ppfiles)[n]
+  net=gsub("../data/Corrected_Matrices/","",file) # Type of network, network name
+  netname=gsub("_corrected.csv","",net)                     # same without .csv
+
+  if(file%in%phfiles){
+    nettype='ph'} else {
+    nettype='pp'}
+
+  # Read in network matrix, convert it to a numeric one
+  network_matrix=read.csv(file,header=TRUE,sep=',',row.names=1)
+  numeric_matrix=make_numeric_matrix(network_matrix)
+
+  nplants=ncol(network_matrix)
+  nanimals=nrow(network_matrix)
+  network_sizes[n,]=c(netname,nplants,nanimals)  
+}
+
+network_sizes=as.data.frame(network_sizes)
+colnames(network_sizes)=c("network","n_plants","n_animals")
+network_sizes$n_plants=as.numeric(as.character(network_sizes$n_plants))
+network_sizes$n_animals=as.numeric(as.character(network_sizes$n_animals))
+network_sizes$total_species=network_sizes$n_plants+network_sizes$n_animals
+
+print(network_sizes)
+# write.table(families_by_network,file='../data/Jaccard/families_to_networks/families_by_network.csv',sep=',')

### 2019-02-14 manuscript/phylogenetic_signal_manuscript.tex
still going through comments

@@
 
-  We calculated niche overlap for each pair of species within
-  a community using a modified Jaccard index. The 
-  Jaccard index $J_{ij}$ describes the proportion of shared interaction 
-  partners for for species $i$ and $j$ and is defined as:
+  We calculated niche overlap for each pair of species within a community 
+  using a Jaccard index to describe the number of shared interaction 
+  partners, augmented with the number of interaction partners which were 
+  not shared. The Jaccard index $J_{ij}$ describes the proportion of 
+  shared interaction partners for for species $i$ and $j$ and is defined as:
 
   \begin{equation}
-    J_{ij} = \frac{M_{ij}}{P_i+P_j-M_ij} ,,
+    J_{ij} = \frac{M_{ij}}{P_i+P_j-M_{ij}} ,
   \end{equation}
@@
   where $M_{ij}$ is the set of \emph{mutual} (shared) interaction partners of 
-  species $i$ and $j$ and $P_i$ and $P_j$ are the sets of interaction 
+  species $i$ and $j$ and $P_i$ and $P_j$ are the sizes of the sets of interaction 
   \emph{partners} for species $i$ and $j$ respectively. We wished to give more 
@@
   shared interaction partners $M_{ij}$ and the number of interaction partners 
-  that were not shared ($U_{ij}$ = $P_{i}$+$P_{j}$-2$M_{ij}$). Instead of a 
-  single index $J_{ij}$ we therefore defined niche overlap between species
-  $i$ and $j$ as a tuple: ($M_{ij}$, $U_{ij}$).
+  for each species pair that were not shared 
+  ($U_{ij}$ = $P_{i}$+$P_{j}$-2$M_{ij}$). Instead of a single index $J_{ij}$ 
+  we therefore keep track of the information needed to compute
+  niche between species $i$ and $j$ as a tuple: ($M_{ij}$, $U_{ij}$).
 
@@
   We modelled the relationship between niche overlap and phylogenetic distance
-  using a logistic regression. We used both the numbers of shared and 
-  non-shared partners as dependent variables and centred, scaled phylogenetic 
-  distance as the independent variable. This is conceptually similar to 
+  using a logistic regression. We used both the numbers of shared ($M_{ij}$)and 
+  non-shared ($U_{ij}$) partners as dependent variables and centred, scaled phylogenetic 
+  distance as the independent variable. This approach is conceptually similar to 
   modelling successes and failures in a binomial-distributed process. 
-  Accordingly, we assumed a binomial distribution for residuals. All regressions were fit using the R~\citep{R} function 
-  ``glm'' from package \emph{lme4}~\citep{lme4}. To avoid potential 
-  confounding effects of different relationships in different networks, we 
-  modelled the relationship between overlap and phylogenetic distance within 
-  each network separately.
+  Accordingly, we assumed a binomial distribution for residuals. Regressions of
+  niche overlap and phylogenetic distance within each network were fit using the
+  R~\citep{R} base function ``glm''. These separate regressions avoid the potential
+  for confounding the effects of different relationships in different networks. As
+  we also wished to evaluate the overall trend across networks, we fit an additional
+  regression of niche overlap and phylogenetic distance across all network types.
+  As well as the fixed effect of phylogenetic distance, this regression included 
+  fixed effects of network type (pollination or herbivory) and the interaction 
+  between phylogenetic network type and random intercepts and slopes per network.
+  This expanded regression was fit using the R~\citep{R} function ``glmer'' from
+  package \emph{lme4}~\citep{lme4}. [[Confirm that I actually use the separate 
+  regressions and not just the full one. ]]
 
@@
   calculating the significance of logistic regressions within the R~\citep{R} 
-  package \emph{lme4}~\citep{lme4}. To calculate significance of the 
-  relationships we observed, it was therefore necessary to compare the 
-  observed relationships to those in a suite of random networks. To create 
+  base package or the package \emph{lme4}~\citep{lme4}. To calculate significance 
+  of the regression coefficients we observed, it was therefore necessary to compare the 
+  observed relationships to those in a suite of appropriately permuted networks. To create 
   these networks, we shuffled interactions among species while preserving row 
@@
   partners (and therefore niche overlaps with all other species) varied across 
-  random networks. We preserved the observed phylogenetic relationships 
+  permuted networks. We preserved the observed phylogenetic relationships 
   between species in all cases. For each observed network, we created 999 such 
-  random networks and calculated the relationship between niche overlap and 
+  permuted networks and calculated the relationship between niche overlap and 
   phylogenetic distance. This gave us a null distribution for each observed 
@@
 
-  This randomization approach also allows us to estimate type I and type II 
-  error for our analysis. To do this, we created 500 randomizations of each 
-  random network and, again keeping the observed phylogenetic distances 
+  This permutation approach also allows us to estimate type I and type II 
+  error for our analysis. To do this, we created 500 permutations of each 
+  permuted network and, again keeping the observed phylogenetic distances 
   between plant species, repeated our analyses. We can then determine the 
-  number of randomized networks which appear to have significant 
-  overlap-phylogenetic distance relationships relative to the randomizations 
-  of these random networks (type I error). [[How does this get at type II error?]]
+  number of permuted networks which appear to have significant 
+  overlap-phylogenetic distance relationships relative to the permutations 
+  of these permuted networks (type I error). [[How does this get at type II error?]]
 
@@
     [[Reviewers demanded this - it seems very boring]]
-    Comparing the results in the observed networks to those obtained after randomising phylogenetic distances across pairs of plants, the observed slope of the relationship between phylogenetic distance and interaction partner overlap was always more extreme (i.e., always lesser or always greater) than that obtained in the random networks (Fig.~\ref{obs_vs_random}).
-Observed networks with a negative relationship between phylogenetic distance and overlap always had a more negative slope than that obtained from the random networks, while the 10 networks with positive relationships between phylogenetic distance and overlap always had more positive relationships than the random networks.
+    Comparing the results in the observed networks to those obtained after permuting phylogenetic distances across pairs of plants, the observed slope of the relationship between phylogenetic distance and interaction partner overlap was always more extreme (i.e., always lesser or always greater) than that obtained in the permuted networks (Fig.~\ref{obs_vs_random}).
+Observed networks with a negative relationship between phylogenetic distance and overlap always had a more negative slope than that obtained from the permuted networks, while the 10 networks with positive relationships between phylogenetic distance and overlap always had more positive relationships than the permuted networks.
 
-    Comparing the random networks to randomizations of the random networks, the slope obtained from the initial random network was quite variable with respect to the slopes obtained from 500 randomizations of the random network.
-Averaged over the 1000 randomizations of each observed network, the slope of the random network was more extreme than 48.1-51.3\% of the randomizations of the random network.
+    Comparing the permuted networks to permutations of the permuted networks, the slope obtained from the initial permuted network was quite variable with respect to the slopes obtained from 500 permutationss of the permuted network.
+Averaged over the 1000 permutations of each observed network, the slope of the permuted network was more extreme than 48.1-51.3\% of the permutations of the permuted network.
 This confirms that shuffling phylogenetic distances between plant pairs destroys the relationship between distance and interaction partner overlap, and that further shuffling distances does not have a predictable effect.

### 2019-02-15 manuscript/phylogenetic_signal_manuscript.tex
realised I need to update the by-family regressions still

@@
   overlap-phylogenetic distance relationships relative to the permutations 
-  of these permuted networks (type I error). [[How does this get at type II error?]]
+  of these permuted networks (type I error). Type II error can be determined
+  from the distribution of p-values obtained when comparing the permuted 
+  networks to permutations of the permuted networks. The distribution of 
+  p-values should be uniform. [[I still do not see how this gives us the
+  probability of a false negative... ]] [[Something to do with comparing
+  the distributions of p-values from glmer and the ones from the randomization.
+  I don't think I actually kept the p-values from glmer, but the p-values from
+  the randomizations are bang-on uniform.]]
+  [[Maybe go back to whichever reviewer comment this was based on?]]
+  [[How does this get at type II error?]] 
+  [[Seems we can calculate power for a specific alternative hypothesis by
+  comparing distributions of p-values from glmer and from the permutations.
+  I can only pray I kept the p-values from the randomised regressions...]]
 
@@
   pairwise niche overlap are due to the different distributions 
-  of families across networks. To do this, we performed a non-parametric
-  permutational multi-variate analysis of variance
-  (PERMANOVA;~\citealp{Anderson2001}) using the change in log
-  odds of two plants sharing an interaction partner to 
-  predict the Bray-Curtis dissimilarity of networks
-  based on the composition of their plant component
-  (defined as the proportions of the plant community
-  made up by each plant family present in the entire dataset).
-  We used Bray-Curtis dissimilarity because, for a given
-  pair of networks, only those plant families that appear
-  in at least one network are considered~\citep{Anderson2001,Cirtwill2015}; 
-  that is, the absence of rare plant families will not make 
+  of families across networks. We defined the relationship between
+  phylogenetic distance and niche overlap as the change in 
+  log odds of two plants in a given network sharing an interaction 
+  partner per million years of divergence (i.e., the slope from the 
+  regression of niche overlap against phylogenetic distance within
+  a single network). We then related differences in this relationship
+  to differences in the composition of the plant community in each
+  network using a non-parametric permutational multi-variate 
+  analysis of variance (PERMANOVA;~\citealp{Anderson2001}).
+  As we did not wish to inflate the perceived similarity between
+  pairs of networks which did not include many of the same families,
+  we used Bray-Curtis dissimilarity to define differences in plant
+  community composition. Bray-Curtwis dissimilarity considers only
+  those plant families which appear in at least one of a pair of
+  networks~\citep{Anderson2001,Cirtwill2015}, ensuring that the
+  shared absence of rare plant families will not make 
   two networks appear more similar than they actually are.
@@
 \subsection*{Calculating niche overlap within families}
+
+  [[I need to double-check that I'm actually doing this, and that the right things
+  are being plotted.]][[I think I may not have updated this since the family composition 
+  was not singificant. Still of interest, so redo. Guess I will also need to do randomisations
+  to make the p-vals here?]]
 

### 2019-02-20 manuscript/phylogenetic_signal_manuscript.tex
I think I shan't redo the within-family stuff after all

@@
 
-Supporting information: 1 file containing 4 sections.
+Supporting information: 1 file containing 1 section.
 
@@
   plant species (mean=39.1, median=29.5). See \emph{Table S1, 
-  Supporting Information} [[NOT DONE!]]for details on the original sources of all 
+  Supporting Information} for details on the original sources of all 
   networks.
@@
   % [[It appears we switched to Jaccard and Sorenson dissimilarities - number of shared partners and number of shared partners*2/notshared.]]
-
 \subsection*{Statistical analysis}
 
-  We modelled the relationship between niche overlap and phylogenetic distance
+  We modelled the relationship between nich
+
+e overlap and phylogenetic distance
   using a logistic regression. We used both the numbers of shared ($M_{ij}$)and 
@@
   This expanded regression was fit using the R~\citep{R} function ``glmer'' from
-  package \emph{lme4}~\citep{lme4}. [[Confirm that I actually use the separate 
-  regressions and not just the full one. ]]
+  package \emph{lme4}~\citep{lme4}.
 
@@
 
+  % Regression of all families at once with RE's for network
     Taking all families together, the probability of species in the same family sharing interaction partners decreased wiht increasing phylogenetic distance in both plant-pollinator and plant-herbivore networks and the strength of this relationship did not differ significantly between network types ($\beta_{distance}$=-4.75, $p$=0.012; $\beta_{distance:PH}$=-1.73, $p$=0.681).
@@
 
+    % Regressions for each family separately.
     For the families
@@
   \caption{\small Change in log odds (per million years of phylogenetic distance) of a pair of plants in the same family sharing a herbivore.}
+  % These are from the regressions within each family. P-vals need to be replaced, to come from randomizations. Coefficients should be fine.
   \label{family_slopes_ph}
@@
   \small Change in log odds (per million years of phylogenetic distance) of a pair of plants in the same family sharing a pollinator.}
+  % These are from the regressions within each family. P-vals need to be replaced, to come from randomizations. Coefficients should be fine.
   \small

### 2019-02-20 code/create_figures/pval_test_observed.py
made a figure for the SI to show distributions of random randoms

@@ -1,25 +1,146 @@
-def pval_getter(netdir):
-  Jaccard_pvals=[]
-  Sorenson_pvals=[]
-  for file in netdir:
-    f=open(file,'r')
-    for line in f: 
+import os
+import sys
+import numpy as np
+
+from PyGrace.grace import Grace
+from PyGrace.colors import RandomColorScheme, MarkovChainColorScheme, ColorBrewerScheme
+from PyGrace.dataset import SYMBOLS
+from PyGrace.Extensions.panel import Panel,MultiPanelGrace, TreePanel
+from PyGrace.drawing_objects import DrawText, DrawLine
+
+from PyGrace.Extensions.distribution import CDFGraph, PDFGraph
+from PyGrace.Extensions.latex_string import LatexString, CONVERT
 
 
+def pval_reader(pfile):
+	pvals={}
+	f=open(pfile,'r')
+	for line in f:
+		if line.split()[0]!='"V1"':
+			network=line.split()[0]
+			ps=line.split()[1:]
+			pvals[network]=[float(x) for x in ps]
+	f.close()
+	return pvals
+
+def pval_binner(ps):
+	bins={}
+	used=[]
+	for i in range(0,21):
+		binmin=round(i*0.05,2)
+		binmax=round(binmin+0.05,2)
+		binmed=round(np.mean([binmin,binmax]),3)
+		bins[binmed]=[]
+		for x in sorted(ps):
+			if round(x,3)>=binmin and round(x,3)<binmax:
+				bins[binmed].append(x)
+				used.append(x)
+		lesser=[x for x in ps if x<binmax]
+		greater=[x for x in lesser if x>=binmin]
+		bins[binmed]=greater
+	lens=[]
+	total=0
+	for x in sorted(bins):
+		y=len(bins[x])
+		lens.append((x-0.025,float(y)/999))
+		lens.append((x+0.025,float(y)/999))
+		total=total+y
+
+	if total!=len(ps):
+		print [x for x in ps if x not in used], 'unused'
+		print total, len(ps), 'error in binning'
+		sys.exit()
+	return lens
+
+def format_graph(graph):
+  graph.world.xmin=0
+  graph.world.xmax=1
+  graph.xaxis.tick.configure(major=.2,minor_ticks=0,major_size=.5,major_linewidth=.5)
+  graph.xaxis.ticklabel.char_size=0.5
[…]

### 2019-02-20 manuscript/supporting_info.tex

--- 2019-02-14 manuscript/phylogenetic_signal_manuscript.tex
@@
 
-\title{Conservation of interaction partners between related plants varies widely across communities and between plant families.}
+\title{Conservation of interaction partners between related plants varies widely across communities and between plant families - Supporting Information}
 
@@
 
-\section*{Word Counts}
-
-Main text: 4522
-
-\begin{itemize}
-  \item Introduction: 805 
-  \item Materials and Methods: 1831 
-  \item Results: 665
-  \item Discussion: 1139 
-  \item Acknowledgements: 83
-\end{itemize}
-
-Figures: 3
-
-Tables: 2
-
 Supporting information: 1 file containing 4 sections.
 
-\vspace{0.4 in}
-
-\section*{Summary}
-
-  \begin{itemize}
-    \item Related plants are often hypothesised to interact with similar sets of 
-          pollinators and herbivores, but empirical support for this idea is mixed.
-          Here we argue that this may be because some plant families vary in their 
-          tendency to share interaction partners.
-
-    \item We introduce a novel approach with which to quantify
-          overlap of interaction
-          partners for each pair of plants in 59 pollination and 11 herbivory
-          networks.  We then tested for relationships between phylogenetic 
-          distance and overlap within each network, and whether these 
-          relationships varied with the composition of the plant community.
-          Finally, we tested for different relationships within well-represented
-          plant families.
-
-    \item Across all networks, more closely-related plants tended to have 
-          greater overlap, and this tendency was stronger in herbivory 
-          networks than pollination networks. These relationships were also significantly related 
-          to the composition of the network's plant component. Within plant families, 
-          relationships varied greatly in both network types.
-
-    \item The variety of relationships between phylogenetic distance and
-          interaction partners in different plant families likely
-          reflects a variety of ecological and evolutionary processes. To 
-          understand the distribution of interactions within a community, 
-          it is therefore important to consider factors affecting particular 
-          plant families.
-
-  \end{itemize}
-
-\section*{Keywords}
-
-defensive syndrome, ecological networks, herbivory, niche overlap, phylogenetic signal, pollination, pollination syndrome, specialisation
-
-\end{spacing}
-\begin{spacing}{1.5}
-
-\section*{Introduction}
-\linenumbers
-
-  Interactions with animals affect plants' life cycles in several critical
-  ways~\citep{Mayr2001,Sauve2015}. On one hand,
-  pollination and other mutualistic interactions contribute
-  to the reproductive success of many angiosperms~\citep{Ollerton2011}. 
-  On the other, herbivores consume plant tissues~\citep{McCall2006} which
-  costs plants energy and likely lowers their fitness.
-  In both cases, these interactions do not occur randomly but
-  are strongly influenced by plants' phenotypes. For example, plants that produce
-  abundant or high-quality nectar may receive more visits from
-  pollinators~\citep{Robertson1999} whereas plants that produce noxious secondary metabolites
-  may suffer fewer herbivores~\citep{Johnson2014}. A plant's traits are also 
-  likely to determine which specific pollinators and herbivores interact with that plant.
-  Plants with different defences (e.g., thorns vs. chemical defences) may deter 
-  different groups of herbivores~\citep{Ehrlich1964,Johnson2014}, and the concept
-  of pollination syndromes has often been used to group plants into phenotypic
-  classes believed to attract certain groups of pollinators~\citep{Waser1996,Fenster2004,Ollerton2009}.
-
-  [[update refs, add definition of plant roles]]
-  If attractive and/or defensive traits are heritable,
-  then we can reasonably expect that related plants will have similar 
-  patterns of interactions with animals~\citep{Schemske1999}.
-  Recent studies that have investigated this question at the level of whole
-  communities, however, have yielded mixed results~\citep{Rezende2007a,Gomez2010,Rohr2014a,Fontaine2015,Lind2015}.
-  In particular, significant phylogenetic signal in plants' interaction partners
-  ---the tendency for more closely-related plants to have more similar interactions---
-  tends to be rare in empirical networks (\citealp{Rezende2007a,Lind2015}; but see~\citealp{Elias2013,Fontaine2015}).
-  Further, plants' roles [[how defined?]] within networks tend to be less phylogenetically constrained than those of 
-  animals~\citep{Rezende2007a,Chamberlain2014,Rohr2014,Vamosi2014,Lind2015}. [[GVDR is skeptical of this - check partiteness, size, type of role and add more detail to support.]]
-
-  Several mechanisms that might weaken the conservation of interactions
-  have been identified in the literature. Pollination and herbivory may be affected
-  by a wide variety of traits, and not all of these are likely to be
-  phylogenetically conserved~\citep{Rezende2007,Kursar2009}. If, for example,
-  floral displays are strongly affected by environmental conditions~\citep{Canto2004}, 
-  then pollinators may not be predicted by plants' phylogenies.
-  Even if the traits affecting pollination and herbivory are
-  heritable, plants may experience conflicting selection pressures that
-  weaken the overall association between plant phylogeny and interaction
-  partners~\citep{Armbruster1997,Lankau2007,Siepielski2010,Wise2013}. 
-  For instance, floral traits that
-  are attractive to pollinators can also increase 
-  herbivory~\citep{Strauss2002,Adler2004,Theis2006}. 
-  Conversely, herbivory can reduce pollination by inducing chemical 
-  defences~\citep{Adler2006} or altering floral display or nectar 
-  availability~\citep{Strauss1997}. Observed patterns
-  of similarity in plants' interaction partners therefore represent
-  a mixture of environmental effects and various selection pressures as
-  well as plants' shared phylogenetic history.
-
-  A further complication is the possibility that the relationship between
-  plants' relatedness and the similarity of their interaction partners is
-  not constant across plant clades. Closely-related plants
-  in one clade might be under strong selection to favour dissimilar
-  sets of pollinators to avoid exchanging pollen with other
-  species~\citep{Levin1970,Bell2005,Mitchell2009}. Similar pressures 
-  could also affect related plants' defences against herbivores if 
-  congeners tend to grow in the same places such that herbivores 
-  could easily move between them.  Unrelated plants might also 
-  converge upon similar phenotypes, attracting a particularly 
-  efficient or abundant pollinator~\citep{Ollerton1996,Ollerton2009}. 
-  Likewise, herbivores may be able to depredate sets of unrelated 
-  plants if the plants have evolved similar defences~\citep{Pichersky2000}. 
-  In either case, dissimilarity of interactions among related species 
-  or similarity of interactions among unrelated species could result 
-  in weaker phylogenetic signal across an entire plant community. 
-  Moreover, all of the aforementioned hypotheses 
-  are non-exclusive; different processes likely affect different
-  clades, and these processes might be associated with different 
-  pressures imposed by pollination and herbivory.
-
-  Here we use a novel approach to investigate how overlap in 
-  interaction partners between pairs of plants (henceforth ``niche 
-  overlap'') varies over phylogenetic distance. Whereas previous 
-  studies have focused on the presence or absence of phylogenetic
-  signal across entire networks, we are able to investigate the
-  relationship between niche overlap and phylogenetic distance in
-  within networks as well as different plant families. Specifically,
-  we test whether niche overlap decreases over increasing phylogenetic
-  distance in a large dataset of pollination and herbivory networks, 
-  whether the plant family composition of a community affects the
-  relationship between niche overlap and phylogenetic distance in that 
-  community, and whether the relationship between niche overlap and 
-  phylogenetic distance differs across plant families.
-
-\section*{Materials and Methods}
-
-\subsection*{Network data}
-
-  We studied tested for phylogenetic signal in niche overlap within a 
-  set of 59 pollination and 11 herbivory networks. These networks span 
-  a range of biomes (desert to scrub forest to grassland) and 
-  countries (Sweden to Australia). The herbivory networks included a 
-  variety of types of herbivores but were dominated by insects 
-  consuming leaves. To ensure that we were analysing interactions 
-  influenced by similar sets of traits across networks, we restricted 
-  our herbivory networks to insects consuming leaves and excluded 
-  sap-sucking, leaf-mining, and galling insects as well as seed 
-  predators and xylophagous insects; all of these interactions involve 
-  different plant tissues and means of feeding than leaf consumption 
-  and so may be influenced by different plant and insect traits. 
-  Specifically, we removed any non-leaf consuming insects and any 
-  plants which had no interaction partners after removing other types  
-  of herbivores. The adjusted networks range in size between 19 and 
-  997 total species (mean=162, median=97) with  between 8 and 132 
-  plant species (mean=39.1, median=29.5). See \emph{Table S1, 
-  Supporting Information} [[NOT DONE!]]for details on the original sources of all 
-  networks.
-
-\subsection*{Phylogenetic data}
-
-  In order to fit the plant species in all networks to a common phylogeny, 
-  we first compared all species and genus names with the 
-  National Center for Biotechnology Information
-  and Taxonomic Name Resolution Service databases to ensure
-  correctness. This was done using the function `get\_tsn' in the R~\citep{R}
-  package taxize~\citep{taxize1,taxize2}. Species which could not 
-  be assigned to an accepted taxonomic name (e.g., `Unknown Forb') were 
-  discarded, as were those with non-unique common names and no binomial 
-  name given (e.g., `Ragwort) or binomial names that could not be definitively 
-  linked to  higher taxa (e.g., \emph{`Salpiglossus sp.'}). We were left with 
-  2341 unique species in 1027 genera and 195 families. On average, 11.43\% of 
-  plants were removed from each network (median 4.60\%, range 0-55.10\%).
-
-  We then estimated phylogenetic distances between species. To accomplish 
-  this, we constructed a phylogenetic tree for our dataset based on a dated
-  `mega-tree' of angiosperms~\citep{Zanne2014}. Some species were not included
-  in the angiosperm mega-tree (largely ferns and tree ferns). For angiosperms,
-  a sister taxon was identified using~\citet{APW} and the species added manually.
-  Ferns, tree ferns, and a single club moss were added to the base of the tree.
-  This means that closely-related non-angiosperm species appear to have very long 
-  phylogenetic distances between them. For this reason, we excluded comparisons 
-  between pairs of non-angiosperms from our analyses. As only two networks (both 
-  plant-herbivore networks) included more than one such species and non-angiosperms
-  were always a small minority of any network, we do not 
-  believe that omitting these comparisons has greatly affected our results.
-  To obtain trees for each network, we 
-  pruned the dated mega-tree to include only species in that network.
-
-\subsection*{Calculating niche overlap within communities}
-
-  We calculated niche overlap for each pair of species within a community 
-  using a Jaccard index to describe the number of shared interaction 
-  partners, augmented with the number of interaction partners which were 
-  not shared. The Jaccard index $J_{ij}$ describes the proportion of 
-  shared interaction partners for for species $i$ and $j$ and is defined as:
-
-  \begin{equation}
-    J_{ij} = \frac{M_{ij}}{P_i+P_j-M_{ij}} ,
-  \end{equation}
-
-  where $M_{ij}$ is the set of \emph{mutual} (shared) interaction partners of 
-  species $i$ and $j$ and $P_i$ and $P_j$ are the sizes of the sets of interaction 
-  \emph{partners} for species $i$ and $j$ respectively. We wished to give more 
-  weight to species sharing a large number of interaction partners as well as 
-  those sharing a large proportion (i.e., to emphasize pairs of generalists 
-  sharing most of their interaction partners over specialists sharing a single 
-  interaction partner). We therefore recorded, for each species, the number of 
-  shared interaction partners $M_{ij}$ and the number of interaction partners 
-  for each species pair that were not shared 
-  ($U_{ij}$ = $P_{i}$+$P_{j}$-2$M_{ij}$). Instead of a single index $J_{ij}$ 
-  we therefore keep track of the information needed to compute
-  niche between species $i$ and $j$ as a tuple: ($M_{ij}$, $U_{ij}$).
-
-  % To fully describe the extent to which two plants' niches overlap,
-  % we defined the overlap between two plants' sets of interaction partners
-  % by recording the frequencies with which pairs of animals (where each animal 
-  % interacted with at least one plant) fall into three unique patterns
-  % (Fig.~\ref{overlap_patterns}). In the first pattern, both plants interact 
-  % with both animals, indicating total overlap for that quartet. In the second pattern, one plant
-  % interacts with both animal partners while the other
-  % interacts with only one animal, indicating partial overlap. In the third pattern,
-  % each animal interacts with only one plant, indicating no overlap. 
-  % Taken together, the frequencies of these three patterns of
-  % overlap can be used to describe the degree to which two plants have
-  % similar interaction partners. %
-
-  % Using the three patterns defined above provides more detail than other measures of overlap,
-  % such as the proportion of one species' partners that are shared with
-  % another as given by Jaccard similarity. In particular, comparing the probability of observing each pattern
-  % rather than one of the other two provides a measure of indirect
-  % interactions between plants by considering pairs of animal partners rather
-  % than each animal separately. For example, a pair of plants which share 
-  % two interaction partners are more likely to influence each other via these partners
-  % than two plants which do not share interaction partners. Moreover, our measure
-  % of overlap has greater statistical power than Jaccard dissimilarity because
-  % it includes information on the \emph{number} of shared interaction partners as
-  % well as the proportion. For instance, a pair of plants which together interact
-  % with 100 animals provides more information about shared overlap than a pair of
-  % plants which together interact with only one animal whereas the Jaccard similarity
-  % of both would simply be one.
-
-  % [[It appears we switched to Jaccard and Sorenson dissimilarities - number of shared partners and number of shared partners*2/notshared.]]
-
-\subsection*{Statistical analysis}
-
-  We modelled the relationship between niche overlap and phylogenetic distance
-  using a logistic regression. We used both the numbers of shared ($M_{ij}$)and 
-  non-shared ($U_{ij}$) partners as dependent variables and centred, scaled phylogenetic 
-  distance as the independent variable. This approach is conceptually similar to 
-  modelling successes and failures in a binomial-distributed process. 
-  Accordingly, we assumed a binomial distribution for residuals. Regressions of
-  niche overlap and phylogenetic distance within each network were fit using the
-  R~\citep{R} base function ``glm''. These separate regressions avoid the potential
-  for confounding the effects of different relationships in different networks. As
-  we also wished to evaluate the overall trend across networks, we fit an additional
-  regression of niche overlap and phylogenetic distance across all network types.
-  As well as the fixed effect of phylogenetic distance, this regression included 
-  fixed effects of network type (pollination or herbivory) and the interaction 
-  between phylogenetic network type and random intercepts and slopes per network.
-  This expanded regression was fit using the R~\citep{R} function ``glmer'' from
-  package \emph{lme4}~\citep{lme4}. [[Confirm that I actually use the separate 
-  regressions and not just the full one. ]]
-
-  Note that pairs of plants are not always independent: the same plant will
-  appear in many pairs. This violates the assumption of independence used when 
-  calculating the significance of logistic regressions within the R~\citep{R} 
-  base package or the package \emph{lme4}~\citep{lme4}. To calculate significance 
-  of the regression coefficients we observed, it was therefore necessary to compare the 
-  observed relationships to those in a suite of appropriately permuted networks. To create 
-  these networks, we shuffled interactions among species while preserving row 
-  and column totals. That is, each species retained the same number of 
-  interaction partners as in the observed network but the exact set of 
-  partners (and therefore niche overlaps with all other species) varied across 
-  permuted networks. We preserved the observed phylogenetic relationships 
-  between species in all cases. For each observed network, we created 999 such 
-  permuted networks and calculated the relationship between niche overlap and 
-  phylogenetic distance. This gave us a null distribution for each observed 
-  network with which to determine the significance of the observed 
-  relationship.
-
-  This permutation approach also allows us to estimate type I and type II 
-  error for our analysis. To do this, we created 500 permutations of each 
-  permuted network and, again keeping the observed phylogenetic distances 
-  between plant species, repeated our analyses. We can then determine the 
-  number of permuted networks which appear to have significant 
-  overlap-phylogenetic distance relationships relative to the permutations 
-  of these permuted networks (type I error). [[How does this get at type II error?]]
-
-  % To determine how overlap of interaction partners
-  % breaks down over phylogenetic distance,
-  % we modelled the probabilities of observing each pattern
-  % of overlap relative to the other two patterns.
-  % We expected that the frequency of the high- and moderate-overlap 
-  % patterns would decrease with increasing phylogenetic distance
-  % between two plants while the frequency of the low-overlap pattern would
-  % increase. As we expect pollination and herbivory networks could 
-  % show different patterns of overlap, we included effects of network 
-  % type and the interaction between network type and distance. Lastly, to
-  % account for the possibility that different communities show different
-  % characteristic relationships, we also included random effects of network ID on the slope 
-  % and intercept, giving a mixed-effects logistic regression of the form
-  % \begin{equation}
-  % logit(\omega_{pnij}) \propto \delta_{ij} + \rho_{n} + \delta_{ij}\rho_{n} + N_{n} + \delta_{ij}N_{n} ,
-  % \label{networklevel}
-  % \end{equation}
-
-  % \noindent where $\omega_{pnij}$ is the probability of overlap pattern $p$ occurring between
-  % species $i$ and $j$ in network $n$, $\delta_{ij}$ is the phylogenetic distance between 
-  % plants $i$ and $j$, $\rho_{n}$ is the network type (one in pollination networks,
-  % zero in herbivory networks), and $N_n$ and $\delta_{ij}N_{n}$ are random slope and intercepts 
-  % for network $n$. All models were fit using R function glmer from package lme4~\citep{lme4}.
-  % Sample size for these models was the sum (over all pairs of plants) of the number of pairs 
-  % of animals where each plant and each animal has at least one interaction partner. Over all 
-  % networks, there were 43,288,090 such sets of plants and animals, with a median of 72 (mean 
-  % 671 +/- 2247) pairs of animals per pair of plants and median 58,528 (mean 636,590)
-  % plant-animal sets per network.
-
-\subsection*{Linking network-level trends and community composition}
-
-  Next, we examined the connection between our network-level observations
-  and the plant families present in each community.
-  Specifically, we tested the hypothesis that
-  varying relationships between phylogenetic distance and
-  pairwise niche overlap are due to the different distributions 
-  of families across networks. To do this, we performed a non-parametric
-  permutational multi-variate analysis of variance
-  (PERMANOVA;~\citealp{Anderson2001}) using the change in log
-  odds of two plants sharing an interaction partner to 
-  predict the Bray-Curtis dissimilarity of networks
-  based on the composition of their plant component
-  (defined as the proportions of the plant community
-  made up by each plant family present in the entire dataset).
-  We used Bray-Curtis dissimilarity because, for a given
-  pair of networks, only those plant families that appear
-  in at least one network are considered~\citep{Anderson2001,Cirtwill2015}; 
-  that is, the absence of rare plant families will not make 
-  two networks appear more similar than they actually are.
-
-  Note that a PERMANOVA does not assume that the data are 
-  normally distributed, but rather compares the pseudo-$F$ 
-  statistic calculated from the observed data to a null 
-  distribution obtained by permuting the raw data. As 
-  pollination and herbivory networks might have different
-  community composition, we stratified these permutations
-  by network type. That is, the change in log odds for a pollination
-  network could only be exchanged for that of another pollination
-  network. Stratifying the permutations in this way ensures that 
-  the null distribution used to calculate the $P$-value is not 
-  biased by including combinations of changes in log odds and 
-  community composition that would not occur because of inherent 
-  differences in the two network types (e.g., \emph{Pinaceae} 
-  only appeared in herbivory networks and should not be assigned 
-  to pollination networks). We used 9999 such stratified permutations 
-  to obtain the null distribution and obtain a $P$-value.
-
-  The PERMANOVA tests whether there is an association between
-  community composition and network-level patterns but does not
-  give any information on \emph{which} plant families have the
-  greatest effects. To address this, we supplemented the 
-  PERMANOVA with three constrained correspondence analyses (CCAs)
-  which placed plant families along an axis representing the
-  change in log odds of sharing an interaction partner.
-  A correspondence 
-  analysis (CA) is similar to other multivariate
-  analyses such as principal components analysis in that it
-  reduces multivariate data to a set of orthogonal axes. A
-  subset of axes that explain the majority of variation in 
-  the data can then be interpreted to elucidate trends that
-  were difficult to interpret in the full multivariate space.
-  A constrained correspondence analysis (CCA) creates an extra
-  axis based on some constraint - in this case, the change in
-  log odds of sharing an interaction partner.
-
-\subsection*{Calculating niche overlap within families}
-
-  Finally, we wished to compare the breakdown of overlap of interactions in
-  different plant families. To do this, we used the same definitions of overlap
-  and phylogenetic distance as in the within-network analysis but restricted
-  our regressions to pairs of plants from the same family and the same network.
-  Unlike in our previous analysis, we analysed data from pollination and
-  herbivory networks separately as most well-represented plant families appeared
-  in only one network type. For those families which appeared in both network types, 
-  we ran separate analyses on each subset of data.
-
-  For each plant family, within each network type, we then fit one of two similar 
-  sets of models. First, when family $f$ was found in several networks of network
-  type $t$, we fit mixed-effects logistic regressions for the probability of sharing an interaction partner $\omega_{ntfij}$ of the form
-  \begin{equation}
-    logit(\omega_{ntfij}) \propto \delta_{ij} + N_{n} ,
-    \label{full}
-  \end{equation}
-
-  \noindent where $\omega_{tnfij}$ is the probability of sharing a partner 
-  in network $n$ of network type $t$ for plants $i$ and $j$ in plant family $f$,
-  $\delta_{ij}$ is the phylogenetic distance between plants $i$ and $j$, and
-  $N_{n}$ is a random effect of network $n$.
-  Second, if a plant family was represented in only one network 
-  and therefore necessarily in only one network type, we omitted the 
-  network-level random effect giving mixed-effects logistic regressions of the form
- \begin{equation}
-    logit(\omega_{pntfij}) \propto \delta_{ij} .
-    \label{minimal}
-  \end{equation}
-
-  \noindent We fit Eq.~\ref{full} using the function `glmer' from the
-  R package lme4~\citep{lme4} and fit Eq.~\ref{minimal} in R using the
-  function `glm' from the same package.
-
-\section*{Results}
-
-  \subsection*{Within-network conservation of niche overlap}
-
-    Across all networks, overlap of interaction partners decreased with increasing phylogenetic distance and the decrease in overlap of pollinators was steeper than that in herbivores ($\beta_{distance}$=-6.82, $p$\textless0.001 and $\beta_{distance:PP}$=-18.5, $p$\textless0.001, respectively).
-That is, a pair of plants in the same genus was more likely to share interaction partners than a pair of plants in the same family in both types of networks, but a pair of congeners would be less likely to share pollinators than to share herbivores.
-Regardless of phylogenetic distance, a pair of plants were also less likely to share pollinators than herbivores ($\beta_{PP}$=-1.44, $p$\textless0.001).
-This may be due to the greater proportion of
-    specialist pollinators than specialist herbivores. In our dataset, an
-    average of 48\% (+/- 14) of pollinators in a given web were extreme 
-    specialists (i.e., visited only one plant species) compared to 29\% 
-    (+/- 29) of herbivores ($z$=5.62, df=68, $P$\textless0.001 
-    for a binomial regression of specialists and generalists over network
-    type). % Are the above betas un-scaled?
-
-    Despite these general trends, there was substantial variation between 
-    pollination networks, with overlap of interaction partners decreasing 
-    with increasing phylogenetic distance in some networks and increasing in 
-    others (Fig.~\ref{within_network_regression}).
-Overlap of interaction partners decreased significantly with increasing phylogenetic distance in 7/11 plant-herbivore networks and 33/59 plant-pollinator networks.
-In the remaining four plant-herbivore networks and 25 of the 26 remaining plant-pollinator networks, overlap of interaction partners was not related to phylogenetic distance.
-Overlap of interaction partners increased with increasing phylogenetic distance in only a single plant-pollinator network.% (M_PL_026).
-
-    [[Reviewers demanded this - it seems very boring]]
-    Comparing the results in the observed networks to those obtained after permuting phylogenetic distances across pairs of plants, the observed slope of the relationship between phylogenetic distance and interaction partner overlap was always more extreme (i.e., always lesser or always greater) than that obtained in the permuted networks (Fig.~\ref{obs_vs_random}).
-Observed networks with a negative relationship between phylogenetic distance and overlap always had a more negative slope than that obtained from the permuted networks, while the 10 networks with positive relationships between phylogenetic distance and overlap always had more positive relationships than the permuted networks.
-
-    Comparing the permuted networks to permutations of the permuted networks, the slope obtained from the initial permuted network was quite variable with respect to the slopes obtained from 500 permutationss of the permuted network.
-Averaged over the 1000 permutations of each observed network, the slope of the permuted network was more extreme than 48.1-51.3\% of the permutations of the permuted network.
-This confirms that shuffling phylogenetic distances between plant pairs destroys the relationship between distance and interaction partner overlap, and that further shuffling distances does not have a predictable effect.
-
-  \subsection*{Linking network-level trends and community composition}
-
-    We were interested in whether the slope of the relationship between phylogenetic distance varied with community composition.
-In a PERMANOVA of slope against community composition, stratified by network type, we did not find a significant relationship between slope and community composition ($F_{1,68}$=1.06, $p$=0.493).
-Of the 200 families in our dataset, only 29 were represented by more than 20 species.
-Lumping all other families into an "other" category and repeating the PERMANOVA, we still did not find a significant relationship between slope and community composition ($F_{1,68}$=1.12, $p$=0.409).
-    % Also performed a CCA to see which fams had most positive/negative associations, but with non-sig results I don't think it's interesting.
-
-  \subsection*{Within-family conservation of niche overlap} [[Still of interest given negative result above?]]
-
-    Taking all families together, the probability of species in the same family sharing interaction partners decreased wiht increasing phylogenetic distance in both plant-pollinator and plant-herbivore networks and the strength of this relationship did not differ significantly between network types ($\beta_{distance}$=-4.75, $p$=0.012; $\beta_{distance:PH}$=-1.73, $p$=0.681).
-Plants in plant-herbivore networks had a higher probability of sharing interaction partners with a member of the same family ($\beta_{PH}$=0.78, $p$=0.007).
-
-    The relationship between within-family niche overlap and phylogenetic distance
-    varied widely in both pollination and herbivory networks. 
-    % Gotta separate plant-herb and plant-poll networks.
-
-    For the families
-    that were well represented in pollination networks, overlap decreased
-    with increasing phylogenetic distance in 18 (Table~\ref{family_slopes_pp}).
-    There was no significant relationship between overlap and phylogenetic distance in
-    a further 15 plant families. Finally, the overlap between pairs of \emph{Polygonaceae}
-    increased with increasing phylogenetic distance. 
-    Of the seven plant families that were sufficiently well represented in herbivory 
-    networks, overlap decreased with increasing phylogenetic distance in four 
-    (Table~\ref{family_slopes_ph}; Fig.~\ref{within_family_regression}). Two
-    families did not show significant relationships between phylogenetic distance and overlap,
-    and in one family, \emph{Fabaceae}, overlap of interaction partners increased with 
-    increasing phylogenetic distance.
-
-    Models for two families did not converge.
-In both the \emph{Lauraceae}, (represented by four species in one pollination network) and the \emph{Sapindaceae} in plant-herbivore networks (represented by five species in one network), one pair of species shared a single interaction partner while all other pairs did not share any interaction partners.
-The model for \emph{Sapindaceae} in plant-pollinator networks did converge.
-
-\section*{Discussion} [[not updated post new results]]
-
-  We found broad support for the hypothesis that more
-  closely-related pairs of plants have a higher degree
-  of niche overlap. Using a novel method which considers
-  all pairs of plants together, 
-  the probability of two plants sharing the same animal 
-  interaction partners decreased with increasing 
-  phylogenetic distance. Considering networks separately,
-  $\approx$78\%  of the pollination and all of the 
-  herbivory networks exhibited the expected trend of decreasing 
-  overlap with increasing distance.
-
-  Within families, however, there was much greater variability. 
-  More than half of the plant families in each network type
-  behaved as we hypothesised, with more 
-  closely-related plants having greater niche overlap than 
-  distantly related plants. This relationship between overlap and 
-  phylogenetic distance is consistent with the idea that traits affecting 
-  interactions are heritable~\citep{Schemske1999} and changing gradually
-  such that closely related plants resemble their common ancestor--- and
-  each other ---more than they do distantly related plants. In some families, 
-  such as \emph{Asteraceae} in pollination networks, the positive slope of 
-  this relationship was very shallow while in others, such as 
-  \emph{Melastomataceae} in herbivory networks, the positive slope was 
-  extremely steep. This could indicate different rates of phenotypic drift 
-  or evolution in different families.
-
-  In contrast, \emph{Polygonaceae} in pollination networks and 
-  \emph{Fabaceae} in herbivory networks showed the opposite 
-  pattern. In these families, closely-related plants had 
-  \emph{lower} overlap than more distantly-related pairs of plants. 
-  There are several possible reasons a plant family might
-  display this pattern. First, part of the family may have recently 
-  undergone a period of rapid diversification with closely-related species 
-  developing novel phenotypes that attract different animal 
-  interaction partners~\citep{Linder2008,Breitkopf2015}. It is also possible that the
-  animals have undergone an adaptive radiation to 
-  specialise on their most profitable partner~\citep{Janz2006}. Second, this pattern 
-  could be the result of ecological or environmental filtering~\citep{Mayfield2009,Ackerly2010}. 
-  Closely-related species which have high degrees of overlap in their interaction 
-  partners might compete too severely to coexist. This is especially likely
-  for plants sharing pollinators, where the loss of pollen to related species 
-  might severely limit reproductive success~\citep{Levin1970,Bell2005,Mitchell2009}.
-  Indeed, animal pollination and seed dispersal have been shown to act
-  as filters for several plant clades~\citep{Mayfield2009}.
-  Distantly-related plants with similar interaction partners,
-  on the other hand, may differ in some other aspect of their niches
-  and so be able to coexist. Plants sharing herbivores are unlikely to
-  compete for these interaction partners, but the presence of both
-  plants in a community could support higher herbivore populations
-  than could one species alone~\citep{Russell2007}. If the plants 
-  compete for some other resource, the combined impact of herbivory
-  and competition could eliminate the rarer plant species. Distantly-related
-  plants sharing herbivores, conversely, would be less likely to compete
-  for vital resources and more likely to persist.
-
-  The remaining families did not show significant relationships 
-  in either direction. That is, the niche overlap between two 
-  plants did not vary linearly over phylogenetic distance. Once again, there 
-  are several possible drivers for this trend (or lack thereof). These plants might 
-  be highly specialised on different interaction partners and therefore
-  have low overlap at all levels of relatedness. In other plant families
-  with more moderate levels of specialisation, it is possible 
-  that pollination and/or herbivory do not exert large
-  selection pressures on the plants. If traits affecting pollination
-  or herbivory are not heritable in these groups~\citep{Kursar2009}
-  and that their phenotypes are constrained by other factors (e.g., 
-  drought tolerance), then we should not expect a relationship 
-  between phylogenetic distance and overlap of interaction partners.
-  Alternatively, pollination and/or herbivory might exert large 
-  pressures that maintain the clade within a pollination or 
-  defensive syndrome. These syndromes are commonly believed to
-  predict the pollinators or herbivores with which a plant will 
-  interact~\citep{Waser1996,Fenster2004,Ollerton2009,Johnson2014}.
-  As some recent studies have suggested that pollination syndromes
-  do not accurately predict plants' visitors in all plant 
-  families~\citep{Ollerton2009},
-  it may be of interest for future researchers to test whether 
-  syndromes are better predictors in families with weak 
-  relationships between overlap and phylogenetic distance.
-  Lastly, it is possible that the absence of a linear relationship 
-  between niche overlap and phylogenetic distance is because the data
-  actually exhibit a strongly non-linear one. This could result, for 
-  example, from an early burst of diversification followed by a period
-  of stasis~\citep{Davis2014}.
-
-  For those families which were well-represented in both pollination
-  and herbivory networks, we can also contrast the 
-  trends in the two network types. In all five such cases, there was
-  a significant relationship between overlap and phylogenetic 
-  distance in only one network type (counting the singular 
-  relationships in \emph{Rubiaceae} in pollination networks as 
-  non-significant). This may indicate that one type of interaction
-  places greater constraints upon these families than the other. Plants
-  may not be able to respond to selection on both types of interaction
-  simultaneously because traits affecting pollination can also affect herbivory, and vice
-  versa~\citep{Strauss1997,Strauss2002,Adler2004,Adler2006,Theis2006}.
-  Associations with pollinators and herbivores may also be constrained by the
-  larger structure of the community. In one recent study, plants which are 
-  visited by many pollinators are also consumed by many herbivores~\citep{Sauve2015}.
-  This may be because pairing antagonistic and mutualistic interactions
-  balances the indirect effects of these interactions, leading to a
-  more stable community~\citep{Sauve2014}. As more networks describing 
-  pollination and herbivory in the same community become available, it 
-  will be interesting to test this hypothesis more thoroughly.
-
-  Altogether, our study has revealed a wide variety of relationships 
-  between overlap of interaction partners and phylogenetic distance 
-  between plants in the same family. Regardless of the precise mechanisms
-  behind these relationships, it is clear
-  that the differences between families can affect the relationship
-  between overlap and phylogenetic distance at the network level. 
-  Interestingly, in our analyses the plant families associated with
-  the steepest relationships between niche overlap and phylogenetic
-  distance at the network level did not show particularly steep
-  relationships within themselves. This result suggests
-  that it is not just which plant families are present but the additional 
-  relationships between the families that affects conservation of
-  interactions at the network level and is consistent with previous
-  work showing that the shape of phylogenetic tress, as well as the
-  phylogenetic distances between species, can affect the strength
-  of phylogenetic signal~\citep{Chamberlain2014a}. Our results 
-  emphasise the importance of considering conservation of interactions at multiple scales.
-  We hope that these results will help to guide future work investigating
-  the genetic and environmental drivers underpinning these relationships.
-
-\section*{Acknowledgements}
-
-  We would like to thank the authors of the published networks used in this study. 
-  We are grateful for the use of the Edward Percival field station in Kaikoura, 
-  New Zealand in May, 2014. This research was supported by an NSERC PGS-D 
-  graduate scholarship (to ARC), a Marsden Fund Fast-Start grant (UOC-1101) and a 
-  Rutherford Discovery Fellowship, both administered by the Royal Society of New 
-  Zealand (to DBS), a BlueFern HPC PhD scholarship (to NJB), and by
-  the Allan Wilson Centre (to GVDR).
-
-\section*{Author Contribution}
-
-  ARC, DBS, GVDR, and NJB designed the research. ARC, JAT, and CJW collected published data. [[Add MSC helpers!]]
-  ARC and GVDR performed the analyses. All authors contributed to the manuscript.
+\section*{Supporting information 1: Sources for networks}
 
@@
 
-\section*{Figures}
-
-  % \begin{figure}[!h]
-  %   \begin{center}
-  %     \centerline{\includegraphics*[width=.75\textwidth]{Figures/Sketches/methods_breakdown.eps}}
-  %   \end{center}
-  %    \caption{Visual depiction of our decomposition of pairwise niche overlap of plants' interaction
-  %    partners. \textbf{(a)} First, consider the representation of any pollination or herbivory network
-  %    as an adjacency matrix. Here, filled cells indicate an interaction between a particular plant 
-  %    (letters on rows) and an animal (numbers on columns). \textbf{(b)} For a given pair of plants (e.g., plants 
-  %    A and B), we then considered the set of animals that interact with at least one of the focal
-  %    plants. Taking each pair of animals in this set in turn, we assigned the resulting quartet (the
-  %    two focal plants plus two animals) to one of three patterns of overlap.
-  %    In the \textbf{total overlap} pattern, both plants interact with both animals. 
-  %    In the \textbf{partial overlap} pattern, one plant interacts with both animals and the other plant
-  %    interacts with only one.
-  %    Finally, in the \textbf{no overlap} pattern each animal interacts with only one plant; note that 
-  %    this includes cases where both animals interact with the same plant (e.g., animals 1 and 5 and plant A)
-  %    as well as cases where each animal interacts with a different plant (e.g., animals 1 with plant A and animal
-  %    4 with plant B). \textbf{(c-e)} The number of times each pattern occurred was used to summarise the pairwise niche 
-  %    overlap between the two plants and then related to their phylogenetic distance.}
-  %   \label{overlap_patterns}
-  % \end{figure}
-
-  \begin{figure}[!h]
-    \begin{center}
-      \centerline{\includegraphics*[width=.75\textwidth]{Figures/dataplots/scaled_regression_lines_full_color.eps}}
-    \end{center}
-     \caption{Results of a mixed-effects logistic regression of pairwise niche overlap
-     against phylogenetic distance for plants in 11
-     herbivory networks (top; green) and 59 pollination
-     networks (bottom; purple). In both network types, the probability of a pair of plants
-     sharing an interaction partner increased with increasing phylogenetic distance (thick,
-     dark lines).
-There was substantial variation among networks (thin, pale lines) of both types.
-The slope of the regression for each network was significantly more extreme than that obtained from 999 permutatations of that network (slopes obtained from the permuted networks ranged between -1.34$\times10^{-12}$ and 9.19$\times10*{-13}$).}
-    \label{within_network_regression} 
-  \end{figure}
-
-  \begin{figure}[!h]
-    \begin{center}
-      \centerline{\includegraphics*[width=.75\textwidth]{Figures/dataplots/observed_vs_random.eps}}
-    \end{center}
-     \caption{The slopes of the mixed-effect logistic regression of pairwise niche overlap against phylogenetic distance was signficantly different from 0 for each network.
-Here we show, for plant-herbivore (PH) and plant-pollinator (PP) networks, the observed slopes (depicted by green squares or purple diamonds, respectively).
-The maximum and minimum slopes obtained from 999 permutations of each network are depicted by thin, black lines.
-For both network types, the slopes obtained from permuted networks were always very close to 0.}
-    \label{obs_vs_random} 
-  \end{figure}
-
-  \begin{figure}[!h]
-    \begin{center}
-      \centerline{\includegraphics*[height=.62\textheight]{Figures/dataplots/Family/allfams_full.eps}}
-    \end{center}
-     \caption{Change in log odds of observing pairwise niche overlap per million
-     years of divergence time between a pair of plants
-     in the 14 plant families where there was a significant
-     relationship between log odds of sharing interaction
-     partners and phylogenetic distance.
-     Families in pollination networks are indicated
-     by dark purple diamonds while families in herbivory
-     networks are indicated by pale green circles.
-     Note that changes in log odds are analogous to the 
-     slopes of the regression lines from Eq. 2-3
-     in logit-transformed space and represent
-     the change in the probability of observing shared 
-     interaction partners per million years of divergence time. We also
-     show the slope of the relationship between the
-     log-odds of observing each overlap pattern and 
-     phylogenetic distance across all plant families
-     in herbivory (pale, green horizontal line) and
-     pollination (dark, purple horizontal line) networks.
-     % See~\emph{Figure S1; Supporting Information} for more details.
-     The phylogenetic tree below the plots indicates the
-     relatedness between plant families. Error bars represent 95\% confidence
-     intervals.}
-    \label{within_family_regression}
-  \end{figure}
-
 \end{document}

### 2019-02-20 manuscript/supporting_info.tex
need to make this a multi-page figure

@@
 
-Supporting information: 1 file containing 4 sections.
+\clearpage
 
@@
 
+  \begin{table}[!h]
+    \caption{Original sources for each network used in our analyses.}
+    \label{sources}
+    \begin{tabular}{|l l l |}
+    \hline
+    Network & Network type & Original source \\
+    \hline
+    M\_PL\_001  & Pollination & \citep{Arroyo1982}  \\
+    M\_PL\_002  & Pollination & \citep{Arroyo1982}  \\
+    M\_PL\_003  & Pollination & \citep{Arroyo1982}  \\
+    M\_PL\_004  & Pollination & \citep{Barrett1987} \\
+    M\_PL\_005  & Pollination & \citep{Clements1923}  \\
+    M\_PL\_006  & Pollination & \citep{Dicks2002} \\
+    M\_PL\_007  & Pollination & \citep{Dicks2002} \\
+    M\_PL\_008  & Pollination & \citep{Dupont2003}  \\
+    M\_PL\_009  & Pollination & \citep{Elberling1999} \\
+    M\_PL\_010  & Pollination & Elberling, H. \& Olesen, J. M. Unpublished. \\
+    M\_PL\_011  & Pollination & \citep{Olesen2002a}  \\
+    M\_PL\_012  & Pollination & Olesen, J. M. Unpublished.  \\
+    M\_PL\_013  & Pollination & \citep{Ollerton2003}  \\
+    M\_PL\_014  & Pollination & \citep{Hocking1968} \\
+    M\_PL\_015  & Pollination & \citep{Petanidou1991} \\
+    M\_PL\_016  & Pollination & \citep{Herrera1988} \\
+    M\_PL\_017  & Pollination & \citep{Memmott1999} \\
+    M\_PL\_018  & Pollination & Olesen, J. M. Unpublished.  \\
+    M\_PL\_019  & Pollination & \citep{Inouye1988}  \\
+    M\_PL\_020  & Pollination & \citep{Kevan1970} \\
+    M\_PL\_021  & Pollination & \citep{Kato1999}  \\
+    M\_PL\_022  & Pollination & \citep{Medan2002} \\
+    M\_PL\_023  & Pollination & \citep{Medan2002} \\
+    M\_PL\_024  & Pollination & \citep{Mosquin1967} \\
+    M\_PL\_025  & Pollination & \citep{Motten1982}  \\
+    M\_PL\_026  & Pollination & \citep{McMullen1993}  \\
+    M\_PL\_027  & Pollination & \citep{Primack1983} \\
+    M\_PL\_028  & Pollination & \citep{Primack1983} \\
+    M\_PL\_029  & Pollination & \citep{Primack1983} \\
+    M\_PL\_030  & Pollination & \citep{Ramirez1992} \\
+    M\_PL\_031  & Pollination & \citep{Ramirez1989} \\
+    M\_PL\_032  & Pollination & \citep{Schemske1978}  \\
+    M\_PL\_033  & Pollination & \citep{Small1976} \\
+    M\_PL\_034  & Pollination & \citep{SmithRamirez2005}  \\
+    M\_PL\_035  & Pollination & \citep{Percival1974}  \\
+    M\_PL\_036  & Pollination & Olesen, J. M. Unpublished.  \\
+    \hline
+    \end{tabular}
+
+    \clearpage
+    \newpage
+
+    \begin{tabular}{|l l l |}
+    \hline
+    Network & Network type & Original source \\
+    \hline
+    M\_PL\_037  & Pollination & \citep{Montero2005} \\
+    M\_PL\_038  & Pollination & \citep{Montero2005} \\
+    M\_PL\_039  & Pollination & \citep{Stald2003} \\
+    M\_PL\_040  & Pollination & \citep{Ingversen2006} \\
+    M\_PL\_041  & Pollination & \citep{Ingversen2006} \\
+    M\_PL\_042  & Pollination & \citep{Philipp2006} \\
+    M\_PL\_043  & Pollination & \citep{Montero2005} \\
+    M\_PL\_044  & Pollination & \citep{Kato2000}  \\
+    M\_PL\_045  & Pollination & \citep{Lundgren2005}  \\
+    M\_PL\_046  & Pollination & \citep{Bundgaard2003} \\
+    M\_PL\_047  & Pollination & \citep{Dupont2009a}  \\
+    M\_PL\_048  & Pollination & \citep{Dupont2009a}  \\
+    M\_PL\_049  & Pollination & \citep{Beks2006}  \\
+    M\_PL\_050  & Pollination & \citep{Stald2003} \\
+    M\_PL\_051  & Pollination & \citep{Vazquez2002} \\
+    M\_PL\_052  & Pollination & \citep{Witt1998}  \\
+    M\_PL\_053  & Pollination & \citep{Yamazaki2003}  \\
+    M\_PL\_054  & Pollination & \citep{Kakutani1990}  \\
+    M\_PL\_055  & Pollination & \citep{Kato1996}  \\
+    M\_PL\_056  & Pollination & \citep{Kato1993}  \\
+    M\_PL\_057  & Pollination & \citep{Inoue1990} \\
+    M\_PL\_058  & Pollination & \citep{Bartomeus2008} \\
+    M\_PL\_059  & Pollination & \citep{Bezerra2009} \\
+    Basset  & Herbivory & \citep{Basset1999}  \\
+    Bluthgen  & Herbivory & \citep{Bluthgen2006}  \\
+    Bodner  & Herbivory & \citep{Bodner2010}  \\
+    Coley & Herbivory & \citep{Coley2006} \\
+    Ibanez  & Herbivory & \citep{Ibanez2013}  \\
+    Joern\_altuda  & Herbivory & \citep{Joern1979} \\
+    Joern\_marathon  & Herbivory & \citep{Joern1979} \\
+    Novotny & Herbivory & \citep{Novotny2012} \\
+    Peralta & Herbivory & \citep{Peralta2015} \\
+    Sheldon & Herbivory & \citep{Sheldon1978} \\
+    Ueckert & Herbivory & \citep{Ueckert1971} \\
+    \hline
+    \end{tabular}
+    \end{table}
+
+\clearpage
+\newpage
+
+\section*{Supporting information 2: Distributions of $p$-values for permuted networks}
+
+% \begin{figure}[!h]
+%     \begin{center}
+%       \centerline{\includegraphics*[height=.62\textheight]{Figures/random_p_distributions.eps}}
+%     \end{center}
+%      \caption{Distributions of $p$-values obtained when comparing the strength of the relationship between niche overlap and phylogenetic distance in 999 permutations of each network in our dataset with 500 permutations of each permuted network.
+Each line in each panel represents the histogram of $p$-values for one network.
+Bins are 0.05 wide.
+Purple lines in panels A-L represent pollination networks while green lines in panels M-N represent plant-herbivore networks.
+Networks are as follows (darkest to lightest):
+%      \textbf{A)} M_PL_001, M_PL_002, M_PL_003, M_PL_004, M_PL_005;
+%      \textbf{B)} M_PL_006, M_PL_007, M_PL_008, M_PL_009, M_PL_010;
+%      \textbf{C)} M_PL_011, M_PL_012, M_PL_013, M_PL_014, M_PL_015;
+%      \textbf{D)} M_PL_016, M_PL_017, M_PL_018, M_PL_019, M_PL_020;
+%      \textbf{E)} M_PL_021, M_PL_022, M_PL_023, M_PL_024, M_PL_025;
+%      \textbf{F)} M_PL_026, M_PL_027, M_PL_028, M_PL_029, M_PL_030;
+%      \textbf{G)} M_PL_031, M_PL_032, M_PL_033, M_PL_034, M_PL_035;
+%      \textbf{H)} M_PL_036, M_PL_037, M_PL_038, M_PL_039, M_PL_040;     
+%      \textbf{I)} M_PL_041, M_PL_042, M_PL_043, M_PL_044, M_PL_045;
+%      \textbf{J)} M_PL_046, M_PL_047, M_PL_048, M_PL_049, M_PL_050;     
+%      \textbf{K)} M_PL_051, M_PL_052, M_PL_053, M_PL_054, M_PL_055;
+%      \textbf{L)} M_PL_056, M_PL_057, M_PL_058, M_PL_059;
+%      \textbf{M)} Ibanez, Joern_altuda, Joern_marathon, Peralta, Sheldon;
+%      \textbf{N)} Ueckert, Basset, Bluthgen, Bodner, Coley, Novotny.
+%      For original sources for each network, see Table S1.
+%      }
+%     \label{within_family_regression}
+%   \end{figure}
+
 \end{spacing}
+
+\clearpage
 
@@
 
-\newpage
-\section*{Tables}
-
-  \begin{table}[!h]
-  \caption{\small Change in log odds (per million years of phylogenetic distance) of a pair of plants in the same family sharing a herbivore.}
-  \label{family_slopes_ph}
-  \begin{tabular}{|l  rr|}
-  \hline
-    Family & Change in log odds & $P$-value \\
-    \hline
-    \emph{Asteraceae} & -1.73 &  0.550 \\
-    \emph{Euphorbiaceae} & -19.2 & \textbf{\textless0.001} \\
-    \emph{Fabaceae} & 18.7 &  \textbf{0.046} \\
-    \emph{Melastomataceae} & -13.2 & \textbf{0.022} \\
-    \emph{Moraceae} & -2.13 & 0.092 \\
-    \emph{Nothofagaceae} & -595 & \textgreater{0.999} \\
-    \emph{Pinaceae} &  -25.8 & 0.733 \\
-    \emph{Poaceae} & -4.50 & \textbf{0.020} \\
-    \emph{Rubiaceae} & -8.16 &  \textbf{0.006} \\
-  \hline
-  \end{tabular}
-  \smallskip
-  \footnotesize
-
-  Nine plant families were sufficiently diverse in our  dataset to permit this analysis
-  (see \emph{Materials \\and Methods} for details). For each pattern of overlap, we show the change
-  in log odds per million years \\and the associated $P$-value. Statistically significant values are
-  indicated in bold. \\
-
-  \end{table}
-
-  \begin{table}[!h]
-  \caption{
-  \small Change in log odds (per million years of phylogenetic distance) of a pair of plants in the same family sharing a pollinator.}
-  \small
-  \label{family_slopes_pp}
-  \begin{tabular}{|l  rr|}
-    \hline
-    Family  & Change in log odds & $P$-value \\
-    \hline
-    \emph{Adoxaceae} &  -65.8 & 0.163 \\
-    \emph{Amaryllidaceae} &  -17.9 & \textbf{0.015} \\
-    \emph{Apiaceae} &  10.9  & \textbf{0.006} \\
-    \emph{Apocynaceae} &  -6.96  & \textbf{0.037} \\
-    \emph{Asparagaceae} &  -6.23  & 0.189 \\
-    \emph{Asteraceae}* &  -1.47  & \textbf{\textless0.001} \\
-    \emph{Berberidaceae} &  -1.48$\times10^3$ & \textgreater0.999 \\
-    \emph{Boraginaceae} &  -5.15  & \textbf{\textless0.001} \\
-    \emph{Brassicaceae} &  -11.2 & 0.072 \\
-    \emph{Calceolariaceae} &  156 & 0.998 \\
-    \emph{Campanulaceae} &  334 & 0.999 \\
-    \emph{Caprifoliaceae} &  0.310 & 0.959 \\
-    \emph{Caryophyllaceae} &  2.09 & 0.644 \\
-    \emph{Cistaceae} &  -11.4 & \textbf{\textless0.001} \\
-    \emph{Convolvulaceae} &  -1.84  & 0.837 \\
-    \emph{Ericaceae} &  4.61 & 0.116 \\
-    \emph{Fabaceae}* &  -12.9 & \textbf{\textless0.001} \\
-    \emph{Geraniaceae} &  -3.31  & 0.624 \\
-    \emph{Hydrangeaceae} &  0.057 & 0.982 \\
-    \emph{Iridaceae} &  -27.9 & 0.078 \\
-    \emph{Lamiaceae} &  -5.01  & \textbf{\textless0.001} \\
-    \emph{Loasaceae} &  -865  & \textgreater0.999 \\
-    \emph{Malpighiaceae} &  2.80 & 0.168 \\
-    \emph{Malvaceae} &  -5.56  & 0.363 \\
-    \emph{Melastomataceae}* &  5.19 & 0.577 \\
-    \emph{Montiaceae} &  -1.12  & 0.870 \\
-    \emph{Myrtaceae} &  8.55 & 0.071 \\
-    \emph{Oleaceae} &  0.995 & 0.855 \\
-    \emph{Onagraceae} &  -556  & \textgreater0.999 \\
-    \emph{Orchidaceae} &  -14.5 & 0.145 \\
-    \emph{Orobanchaceae} &  24.2  & 0.326 \\
-    \emph{Papaveraceae} &  -11.2 & 0.511 \\
-    \emph{Phyllanthaceae} &  9.99 & 0.433 \\
-    \emph{Plantaginaceae} &  -8.48  & \textbf{0.001} \\
-    \emph{Poaceae}* &  69.2  & \textbf{0.003} \\
-    \emph{Polygonaceae} &  -14.8 & \textbf{\textless0.001} \\
-    \emph{Primulaceae} &  14.9  & 0.343 \\
-    \emph{Ranunculaceae} &  -38.0 & \textbf{\textless0.001} \\
-    \emph{Rosaceae} &  0.759 & 0.735 \\
-    \emph{Rubiaceae}* &  -13.0 & \textbf{0.026} \\
-    \emph{Salicaceae} &  -1.90  & 0.545 \\
-    \emph{Sapindaceae} &  821 & 0.999 \\
-    \emph{Saxifragaceae} &  -0.092  & 0.992 \\
-    \emph{Solanaceae} &  -21.9 & 0.189 \\
-    \emph{Tropaeolaceae} &  192 & 0.997 \\
-    \emph{Verbenaceae} &  -9.03  & 0.627 \\
-    \emph{Violaceae} &  -0.487  & 0.974 \\
-  \hline
-  \end{tabular}
-  \smallskip
-  \footnotesize
-
-    We were able to fit these models to 47 plant families (see \emph{Materials and Methods} for     details). 
-    Families \\ marked with an asterisk were also sufficiently diverse in herbivory networks. 
-    Statistically significant values \\ are indicated in bold.
-
-    \end{table}
-
-\clearpage
-
 \end{document}

### 2019-02-20 manuscript/supporting_info.tex
supporting info now all pretty

@@
 
+\beginsupplement
 \clearpage
@@
 \section*{Supporting information 1: Sources for networks}
-
   \begin{table}[!h]
@@
     \label{sources}
-    \begin{tabular}{|l l l |}
+    \begin{center}
+    \begin{tabular}{|l l m{6cm} |}
     \hline
@@
     M\_PL\_031  & Pollination & \citep{Ramirez1989} \\
+    \hline
+    \end{tabular}
+    \end{center}
+    \end{table}
+
+    \clearpage
+    \newpage
+
+    \begin{table*}[h!]
+    \begin{center}
+    \begin{tabular}{|l l m{6cm} |}
+    \hline
+    Network & Network type & Original source \\
+    \hline
     M\_PL\_032  & Pollination & \citep{Schemske1978}  \\
@@
     M\_PL\_036  & Pollination & Olesen, J. M. Unpublished.  \\
-    \hline
-    \end{tabular}
-
-    \clearpage
-    \newpage
-
-    \begin{tabular}{|l l l |}
-    \hline
-    Network & Network type & Original source \\
-    \hline
     M\_PL\_037  & Pollination & \citep{Montero2005} \\
@@
     \end{tabular}
-    \end{table}
-
+    \end{center}
+    \end{table*}
 \clearpage
@@
 
-% \begin{figure}[!h]
-%     \begin{center}
-%       \centerline{\includegraphics*[height=.62\textheight]{Figures/random_p_distributions.eps}}
-%     \end{center}
-%      \caption{Distributions of $p$-values obtained when comparing the strength of the relationship between niche overlap and phylogenetic distance in 999 permutations of each network in our dataset with 500 permutations of each permuted network.
+\begin{figure}[!h]
+    \begin{center}
+      \centerline{\includegraphics*[width=.75\textwidth]{Figures/random_p_distributions.eps}}
+    \end{center}
+     \caption{\small Distributions of $p$-values obtained when comparing the strength of the relationship between niche overlap and phylogenetic distance in 999 permutations of each network in our dataset with 500 permutations of each permuted network.
 Each line in each panel represents the histogram of $p$-values for one network.
@@
 Purple lines in panels A-L represent pollination networks while green lines in panels M-N represent plant-herbivore networks.
-Networks are as follows (darkest to lightest):
-%      \textbf{A)} M_PL_001, M_PL_002, M_PL_003, M_PL_004, M_PL_005;
-%      \textbf{B)} M_PL_006, M_PL_007, M_PL_008, M_PL_009, M_PL_010;
-%      \textbf{C)} M_PL_011, M_PL_012, M_PL_013, M_PL_014, M_PL_015;
-%      \textbf{D)} M_PL_016, M_PL_017, M_PL_018, M_PL_019, M_PL_020;
-%      \textbf{E)} M_PL_021, M_PL_022, M_PL_023, M_PL_024, M_PL_025;
-%      \textbf{F)} M_PL_026, M_PL_027, M_PL_028, M_PL_029, M_PL_030;
-%      \textbf{G)} M_PL_031, M_PL_032, M_PL_033, M_PL_034, M_PL_035;
-%      \textbf{H)} M_PL_036, M_PL_037, M_PL_038, M_PL_039, M_PL_040;     
-%      \textbf{I)} M_PL_041, M_PL_042, M_PL_043, M_PL_044, M_PL_045;
-%      \textbf{J)} M_PL_046, M_PL_047, M_PL_048, M_PL_049, M_PL_050;     
-%      \textbf{K)} M_PL_051, M_PL_052, M_PL_053, M_PL_054, M_PL_055;
-%      \textbf{L)} M_PL_056, M_PL_057, M_PL_058, M_PL_059;
-%      \textbf{M)} Ibanez, Joern_altuda, Joern_marathon, Peralta, Sheldon;
-%      \textbf{N)} Ueckert, Basset, Bluthgen, Bodner, Coley, Novotny.
-%      For original sources for each network, see Table S1.
-%      }
-%     \label{within_family_regression}
-%   \end{figure}
+A list of networks shown on each panel follows; see Table S1 for original sources.
+     % Networks are as follows (darkest to lightest): \textbf{A)} M\_PL\_001, M\_PL\_002, M\_PL\_003, M\_PL\_004, M\_PL\_005;      \textbf{B)} M\_PL\_006, M\_PL\_007, M\_PL\_008, M\_PL\_009, M\_PL\_010;      \textbf{C)} M\_PL\_011, M\_PL\_012, M\_PL\_013, M\_PL\_014, M\_PL\_015;      \textbf{D)} M\_PL\_016, M\_PL\_017, M\_PL\_018, M\_PL\_019, M\_PL\_020;      \textbf{E)} M\_PL\_021, M\_PL\_022, M\_PL\_023, M\_PL\_024, M\_PL\_025;   \textbf{F)} M\_PL\_026, M\_PL\_027, M\_PL\_028, M\_PL\_029, M\_PL\_030;     \textbf{G)} M\_PL\_031, M\_PL\_032, M\_PL\_033, M\_PL\_034, M\_PL\_035;   \textbf{H)} M\_PL\_036, M\_PL\_037, M\_PL\_038, M\_PL\_039, M\_PL\_040;     \textbf{I)} M\_PL\_041, M\_PL\_042, M\_PL\_043, M\_PL\_044, M\_PL\_045; \textbf{J)} M\_PL\_046, M\_PL\_047, M\_PL\_048, M\_PL\_049, M\_PL\_050;      \textbf{K)} M\_PL\_051, M\_PL\_052, M\_PL\_053, M\_PL\_054, M\_PL\_055;     \textbf{L)} M\_PL\_056, M\_PL\_057, M\_PL\_058, M\_PL\_059;      \textbf{M)} Ibanez, Joern\_altuda, Joern\_marathon, Peralta, Sheldon;      \textbf{N)} Ueckert, Basset, Bluthgen, Bodner, Coley, Novotny.
+For original sources for each network, see Table S1.
+     }
+    \label{within_family_regression}
+  \end{figure}
+
+\subsection*{Networks shown in each panel of Figure S1}
+
+All names are as in Table S1. Networks included in each panel (from darkest to lightest line colours) are:
+
+\noindent \textbf{A)} M\_PL\_001, M\_PL\_002, M\_PL\_003, M\_PL\_004, M\_PL\_005;      \\
+\textbf{B)} M\_PL\_006, M\_PL\_007, M\_PL\_008, M\_PL\_009, M\_PL\_010;    \\
+\textbf{C)} M\_PL\_011, M\_PL\_012, M\_PL\_013, M\_PL\_014, M\_PL\_015;  \\
+\textbf{D)} M\_PL\_016, M\_PL\_017, M\_PL\_018, M\_PL\_019, M\_PL\_020;   \\
+\textbf{E)} M\_PL\_021, M\_PL\_022, M\_PL\_023, M\_PL\_024, M\_PL\_025;  \\
+\textbf{F)} M\_PL\_026, M\_PL\_027, M\_PL\_028, M\_PL\_029, M\_PL\_030;  \\
+\textbf{G)} M\_PL\_031, M\_PL\_032, M\_PL\_033, M\_PL\_034, M\_PL\_035; \\
+\textbf{H)} M\_PL\_036, M\_PL\_037, M\_PL\_038, M\_PL\_039, M\_PL\_040;   \\
+\textbf{I)} M\_PL\_041, M\_PL\_042, M\_PL\_043, M\_PL\_044, M\_PL\_045;\\
+\textbf{J)} M\_PL\_046, M\_PL\_047, M\_PL\_048, M\_PL\_049, M\_PL\_050;  \\
+\textbf{K)} M\_PL\_051, M\_PL\_052, M\_PL\_053, M\_PL\_054, M\_PL\_055;   \\
+\textbf{L)} M\_PL\_056, M\_PL\_057, M\_PL\_058, M\_PL\_059;  \\
+\textbf{M)} Ibanez, Joern\_altuda, Joern\_marathon, Peralta, Sheldon;  \\
+\textbf{N)} Ueckert, Basset, Bluthgen, Bodner, Coley, Novotny.
 

### 2019-02-22 manuscript/phylogenetic_signal_manuscript.tex
arg, need details from the other copy

@@
 
-  We modelled the relationship between nich
-
-e overlap and phylogenetic distance
+  We modelled the relationship between niche overlap and phylogenetic distance
   using a logistic regression. We used both the numbers of shared ($M_{ij}$)and 
@@
   niche overlap and phylogenetic distance within each network were fit using the
-  R~\citep{R} base function ``glm''. These separate regressions avoid the potential
+  R~\citep{R} base function ``glm'' and took the form. The fixed effect of distance
+  in this regression, $\beta_{distance}$, can
+  be understood as the change in log odds of sharing an interaction partner per
+  million-year change in phylogenetic distance.
+
+  These separate regressions avoid the potential
   for confounding the effects of different relationships in different networks. As
@@
   from the distribution of p-values obtained when comparing the permuted 
-  networks to permutations of the permuted networks. The distribution of 
-  p-values should be uniform. [[I still do not see how this gives us the
-  probability of a false negative... ]] [[Something to do with comparing
-  the distributions of p-values from glmer and the ones from the randomization.
-  I don't think I actually kept the p-values from glmer, but the p-values from
-  the randomizations are bang-on uniform.]]
-  [[Maybe go back to whichever reviewer comment this was based on?]]
-  [[How does this get at type II error?]] 
-  [[Seems we can calculate power for a specific alternative hypothesis by
-  comparing distributions of p-values from glmer and from the permutations.
-  I can only pray I kept the p-values from the randomised regressions...]]
+  networks to permutations of the permuted networks. Although calculating the
+  exact type II error requires a specific alternative hypothesis, the uniform
+  distribution of p-values we obtained after permuting the permuted networks
+  means that the type II error would increase linearly as the alternative 
+  hypothesis was set farther from zero. [[Is this cogent? Correct? If not, I think I
+  will have to remove all reference to type II error and hope we don't get the
+  same reviewer again. It may not be an issue since we've moved away from the
+  motif-like measures.]]
 
@@
 
-  [[I need to double-check that I'm actually doing this, and that the right things
-  are being plotted.]][[I think I may not have updated this since the family composition 
-  was not singificant. Still of interest, so redo. Guess I will also need to do randomisations
-  to make the p-vals here?]]
-
   Finally, we wished to compare the breakdown of overlap of interactions in
@@
   For each plant family, within each network type, we then fit one of two similar 
-  sets of models. First, when family $f$ was found in several networks of network
-  type $t$, we fit mixed-effects logistic regressions for the probability of sharing an interaction partner $\omega_{ntfij}$ of the form
-  \begin{equation}
-    logit(\omega_{ntfij}) \propto \delta_{ij} + N_{n} ,
-    \label{full}
-  \end{equation}
-
-  \noindent where $\omega_{tnfij}$ is the probability of sharing a partner 
-  in network $n$ of network type $t$ for plants $i$ and $j$ in plant family $f$,
-  $\delta_{ij}$ is the phylogenetic distance between plants $i$ and $j$, and
-  $N_{n}$ is a random effect of network $n$.
-  Second, if a plant family was represented in only one network 
-  and therefore necessarily in only one network type, we omitted the 
-  network-level random effect giving mixed-effects logistic regressions of the form
- \begin{equation}
-    logit(\omega_{pntfij}) \propto \delta_{ij} .
-    \label{minimal}
-  \end{equation}
-
-  \noindent We fit Eq.~\ref{full} using the function `glmer' from the
-  R package lme4~\citep{lme4} and fit Eq.~\ref{minimal} in R using the
-  function `glm' from the same package.
+  sets of models. If family $f$ was found in several networks of the same type
+  (e.g., several pollination networks), we fit a mixed-effects logistic regression
+  relating niche overlap to a fixed effect of phylogenetic distance and a random
+  effect for each network using the R~\citep{R} function ``glmer'' from
+  package \emph{lme4}~\citep{lme4}. If family $f$ was found in only one network
+  (and therefore only one network type), we omitted the 
+  network-level random effect and fit a logistic regression using the R~\citep{R}
+  base function ``glm''. [[We didn't use equations to explain the first round
+  of logistic regressions, so not sure why I was doing that here...]]
 
@@
 
-  \subsection*{Within-network conservation of niche overlap}
+  \subsection*{Within-network conservation of niche overlap} [[ok, need to make some updates here.]]
 
-    Across all networks, overlap of interaction partners decreased with increasing phylogenetic distance and the decrease in overlap of pollinators was steeper than that in herbivores ($\beta_{distance}$=-6.82, $p$\textless0.001 and $\beta_{distance:PP}$=-18.5, $p$\textless0.001, respectively).
+    Across all networks, overlap of interaction partners decreased with increasing phylogenetic distance and the decrease in overlap of pollinators was steeper than that in herbivores ($\beta_{distance:herbivory}$=-6.82, $p$\textless0.001 and $\beta_{distance:pollination}$=-18.5, $p$\textless0.001, respectively).
 That is, a pair of plants in the same genus was more likely to share interaction partners than a pair of plants in the same family in both types of networks, but a pair of congeners would be less likely to share pollinators than to share herbivores.
@@
 Observed networks with a negative relationship between phylogenetic distance and overlap always had a more negative slope than that obtained from the permuted networks, while the 10 networks with positive relationships between phylogenetic distance and overlap always had more positive relationships than the permuted networks.
+This suggests that even in the networks with non-significant relationships between niche overlap and phylogenetic distance, the association between niche overlap and phylogenetic distance was not random.
 
@@
 
-  \subsection*{Within-family conservation of niche overlap} [[Still of interest given negative result above?]]
+  \subsection*{Within-family conservation of niche overlap}
 

### 2019-03-13 manuscript/phylogenetic_signal_manuscript.tex
tested for a relationship between network size and slopes

@@
 
+  To test whether the relationship between phylogenetic distance and niche overlap
+  depended on network size, we fit a general linear model for the slope  of this relationship against the number of plant pairs for which distances could be calculated (hereafter ``network size"), network type, and their interaction.
+As the interaction between network type and network size was strong and opposite to the direction of the main effect of network size, we fit an additional general linear model using only data from plant-pollinator networks and including only the effect of network size (plant-herbivore networks were the baseline in the full glm).
+Both models were fit using the R~\citep{R} base function ``glm".
+
   % To determine how overlap of interaction partners
@@
 Overlap of interaction partners increased with increasing phylogenetic distance in only a single plant-pollinator network.% (M_PL_026).
+    The slope of the relationship between phylogenetic distance and overlap of interaction partners was related to the number of plant pairs in plant-herbivore, but not plant-pollinator, networks.
+Larger plant-herbivore networks had higher values of $\beta_{distance}$ ($\beta_{size}$=2.58$\times$10$^{-4}$, $p$=0.011 for the full glm; plant-herbivore networks are the baseline).
+Plant-pollinator networks had higher (less negative) slopes overall ($\beta_{pollinator}$=0.306, $p$\textless0.001 compared to the intercept value of -0.434 for plant-herbivore networks).
+Plant-pollinator networks moreover showed a much weaker relationship between network size and the strength of the overlap-distance relationship ($\beta_{pollination:size}$=-2.64$\times$10$^{-4}$, $p$=0.009).
+After refitting the glm to the plant-pollinator networks alone, there was no significant relationship between network size and the slope of the overlap-distance relationship ($\beta_{size}$=-5.91$\times$10$^{-6}$, $p$=0.572).
 

### 2019-03-13 code/Jaccard_regressions.R

@@ -6,8 +6,8 @@ files2<-as.character(list.files(path="../data/Jaccard/Overlap_dist/Stouffer_Ecol
 
 files=c(files1,files2)
 
-outtab=matrix(nrow=length(files),ncol=5)
-colnames(outtab)=c('network','Jaccard_slope','Jaccard_p','Sorenson_slope','Sorenson_p')
+outtab=matrix(nrow=length(files),ncol=6)
+colnames(outtab)=c('network','Jaccard_slope','Jaccard_p','Sorenson_slope','Sorenson_p','n_pairs')
 combi=matrix(nrow=0,ncol=6)
 
 for(n in 1:length(files)){
@@ -17,9 +17,10 @@ for(n in 1:length(files)){
   netdata=read.csv(network,header=TRUE,row.names=1,check.names=FALSE,sep=',')
   Jaccard=glm(cbind(n_shared_animals,n_notshared)~scale(distance),data=netdata,family="binomial")
   Sorenson=glm(cbind(n_shared_interactions,n_notshared)~scale(distance),data=netdata,family="binomial")
+  size=nrow(netdata)
 
   obs_slopes=c(Jaccard$coefficients['scale(distance)'],summary(Jaccard)$coefficients['scale(distance)',4],Sorenson$coefficients['scale(distance)'],summary(Sorenson)$coefficients['scale(distance)',4])
-  outtab[n,]=c(net,obs_slopes)
+  outtab[n,]=c(net,obs_slopes,size)
 
   if(n<12){
   	netdata$nettype='ph'
@@ -29,6 +30,7 @@ for(n in 1:length(files)){
   print(n)
   netdata$network=netname
   combi=rbind(combi,netdata)
+  print(outtab[n,])
 
 }
 

### 2019-04-18 manuscript/phylogenetic_signal_manuscript.tex
all major comments addressed, I think. Now need to read and update

--- 2019-02-22 manuscript/phylogenetic_signal_manuscript.tex
@@
 
-\author{Alyssa R. Cirtwill$^{1}$, Giulio V. Dalla Riva$^{2}$, Nick J. Baker$^{1}$,\\
- Joshua A. Thia$^{1,3}$, Christie J. Webber$^{1}$, Daniel B. Stouffer$^{1}$, MSC helpers from Linkoping}
+\author{Alyssa R. Cirtwill$^{1,2}$, Giulio V. Dalla Riva$^{3}$, Nick J. Baker$^{1}$,\\
+Mikael Ohlsson$^{4}$, Isabelle Norstr\"{o}m$^{4}$, Inger-Marie Wohlfarth Hasle$^{4}$,\\
+Joshua A. Thia$^{1,5}$, Christie J. Webber$^{1}$, Daniel B. Stouffer$^{1}$}
 \date{\small$^1$Centre for Integrative Ecology, School of Biological Sciences\\
-    \medskip$^2$Biomathematics Research Centre, School of Mathematics and Statistics\\
+\medskip$^2$Department of Ecology,\\
+Environment, and Plant Sciences (DEEP)\\
+Stockholm University\\
+114 19 Stockholm, Sweden\\
+\medskip$^3$Biomathematics Research Centre, School of Mathematics and Statistics\\
 University of Canterbury\\Private Bag 4800\\
 Christchurch 8140, New Zealand\\
-\medskip$^3$Present Address: School of Biological Sciences\\
+\medskip$^4$Department of Physics, Chemistry, and Biology (IFM)\\ Link\"{o}ping University\\ 581 83 Link\"{o}ping, Sweden
+\medskip$^5$Present Address: School of Biological Sciences\\
 University of Queensland\\Brisbane, QLD 4072, Australia }
@@
   In both cases, these interactions do not occur randomly but
-  are strongly influenced by plants' phenotypes. For example, plants that produce
-  abundant or high-quality nectar may receive more visits from
-  pollinators~\citep{Robertson1999} whereas plants that produce noxious secondary metabolites
-  may suffer fewer herbivores~\citep{Johnson2014}. A plant's traits are also 
-  likely to determine which specific pollinators and herbivores interact with that plant.
-  Plants with different defences (e.g., thorns vs. chemical defences) may deter 
-  different groups of herbivores~\citep{Ehrlich1964,Johnson2014}, and the concept
-  of pollination syndromes has often been used to group plants into phenotypic
+  are strongly influenced by plants' phenotypes. For example, plants that 
+  produce abundant or high-quality nectar may receive more visits from
+  pollinators~\citep{Robertson1999} whereas plants that produce noxious 
+  secondary metabolites may suffer fewer herbivores~\citep{Johnson2014}. 
+  A plant's traits are also likely to determine which specific pollinators 
+  and herbivores interact with that plant. Plants with different defences 
+  (e.g., thorns vs. chemical defences) may deter different groups of 
+  herbivores~\citep{Ehrlich1964,Johnson2014}, and the concept of 
+  pollination syndromes has often been used to group plants into phenotypic
   classes believed to attract certain groups of pollinators~\citep{Waser1996,Fenster2004,Ollerton2009}.
 
-  [[update refs, add definition of plant roles]]
+  [[update refs, perhaps expand?]]
   If attractive and/or defensive traits are heritable,
@@
   patterns of interactions with animals~\citep{Schemske1999}.
+That is, there may be \emph{phylogenetic signal} in plants' interactions such that closely-related plants may tend to have similar interaction partners.
   Recent studies that have investigated this question at the level of whole
   communities, however, have yielded mixed results~\citep{Rezende2007a,Gomez2010,Rohr2014a,Fontaine2015,Lind2015}.
-  In particular, significant phylogenetic signal in plants' interaction partners
-  ---the tendency for more closely-related plants to have more similar interactions---
-  tends to be rare in empirical networks (\citealp{Rezende2007a,Lind2015}; but see~\citealp{Elias2013,Fontaine2015}).
-  Further, plants' roles [[how defined?]] within networks tend to be less phylogenetically constrained than those of 
-  animals~\citep{Rezende2007a,Chamberlain2014,Rohr2014,Vamosi2014,Lind2015}. [[GVDR is skeptical of this - check partiteness, size, type of role and add more detail to support.]]
+  In particular, significant phylogenetic signal in plants' sets of interaction partners tends to be rare in empirical networks (\citealp{Rezende2007a,Lind2015}; but see~\citealp{Elias2013,Fontaine2015}).
+  % Further, plants' roles [[how defined?]] within networks tend to be less phylogenetically constrained than those of 
+  % animals~\citep{Rezende2007a,Chamberlain2014,Rohr2014,Vamosi2014,Lind2015}.
+[[GVDR is skeptical of this - check partiteness, size, type of role and add more detail to support.]] % I doubt this is really important, probably more trouble than it's worth.
 
@@
   between pairs of non-angiosperms from our analyses. As only two networks (both 
-  plant-herbivore networks) included more than one such species and non-angiosperms
+  herbivory networks) included more than one such species and non-angiosperms
   were always a small minority of any network, we do not 
@@
   % [[It appears we switched to Jaccard and Sorenson dissimilarities - number of shared partners and number of shared partners*2/notshared.]]
+
 \subsection*{Statistical analysis}
 
-  We modelled the relationship between niche overlap and phylogenetic distance
-  using a logistic regression. We used both the numbers of shared ($M_{ij}$)and 
-  non-shared ($U_{ij}$) partners as dependent variables and centred, scaled phylogenetic 
-  distance as the independent variable. This approach is conceptually similar to 
-  modelling successes and failures in a binomial-distributed process. 
-  Accordingly, we assumed a binomial distribution for residuals. Regressions of
-  niche overlap and phylogenetic distance within each network were fit using the
-  R~\citep{R} base function ``glm'' and took the form. The fixed effect of distance
-  in this regression, $\beta_{distance}$, can
-  be understood as the change in log odds of sharing an interaction partner per
-  million-year change in phylogenetic distance.
+  We modelled the relationship between niche overlap and phylogenetic 
+  distance using a logistic regression. We used both the numbers of shared 
+  ($M_{ij}$) and non-shared ($U_{ij}$) partners as dependent variables and 
+  centred, scaled phylogenetic distance as the independent variable. This 
+  approach is conceptually similar to modelling successes and failures in a 
+  binomial-distributed process. Accordingly, we assumed a binomial 
+  distribution for residuals and used a logit link function to model the 
+  probability $\omega_{ij}$ of plants $i$ and $j$ sharing an interaction 
+  partner. Regressions of niche overlap and phylogenetic distance within 
+  each network were fit using the R~\citep{R} base function ``glm'' and 
+  took the form
 
-  These separate regressions avoid the potential
-  for confounding the effects of different relationships in different networks. As
-  we also wished to evaluate the overall trend across networks, we fit an additional
-  regression of niche overlap and phylogenetic distance across all network types.
-  As well as the fixed effect of phylogenetic distance, this regression included 
-  fixed effects of network type (pollination or herbivory) and the interaction 
-  between phylogenetic network type and random intercepts and slopes per network.
-  This expanded regression was fit using the R~\citep{R} function ``glmer'' from
-  package \emph{lme4}~\citep{lme4}.
+    \begin{equation}
+      \omega_{ij} \propto \beta_{distance}\delta_{ij} ,
+      \label{basic}
+    \end{equation}
+
+  where $\delta_{ij}$ is the phylogenetic distance between plants $i$ and 
+  $j$. The fixed effect of distance in this regression, $\beta_{distance}$, 
+  can be understood as the change in log odds of sharing an interaction 
+  partner per million-year change in phylogenetic distance.
+
+  These separate regressions avoid the potential for confounding the effects
+  of different relationships in different networks. As we also wished to 
+  evaluate the overall trend across networks, we fit an additional
+  regression of niche overlap and phylogenetic distance across all network 
+  types. As well as the fixed effect of phylogenetic distance, this 
+  regression included fixed effects of network type (pollination or 
+  herbivory) and the interaction between phylogenetic network type and 
+  random intercepts and slopes per network. This expanded regression was fit
+  using the R~\citep{R} function ``glmer'' from package 
+  \emph{lme4}~\citep{lme4} and took the form
+
+    \begin{equation}
+      \omega_{ij} \propto \beta_{distance} \delta_{ij} + \beta_{pollination} I_ij + \beta_{distance:pollination} \delta_{ij} I_ij ,
+    \end{equation}
+
+  where $I_{ij}=1$ when plants $i$ and $j$ are drawn from a 
+  pollination network and $I_{ij}=0$ otherwise and all other symbols 
+  are as above. Note that we only compared pairs of plants taken from the 
+  same network. The fixed effects $\beta_{pollination}$ and $\beta_{distance:pollination}$ 
+  are the change in intercept and slope of the log odds of sharing an 
+  interaction partner, respectively relative to the baseline of 
+  herbivory networks.
 
   Note that pairs of plants are not always independent: the same plant will 
-  appear in many pairs. This violates the assumption of independence used when 
-  calculating the significance of logistic regressions within the R~\citep{R} 
-  base package or the package \emph{lme4}~\citep{lme4}. To calculate significance 
-  of the regression coefficients we observed, it was therefore necessary to compare the 
-  observed relationships to those in a suite of appropriately permuted networks. To create 
-  these networks, we shuffled interactions among species while preserving row 
-  and column totals. That is, each species retained the same number of 
-  interaction partners as in the observed network but the exact set of 
-  partners (and therefore niche overlaps with all other species) varied across 
-  permuted networks. We preserved the observed phylogenetic relationships 
-  between species in all cases. For each observed network, we created 999 such 
-  permuted networks and calculated the relationship between niche overlap and 
-  phylogenetic distance. This gave us a null distribution for each observed 
-  network with which to determine the significance of the observed 
+  appear in many pairs. This violates the assumption of independence used 
+  when calculating the significance of logistic regressions within 
+  the R~\citep{R} base package or the package \emph{lme4}~\citep{lme4}. To 
+  calculate significance of the regression coefficients we observed, it was 
+  therefore necessary to compare the observed relationships to those in a 
+  suite of appropriately permuted networks. To create these networks, we 
+  shuffled interactions among species while preserving row and column 
+  totals. That is, each species retained the same number of interaction 
+  partners as in the observed network but the exact set of partners (and 
+  therefore niche overlaps with all other species) varied across permuted 
+  networks. We preserved the observed phylogenetic relationships between 
+  species in all cases. For each observed network, we created 999 such 
+  permuted networks and calculated the relationship between niche overlap 
+  and phylogenetic distance. This gave us a null distribution for each 
+  observed network with which to determine the significance of the observed 
   relationship.
@@
   from the distribution of p-values obtained when comparing the permuted 
-  networks to permutations of the permuted networks. Although calculating the
-  exact type II error requires a specific alternative hypothesis, the uniform
-  distribution of p-values we obtained after permuting the permuted networks
-  means that the type II error would increase linearly as the alternative 
-  hypothesis was set farther from zero. [[Is this cogent? Correct? If not, I think I
-  will have to remove all reference to type II error and hope we don't get the
-  same reviewer again. It may not be an issue since we've moved away from the
-  motif-like measures.]]
+  networks to permutations of the permuted networks. Although calculating 
+  the exact type II error requires a specific alternative hypothesis, the 
+  uniform distribution of p-values we obtained after permuting the permuted 
+  networks means that the type II error would increase linearly as the 
+  alternative hypothesis was set farther from zero.
+[[Is this cogent?
+Correct?
+If not, I think I will have to remove all reference to type II error and hope we don't get the same reviewer again.
+It may not be an issue since we've moved away from the motif-like measures.]]
+
+  To test whether the relationship between phylogenetic distance and niche overlap depended on network size, we fit a general linear model for the slope of this relationship in the glm models against the number of plant pairs for which distances could be calculated (hereafter ``network size"), network type (again using herbivory networks as a baseline), and their interaction.
+
+    \begin{equation}
+      \beta_{distance} \propto \beta_{size} \eta_{N} + \beta_{pollination} I_N + \beta_{size:pollination} \eta_{N} I_N ,
+    \end{equation}
+
+  where $\eta_{N}$ is the number of plant pairs in network $N$ for which distances could be calculated, $I_N$ is an indicator equal to 1 if network $N$ is a pollination network and 0 otherewise.
+
+  As the interaction between network type and network size was strong and opposite to the direction of the main effect of network size, we fit an additional general linear model using only data from pollination networks and including only the effect of network size (herbivory networks were the baseline in the full glm).
+Both models were fit using the R~\citep{R} base function ``glm".
 
@@
   Finally, we wished to compare the breakdown of overlap of interactions in
-  different plant families. To do this, we used the same definitions of overlap
-  and phylogenetic distance as in the within-network analysis but restricted
-  our regressions to pairs of plants from the same family and the same network.
-  Unlike in our previous analysis, we analysed data from pollination and
-  herbivory networks separately as most well-represented plant families appeared
-  in only one network type. For those families which appeared in both network types, 
-  we ran separate analyses on each subset of data.
+  different plant families. To do this, we used the same definitions of 
+  overlap and phylogenetic distance as in the within-network analysis but 
+  restricted our regressions to pairs of plants from the same family and 
+  the same network. Unlike in our previous analysis, we analysed data from 
+  pollination and herbivory networks separately as most well-represented 
+  plant families appeared in only one network type. For those families 
+  which appeared in both network types, we ran separate analyses on each 
+  subset of data.
 
-  For each plant family, within each network type, we then fit one of two similar 
-  sets of models. If family $f$ was found in several networks of the same type
-  (e.g., several pollination networks), we fit a mixed-effects logistic regression
-  relating niche overlap to a fixed effect of phylogenetic distance and a random
-  effect for each network using the R~\citep{R} function ``glmer'' from
-  package \emph{lme4}~\citep{lme4}. If family $f$ was found in only one network
+  For each plant family, within each network type, we then fit one of two 
+  similar sets of models. If family $f$ was found in several networks of 
+  the same type (e.g., several pollination networks), we fit a 
+  mixed-effects logistic regression relating niche overlap to a fixed 
+  effect of phylogenetic distance and a random effect for each network 
+  using the R~\citep{R} function ``glmer'' from package
+   \emph{lme4}~\citep{lme4}. If family $f$ was found in only one network
   (and therefore only one network type), we omitted the 
-  network-level random effect and fit a logistic regression using the R~\citep{R}
-  base function ``glm''. [[We didn't use equations to explain the first round
-  of logistic regressions, so not sure why I was doing that here...]]
+  network-level random effect and fit a logistic regression using the 
+  R~\citep{R} base function ``glm''. These equations took the same form as equation~\ref{basic}.
 
@@
 
-  \subsection*{Within-network conservation of niche overlap} [[ok, need to make some updates here.]]
+  \subsection*{Within-network conservation of niche overlap}
 
-    Across all networks, overlap of interaction partners decreased with increasing phylogenetic distance and the decrease in overlap of pollinators was steeper than that in herbivores ($\beta_{distance:herbivory}$=-6.82, $p$\textless0.001 and $\beta_{distance:pollination}$=-18.5, $p$\textless0.001, respectively).
-That is, a pair of plants in the same genus was more likely to share interaction partners than a pair of plants in the same family in both types of networks, but a pair of congeners would be less likely to share pollinators than to share herbivores.
-Regardless of phylogenetic distance, a pair of plants were also less likely to share pollinators than herbivores ($\beta_{PP}$=-1.44, $p$\textless0.001).
-This may be due to the greater proportion of
-    specialist pollinators than specialist herbivores. In our dataset, an
-    average of 48\% (+/- 14) of pollinators in a given web were extreme 
-    specialists (i.e., visited only one plant species) compared to 29\% 
-    (+/- 29) of herbivores ($z$=5.62, df=68, $P$\textless0.001 
-    for a binomial regression of specialists and generalists over network
-    type). % Are the above betas un-scaled?
+    Across all networks, more distantly-related plants were less likely to 
+    share interaction partners ($\beta_{distance}$=-6.82, 
+    $p$\textless0.001). Plants in pollination networks tended to share 
+    fewer interaction partners overall, and the decrease in overlap with 
+    increasing phylogenetic distance was steeper 
+    ($\beta_{pollination}$=-1.44, $p$\textless0.001 and 
+    $\beta_{distance:pollination}$=-18.5, $p$\textless0.001, respectively). 
+    That is, a pair of plants in the same genus was more likely to share 
+    interaction partners than a pair of plants in the same family in both 
+    types of networks, but a pair of congeners would be less likely to 
+    share pollinators than to share herbivores. [[Add predicted overlap values at extremes of distance?]] These trends may be partly 
+    due to the greater proportion of specialist pollinators than specialist 
+    herbivores. In our dataset, an average of 48\% (+/- 14) of pollinators 
+    in a given web were extreme specialists (i.e., visited only one plant 
+    species) compared to 29\% (+/- 29) of herbivores ($z$=5.62, df=68, 
+    $P$\textless0.001 for a binomial regression of specialists and 
+    generalists over network type).
 
@@
     pollination networks, with overlap of interaction partners decreasing 
-    with increasing phylogenetic distance in some networks and increasing in 
-    others (Fig.~\ref{within_network_regression}).
-Overlap of interaction partners decreased significantly with increasing phylogenetic distance in 7/11 plant-herbivore networks and 33/59 plant-pollinator networks.
-In the remaining four plant-herbivore networks and 25 of the 26 remaining plant-pollinator networks, overlap of interaction partners was not related to phylogenetic distance.
-Overlap of interaction partners increased with increasing phylogenetic distance in only a single plant-pollinator network.% (M_PL_026).
+    with increasing phylogenetic distance in some networks and increasing 
+    in others (Fig.~\ref{within_network_regression}).
+Overlap of interaction partners decreased significantly with increasing phylogenetic distance in 7/11 herbivory networks and 33/59 pollination networks.
+In the remaining four herbivory networks and 25 of the 26 remaining pollination networks, overlap of interaction partners was not related to phylogenetic distance.
+Overlap of interaction partners increased with increasing phylogenetic distance in only a single pollination network.% (M_PL_026).
+    The slope of the relationship between phylogenetic distance and overlap of interaction partners was related to the number of plant pairs in herbivory, but not pollination, networks.
+Larger herbivory networks had higher values of $\beta_{distance}$ ($\beta_{size}$=2.58$\times$10$^{-4}$, $p$=0.011 for the full glm; herbivory networks are the baseline).
+Plant-pollinator networks had higher (less negative) slopes overall ($\beta_{pollinator}$=0.306, $p$\textless0.001 compared to the intercept value of -0.434 for herbivory networks).
+Plant-pollinator networks moreover showed a much weaker relationship between network size and the strength of the overlap-distance relationship ($\beta_{pollination:size}$=-2.64$\times$10$^{-4}$, $p$=0.009).
+After refitting the glm to the pollination networks alone, there was no significant relationship between network size and the slope of the overlap-distance relationship ($\beta_{size}$=-5.91$\times$10$^{-6}$, $p$=0.572).
 
-    [[Reviewers demanded this - it seems very boring]]
+    [[to SI?]]
     Comparing the results in the observed networks to those obtained after permuting phylogenetic distances across pairs of plants, the observed slope of the relationship between phylogenetic distance and interaction partner overlap was always more extreme (i.e., always lesser or always greater) than that obtained in the permuted networks (Fig.~\ref{obs_vs_random}).
@@
 
-    Comparing the permuted networks to permutations of the permuted networks, the slope obtained from the initial permuted network was quite variable with respect to the slopes obtained from 500 permutationss of the permuted network.
+    [[To SI.]]
+    Comparing the permuted networks to permutations of the permuted networks, the slope obtained from the initial permuted network showed no clear relationship to the slopes obtained from 500 permutations of the permuted network.
 Averaged over the 1000 permutations of each observed network, the slope of the permuted network was more extreme than 48.1-51.3\% of the permutations of the permuted network.
@@
   % Regression of all families at once with RE's for network
-    Taking all families together, the probability of species in the same family sharing interaction partners decreased wiht increasing phylogenetic distance in both plant-pollinator and plant-herbivore networks and the strength of this relationship did not differ significantly between network types ($\beta_{distance}$=-4.75, $p$=0.012; $\beta_{distance:PH}$=-1.73, $p$=0.681).
-Plants in plant-herbivore networks had a higher probability of sharing interaction partners with a member of the same family ($\beta_{PH}$=0.78, $p$=0.007).
+    Taking all families together, the probability of species in the same family sharing interaction partners was not significantly related to phylogenetic distance ($\beta_{distance}$=-6.48, $p$=0.087).
+Pollination networks did not show a significantly different trend from the herbivory networks ($\beta_{distance:pollination}$=1.73, $p$=0.681).
+More closely-related pollinators did, however, tend to share fewer interaction partners ($\beta_{pollination}$=-0.776, $p$=0.007), similar to our within-network results above.
 
-    The relationship between within-family niche overlap and phylogenetic distance
-    varied widely in both pollination and herbivory networks. 
-    % Gotta separate plant-herb and plant-poll networks.
-
-    % Regressions for each family separately.
+    Considering each family separately, the relationship between within-family niche overlap and phylogenetic distance varied widely in both pollination and herbivory networks. 
     For the families
@@
     Models for two families did not converge.
-In both the \emph{Lauraceae}, (represented by four species in one pollination network) and the \emph{Sapindaceae} in plant-herbivore networks (represented by five species in one network), one pair of species shared a single interaction partner while all other pairs did not share any interaction partners.
-The model for \emph{Sapindaceae} in plant-pollinator networks did converge.
+In both the \emph{Lauraceae}, (represented by four species in one pollination network) and the \emph{Sapindaceae} in herbivory networks (represented by five species in one network), one pair of species shared a single interaction partner while all other pairs did not share any interaction partners.
+The model for \emph{Sapindaceae} in pollination networks did converge.
 
@@
 
-  ARC, DBS, GVDR, and NJB designed the research. ARC, JAT, and CJW collected published data. [[Add MSC helpers!]]
+  ARC, DBS, GVDR, and NJB designed the research. ARC, MO, IN, and IMWH, JAT, and CJW collected published data. 
   ARC and GVDR performed the analyses. All authors contributed to the manuscript.
@@
     \begin{center}
-      \centerline{\includegraphics*[width=.75\textwidth]{Figures/dataplots/observed_vs_random.eps}}
+      \centerline{\includegraphics*[height=.75\textwidth]{Figures/dataplots/observed_vs_random.eps}}
     \end{center}
      \caption{The slopes of the mixed-effect logistic regression of pairwise niche overlap against phylogenetic distance was signficantly different from 0 for each network.
-Here we show, for plant-herbivore (PH) and plant-pollinator (PP) networks, the observed slopes (depicted by green squares or purple diamonds, respectively).
+Here we show, for herbivory (PH) and pollination (PP) networks, the observed slopes (depicted by green squares or purple diamonds, respectively).
 The maximum and minimum slopes obtained from 999 permutations of each network are depicted by thin, black lines.

### 2019-05-23 manuscript/phylogenetic_signal_manuscript.tex
checked bib, ready to send out revamped discussion

@@
 Christchurch 8140, New Zealand\\
-\medskip$^4$Department of Physics, Chemistry, and Biology (IFM)\\ Link\"{o}ping University\\ 581 83 Link\"{o}ping, Sweden
+\medskip$^4$Department of Physics, Chemistry, and Biology (IFM)\\ Link\"{o}ping University\\ 581 83 Link\"{o}ping, Sweden\\
 \medskip$^5$Present Address: School of Biological Sciences\\
@@
 
+\section*{Warning}
+
+Our original methodology was different from that in Fontaine \& Th\'{e}bault 2015 (Popul Ecol), but now that we've switched to Jaccard as our overlap measure we're doing almost the exact same thing with a slightly different set of networks.
+This will probably make it quite hard to argue novelty.
+
 \section*{Keywords}
@@
   Interactions with animals affect plants' life cycles in several critical
-  ways~\citep{Mayr2001,Sauve2015}. On one hand,
+  ways~\citep{Mayr2001,Sauve2016}. On one hand,
   pollination and other mutualistic interactions contribute
@@
   In both cases, these interactions do not occur randomly but
-  are strongly influenced by plants' phenotypes. For example, plants that 
+  are strongly influenced by plants' phenotypes~\citep{Fontaine2015}. 
+  For example, plants that 
   produce abundant or high-quality nectar may receive more visits from
@@
   secondary metabolites may suffer fewer herbivores~\citep{Johnson2014}. 
-  A plant's traits are also likely to determine which specific pollinators 
+  A plant's traits are also likely to determine \emph{which} specific pollinators 
   and herbivores interact with that plant. Plants with different defences 
@@
 
-  [[update refs, perhaps expand?]]
   If attractive and/or defensive traits are heritable,
   then we can reasonably expect that related plants will have similar 
-  patterns of interactions with animals~\citep{Schemske1999}.
+  patterns of interactions with animals, especially if there is some selection in either group to avoid competition or the number of potential partners is limited~\citep{Schemske1999,Ponisio2017}.
 That is, there may be \emph{phylogenetic signal} in plants' interactions such that closely-related plants may tend to have similar interaction partners.
   Recent studies that have investigated this question at the level of whole
-  communities, however, have yielded mixed results~\citep{Rezende2007a,Gomez2010,Rohr2014a,Fontaine2015,Lind2015}.
-  In particular, significant phylogenetic signal in plants' sets of interaction partners tends to be rare in empirical networks (\citealp{Rezende2007a,Lind2015}; but see~\citealp{Elias2013,Fontaine2015}).
+  communities, however, have yielded mixed results~\citep{Rezende2007a,Gomez2010,Rohr2014a,Fontaine2015,Lind2015,Ibanez2016,Bergamini2017,Sydenham2017,Volf2017,Hutchinson2017}.
+  In particular, significant phylogenetic signal in plants' sets of interaction partners tends to be rare in empirical networks (\citealp{Rezende2007a,Lind2015,Ibanez2016}; but see~\citealp{Elias2013,Fontaine2015,Hutchinson2017}).
+Significant degrees of phylogentic signal and/or coevolution may also lead to only small differences in network structure, adding to the difficulty of understanding patterns in species' interaction partners~\citep{Ponisio2017}.
+  Further, the plant and animal components of networks can show different degrees of phylogenetic conservation of interaction partners.
+In mutualistic networks, animals often show a stronger phylogenetic signal in their partners than plants~\citep{Rezende2007a,Chamberlain2014,Rohr2014,Vamosi2014,Lind2015,Fontaine2015} (but see~\citep{Rafferty2013} for a counterexample).
+In antagonistic networks, however, actively-foraging consumers tend to show less phylogenetic signal than their prey~\citep{Ives2006,Cagnolo2011,Naisbit2011,Fontaine2015}.
+Thus, it is not straightforward to assume that interactions will be similar among related species.
+[[GVDR was skeptical of a similar point in the previous draft - less contentious now?]]
   % Further, plants' roles [[how defined?]] within networks tend to be less phylogenetically constrained than those of 
@@
   by a wide variety of traits, and not all of these are likely to be
-  phylogenetically conserved~\citep{Rezende2007,Kursar2009}. If, for example,
+  phylogenetically conserved~\citep{Rezende2007,Kursar2009,Ibanez2016}. If, for example,
   floral displays are strongly affected by environmental conditions~\citep{Canto2004}, 
@@
   weaken the overall association between plant phylogeny and interaction
-  partners~\citep{Armbruster1997,Lankau2007,Siepielski2010,Wise2013}. 
+  partners~\citep{Armbruster1997,Lankau2007,Siepielski2010,Wise2013,Karinho2014}. 
   For instance, floral traits that
@@
   defences~\citep{Adler2006} or altering floral display or nectar 
-  availability~\citep{Strauss1997}. Observed patterns
+  availability~\citep{Strauss1997}. There may also be tradeoffs between chemical and physical defenses, or defenses at different life stages~\citep{Karinho2014,Endara2017}. Observed patterns
   of similarity in plants' interaction partners therefore represent
@@
   converge upon similar phenotypes, attracting a particularly 
-  efficient or abundant pollinator~\citep{Ollerton1996,Ollerton2009}. 
+  efficient or abundant pollinator~\citep{Ollerton1996,Ollerton2009,Ibanez2016}. 
   Likewise, herbivores may be able to depredate sets of unrelated 
@@
 
-  Here we use a novel approach to investigate how overlap in 
-  interaction partners between pairs of plants (henceforth ``niche 
-  overlap'') varies over phylogenetic distance. Whereas previous 
+  [[Trying to emphasize the family-wise part as a point of difference from Fontaine \& Thebault, even though our results weren't the most exciting.]]
+  Here we investigate how overlap in interaction partners between 
+  pairs of plants (henceforth ``niche overlap'') varies over 
+  phylogenetic distance and how this differs between plant families. 
+  Whereas previous 
   studies have focused on the presence or absence of phylogenetic
-  signal across entire networks, we are able to investigate the
-  relationship between niche overlap and phylogenetic distance in
-  within networks as well as different plant families. Specifically,
+  signal across entire networks, we take a pairwise perspective in
+  order to ontain a more detailed picture of how plant phylogeny
+  relates to network structure. Specifically,
   we test whether niche overlap decreases over increasing phylogenetic
@@
   plant species (mean=39.1, median=29.5). See \emph{Table S1, 
-  Supporting Information} for details on the original sources of all 
+  Supporting information 1} for details on the original sources of all 
   networks.
@@
     \begin{equation}
-      \omega_{ij} \propto \beta_{distance} \delta_{ij} + \beta_{pollination} I_ij + \beta_{distance:pollination} \delta_{ij} I_ij ,
+      \omega_{ij} \propto \beta_{distance} \delta_{ij} + \beta_{pollination} I_{ij} + \beta_{distance:pollination} \delta_{ij} I_{ij} ,
     \end{equation}
@@
 
-  To test whether the relationship between phylogenetic distance and niche overlap depended on network size, we fit a general linear model for the slope of this relationship in the glm models against the number of plant pairs for which distances could be calculated (hereafter ``network size"), network type (again using herbivory networks as a baseline), and their interaction.
+  To test whether the relationship between phylogenetic distance and niche overlap depended on network size, we fit a general linear model for the slope of this relationship in the glm models against the number of plant pairs for which distances could be calculated (hereafter ``network size"), network type (again using herbivory networks as a baseline), and their interaction:
 
@@
 
-  The PERMANOVA tests whether there is an association between
-  community composition and network-level patterns but does not
-  give any information on \emph{which} plant families have the
-  greatest effects. To address this, we supplemented the 
-  PERMANOVA with three constrained correspondence analyses (CCAs)
-  which placed plant families along an axis representing the
-  change in log odds of sharing an interaction partner.
-  A correspondence 
-  analysis (CA) is similar to other multivariate
-  analyses such as principal components analysis in that it
-  reduces multivariate data to a set of orthogonal axes. A
-  subset of axes that explain the majority of variation in 
-  the data can then be interpreted to elucidate trends that
-  were difficult to interpret in the full multivariate space.
-  A constrained correspondence analysis (CCA) creates an extra
-  axis based on some constraint - in this case, the change in
-  log odds of sharing an interaction partner.
+  % # This isn't mentioned anywhere else, likely a relic of an older plan.
+  % The PERMANOVA tests whether there is an association between
+  % community composition and network-level patterns but does not
+  % give any information on \emph{which} plant families have the
+  % greatest effects. To address this, we supplemented the 
+  % PERMANOVA with three constrained correspondence analyses (CCAs)
+  % which placed plant families along an axis representing the
+  % change in log odds of sharing an interaction partner.
+  % A correspondence 
+  % analysis (CA) is similar to other multivariate
+  % analyses such as principal components analysis in that it
+  % reduces multivariate data to a set of orthogonal axes. A
+  % subset of axes that explain the majority of variation in 
+  % the data can then be interpreted to elucidate trends that
+  % were difficult to interpret in the full multivariate space.
+  % A constrained correspondence analysis (CCA) creates an extra
+  % axis based on some constraint - in this case, the change in
+  % log odds of sharing an interaction partner.
 
@@
     types of networks, but a pair of congeners would be less likely to 
-    share pollinators than to share herbivores. [[Add predicted overlap values at extremes of distance?]] These trends may be partly 
+    share pollinators than to share herbivores. As an illustration, a pair
+    of plants which diverged 10mya would have a probability of 0.202 of sharing
+    a given herbivore and 0.094 of sharing a given pollinator, while a 
+    pair of plants which diverged 750mya would 
+    have a probability of 0.121 of sharing a given herbivore or 
+    0.011 of sharing a given pollinator.
+    These trends may be partly 
     due to the greater proportion of specialist pollinators than specialist 
@@
     $P$\textless0.001 for a binomial regression of specialists and 
-    generalists over network type).
+    generalists over network type). As extreme specialists by definition 
+    are never shared by more than one plant, a large proportion of specialists
+    would decrease interaction partner overlap.
 
@@
     with increasing phylogenetic distance in some networks and increasing 
-    in others (Fig.~\ref{within_network_regression}).
-Overlap of interaction partners decreased significantly with increasing phylogenetic distance in 7/11 herbivory networks and 33/59 pollination networks.
-In the remaining four herbivory networks and 25 of the 26 remaining pollination networks, overlap of interaction partners was not related to phylogenetic distance.
-Overlap of interaction partners increased with increasing phylogenetic distance in only a single pollination network.% (M_PL_026).
-    The slope of the relationship between phylogenetic distance and overlap of interaction partners was related to the number of plant pairs in herbivory, but not pollination, networks.
-Larger herbivory networks had higher values of $\beta_{distance}$ ($\beta_{size}$=2.58$\times$10$^{-4}$, $p$=0.011 for the full glm; herbivory networks are the baseline).
-Plant-pollinator networks had higher (less negative) slopes overall ($\beta_{pollinator}$=0.306, $p$\textless0.001 compared to the intercept value of -0.434 for herbivory networks).
-Plant-pollinator networks moreover showed a much weaker relationship between network size and the strength of the overlap-distance relationship ($\beta_{pollination:size}$=-2.64$\times$10$^{-4}$, $p$=0.009).
-After refitting the glm to the pollination networks alone, there was no significant relationship between network size and the slope of the overlap-distance relationship ($\beta_{size}$=-5.91$\times$10$^{-6}$, $p$=0.572).
+    in others (Fig.~\ref{within_network_regression}). Overlap of 
+    interaction partners decreased significantly with increasing 
+    phylogenetic distance in 7/11 herbivory networks and 33/59 
+    pollination networks. In the remaining four herbivory networks and 
+    25 of the 26 remaining pollination networks, overlap of interaction 
+    partners was not related to phylogenetic distance. Overlap of 
+    interaction partners increased with increasing phylogenetic distance 
+    in only a single pollination network.% (M_PL_026).
 
-    [[to SI?]]
-    Comparing the results in the observed networks to those obtained after permuting phylogenetic distances across pairs of plants, the observed slope of the relationship between phylogenetic distance and interaction partner overlap was always more extreme (i.e., always lesser or always greater) than that obtained in the permuted networks (Fig.~\ref{obs_vs_random}).
-Observed networks with a negative relationship between phylogenetic distance and overlap always had a more negative slope than that obtained from the permuted networks, while the 10 networks with positive relationships between phylogenetic distance and overlap always had more positive relationships than the permuted networks.
-This suggests that even in the networks with non-significant relationships between niche overlap and phylogenetic distance, the association between niche overlap and phylogenetic distance was not random.
+    The slope of the relationship between phylogenetic distance and 
+    overlap of interaction partners was related to the number of plant pairs 
+    in herbivory, but not pollination, networks. Larger herbivory networks 
+    had higher values of $\beta_{distance}$ 
+    ($\beta_{size}$=2.58$\times$10$^{-4}$, $p$=0.011 for the full glm; 
+    herbivory networks are the baseline). Plant-pollinator networks had 
+    higher (less negative) slopes overall ($\beta_{pollinator}$=0.306, 
+    $p$\textless0.001 compared to the intercept value of -0.434 for 
+    herbivory networks). Plant-pollinator networks moreover showed a 
+    much weaker relationship between network size and the strength of the 
+    overlap-distance relationship 
+    ($\beta_{pollination:size}$=-2.64$\times$10$^{-4}$, $p$=0.009). 
+    After refitting the glm to the pollination networks alone, there was 
+    no significant relationship between network size and the slope of 
+    the overlap-distance relationship ($\beta_{size}$=-5.91$\times$10$^{-6}$, 
+    $p$=0.572).
 
-    [[To SI.]]
-    Comparing the permuted networks to permutations of the permuted networks, the slope obtained from the initial permuted network showed no clear relationship to the slopes obtained from 500 permutations of the permuted network.
-Averaged over the 1000 permutations of each observed network, the slope of the permuted network was more extreme than 48.1-51.3\% of the permutations of the permuted network.
-This confirms that shuffling phylogenetic distances between plant pairs destroys the relationship between distance and interaction partner overlap, and that further shuffling distances does not have a predictable effect.
+    Comparing the results in the observed networks to those obtained after 
+    permuting phylogenetic distances across pairs of plants, the observed 
+    slope of the relationship between phylogenetic distance and interaction 
+    partner overlap was always more extreme (i.e., always lesser or always 
+    greater) than that obtained in the permuted networks (Fig.~\ref{obs_vs_random}).
+    Observed networks with a negative relationship between phylogenetic distance 
+    and overlap always had a more negative slope than that obtained from the 
+    permuted networks, while the 10 networks with positive relationships 
+    between phylogenetic distance and overlap always had more positive 
+    relationships than the permuted networks. This suggests that even in 
+    the networks with non-significant relationships between niche overlap 
+    and phylogenetic distance, the association between niche overlap and 
+    phylogenetic distance was not random. When the slopes of the permuted 
+    networks were compared to those obtained from permutations of the 
+    permuted networks, there was no relationship (\emph{Supporting 
+    information 2}).
 
@@
 
-\section*{Discussion} [[not updated post new results]]
+\section*{Discussion}
 
@@
   the probability of two plants sharing the same animal 
-  interaction partners decreased with increasing 
+  interaction partners generally decreased with increasing 
   phylogenetic distance. Considering networks separately,
-  $\approx$78\%  of the pollination and all of the 
+  $\approx$56\%  of the pollination and $\approx$64\% of the 
   herbivory networks exhibited the expected trend of decreasing 
-  overlap with increasing distance.
+  overlap with increasing distance. This variation between networks
+  echoes earlier studies (e.g.,~\citep{Fontaine2015,Hutchinson2017})
+  which also found broad evidence for phylogenetic conservation
+  of interaction partners despite variation between particular 
+  networks. 
+  % The lack of a relationship between phylogenetic
+  % distance and interaction partner overlap in many networks 
+  % could have several explanations. First, our dataset included
+  % many extreme specialists, especially among the pollination 
+  % networks. These species interact with only one plant and
+  % therefore weaken any signal of interaction partner overlap.
 
-  Within families, however, there was much greater variability. 
+  We found that the composition of plant families in a network
+  was not related to the slope of the relationship between phylogenetic
+  distance and interaction partner overlap. This suggests that 
+  conservation of interaction partners among closely related plants
+  (e.g., congeners or members of the same subfamilies) is more
+  important than phylogenetic signal from deeper within the phylognetic
+  tree. This echoes earlier results relating plant phylogeny to 
+  predation by particular insect species~\citep{Novotny2002,Novotny2004,
+  Odegaard2005} and in whole herbivory networks~\citep{Volf2017}. As
+  we did not find any relationship between the families present in
+  a network and the relationship between phylogenetic distance and
+  interaction partner overlap in pollination or herbivory networks,
+  the greater importance of shallow phylogeny may be a general 
+  feature of plant-insect interaction networks.
+
+  The variability of the relationship between partner overlap and
+  phylogenetic distance at the network level and the lack of influence
+  of community composition on the strength of this relationship could
+  be partly due to the different trends within families. 
   More than half of the plant families in each network type
@@
   phylogenetic distance is consistent with the idea that traits affecting 
-  interactions are heritable~\citep{Schemske1999} and changing gradually
+  interactions are heritable and change gradually
   such that closely related plants resemble their common ancestor--- and
-  each other ---more than they do distantly related plants. In some families, 
+  each other ---more than they do distantly related 
+  plants~\citep{Schemske1999,Gilbert2015,Ponisio2017}. In some families, 
   such as \emph{Asteraceae} in pollination networks, the positive slope of 
@@
   extremely steep. This could indicate different rates of phenotypic drift 
-  or evolution in different families.
+  or evolution in different families. Alternatively, key traits
+  affecting plant-insect interactions may not be strongly
+  conserved. Studies showing a stronger relationship between trait similarity
+  and shared interaction partners than phylogenetic similarity and shared
+  interaction partners suggest that traits may indeed be evolutionarily
+  labile~\citep{Junker2015,Ibanez2016,Endara2017}.
 
-  In contrast, \emph{Polygonaceae} in pollination networks and 
+  Moreover, \emph{Polygonaceae} in pollination networks and 
   \emph{Fabaceae} in herbivory networks showed the opposite 
-  pattern. In these families, closely-related plants had 
+  pattern to what we expected. In these families, closely-related plants had 
   \emph{lower} overlap than more distantly-related pairs of plants. 
@@
   specialise on their most profitable partner~\citep{Janz2006}. Second, this pattern 
-  could be the result of ecological or environmental filtering~\citep{Mayfield2009,Ackerly2010}. 
+  could be the result of ecological or environmental 
+  filtering~\citep{Ackerly2003,Mayfield2009}. 
   Closely-related species which have high degrees of overlap in their interaction 
@@
   Indeed, animal pollination and seed dispersal have been shown to act
-  as filters for several plant clades~\citep{Mayfield2009}.
-  Distantly-related plants with similar interaction partners,
-  on the other hand, may differ in some other aspect of their niches
-  and so be able to coexist. Plants sharing herbivores are unlikely to
-  compete for these interaction partners, but the presence of both
-  plants in a community could support higher herbivore populations
-  than could one species alone~\citep{Russell2007}. If the plants 
-  compete for some other resource, the combined impact of herbivory
-  and competition could eliminate the rarer plant species. Distantly-related
-  plants sharing herbivores, conversely, would be less likely to compete
-  for vital resources and more likely to persist.
+  as filters for several plant clades~\citep{Mayfield2009}, while selection to avoid 
+  competition and restriction on numbers of interaction partners may lead to
+  more intimate or specialised interactions~\citep{Ponisio2017}. This is
+  consistent with the relatively high proportion of extreme specialists we
+  observed in the pollination networks, which likely contributes to the weak
+  relationships between phylogenetic distance and interaction partner overlap
+  in many networks. Finally, although we do not have information about plants'
+  traits in these networks, it is possible that convergence or a high degree of
+  ancestral trait conservation has occurred
+  allowing distantly-related \emph{Polygonaceae} and \emph{Fabaceae} to
+  interact with the same insects.
 
@@
   or herbivory are not heritable in these groups~\citep{Kursar2009}
-  and that their phenotypes are constrained by other factors (e.g., 
-  drought tolerance), then we should not expect a relationship 
+  or their phenotypes are constrained by other factors (e.g., 
+  environmental conditions, trade-offs with other traits, ontogenic
+  change~\citep{Karinho2014}), then we should not expect a relationship 
   between phylogenetic distance and overlap of interaction partners.
@@
   relationships between overlap and phylogenetic distance.
-  Lastly, it is possible that the absence of a linear relationship 
-  between niche overlap and phylogenetic distance is because the data
-  actually exhibit a strongly non-linear one. This could result, for 
-  example, from an early burst of diversification followed by a period
-  of stasis~\citep{Davis2014}.
+  % Lastly, it is possible that the absence of a linear relationship 
+  % between niche overlap and phylogenetic distance is because the data
+  % actually exhibit a strongly non-linear one. This could result, for 
+  % example, from an early burst of diversification followed by a period
+  % of stasis~\citep{Davis2014}.
 
@@
   and herbivory networks, we can also contrast the 
-  trends in the two network types. In all five such cases, there was
-  a significant relationship between overlap and phylogenetic 
-  distance in only one network type (counting the singular 
-  relationships in \emph{Rubiaceae} in pollination networks as 
-  non-significant). This may indicate that one type of interaction
+  trends in the two network types. While \emph{Asteraceae} showed the
+  expected decrease in interaction partner overlap with increasing
+  phylogenetic distance, the other families showed different trends in
+  different network types. This may indicate that one type of interaction
   places greater constraints upon these families than the other. Plants
@@
   larger structure of the community. In one recent study, plants which are 
-  visited by many pollinators are also consumed by many herbivores~\citep{Sauve2015}.
+  visited by many pollinators are also consumed by many herbivores~\citep{Sauve2016}.
   This may be because pairing antagonistic and mutualistic interactions
@@
   phylogenetic distances between species, can affect the strength
-  of phylogenetic signal~\citep{Chamberlain2014a}. Our results 
-  emphasise the importance of considering conservation of interactions at multiple scales.
-  We hope that these results will help to guide future work investigating
-  the genetic and environmental drivers underpinning these relationships.
+  of phylogenetic signal~\citep{Chamberlain2014a}.
 
@@
 \renewcommand*{\bibfont}{\raggedright}
-\bibliography{noisn}
+\bibliography{manual}
 
@@
   \label{family_slopes_pp}
-  \begin{tabular}{|l  rr|}
+  \begin{tabular}{|l  rr|| l rr|}
     \hline
-    Family  & Change in log odds & $P$-value \\
+    Family  & Change in log odds & $P$-value & Family  & Change in log odds & $P$-value \\
     \hline
-    \emph{Adoxaceae} &  -65.8 & 0.163 \\
-    \emph{Amaryllidaceae} &  -17.9 & \textbf{0.015} \\
-    \emph{Apiaceae} &  10.9  & \textbf{0.006} \\
-    \emph{Apocynaceae} &  -6.96  & \textbf{0.037} \\
-    \emph{Asparagaceae} &  -6.23  & 0.189 \\
-    \emph{Asteraceae}* &  -1.47  & \textbf{\textless0.001} \\
-    \emph{Berberidaceae} &  -1.48$\times10^3$ & \textgreater0.999 \\
-    \emph{Boraginaceae} &  -5.15  & \textbf{\textless0.001} \\
-    \emph{Brassicaceae} &  -11.2 & 0.072 \\
-    \emph{Calceolariaceae} &  156 & 0.998 \\
-    \emph{Campanulaceae} &  334 & 0.999 \\
-    \emph{Caprifoliaceae} &  0.310 & 0.959 \\
-    \emph{Caryophyllaceae} &  2.09 & 0.644 \\
-    \emph{Cistaceae} &  -11.4 & \textbf{\textless0.001} \\
-    \emph{Convolvulaceae} &  -1.84  & 0.837 \\
-    \emph{Ericaceae} &  4.61 & 0.116 \\
-    \emph{Fabaceae}* &  -12.9 & \textbf{\textless0.001} \\
-    \emph{Geraniaceae} &  -3.31  & 0.624 \\
-    \emph{Hydrangeaceae} &  0.057 & 0.982 \\
-    \emph{Iridaceae} &  -27.9 & 0.078 \\
-    \emph{Lamiaceae} &  -5.01  & \textbf{\textless0.001} \\
-    \emph{Loasaceae} &  -865  & \textgreater0.999 \\
-    \emph{Malpighiaceae} &  2.80 & 0.168 \\
-    \emph{Malvaceae} &  -5.56  & 0.363 \\
-    \emph{Melastomataceae}* &  5.19 & 0.577 \\
-    \emph{Montiaceae} &  -1.12  & 0.870 \\
-    \emph{Myrtaceae} &  8.55 & 0.071 \\
-    \emph{Oleaceae} &  0.995 & 0.855 \\
-    \emph{Onagraceae} &  -556  & \textgreater0.999 \\
-    \emph{Orchidaceae} &  -14.5 & 0.145 \\
-    \emph{Orobanchaceae} &  24.2  & 0.326 \\
-    \emph{Papaveraceae} &  -11.2 & 0.511 \\
-    \emph{Phyllanthaceae} &  9.99 & 0.433 \\
-    \emph{Plantaginaceae} &  -8.48  & \textbf{0.001} \\
-    \emph{Poaceae}* &  69.2  & \textbf{0.003} \\
-    \emph{Polygonaceae} &  -14.8 & \textbf{\textless0.001} \\
-    \emph{Primulaceae} &  14.9  & 0.343 \\
-    \emph{Ranunculaceae} &  -38.0 & \textbf{\textless0.001} \\
-    \emph{Rosaceae} &  0.759 & 0.735 \\
-    \emph{Rubiaceae}* &  -13.0 & \textbf{0.026} \\
-    \emph{Salicaceae} &  -1.90  & 0.545 \\
-    \emph{Sapindaceae} &  821 & 0.999 \\
-    \emph{Saxifragaceae} &  -0.092  & 0.992 \\
-    \emph{Solanaceae} &  -21.9 & 0.189 \\
-    \emph{Tropaeolaceae} &  192 & 0.997 \\
-    \emph{Verbenaceae} &  -9.03  & 0.627 \\
-    \emph{Violaceae} &  -0.487  & 0.974 \\
+    \emph{Adoxaceae}  & -65.8 &  0.163  &     \emph{Melastomataceae}*   & 5.19  &  0.577 \\
+    \emph{Amaryllidaceae}   & -17.9 &  \textbf{0.015} &     \emph{Montiaceae}   & -1.12 &  0.870 \\
+    \emph{Apiaceae}   & 10.9  &  \textbf{0.006} &     \emph{Myrtaceae}  & 8.55  &  0.071 \\
+    \emph{Apocynaceae}  & -6.96 &  \textbf{0.037} &     \emph{Oleaceae}   & 0.995 &  0.855 \\
+    \emph{Asparagaceae}   & -6.23 &  0.189  &     \emph{Onagraceae}   & -556  &  \textgreater0.999 \\
+    \emph{Asteraceae}*  & -1.47 &  \textbf{\textless0.001}  &     \emph{Orchidaceae}  & -14.5 &  0.145 \\
+    \emph{Berberidaceae}  &   -1.48$\times10^3$   &  \textgreater0.999  &     \emph{Orobanchaceae}  & 24.2  &  0.326 \\
+    \emph{Boraginaceae}   & -5.15 &  \textbf{\textless0.001}  &     \emph{Papaveraceae}   & -11.2 &  0.511 \\
+    \emph{Brassicaceae}   & -11.2 &  0.072  &     \emph{Phyllanthaceae}   & 9.99  &  0.433 \\
+    \emph{Calceolariaceae}  & 156 &  0.998  &     \emph{Plantaginaceae}   & -8.48 &  \textbf{0.001} \\
+    \emph{Campanulaceae}  & 334 &  0.999  &     \emph{Poaceae}*   & 69.2  &  \textbf{0.003} \\
+    \emph{Caprifoliaceae}   & 0.31  &  0.959  &     \emph{Polygonaceae}   & -14.8 &  \textbf{\textless0.001} \\
+    \emph{Caryophyllaceae}  & 2.09  &  0.644  &     \emph{Primulaceae}  & 14.9  &  0.343 \\
+    \emph{Cistaceae}  & -11.4 &  \textbf{\textless0.001}  &     \emph{Ranunculaceae}  & -38 &  \textbf{\textless0.001} \\
+    \emph{Convolvulaceae}   & -1.84 &  0.837  &     \emph{Rosaceae}   & 0.759 &  0.735 \\
+    \emph{Ericaceae}  & 4.61  &  0.116  &     \emph{Rubiaceae}*   & -13 &  \textbf{0.026} \\
+    \emph{Fabaceae}*  & -12.9 &  \textbf{\textless0.001}  &     \emph{Salicaceae}   & -1.9  &  0.545 \\
+    \emph{Geraniaceae}  & -3.31 &  0.624  &     \emph{Sapindaceae}  & 821 &  0.999 \\
+    \emph{Hydrangeaceae}  & 0.057 &  0.982  &     \emph{Saxifragaceae}  & -0.092  &  0.992 \\
+    \emph{Iridaceae}  & -27.9 &  0.078  &     \emph{Solanaceae}   & -21.9 &  0.189 \\
+    \emph{Lamiaceae}  & -5.01 &  \textbf{\textless0.001}  &     \emph{Tropaeolaceae}  & 192 &  0.997 \\
+    \emph{Loasaceae}  & -865  &  \textgreater0.999  &     \emph{Verbenaceae}  & -9.03 &  0.627 \\
+    \emph{Malpighiaceae}  & 2.8 &  0.168  &     \emph{Violaceae}  & -0.487  &  0.974 \\
+    \emph{Malvaceae}  & -5.56 &  0.363  &   &   & \\
   \hline
@@
     We were able to fit these models to 47 plant families (see \emph{Materials and Methods} for details). 
-    Families \\ marked with an asterisk were also sufficiently diverse in herbivory networks. 
-    Statistically significant values \\ are indicated in bold.
+    Families marked with an asterisk were also sufficiently diverse to model in herbivory networks. 
+    Statistically significant values are indicated in bold.
 

### 2019-05-23 manuscript/supporting_info.tex
checked bib, ready to send out revamped discussion

@@
 
-\author{Alyssa R. Cirtwill$^{1}$, Giulio V. Dalla Riva$^{2}$, Nick J. Baker$^{1}$,\\
- Joshua A. Thia$^{1,3}$, Christie J. Webber$^{1}$, Daniel B. Stouffer$^{1}$, MSC helpers from Linkoping}
+\author{Alyssa R. Cirtwill$^{1,2}$, Giulio V. Dalla Riva$^{3}$, Nick J. Baker$^{1}$,\\
+Mikael Ohlsson$^{4}$, Isabelle Norstr\"{o}m$^{4}$, Inger-Marie Wohlfarth Hasle$^{4}$,\\
+Joshua A. Thia$^{1,5}$, Christie J. Webber$^{1}$, Daniel B. Stouffer$^{1}$}
 \date{\small$^1$Centre for Integrative Ecology, School of Biological Sciences\\
-    \medskip$^2$Biomathematics Research Centre, School of Mathematics and Statistics\\
+\medskip$^2$Department of Ecology,\\
+Environment, and Plant Sciences (DEEP)\\
+Stockholm University\\
+114 19 Stockholm, Sweden\\
+\medskip$^3$Biomathematics Research Centre, School of Mathematics and Statistics\\
 University of Canterbury\\Private Bag 4800\\
 Christchurch 8140, New Zealand\\
-\medskip$^3$Present Address: School of Biological Sciences\\
+\medskip$^4$Department of Physics, Chemistry, and Biology (IFM)\\ Link\"{o}ping University\\ 581 83 Link\"{o}ping, Sweden\\
+\medskip$^5$Present Address: School of Biological Sciences\\
 University of Queensland\\Brisbane, QLD 4072, Australia }
@@
     \begin{center}
-    \begin{tabular}{|l l m{6cm} |}
+    \begin{tabular}{|l l m{10cm} |}
     \hline
@@
     M\_PL\_016  & Pollination & \citep{Herrera1988} \\
-    M\_PL\_017  & Pollination & \citep{Memmott1999} \\
+    M\_PL\_017  & Pollination & \citep{Memmott2002} \\
     M\_PL\_018  & Pollination & Olesen, J. M. Unpublished.  \\
@@
     M\_PL\_020  & Pollination & \citep{Kevan1970} \\
-    M\_PL\_021  & Pollination & \citep{Kato1999}  \\
+    M\_PL\_021  & Pollination & \citep{Kato1990}  \\
     M\_PL\_022  & Pollination & \citep{Medan2002} \\
@@
     M\_PL\_048  & Pollination & \citep{Dupont2009a}  \\
-    M\_PL\_049  & Pollination & \citep{Beks2006}  \\
+    M\_PL\_049  & Pollination & \citep{Bek2006}  \\
     M\_PL\_050  & Pollination & \citep{Stald2003} \\
@@
     M\_PL\_059  & Pollination & \citep{Bezerra2009} \\
-    Basset  & Herbivory & \citep{Basset1999}  \\
+    Basset  & Herbivory & \citep{Basset1996}  \\
     Bluthgen  & Herbivory & \citep{Bluthgen2006}  \\
@@
     Novotny & Herbivory & \citep{Novotny2012} \\
-    Peralta & Herbivory & \citep{Peralta2015} \\
+    Peralta & Herbivory & \citep{Peralta2016} \\
     Sheldon & Herbivory & \citep{Sheldon1978} \\
@@
 \section*{Supporting information 2: Distributions of $p$-values for permuted networks}
+
+    Comparing the permuted networks to permutations of the permuted networks, the slope obtained from the initial permuted network showed no clear relationship to the slopes obtained from 500 permutations of the permuted network.
+Averaged over the 1000 permutations of each observed network, the slope of the permuted network was more extreme than 48.1-51.3\% of the permutations of the permuted network.
+This confirms that shuffling phylogenetic distances between plant pairs destroys the relationship between distance and interaction partner overlap, and that further shuffling distances does not have a predictable effect.
 

### 2019-05-23 code/create_figures/pval_test_observed.py

@@ -113,7 +113,7 @@ def main():
   # grace.set_label_scheme("dummy")
   for i in range(0,12):
   	keys=sorted(pps)[i*5:i*5+5]
-  	print i, len(keys)
+  	# print i, len(keys)
 	graph=grace.add_graph(Panel)
 	graph=format_graph(graph)
 	j=0
@@ -126,7 +126,7 @@ def main():
   		keys.append(sorted(phs)[-1])
   	elif i==2:
   		keys=[]
-  	print i,len(keys)
+  	print i,keys
 	graph=grace.add_graph(Panel)
 	graph=format_graph(graph)
 	j=0

### 2019-05-23 code/create_figures/regression_line_plot.py

@@ -37,15 +37,6 @@ def signalreader(datapath,suffix):
 
   return databank
 
-def simlines(inter,beta):
-  simdata=[]
-  for i in range(0,101):
-    x=float(i)/100
-    y=inter+x*beta
-    logity=1/(1+math.exp(0-y))
-    simdata.append((x,logity))
-  return simdata
-
 def simlines_scaled(inter,beta):
   simdata=[]
   for i in range(0,80):
@@ -62,8 +53,6 @@ def lineplotter(datapath,modeltype,colormode):
   # dummy=['Total overlap','Partial overlap','No overlap','','','']
   if modeltype=='scaled':
     suffix='_reg_unranked_scaled'
-  else:
-    suffix='_reg'
 
   graphtype='full'
   if colormode=='grey':
@@ -80,29 +69,17 @@ def lineplotter(datapath,modeltype,colormode):
     graph=grace.add_graph(Panel)
 
     fdatabank=databank['fixef']
-    if modeltype=='ranked':
-      # Mean lines useful for all graphs
-      # First let's just show the overall effect for pp webs
-      ppinter=fdatabank['(Intercept)']+fdatabank['nettypepp'] #Because R loves to alphabetise :(
-      ppbeta=fdatabank['rankdist']+fdatabank['rankdist:nettypepp']
-      pp_simdata=simlines(ppinter,ppbeta)
 
-      # Now add the overall effect for ph webs
-      phinter=fdatabank['(Intercept)']
-      phbeta=fdatabank['rankdist']
-      ph_simdata=simlines(phinter,phbeta)
+    ppinter=fdatabank['(Intercept)']+fdatabank['nettypepp'] #Because R loves to alphabetise :(
+    ppbeta=fdatabank['scale(distance)']+fdatabank['scale(distance):nettypepp']
+    pp_simdata=simlines_scaled(ppinter,ppbeta)
+    print('pp lines ok')
 
-    elif modeltype=='scaled':
-      ppinter=fdatabank['(Intercept)']+fdatabank['nettypepp'] #Because R loves to alphabetise :(
-      ppbeta=fdatabank['scale(distance)']+fdatabank['scale(distance):nettypepp']
-      pp_simdata=simlines_scaled(ppinter,ppbeta)
-      print('pp lines ok')
-
-      # Now add the overall effect for ph webs
-      phinter=fdatabank['(Intercept)']
-      phbeta=fdatabank['scale(distance)']
[…]

### 2019-06-03 manuscript/coverletter_resub.tex
revising coverletter

\documentclass[12pt]{letter}

% \usepackage[britdate]{canterbury-letter}
\usepackage[britdate]{SU-letter}
\usepackage{times}
\usepackage{letterbib}
\usepackage{geometry}
\usepackage[round]{natbib}
\usepackage{graphicx}
\geometry{a4paper}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage[running]{lineno}
\usepackage{amsmath,amsfonts,amssymb}
% \usepackage[margin=10pt,font=small,labelfont=bf]{caption}

%\usepackage{natbib}
% \bibpunct[; ]{(}{)}{;}{a}{,}{;}

\newenvironment{refquote}{\bigskip \begin{it}}{\end{it}\smallskip}

\newenvironment{figure}{}

\position{Postdoctoral fellow}
\department{Department of Ecology, Environment, and Plant Sciences (DEEP)}
\location{Stockholm University}
\cityzip{Stockholm, Sweden}
\telephone{}
\fax{}
\email{alyssa.cirtwill@liu.se}
\url{http://cirtwill.github.io}
\name{Dr. Alyssa R. Cirtwill}

\newcommand{\myjournal}{\emph{New Phytologist}}

\begin{document}

\begin{letter}{\bf Professor Alistair M. Hetherington\\
               Editor-in-Chief, New Phytologist\\
               School of Biological Sciences\\
               University of Bristol\\
               Bristol BS8 1TQ, UK
                               }

% Borrowing heavily from the proposal

\opening{Dear Prof. Hetherington:}

	My co-authors and I are pleased to submit our manuscript for consideration as a research article in \textbf{New Phytologist}.

	\begin{enumerate}

	\item What hypotheses or questions does this work address?
		\smallskip

		We test whether	more closely-related plants tend to share more pollinators and/or herbivores using a set of published plant-insect networks. We test this hypothesis both across whole communities and within plant families co-occurring in a community. We link the two scales of inquiry by investigating whether the strength of the whole-community relationship is related to the families present in the community.

		\smallskip

		\item How does this work advance our current understanding of plant science?
		\smallskip

		By combining community-scale and family-scale analyses, we gain a richer and more detailed picture of the ways in which plant-animal interactions are structured with respect to evolutionary history. In particular, while we found that more closely-related plants do generally tend to share more interaction partners, we demonstrate the variety of patterns of conservation across families. This variability may help to explain the mixed results from earlier studies, especially those considering only a single network.

		\smallskip

		\item Why is this work important and timely?
		\smallskip

		[[Not sure this is the best angle.]]
		Plants' interactions with animals can significantly affect their fitness, both positively and negatively. These interactions might be conserved through stabilising selection or if key traits affecting the interactions are highly heritable, or they might not be if there is selection to avoid overlap with close relatives or if distant relatives converge. By comparing plant families displaying different patterns of conservation of these interactions, we can predict which families may experience different types of selection pressures. Thus, we can use ecological data to guide future evolutionary research.

	\end{enumerate}

	Note that we submitted an earlier version of this manuscript to New Phytologist, for which the revision period expired in August 2017. We now use a different methodology from that presented in the initial submission, and we are happy to have the current version stand on its own merits as a new initial submission. We hope that you will agree that the question we investigate remains of interest to the readership of \textbf{New Phytologist}.

    % My co-authors and I are pleased to resubmit a second revision of our manuscript  MEE-18-07-452:  \emph{A quantitative framework for investigating the reliability of empirical network construction} for consideration as a research article in \textbf{Methods in Ecology and Evolution}. Dr. Aaron Ellison, Senior Editor, noted that the reviewer who provided additional feedback was very positive about our revision but requested more discussion about prior choice. We have expanded our discussion to emphasise the need for careful prior selection and now refer to a demonstration of problems that can result from a poorly-chosen prior. We believe that these additions, although slightly exceeding the normal length restrictions of \textbf{Methods in Ecology and Evolution}, have improved the manuscript enough to justify the extra length. We thank the Editor for his encouragement and the Reviewer for his further thoughtful feedback.

    % Note that we uploaded an earlier version of this manuscript to biorXiv \\(doi: \emph{https://doi.org/10.1101/332536}). We have uploaded a copy of this version as CI\_preprint.pdf. The present version has been substantially re-organised and contains additional material not included in the pre-print.

    % We appreciate the opportunity to resubmit a further revision of our manuscript and thank you for your continued consideration. We remain confident that our manuscript will be of broad interest to the readers of \textbf{Methods in Ecology and Evolution}. We hope that you agree and eagerly await your reply.

\closing{Best regards,}

\end{letter}
\end{document}

### 2019-06-11 manuscript/phylogenetic_signal_manuscript.tex
some DBS edits and comments

@@
           networks.  We then tested for relationships between phylogenetic 
-          distance and overlap within each network, and whether these 
+          distance and partner overlap within each network, and whether these 
           relationships varied with the composition of the plant community.
@@
           interaction partners in different plant families likely
-          reflects a variety of ecological and evolutionary processes. To 
+          reflects a comparable variety of ecological and evolutionary processes. To 
           understand the distribution of interactions within a community, 
@@
 This will probably make it quite hard to argue novelty.
+
+\textbf{DBS: }
 
@@
   Further, the plant and animal components of networks can show different degrees of phylogenetic conservation of interaction partners.
-In mutualistic networks, animals often show a stronger phylogenetic signal in their partners than plants~\citep{Rezende2007a,Chamberlain2014,Rohr2014,Vamosi2014,Lind2015,Fontaine2015} (but see~\citep{Rafferty2013} for a counterexample).
+In mutualistic networks, animals often show a stronger phylogenetic signal in their partners than do plants~\citep{Rezende2007a,Chamberlain2014,Rohr2014,Vamosi2014,Lind2015,Fontaine2015} (but see~\citep{Rafferty2013} for a counterexample).
 In antagonistic networks, however, actively-foraging consumers tend to show less phylogenetic signal than their prey~\citep{Ives2006,Cagnolo2011,Naisbit2011,Fontaine2015}.
-Thus, it is not straightforward to assume that interactions will be similar among related species.
+Thus, it is not straightforward to assume that interactions will always be similar among related species.
 [[GVDR was skeptical of a similar point in the previous draft - less contentious now?]]
@@
   signal across entire networks, we take a pairwise perspective in
-  order to ontain a more detailed picture of how plant phylogeny
+  order to obtain a more detailed picture of how plant phylogeny
   relates to network structure. Specifically,
@@
   community, and whether the relationship between niche overlap and 
-  phylogenetic distance differs across plant families.
+  phylogenetic distance differs systematically across plant families.
 
@@
 
-  We studied tested for phylogenetic signal in niche overlap within a 
+  We tested for phylogenetic signal in niche overlap within a 
   set of 59 pollination and 11 herbivory networks. These networks span 
@@
 
-  We then estimated phylogenetic distances between species. To accomplish 
+  We then estimated phylogenetic distances between the remaining species. To accomplish 
   this, we constructed a phylogenetic tree for our dataset based on a dated
@@
   phylogenetic distances between them. For this reason, we excluded comparisons 
-  between pairs of non-angiosperms from our analyses. As only two networks (both 
+  between pairs of non-angiosperms from our subsequent analyses. As only two networks (both 
   herbivory networks) included more than one such species and non-angiosperms
@@
   shared interaction partners for for species $i$ and $j$ and is defined as: 
-
+%
   \begin{equation}
@@
   \end{equation}
-
+%
   where $M_{ij}$ is the set of \emph{mutual} (shared) interaction partners of 
@@
   sharing most of their interaction partners over specialists sharing a single 
-  interaction partner). We therefore recorded, for each species, the number of 
-  shared interaction partners $M_{ij}$ and the number of interaction partners 
-  for each species pair that were not shared 
-  ($U_{ij}$ = $P_{i}$+$P_{j}$-2$M_{ij}$). Instead of a single index $J_{ij}$ 
-  we therefore keep track of the information needed to compute
-  niche between species $i$ and $j$ as a tuple: ($M_{ij}$, $U_{ij}$).
+  interaction partner). For each species pair, we therefore recorded the number of 
+  shared interaction partners ($M_{ij}$) and the number of interaction partners 
+  that were not shared 
+  ($U_{ij}$ = $P_{i}$+$P_{j}$-2$M_{ij}$). Instead of a single index $J_{ij}$, 
+  we thus kept track of the full information needed to compute
+  niche overlap between species $i$ and $j$ as a tuple: ($M_{ij}$, $U_{ij}$).
 
@@
   approach is conceptually similar to modelling successes and failures in a 
-  binomial-distributed process. Accordingly, we assumed a binomial 
-  distribution for residuals and used a logit link function to model the 
+  binomial-distributed process. Accordingly, we assumed a binomially-  distributed error structure and used a logit link function to model the 
   probability $\omega_{ij}$ of plants $i$ and $j$ sharing an interaction 
@@
   took the form
-
+%
     \begin{equation}
-      \omega_{ij} \propto \beta_{distance}\delta_{ij} ,
+      {\rm logit}\left(\omega_{ij}\right) \propto \beta_{distance}\delta_{ij} ,
       \label{basic}
     \end{equation}
-
+%
   where $\delta_{ij}$ is the phylogenetic distance between plants $i$ and 
@@
   \emph{lme4}~\citep{lme4} and took the form
-
+%
     \begin{equation}
-      \omega_{ij} \propto \beta_{distance} \delta_{ij} + \beta_{pollination} I_{ij} + \beta_{distance:pollination} \delta_{ij} I_{ij} ,
+      {\rm logit}\left(\omega_{ij}\right) \propto \beta_{distance} \delta_{ij} + \beta_{pollination} I_{ij} + \beta_{distance:pollination} \delta_{ij} I_{ij} ,
     \end{equation}
-
+%
   where $I_{ij}=1$ when plants $i$ and $j$ are drawn from a 
@@
   alternative hypothesis was set farther from zero.
-[[Is this cogent?
+  % [[Is this cogent?
 Correct?
@@
 It may not be an issue since we've moved away from the motif-like measures.]]
+  % DBS: I think it's fine.
 
-  To test whether the relationship between phylogenetic distance and niche overlap depended on network size, we fit a general linear model for the slope of this relationship in the glm models against the number of plant pairs for which distances could be calculated (hereafter ``network size"), network type (again using herbivory networks as a baseline), and their interaction:
-
+  To test whether the relationship between phylogenetic distance and niche overlap depended on network size, we fit a general linear model for the slope of this relationship inferred from the glm models against the number of plant pairs for which distances could be calculated (hereafter ``network size"), network type (again using herbivory networks as a baseline), and their interaction:
+%
     \begin{equation}
@@
     \end{equation}
-
+%
   where $\eta_{N}$ is the number of plant pairs in network $N$ for which distances could be calculated, $I_N$ is an indicator equal to 1 if network $N$ is a pollination network and 0 otherewise.
@@
   log odds of two plants in a given network sharing an interaction 
-  partner per million years of divergence (i.e., the slope from the 
+  partner per million years of divergence (i.e., the slope $\beta_{distance}$ from the 
   regression of niche overlap against phylogenetic distance within
@@
   we used Bray-Curtis dissimilarity to define differences in plant
-  community composition. Bray-Curtwis dissimilarity considers only
+  community composition. Bray-Curtis dissimilarity considers only
   those plant families which appear in at least one of a pair of
@@
   community composition, we stratified these permutations
-  by network type. That is, the change in log odds for a pollination
+  by network type. That is, the response variable of change in log odds for a pollination
   network could only be exchanged for that of another pollination
@@
     relationships than the permuted networks. This suggests that even in 
-    the networks with non-significant relationships between niche overlap 
-    and phylogenetic distance, the association between niche overlap and 
+    the networks with non-significant relationships, the association between niche overlap and 
     phylogenetic distance was not random. When the slopes of the permuted 
     networks were compared to those obtained from permutations of the 
-    permuted networks, there was no relationship (\emph{Supporting 
+    permuted networks, there was no relationship, which speaks to the robustness of our methodology (\emph{Supporting 
     information 2}).
@@
 Of the 200 families in our dataset, only 29 were represented by more than 20 species.
-Lumping all other families into an "other" category and repeating the PERMANOVA, we still did not find a significant relationship between slope and community composition ($F_{1,68}$=1.12, $p$=0.409).
+Lumping all other families into an ``other'' category and repeating the PERMANOVA, we still did not find a significant relationship between slope and community composition ($F_{1,68}$=1.12, $p$=0.409).
     % Also performed a CCA to see which fams had most positive/negative associations, but with non-sig results I don't think it's interesting.
@@
     Considering each family separately, the relationship between within-family niche overlap and phylogenetic distance varied widely in both pollination and herbivory networks. 
-    For the families
+    For the 47 families % DBS: Alyssa, please check this number!
     that were well represented in pollination networks, overlap decreased
@@
     a further 15 plant families. Finally, the overlap between pairs of \emph{Polygonaceae}
+    % DBS: According to the table, this should probably be Apiaceae and Poaceae. Please check.
     increased with increasing phylogenetic distance. 
@@
 The model for \emph{Sapindaceae} in pollination networks did converge.
+
+    % DBS: The section above seems like it would fit better in the Methods and then we just say nothing about these families.
 
@@
   overlap with increasing distance. This variation between networks
-  echoes earlier studies (e.g.,~\citep{Fontaine2015,Hutchinson2017})
+  echoes earlier studies \citep[e.g.,][]{Fontaine2015,Hutchinson2017}
   which also found broad evidence for phylogenetic conservation
@@
 
-  For those families which were well-represented in both pollination
+  For those few families which were well-represented in \emph{both} pollination
   and herbivory networks, we can also contrast the 
@@
 There was substantial variation among networks (thin, pale lines) of both types.
-The slope of the regression for each network was significantly more extreme than that obtained from 999 permutatations of that network (slopes obtained from the permuted networks ranged between -1.34$\times10^{-12}$ and 9.19$\times10*{-13}$).}
+The slope of the regression for each network was significantly more extreme than that obtained from 999 permutatations of that network (slopes obtained from the permuted networks ranged between -1.34$\times10^{-12}$ and 9.19$\times10^{-13}$).}
     \label{within_network_regression} 
@@
      partners and phylogenetic distance.
+     % DBS: The above is near indecipherable. Can we please simplify it substantially?
      Families in pollination networks are indicated
@@
      The phylogenetic tree below the plots indicates the
-     relatedness between plant families. Error bars represent 95\% confidence
+     relatedness between these plant families. Error bars represent 95\% confidence
      intervals.}

### 2019-06-24 code/create_figures/regression_line_plot.py
attempting to adjust figure, relies on data not included in minimal git repo

@@ -47,21 +47,39 @@ def simlines_scaled(inter,beta):
     simdata.append((dist,logity))
   return simdata
 
-def lineplotter(datapath,modeltype,colormode):
-  # dummy=[r"\| \|",r"\|\\\|",r"\|,X\|"]
-  dummy=['Plant-herbivore networks','Plant-pollinator networks','','','','']
-  # dummy=['Total overlap','Partial overlap','No overlap','','','']
-  if modeltype=='scaled':
-    suffix='_reg_unranked_scaled'
+def format_graph(rowtype,graph,colormode):
 
   graphtype='full'
-  if colormode=='grey':
-    grace=MultiPanelGrace(colors=ColorBrewerScheme('Greys'))
-  else:
-    grace=MultiPanelGrace(colors=ColorBrewerScheme('PRGn'))
 
-  grace.add_label_scheme("dummy",dummy)
-  grace.set_label_scheme("dummy")
+  if rowtype=='ph':
+    ytext='Proportion of shared herbivores'
+  else:
+    ytext='Proportion of shared pollinators'
+
+  graph.yaxis.configure(text=ytext,char_size=0.5,just=2)
+  graph.world.xmax=800
+  major=200
+  prec=0
+
+  graph.world.ymax=0.60000000001
+  graph.yaxis.tick.configure(place='both',major_size=.4,minor_ticks=1,minor_size=.2,major=.2,major_linewidth=1,minor_linewidth=1)
+
+  graph.yaxis.ticklabel.configure(char_size=.75,format='decimal',prec=1)
+  graph.xaxis.tick.configure(place='both',major_size=.4,minor_ticks=1,minor_size=.2,major=major,major_linewidth=1,minor_linewidth=1)
+  graph.xaxis.ticklabel.configure(char_size=.75,format='decimal',prec=prec)
+
+  graph.frame.linewidth=1
+  graph.xaxis.bar.linewidth=1
+  graph.yaxis.bar.linewidth=1
+  
+  graph.panel_label.configure(char_size=.85,placement='iuc',dy=0.01,dx=0,just=2)
+
+  return graph
+
+def lineplotter(grace,datapath,modeltype,colormode):
+
+  if modeltype=='scaled':
+    suffix='_reg_unranked_scaled'
 
   for rowtype in ['ph','pp']:
     # Looks like these are supposed to be overall regs?
@@ -127,26 +145,35 @@ def lineplotter(datapath,modeltype,colormode):
[…]

### 2019-06-24 code/create_figures/regression_line_plot.py
reformatted Fig. 1

@@ -25,7 +25,7 @@ def signalreader(datapath,suffix):
       effect=float(line.split()[1])
       databank['fixef'][name]=effect
   f.close()
-
+ 
   ran=open(datapath+suffix+'_ranef.tsv','r')
   for line in ran:
     if len(line.split())==3:
@@ -47,8 +47,8 @@ def simlines_scaled(inter,beta):
     simdata.append((dist,logity))
   return simdata
 
-def format_graph(rowtype,graph,colormode):
-
+def format_graph(graph,rowtype,colormode):
+  print rowtype
   graphtype='full'
 
   if rowtype=='ph':
@@ -56,7 +56,7 @@ def format_graph(rowtype,graph,colormode):
   else:
     ytext='Proportion of shared pollinators'
 
-  graph.yaxis.configure(text=ytext,char_size=0.5,just=2)
+  graph.yaxis.label.configure(text=ytext,char_size=0.85,just=2)
   graph.world.xmax=800
   major=200
   prec=0
@@ -78,13 +78,13 @@ def format_graph(rowtype,graph,colormode):
 
 def lineplotter(grace,datapath,modeltype,colormode):
 
-  if modeltype=='scaled':
-    suffix='_reg_unranked_scaled'
+  suffix='_reg_unranked_scaled'
 
   for rowtype in ['ph','pp']:
     # Looks like these are supposed to be overall regs?
     databank=signalreader(datapath,suffix)
     graph=grace.add_graph(Panel)
+    graph=format_graph(graph,rowtype,colormode)
 
     fdatabank=databank['fixef']
 
@@ -131,26 +131,23 @@ def lineplotter(grace,datapath,modeltype,colormode):
           else:
             dat.line.configure(linestyle=1,linewidth=1,color=10)
 
-    for dataset in [eval(rowtype+'_simdata')]:
-      if colormode=='grey':
-        if dataset==pp_simdata:
-          linecol=9
-        else:
-          linecol=9
-      else:
-        if dataset==pp_simdata:
-          linecol=2
-        else:
-          linecol=11
-      dat=graph.add_dataset(dataset)
-      dat.symbol.shape=0
-      dat.line.configure(linestyle=1,linewidth=4,color=linecol)
-      graph=format_graph(graph,rowtype,colormode)
+    # Add thick overall lines
+	for dataset in [eval(rowtype+'_simdata')]:
+	  if colormode=='grey':
[…]

### 2019-06-24 code/create_figures/observed_vs_random_slopes.py
reconfigured Figs. 1 and 2

@@ -14,6 +14,8 @@ from PyGrace.drawing_objects import DrawText, DrawLine
 from PyGrace.Extensions.distribution import CDFGraph, PDFGraph
 from PyGrace.Extensions.latex_string import LatexString, CONVERT
 
+from regression_line_plot import signalreader
+
 
 def read_regfile(regfile):
   obslopes={'pp':[],'ph':[]}
@@ -41,7 +43,7 @@ def read_regfile(regfile):
 def format_graph(graph,nettype):
 
   graph.world.ymin=-.600000000001
-  graph.world.ymax=.2
+  graph.world.ymax=.25
   graph.yaxis.tick.configure(place='both',major_size=.4,minor_ticks=1,minor_size=.2,major=.2,major_linewidth=1,minor_linewidth=1)
   graph.yaxis.ticklabel.configure(char_size=.75,format='decimal',prec=1)
   graph.yaxis.bar.linewidth=1
@@ -54,13 +56,13 @@ def format_graph(graph,nettype):
   graph.frame.linewidth=1
   graph.xaxis.bar.linewidth=1
   
-  graph.panel_label.configure(char_size=.85,placement='ouc',dy=0.01,dx=0,just=2)
+  graph.panel_label.configure(char_size=.85,placement='iuc',dy=0.01,dx=0,just=2)
 
   return graph
 
-def grace_setup(obsslopes,ranslopes):
+def grace_setup(obsslopes,ranslopes,slopedict):
   # dummy=[r"\| \|",r"\|\\\|",r"\|,X\|"]
-  dummy=['PH','PP','','','','']
+  dummy=['Plant-herbivore','Plant-pollinator','','','','']
   # dummy=['Total overlap','Partial overlap','No overlap','','','']
   grace=MultiPanelGrace(colors=ColorBrewerScheme('PRGn'))
 
@@ -70,20 +72,20 @@ def grace_setup(obsslopes,ranslopes):
   for nettype in ['ph','pp']:
     graph=grace.add_graph(Panel)
     graph=format_graph(graph,nettype)
-    graph=lineplotter(graph,obsslopes[nettype],ranslopes[nettype],nettype)
+    graph=lineplotter(graph,obsslopes[nettype],ranslopes[nettype],nettype,slopedict)
 
   grace.multi(rows=1,cols=2,hgap=.05,vgap=.04)
   grace.hide_redundant_labels()
   # grace.hide_redundant_labels()
[…]

### 2019-06-24 code/create_figures/regression_line_plot.py

@@ -158,7 +158,7 @@ def main():
     grace=MultiPanelGrace(colors=ColorBrewerScheme('PRGn'))
 
   # dummy=[r"\| \|",r"\|\\\|",r"\|,X\|"]
-  dummy=['Plant-herbivore networks','Plant-pollinator networks','','','','']
+  dummy=['Plant-herbivore','Plant-pollinator','','','','']
   # dummy=['Total overlap','Partial overlap','No overlap','','','']
 
 

### 2019-06-24 code/Jaccard_regressions.R
updated figures 1 and 2, still need to double-check familywise results

@@ -52,5 +52,17 @@ outtab$Jaccard_slope=as.numeric(as.character(outtab$Jaccard_slope))
 outtab$Jaccard_p=as.numeric(as.character(outtab$Jaccard_p))
 outtab$Sorenson_slope=as.numeric(as.character(outtab$Sorenson_slope))
 outtab$Sorenson_p=as.numeric(as.character(outtab$Sorenson_p))
-
+outtab$nettype=c(rep('PH',11),rep('PP',59))
+outtab$nettype=as.factor(outtab$nettype)
+outtab$n_pairs=as.numeric(as.character(outtab$n_pairs))
 # I think it may be best to make observed slopes, random slopes, and random-random slopes separately?
+
+
+slope_test=with(outtab,glm(Jaccard_slope~nettype*n_pairs))
+pval_test=with(outtab,glm(Jaccard_p~nettype*n_pairs))
+pptab=outtab[which(outtab$nettype=='PP'),]
+# Significant positive effect of size and negative interaction with nettype==PP
+PP_slope_test=with(pptab,glm(Jaccard_slope~n_pairs))
+PP_pval_test=with(pptab,glm(Jaccard_p~n_pairs))
+
+

### 2019-06-24 code/create_figures/regression_line_plot.py

@@ -105,7 +105,6 @@ def lineplotter(grace,datapath,modeltype,colormode):
         nettype='pp'
       else:
         nettype='ph'
-
       if nettype==rowtype:
         if nettype=='pp':
           inter=ppinter+databank['ranef'][network][0]

### 2019-06-25 manuscript/phylogenetic_signal_manuscript.tex
beginning to address DBS comments
double-checked family-wise results in main text

@@
     alternative hypothesis was set farther from zero.
-  % [[Is this cogent?
-Correct?
-If not, I think I will have to remove all reference to type II error and hope we don't get the same reviewer again.
-It may not be an issue since we've moved away from the motif-like measures.]]
-  % DBS: I think it's fine.
 
@@
 
+    Models for two families did not converge.
+In both the \emph{Lauraceae}, (represented by four species in one pollination network) and the \emph{Sapindaceae} in herbivory networks (represented by five species in one network), one pair of species shared a single interaction partner while all other pairs did not share any interaction partners.
+The model for \emph{Sapindaceae} in pollination networks did converge.
+
 \section*{Results}
@@
     Considering each family separately, the relationship between within-family niche overlap and phylogenetic distance varied widely in both pollination and herbivory networks. 
-    For the 47 families % DBS: Alyssa, please check this number!
-    that were well represented in pollination networks, overlap decreased
+    For the 48 families that were well represented in pollination networks, overlap decreased
     with increasing phylogenetic distance in 18 (Table~\ref{family_slopes_pp}).
@@
     increasing phylogenetic distance.
-
-    Models for two families did not converge.
-In both the \emph{Lauraceae}, (represented by four species in one pollination network) and the \emph{Sapindaceae} in herbivory networks (represented by five species in one network), one pair of species shared a single interaction partner while all other pairs did not share any interaction partners.
-The model for \emph{Sapindaceae} in pollination networks did converge.
-
-    % DBS: The section above seems like it would fit better in the Methods and then we just say nothing about these families.
 
@@
     \hline
-    \emph{Adoxaceae}  & -65.8 &  0.163  &     \emph{Melastomataceae}*   & 5.19  &  0.577 \\
-    \emph{Amaryllidaceae}   & -17.9 &  \textbf{0.015} &     \emph{Montiaceae}   & -1.12 &  0.870 \\
-    \emph{Apiaceae}   & 10.9  &  \textbf{0.006} &     \emph{Myrtaceae}  & 8.55  &  0.071 \\
-    \emph{Apocynaceae}  & -6.96 &  \textbf{0.037} &     \emph{Oleaceae}   & 0.995 &  0.855 \\
-    \emph{Asparagaceae}   & -6.23 &  0.189  &     \emph{Onagraceae}   & -556  &  \textgreater0.999 \\
-    \emph{Asteraceae}*  & -1.47 &  \textbf{\textless0.001}  &     \emph{Orchidaceae}  & -14.5 &  0.145 \\
-    \emph{Berberidaceae}  &   -1.48$\times10^3$   &  \textgreater0.999  &     \emph{Orobanchaceae}  & 24.2  &  0.326 \\
-    \emph{Boraginaceae}   & -5.15 &  \textbf{\textless0.001}  &     \emph{Papaveraceae}   & -11.2 &  0.511 \\
-    \emph{Brassicaceae}   & -11.2 &  0.072  &     \emph{Phyllanthaceae}   & 9.99  &  0.433 \\
-    \emph{Calceolariaceae}  & 156 &  0.998  &     \emph{Plantaginaceae}   & -8.48 &  \textbf{0.001} \\
-    \emph{Campanulaceae}  & 334 &  0.999  &     \emph{Poaceae}*   & 69.2  &  \textbf{0.003} \\
-    \emph{Caprifoliaceae}   & 0.31  &  0.959  &     \emph{Polygonaceae}   & -14.8 &  \textbf{\textless0.001} \\
-    \emph{Caryophyllaceae}  & 2.09  &  0.644  &     \emph{Primulaceae}  & 14.9  &  0.343 \\
-    \emph{Cistaceae}  & -11.4 &  \textbf{\textless0.001}  &     \emph{Ranunculaceae}  & -38 &  \textbf{\textless0.001} \\
-    \emph{Convolvulaceae}   & -1.84 &  0.837  &     \emph{Rosaceae}   & 0.759 &  0.735 \\
-    \emph{Ericaceae}  & 4.61  &  0.116  &     \emph{Rubiaceae}*   & -13 &  \textbf{0.026} \\
-    \emph{Fabaceae}*  & -12.9 &  \textbf{\textless0.001}  &     \emph{Salicaceae}   & -1.9  &  0.545 \\
-    \emph{Geraniaceae}  & -3.31 &  0.624  &     \emph{Sapindaceae}  & 821 &  0.999 \\
-    \emph{Hydrangeaceae}  & 0.057 &  0.982  &     \emph{Saxifragaceae}  & -0.092  &  0.992 \\
-    \emph{Iridaceae}  & -27.9 &  0.078  &     \emph{Solanaceae}   & -21.9 &  0.189 \\
-    \emph{Lamiaceae}  & -5.01 &  \textbf{\textless0.001}  &     \emph{Tropaeolaceae}  & 192 &  0.997 \\
+    \emph{Adoxaceae}  & -65.8 & 0.163 & \emph{Malvaceae}  & -5.56 & 0.363 \\
+    \emph{Amaryllidaceae} & -17.9 & \textbf{0.015}  & \emph{Melastomataceae}* & 5.19  & 0.577 \\
+    \emph{Apiaceae} & 10.9  & \textbf{0.006}  & \emph{Montiaceae} & -1.12 & 0.87  \\
+    \emph{Apocynaceae}  & -6.96 & \textbf{0.037}  & \emph{Myrtaceae}  & 8.55  & 0.071 \\
+    \emph{Asparagaceae} & -6.23 & 0.189 & \emph{Oleaceae} & 0.995 & 0.855 \\
+    \emph{Asteraceae}*  & -1.47 & \textbf{\textless0.001} & \emph{Onagraceae} & -556  & \textgreater0.999 \\
+    \emph{Berberidaceae}  & -1.48$\times10^3$ & \textgreater0.999 & \emph{Orchidaceae}  & -14.5 & 0.145 \\
+    \emph{Boraginaceae} & -5.15 & \textbf{\textless0.001} & \emph{Orobanchaceae}  & 24.2  & 0.326 \\
+    \emph{Brassicaceae} & -11.2 & 0.072 & \emph{Papaveraceae} & -11.2 & 0.511 \\
+    \emph{Calceolariaceae}  & 156 & 0.998 & \emph{Phyllanthaceae} & 9.99  & 0.433 \\
+    \emph{Campanulaceae}  & 334 & 0.999 & \emph{Plantaginaceae} & -8.48 & \textbf{0.001}  \\
+    \emph{Caprifoliaceae} & 0.31  & 0.959 & \emph{Poaceae}* & 69.2  & \textbf{0.003}  \\
+    \emph{Caryophyllaceae}  & 2.09  & 0.644 & \emph{Polygonaceae} & -14.8 & \textbf{\textless0.001} \\
+    \emph{Cistaceae}  & -11.4 & \textbf{\textless0.001} & \emph{Primulaceae}  & 14.9  & 0.343 \\
+    \emph{Convolvulaceae} & -1.84 & 0.837 & \emph{Ranunculaceae}  & -38 & \textbf{\textless0.001} \\
+    \emph{Ericaceae}  & 4.61  & 0.116 & \emph{Rosaceae} & 0.759 & 0.735 \\
+    \emph{Fabaceae}*  & -12.9 & \textbf{\textless0.001} & \emph{Rubiaceae}* & -13 & \textbf{0.026}  \\
+    \emph{Geraniaceae}  & -3.31 & 0.624 & \emph{Salicaceae} & -1.9  & 0.545 \\
+    \emph{Hydrangeaceae}  & 0.057 & 0.982 & \emph{Sapindaceae}  & 821 & 0.999 \\
+    \emph{Iridaceae}  & -27.9 & 0.078 & \emph{Saxifragaceae}  & -0.092  & 0.992 \\
+    \emph{Lamiaceae}  & -5.01 & \textbf{\textless0.001} & \emph{Solanaceae} & -21.9 & 0.189 \\
+    \emph{Lauraceae}  & -79.9 & \textbf{\textless0.001} & \emph{Tropaeolaceae}  & 192 & 0.997 \\
     \emph{Loasaceae}  & -865  & \textgreater0.999 & \emph{Verbenaceae}  & -9.03 & 0.627 \\
     \emph{Malpighiaceae}  & 2.8 & 0.168 & \emph{Violaceae}  & -0.487  & 0.974 \\
-    \emph{Malvaceae}  & -5.56 &  0.363  &   &   & \\
   \hline
@@
     \end{center}
-     \caption{Change in log odds of observing pairwise niche overlap per million
-     years of divergence time between a pair of plants
-     in the 14 plant families where there was a significant
-     relationship between log odds of sharing interaction
-     partners and phylogenetic distance.
+     \caption{Change in log odds of a pair of plants sharing a pollinator or herbivore as phylogenetic distance between the plants increases.
+For clarity, we show only the 15 plant families for which the slope of the regression of the proportion of shared interaction partners against phylogenetic distance was significant in at least one network type.
+Note that the change in log odds for \emph{Asteraceae} in herbivory networks and \emph{Melastomataceae} and \emph{Poaceae} in pollination networks are not significantly different from zero; we present these values only for comparison across network types.
+All other plant families were well-represented in only one network type.
      % DBS: The above is near indecipherable. Can we please simplify it substantially?
+     [[Simpler now?]]
      Families in pollination networks are indicated

### 2019-06-25 manuscript/supporting_info.tex
double-checked family-wise results in main text

@@
 
+\section*{Supporting information 3: Details of within-family regressions}
+
+    Models for nine families could not be fit because there was no variation in the phylogenetic distance between plants, their numbers of shared interaction partners, or both.
+These families were \emph{Amaranthaceae}, \emph{Araliaceae}, \emph{Cactaceae}, \emph{Cornaceae}, \emph{Gentianaceae}, \emph{Liliaceae}, \emph{Oxalidaceae}, \emph{Rhamnaceae}, and \emph{Zingiberaceae}.
+Further, we could not fit a model for \emph{Sapindaceae} in herbivory networks as all but one plant pair had the same phylogenetic distances.
+
+    Only five families were sufficiently well-represented to fit models for shared herbivores: \emph{Asteraceae}, \emph{Fabaceae}, \emph{Melastomataceae}, \emph{Poaceae}, and \emph{Rubiaceae}.
+All were also well-represented enough to fit models for shared pollinators.
+
+    In total, there were 48 families which were well-represented enough to fit models for shared pollinators. For 13 of these, we obtained singular fits.
+    Singular fits were obtained for \emph{Amaranthaceae}, \emph{Araliaceae}, \emph{Boraginaceae},
+    \emph{Campanulaceae}, \emph{Caryophyllaceae}, \emph{Ericaceae}, \emph{Geraniaceae}, 
+    \emph{Hydrangeaceae}, \emph{Malvaceae}, \emph{Oxalidaceae}, \emph{Primulaceae}, 
+    \emph{Saxifragaceae}, \emph{Verbenaceae}.
+
+    6+42=48
+    \emph{Sapindaceae}
+
 \end{spacing}

### 2019-06-25 code/create_figures/cladewise_barplot.py

@@ -86,8 +86,8 @@ scaledict={
   "overall":(92.11035845,42.69432146)}
 
 
-# Two families didn't converge (small samples with one odd value)
-non_convergent={'pp':'lauraceae','ph':'sapindaceae'}
+# One family didn't converge (small samples with one odd value). Lauraceae converges fine now.
+non_convergent={'ph':'sapindaceae','pp':''}
 legenddict={'pp':'Plant-pollinator','ph':'Plant-herbivore'}
 
 def read_tree(filename):
@@ -133,6 +133,9 @@ def lineplotter(datapath,family,grace,graph,x,graphtype,supertype,nettype,summar
   else:
     shap=2
   databank=signalreader(datapath,family,nettype)
+  if family=='lauraceae':
+    print databank
+  # sys.exit()
   if family not in non_convergent[nettype] and databank!={'fixef':{},'ranef':{}}:
     try:
       scal=scaledict[family]
@@ -142,8 +145,9 @@ def lineplotter(datapath,family,grace,graph,x,graphtype,supertype,nettype,summar
     err=databank['fixef']['scale(distance)'][1]*scal[1]*1.96
     p=databank['fixef']['scale(distance)'][2]
     summarydict[family][nettype]=(str(x),str(p))
-    if nettype=='ph' and family in ['rubiaceae']:
+    if nettype=='ph' and family in ['asteraceae','fabaceae','melastomataceae','poaceae','rubiaceae']:
       x=x+.25
+    # print x, y
     if y>0:
       if y-err >0:
         sig=1
@@ -156,18 +160,19 @@ def lineplotter(datapath,family,grace,graph,x,graphtype,supertype,nettype,summar
         sig=0
     else:
       print family
-    if sig==1:
-      dat=graph.add_dataset([(x,y,err)],type='xydy')
-      if graphtype=='grey':
-        if nettype=='pp':
-          col=8
-        else:
-          col=5
+    # if sig==1:
+    # print sig
+    dat=graph.add_dataset([(x,y,err)],type='xydy')
+    if graphtype=='grey':
+      if nettype=='pp':
+        col=8
       else:
-        if nettype=='pp':
-          col=3
-        else:
-          col=10
+        col=5
+    else:
+      if nettype=='pp':
+        col=3
+      else:
[…]

### 2019-06-25 manuscript/phylogenetic_signal_manuscript.tex
finished double-checking main text familywise stuff

@@
     Considering each family separately, the relationship between within-family niche overlap and phylogenetic distance varied widely in both pollination and herbivory networks. 
-    For the 48 families that were well represented in pollination networks, overlap decreased
-    with increasing phylogenetic distance in 18 (Table~\ref{family_slopes_pp}).
+    For the 48 families that were well represented in pollination networks, overlap decreased significantly with increasing phylogenetic distance in 12 (Table~\ref{family_slopes_pp}).
     There was no significant relationship between overlap and phylogenetic distance in
-    a further 15 plant families. Finally, the overlap between pairs of \emph{Polygonaceae}
-    % DBS: According to the table, this should probably be Apiaceae and Poaceae. Please check.
-    increased with increasing phylogenetic distance. 
-    Of the seven plant families that were sufficiently well represented in herbivory 
-    networks, overlap decreased with increasing phylogenetic distance in four 
-    (Table~\ref{family_slopes_ph}; Fig.~\ref{within_family_regression}). Two
+    a further 34 plant families. Finally, the overlap between pairs of \emph{Apiaceae} and \emph{Poaceae} increased significantly with increasing phylogenetic distance.
+
+    Of the nine plant families that were sufficiently well represented in herbivory 
+    networks, overlap decreased significantly with increasing phylogenetic distance in four 
+    (Table~\ref{family_slopes_ph}; Fig.~\ref{within_family_regression}). Four
     families did not show significant relationships between phylogenetic distance and overlap,
-    and in one family, \emph{Fabaceae}, overlap of interaction partners increased with 
+    and in one family, \emph{Fabaceae}, overlap of interaction partners increased significantly with 
     increasing phylogenetic distance.

### 2019-06-25 code/create_figures/observed_vs_random_slopes.py
consistency in labels

@@ -62,7 +62,7 @@ def format_graph(graph,nettype):
 
 def grace_setup(obsslopes,ranslopes,slopedict):
   # dummy=[r"\| \|",r"\|\\\|",r"\|,X\|"]
-  dummy=['Plant-herbivore','Plant-pollinator','','','','']
+  dummy=['Herbivory','Pollination','','','','']
   # dummy=['Total overlap','Partial overlap','No overlap','','','']
   grace=MultiPanelGrace(colors=ColorBrewerScheme('PRGn'))
 

### 2019-06-25 code/create_figures/regression_line_plot.py

@@ -157,7 +157,7 @@ def main():
     grace=MultiPanelGrace(colors=ColorBrewerScheme('PRGn'))
 
   # dummy=[r"\| \|",r"\|\\\|",r"\|,X\|"]
-  dummy=['Plant-herbivore','Plant-pollinator','','','','']
+  dummy=['Herbivory','Pollination','','','','']
   # dummy=['Total overlap','Partial overlap','No overlap','','','']
 
 

### 2019-06-25 manuscript/supporting_info.tex
supporting info ready

@@
 
+\clearpage
+
 \section*{Supporting information 3: Details of within-family regressions}
@@
 
-    Only five families were sufficiently well-represented to fit models for shared herbivores: \emph{Asteraceae}, \emph{Fabaceae}, \emph{Melastomataceae}, \emph{Poaceae}, and \emph{Rubiaceae}.
-All were also well-represented enough to fit models for shared pollinators.
-
-    In total, there were 48 families which were well-represented enough to fit models for shared pollinators. For 13 of these, we obtained singular fits.
-    Singular fits were obtained for \emph{Amaranthaceae}, \emph{Araliaceae}, \emph{Boraginaceae},
+    Only nine families were sufficiently well-represented to fit models for shared herbivores.
+Five of these were also well-represented in plant-pollinator networks: \emph{Asteraceae}, \emph{Fabaceae}, \emph{Melastomataceae}, \emph{Poaceae}, and \emph{Rubiaceae}.
+In total, there were 48 families which were well-represented enough to fit models for shared pollinators.
+Note that singular fits were obtained for \emph{Amaranthaceae}, \emph{Araliaceae}, \emph{Boraginaceae},
     \emph{Campanulaceae}, \emph{Caryophyllaceae}, \emph{Ericaceae}, \emph{Geraniaceae}, 
     \emph{Hydrangeaceae}, \emph{Malvaceae}, \emph{Oxalidaceae}, \emph{Primulaceae}, 
-    \emph{Saxifragaceae}, \emph{Verbenaceae}.
-
-    6+42=48
-    \emph{Sapindaceae}
+    \emph{Saxifragaceae}, and \emph{Verbenaceae}.
 

### 2019-06-25 manuscript/phylogenetic_signal_manuscript.tex
added reference to proportion re-framing in SI

@@
 
-Supporting information: 1 file containing 1 section.
+Supporting information: 1 file containing 4 sections.
 
@@
           greater overlap, and this tendency was stronger in herbivory 
-          networks than pollination networks. These relationships were also significantly related 
-          to the composition of the network's plant component. Within plant families, 
-          relationships varied greatly in both network types.
+          networks than pollination networks.
+While the strength of this relationship within a network was not related to the composition of the network's plant component, we nevertheless found that different plant families showed different relationships between phylogenetic distance and overlap of interaction partners.
 
@@
 
+    To demonstrate the power of defining $\omega_{ij}$ as a tuple of $M_{ij}$ and $U_{ij}$, we repeated the above analyses instead defining $\omega_{ij}$ as the proportion of interaction partners that are shared (i.e., $M_{ij}$/[$M_{ij}+U_{ij}$]).
+We observed similar trends but, notably, the tuple definition of $\omega_{ij}$ had greater power to detect weak relationships (\emph{Supporting information 2}).
+We therefore show only the results when defining $\omega_{ij}$ as a tuple in the main text.
+
     Note that pairs of plants are not always independent: the same plant will 
@@
     networks were compared to those obtained from permutations of the 
-    permuted networks, there was no relationship, which speaks to the robustness of our methodology (\emph{Supporting 
-    information 2}).
+    permuted networks, there was no relationship, which speaks to the robustness of our methodology (\emph{Supporting information 3}).
 
@@
     There was no significant relationship between overlap and phylogenetic distance in
-    a further 34 plant families. Finally, the overlap between pairs of \emph{Apiaceae} and \emph{Poaceae} increased significantly with increasing phylogenetic distance.
+    a further 34 plant families (see \emph{Supporting information 4} for further 
+    details). Finally, the overlap between pairs of \emph{Apiaceae} and \emph{Poaceae} increased significantly with increasing phylogenetic distance.
 
@@
 
-    We were able to fit these models to 47 plant families (see \emph{Materials and Methods} for details). 
+    We were able to fit these models to 48 plant families (see \emph{Materials and Methods} for details). 
     Families marked with an asterisk were also sufficiently diverse to model in herbivory networks. 
@@
 
-  % \begin{figure}[!h]
-  %   \begin{center}
-  %     \centerline{\includegraphics*[width=.75\textwidth]{Figures/Sketches/methods_breakdown.eps}}
-  %   \end{center}
-  %    \caption{Visual depiction of our decomposition of pairwise niche overlap of plants' interaction
-  %    partners. \textbf{(a)} First, consider the representation of any pollination or herbivory network
-  %    as an adjacency matrix. Here, filled cells indicate an interaction between a particular plant 
-  %    (letters on rows) and an animal (numbers on columns). \textbf{(b)} For a given pair of plants (e.g., plants 
-  %    A and B), we then considered the set of animals that interact with at least one of the focal
-  %    plants. Taking each pair of animals in this set in turn, we assigned the resulting quartet (the
-  %    two focal plants plus two animals) to one of three patterns of overlap.
-  %    In the \textbf{total overlap} pattern, both plants interact with both animals. 
-  %    In the \textbf{partial overlap} pattern, one plant interacts with both animals and the other plant
-  %    interacts with only one.
-  %    Finally, in the \textbf{no overlap} pattern each animal interacts with only one plant; note that 
-  %    this includes cases where both animals interact with the same plant (e.g., animals 1 and 5 and plant A)
-  %    as well as cases where each animal interacts with a different plant (e.g., animals 1 with plant A and animal
-  %    4 with plant B). \textbf{(c-e)} The number of times each pattern occurred was used to summarise the pairwise niche 
-  %    overlap between the two plants and then related to their phylogenetic distance.}
-  %   \label{overlap_patterns}
-  % \end{figure}
-
   \begin{figure}[!h]
     \begin{center}
-      \centerline{\includegraphics*[width=.75\textwidth]{Figures/dataplots/scaled_regression_lines_full_color.eps}}
+      \centerline{\includegraphics*[width=.5\textwidth]{Figures/dataplots/scaled_regression_lines_full_color.eps}}
     \end{center}
@@
      \caption{The slopes of the mixed-effect logistic regression of pairwise niche overlap against phylogenetic distance was signficantly different from 0 for each network.
-Here we show, for herbivory (PH) and pollination (PP) networks, the observed slopes (depicted by green squares or purple diamonds, respectively).
+Here we show the observed slopes for herbivory (green squares) and pollination (purple diamonds) networks.
 The maximum and minimum slopes obtained from 999 permutations of each network are depicted by thin, black lines.
@@
     \end{center}
-     \caption{Change in log odds of a pair of plants sharing a pollinator or herbivore as phylogenetic distance between the plants increases.
+    \caption{Change in the log odds of a pair of plants sharing a pollinator or herbivore as phylogenetic distance between the plants increases.
+These values are analogous to the slopes of the regression lines from Eq.
+2-3 and represent
+    the change in the probability of observing shared 
+    interaction partners per million years of divergence time. 
     For clarity, we show only the 15 plant families for which the slope of the regression of the proportion of shared interaction partners against phylogenetic distance was significant in at least one network type.
@@
     networks are indicated by pale green circles.
-     Note that changes in log odds are analogous to the 
-     slopes of the regression lines from Eq. 2-3
-     in logit-transformed space and represent
-     the change in the probability of observing shared 
-     interaction partners per million years of divergence time. We also
+    We also
     show the slope of the relationship between the
@@
     pollination (dark, purple horizontal line) networks.
-     % See~\emph{Figure S1; Supporting Information} for more details.
     The phylogenetic tree below the plots indicates the
-     relatedness between these plant families. Error bars represent 95\% confidence
-     intervals.}
+    relatedness between these plant families. Error bars represent 95\% 
+    confidence intervals.}
     \label{within_family_regression}

### 2019-06-25 manuscript/supporting_info.tex
added reference to proportion re-framing in SI

@@
 
-\section*{Supporting information 2: Distributions of $p$-values for permuted networks}
+\section*{Supporting information 2: Repeating our analyses with proportion of shared partners}
+
+    We repeated some of our analyses using the proportion of shared interaction partners as the response rather than a tuple describing the number of interaction partners that are shared and not shared.
+This approach is more common when performing logistic regressions, but loses information about the varying weights of evidence about different plant pairs.
+This lost information can limit the power of the regression to detect weak trends.
+
+    Across all networks, more distantly-related plants remained less likely
+    to share interaction partners, but this relationship was not significant 
+    in herbivory networks ($\beta_{distance}$=-1.07, $p$=0.477; compare to 
+    $\beta_{distance}$=-6.82, $p$\textless0.001 in the main text).
+Plants in pollination networks again tended to share fewer interaction partners overall ($\beta_{pollination}$=-0.881, $p$\textless0.001; compare to $
+    beta_{pollination}$=-1.44, $p$\textless0.001 in the main text), and the decrease in overlap with increasing phylogenetic distance was steeper than in herbivory networks ($\beta_{distance:pollination}$=-26.8, $p$\textless0.001).
+Thus, while we observed the same trends when treating the response as a proportion and as a tuple, the tuple format displayed these trends more clearly.
+This is likely because of the additional informaion incorporated in the tuple.
+
+    Within networks, using the proportion of shared interaction partners rather than a tuple resulted in significant relationships between phylogenetic distance and overlap in interaction partners in five herbivory networks and seven pollination networks (compare to seven and 34 networks, respectively, in the main text).
+In each case, the proportion of shared interaction partners decreased with increasing phylogenetic distance.
+Again, this demonstrates the greater power of a Jaccard regression with a tuple response to capture weak trends.
+Notably, the single pollination network where overlap of interaction partners significantly \emph{increased} with increasing phylogenetic distance was not detected when using the proportion of shared interaction partners as a response.
+
+\clearpage
+
+\section*{Supporting information 3: Distributions of $p$-values for permuted networks}
 
@@
 
-\section*{Supporting information 3: Details of within-family regressions}
+\section*{Supporting information 4: Details of within-family regressions}
 
@@
 
+\section*{Supporting information 2: Repeating our analyses with proportion of shared partners}
+
+    We repeated some of our analyses using the proportion of shared interaction partners as the response rather than a tuple describing the number of interaction partners that are shared and not shared.
+This approach is more common when performing logistic regressions, but loses information about the varying weights of evidence about different plant pairs.
+This lost information can limit the power of the regression to detect weak trends.
+
+    Across all networks, more distantly-related plants remained less likely
+    to share interaction partners, but this relationship was not significant 
+    in herbivory networks ($\beta_{distance}$=-1.07, $p$=0.477; compare to 
+    $\beta_{distance}$=-6.82, $p$\textless0.001 in the main text).
+Plants in pollination networks again tended to share fewer interaction partners overall ($\beta_{pollination}$=-0.881, $p$\textless0.001; compare to $
+    beta_{pollination}$=-1.44, $p$\textless0.001 in the main text), and the decrease in overlap with increasing phylogenetic distance was steeper than in herbivory networks ($\beta_{distance:pollination}$=-26.8, $p$\textless0.001).
+Thus, while we observed the same trends when treating the response as a proportion and as a tuple, the tuple format displayed these trends more clearly.
+This is likely because of the additional informaion incorporated in the tuple.
+
+    Within networks, using the proportion of shared interaction partners rather than a tuple resulted in significant relationships between phylogenetic distance and overlap in interaction partners in five herbivory networks and seven pollination networks (compare to seven and 34 networks, respectively, in the main text).
+In each case, the proportion of shared interaction partners decreased with increasing phylogenetic distance.
+Again, this demonstrates the greater power of a Jaccard regression with a tuple response to capture weak trends.
+Notably, the single pollination network where overlap of interaction partners significantly \emph{increased} with increasing phylogenetic distance was not detected when using the proportion of shared interaction partners as a response.
+
 \end{spacing}

### 2019-06-25 manuscript/supporting_info.tex
Recreated Fig. 1 with proportions in the SI

@@
 Again, this demonstrates the greater power of a Jaccard regression with a tuple response to capture weak trends.
-Notably, the single pollination network where overlap of interaction partners significantly \emph{increased} with increasing phylogenetic distance was not detected when using the proportion of shared interaction partners as a response.
+The best-fit models for individual networks show much less variation when framing the response as a proportion (Fig.~\ref{lineplot}).
+
+    \begin{figure}[!h]
+        \begin{center}
+          \centerline{\includegraphics*[width=.75\textwidth]{Figures/dataplots/proportion_regression_lines_full_color.eps}}
+        \end{center}
+         \caption{\small When considering niche overlap as the proportion of shared interaction partners rather than both the number of interaction partners that are shared and not shared, there is much less variability between networks.
+The overall trends observed are also much weaker than those detected when using all of the available information.
+Compare with Fig.
+1, main text.
+         }
+        \label{within_family_regression}
+      \end{figure}
 

### 2019-06-25 manuscript/phylogenetic_signal_manuscript.tex
local changes

--- 2019-06-25 manuscript/phylogenetic_signal_manuscript.tex
@@
     ($\beta_{size}$=2.58$\times$10$^{-4}$, $p$=0.011 for the full glm; 
-    herbivory networks are the baseline). Plant-pollinator networks had 
+    herbivory networks are the baseline). Pollination networks had 
     higher (less negative) slopes overall ($\beta_{pollinator}$=0.306, 
     $p$\textless0.001 compared to the intercept value of -0.434 for 
-    herbivory networks). Plant-pollinator networks moreover showed a 
+    herbivory networks). Pollination networks moreover showed a 
     much weaker relationship between network size and the strength of the 
@@
 The maximum and minimum slopes obtained from 999 permutations of each network are depicted by thin, black lines.
+Dashed lines indicate the mean observed slope across all pollination or herbivory networks.
 For both network types, the slopes obtained from permuted networks were always very close to 0.}

### 2019-06-25 manuscript/supporting_info.tex
local changes

--- 2019-06-25 manuscript/supporting_info.tex
@@
 
-\clearpage
-
 \section*{Supporting information 3: Details of within-family regressions}
@@
     Only nine families were sufficiently well-represented to fit models for shared herbivores.
-Five of these were also well-represented in plant-pollinator networks: \emph{Asteraceae}, \emph{Fabaceae}, \emph{Melastomataceae}, \emph{Poaceae}, and \emph{Rubiaceae}.
-In total, there were 48 families which were well-represented enough to fit models for shared pollinators.
-Note that singular fits were obtained for \emph{Amaranthaceae}, \emph{Araliaceae}, \emph{Boraginaceae},
+Five (\emph{Asteraceae}, \emph{Fabaceae}, \emph{Melastomataceae}, \emph{Poaceae}, and \emph{Rubiaceae}) were also well-represented in pollination networks.
+\emph{Euphorbiaceae}, \emph{Moraceae}, \emph{Nothofagaceae}, and \emph{Pinaceae} were only sufficiently represented in herbivory networks.
+
+    In total, there were 48 families which were well-represented enough to fit models for shared pollinators. For 13 of these, we obtained singular fits.
+    Singular fits were obtained for \emph{Amaranthaceae}, \emph{Araliaceae}, \emph{Boraginaceae},
     \emph{Campanulaceae}, \emph{Caryophyllaceae}, \emph{Ericaceae}, \emph{Geraniaceae}, 
     \emph{Hydrangeaceae}, \emph{Malvaceae}, \emph{Oxalidaceae}, \emph{Primulaceae}, 
-    \emph{Saxifragaceae}, and \emph{Verbenaceae}.
+    \emph{Saxifragaceae}, \emph{Verbenaceae}.
+
+    6+42=48
+    \emph{Sapindaceae}
 

### 2019-06-27 manuscript/coverletter_resub.tex
possibly ready to send out to coauthors

@@
 
-		[[Not sure this is the best angle.]]
 		Plants' interactions with animals can significantly affect their fitness, both positively and negatively.
 These interactions might be conserved through stabilising selection or if key traits affecting the interactions are highly heritable, or they might not be if there is selection to avoid overlap with close relatives or if distant relatives converge.
-By comparing plant families displaying different patterns of conservation of these interactions, we can predict which families may experience different types of selection pressures.
-Thus, we can use ecological data to guide future evolutionary research.
+The question of whether, and how strongly, plants' interaction partners are phylogenetically conserved has excited continuing interest, as it is likely an important step towards understanding the eco-evolutionary dynamics of plant-insect communities.
+Within this context, our work takes one step beyond considering whole-network trends to examine variation between plant families.
+We believe that this finer-grained approach will be critical in future efforts to find the mechanisms driving conservationof interaction partners.
+
+		We note that our manuscript shares some methodological similarities with another important and timely article: Fontaine \& Th\'{e}bault, 2015 (Population Ecology).
+Due to the long gestation of this manuscript, we believe that the two manuscripts were developed independently.
+Nevertheless, we respect their prior publication and have taken care to refer to it in our manuscript.
+Our manuscript does, however, include a few methodological innovations which greatly add to its novelty.
+First, we define overlap in interaction partners using numbers of shared and not-shared partners (analogous to numbers of successes and failures in Bernoulli trials).
+This approach, as opposed to using only the number or propotion of shared interaction partners, effectively weights our data according to how much information is available and appears to be a more powerful tool to detect weak trends.
+Second, in addition to overall trends at the network level, we also test whether these trends are related to community composition and whether different plant families show different trends.
+These more-detailed analyses complement the usual network-level approach to give more insight into potential drivers of conservation of interaction partners.
+We believe that these additions to our methodology are enough to distinguish our work from that of Fontaine \& Th\'{e}bault.
+]]
 
@@
 	Note that we submitted an earlier version of this manuscript to New Phytologist, for which the revision period expired in August 2017.
-We now use a different methodology from that presented in the initial submission, and we are happy to have the current version stand on its own merits as a new initial submission.
-We hope that you will agree that the question we investigate remains of interest to the readership of \textbf{New Phytologist}.
+As the lead author was completing her PhD and transitioning to a postdoctoral appointment in a different country, we hope that the Editorial team will understand our failure to meet the original deadline.
+While we have taken the comments provided on the earlier version to heart, we now use a very different methodology and have revised the entire manuscript.
+We are therefore happy to have the current version stand on its own merits as a new initial submission, but are also prepared to provide a response to the previous round of comments if requested.
+Despite the delay, we hope that you will agree that the question we investigate remains of interest to the readership of \textbf{New Phytologist}.
 

### 2019-06-27 manuscript/phylogenetic_signal_manuscript.tex
added a few more refs to Fontaine, not sure about a particular result I disagree with

@@
   On the other, herbivores consume plant tissues~\citep{McCall2006} which
-  costs plants energy and likely lowers their fitness.
+  costs plants energy and likely lowers their fitness~\citep{Strauss2002}.
   In both cases, these interactions do not occur randomly but
@@
   clades, and these processes might be associated with different 
-  pressures imposed by pollination and herbivory.
+  pressures imposed by pollination and herbivory~\citep{Fontaine2015}.
 
-  [[Trying to emphasize the family-wise part as a point of difference from Fontaine \& Thebault, even though our results weren't the most exciting.]]
   Here we investigate how overlap in interaction partners between 
@@
   phylogenetic distance differs systematically across plant families.
+  This fine-grained approach gives more detailed information than 
+  previous studies.
 
@@
   different network types. This may indicate that one type of interaction
-  places greater constraints upon these families than the other. Plants
+  places greater constraints upon these families than the other, 
+  similar to the expectation that greater constraints upon consumers 
+  than upon their resources explains the assymmetry in conservation 
+  of interaction partners~\citep{Fontaine2015}. Plants
   may not be able to respond to selection on both types of interaction

### 2019-07-01 manuscript/coverletter_resub.tex
coverletter looks good enough to send to co-authors

@@
 		Plants' interactions with animals can significantly affect their fitness, both positively and negatively.
-These interactions might be conserved through stabilising selection or if key traits affecting the interactions are highly heritable, or they might not be if there is selection to avoid overlap with close relatives or if distant relatives converge.
+These interactions might be conserved through stabilising selection or if key traits affecting the interactions are highly heritable, or they might not be conserved if there is selection to avoid overlap with close relatives or if distant relatives converge.
 The question of whether, and how strongly, plants' interaction partners are phylogenetically conserved has excited continuing interest, as it is likely an important step towards understanding the eco-evolutionary dynamics of plant-insect communities.
@@
 
-		We note that our manuscript shares some methodological similarities with another important and timely article: Fontaine \& Th\'{e}bault, 2015 (Population Ecology).
+		\indent We note that our manuscript shares some methodological similarities with another important and timely article: Fontaine \& Th\'{e}bault, 2015 (Population Ecology).
 Due to the long gestation of this manuscript, we believe that the two manuscripts were developed independently.
@@
 We believe that these additions to our methodology are enough to distinguish our work from that of Fontaine \& Th\'{e}bault.
-]]
 

### 2019-07-02 code/create_figures/cladewise_barplot.py
now all figures have consistent labels

@@ -88,7 +88,7 @@ scaledict={
 
 # One family didn't converge (small samples with one odd value). Lauraceae converges fine now.
 non_convergent={'ph':'sapindaceae','pp':''}
-legenddict={'pp':'Plant-pollinator','ph':'Plant-herbivore'}
+legenddict={'pp':'Pollination','ph':'Herbivory'}
 
 def read_tree(filename):
     inFile = open(filename,'r')

### 2019-07-02 manuscript/phylogenetic_signal_manuscript.tex
some very small corrections, updated word count

@@
 
-Main text: 4522
+Main text: 5612 % Limit 6,500
 
 \begin{itemize}
-  \item Introduction: 805 
-  \item Materials and Methods: 1831 
-  \item Results: 665
-  \item Discussion: 1139 
+  \item Introduction: 1074
+  \item Materials and Methods: 2223 
+  \item Results: 890
+  \item Discussion: 1342
   \item Acknowledgements: 83
 \end{itemize}
+
+% Word counts updated July 2, include some comments.
 
@@
           partners for each pair of plants in 59 pollination and 11 herbivory
-          networks.  We then tested for relationships between phylogenetic 
+          networks based on the numbers of potential interaction partners which are shared and not shared.  We then tested for relationships between phylogenetic 
           distance and partner overlap within each network, and whether these 
@@
 
-\section*{Warning}
-
-Our original methodology was different from that in Fontaine \& Th\'{e}bault 2015 (Popul Ecol), but now that we've switched to Jaccard as our overlap measure we're doing almost the exact same thing with a slightly different set of networks.
-This will probably make it quite hard to argue novelty.
-
-\textbf{DBS: }
-
 \section*{Keywords}
@@
 \begin{spacing}{1.5}
+% \clearpage
 
@@
 
+% \clearpage
+
 \section*{Materials and Methods}
@@
     `mega-tree' of angiosperms~\citep{Zanne2014}. Some species were not included
-    in the angiosperm mega-tree (largely ferns and tree ferns). For angiosperms,
+    in the angiosperm mega-tree. For angiosperms,
     a sister taxon was identified using~\citet{APW} and the species added manually.
@@
     Models for two families did not converge.
-In both the \emph{Lauraceae}, (represented by four species in one pollination network) and the \emph{Sapindaceae} in herbivory networks (represented by five species in one network), one pair of species shared a single interaction partner while all other pairs did not share any interaction partners.
-The model for \emph{Sapindaceae} in pollination networks did converge.
+In the \emph{Lauraceae}, (represented by four species in one pollination network) and the \emph{Sapindaceae} (represented by five species in one herbivory network and five species in two pollination networks), only one pair of species per network type shared any interaction partners while all other pais did not share any interaction partners.
+
+% \clearpage
 
@@
     increasing phylogenetic distance.
+
+% \clearpage
 
@@
 
+% \clearpage
+
 \section*{Acknowledgements}

### 2019-07-05 manuscript/supporting_info.tex
SI text ok, want to fix Fig. S2

--- 2019-06-25 manuscript/supporting_info.tex
@@
     We repeated some of our analyses using the proportion of shared interaction partners as the response rather than a tuple describing the number of interaction partners that are shared and not shared.
-This approach is more common when performing logistic regressions, but loses information about the varying weights of evidence about different plant pairs.
+This approach is common when performing logistic regressions, but loses information about the varying weights of evidence about different plant pairs.
 This lost information can limit the power of the regression to detect weak trends.
@@
 Plants in pollination networks again tended to share fewer interaction partners overall ($\beta_{pollination}$=-0.881, $p$\textless0.001; compare to $
-    beta_{pollination}$=-1.44, $p$\textless0.001 in the main text), and the decrease in overlap with increasing phylogenetic distance was steeper than in herbivory networks ($\beta_{distance:pollination}$=-26.8, $p$\textless0.001).
+    \beta_{pollination}$=-1.44, $p$\textless0.001 in the main text), and the decrease in overlap with increasing phylogenetic distance was steeper than in herbivory networks ($\beta_{distance:pollination}$=-26.8, $p$\textless0.001; compare to $\beta_{distance:pollination}$=-18.5, $p$\textless0.001 in the main text).
 Thus, while we observed the same trends when treating the response as a proportion and as a tuple, the tuple format displayed these trends more clearly.
@@
          \caption{\small When considering niche overlap as the proportion of shared interaction partners rather than both the number of interaction partners that are shared and not shared, there is much less variability between networks.
-The overall trends observed are also much weaker than those detected when using all of the available information.
+The overall trends (thicker, darker lines) observed are also much weaker than those detected when using all of the available information.
 Compare with Fig.
 1, main text.
+Both figures are plotted on the same scale.
          }
-        \label{within_family_regression}
+        \label{lineplot}
       \end{figure}
@@
 
-    \subsection*{Networks shown in each panel of Figure S1}
+    \subsection*{Networks shown in each panel of Figure S2}
 
@@
 These families were \emph{Amaranthaceae}, \emph{Araliaceae}, \emph{Cactaceae}, \emph{Cornaceae}, \emph{Gentianaceae}, \emph{Liliaceae}, \emph{Oxalidaceae}, \emph{Rhamnaceae}, and \emph{Zingiberaceae}.
-Further, we could not fit a model for \emph{Sapindaceae} in herbivory networks as all but one plant pair had the same phylogenetic distances.
+Further, we could not fit a model for \emph{Lauraceae} in pollination networks or \emph{Sapindaceae} in herbivory or pollination networks as only one plant pair in each network type shared any interaction partners.
 
@@
     \emph{Saxifragaceae}, and \emph{Verbenaceae}.
-
-\section*{Supporting information 2: Repeating our analyses with proportion of shared partners}
-
-    We repeated some of our analyses using the proportion of shared interaction partners as the response rather than a tuple describing the number of interaction partners that are shared and not shared.
-This approach is more common when performing logistic regressions, but loses information about the varying weights of evidence about different plant pairs.
-This lost information can limit the power of the regression to detect weak trends.
-
-    Across all networks, more distantly-related plants remained less likely
-    to share interaction partners, but this relationship was not significant 
-    in herbivory networks ($\beta_{distance}$=-1.07, $p$=0.477; compare to 
-    $\beta_{distance}$=-6.82, $p$\textless0.001 in the main text).
-Plants in pollination networks again tended to share fewer interaction partners overall ($\beta_{pollination}$=-0.881, $p$\textless0.001; compare to $
-    beta_{pollination}$=-1.44, $p$\textless0.001 in the main text), and the decrease in overlap with increasing phylogenetic distance was steeper than in herbivory networks ($\beta_{distance:pollination}$=-26.8, $p$\textless0.001).
-Thus, while we observed the same trends when treating the response as a proportion and as a tuple, the tuple format displayed these trends more clearly.
-This is likely because of the additional informaion incorporated in the tuple.
-
-    Within networks, using the proportion of shared interaction partners rather than a tuple resulted in significant relationships between phylogenetic distance and overlap in interaction partners in five herbivory networks and seven pollination networks (compare to seven and 34 networks, respectively, in the main text).
-In each case, the proportion of shared interaction partners decreased with increasing phylogenetic distance.
-Again, this demonstrates the greater power of a Jaccard regression with a tuple response to capture weak trends.
-Notably, the single pollination network where overlap of interaction partners significantly \emph{increased} with increasing phylogenetic distance was not detected when using the proportion of shared interaction partners as a response.
 

### 2019-07-05 manuscript/supporting_info.tex
figure is fine, was just a little small

@@
         \end{center}
-         \caption{\small Distributions of $p$-values obtained when comparing the strength of the relationship between niche overlap and phylogenetic distance in 999 permutations of each network in our dataset with 500 permutations of each permuted network.
+         \caption{\small Nearly uniform distributions of $p$-values where obtained when comparing the strength of the relationship between niche overlap and phylogenetic distance in 999 permutations of each network in our dataset with 500 permutations of each permuted network.
 Each line in each panel represents the histogram of $p$-values for one network.
-Bins are 0.05 wide.
+Bins are 0.1 wide.
 Purple lines in panels A-L represent pollination networks while green lines in panels M-N represent plant-herbivore networks.

### 2019-07-05 code/create_figures/pval_test_observed.py

@@ -27,8 +27,8 @@ def pval_binner(ps):
 	bins={}
 	used=[]
 	for i in range(0,21):
-		binmin=round(i*0.05,2)
-		binmax=round(binmin+0.05,2)
+		binmin=round(i*0.1,2)
+		binmax=round(binmin+0.1,2)
 		binmed=round(np.mean([binmin,binmax]),3)
 		bins[binmed]=[]
 		for x in sorted(ps):
@@ -42,8 +42,8 @@ def pval_binner(ps):
 	total=0
 	for x in sorted(bins):
 		y=len(bins[x])
-		lens.append((x-0.025,float(y)/999))
-		lens.append((x+0.025,float(y)/999))
+		lens.append((x-0.05,float(y)/999))
+		lens.append((x+0.05,float(y)/999))
 		total=total+y
 
 	if total!=len(ps):
@@ -58,7 +58,7 @@ def format_graph(graph):
   graph.xaxis.tick.configure(major=.2,minor_ticks=0,major_size=.5,major_linewidth=.5)
   graph.xaxis.ticklabel.char_size=0.5
 
-  graph.world.ymax=.08
+  graph.world.ymax=.15
   graph.yaxis.tick.configure(major=.02,minor_ticks=0,major_size=.5,major_linewidth=.5)
   graph.yaxis.ticklabel.char_size=0.5
 
@@ -113,7 +113,7 @@ def main():
   # grace.set_label_scheme("dummy")
   for i in range(0,12):
   	keys=sorted(pps)[i*5:i*5+5]
-  	# print i, len(keys)
+  	print i, len(keys)
 	graph=grace.add_graph(Panel)
 	graph=format_graph(graph)
 	j=0
@@ -126,7 +126,7 @@ def main():
   		keys.append(sorted(phs)[-1])
   	elif i==2:
   		keys=[]
-  	print i,keys
+  	print i,len(keys)
 	graph=grace.add_graph(Panel)
 	graph=format_graph(graph)
 	j=0

### 2019-07-08 manuscript/coverletter_resub.tex
small DBS comments

@@
 This variability may help to explain the mixed results from earlier studies, especially those considering only a single network.
+Moreover, our approach takes into account both the numbers of shared interaction partners and the number of interaction partners which are not shared.
+We thus avoid discarding information, as happens when numbers of shared and not-shared interaction partners are converted to a single proportion.
+This more-detailed approach gives us more power to detect subtle trends.
 
@@
 
-		\indent We note that our manuscript shares some methodological similarities with another important and timely article: Fontaine \& Th\'{e}bault, 2015 (Population Ecology).
+		% \indent We note that our manuscript shares some methodological similarities with another important and timely article: Fontaine \& Th\'{e}bault, 2015 (Population Ecology).
 Due to the long gestation of this manuscript, we believe that the two manuscripts were developed independently.
@@
 
-	Note that we submitted an earlier version of this manuscript to New Phytologist, for which the revision period expired in August 2017.
+	Note that we submitted an earlier version of this manuscript to New Phytologist (NPH-MS-2016-21211), for which the revision period expired in August 2017.
 As the lead author was completing her PhD and transitioning to a postdoctoral appointment in a different country, we hope that the Editorial team will understand our failure to meet the original deadline.

### 2019-07-08 manuscript/phylogenetic_signal_manuscript.tex
trimmed summary to fit word limit, small formatting tweaks

@@
 Joshua A. Thia$^{1,5}$, Christie J. Webber$^{1}$, Daniel B. Stouffer$^{1}$}
-\date{\small$^1$Centre for Integrative Ecology, School of Biological Sciences\\
-\medskip$^2$Department of Ecology,\\
+\date{\small$^1$Centre for Integrative Ecology, School of Biological Sciences\\University of Canterbury\\Private Bag 4800\\
+Christchurch 8140, New Zealand\\
+\medskip$^2$Present address: Department of Ecology,\\
 Environment, and Plant Sciences (DEEP)\\
@@
 
-\section*{Summary}
+\section*{Summary} % Must be <200 words. Currently 199
 
   \begin{itemize}
-    \item Related plants are often hypothesised to interact with similar sets of 
-          pollinators and herbivores, but empirical support for this idea is mixed.
-          Here we argue that this may be because some plant families vary in their 
-          tendency to share interaction partners.
+    \item Related plants are often hypothesised to interact with similar sets of pollinators and herbivores, but empirical support for this idea is mixed.
+We argue that this may be because plant families vary in their tendency to share interaction partners.
 
-    \item We introduce a novel approach with which to quantify
-          overlap of interaction
-          partners for each pair of plants in 59 pollination and 11 herbivory
-          networks based on the numbers of potential interaction partners which are shared and not shared.  We then tested for relationships between phylogenetic 
-          distance and partner overlap within each network, and whether these 
-          relationships varied with the composition of the plant community.
-          Finally, we tested for different relationships within well-represented
-          plant families.
+    \item We introduce a novel way to quantify overlap of interaction partners for each pair of plants in 59 pollination and 11 herbivory networks based on the numbers of shared and unshared interaction partners.
+We test for relationships between phylogenetic distance and partner overlap within each network, and whether these relationships varied with the composition of the plant community.
+Finally, we test for different relationships within well-represented plant families.
 
-    \item Across all networks, more closely-related plants tended to have 
-          greater overlap, and this tendency was stronger in herbivory 
-          networks than pollination networks.
-While the strength of this relationship within a network was not related to the composition of the network's plant component, we nevertheless found that different plant families showed different relationships between phylogenetic distance and overlap of interaction partners.
+    \item Across all networks, more closely-related plants tended to have greater overlap, especially in herbivory networks.
+The strength of this relationship within a network was unrelated to the composition of the network's plant component, but different plant families showed different relationships between phylogenetic distance and overlap of interaction partners.
 
-    \item The variety of relationships between phylogenetic distance and
-          interaction partners in different plant families likely
-          reflects a comparable variety of ecological and evolutionary processes. To 
-          understand the distribution of interactions within a community, 
-          it is therefore important to consider factors affecting particular 
-          plant families.
+    \item The variety of relationships between phylogenetic distance and partner overlap in different plant families likely reflects a comparable variety of ecological and evolutionary processes.
+Considering factors affecting the dominant plant families within a community may be the key to understanding the distribution of interactions.
 

### 2019-07-10 manuscript/phylogenetic_signal_manuscript.tex
addressed Josh comments

@@
   In particular, significant phylogenetic signal in plants' sets of interaction partners tends to be rare in empirical networks (\citealp{Rezende2007a,Lind2015,Ibanez2016}; but see~\citealp{Elias2013,Fontaine2015,Hutchinson2017}).
-Significant degrees of phylogentic signal and/or coevolution may also lead to only small differences in network structure, adding to the difficulty of understanding patterns in species' interaction partners~\citep{Ponisio2017}.
+  Moreover, statistically significant degrees of phylogenetic signal or coevolution may only result in small differences in network structure, adding to the difficulty of understanding patterns in species' interaction partners~\citep{Ponisio2017}.
   Further, the plant and animal components of networks can show different degrees of phylogenetic conservation of interaction partners.
-In mutualistic networks, animals often show a stronger phylogenetic signal in their partners than do plants~\citep{Rezende2007a,Chamberlain2014,Rohr2014,Vamosi2014,Lind2015,Fontaine2015} (but see~\citep{Rafferty2013} for a counterexample).
+In mutualistic networks, animals often show a stronger phylogenetic signal in their partners than do plants~\citep{Rezende2007a,Chamberlain2014,Rohr2014,Vamosi2014,Lind2015,Fontaine2015} (but see~\citet{Rafferty2013} for a counterexample).
 In antagonistic networks, however, actively-foraging consumers tend to show less phylogenetic signal than their prey~\citep{Ives2006,Cagnolo2011,Naisbit2011,Fontaine2015}.
@@
   defences~\citep{Adler2006} or altering floral display or nectar 
-  availability~\citep{Strauss1997}. There may also be tradeoffs between chemical and physical defenses, or defenses at different life stages~\citep{Karinho2014,Endara2017}. Observed patterns
+  availability~\citep{Strauss1997}.
+There may also be tradeoffs between chemical and physical defenses, or defenses at different life stages, that weaken the overall heritability of plants' sets of herbivores~\citep{Karinho2014,Endara2017}.
+Observed patterns
   of similarity in plants' interaction partners therefore represent
@@
   sets of pollinators to avoid exchanging pollen with other
-  species~\citep{Levin1970,Bell2005,Mitchell2009}. Similar pressures 
-  could also affect related plants' defences against herbivores if 
-  congeners tend to grow in the same places such that herbivores 
-  could easily move between them.  Unrelated plants might also 
+  species~\citep{Levin1970,Bell2005,Mitchell2009}.
+Similarly, plants may experience disruptive selection on defenses against herbivores if congeners tend to grow in the same places such that herbivore able to consume one species could easily spread to close relatives.
+  % Similar pressures  could also affect related plants' defences against herbivores if congeners tend to grow in the same places such that herbivores could easily move between them.  
+  Unrelated plants might also 
   converge upon similar phenotypes, attracting a particularly 
   efficient or abundant pollinator~\citep{Ollerton1996,Ollerton2009,Ibanez2016}. 
-  Likewise, herbivores may be able to depredate sets of unrelated 
-  plants if the plants have evolved similar defences~\citep{Pichersky2000}. 
+  Likewise, unrelated plants may converge upon similar defenses, leading them to share herbivores which can overcome these defenses~\citep{Pichersky2000}. 
   In either case, dissimilarity of interactions among related species 
@@
   relates to network structure. Specifically,
-  we test whether niche overlap decreases over increasing phylogenetic
+  we test 1) whether niche overlap decreases over increasing phylogenetic
   distance in a large dataset of pollination and herbivory networks, 
-  whether the plant family composition of a community affects the
+  2) whether the plant family composition of a community affects the
   relationship between niche overlap and phylogenetic distance in that 
-  community, and whether the relationship between niche overlap and 
+  community, and 3) whether the relationship between niche overlap and 
   phylogenetic distance differs systematically across plant families.
@@
     correctness. This was done using the function `get\_tsn' in the R~\citep{R}
-    package taxize~\citep{taxize1,taxize2}. Species which could not 
+    package \emph{taxize}~\citep{taxize1,taxize2}. Species which could not 
     be assigned to an accepted taxonomic name (e.g., `Unknown Forb') were 
@@
     sharing most of their interaction partners over specialists sharing a single 
-    interaction partner). For each species pair, we therefore recorded the number of 
+    interaction partner).
+Note that species sharing a large \emph{number} of interaction partners may not share a large \emph{proportion} of interaction partners if the number of interaction partners that are not shared is also large.
+% Added because Josh got confused about the distinction.
+    To capture all of this information for each species pair, we therefore recorded the number of 
     shared interaction partners ($M_{ij}$) and the number of interaction partners 
@@
     niche overlap between species $i$ and $j$ as a tuple: ($M_{ij}$, $U_{ij}$).
-
-    % To fully describe the extent to which two plants' niches overlap,
-    % we defined the overlap between two plants' sets of interaction partners
-    % by recording the frequencies with which pairs of animals (where each animal 
-    % interacted with at least one plant) fall into three unique patterns
-    % (Fig.~\ref{overlap_patterns}). In the first pattern, both plants interact 
-    % with both animals, indicating total overlap for that quartet. In the second pattern, one plant
-    % interacts with both animal partners while the other
-    % interacts with only one animal, indicating partial overlap. In the third pattern,
-    % each animal interacts with only one plant, indicating no overlap. 
-    % Taken together, the frequencies of these three patterns of
-    % overlap can be used to describe the degree to which two plants have
-    % similar interaction partners. %
-
-    % Using the three patterns defined above provides more detail than other measures of overlap,
-    % such as the proportion of one species' partners that are shared with
-    % another as given by Jaccard similarity. In particular, comparing the probability of observing each pattern
-    % rather than one of the other two provides a measure of indirect
-    % interactions between plants by considering pairs of animal partners rather
-    % than each animal separately. For example, a pair of plants which share 
-    % two interaction partners are more likely to influence each other via these partners
-    % than two plants which do not share interaction partners. Moreover, our measure
-    % of overlap has greater statistical power than Jaccard dissimilarity because
-    % it includes information on the \emph{number} of shared interaction partners as
-    % well as the proportion. For instance, a pair of plants which together interact
-    % with 100 animals provides more information about shared overlap than a pair of
-    % plants which together interact with only one animal whereas the Jaccard similarity
-    % of both would simply be one.
-
-    % [[It appears we switched to Jaccard and Sorenson dissimilarities - number of shared partners and number of shared partners*2/notshared.]]
 
@@
     approach is conceptually similar to modelling successes and failures in a 
-    binomial-distributed process. Accordingly, we assumed a binomially-  distributed error structure and used a logit link function to model the 
+    binomial-distributed process. Accordingly, we assumed a binomially-distributed error structure and used a logit link function to model the 
     probability $\omega_{ij}$ of plants $i$ and $j$ sharing an interaction 
@@
     random intercepts and slopes per network. This expanded regression was fit
-    using the R~\citep{R} function ``glmer'' from package 
+    using the R~\citep{R} function `glmer from package 
     \emph{lme4}~\citep{lme4} and took the form
@@
     where $I_{ij}=1$ when plants $i$ and $j$ are drawn from a 
-    pollination network and $I_{ij}=0$ otherwise and all other symbols 
+    pollination network and $I_{ij}=0$ when $i$ and $j$ are drawn from a herbivory network, and all other symbols 
     are as above. Note that we only compared pairs of plants taken from the 
@@
   overlap with increasing distance. This variation between networks
-  echoes earlier studies \citep[e.g.,][]{Fontaine2015,Hutchinson2017}
+  echoes earlier studies \citep[e.g.,][]{Fontaine2015,Hutchinson2017},
   which also found broad evidence for phylogenetic conservation
@@
   interaction partner overlap in pollination or herbivory networks,
-  the greater importance of shallow phylogeny may be a general 
+  the greater importance of shallow phylogeny (as reported for leaf
+  miners and gallers in~\citet{Volf2017}) may be a general 
   feature of plant-insect interaction networks.
 
-  The variability of the relationship between partner overlap and
-  phylogenetic distance at the network level and the lack of influence
-  of community composition on the strength of this relationship could
-  be partly due to the different trends within families. 
+  The variability of the strength of phylogenetic signal across networks 
+  and the lack of influence of community composition on the strength of 
+  the relationship between phylogenetic distance and interaction partner
+  overlap could be partly due to the different trends within families. 
   More than half of the plant families in each network type
@@
   each other ---more than they do distantly related 
-  plants~\citep{Schemske1999,Gilbert2015,Ponisio2017}. In some families, 
-  such as \emph{Asteraceae} in pollination networks, the positive slope of 
-  this relationship was very shallow while in others, such as 
-  \emph{Melastomataceae} in herbivory networks, the positive slope was 
-  extremely steep. This could indicate different rates of phenotypic drift 
-  or evolution in different families. Alternatively, key traits
-  affecting plant-insect interactions may not be strongly
+  plants~\citep{Schemske1999,Gilbert2015,Ponisio2017}. The degree of 
+  heritability of key traits may, however, differ between families. In
+  some families, such as \emph{Asteraceae} in pollination networks, 
+  the positive slope of this relationship was very shallow while in 
+  others, such as \emph{Melastomataceae} in herbivory networks, the 
+  positive slope was extremely steep. This could indicate different 
+  rates of phenotypic drift or evolution in different families. 
+  In other families, there was no significant relationship between phylogenetic
+  distance and interaction partner overlap. In these cases, key traits affecting 
+  plant-insect interactions may not be strongly
   conserved. Studies showing a stronger relationship between trait similarity
@@
   labile~\citep{Junker2015,Ibanez2016,Endara2017}. 
+  [[Josh had some objections to this paragraph, but I didn't quite understand what he was going for. Clearer now?]]
 
@@
   selection pressures on the plants. If traits affecting pollination
-  or herbivory are not heritable in these groups~\citep{Kursar2009}
+  or herbivory are not heritable in these groups [\citealp{Kursar2009}] 
   or their phenotypes are constrained by other factors (e.g., 
   environmental conditions, trade-offs with other traits, ontogenic
-  change~\citep{Karinho2014}), then we should not expect a relationship 
+  change [\citealp{Karinho2014}]), then we should not expect a relationship 
   between phylogenetic distance and overlap of interaction partners.
@@
 All other plant families were well-represented in only one network type.
-    % DBS: The above is near indecipherable. Can we please simplify it substantially?
-    [[Simpler now?]]
     Families in pollination networks are indicated

### 2019-07-15 manuscript/phylogenetic_signal_manuscript.tex
older changes
removed Christie from author list as per her request

@@
 Mikael Ohlsson$^{4}$, Isabelle Norstr\"{o}m$^{4}$, Inger-Marie Wohlfarth Hasle$^{4}$,\\
-Joshua A. Thia$^{1,5}$, Christie J. Webber$^{1}$, Daniel B. Stouffer$^{1}$}
+Joshua A. Thia$^{1,5}$, 
+% Christie J. Webber$^{1}$, % Christie has confirmed that she'd rather be in the acknowledgements than an author
+Daniel B. Stouffer$^{1}$}
 \date{\small$^1$Centre for Integrative Ecology, School of Biological Sciences\\University of Canterbury\\Private Bag 4800\\
@@
 \medskip$^5$Present Address: School of Biological Sciences\\
-University of Queensland\\Brisbane, QLD 4072, Australia }
+The University of Queensland\\Brisbane, QLD 4072, Australia }
 
@@
 
-  We would like to thank the authors of the published networks used in this study. 
+  We thank Christiee J. Webber [[and others?]] for comments on the design of the 
+  study and for data collection. 
+  We also thank the authors of the published networks used in this study. 
   We are grateful for the use of the Edward Percival field station in Kaikoura, 

### 2019-07-24 manuscript/phylogenetic_signal_manuscript.tex
small catches from Micke

@@
   (e.g., congeners or members of the same subfamilies) is more
-  important than phylogenetic signal from deeper within the phylognetic
+  important than phylogenetic signal from deeper within the phylogenetic
   tree. This echoes earlier results relating plant phylogeny to 
@@
 Here we show the observed slopes for herbivory (green squares) and pollination (purple diamonds) networks.
+Thick, dashed lines represent the mean slopes across all networks of each type.
 The maximum and minimum slopes obtained from 999 permutations of each network are depicted by thin, black lines.

### 2019-07-24 code/create_figures/observed_vs_random_slopes.py

@@ -124,7 +124,7 @@ def overall_lineplotter(graph,nettype,slopedict):
   else:
     y=slopedict['fixef']['scale(distance)']+slopedict['fixef']['scale(distance):nettypepp']
     col=3
-  dats=graph.add_dataset([(-1,y),(1,y)])
+  dats=graph.add_dataset([(-2,y),(2,y)])
   dats.symbol.configure(shape=0,size=0)
   dats.line.configure(linestyle=3,linewidth=2.5,color=col)
 

### 2019-07-30 manuscript/phylogenetic_signal_manuscript.tex
small catches
changing Inger-Marie's name, minor typos

@@
 \author{Alyssa R. Cirtwill$^{1,2}$, Giulio V. Dalla Riva$^{3}$, Nick J. Baker$^{1}$,\\
-Mikael Ohlsson$^{4}$, Isabelle Norstr\"{o}m$^{4}$, Inger-Marie Wohlfarth Hasle$^{4}$,\\
-Joshua A. Thia$^{1,5}$, 
+Mikael Ohlsson$^{4}$, Isabelle Norstr\"{o}m$^{4}$, Inger-Marie Wohlfarth$^{4}$,\\ % All confirmed to submit
+Joshua A. Thia$^{1,5}$, % Confirmed to submit
 % Christie J. Webber$^{1}$, % Christie has confirmed that she'd rather be in the acknowledgements than an author
@@
     not shared. The Jaccard index $J_{ij}$ describes the proportion of 
-    shared interaction partners for for species $i$ and $j$ and is defined as: 
+    shared interaction partners for species $i$ and $j$ and is defined as: 
   %
@@
 
-  ARC, DBS, GVDR, and NJB designed the research. ARC, MO, IN, and IMWH, JAT, and CJW collected published data. 
+  ARC, DBS, GVDR, and NJB designed the research. ARC, MO, IN, and IMW, JAT, and CJW collected published data. 
   ARC and GVDR performed the analyses. All authors contributed to the manuscript.

### 2019-07-30 manuscript/supporting_info.tex
increased size of Fig. S2
trimmed summary to fit word limit, small formatting tweaks
older changes
small catches from Micke
changing Inger-Marie's name, minor typos

@@
 \author{Alyssa R. Cirtwill$^{1,2}$, Giulio V. Dalla Riva$^{3}$, Nick J. Baker$^{1}$,\\
-Mikael Ohlsson$^{4}$, Isabelle Norstr\"{o}m$^{4}$, Inger-Marie Wohlfarth Hasle$^{4}$,\\
-Joshua A. Thia$^{1,5}$, Christie J. Webber$^{1}$, Daniel B. Stouffer$^{1}$}
+Mikael Ohlsson$^{4}$, Isabelle Norstr\"{o}m$^{4}$, Inger-Marie Wohlfarth$^{4}$,\\
+Joshua A. Thia$^{1,5}$, 
+% Christie J. Webber$^{1}$, 
+Daniel B. Stouffer$^{1}$}
 \date{\small$^1$Centre for Integrative Ecology, School of Biological Sciences\\
@@
 \baselineskip=8.5mm
-\begin{spacing}{1.0}
+\begin{spacing}{1.5}
 
+\linenumbers
 \beginsupplement
@@
         \begin{center}
-          \centerline{\includegraphics*[width=.75\textwidth]{Figures/random_p_distributions.eps}}
+          \centerline{\includegraphics*[width=.99\textwidth]{Figures/random_p_distributions.eps}}
         \end{center}
+        \vspace{-1cm}
          \caption{\small Nearly uniform distributions of $p$-values where obtained when comparing the strength of the relationship between niche overlap and phylogenetic distance in 999 permutations of each network in our dataset with 500 permutations of each permuted network.

### 2019-07-31 manuscript/phylogenetic_signal_manuscript.tex
found Christie still in author contributions

@@
 Thus, it is not straightforward to assume that interactions will always be similar among related species.
-[[GVDR was skeptical of a similar point in the previous draft - less contentious now?]]
-  % Further, plants' roles [[how defined?]] within networks tend to be less phylogenetically constrained than those of 
-  % animals~\citep{Rezende2007a,Chamberlain2014,Rohr2014,Vamosi2014,Lind2015}.
-[[GVDR is skeptical of this - check partiteness, size, type of role and add more detail to support.]] % I doubt this is really important, probably more trouble than it's worth.
 
@@
   labile~\citep{Junker2015,Ibanez2016,Endara2017}.
-  [[Josh had some objections to this paragraph, but I didn't quite understand what he was going for. Clearer now?]]
 
@@
 
-  We thank Christiee J. Webber [[and others?]] for comments on the design of the 
+  We thank Christiee J. Webber for comments on the design of the 
   study and for data collection. 
@@
 
-  ARC, DBS, GVDR, and NJB designed the research. ARC, MO, IN, and IMW, JAT, and CJW collected published data. 
+  ARC, DBS, GVDR, and NJB designed the research. ARC, MO, IN, IMW, and JAT collected published data. 
   ARC and GVDR performed the analyses. All authors contributed to the manuscript.

### 2019-08-02 manuscript/reply_to_referees.tex
ummm submitted this as well on request of the managing editor.|

@@
 
+{\Large \bf Preface}
+
+Here we include the Reply to Referees for a previous submission of this manuscript.
+Note that we substantially changed our methodology and repeated all analyses such that many of the Referee comments do not apply to the current submission.
+We appreciate the Referee's feedback and feel that we have been able to substantially improve the manuscript after consideration of their comments.
+
+\clearpage
+
 % -----------------------------------------------------------------------------
@@
 They were concerned that our novel approach had not been properly validated or compared to previous methods, and that we did not have within-family resolution for our tree.
+In the current submission we have adopted a more tried-and-true methodology and now use an improved phylogeny.
 We respond (preceded by \textbf{R:}) to each of these concerns in detail below.
@@
 
-    \textbf{R:} Solution was something to do with making >100 simulations of each empirical network and then >100 simulations of each simulation...
+    \textbf{R:} We now use a more common method (logistic regression of Jaccard dissimilarity between plants' interaction partners) rather than our previous attempt to quantify degrees of overlap among quartets of species.
+In addition, we have validated the statistical power of our approach by repeating our analyses using permutations of the original networks.
+We hope that this proves more convincing.
 
@@
 
-    \textbf{R:} I need to re-read these papers. As I recall, they were asking slightly different questions but I didn't fully understand their methodologies.
-
-      %     Our study and those that the author mention are designed to answer different
-      % questions. Ives \& Godfray (2006) developed their method to ask whether a
-      % plant (or the majority of plants in a community) is visited by a related set of 
-      % pollinators (and vice versa). We are interested in whether related plants are 
-      % visited by similar sets of pollinators, regardless of whether or not the 
-      % pollinators are related. It is not obvious how to translate the results of their 
-      % method (e.g., individual species of pollinators tend to visit related sets of plants) 
-      % to our question, as two closely-related plants might be visited by non-overlapping 
-      % sets of pollinators which nevertheless tend to visit related plants. This could 
-      % occur, for example, if plants within a particular genus grow either in the 
-      % understory or in more open microhabitats and each pollinator visits only plants of 
-      % this genus that grow within its preferred microhabitat.
-
-      % Similarly, Rafferty \& Ives (2013) used two phylogenetic linear
-      % mixed models (PLMM's) to model the strength of plant-pollinator
-      % interactions as a function of 1) plant traits and pollinator
-      % phylogeny; and 2) plant and pollinator phylogenies. We were instead
-      % interested in modelling plants' traits (i.e., their interaction
-      % partners) over their phylogeny. In our case, we did not have pollinator
-      % phylogenies and our `trait' of interest was the set of animals with
-      % which a plant interacts. In Rafferty \& Ives' first PLMM, then, we
-      % would need to include network structure as both a dependent and the
-      % independent variable, while in the second we would be obliged to assume
-      % that the pollinator phylogenies were completely uninformative. This is
-      % almost certainly not the case. More importantly, even if we accept this
-      % limitation and model the strength (or in our case, binary presence or 
-      % absence) of interactions purely based on the plant phylogeny, it is not
-      % clear how this model would allow us to assess whether or not plants 
-      % tend to interact with similar \emph{sets} of animals. That is, we are not
-      % interested in whether each particular animal has similar probabilities
-      % of interacting with closely-related plants but rather in the amount of
-      % overlap in the sets of animals that visit related and unrelated plants.
-
-      % Hadfield \emph{et. al.}'s 2014 study addresses questions that are even
-      % further from our study's focus. The authors of that study are mainly
-      % interested in the interplay of two phylogenies (also a focus of
-      % Rafferty \& Ives, 2013, but to a lesser degree). In our datset, we
-      % had access to phylogenies for the plants but not their animal interaction
-      % partners. As such, the referee is correct in noting that we do not 
-      % identify sources of phylogenetic signal \emph{a la} Hadfield \emph{et. al.}.
-      % In our study, we cannot test for co-evolution of plants and their 
-      % partners or for other forms of evolutionary interaction between them. 
-      % Without being able to eliminate these possibilities, testing for an 
-      % effect of animal or plant specialism on interaction patterns tells us
-      % little about the effect of plants' evolutionary histories.
-
-      % [[We have edited the main text to make our question of interest (and
-      % the ways in which it differs from the questions asked by other 
-      % researchers) clearer. We have also added tests for type I and type II
-      % statistical errors, as described below. We hope that this will provide
-      % a sufficient indication of the quality of our method, as we cannot 
-      % in good concience compare our results to those of methods asking different
-      % questions.]]
+    \textbf{R:} We thank the Referee for the literature suggestions.
+Ultimately, we opted to change our methodology to a less novel and hopefully more palatable approach.
+Therefore we have not explicitly compared our approach with those mentioned above.
 
@@
 
+\clearpage
+
 \section*{Referee 2}
 
-  Referee 2 was very positive about our manuscript and only had a few minor suggestions. We thank the Referee for her thoughtful input.
+  Referee 2 was very positive about our manuscript and only had a few minor suggestions.
+We thank the Referee for her thoughtful input.
+In the present submission, however, we were more focused on the more fundamental issues of methodology.
+We apologise deeply for neglecting the suggestions below and hope to address them in a subsequent round of revisions, after questions about our methodology have been satisfied.
 
@@
     \end{refquote}
-
-    \textbf{R:} Assuming this still fits after re-analysis, seems like a good idea.
 
@@
 
-    \textbf{R:}
-
 \section*{Referee 3}
@@
 
-      \textbf{R:}
+      \textbf{R:} We thank the Referee for this suggestion and have repeated our analyses using permutations of the original networks, as requested.
 
@@
 
-    \textbf{R:} We hope that the Referee appreciates the fact that length restrictions limit our ability to go into too much detail in the Discussion without severely compromising our explanation of the methods.
-Nevertheless, where possible we have added biological details throughout the manuscript.
-We have taken particular care to address the specific points the Referee has highlighted above.
+    \textbf{R:} We appreciate the Referee's comments, but feel that a detailed discussion of the traits (flower morphology, metabolites, etc.) is beyond the scope of this manuscript.
+In particular, the interaction networks we use did not contain any information on plant traits.
+Any inference we might draw based on more general literature would therefore be highly speculative.
+Taking the Referee's broader point that our manuscript lacked biological detail, however, we have revised the introduction and discussion where possible to include more nuance.
+We hope that these additions have improved the discussion.
 
@@
 
-    \textbf{R:} As we used published networks rather than collecting data ourselves, we cannot provide information on the exhaustiveness of sampling other than that given in the original sources (detailed in the SI).
+    \textbf{R:} As we used published networks rather than collecting data ourselves, we cannot provide information on the exhaustiveness of sampling.
 In particular, we cannot say which apparently specialist pollinators appear specialized because of rarity and which are genuinely specialized as data on abundances were not published together with the bulk of the metworks we used.
 The questions the Referee asks about the adequacy of sampling and specialization in plant-pollinator networks are very important, but we respectfully suggest that they are best addressed by encouraging empirical researchers to publish abundance data as well as interaction networks.
-There is very little we can do to address these questions when re-analysing the limited data that have been made available.
-
-   One thing we can do, however, is investigate the effects of lumping grasshoppers in with other herbivores.
-To that end, we have repeated our analyses excluding the plant-herbivore networks which contained grasshoppers.
-As removing these networks substantially reduces our already small collection of plant-herbivore networks, we retain these networks in the main text and present the re-analysis in the SI.
-[[What changed?]]
+There is very little we can do to address these questions \emph{post hoc} when re-analysing the limited data that have been made available.
 
@@
 
-      \textbf{R:} We appreciate the Referee's frankness.
+      \textbf{R:} We appreciate the Referee's frankness. Due to comments by this Referee and Referee 1 we have changed our methodology. We hope that the new methods are clearer and more appoachable.
 
@@
 
-      \textbf{R:}
+      \textbf{R:} We do not agree that it is sensible to swap plants between network types.
+Antagonistic interaction networks tend to be structured quite differently from mutualistic networks, such that a mixture of the two is not a good null model for either network type.
+Moreover, as many plant families and genera are quite widespread and/or morphologically similar to species in other continents.
+We therefore see no particular reason by network structure should differ betweeen continents.
+Without a stronger justification for this additional layer of stratification, we have left the null model approach as-is.
 
@@
 
-  7. The Referee is confused
+  7. Some phrasing puzzling
 
@@
 
-    \textbf{R:} We do not understand why the Referee finds some of the above examples confusing, particularly "plants that produce noxious secondary metabolites may suffer fewer herbivores".
-We have nevertheless rephrased the cited examples and revised our manuscript for clarity.
-This request for simpler phrasing often comes at the cost of brevity, which unfortanately makes it very difficult to comply with the Referee's demand for more biological detail (point 2).
-We hope that we have struck a reasonable balance between these two criticisms.
+    \textbf{R:} We do not understand what is puzzling about these sentences and have not been able to find a simpler, yet accurate, way to phrase them.
+We hope that adopting a more straightforward methodology will improve the manuscript's overall readability and allow the Referee to follow these points.
+If not, we welcome further feedback as to how we may improve our writing.
 
-  8. The Referee hates our conclusion
+  8. The Referee dislikes our conclusion
 
@@
       \textbf{R:} We are confused by the Referee's argument that communities show no clear boundaries in either space or time and that there is little evidence of heritability in traits within a community.
-This seems to suggest that the Referee does not believe in ecological communities or networks as viable units of study or in evolution (which requires heritability of traits).
-If this is so, then the Referee is not an appropriate reviewer for this manuscript.
-We instead hope that the Referee is attempting to make the point that communities are not shaped for the benefit of the species within them and simply doing so in an unclear way.
-That being the case, of course we are aware of this and agree 100\%.
-We did not intend to suggest that either species are selected to stabilize their communities or that communities are selected to maintain the species within them.
-We are well aware of spatial and temporal turnover, and of the fact that most communities are not at equilibrium and therefore we should not expect network structure to remain constant.
-Our point was rather that a more stable community is likely to persist longer than a less stable community and, therefore, more likely to be observed.
-We therefore expect communities with patterns of interactions condusive to long-term persistence to be over-represented in the empirical networks available to us.
-We have revised and expanded our conclusion to explicitly state that we are \textbf{not} suggesting any kind of community-level selection process, only the disproportionate change of unstable communities to more stable ones.
-We hope that this revision is less objectionable to the Referee.
+This seems to suggest that the Referee does not believe in ecological communities or networks as viable units of study, which is the entire basis of network ecology.
+We fully agree that communities change over time (including both community turnover and species traits), but do not believe that this means we can learn nothing from studying current communities.
+
+      Moreover, we do not suggest that either species are selected to stabilize their communities or that communities are selected to maintain the species within them and are not sure how the Referee has got this idea.
+In our original manuscript, we referred to the over-representation of stable communities.
+Note that this can occur purely due to the longer persistence of stable than unstable configures of species, with no selection required.
+However, this theme was peripheral to the main goal of our study and,
+      to avoid such confusion in the future, our discussion no longer references community stability.
 

### 2019-08-06 manuscript/reply_to_referees.tex
some more revisions since the reply was requested

@@
 \setcounter{page}{1}
-
-{\Large \bf Preface}
-
-Here we include the Reply to Referees for a previous submission of this manuscript.
-Note that we substantially changed our methodology and repeated all analyses such that many of the Referee comments do not apply to the current submission.
-We appreciate the Referee's feedback and feel that we have been able to substantially improve the manuscript after consideration of their comments.
-
-\clearpage
 
@@
 
-      Regarding the phylogenetic patterns within plant families, I am afraid that the authors do not have neither topological nor cronological resolution in the phylogenetic tree to run these analyses.
+      Regarding the phylogenetic patterns within plant families, I am afraid that the authors do not have neither topological nor chronological resolution in the phylogenetic tree to run these analyses.
 The topology provided by phylomatic is resolved at the family level, and then it may produce a lot of polytomies at the genus and species level.
@@
 Fortunately, while this manuscript was being revised a recent dated tree (that of Zanne \emph{et al.}, 2014) has been incorporated into the Phylomatic web tool.
-We have rebuilt our dated trees using this phlogeny, which incorporates within-family divisions.
+We have rebuilt our dated trees using this phylogeny, which incorporates within-family divisions.
 We hope that this additional detail will satisfy the reviewer.
@@
 
-\section*{Referee 2}
+{\Large \bf Reply to Referee \#2}
 
@@
 We thank the Referee for her thoughtful input.
-In the present submission, however, we were more focused on the more fundamental issues of methodology.
-We apologise deeply for neglecting the suggestions below and hope to address them in a subsequent round of revisions, after questions about our methodology have been satisfied.
+Our responses (preceded by \textbf{R:}) give more detail as to how we have included her suggestions in our revised manuscript.
 
@@
     \end{refquote}
+
+    \textbf{R:} We thank the Referee for the suggestion, and have changed our title to "At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families." We hope that this successfully communicates a bigger message.
 
@@
 
-\section*{Referee 3}
+      \textbf{R:} We thank the Referee for the suggestions.
+While we have not performed new analyses along this line (instead, we focused on changing our methodology in response to comments from the other two Referees), we are happy to include some references to these ideas in our discussion.
+In particular, we now end the manuscript by mentioning the possibilities for phylogenetic distance between plants to affect interaction strengths as well as presence/absence, and mention the suggested authors' very interesting findings with regard to spatial structure.
+As our dataset does not contain information on spatial structure we cannot test such ideas in our manuscript, but it is a very intriguing avenue for future work.
 
-  Referee 3 saw "the potential [[for our study]] to become a significant contribution to the field of ecological networks" if a number of significant issues are addressed.
-Specifically, the Referee found several sections to be unclear, the discussion to be shallow, and lacked confidence in our statistical analyses.
-We address each point below and hope that our responses (preceded by \textbf{R:}) will satisfy the Referee.
+      Lines 346-354:
 
-  1. Use randomization tests to address non-independence of pairs of species
+      \begin{quotation}
+
+        The lack of a significant relationship between
+        phylogenetic distance and interaction partner overlap in many
+        networks could be partly due to the large number of extreme
+        specialists, especially among the pollination networks.
+        These species interact with only one plant and
+        therefore weaken any signal of interaction partner overlap.
+        The herbivory networks did not contain as many obligate 
+        specialists, but we note that many herbivorous insects are
+        oligotrophs which consume only a few closely-related hosts~\citep{Yguel2011,Castagneyrol2014}.
+        These oligotrophs may affect overall phylogenetic signal in the same
+        way as the specialist partners: in both cases plants in different
+        families are unlikely to share interaction partners.
+
+      \end{quotation}
+
+      Lines 449-458:
+
+      \begin{quotation}
+
+        Although here we considered only the presence or absence of interactions,
+        recent work also suggests that the phylogenetic composition of a plant
+        community can affect the strength of 
+        interactions, and that the spatial arrangement of plants within a 
+        community may be particularly important~\citep{Yguel2011,Castagneyrol2014}.
+        If so, then the study of how phylogenetic relationships between plants
+        affect their interactions with animals has only just begun.
+
+      \end{quotation}
+
+\clearpage
+
+{\Large \bf Reply to Referee \#3}
+
+  Referee 3 saw "the potential [for our study] to become a significant contribution to the field of ecological networks" if a number of significant issues are addressed.
+Like Referee 1, this Referee lacked confidence in our methods.
+We address each point of criticism below and hope that our responses (preceded by \textbf{R:}) will satisfy the Referee.
+
+  1. Use randomisation tests to address non-independence of pairs of species
 
@@
 These data points, as a consequence, are not independent and the authors need to incorporate this dependency in their analysis.
-A simple way of circumvent this problem is to use randomization tests to build up an empirical distribution for the metric of interest in the presence of the dependency of data points.
+A simple way of circumvent this problem is to use randomisation tests to build up an empirical distribution for the metric of interest in the presence of the dependency of data points.
 
@@
     \textbf{R:} We appreciate the Referee's comments, but feel that a detailed discussion of the traits (flower morphology, metabolites, etc.) is beyond the scope of this manuscript.
-In particular, the interaction networks we use did not contain any information on plant traits.
-Any inference we might draw based on more general literature would therefore be highly speculative.
-Taking the Referee's broader point that our manuscript lacked biological detail, however, we have revised the introduction and discussion where possible to include more nuance.
+Our dataset does not include any information on which plant (or arthropod) traits were present.
+We are therefore unable to test any trait-based inference, so any statements we might make to that effect would be highly speculative.
+We agree that traits are highly likely to mediate plant-animal interactions (together with abundance, spatial structure of the community, the presence of other interaction partners such as predators of the animals, etc.) but feel that testing the effects of traits is better done in a more spatially/taxonomically restricted dataset that is collected for this purpose.
+
+    Taking the Referee's broader point that our manuscript lacked biological detail, however, we have revised the introduction and discussion where possible to include more nuance (keeping in mind the limitations of space and the fact that traits are not the main focus of our manuscript).
 We hope that these additions have improved the discussion.
+We have also edited the manuscript to remove lines 238-248 and 339-341 as the Referee found these confusing.
+
+    Finally, seed-dispersal syndromes may well be associated with shared evolutionary history, but this says little about pollination syndromes.
+Different traits and different sets of animal partners are involved, and the strength of selection pressures may also differ.
+Seed-dispersal syndromes may also be better-defined; as Ollerton et.
+al (2009, Annals of Botany) point out, "pollination syndromes" tend to be rather vague ideas.
+In any case, we do not see why pollination should behave the same way as seed dispersal and have not altered this part of the discussion as we still believe that the question is worth testing.
+Note that pollination syndromes might still predict interaction partners if phylogenetic signal in partner overlap is weak if all plants in a family belong to the same syndrome.
+This is the logic behind our proposal and sounds similar to what the Referee is describing in seed-dispersal syndromes.
 
@@
     \textbf{R:} As we used published networks rather than collecting data ourselves, we cannot provide information on the exhaustiveness of sampling.
-In particular, we cannot say which apparently specialist pollinators appear specialized because of rarity and which are genuinely specialized as data on abundances were not published together with the bulk of the metworks we used.
+In particular, we cannot say which apparently specialist pollinators appear specialised because of rarity and which are genuinely specialised as data on abundances were not published together with the bulk of the networks we used.
 The questions the Referee asks about the adequacy of sampling and specialization in plant-pollinator networks are very important, but we respectfully suggest that they are best addressed by encouraging empirical researchers to publish abundance data as well as interaction networks.
@@
 
-      Some methodological approaches are not clear and becase of that it would be impossible to replicate this study.
+      Some methodological approaches are not clear and because of that it would be impossible to replicate this study.
 
@@
 
-      \textbf{R:} We appreciate the Referee's frankness. Due to comments by this Referee and Referee 1 we have changed our methodology. We hope that the new methods are clearer and more appoachable.
+      \textbf{R:} We appreciate the Referee's frankness. Due to comments by this Referee and Referee 1 we have changed our methodology. We hope that the new methods are clearer and more approachable.
 
@@
 In contrast, the authors randomize species from pollinator networks that are occuring in distinct biogeographical regions.
-I understand that in such kind of broad scale study we need to simplify the use of biological information, but a really robust approach would control for non-sense geographical swaps (e.g., among distinct continents) and to prevent the swap that place plants that are not pollinated by animals in pollinator networks but otherwise would allow that plant species to be swaped between network types.
+I understand that in such kind of broad scale study we need to simplify the use of biological information, but a really robust approach would control for non-sense geographical swaps (e.g., among distinct continents) and to prevent the swap that place plants that are not pollinated by animals in pollinator networks but otherwise would allow that plant species to be swapped between network types.
 
@@
 Antagonistic interaction networks tend to be structured quite differently from mutualistic networks, such that a mixture of the two is not a good null model for either network type.
-Moreover, as many plant families and genera are quite widespread and/or morphologically similar to species in other continents.
-We therefore see no particular reason by network structure should differ betweeen continents.
-Without a stronger justification for this additional layer of stratification, we have left the null model approach as-is.
+This would tend to over-inflate the significance of our results and is not worth doing without a very strong justification that networks are structured differently between continents.
+As many plant families and genera are quite widespread and/or morphologically similar to species in other continents, we do not believe that we could give such a justification.
+We have therefore left the null model approach as-is.
 
@@
 As both of these clades have already been published, repeating them in our manuscript would be purely redundant.
+We hope that these improved dates will satisfy the Referee.
 
@@
       Some sentences are just hard to follow and/or are puzzling.
-Exemples include but are not limited to: "These relationships were also significantly related to the composition of the network’s plant component", "plants that produce noxious secondary metabolites may suffer fewer herbivores", "Interestingly, in our analyses the plant families associated with the steepest relationships between niche overlap and phylogenetic distance at the network level did not show particularly steep relationships within themselves".
+Examples include but are not limited to: "These relationships were also significantly related to the composition of the network’s plant component", "plants that produce noxious secondary metabolites may suffer fewer herbivores", "Interestingly, in our analyses the plant families associated with the steepest relationships between niche overlap and phylogenetic distance at the network level did not show particularly steep relationships within themselves".
 
@@
 
-    \textbf{R:} We do not understand what is puzzling about these sentences and have not been able to find a simpler, yet accurate, way to phrase them.
-We hope that adopting a more straightforward methodology will improve the manuscript's overall readability and allow the Referee to follow these points.
-If not, we welcome further feedback as to how we may improve our writing.
+    \textbf{R:} While the Referee's feedback is rather vague, we have revised the manuscript to improve clarity.
+If the Referee would care to give more detail about any remaining points that are unclear, we can revise them in a more targeted manner.
 
@@
 
-      Moreover, we do not suggest that either species are selected to stabilize their communities or that communities are selected to maintain the species within them and are not sure how the Referee has got this idea.
+      Moreover, we do not suggest that either species are selected to stabilise their communities or that communities are selected to maintain the species within them and are not sure how the Referee has got this idea.
 In our original manuscript, we referred to the over-representation of stable communities.
 Note that this can occur purely due to the longer persistence of stable than unstable configures of species, with no selection required.
-However, this theme was peripheral to the main goal of our study and,
-      to avoid such confusion in the future, our discussion no longer references community stability.
+However, this theme was peripheral to the main goal of our study and, to avoid such confusion in the future, our discussion no longer references community stability.
+
+\newpage
+\bibliographystyle{newphy}
+\renewcommand*{\bibfont}{\raggedright}
+\bibliography{manual}
 

### 2019-08-06 manuscript/phylogenetic_signal_manuscript.tex
some more revisions since the reply was requested

@@
 
-\title{Conservation of interaction partners between related plants varies widely across communities and between plant families.}
+\title{At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families.}
 
@@
 \section*{Introduction}
-\linenumbers
+% \linenumbers
 
@@
   pollinators~\citep{Robertson1999} whereas plants that produce noxious 
-  secondary metabolites may suffer fewer herbivores~\citep{Johnson2014}. 
+  secondary metabolites may have fewer herbivores~\citep{Johnson2014}. 
   A plant's traits are also likely to determine \emph{which} specific pollinators 
@@
   availability~\citep{Strauss1997}.
-There may also be tradeoffs between chemical and physical defenses, or defenses at different life stages, that weaken the overall heritability of plants' sets of herbivores~\citep{Karinho2014,Endara2017}.
+There may also be trade-offs between chemical and physical defences, or defences at different life stages, that weaken the overall heritability of plants' sets of herbivores~\citep{Karinho2014,Endara2017}.
 Observed patterns
@@
   species~\citep{Levin1970,Bell2005,Mitchell2009}.
-Similarly, plants may experience disruptive selection on defenses against herbivores if congeners tend to grow in the same places such that herbivore able to consume one species could easily spread to close relatives.
+Similarly, plants may experience disruptive selection on defences against herbivores if congeners tend to grow in the same places such that herbivore able to consume one species could easily spread to close relatives~\citep{Kursar2009}.
   % Similar pressures  could also affect related plants' defences against herbivores if congeners tend to grow in the same places such that herbivores could easily move between them.  
@@
   converge upon similar phenotypes, attracting a particularly 
-  efficient or abundant pollinator~\citep{Ollerton1996,Ollerton2009,Ibanez2016}. 
-  Likewise, unrelated plants may converge upon similar defenses, leading them to share herbivores which can overcome these defenses~\citep{Pichersky2000}. 
+  efficient or abundant pollinator~\citep{Ollerton1996,Wilson2007,Ollerton2009,Ibanez2016}. 
+  Likewise, unrelated plants may converge upon similar defences, leading them to share 
+  those herbivores which can overcome these defences~\citep{Pichersky2000}. 
   In either case, dissimilarity of interactions among related species 
@@
     weight to species sharing a large number of interaction partners as well as 
-    those sharing a large proportion (i.e., to emphasize pairs of generalists 
+    those sharing a large proportion (i.e., to emphasise pairs of generalists 
     sharing most of their interaction partners over specialists sharing a single 
@@
   %
-    where $\eta_{N}$ is the number of plant pairs in network $N$ for which distances could be calculated, $I_N$ is an indicator equal to 1 if network $N$ is a pollination network and 0 otherewise.
+    where $\eta_{N}$ is the number of plant pairs in network $N$ for which distances could be calculated, $I_N$ is an indicator equal to 1 if network $N$ is a pollination network and 0 otherwise.
 
@@
     Models for two families did not converge.
-In the \emph{Lauraceae}, (represented by four species in one pollination network) and the \emph{Sapindaceae} (represented by five species in one herbivory network and five species in two pollination networks), only one pair of species per network type shared any interaction partners while all other pais did not share any interaction partners.
+In the \emph{Lauraceae}, (represented by four species in one pollination network) and the \emph{Sapindaceae} (represented by five species in one herbivory network and five species in two pollination networks), only one pair of species per network type shared any interaction partners while all other pairs did not share any interaction partners.
 
@@
   of interaction partners despite variation between particular 
-  networks. 
-  % The lack of a relationship between phylogenetic
-  % distance and interaction partner overlap in many networks 
-  % could have several explanations. First, our dataset included
-  % many extreme specialists, especially among the pollination 
-  % networks. These species interact with only one plant and
-  % therefore weaken any signal of interaction partner overlap.
+  networks. The lack of a significant relationship between
+  phylogenetic distance and interaction partner overlap in many
+  networks could be partly due to the large number of extreme
+  specialists, especially among the pollination networks.
+  These species interact with only one plant and
+  therefore weaken any signal of interaction partner overlap.
+  The herbivory networks did not contain as many obligate 
+  specialists, but we note that many herbivorous insects are
+  oligotrophs which consume only a few closely-related 
+  hosts~\citep{Novotny2005,Yguel2011}.
+  These oligotrophs may affect overall phylogenetic signal in the same
+  way as the specialist partners: in both cases plants in different
+  families are unlikely to share interaction partners.
 
@@
   a network and the relationship between phylogenetic distance and
-  interaction partner overlap in pollination or herbivory networks,
+  interaction partner overlap in either pollination or herbivory networks,
   the greater importance of shallow phylogeny (as reported for leaf
   miners and gallers in~\citet{Volf2017}) may be a general 
-  feature of plant-insect interaction networks.
+  feature of plant-insect interaction networks. This contrasts with
+  the findings of~\citet{Chamberlain2014}, who found that the \emph{shape}
+  of the phylogenetic tree rather than whether speciation was more or
+  less recent had a larger effect on network structure. As~\citet{Chamberlain2014}
+  were interested in overall structural properties of networks rather
+  than interaction partner overlap, this discrepancy may indicate that
+  different aspects of plant-insect interaction networks are influenced
+  by different aspects of plant phylogenies.
 
@@
   similar to the expectation that greater constraints upon consumers 
-  than upon their resources explains the assymmetry in conservation  
+  than upon their resources explains the asymmetry in conservation  
   of interaction partners~\citep{Fontaine2015}. Plants
@@
   between overlap and phylogenetic distance at the network level.  
-  Interestingly, in our analyses the plant families associated with
-  the steepest relationships between niche overlap and phylogenetic
-  distance at the network level did not show particularly steep
-  relationships within themselves. This result suggests
-  that it is not just which plant families are present but the additional 
-  relationships between the families that affects conservation of
-  interactions at the network level and is consistent with previous
-  work showing that the shape of phylogenetic tress, as well as the
-  phylogenetic distances between species, can affect the strength
-  of phylogenetic signal~\citep{Chamberlain2014a}.
+  Although here we considered only the presence or absence of interactions,
+  recent work also suggests that the phylogenetic composition of a plant
+  community can affect the strength of 
+  interactions, and that the spatial arrangement of plants within a 
+  community may be particularly important~\citep{Yguel2011,Castagneyrol2014}.
+  If so, then the study of how phylogenetic relationships between plants
+  affect their interactions with animals has only just begun.
+  % This result suggests
+  % that it is not just which plant families are present but the additional 
+  % relationships between the families that affects conservation of
+  % interactions at the network level and is consistent with previous
+  % work showing that the shape of phylogenetic tress, as well as the
+  % phylogenetic distances between species, can affect the strength
+  % of phylogenetic signal~\citep{Chamberlain2014a}.
 
@@
 
-  We thank Christiee J. Webber for comments on the design of the 
+  We thank Christie J. Webber for comments on the design of the 
   study and for data collection. 

### 2019-08-06 manuscript/supporting_info.tex
some more revisions since the reply was requested

@@
 
-\title{Conservation of interaction partners between related plants varies widely across communities and between plant families - Supporting Information}
+\title{At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families - Supporting Information}
 

### 2019-11-13 manuscript/reply_to_referees_2.tex
launching second reply

\documentclass[12pt]{letter}

%\usepackage[britdate]{stockholm-letter}
 \usepackage[britdate,alyssa-signature]{stockholm-letter}
\usepackage{times}
\usepackage{letterbib}
\usepackage{geometry}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{graphicx}
\geometry{a4paper}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage[running]{lineno}
\usepackage{amsmath,amsfonts,amssymb}
% \usepackage[margin=10pt,font=small,labelfont=bf]{caption}

%\usepackage{natbib}
% \bibpunct[; ]{(}{)}{;}{a}{,}{;}

\newenvironment{refquote}{\bigskip \begin{it}}{\end{it}\smallskip}

\newenvironment{figure}{}

\position{Postdoctoral fellow}
\department{Department of Ecology, Evolution, and Plant Sciences}
\location{Private Bag 4800}
\telephone{+64 3 364 2729}
\fax{+64 3 364 2590}
\email{alyssa.cirtwill@gmail.com}
\url{http://cirtwill.github.io}
\name{Alyssa R. Cirtwill}

\newcommand{\mytitle}{\emph{At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families.}}
\newcommand{\myjournal}{\emph{New Phytologist}}

\begin{document}

\begin{letter}{\bf Dr. Jana Vamosi\\
               Editor\\
               Proceedings of the Royal Society B\\
               6-9 Carlton House Terrace\\
               London, UK\\
               SW1Y 5AG\\
                }

\opening{Dear Dr. Vamosi:}

\closing{Regards,}

\end{letter}

\newpage

\setcounter{page}{1}

NPH-MS-2019-30803 At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families.
by Cirtwill, Alyssa; Dalla Riva, Giulio; Baker, Nick; Ohlsson, Mikael; Norström, Isabelle; Wohlfarth, Inger-Marie; Thia, Josh; Stouffer, Daniel

Dear Dr Cirtwill

I write you in regard to your submitted manuscript, NPH-MS-2019-30803 "At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families.”, which has now been reviewed. We found four reviewers (some original reviewers and some new) and they all generally enjoyed your revised manuscript. However, they also provided suggestions for some expanding certain sections and providing additional clarification. In particular, Reviewer #2 and #4 provide some detailed suggestions, especially with regard to keeping the aims and logic consistent, that will help strengthen the manuscript.

Although resolving these issues will require some restructuring, I think you should be able to handle these suggestions through revision (see below) and, ultimately, this manuscript will make a nice contribution to the literature.

Please carefully revise your manuscript and resubmit your revised version within 4 weeks. Please also include a summary of how you have incorporated the suggestions of the reviewers.

Thank you for submitting your work to New Phytologist.

Sincerely,

Jana Vamosi
Editor, New Phytologist

*****************************************************************
To revise your manuscript please click on the link below
*** PLEASE NOTE: This is a two-step process. After clicking on the link, you will be directed to a webpage to confirm. ***

https://mc.manuscriptcentral.com/newphytologist?URL_MASK=ebf0a265cb2d423bb35580e635386130

Alternatively log on to New Phytologist ScholarOne Manuscripts:
http://mc.manuscriptcentral.com/newphytologist

Enter your Author Centre.

Under the ‘My Manuscripts' list click on 'Manuscripts with Decisions'. From the list of manuscripts click the ‘create a revision' link, next to the manuscript you wish to submit a revision for. From here follow the instructions inputting you responses to the decision letter through to the uploading of your new files.

Please note you will be unable to make your revisions directly on the submitted ScholarOne Manuscripts version of your manuscript. Instead, you should revise your original word processor file, and then submit the revised version. When revising your manuscript, please prepare two versions: 1) the final revised manuscript and 2) the revised manuscript with revision marks showing. The latter file should be designated as a 'document with revision changes highlighted' when uploading.

In any correspondence regarding this manuscript, please include the manuscript reference number and copy the correspondence to New Phytologist Central Office (np-managinged@lancaster.ac.uk).
*************************************************************

Decision: Accept subject to revision

\clearpage

{\Large \bf Reply to Referee 1}

\begin{refquote}
Having read the manuscript and the response to previous reviewers’ comments, I do not see any further changes that need to be made. Any concerns I would have had, have been addressed by the latest round of revisions. I did not even spot any typos!
\end{refquote}

\textbf{R:} We thank the referee for taking the time to read our manuscript and for the compliment to our proof-reading.

\clearpage

{\Large \bf Reply to Referee 2}

	\begin{refquote}
	General comments

	The manuscript proposes to evaluate how phylogeny modulates species interaction patterns in plant-pollinator and a subset of plant-herbivory networks. In this regard, it explores an extremely relevant question for ecologists. However, it still needs work on the logic of the introduction section and methodological decisions need to be revised in order to achieve more confident results. The Introduction lacks focus and presents unclear aims, which leads to an unfocused discussion of the results, being one of the main weaknesses of the manuscript. Also, there is a lack of logical consistency between the abstract (methodologically-oriented) and the introduction and discussion sections (both biologically-oriented). On the other hand, we do not understand why authors do not incorporate ideas of species evolution and coevolution in a network context if you are trying to understand how phylogenetic constraints may modulate species interaction patterns in networks. Considering such exciting ideas may help to understand some of your results and may advance our understanding of  the importance evolutionary processes in determining species interaction patterns in communities.
	Another main point that you should revise across your manuscript is that you confound phylogenetic patterns with taxonomic patterns, for instance when thinking about congeneric species as closely related species (which is not necessarily true in several cases).

	\smallskip

	In what follows we share with authors our specific comments expecting that they will help to re-think the manuscript and get a stronger contribution.

	\end{refquote}

	The referee seems to view our basic question and analyses positively, but is rather critical of our  writing both in terms of logical clarity and style. We thank the referee for taking the time to provide such extensive feedback and have done our best to incorporate as many of their suggestions as possible. While we now mention the potential for coevolution to affect network structure, we have opted not to make this a major theme of the manuscript. What is and is not coevolution seems to be hotly debated. In the absence of any historical, paleontological, or genetic data to settle the question in our dataset, we feel it is not appropriate to make coevolutionary claims about our results. We address each comment in detail below (preceded by \textbf{R:}). It appears that the Referee wrote their specific comments before reading the manuscript in its entirety. Thus, some of the Referee's objections are in fact addressed at later points. In these cases, we have juxtaposed the Referee's comments to demonstrate this.

	1. General criticism of the language of the text

		\begin{refquote}

		Finally, the text needs English revision by the authors as we feel that some ideas are not clearly stated because of the way they are presented to readers.

		\end{refquote}

		\textbf{R:} We would like to point out that both the lead and corresponding authors of this manuscript are native English speakers and that Referees 1 and 3 praised the quality of our writing. Of course technical correctness does not necessarily imply clarity of expression, and so we have revised the manuscript according to the Referee's suggestions. [[Given the Referee's own moderate to poor command of English, this is a hell of a thing to say!!]]

	2. Title lacks clarity

		\begin{refquote}
		Specific comments
		Title
		Your title still lacks clarity and does not reflect the main message you state at the beginning of your discussion (in the first sentence of it you state that you found broad support for the hypothesis that more closely related plants tend to have more niche overlap). We feel that this reflects lack of logical consistency across your manuscript, so re-thinking it should help to define your title.
		\end{refquote}

	3. Summary too methodologically-oriented in general

		\begin{refquote}
			Summary
			General comments
			Your summary is too methodologically-oriented. In fact, when we were invited to be reviewers of your manuscript and received your abstract we thought that your paper represented a methodological contribution and it is not. After reading the comments that former reviewers sent you, your abstract seems to correspond to an older version of your manuscript. The thing is that by presenting an abstract that is methodologically-oriented when in fact you are not innovating in this sense, and having an introduction and a discussion that lack such methodological issue and are clearly more biologically-oriented can be read as that your work lacks focus.
		\end{refquote}

		\textbf{R:}

	4. Persistent mis-understanding of purpose and scope of within-family analyses

		\begin{refquote}
		Your abstract also evidences your confusion with phylogenetic issues and taxonomic ones. For instance, your hypothesis is that more closely related plants will share more pollinators and herbivores than less closely related. Then, why searching for different relationships within families? This decision is completely arbitrary is one of the weakest point of the manuscript in general.
		\end{refquote}

		\textbf{R:} Analyses of relationships between phylogenetic relatedness and niche overlap within families was specifically requested in a previous round of review [[check this]]. It also represents a major difference between our manuscript and previous work. We therefore disagree with the Referee that including this analysis is either "completely arbitrary" or "one of the weakest point(sic) of the manuscript in general". If more closely-related plants are indeed more likely to share interaction partners, then why shouldn't this be true within a family as well as between families? This additional level of detail demonstrates that not all plant families show the same relationships. We feel that this is useful. Based on point 6 (below), it appears that the Referee's objection is actually to the choice of family as our unit for detailed analysis rather than the analysis itself. We address this below.

		\begin{refquote}
		3rd paragraph:  which is your biological argument to consider families as the taxonomic level to search for differences across communities?
		\end{refquote}

		\textbf{R:} This comment suggests that the Referee was confused about our analyses. We did not search for differences between communities in our family-level analyses. Our between-community comparisons included comparisons between plant pairs pairs at all taxonomic levels. Our within-family analyses (based on pairs of species from the same community) were intended to detect differences between plant families \emph{across communities}. [[Clearly need to make this clearer in the summary, but R2 is also evidently a bit of an idiot. And probably Francophone. Maybe Indian?]]

		\begin{refquote}
		Aims
		Why considering the phylogenetic signal at the plant families level? There is no introduction for this aim. Why focusing at such taxonomic level?
		\end{refquote}

		\begin{refquote}
			Line 318. Within-family conservation of niche overlap. Your result is almost expected so we think is important to justify biologically why you decided to look at the family level.
		\end{refquote}

	5. Second paragraph of summary is too technical

		\begin{refquote}
		Your 2nd paragraph is too technical: which is the biological meaning of it? Why are you going to compare pollination and herbivory networks? Why your datasets are so unbalanced? Why are you considering a wide range of pollination networks and a narrow one for herbivory networks? Why you consider shared and unshared partners? Your first point in the abstract doesn't introduce a methodological problem to be solve. (...) "and whether this relationship varies with the composition of the plant community"? What does it mean?
		\end{refquote}

		\textbf{R:}

	6. Very confusing comment complaining about paragraph 4

		\begin{refquote}
		4st paragraph "Considering factors affecting the dominant plant families within
		a community may be the key to understanding the distribution of interactions." So, relationships are more functional? Why focusing on plant families? we are not sure the logic of your thoughts can be followed (can the reader reach this conclusion? is it ok? we mean, if there are other eco-evolutionary processes determining species interactions why focusing in the dominant plant families would be informative? I feel the way this last paragraph is written isn't clear enough and is your main paragraph.
		\end{refquote}

		\textbf{R:} This comment is difficult to follow. Part of the issue seems to be the Referee's mistaken belief that all of our analyses are at the level of plant families (addressed above). The remaining objection seems to be our suggestion that focusing on the plant groups which contribute the bulk of species in a community is more informative than focusing on species which represent unusual groups for the community. These dominant, species-rich groups contribute the bulk of unique interactions to a community, even if not necessarily the bulk of individuals. For this reason alone, it is worth understanding relationships between relatedness and niche overlaps in these groups. More pragmatically, species which are the lone representatives of a clade (we use families) do not provide much evidence for \emph{any} process.

	7. Complaint about keywords absent from the abstract

		\begin{refquote}
		Keywords
		Syndrome:  Why you do not mention such theory in your abstract?
		\end{refquote}

		\textbf{R:} The abstract/summary is under strict word limits, and we did not feel that inserting each keyword without a clear purpose could justify the elimination of other material. Given the Referee's confusion regarding our analyses, we are more convinced than ever that our decision to omit some keywords (which do appear in the introduction) in favour of spending more words explaining our methodology was correct.

	8. Mistake about the focus of the manuscript

		\begin{refquote}
		Introduction
		General. You focus on the compromise between pollination and herbivory interactions but then you do not use this approach in your analyses.
		\end{refquote}

		\textbf{R:} Potential tradeoffs between encouraging interactions with pollinators and discouraging herbivores are just one of the possible reasons why networks may not display the expected relationship between relatedness and niche overlap. Note that we also propose several others [[pull quotes]]. [[Apparently I need to adjust so it's clear that this isn't our main focus]]

	9. Suggestion to reframe the first paragraph in terms of functionality

		\begin{refquote}
		1st paragraph: We suggest this paragraph needs to be more functionally-oriented than phylogenetically-oriented. Syndromes may respond to the convergence of differently related organisms to a similar phenotype to attract the same pollinators. That is why plant syndromes can be more related with higher levels of taxonomic classification (orders) or to functionally defined groups like short and long-tongued bees, and not necessarily with sharing exactly the same pollinator species. Are you aware of articles showing that plant syndromes are phylogenetically conserved? We can think about many genera in which closely related plants show the same syndrome but bee or hummingbird syndromes are found within the family, so why should we expect that phylogeny has a strong signal? Or that more closely related plants will show more similar pollinators?
		\end{refquote}

		\textbf{R:}

	10. Referee hates paragraph 2 as well.

		\begin{refquote}
		2nd paragraph: your reasoning is not clear for us. Syndromes imply the convergence of phenotypic traits into one common set of traits because of their functionality in increasing fitness (because of the selection pressures imposed by functional groups of pollinators that can or cannot be closely related). Even if traits are heritable, if many unrelated groups converge into one functional group of interaction partners, why you may expect more similarity among closely related species? On the other hand, can we expect modular structures based on your reasoning? Then, how you explain the high incidence of nested structures in both mutualistic and antagonistic networks? In fact, what has been proposed for coevolution in mutualistic networks is the convergence of species traits to those of the species forming the core (see Guimaraes et al 2017, Nuismer et al. 2018). In antagonistic networks your line of reasoning may apply, but this will clearly depend on the intimacy of your network as most herbivory networks tend to show nested structures too. Your reasoning is based on pairwise coevolution and does not incorporate ideas of evolution and coevolution in networks, which may completely alter your predictions about niche overlap.
		\end{refquote}

		\begin{refquote}
		Lines 65-65. You wrote: Unrelated plants might also converge upon similar phenotypes, attracting a particularly efficient or abundant pollinator (Ollerton, 1996; Wilson et al., 2007; Ollerton et al., 2009; Ibanez et al., 2016). This is exactly our point: pollination syndromes may reflect trait convergence among unrelated species.
		\end{refquote}

		\textbf{R:} [[Fuck, this dude really seems to hate syndromes?]]

	11. Request to include interaction intimacy

		\begin{refquote}
		Lines 35-39. Maybe you should use the idea of interaction intimacy, since it clearly will determine the level of selective pressure landscape perceived by a given species?
		\end{refquote}

		\textbf{R:} We have no information on interaction strengths or intimacies, and so cannot test whether this is affecting our results. [[We could introduce the idea?]]

	12. Criticising methodological choices required by previous reviewers

		\begin{refquote}
		Methods
		Dataset
		Several networks can be reviewed in the literature or are available in different websites. Why authors decide not to consider several plant-herbivore networks but have no filter to separate plant-pollinator networks? The reason of why focusing in plant-pollinator and plant-herbivory networks is not clear for us as well why authors choose to select just one kind of herbivory interaction and as a consequence have a highly unbalanced design. Such decision seems to be crucial as it may modulate the results and conclusions they achieve. By eliminating the herbivory interactions that are more phylogenetically constrained their result that pollination interactions may be more conserved than herbivory interactions seems to be a by-product of such decision.
		\end{refquote}

		\textbf{R:} We restricted our selection of herbivory networks in response to a previous round of review. Without more details why (or if) the Referee believes that the herbivory networks we removed should be included, we have opted not to reject that earlier feedback. We would have appreciated specific tips for additional herbivory networks, but since the Referee does not provide any specifics there would appear to be little we can do to addrss this comment.

	13. Request to change "insects consuming leaves" to "chewing insects"

		\begin{refquote}
			Lines 93 to 96. We think that sap-sucking, leaf mining, and galling insects are also insect consuming leaves. Maybe you could change "insect consuming leaves" by "chewing insects"
		\end{refquote}

		\textbf{R:} [[Sure, why not.]]

	14. Mis-understanding of methods

		\begin{refquote}
			Measuring niche overlap
			Why you used absolute numbers to measure shared and unshared pollinators and not the Jaccard index? Or, instead, why you did not use a binomial regression considering the absolute number of the whole set of pollinators that can be shared ? You should use generalized linear models with a binomial distribution considering the total number of pollinators and shared pollinators to give more weight to those species sharing more pollinators in a larger sample (generalists s for instance). It is not clear for us if your analysis considers the full number of species over which you obtain the percentage of shared species.
		\end{refquote}

		\textbf{R:} If fact we did use a Jaccard index \emph{and} generalised linear models. Please read the methods carefully. These details can be found [[quote]]

	15. Confusing request to change methods

		\begin{refquote}
			176-178. Why you do not consider using plant species as another fixed factor to break the lack of independence? This is because generalist species may have more weight in your analyses than other species. It would be interesting to see how your results differ from an analysis considering such approach.
		\end{refquote}

		\textbf{R:} It sounds as though the Referee would like us to include plant species as a predictor in our regressions. Due to the fact that species generally appear in few networks (many in only a single network), this would result in near singularity. We would therefore be completely unable to observe any other patterns. If the Referee is referring to a potential effect of network size, we did in fact test this (lines XX-XX) [[[pull a quote]]]. If the Referee did not mean either of these possibilities, we apologise but are unable to understand this comment.

	16. Un-justified request to include connectance

		\begin{refquote}
			198-209. Why did you decide to control just for network size and do not consider network connectance? You provide methodological information to explain your decision but there is no biological argument explaining why network size may influence the relationship between phylogenetic relatedness and niche overlap.
		\end{refquote}

		\textbf{R:} We did not include connectance because we can offer no justification (biological or methodological) why the overall connectance of the network should affect the strength of the relationship between relatedness and niche overlap. It is possible that there might be an effect of connectance on the intercept of this relationship (as we would expect higher overlap in general when connectance is high), but we see no particular reason why connectance should change how closely-related species differ from distantly-related species in the same network. Since the Referee also does not provide any reasoning behind this request, we have opted to leave our analyses as-is.

		[[Maybe I can add a bit of a biological argument that network size can affect overlap? I'm not sure what methodological but not biological means here.]]

	17. Poor understanding of methods

		\begin{refquote}
			Line 210 Linking network level trends and community composition

			(related with this part of the methods but referring to the Introduction section) Which are the hypothesis for this analysis? How do you think that family composition (and no species composition) could affect the relationship between phylogenetic  distances and niche overlap?
			In the analysis it is not clear for us which are the dependent and independent variables. Is the independent variable a matrix with coefficients of similarity between networks?  Do you want to explore if more similar networks have a more similar relationship (slope) between phylogenetic distance and niche overlap? Or you want to investigate if the slopes are more o less strong depending on the local composition of communities (for each network separately) ? If this is the case you could compare slopes with a local diversity index (e.g. Shannon) instead of a beta diversity index.
		\end{refquote}

		\textbf{R:}

	18. Condescending critique of manuscript structure

		\begin{refquote}
			Results
			General: Please, do not include discussion in your results, it may confound readers.
		\end{refquote}

		\textbf{R:} The Referee appears to be confounded by our manuscript in general and is extremely dismissive of our understanding of how to write a manuscript...

	19. Possible complaint about mixing numbers and percentages?

		\begin{refquote}
			Line 262. Your first sentence of results do not correspond with what follows. We will suggest you use most networks, or most herbivory networks and half pollination networks, or using the percentages you present in the discussion section.
		\end{refquote}

		\textbf{R:} This comment is in such poor English as to be nearly unintelligible. It is not clear whether the Referee is suggesting that we repeat our analyses using half of the pollination networks (without any clear reason as to why) or complaining that we have mixed qualitative descriptors, numbers, and percentages. We assume the latter as we are able to address this complaint. [[check what's going on]]

	20. Confusion about methodology

		\begin{refquote}
			Line 310. How was community composition measured? Is difficult to evaluate the quality of this result because you haven't described this methodology.
		\end{refquote}

		\textbf{R:} Community composition is the set of plant species that make up a community. It was defined by the researchers constructing each network according to the specific methodology employed in each case. [[Add a parenthetical definition]]

	21. Confusion about permutation methodology

		\begin{refquote}
			Minor comments on Results
			297-298 You permuted interactions or phylogenetic distances?
		\end{refquote}

		\textbf{R:} [[double-check and provide a line ref]]

	22. Request to change direction of relationship?
		\begin{refquote}
			Fig 1. "...the probability of a pair of plants sharing an interaction partner increased with increasing phylogenetic distance..." please, write decreased instead of increased.
		\end{refquote}

		\textbf{R:} Sweet Satan, I hope this isn't a typo?

	23. Difference between minimum and maximum slopes not visible

		\begin{refquote}
			Fig 2. It is no clear for us. Minimum and maximum slopes obtained from 999 permutations are the same value?
		\end{refquote}

		\textbf{R:} [[Check that caption states that min and max are very close together since permutation completely destroyed pattern.]]

	24. Missing word in line 328

		\begin{refquote}
			Line  328: "...increasing phylogenetic distance in 12...", what is 12? the number of families?
		\end{refquote}

		\textbf{R:}

	25. Sundry complaints about table numbering and figure referencing

		\begin{refquote}
			Table number seem to be erroneous as you first mention table 2 and then table 1.

			\smallskip

			Figure 3 is only referenced in the text when talking about herbivory networks but not for pollination networks.
		\end{refquote}

		\textbf{R:}

	26. Blanket demand for more evolution content

		\begin{refquote}
			Discussion
			General
			We suggest you include ideas about evolution and coevolution in networks in your discussion. It is important to recognize that network structure is in part a consequence of the evolutionary process and that we cannot think in the pairwise-coevolutionary framework as the only one modulating trait evolution in species rich assemblages.
			You state that the fact that the proportion of specialist species may explain differences between plant-pollination and plant-herbivore network patterns and you discuss the mathematical consequences of such difference but you should discuss the ecological and evolutionary causes and consequences of having higher specialization in pollination networks. This is also related with your methodological decision of excluding more specialized herbivores, isn't it?
		\end{refquote}

		\textbf{R:} THIS IS NOT AN EVOLUTION PAPER! WE HAVE NO DATA TO INFER ANYTHING ABOUT THE EVOLUTION OF THESE SYSTEMS!

	27. Debate over the meaning of "broad"

		\begin{refquote}
			338-339. You state We found broad support for the hypothesis that more closely-related pairs of plants have a higher degree of niche overlap. This is a very strong sentence that is not supported by your results. You found evidence in 55% of plant-pollination networks (almost half of your dataset). In fact, it is interesting to note that even the slope is more pronounced in mutualistic networks you found higher support in herbivory networks, as a higher percentage of networks showed a tendency.
		\end{refquote}

		\textbf{R:}

	28. Another complaint about sub-setting the herbivory networks, possibly addressable in text

		\begin{refquote}
			351-352 The herbivory networks did not contain as many obligate specialists, but we note that many herbivorous insects are oligotrophs which consume only a few closely-related hosts (Novotny & Basset, 2005; Yguel et al., 2011). This sentence is confuse because you have a subsample of herbivory networks and then this seems to be a by-product of your study design associated with your decision of removing networks that may show strong phylogenetic signal.
		\end{refquote}

		\textbf{R:}

	29. Claims that congeneric species are not closely related

		\begin{refquote}
			357-359 This suggests that conservation of interaction partners among closely related plants (e.g., congeners or members of the same subfamilies) is more important than phylogenetic signal from deeper within the phylogenetic tree. Congeneric species can be not closely related, please revise sentences like this one across the manuscript because you are confounding phylogeny with taxonomy.
		\end{refquote}

		\textbf{R:} Does the Referee really mean to suggest that plants in the same genus are less closely-related than plants in different families? Without some sources to substantiate this, we find this claim very far-fetched!

	30. Another demand to discuss intimacy

		\begin{refquote}
			361-365. How interaction intimacy may explain your results? Please, discuss your results in light of the interplay between interaction type (pollination, herbivory) and intimacy (see Hembry et al. 2018).
		\end{refquote}

		\textbf{R:}

\clearpage

{\Large \bf Reply to Referee 3}

	\begin{refquote}
		The study is well designed and the manuscript well written, and the authors clearly demonstrate their comprehensive grasp of the subject and the applied statistical analyses.
		My only more general comment is whether authors have considered potential applications of such phylogenetic approaches for ecological restoration? If closely-related species provide similar functions in ecological networks, they could be used interchangeably to restore ecological interactions/functions. This is an exciting potential application of phylogenetic data in biodiversity conservation and restoration, and could be touched upon/discussed in this manuscript.. 
		Otherwise, I have only minor comments.
	\end{refquote}

	\textbf{R:} We thank the Referee for their compliments to our approach and to our writing, as well as their more detailed comments (addressed one-by one below; replies preceded by \textbf{R:}). We had not considered this potential application for ecological restoration but are very pleased to have it pointed out. It is often difficult to see how theoretical work may relate to conservation practice, so we are glad to take the opportunity to make a link here. [[Add a bit of this, I think we have room]]

	1. Title is confusing

		\begin{refquote}
			Title is confusing – difficult to pick out key message. And given that your analyses broadly give support for effects of phylogenetic distance on niche overlap, why not focus on this message, rather than variability at among individual networks/plant families
		\end{refquote}

		\textbf{R:}

	2. Request to state that networks are qualitative rather than quantitative

	3. L298 – Please be careful with use of “lesser/greater” “more negative or positive than expected from permuted networks”

	4. Confusion about result in line 322

		\begin{refquote}
			L322 – how was this result obtained if insect phylogenies were not caclculated? Do you mean “more closely-related plants in pollinator networks”?
		\end{refquote}

		\textbf{R:}

\clearpage

{\Large \bf Reply to Referee 4}

	\begin{refquote}
		Understanding what drives the structure of networks of interactions is key to predict the structure of plant-insect communities (e.g., for conservation or restoration purposes, or to support benefit organisms in agriculture).
		The present study focuses on the contribution of the evolutionary history to the interaction structure, and makes a significant contribution to the understanding of the variability of the phylogenetic signal in plant-insect networks. Here, the strength of the phylogenetic signal is actually quantified while it usually relies on correlation scores, and the effect of plant composition and the identity of plant families are examined to assess whether they could explain the variability of trends described in the literature.
		The dense writing turns out to be a double-edge sword: a lot of information on drivers of phylogenetic signals is compiled in here, but the text is sometime hard to follow. Hence, my following comments mostly pertains to the form, and I trust the authors should be able to address them fairly easily.
	\end{refquote}

	\textbf{R:} We thank the Referee for their compliments to our analysis and for taking the time to review our manuscript. We appreciate that our writing can be dense at times and appreciate the Referee pointing out places where we may clarify our prose. Below, we respond to each comment in detail (preceded by \textbf{R:}). We are confident that revising the manuscript in response to the Referee's comments has improved the manuscript.

This is the first time I review the present manuscript, so I apologise in advance if my comments were already addressed in previous reviewing rounds (despite checking with the most recent reply to reviewers).

Statistical analyses

* Modelling the relationship between niche overlap and phylogenetic distance
I did not managed to fully grasp the statistical analysis right away (I reckon I'm not a statistical master, but this may be the case of other readers), and I think it was mostly due to the way the methods are described. The writing is nice, but some tiny details are missing while they could help the reader to understand more quickly how the authors distinguish the use of the {M_ij, U_ij}-tuple from that of J_ij.
Based on l. 143-167, I understand that the number of shared interactions M_ij is modelled with a binomial distribution, with the number of trials being M_ij+U_ij, and the probability of success being w_ij (M_ij ~ B(M_ij + U_ij, w_ij)). The {M_ij, U_ij}-tuple would appear in R as follows:
model ← glm(cbind(M_ij, M_ij+U_ij) ~ d_ij + ..., family = “binomial”)
But, can we actually say that there are two dependent variables? To me, it is the number of shared interactions that is modelled as a binomial process, not both the number of shared and unshared interactions.

I suppose that the analysis described in paragraph starting from l. 168 corresponds to actually modelling the Jaccard index (J_ij ~ ...). If this is right, I think this should be specified in the second paragraph (no direct mention of the Jaccard index is currently made, except the proportion l. 170 between brackets although it is not exactly written as in eq. (1)), while in the first paragraph, an equation should specify that M_ij ~ B(M_ij + U_ij, w_ij)).

Another point pertains to the definition of “trials” in the binomial-distributed process. If I get it right, these correspond to the union of species i and j interactions (of size P_i + P_j -2M_ij = M_ij + U_ij). However, these are not independent for reasons highlighted in the introduction (e.g., competition, facilitation between plants and/or insects). This may question the robustness of the analysis, but testing the effect of the plant community composition (negative) allows to verify this. This should be specified, I think.

* Evaluating type I and type II errors: Permutations of permutations
Paragraph p. 10, l. 187-197 is a bit confusing because of phrasings such as “permutations/permuting of the permuted networks”. I don't have a better way to name this second round of permutations, but the overall is difficult to follow and could be shortened while still conveying the same message.
Actually, I find the comment in Supplementary information 3 clearer, although no reference to Supplementary information 3 is made.
Besides, as slopes of regressions in permuted networks are tightly grouped around zero (Fig. 2, thin lines indicating extrema of slopes distribution overlapping each other), so type II errors do not seem to be a big problem here.

* Testing the effect of network size on the existence of a phylogenetic signal
Here, it is specifically the number of plant pairs that is studied. I wonder whether the phylogenetic diversity of plants would not be more adapted here. Is it overlooked because similar among networks?
I think knowing more about this effect would further illuminate why the strength of the phylogenetic signal varies between networks and would be complementary to the analysis testing the effect of plant community composition.

* Testing within-family existence of a phylogenetic signal
Examining the strength of phylogenetic signal within plant families is an interesting idea. However, this leads to multiple testing which is prone to type I errors and I could not find mention of correction for this multiple testing in the text. There are actually high chances that there is at least one significant test in each table (1 – (1 – alpha)^N = 0.36 and 0.91 respectively, alpha = 0.05). Yet, the authors can indicate that there are low chances to have that many significant phylogenetic signals (using the probability mass function of the Binomial distribution, see Moran 2003 in Oikos).

On the effect of specialist pollinators

I think that Reviewer #3 made an interesting remark on specialist pollinators, and I agree with the authors on the impossibility to assess sampling completeness on the network of this database. However, I think this should be mentioned in the text, at least to invite future works to provide their sampling effort when publishing new empirical data (hence, helping to improve future analyses).

On plant families involved in different types of interactions

p. 19-20, l. 432-448: This paragraph on systems for which both pollination and herbivory were sampled is a bit fuzzy. Talking about how diverse types of interactions can work together is a nice way to bring back the study to a broader context, though.
First, I think the sentence of simultaneous selection pressure of pollination and herbivory could be a bit clarified (l. 439-442, “Plants may not be able to respond (…).”). Strauss & Whitthall’s chapter in the book “Ecology and evolution of flowers” gives a good insight on how these selection pressures can act together or antagonistically in shaping plants phenotypes (and eventually interactions, although not specifically discussed in their chapter).
Second, the structure of interaction patterns could be discussed with more references than Sauve et al. (2016). Astegiano et al. (2017) make an interesting point on the asymmetry of interaction patterns in such systems (using Pearse and Altermatt (2011)’s data on Lepidotera diet, and citing the Norwood farm data set of Pocock et al. 2012, and the Donana network in Melian et al. 2009).
Finally, the existence dynamical drivers of the structure of pollination and herbivory is mentioned. Sauve et al. (2014, 2016) indeed suggest that the way pollination and herbivory are distributed on the plant community may matter for community stability, and they studied one case where this structure is indeed not random. Yet, they do not say that these communities should be more stable (compared to which ones since plants undergo both herbivory and pollination in nature?). Whether the interconnection structure arises because it provides greater stability (as discussed by Sauve et al. 2016), or as a by-product of the assembly process (Maynard et al. 2018, Ecol. Lett.) remains to be discussed for networks combining different types of networks.
Despite the length of this last comment, I don’t mean that the authors should develop proportionally this paragraph, but rather sharpen it.

Minor comments

In the abstract, item 2 « shared and unshared interactions »: if it does not breach the word limit, I think a few words specifying why this is important would better showcase the study, and help to understand how it contributes to the study novelty.

p.3, l. 1-2, citation of Sauve et al. 2016 (Ecology) to say that interactions between plants and animals are critical to plants’ life cycle. I’m not sure this is the best pick as Sauve et al. rather look at how pollination and herbivory interactions are distributed in the plant community and how it may affect community stability. The following references are adequate though.

p. 3, l. 9-10 « A plant’s traits are also (...) », I think there is a typo here. Shouldn’t « a » be removed ?

p. 3, l. 22-25 : There is a lot of citations here. I agree they all point to « mixed results » but this pertains to different aspects of phylogenetic signal. Some highlight differences between mutualistic and antagonistic systems, other rather focus on difference of phylogenetic signal between trophic levels, or even focus on subset of interaction networks. I think, it would be more relevant to the reader to cite these different works to explain how mixed results are (as done in the text following this long citation list).

p. 5, l. 69-71 « In either case, dissimilarity (…). » This sentence helped me to understand why it is important to look at unshared interactions. To be better showcased ?

p. 5, l. 78 « a pairwise perspective » : This contributes to the manuscript novelty. Maybe this should be further specified?

p. 6, l. 89-90 « These networks span a range of biomes (…). » In supporting information, the countries are not indicated in the list. Alternatively, and to emphasize on the title following Reviewer #2 suggestion in the previous round of review, a figure showing the spatial distributions of the 59 + 11 network on a world map would be welcome here.

p. 7, l. 125-141 : I think the beginning of this section should be more straightforward and contrast better the information provided by M_ij and U_ij (starting with them) with that of the Jaccard index J_ij. In addition, J_ij is never mentioned again as such (but is an estimate of w_ij).

p. 14, l. 297-298 “Comparing the results in the observed networks with those obtained after permuting phylogenetic distances across pairs of plants (...)”: In the methods, interactions are shuffled, not phylogenetic distances. Doing one of the other seems equivalent for this test, but this rephrasing is a bit confusing.

p. 15, l. 322-324 “ More closely-related pollinators did, however, tend to share fewer interaction partners (…).”: This is the first time that conservatism of interactions is checked from the pollinators perspective in the manuscript. Is it a typo or did I miss something in the manuscript?

Legend of Fig. 3 “(…) Melastomatoaceae and Poaceae in pollination networks are not significantly different from zero.” but Table 2 shows the opposite for Poaceae.

In the figures, \beta_distance is alternatively named “slope of regression line” (Fig. 2) and “change in log odds” (Fig. 3).

References

Altermatt, F. and Pearse, I.S., 2011. Similarity and specialization of the larval versus adult diet of European butterflies and moths. The American Naturalist, 178(3), pp.372-382.

Astegiano, J., Altermatt, F. and Massol, F., 2017. Disentangling the co-structure of multilayer interaction networks: degree distribution and module composition in two-layer bipartite networks. Scientific reports, 7(1), p.15465.

Maynard, D.S., Serván, C.A. and Allesina, S., 2018. Network spandrels reflect ecological assembly. Ecology letters, 21(3), pp.324-334.

Melián, C.J., Bascompte, J., Jordano, P. and Krivan, V., 2009. Diversity in a complex ecological network with two interaction types. Oikos, 118(1), pp.122-130.

Moran, M.D., 2003. Arguments for rejecting the sequential Bonferroni in ecological studies. Oikos, 100(2), pp.403-405.

Strauss, S.Y. and Whittall, J.B., 2006. Non-pollinator agents of selection on floral traits. Ecology and evolution of flowers, pp.120-138.

  \newpage

\bibliographystyle{prsb} 
\bibliography{abbreviated}

\end{document}

### 2019-11-22 manuscript/reply_to_referees_2.tex
partial edits

@@
 
-{\Large \bf Reply to Referee 1}
+{\Large \bf Reply to Referee 1} [[done]]
 
@@
 
-\textbf{R:} We thank the referee for taking the time to read our manuscript and for the compliment to our proof-reading.
+	\textbf{R:} We thank the referee for taking the time to read our manuscript and for the compliments to our revision and proof-reading.
 
@@
 
-	The referee seems to view our basic question and analyses positively, but is rather critical of our  writing both in terms of logical clarity and style.
-We thank the referee for taking the time to provide such extensive feedback and have done our best to incorporate as many of their suggestions as possible.
-While we now mention the potential for coevolution to affect network structure, we have opted not to make this a major theme of the manuscript.
-What is and is not coevolution seems to be hotly debated.
-In the absence of any historical, paleontological, or genetic data to settle the question in our dataset, we feel it is not appropriate to make coevolutionary claims about our results.
+	The Referee(s?) seems to view our basic question and analyses positively, but is rather critical of our  writing both in terms of logical clarity and style.
+It is also clear that the Referee is more interested in coevolution than in any purely ecological network patterns.
+We thank the referee for taking the time to provide such extensive feedback and have done our best to incorporate as many of their suggestions as possible, although our ecological focus means that we have not made coevolution a major theme.
+Nevertheless, we now mention the potential for coevolution to affect network structure in the discussion.
 We address each comment in detail below (preceded by \textbf{R:}).
@@
 Of course technical correctness does not necessarily imply clarity of expression, and so we have revised the manuscript according to the Referee's suggestions.
-[[Given the Referee's own moderate to poor command of English, this is a hell of a thing to say!!]]
+[[Given the Referee's own moderate to poor command of English, this is a hell of a thing to say!!]] If our loquacious verbiage has obfuscated any modicum of information, we apologise.
 
@@
 
-	3. Summary too methodologically-oriented in general
+	3. Summary too methodologically-oriented in general [[done]]
 
@@
 		\end{refquote}
-
-		\textbf{R:}
-
-	4. Persistent mis-understanding of purpose and scope of within-family analyses
-
-		\begin{refquote}
-		Your abstract also evidences your confusion with phylogenetic issues and taxonomic ones.
-For instance, your hypothesis is that more closely related plants will share more pollinators and herbivores than less closely related.
-Then, why searching for different relationships within families?
-This decision is completely arbitrary is one of the weakest point of the manuscript in general.
-		\end{refquote}
-
-		\textbf{R:} Analyses of relationships between phylogenetic relatedness and niche overlap within families was specifically requested in a previous round of review [[check this]].
-It also represents a major difference between our manuscript and previous work.
-We therefore disagree with the Referee that including this analysis is either "completely arbitrary" or "one of the weakest point(sic) of the manuscript in general".
-If more closely-related plants are indeed more likely to share interaction partners, then why shouldn't this be true within a family as well as between families?
-This additional level of detail demonstrates that not all plant families show the same relationships.
-We feel that this is useful.
-Based on point 6 (below), it appears that the Referee's objection is actually to the choice of family as our unit for detailed analysis rather than the analysis itself.
-We address this below.
-
-		\begin{refquote}
-		3rd paragraph:  which is your biological argument to consider families as the taxonomic level to search for differences across communities?
-		\end{refquote}
-
-		\textbf{R:} This comment suggests that the Referee was confused about our analyses.
-We did not search for differences between communities in our family-level analyses.
-Our between-community comparisons included comparisons between plant pairs pairs at all taxonomic levels.
-Our within-family analyses (based on pairs of species from the same community) were intended to detect differences between plant families \emph{across communities}.
-[[Clearly need to make this clearer in the summary, but R2 is also evidently a bit of an idiot.
-And probably Francophone.
-Maybe Indian?]]
-
-		\begin{refquote}
-		Aims
-		Why considering the phylogenetic signal at the plant families level? There is no introduction for this aim. Why focusing at such taxonomic level?
-		\end{refquote}
-
-		\begin{refquote}
-			Line 318. Within-family conservation of niche overlap. Your result is almost expected so we think is important to justify biologically why you decided to look at the family level.
-		\end{refquote}
-
-	5. Second paragraph of summary is too technical
 
@@
 
-		\textbf{R:}
+		\textbf{R:} We regret that the Referee finds our summary too methodologically-orientated, but note that Referee 4 has requested that we include further methodological details in the summary.
+Moreover, in a later comment this Referee also requests more methodological details.
+To balance these conflicting comments, we no longer emphasise the methodological novelty of our study but have added the greater detail requested.
+As the other three Referees for this revision did not find the summary overly methodological in its original form, we are confident that the revised summary does not indicate that we lack focus.
+We also note that the extremely tight word limit for the summary does not allow us to explain why we have unbalanced numbers of pollination and herbivory networks.
+This information is contained in the methods.
 
-	6. Very confusing comment complaining about paragraph 4
+	4. Persistent mis-understanding of purpose and scope of within-family analyses [[done]]
+
+		\begin{refquote}
+		Your abstract also evidences your confusion with phylogenetic issues and taxonomic ones.
+For instance, your hypothesis is that more closely related plants will share more pollinators and herbivores than less closely related.
+Then, why searching for different relationships within families?
+This decision is completely arbitrary is one of the weakest point of the manuscript in general.
+		\end{refquote}
+
+		\textbf{R:} This comment indicates that the Referee has fundamentally misunderstood our manuscript based on the summary.
+Point 2 of the summary lists three separate analyses: testing for relationships between phylogenetic distance and partner overlap in \emph{all pairs of plants in a network, regardless of family}, testing whether the slopes of these whole-network relationships are related to the composition of the plant community in each network, and, as a supplement to these analyses, testing whether the slopes of these relationships differ if we consider only pairs of plants within the same family.
+We now number these three different analyses to avoid any further confusion.
+
+		As we are \emph{not} searching for differences between communities at the family level, but rather at all levels within the angiosperms, a number of the Referee's comments do not apply.
+For example, the comments below:
+
+		\begin{refquote}
+		3rd paragraph:  which is your biological argument to consider families as the taxonomic level to search for differences across communities?
+		\end{refquote}
+
+		\begin{refquote}
+		Aims
+		Why considering the phylogenetic signal at the plant families level? There is no introduction for this aim. Why focusing at such taxonomic level?
+		\end{refquote}
+
+		\begin{refquote}
+			Line 318. Within-family conservation of niche overlap. Your result is almost expected so we think is important to justify biologically why you decided to look at the family level.
+		\end{refquote}
+
+	5. Very confusing comment complaining about paragraph 4 [[done]]
 
@@
 
-		\textbf{R:} This comment is difficult to follow.
-Part of the issue seems to be the Referee's mistaken belief that all of our analyses are at the level of plant families (addressed above).
-The remaining objection seems to be our suggestion that focusing on the plant groups which contribute the bulk of species in a community is more informative than focusing on species which represent unusual groups for the community.
-These dominant, species-rich groups contribute the bulk of unique interactions to a community, even if not necessarily the bulk of individuals.
-For this reason alone, it is worth understanding relationships between relatedness and niche overlaps in these groups.
-More pragmatically, species which are the lone representatives of a clade (we use families) do not provide much evidence for \emph{any} process.
+		\textbf{R:} The Referee appears to have some deep-seated objection to any reference to plant families, but has not made the reasons for this objection at all clear.
+As noted above, we do in fact consider relationships between phylogenetic distance and interaction partner overlap at \emph{all} taxonomic levels, not just within families.
+Apart from this, we are confused by the remainder of the Referee's complaint.
+By 'dominant', we mean 'most species-rich in the focal community' rather than any kind of functional interpretation.
+Note that we do not address functions in the rest of the manuscript, so it is not clear why the Referee makes this leap.
+In order to avoid future confusion, we now replace 'dominant families' with 'species-rich groups'.
+We hope that this makes it clear that we are advocating researcher take a finer-scale perspective on phylogenetic signal in ecological networks.
 
-	7. Complaint about keywords absent from the abstract
+		\begin{quotation}
+		    \item The variety of relationships between phylogenetic distance and partner overlap in different plant families likely reflects a comparable variety of ecological and evolutionary processes.
+Considering factors affecting particular species-rich groups within a community may be the key to understanding the distribution of interactions.
+		\end{quotation}
+
+	6. Complaint about keywords absent from the abstract [[done]]
 
@@
 Given the Referee's confusion regarding our analyses, we are more convinced than ever that our decision to omit some keywords (which do appear in the introduction) in favour of spending more words explaining our methodology was correct.
+As we do not directly test pollination or defensive syndromes, we have removed these keywords from the list.
 
-	8. Mistake about the focus of the manuscript
+	7. Mistake about the focus of the introduction [[done]]
 
@@
 		\textbf{R:} Potential tradeoffs between encouraging interactions with pollinators and discouraging herbivores are just one of the possible reasons why networks may not display the expected relationship between relatedness and niche overlap.
-Note that we also propose several others [[pull quotes]].
-[[Apparently I need to adjust so it's clear that this isn't our main focus]]
+Note that we also propose several others in the same paragraph, including convergent evolution or selection to avoid pollen dilution.
+We therefore disagree with the Referee's perception that we focus on compromise between pollination and herbivory.
+It is beyond the scope of this manuscript to test all possible reasons why closely-related plants might not share interaction partners.
+This material is intended solely as background for readers who may not be familiar with arguments against the phylogenetic conservation of interaction partners.
 
-	9. Suggestion to reframe the first paragraph in terms of functionality
+	8. Deep disagreement with any link between syndromes and conservation of interaction partners [[done]]
 
@@
 		\end{refquote}
-
-		\textbf{R:}
-
-	10. Referee hates paragraph 2 as well.
 
@@
 
-		\textbf{R:} [[Fuck, this dude really seems to hate syndromes?]]
+		\textbf{R:} As the Referee notes, we do address the possibility of convergence later in our introduction.
+We do not make any claim as to whether the putative pollination syndromes actually reflect plants with common sets of pollinators (the evidence we are aware of is rather mixed).
+Since the Referee appears to object violently to this very common idea in the literature, and because syndromes do not form a major part of our analysis, we have removed it as a keyword and rephrased our introduction.
+It now no longer references pollination syndromes.
+Hopefully this will avoid other readers becoming fixated on the validity or otherwise of the syndrome idea and enable them to take our manuscript on its own merits.
 
-	11. Request to include interaction intimacy
+		Lines XX-XX:
+
+		\begin{quotation}
+
+			Plants with different defences 
+		  	(e.g., thorns vs. chemical defences) may deter different groups of 
+		  	herbivores~\citep{Ehrlich1964,Johnson2014}, and pollinators with similar traits are often expected to attract similar sets of pollinators~\citep{Waser1996,Fenster2004,Ollerton2009}.
+
+		\end{quotation}
+
+	9. Request to include interaction intimacy [[done]]
 
@@
 
-		\textbf{R:} We have no information on interaction strengths or intimacies, and so cannot test whether this is affecting our results. [[We could introduce the idea?]]
+		\textbf{R:} We have no information on interaction strengths or intimacies, and so cannot test whether this is affecting our results.
+However, we are happy to include the idea as yet another reason why plant communities may or may not show conservation of interactions.
+We have added a brief description of intimacy as follows:
 
-	12. Criticising methodological choices required by previous reviewers
+		Lines XX-XX:
+
+		\begin{quotation}
+
+			In mutualistic networks, animals often show a stronger phylogenetic signal in their partners than do plants~\citep{Rezende2007a,Chamberlain2014,Rohr2014,Vamosi2014,Lind2015,Fontaine2015} (but see~\citet{Rafferty2013} for a counterexample).
+In antagonistic networks, however, actively-foraging consumers tend to show less phylogenetic signal than their prey~\citep{Ives2006,Cagnolo2011,Naisbit2011,Fontaine2015}.
+In part, this may be related to different degrees of interaction intimacy (dependence of one predator on another), which appears to contribute to network structure in mutualistic, but not antagonistic, networks~\citep{Guimaraes2007,Ponisio2017}.
+
+		\end{quotation}
+
+	10. Criticisism of methodological changes required by previous reviewers [[done]]
 
@@
 		\textbf{R:} We restricted our selection of herbivory networks in response to a previous round of review.
-Without more details why (or if) the Referee believes that the herbivory networks we removed should be included, we have opted not to reject that earlier feedback.
-We would have appreciated specific tips for additional herbivory networks, but since the Referee does not provide any specifics there would appear to be little we can do to addrss this comment.
+Without more details why (or if) the Referee believes that the herbivory networks we removed should be included, we have opted to continue following that earlier feedback.
+We would have appreciated specific tips for additional herbivory networks, but since the Referee does not provide any specifics there would appear to be little we can do to address this comment.
 
-	13. Request to change "insects consuming leaves" to "chewing insects"
+	11. Request to change "insects consuming leaves" to "chewing insects" [[done]]
 
@@
 
-		\textbf{R:} [[Sure, why not.]]
+		\textbf{R:} The term "insects consuming leaves" was recommended by an earlier reviewer, but we agree that leaf mining also constitutes leaf consumption (this is not necessarily the case for sap-sucking and galling, which is less leaf-specific).
+We have changed these lines as suggested.
 
-	14. Mis-understanding of methods
+	12. Recommendation to continue using the same methodology [[done]]
 
@@
 
-		\textbf{R:} If fact we did use a Jaccard index \emph{and} generalised linear models. Please read the methods carefully. These details can be found [[quote]]
+		\textbf{R:} We did use a Jaccard index, as stated in the first and second sentences under the sub-heading \textbf{Calculating niche overlap between communities}.
+The Jaccard index is calculated using the number of shared and un-shared interaction partners for a pair of plants, as stated in equation 1.
+We also did use a generalised linear model with binomial error distribution, as stated in the \textbf{Statistical analysis} section.
+We chose this methodology for exactly the reasons the Referee suggests, to give more weight to generalists sharing many interaction partners.
+This is stated in lines XX-XX (quoted below).
+We are glad that the Referee agrees with our choice in methdology.
 
-	15. Confusing request to change methods
+		\begin{quotation}
+
+			We wished to give more 
+		    weight to species sharing a large number of interaction partners as well as 
+		    those sharing a large proportion (i.e., to emphasise pairs of generalists 
+		    sharing most of their interaction partners over specialists sharing a single 
+		    interaction partner).
+Note that species sharing a large \emph{number} of interaction partners may not share a large \emph{proportion} of interaction partners if the number of interaction partners that are not shared is also large.
+
+		\end{quotation}
+
+	13. Request to include plant species as a fixed effect [[done]]
 
@@
 		\textbf{R:} It sounds as though the Referee would like us to include plant species as a predictor in our regressions.
-Due to the fact that species generally appear in few networks (many in only a single network), this would result in near singularity.
-We would therefore be completely unable to observe any other patterns.
-If the Referee is referring to a potential effect of network size, we did in fact test this (lines XX-XX) [[[pull a quote]]].
+Due to the fact that species generally appear in few networks (many in only a single network), this would result in near singularity of our models.
+We would therefore be completely unable to observe any patterns as species identity would explain essentially all variation.
+If the Referee is referring to a potential effect of network size, we did in fact test this (see equation 4 and description).
 If the Referee did not mean either of these possibilities, we apologise but are unable to understand this comment.
 
-	16. Un-justified request to include connectance
+	16. Un-justified request to include connectance [[just address here]]
 
@@
 
-	17. Poor understanding of methods
+	17. Confusion about motivation for community composition analyses [[done]]
 
@@
 
-		\textbf{R:}
+		\textbf{R:} The Referee was correct with their first idea.
+We want to explore whether more similar networks have more similar slopes of partner overlap against phylogenetic distance.
+Once again, we are pleased that the Referee agrees with our analysis.
+We did this because different plant families likely experienced different levels of convergence, coevolution, have different levels of intimacy with their partners, etc.
+We now explicitly state this in the introduction.
 
-	18. Condescending critique of manuscript structure
+		Lines XX-XX:
+
+		\begin{quotation}
+
+		  Here we investigate how overlap in interaction partners between 
+		  pairs of plants (henceforth ``niche overlap'') varies over 
+		  phylogenetic distance and how this differs between plant families. 
+		  Whereas previous 
+		  studies have focused on the presence or absence of phylogenetic
+		  signal across entire networks, we take a pairwise perspective in
+		  order to obtain a more detailed picture of how plant phylogeny
+		  relates to network structure.
+As different plant families may have experienced different degrees of coevolution, convergence, etc., we also complement analyses with entire networks with comparisons among plants in the same family within a network.
+		  This novel perspective allows us to investigate the relationship between phylogenetic distance and partner overlap at different scales.
+
+  		\end{quotation}
+
+	18. Critique of manuscript structure [[not sure  how to address]]
 
@@
 
-		\textbf{R:} The Referee appears to be confounded by our manuscript in general and is extremely dismissive of our understanding of how to write a manuscript...
+		\textbf{R:} Where, specifically, does the Referee feel that we have included discussion in our results? This vague and somewhat condescending feedback is not helpful.
 
@@
 
-	30. Another demand to discuss intimacy
+	30. Another demand to discuss intimacy [[possibly addressable, since we did add a tiny reference in intro]]
 
@@
 
-{\Large \bf Reply to Referee 3}
+{\Large \bf Reply to Referee 3} [[Still to do: title, add a bit about how this could be relevant for conservation.]]
 
@@
 
-	2. Request to state that networks are qualitative rather than quantitative
+	2. Request to state that networks are qualitative rather than quantitative [[done]]
 
-	3. L298 – Please be careful with use of “lesser/greater” “more negative or positive than expected from permuted networks”
+		\textbf{R:} The Referee is correct that the difference between qualitative and quantitative networks is crucial for the correct ecological interpretation of said networks.
+We thank them for pointing out that the distinction wasn't clear in the previous version.
+We now specify that our networks are qualitative at the beginning of the methods and results and the end of the discussion.
+We hope that these few reminders will be enough to remind readers about the structure of our networks.
 
-	4. Confusion about result in line 322
+		Lines XX-XX (methods):
+
+		\begin{quotation}
+
+			All networks were qualitative, recording the presence or 
+		    absence of interactions rather than their strength.
+
+		\end{quotation}
+
+		Lines XX-XX (results):
+
+		\begin{quotation}
+
+			Note that, as our networks 
+		    are qualitative, these results refer only to the number of shared interaction
+	    	partners rather than to the quantitative strength of competition.
+
+    	\end{quotation}
+
+    	Lines XX-XX (discussion):
+
+    	\begin{quotation}
+
+		  Although here we considered only the presence or absence of interactions,
+		  (i.e., qualitative networks)
+
+    	\end{quotation}
+
+	3. L298 – Please be careful with use of “lesser/greater” “more negative or positive than expected from permuted networks” [[done]]
+
+		\textbf{R:} We appreciate that this desceription could be unclear, and have revised this line as suggested. It now reads:
+
+		Lines XX-XX:
+
+		\begin{quotation}
+
+			the observed 
+		    slope of the relationship between phylogenetic distance and interaction 
+		    partner overlap was always more extreme (i.e., always more negative or 
+		    always more positive) than that obtained in the permuted networks (Fig. 2).
+
+	    \end{quotation}
+
+	4. Typo in line 322 [[done]]
 
@@
 
-		\textbf{R:}
+		\textbf{R:} The Referee is correct and we apologize for this extremely confusing typo. We have corrected this line as suggested.
 
@@
 
-This is the first time I review the present manuscript, so I apologise in advance if my comments were already addressed in previous reviewing rounds (despite checking with the most recent reply to reviewers).
+1. Confusion about description of two dependent variables in analyses
 
-Statistical analyses
-
+	\begin{refquote}
 		* Modelling the relationship between niche overlap and phylogenetic distance
@@
 
+		\smallskip
+
+		p. 5, l. 69-71 « In either case, dissimilarity (…). » This sentence helped me to understand why it is important to look at unshared interactions. To be better showcased ?
+
+	\end{refquote}
+
+	\textbf{R:} The number of shared and unshared interactions are both dependent variables included in the analysis.
+The number of shared variables is indeed the key variable, but the number of unshared interactions is also important as it indicates how extraordinary a particular number of shared interactions is.
+The binomial process incorportates both quantities; converting the numbers of shared and unshared interactions to a proportion and weighting the observations by the total number of interactions.
+[[Need to address this in the text]]
+
+2. Request to state that we use the Jaccard index more explicitly [[done]]
+
+	\begin{refquote}
 		I suppose that the analysis described in paragraph starting from l.
@@
 (1)), while in the first paragraph, an equation should specify that M_ij ~ B(M_ij + U_ij, w_ij)).
+	\end{refquote}
 
+	\textbf{R:} Yes, this analysis is also using a Jaccard index, but we see how the previous version did not make this clear.
+We now state that both the tuple and proportional glm's use Jaccard dissimilarity.
+We also re-iterate the logic behind the tuple-based formulation in this paragraph.
+
+		Lines XX-XX:
+
+		\begin{quotation}
+
+			To demonstrate the power of defining $\omega_{ij}$ as a tuple of $M_{ij}$ and $U_{ij}$, we repeated the above analyses using a Jaccard index based only on the proportion of interaction partners that are shared (i.e., $\omega_{ij}$ = $M_{ij}$/[$M_{ij}+U_{ij}$]).
+Note that while the proportion of shared interaction partners is the same in both cases, the tuple formulation gives more weight to plants with many interaction partners as these provide more information.
+When comparing the two approaches
+		    we observed similar trends but, notably, the tuple definition of $\omega_{ij}$ had greater power to detect weak relationships (\emph{Supporting information 2}).
+We therefore show only the results when defining $\omega_{ij}$ as a tuple in the main text.
+
+		\end{quotation}
+
+3. Request to make non-independence of species within each community explicit. [[done]]
+
+	\begin{refquote}
 		Another point pertains to the definition of “trials” in the binomial-distributed process.
@@
 This should be specified, I think.
+	\end{refquote}
 
+	\textbf{R:} We actually address the non-independence of trials (pairs of plants) by calculating $p$-values based on permutations of the observed networks (as opposed to assuming independent, binomially-distributed trials, which is certainly not the case).
+To emphasize our explanation of this, we have reordered the text and placed our discussion of the permutation methods under the sub-heading 'accounting for non-independence'.
+We hope that this will calm reader's worries about the validity of our conclusions.
+
+4. Permuting the permuted networks is confusing
+
+	\begin{refquote}
 		* Evaluating type I and type II errors: Permutations of permutations
@@
 		Actually, I find the comment in Supplementary information 3 clearer, although no reference to Supplementary information 3 is made.
-Besides, as slopes of regressions in permuted networks are tightly grouped around zero (Fig.
-2, thin lines indicating extrema of slopes distribution overlapping each other), so type II errors do not seem to be a big problem here.
+		Besides, as slopes of regressions in permuted networks are tightly grouped around zero (Fig. 2, thin lines indicating 
+		extrema of slopes distribution overlapping each other), so type II errors do not seem to be a big problem here.
+	\end{refquote}
 
+	\textbf{R:} We agree with the Referee about the difficulty of describing this procedure.
+[[Can I just swap in whatever is in S3?]] Despite the difficulty in describing our process for finding type II error verbally, we are pleased that the Referee found the end result (Fig.
+2) interpretable.
+[[Maybe I can move all of the type II error testing to SI?]]
+
+5. Suggestion to consider phylogenetic diversity instead of number of plant pairs
+
+	\begin{refquote}
 		* Testing the effect of network size on the existence of a phylogenetic signal
@@
 		I think knowing more about this effect would further illuminate why the strength of the phylogenetic signal varies between networks and would be complementary to the analysis testing the effect of plant community composition.
+	\end{refquote}
 
+	\textbf{R:} Umm... what does this mean? [[Probably going to go with "beyond the scope"]]
+
+6. Request for consideration of multiple testing
+
+	\begin{refquote}
 		* Testing within-family existence of a phylogenetic signal
@@
 Yet, the authors can indicate that there are low chances to have that many significant phylogenetic signals (using the probability mass function of the Binomial distribution, see Moran 2003 in Oikos).
+	\end{refquote}
 
+	\textbf{R:} [[Wasn't this the point of looking at type I errors? Or something?]]
+
+7. Suggestion to mention sampling completeness as a potential explanation for specialists (discussion)
+
+	\begin{refquote}
 		On the effect of specialist pollinators
@@
 However, I think this should be mentioned in the text, at least to invite future works to provide their sampling effort when publishing new empirical data (hence, helping to improve future analyses).
+	\end{refquote}
 
+	\textbf{R:}
+
+8. Discussion of potential tradeoffs between interactions could be sharpened (discussion)
+
+	\begin{refquote}
 		On plant families involved in different types of interactions
@@
 		Despite the length of this last comment, I don’t mean that the authors should develop proportionally this paragraph, but rather sharpen it.
+	\end{refquote}
+
+	\textbf{R:} - merging interaction types is a good way to bring back to broader context :) - line 439-442 could be clarified based on Strauss & Whitthall (if I can find it) - more references for structure of interaction patterns: e.g., Astegiano et al.
+- be more tentative for dynamical drivers (apparently Sauve et al.
+don't really discuss stability).
+Could be a by-product of assembly process (Maynard et al., 2018)
 
@@
 
+9. Request for additional detail in summary point 2 [[done]]
+
+	\begin{refquote}
 		In the abstract, item 2 « shared and unshared interactions »: if it does not breach the word limit, I think a few words specifying why this is important would better showcase the study, and help to understand how it contributes to the study novelty.
+	\end{refquote}
 
+	\textbf{R:} We appreciate the Referee's suggestion.
+Although we did not have much room to expand the summary, we have added a short parenthetical explanation of why considering both shared and unshared partners is helpful.
+This point now reads:
+
+	\begin{quotation}
+
+		\item We quantify overlap of interaction partners for all pairs of plants in 59 pollination and 11 herbivory networks based on the numbers of shared and unshared interaction partners (thereby capturing both proportional and absolute overlap).
+We test 1) for relationships between phylogenetic distance and partner overlap within each network, 2) whether these relationships varied with the composition of the plant community, and 3) whether well-represented plant families showed different relationships.
+
+	\end{quotation}
+
+10. Incorrect referencing of Sauve et al., 2016 [[done]]
+
+	\begin{refquote}
 		p.3, l.
@@
 The following references are adequate though.
+	\end{refquote}
 
+	\textbf{R:} We have removed this reference as suggested.
+
+11. Possible typo in page 3, lines 9-10 [[done]]
+
+	\begin{refquote}
 		p. 3, l. 9-10 « A plant’s traits are also (...) », I think there is a typo here. Shouldn’t « a » be removed ?
+	\end{refquote}
 
+	\textbf{R:} We do not believe that the original formulation was incorrect, but agree that it was inelegant. We have revised this line to read:
+	\begin{quotation}
+		Plant traits are also likely to determine \emph{which} specific pollinators and herbivores interact with a particular plant.
+  	\end{quotation}
+  	We hope that this revised version reads better.
+
+12. ?Suggestion to remove long list of citations in lines 22-25? [[done]]
+
+	\begin{refquote}
 		p.
@@
 I think, it would be more relevant to the reader to cite these different works to explain how mixed results are (as done in the text following this long citation list).
+	\end{refquote}
 
-p. 5, l. 69-71 « In either case, dissimilarity (…). » This sentence helped me to understand why it is important to look at unshared interactions. To be better showcased ?
+	\textbf{R:} We had intended these citations to showcase a selection of researchers addressing different aspectsof phylogenetic signal, but appreciate how including them all together could be confusing.
+We have removed the large list so as not to distract from the more specific citations in subsequent lines.
 
+11. Better showcase sentence on page 5, lines 78 [[done]]
+
+	\begin{refquote}
 		p. 5, l. 78 « a pairwise perspective » : This contributes to the manuscript novelty. Maybe this should be further specified?
+	\end{refquote}
 
+	\textbf{R:} We thank the Referee for noticing this line, and have added a bit more detail as to how this pairwise perspective allows us to consider both whole-network trends and trends within families.
+
+	Lines XX-XX:
+
+	\begin{quotation}
+
+		Whereas previous 
+	  studies have focused on the presence or absence of phylogenetic
+	  signal across entire networks, we take a pairwise perspective in
+	  order to obtain a more detailed picture of how plant phylogeny
+	  relates to network structure. This novel perspective allows us to investigate the relationship between phylogenetic distance and partner overlap at different scales.
+
+	\end{quotation}
+
+12. Suggestion to make a figure showing distribution of webs, or at least to add countries to the list in SI [[done]]
+
+	\begin{refquote}
 		p.
@@
 Alternatively, and to emphasize on the title following Reviewer #2 suggestion in the previous round of review, a figure showing the spatial distributions of the 59 + 11 network on a world map would be welcome here.
+	\end{refquote}
 
+	\textbf{R:} We have added the countries or regions (e.g., islands associated with mainland countries, such as Greenland and Denmark) to Table 1 in the SI.
+We hope that this will provide enough clarification about the spatial scale of our dataset.
+For readers who are interested, we now refer both to the original sources and from an online database (the Web of Life dataset) which collects the pollination networks we used.
+These sources can be used to obtain more exact coordinates.
+
+13. Suggestions to clarify explanation of regressions [[done?]]
+
+	\begin{refquote}
 		p.
@@
 In addition, J_ij is never mentioned again as such (but is an estimate of w_ij).
+	\end{refquote}
 
+	\textbf{R:} We have reworded this section in an attempt to clarify the relationships between $M_{ij}$, $U_{ij}$, and $J_{ij}$ and better contrast the information given by each value.
+We have also changed all $\omega_{ij}$ to $J_{ij}$ for simplicity.
+This paragraph now reads:
+
+	\begin{quotation}
+	    We calculated niche overlap for each pair of plants $i$ and $j$ by 
+	    combining the number of shared interaction
+	    partners ($M_{ij}$) and the number of interaction partners which are not
+	    shared ($U_{ij}$) into a Jaccard index ($J_{ij}$) describing 
+	    the proportion of shared interactions. Importantly, we do this while 
+	    preserving the amount of information provided by each pair of plants
+	    (indicated by their numbers of interaction partners). $J_{ij}$ is usually defined as: 
+	    %
+	    \begin{equation}
+	      J_{ij} = \frac{M_{ij}}{P_i+P_j-M_{ij}} ,
+	    \end{equation}
+	    %
+	    where $M_{ij}$ is the set of \emph{mutual} (shared) interaction partners of 
+	    species $i$ and $j$ and $P_i$ and $P_j$ are the sizes of the sets of interaction 
+	    \emph{partners} for species $i$ and $j$ respectively. $J_{ij}$ can also be defined:
+	    %
+	    \begin{equation}
+	      J_{ij} = \frac{M_{ij}}{U_{ij}+M_{ij}} ,
+	    \end{equation}
+	    %
+	    since $U_{ij}$ = $P_{i}$+$P_{j}$-2$M_{ij}$. This second definition more closely
+	    relates to our methodology, which used the tuple ($M_{ij}$, $U_{ij}$) as the
+	    dependent variable rather than the single value $J_{ij}$. Using this tuple form
+	    allows us to give more 
+	    weight to species sharing a large number of interaction partners as well as 
+	    those sharing a large proportion (i.e., to emphasise pairs of generalists 
+	    sharing most of their interaction partners over specialists sharing a single 
+	    interaction partner).
+Note that species sharing a large \emph{number} of interaction partners may not share a large \emph{proportion} of interaction partners if the number of interaction partners that are not shared is also large.
+% Added because Josh got confused about the distinction.
+	    \end{quotation}
+
+14. R4 has identified the source of R2's confusion about whether we permuted interactions or phylogenetic distances!
+
+	\begin{refquote}
 		p.
@@
 Doing one of the other seems equivalent for this test, but this rephrasing is a bit confusing.
+	\end{refquote}
 
+	\textbf{R:}
+
+15. Typo in page 15, lines 322-324 [[done]]
+
+	\begin{refquote}
 		p.
@@
 Is it a typo or did I miss something in the manuscript?
+	\end{refquote}
 
+	\textbf{R:} Yes, this is indeed a typo.
+We did not have information on pollinator phylogenies and did not test anything from the pollinator perspective.
+We thank the Referee for pointing this out, and have corrected the line.
+The sentence now reads:
+
+	Lines XX-XX:
+	\begin{quotation}
+		More closely-related plants in pollination networks did, however, tend to share fewer interaction partners ($\beta_{pollination}$=-0.776, $p$=0.007), similar to our within-network results above.
+	\end{quotation}
+
+16. Fig. 3, Table 2 conflict for Poaceae
+
+	\begin{refquote}
 		Legend of Fig. 3 “(…) Melastomatoaceae and Poaceae in pollination networks are not significantly different from zero.” but Table 2 shows the opposite for Poaceae.
+	\end{refquote}
 
+	\textbf{R:}
+
+17. A confusing attempt at subtelty
+
+	\begin{refquote}
 		In the figures, \beta_distance is alternatively named “slope of regression line” (Fig. 2) and “change in log odds” (Fig. 3).
+	\end{refquote}
 
-References
+	\textbf{R:} I think this was intentional since both interpretations apply ... but this appears to have caused some confusion. Oops.
 
-Altermatt, F. and Pearse, I.S., 2011. Similarity and specialization of the larval versus adult diet of European butterflies and moths. The American Naturalist, 178(3), pp.372-382.
+% References
 
-Astegiano, J., Altermatt, F.
+% Altermatt, F. and Pearse, I.S., 2011. Similarity and specialization of the larval versus adult diet of European butterflies and moths. The American Naturalist, 178(3), pp.372-382.
+
+% Astegiano, J., Altermatt, F.
 and Massol, F., 2017.
@@
 
-Maynard, D.S., Serván, C.A. and Allesina, S., 2018. Network spandrels reflect ecological assembly. Ecology letters, 21(3), pp.324-334.
+% Maynard, D.S., Serván, C.A. and Allesina, S., 2018. Network spandrels reflect ecological assembly. Ecology letters, 21(3), pp.324-334.
 
-Melián, C.J., Bascompte, J., Jordano, P. and Krivan, V., 2009. Diversity in a complex ecological network with two interaction types. Oikos, 118(1), pp.122-130.
+% Melián, C.J., Bascompte, J., Jordano, P. and Krivan, V., 2009. Diversity in a complex ecological network with two interaction types. Oikos, 118(1), pp.122-130.
 
-Moran, M.D., 2003. Arguments for rejecting the sequential Bonferroni in ecological studies. Oikos, 100(2), pp.403-405.
+% Moran, M.D., 2003. Arguments for rejecting the sequential Bonferroni in ecological studies. Oikos, 100(2), pp.403-405.
 
-Strauss, S.Y. and Whittall, J.B., 2006. Non-pollinator agents of selection on floral traits. Ecology and evolution of flowers, pp.120-138.
+% Strauss, S.Y. and Whittall, J.B., 2006. Non-pollinator agents of selection on floral traits. Ecology and evolution of flowers, pp.120-138.
 

### 2019-11-22 manuscript/phylogenetic_signal_manuscript.tex
partial edits

@@
 \title{At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families.}
+[[Title bad, vague, needs replacing.]]
 
@@
 
-\section*{Summary} % Must be <200 words. Currently 199
+\section*{Summary} % Must be <200 words. Currently 200.
 
   \begin{itemize}
-    \item Related plants are often hypothesised to interact with similar sets of pollinators and herbivores, but empirical support for this idea is mixed.
-We argue that this may be because plant families vary in their tendency to share interaction partners.
+    \item Related plants are often hypothesised to interact with similar sets of pollinators and herbivores, but this idea has only mixed empirical support.
+This may be because plant families vary in their tendency to share interaction partners.
 
-    \item We introduce a novel way to quantify overlap of interaction partners for each pair of plants in 59 pollination and 11 herbivory networks based on the numbers of shared and unshared interaction partners.
-We test for relationships between phylogenetic distance and partner overlap within each network, and whether these relationships varied with the composition of the plant community.
-Finally, we test for different relationships within well-represented plant families.
+    \item We quantify overlap of interaction partners for all pairs of plants in 59 pollination and 11 herbivory networks based on the numbers of shared and unshared interaction partners (thereby capturing both proportional and absolute overlap).
+We test 1) for relationships between phylogenetic distance and partner overlap within each network, 2) whether these relationships varied with the composition of the plant community, and 3) whether well-represented plant families showed different relationships.
 
-    \item Across all networks, more closely-related plants tended to have greater overlap, especially in herbivory networks.
-The strength of this relationship within a network was unrelated to the composition of the network's plant component, but different plant families showed different relationships between phylogenetic distance and overlap of interaction partners.
+    \item Across all networks, more closely-related plants tended to have greater overlap.
+The strength of this relationship within a network was unrelated to the composition of the network's plant component, but, when considered separately, different plant families showed different relationships between phylogenetic distance and overlap of interaction partners.
 
     \item The variety of relationships between phylogenetic distance and partner overlap in different plant families likely reflects a comparable variety of ecological and evolutionary processes.
-Considering factors affecting the dominant plant families within a community may be the key to understanding the distribution of interactions.
+Considering factors affecting particular species-rich groups within a community may be the key to understanding the distribution of interactions at the network level.
 
@@
 
-defensive syndrome, ecological networks, herbivory, niche overlap, phylogenetic signal, pollination, pollination syndrome, specialisation
+ecological networks, herbivory, niche overlap, phylogenetic signal, pollination, specialisation
 
@@
   Interactions with animals affect plants' life cycles in several critical
-  ways~\citep{Mayr2001,Sauve2016}. On one hand,
+  ways~\citep{Mayr2001}. On one hand,
   pollination and other mutualistic interactions contribute
@@
   secondary metabolites may have fewer herbivores~\citep{Johnson2014}. 
-  A plant's traits are also likely to determine \emph{which} specific pollinators 
-  and herbivores interact with that plant. Plants with different defences 
+  Plant traits are also likely to determine \emph{which} specific pollinators 
+  and herbivores interact with a particular plant. Plants with different defences 
   (e.g., thorns vs. chemical defences) may deter different groups of 
-  herbivores~\citep{Ehrlich1964,Johnson2014}, and the concept of 
-  pollination syndromes has often been used to group plants into phenotypic
-  classes believed to attract certain groups of pollinators~\citep{Waser1996,Fenster2004,Ollerton2009}.
+  herbivores~\citep{Ehrlich1964,Johnson2014}, and pollinators with similar traits are often expected to attract similar sets of pollinators~\citep{Waser1996,Fenster2004,Ollerton2009}.
 
@@
   Recent studies that have investigated this question at the level of whole
-  communities, however, have yielded mixed results~\citep{Rezende2007a,Gomez2010,Rohr2014a,Fontaine2015,Lind2015,Ibanez2016,Bergamini2017,Sydenham2017,Volf2017,Hutchinson2017}.
+  communities, however, have yielded mixed results.
   In particular, significant phylogenetic signal in plants' sets of interaction partners tends to be rare in empirical networks (\citealp{Rezende2007a,Lind2015,Ibanez2016}; but see~\citealp{Elias2013,Fontaine2015,Hutchinson2017}).
@@
 In antagonistic networks, however, actively-foraging consumers tend to show less phylogenetic signal than their prey~\citep{Ives2006,Cagnolo2011,Naisbit2011,Fontaine2015}.
+In part, this may be related to different degrees of interaction intimacy (dependence of one predator on another), which appears to contribute to network structure in mutualistic, but not antagonistic, networks~\citep{Guimaraes2007,Ponisio2017}.
 Thus, it is not straightforward to assume that interactions will always be similar among related species.
@@
   order to obtain a more detailed picture of how plant phylogeny
-  relates to network structure. Specifically,
+  relates to network structure.
+As different plant families may have experienced different degrees of coevolution, convergence, etc., we also complement analyses with entire networks with comparisons among plants in the same family within a network.
+  This novel perspective allows us to investigate the relationship between phylogenetic distance and partner overlap at different scales. 
+  Specifically,
   we test 1) whether niche overlap decreases over increasing phylogenetic
@@
   phylogenetic distance differs systematically across plant families. 
-  This fine-grained approach gives more detailed information than 
   previous studies.
 
+  This fine-grained approach gives more detailed information than 
 % \clearpage
@@
     set of 59 pollination and 11 herbivory networks. These networks span 
-    a range of biomes (desert to scrub forest to grassland) and 
-    countries (Sweden to Australia). The herbivory networks included a 
-    variety of types of herbivores but were dominated by insects 
-    consuming leaves. To ensure that we were analysing interactions 
+    a range of biomes (desert to grassland to tundra) and 
+    countries (Sweden to New Zealand). The herbivory networks included a 
+    variety of types of herbivores but were dominated by leaf-chewing insects. To ensure that we were analysing interactions 
     influenced by similar sets of traits across networks, we restricted 
-    our herbivory networks to insects consuming leaves and excluded 
+    our herbivory networks to leaf-chewing insects and excluded 
     sap-sucking, leaf-mining, and galling insects as well as seed 
     predators and xylophagous insects; all of these interactions involve 
-    different plant tissues and means of feeding than leaf consumption 
+    different plant tissues and means of feeding than leaf chewing 
     and so may be influenced by different plant and insect traits. 
-    Specifically, we removed any non-leaf consuming insects and any 
+    Specifically, we removed any non-leaf chewing insects and any 
     plants which had no interaction partners after removing other types  
@@
     Supporting information 1} for details on the original sources of all 
-    networks.
+    networks. All networks were qualitative, recording the presence or 
+    absence of interactions rather than their strength.
 
@@
 
-    We calculated niche overlap for each pair of species within a community 
-    using a Jaccard index to describe the number of shared interaction 
-    partners, augmented with the number of interaction partners which were 
-    not shared. The Jaccard index $J_{ij}$ describes the proportion of 
-    shared interaction partners for species $i$ and $j$ and is defined as: 
+    We calculated niche overlap for each pair of plants $i$ and $j$ by 
+    combining the number of shared interaction
+    partners ($M_{ij}$) and the number of interaction partners which are not
+    shared ($U_{ij}$) into a Jaccard index ($J_{ij}$) describing 
+    the proportion of shared interactions. Importantly, we do this while 
+    preserving the amount of information provided by each pair of plants
+    (indicated by their numbers of interaction partners). $J_{ij}$ is usually defined as: 
     %
@@
     species $i$ and $j$ and $P_i$ and $P_j$ are the sizes of the sets of interaction 
-    \emph{partners} for species $i$ and $j$ respectively. We wished to give more 
+    \emph{partners} for species $i$ and $j$ respectively. $J_{ij}$ can also be defined:
+    %
+    \begin{equation}
+      J_{ij} = \frac{M_{ij}}{U_{ij}+M_{ij}} ,
+    \end{equation}
+    %
+    since $U_{ij}$ = $P_{i}$+$P_{j}$-2$M_{ij}$. This second definition more closely
+    relates to our methodology, which used the tuple ($M_{ij}$, $U_{ij}$) as the
+    dependent variable rather than the single value $J_{ij}$. Using this tuple form
+    allows us to give more 
     weight to species sharing a large number of interaction partners as well as 
@@
 % Added because Josh got confused about the distinction.
-    To capture all of this information for each species pair, we therefore recorded the number of 
-    shared interaction partners ($M_{ij}$) and the number of interaction partners 
-    that were not shared 
-    ($U_{ij}$ = $P_{i}$+$P_{j}$-2$M_{ij}$). Instead of a single index $J_{ij}$, 
-    we thus kept track of the full information needed to compute
-    niche overlap between species $i$ and $j$ as a tuple: ($M_{ij}$, $U_{ij}$).
 
@@
     approach is conceptually similar to modelling successes and failures in a 
-    binomial-distributed process. Accordingly, we assumed a binomially-distributed error structure and used a logit link function to model the 
-    probability $\omega_{ij}$ of plants $i$ and $j$ sharing an interaction 
-    partner. Regressions of niche overlap and phylogenetic distance within 
+    binomial-distributed process. Accordingly, we assumed a binomially-distributed error structure and used a logit link function to model the dissimilarity in interaction partners 
+    $J_{ij}$ of plants $i$ and $j$. Regressions of niche overlap and 
+    phylogenetic distance within 
     each network were fit using the R~\citep{R} base function ``glm'' and 
@@
       \begin{equation}
-        {\rm logit}\left(\omega_{ij}\right) \propto \beta_{distance}\delta_{ij} ,
+        {\rm logit}\left(J_{ij}\right) \propto \beta_{distance}\delta_{ij} ,
         \label{basic}
@@
     where $\delta_{ij}$ is the phylogenetic distance between plants $i$ and 
-    $j$. The fixed effect of distance in this regression, $\beta_{distance}$, 
+    $j$ and $J_{ij}$ is defined by the tuple ($M_{ij}$, $U_{ij}$) . 
+    The fixed effect of distance in this regression, $\beta_{distance}$, 
     can be understood as the change in log odds of sharing an interaction 
@@
       \begin{equation}
-        {\rm logit}\left(\omega_{ij}\right) \propto \beta_{distance} \delta_{ij} + \beta_{pollination} I_{ij} + \beta_{distance:pollination} \delta_{ij} I_{ij} ,
+        {\rm logit}\left(J_{ij}\right) \propto \beta_{distance} \delta_{ij} + \beta_{pollination} I_{ij} + \beta_{distance:pollination} \delta_{ij} I_{ij} ,
       \end{equation}
@@
 
-    To demonstrate the power of defining $\omega_{ij}$ as a tuple of $M_{ij}$ and $U_{ij}$, we repeated the above analyses instead defining $\omega_{ij}$ as the proportion of interaction partners that are shared (i.e., $M_{ij}$/[$M_{ij}+U_{ij}$]).
-We observed similar trends but, notably, the tuple definition of $\omega_{ij}$ had greater power to detect weak relationships (\emph{Supporting information 2}).
-We therefore show only the results when defining $\omega_{ij}$ as a tuple in the main text.
+    To demonstrate the power of defining $J_{ij}$ as a tuple of $M_{ij}$ and $U_{ij}$, we repeated the above analyses using a Jaccard index based only on the proportion of interaction partners that are shared (i.e., $J_{ij}$ = $M_{ij}$/[$M_{ij}+U_{ij}$]).
+Note that while the proportion of shared interaction partners is the same in both cases, the tuple formulation gives more weight to plants with many interaction partners as these provide more information.
+When comparing the two approaches
+    we observed similar trends but, notably, the tuple definition of $J_{ij}$ had greater power to detect weak relationships (\emph{Supporting information 2}).
+We therefore show only the results when defining $J_{ij}$ as a tuple in the main text.
+
+    To test whether the relationship between phylogenetic distance and niche overlap depended on network size, we fit a general linear model for the slope of this relationship inferred from the glm models against the number of plant pairs for which distances could be calculated (hereafter ``network size"), network type (again using herbivory networks as a baseline), and their interaction:
+  %
+      \begin{equation}
+        \beta_{distance} \propto \beta_{size} \eta_{N} + \beta_{pollination} I_N + \beta_{size:pollination} \eta_{N} I_N ,
+      \end{equation}
+  %
+    where $\eta_{N}$ is the number of plant pairs in network $N$ for which distances could be calculated, $I_N$ is an indicator equal to 1 if network $N$ is a pollination network and 0 otherwise.
+
+    As the interaction between network type and network size was strong and opposite to the direction of the main effect of network size, we fit an additional general linear model using only data from pollination networks and including only the effect of network size (herbivory networks were the baseline in the full glm).
+Both models were fit using the R~\citep{R} base function ``glm".
+
+    \subsubsection*{Accounting for non-independence}
 
@@
       alternative hypothesis was set farther from zero.
-
-    To test whether the relationship between phylogenetic distance and niche overlap depended on network size, we fit a general linear model for the slope of this relationship inferred from the glm models against the number of plant pairs for which distances could be calculated (hereafter ``network size"), network type (again using herbivory networks as a baseline), and their interaction:
-  %
-      \begin{equation}
-        \beta_{distance} \propto \beta_{size} \eta_{N} + \beta_{pollination} I_N + \beta_{size:pollination} \eta_{N} I_N ,
-      \end{equation}
-  %
-    where $\eta_{N}$ is the number of plant pairs in network $N$ for which distances could be calculated, $I_N$ is an indicator equal to 1 if network $N$ is a pollination network and 0 otherwise.
-
-    As the interaction between network type and network size was strong and opposite to the direction of the main effect of network size, we fit an additional general linear model using only data from pollination networks and including only the effect of network size (herbivory networks were the baseline in the full glm).
-Both models were fit using the R~\citep{R} base function ``glm".
 
@@
     types of networks, but a pair of congeners would be less likely to 
-    share pollinators than to share herbivores. As an illustration, a pair
+    share pollinators than to share herbivores. Note that, as our networks 
+    are qualitative, these results refer only to the number of shared interaction
+    partners rather than to the quantitative strength of competition.
+    As an illustration, a pair
     of plants which diverged 10mya would have a probability of 0.202 of sharing
@@
     slope of the relationship between phylogenetic distance and interaction 
-    partner overlap was always more extreme (i.e., always lesser or always 
-    greater) than that obtained in the permuted networks (Fig.~\ref{obs_vs_random}).
+    partner overlap was always more extreme (i.e., always more negative or 
+    always more positive) than that obtained in the permuted networks (Fig.~\ref{obs_vs_random}).
     Observed networks with a negative relationship between phylogenetic distance 
@@
 Pollination networks did not show a significantly different trend from the herbivory networks ($\beta_{distance:pollination}$=1.73, $p$=0.681).
-More closely-related pollinators did, however, tend to share fewer interaction partners ($\beta_{pollination}$=-0.776, $p$=0.007), similar to our within-network results above.
+More closely-related plants in pollination networks did, however, tend to share fewer interaction partners ($\beta_{pollination}$=-0.776, $p$=0.007), similar to our within-network results above.
 
@@
   Although here we considered only the presence or absence of interactions,
+  (i.e., qualitative networks)
   recent work also suggests that the phylogenetic composition of a plant

### 2019-11-22 manuscript/supporting_info.tex
partial edits

@@
 \date{\small$^1$Centre for Integrative Ecology, School of Biological Sciences\\
-\medskip$^2$Department of Ecology,\\
+\medskip$^2$Present address: Department of Ecology,\\
 Environment, and Plant Sciences (DEEP)\\
@@
   \begin{table}[!h]
-    \caption{Original sources for each network used in our analyses.}
+    \caption{Original sources for each network used in our analyses.
+All networks beginning 'M\_PL\_' were collected from~\citet{weboflife}.
+Further details for unpublished networks may be found there.}
     \label{sources}
     \begin{center}
-    \begin{tabular}{|l l m{10cm} |}
+    \begin{tabular}{|l l l m{8cm} |}
     \hline
-    Network & Network type & Original source \\
+    Network & Network type & Country & Original source  \\
     \hline
-    M\_PL\_001  & Pollination & \citep{Arroyo1982}  \\
-    M\_PL\_002  & Pollination & \citep{Arroyo1982}  \\
-    M\_PL\_003  & Pollination & \citep{Arroyo1982}  \\
-    M\_PL\_004  & Pollination & \citep{Barrett1987} \\
-    M\_PL\_005  & Pollination & \citep{Clements1923}  \\
-    M\_PL\_006  & Pollination & \citep{Dicks2002} \\
-    M\_PL\_007  & Pollination & \citep{Dicks2002} \\
-    M\_PL\_008  & Pollination & \citep{Dupont2003}  \\
-    M\_PL\_009  & Pollination & \citep{Elberling1999} \\
-    M\_PL\_010  & Pollination & Elberling, H. \& Olesen, J. M. Unpublished. \\
-    M\_PL\_011  & Pollination & \citep{Olesen2002a}  \\
-    M\_PL\_012  & Pollination & Olesen, J. M. Unpublished.  \\
-    M\_PL\_013  & Pollination & \citep{Ollerton2003}  \\
-    M\_PL\_014  & Pollination & \citep{Hocking1968} \\
-    M\_PL\_015  & Pollination & \citep{Petanidou1991} \\
-    M\_PL\_016  & Pollination & \citep{Herrera1988} \\
-    M\_PL\_017  & Pollination & \citep{Memmott2002} \\
-    M\_PL\_018  & Pollination & Olesen, J. M. Unpublished.  \\
-    M\_PL\_019  & Pollination & \citep{Inouye1988}  \\
-    M\_PL\_020  & Pollination & \citep{Kevan1970} \\
-    M\_PL\_021  & Pollination & \citep{Kato1990}  \\
-    M\_PL\_022  & Pollination & \citep{Medan2002} \\
-    M\_PL\_023  & Pollination & \citep{Medan2002} \\
-    M\_PL\_024  & Pollination & \citep{Mosquin1967} \\
-    M\_PL\_025  & Pollination & \citep{Motten1982}  \\
-    M\_PL\_026  & Pollination & \citep{McMullen1993}  \\
-    M\_PL\_027  & Pollination & \citep{Primack1983} \\
-    M\_PL\_028  & Pollination & \citep{Primack1983} \\
-    M\_PL\_029  & Pollination & \citep{Primack1983} \\
-    M\_PL\_030  & Pollination & \citep{Ramirez1992} \\
-    M\_PL\_031  & Pollination & \citep{Ramirez1989} \\
+    M\_PL\_001  & Pollination & Chile & \citep{Arroyo1982}  \\
+    M\_PL\_002  & Pollination & Chile & \citep{Arroyo1982}  \\
+    M\_PL\_003  & Pollination & Chile & \citep{Arroyo1982}  \\
+    M\_PL\_004  & Pollination & Canada (New Brunswick) & \citep{Barrett1987} \\
+    M\_PL\_005  & Pollination & U.S.A. (Colorado) & \citep{Clements1923}  \\
+    M\_PL\_006  & Pollination & U.K. (Norfolk) & \citep{Dicks2002} \\
+    M\_PL\_007  & Pollination & U.K. (Norfolk) & \citep{Dicks2002} \\
+    M\_PL\_008  & Pollination & Spain (Canary Islands) & \citep{Dupont2003}  \\
+    M\_PL\_009  & Pollination & Sweden & \citep{Elberling1999} \\
+    M\_PL\_010  & Pollination & Denmark (Greenland) & Elberling, H. \& Olesen, J. M. Unpub. \\
+    M\_PL\_011  & Pollination & Mauritius & \citep{Olesen2002a}  \\
+    M\_PL\_012  & Pollination & Portugal (Azores) & \citep{Olesen2002a}  \\
+    M\_PL\_013  & Pollination & South Africa (KwaZulu-Natal) & \citep{Ollerton2003}  \\
+    M\_PL\_014  & Pollination & Canada (N.W.T.) & \citep{Hocking1968} \\
+    M\_PL\_015  & Pollination & Greece (Athens) & \citep{Petanidou1991} \\
+    M\_PL\_016  & Pollination & Spain (Andalucia) & \citep{Herrera1988} \\
+    M\_PL\_017  & Pollination & U.K. (England) & \citep{Memmott2002} \\
+    M\_PL\_018  & Pollination & Denmark & Olesen, J. M. Unpublished.  \\
+    M\_PL\_019  & Pollination & U.S.A. (Colorado) & \citep{Inouye1988}  \\
+    M\_PL\_020  & Pollination & Canada (N.W.T.) & \citep{Kevan1970} \\
+    M\_PL\_021  & Pollination & Japan (Kyoto) & \citep{Kato1990}  \\
+    M\_PL\_022  & Pollination & Argentina (Mendoza) & \citep{Medan2002} \\
+    M\_PL\_023  & Pollination & Argentina (Mendoza) & \citep{Medan2002} \\
+    M\_PL\_024  & Pollination & Canada (N.W.T.) & \citep{Mosquin1967} \\
+    M\_PL\_025  & Pollination & U.S.A. (North Carolina) & \citep{Motten1982}  \\
+    M\_PL\_026  & Pollination & Ecuador (Gal\'{a}pagos Islands) & \citep{McMullen1993}  \\
+    M\_PL\_027  & Pollination & New Zealand (South Island) & \citep{Primack1983} \\
+    M\_PL\_028  & Pollination & New Zealand (South Island) & \citep{Primack1983} \\
+    M\_PL\_029  & Pollination & New Zealand (South Island) & \citep{Primack1983} \\
+    M\_PL\_030  & Pollination & Venezuela & \citep{Ramirez1992} \\
+    M\_PL\_031  & Pollination & Venezuela & \citep{Ramirez1989} \\
     \hline
@@
     \begin{center}
-    \begin{tabular}{|l l m{6cm} |}
+    \begin{tabular}{|l l l m{6cm} |}
     \hline
-    Network & Network type & Original source \\
+    Network & Network type & Country & Original source \\
     \hline
-    M\_PL\_032  & Pollination & \citep{Schemske1978}  \\
-    M\_PL\_033  & Pollination & \citep{Small1976} \\
-    M\_PL\_034  & Pollination & \citep{SmithRamirez2005}  \\
-    M\_PL\_035  & Pollination & \citep{Percival1974}  \\
-    M\_PL\_036  & Pollination & Olesen, J. M. Unpublished.  \\
-    M\_PL\_037  & Pollination & \citep{Montero2005} \\
-    M\_PL\_038  & Pollination & \citep{Montero2005} \\
-    M\_PL\_039  & Pollination & \citep{Stald2003} \\
-    M\_PL\_040  & Pollination & \citep{Ingversen2006} \\
-    M\_PL\_041  & Pollination & \citep{Ingversen2006} \\
-    M\_PL\_042  & Pollination & \citep{Philipp2006} \\
-    M\_PL\_043  & Pollination & \citep{Montero2005} \\
-    M\_PL\_044  & Pollination & \citep{Kato2000}  \\
-    M\_PL\_045  & Pollination & \citep{Lundgren2005}  \\
-    M\_PL\_046  & Pollination & \citep{Bundgaard2003} \\
-    M\_PL\_047  & Pollination & \citep{Dupont2009a}  \\
-    M\_PL\_048  & Pollination & \citep{Dupont2009a}  \\
-    M\_PL\_049  & Pollination & \citep{Bek2006}  \\
-    M\_PL\_050  & Pollination & \citep{Stald2003} \\
-    M\_PL\_051  & Pollination & \citep{Vazquez2002} \\
-    M\_PL\_052  & Pollination & \citep{Witt1998}  \\
-    M\_PL\_053  & Pollination & \citep{Yamazaki2003}  \\
-    M\_PL\_054  & Pollination & \citep{Kakutani1990}  \\
-    M\_PL\_055  & Pollination & \citep{Kato1996}  \\
-    M\_PL\_056  & Pollination & \citep{Kato1993}  \\
-    M\_PL\_057  & Pollination & \citep{Inoue1990} \\
-    M\_PL\_058  & Pollination & \citep{Bartomeus2008} \\
-    M\_PL\_059  & Pollination & \citep{Bezerra2009} \\
-    Basset  & Herbivory & \citep{Basset1996}  \\
-    Bluthgen  & Herbivory & \citep{Bluthgen2006}  \\
-    Bodner  & Herbivory & \citep{Bodner2010}  \\
-    Coley & Herbivory & \citep{Coley2006} \\
-    Ibanez  & Herbivory & \citep{Ibanez2013}  \\
-    Joern\_altuda  & Herbivory & \citep{Joern1979} \\
-    Joern\_marathon  & Herbivory & \citep{Joern1979} \\
-    Novotny & Herbivory & \citep{Novotny2012} \\
-    Peralta & Herbivory & \citep{Peralta2016} \\
-    Sheldon & Herbivory & \citep{Sheldon1978} \\
-    Ueckert & Herbivory & \citep{Ueckert1971} \\
+    M\_PL\_032  & Pollination & U.S.A. (Illinois) & \citep{Schemske1978}  \\
+    M\_PL\_033  & Pollination & Canada (Ontario) & \citep{Small1976} \\
+    M\_PL\_034  & Pollination & Chile & \citep{SmithRamirez2005}  \\
+    M\_PL\_035  & Pollination & Jamaica & \citep{Percival1974}  \\
+    M\_PL\_036  & Pollination & Portugal (Azores) & Olesen, J. M. Unpublished.  \\
+    M\_PL\_037  & Pollination & Denmark & \citep{Montero2005} \\
+    M\_PL\_038  & Pollination & Denmark & \citep{Montero2005} \\
+    M\_PL\_039  & Pollination & Spain (Canary Islands) & \citep{Stald2003} \\
+    M\_PL\_040  & Pollination & Jamaica & \citep{Ingversen2006} \\
+    M\_PL\_041  & Pollination & Dominica & \citep{Ingversen2006} \\
+    M\_PL\_042  & Pollination & Ecuador (Gal\'{a}pagos Islands) & \citep{Philipp2006} \\
+    M\_PL\_043  & Pollination & Denmark & \citep{Montero2005} \\
+    M\_PL\_044  & Pollination & Japan (Amami Islands) & \citep{Kato2000}  \\
+    M\_PL\_045  & Pollination & Denmark (Greenland) & \citep{Lundgren2005}  \\
+    M\_PL\_046  & Pollination & Denmark & \citep{Bundgaard2003} \\
+    M\_PL\_047  & Pollination & Denmark & \citep{Dupont2009a}  \\
+    M\_PL\_048  & Pollination & Denmark & \citep{Dupont2009a}  \\
+    M\_PL\_049  & Pollination & Denmark & \citep{Bek2006}  \\
+    M\_PL\_050  & Pollination & Spain (Canary Islands) & \citep{Stald2003} \\
+    M\_PL\_051  & Pollination & Argentina (R\'{i}o Negro) & \citep{Vazquez2002} \\
+    M\_PL\_052  & Pollination & Denmark (Greenland) & \citep{Witt1998}  \\
+    M\_PL\_053  & Pollination & Japan (Kyusu) & \citep{Yamazaki2003}  \\
+    M\_PL\_054  & Pollination & Japan (Kyoto) & \citep{Kakutani1990}  \\
+    M\_PL\_055  & Pollination & Japan (Fukui Prefacture) & \citep{Kato1996}  \\
+    M\_PL\_056  & Pollination & Japan (Yamanashi) & \citep{Kato1993}  \\
+    M\_PL\_057  & Pollination & Japan (Kibune) & \citep{Inoue1990} \\
+    M\_PL\_058  & Pollination & Spain (Catalonia) & \citep{Bartomeus2008} \\
+    M\_PL\_059  & Pollination & Brazil (Bu\'{i}que) & \citep{Bezerra2009} \\
+    Basset  & Herbivory & Papua New Guinea & \citep{Basset1996}  \\
+    Bl\"{u}thgen  & Herbivory & Malaysia (Sabah) & \citep{Bluthgen2006a}  \\
+    Bodner  & Herbivory & Ecuador & \citep{Bodner2010}  \\
+    Coley & Herbivory & Panama & \citep{Coley2006} \\
+    Ibanez  & Herbivory & France (Central French Alps) & \citep{Ibanez2013}  \\
+    Joern\_altuda  & Herbivory & U.S.A. (Texas) & \citep{Joern1979} \\
+    Joern\_marathon  & Herbivory & U.S.A. (Texas) & \citep{Joern1979} \\
+    Novotny & Herbivory & Papua New Guinea & \citep{Novotny2012} \\
+    Peralta & Herbivory & New Zealand (South Island) & \citep{Peralta2016} \\
+    Sheldon & Herbivory & U.S.A. (Washington) & \citep{Sheldon1978} \\
+    Ueckert & Herbivory & U.S.A. (Colorado) & \citep{Ueckert1971} \\
     \hline

### 2019-11-25 manuscript/reply_to_referees_2.tex
more corrections. Nearly done with R4

@@
 
-	19. Possible complaint about mixing numbers and percentages?
+	19. Incorrect claim that beginning of results is inaccurate [[done]]
 
@@
 		\textbf{R:} This comment is in such poor English as to be nearly unintelligible.
-It is not clear whether the Referee is suggesting that we repeat our analyses using half of the pollination networks (without any clear reason as to why) or complaining that we have mixed qualitative descriptors, numbers, and percentages.
-We assume the latter as we are able to address this complaint.
-[[check what's going on]]
-
-	20. Confusion about methodology
+It is not clear whether the Referee is suggesting that we repeat our analyses using half of the pollination networks (without any clear reason as to why) or is simply confused about which analysis these results refer to.
+Since the Referee appears to have assumed that the within-family analyses are the \emph{only} analyses in the manuscript, the latter seems likely.
+
+		Note that the results in lines XX-XX correspond to our first analysis: testing whether niche overlap decreases over increasing phylogenetic
+		distance in a large dataset of pollination and herbivory networks.
+The overall regression did show that partner overlap decreases with increasing phylogenetic distance, so that more distantly-related plants are less likely to share interaction partners (see Fig.
+1).
+The rest of this section gives more details about the differences between pollination and herbivory networks (lines XX-XX) and variation across networks (lines XX-XX), but note that none of these details change the overall regression.
+As this text is correct we have left it unchanged.
+
+	20. Definition of community composition unclear [[done]]
 
@@
 
-		\textbf{R:} Community composition is the set of plant species that make up a community.
-It was defined by the researchers constructing each network according to the specific methodology employed in each case.
-[[Add a parenthetical definition]]
-
-	21. Confusion about permutation methodology
+		\textbf{R:} Community composition is the set of plant species that make up a community, as described by the researchers constructing each network.
+For tractability, we have summarized community composition as the number of species in each plant family.
+We have added text to the methods to state this more obviously.
+
+		Lines XX-XX:
+
+		\begin{quotation}
+			Next, we examined the connection between our network-level observations
+		    and the number of species in each plant family present in each community.
+		    Specifically, we tested the hypothesis that
+		    varying relationships between phylogenetic distance and
+		    pairwise niche overlap are due to the different distributions 
+		    of families across networks. We defined the relationship between
+		    phylogenetic distance and niche overlap as the change in 
+		    log odds of two plants in a given network sharing an interaction 
+		    partner per million years of divergence (i.e., the slope $\beta_{distance}$ from the 
+		    regression of niche overlap against phylogenetic distance within
+		    a single network). We then related differences in this relationship
+		    to differences in the composition of the plant community (defined as the number of species in each plant family present in each network) using a non-parametric permutational multi-variate 
+		    analysis of variance (PERMANOVA;~\citealp{Anderson2001}).
+	    \end{quotation}
+
+	21. Confusion about permutation methodology [[done]]
 
@@
 
-		\textbf{R:} [[double-check and provide a line ref]]
-
-	22. Request to change direction of relationship?
+		\textbf{R:} As stated in the methods, we permuted interactions. Note that, in statistical terms, the two approaches are equivalent. We have rephrased the results to match the methods.
+
+	22. Typo in Fig. 1 caption [[done]]
+
 		\begin{refquote}
@@
 
-		\textbf{R:} Sweet Satan, I hope this isn't a typo?
+		\textbf{R:} We thank the Referee for pointing out this truly egregious typo, and have corrected it.
 
@@
 
-	24. Missing word in line 328
+	24. Confusion about line 328 [[done]]
 
@@
 
-		\textbf{R:}
-
-	25. Sundry complaints about table numbering and figure referencing
+		\textbf{R:} Yes, 12 is the number of families. We have revised the line to make this more explicit.
+
+		Lines XX-XX:
+
+		\begin{quotation}
+
+		In pollination networks, overlap decreased significantly with increasing phylogenetic distance in 12 of the 48 well-represented families
+
+		\end{quotation}
+
+	25. Complaints about table numbering and figure referencing [[done]]
 
@@
 
-		\textbf{R:}
+		\textbf{R:} We have reordered the tables and added a redundant reference to Fig. 3.
 
@@
 
-4. Permuting the permuted networks is confusing
+4. Permuting the permuted networks is confusing [[done]]
 
@@
 	\textbf{R:} We agree with the Referee about the difficulty of describing this procedure.
-[[Can I just swap in whatever is in S3?]] Despite the difficulty in describing our process for finding type II error verbally, we are pleased that the Referee found the end result (Fig.
-2) interpretable.
-[[Maybe I can move all of the type II error testing to SI?]]
+We have added an extra line to further explain the logic behind the second round of permutations and hope that this will clarify the goal of these analyses.
+We have also added a reference to Supplementary Information 3 and thank the Referee for pointing out the oversight.
+
+	Lines XX-XX:
+
+	\begin{quotation}
+		This permutation approach also allows us to estimate type I and type II 
+	    error for our analysis.
+Because the permuted networks should not demonstrate any particular relationship between phylogenetic distance and partner overlap, these slopes should be similar to those obtained after permuting these networks a second time.
+	\end{quotation}
 
@@
 
-	\textbf{R:} [[Wasn't this the point of looking at type I errors? Or something?]]
+	\textbf{R:} [[Wasn't this the point of looking at type I errors? Or something?]] [[maybe we talk about this in the discussion?]][[Or I can compare to the permuted networks?]]
 
@@
 
-14. R4 has identified the source of R2's confusion about whether we permuted interactions or phylogenetic distances!
+14. Rephrasing of permutation strategy confusing [[done]]
 
@@
 
-	\textbf{R:}
+	\textbf{R:} We thank the Referee for pointing out this rephrasing, and have corrected the results to read the same as the methods.
 
@@
 
-16. Fig. 3, Table 2 conflict for Poaceae
+16. Fig. 3, Table 2 conflict for Poaceae [[done]]
 
@@
 
-	\textbf{R:}
-
-17. A confusing attempt at subtelty
-
-	\begin{refquote}
-		In the figures, \beta_distance is alternatively named “slope of regression line” (Fig. 2) and “change in log odds” (Fig. 3).
-	\end{refquote}
-
-	\textbf{R:} I think this was intentional since both interpretations apply ... but this appears to have caused some confusion. Oops.
+	\textbf{R:} We thank the Referee for pointing out this error.
+The table is correct, and the change in log odds for \emph{Poaceae} in pollination networks was significant.
+We have corrected the legend of Fig.
+3.
+
+17. A confusing attempt at subtelty [[done]]
+
+	\begin{refquote}
+		In the figures, $\beta_{distance}$ is alternatively named “slope of regression line” (Fig. 2) and “change in log odds” (Fig. 3).
+	\end{refquote}
+
+	\textbf{R:} $\beta_{distance}$ is both the slope of the regression line \emph{and} the change in log odds of a pair of plants sharing a partner as distance increases.
+We wanted to include both interpretations to help readers relate the regressions to what is happening ecologically.
+However, we can see how having the different interpretations isolated in different figures could be confusing.
+We have therefore added parenthetical definitions in both captions to make it clear that Fig.
+2 and Fig.
+3 are referring to the same quantity.
 

### 2019-11-25 manuscript/phylogenetic_signal_manuscript.tex
more corrections. Nearly done with R4

@@
       This permutation approach also allows us to estimate type I and type II 
-      error for our analysis. To do this, we created 500 permutations of each 
+      error for our analysis.
+Because the permuted networks should not demonstrate any particular relationship between phylogenetic distance and partner overlap, these slopes should be similar to those obtained after permuting these networks a second time.
+      To estimate type I and type II errors, we created 500 permutations of each 
       permuted network and, again keeping the observed phylogenetic distances 
-      between plant species, repeated our analyses. We can then determine the 
+      between plant species, repeated our analyses. We could then determine the 
       number of permuted networks which appear to have significant 
@@
       networks means that the type II error would increase linearly as the 
-      alternative hypothesis was set farther from zero.
+      alternative hypothesis was set farther from zero (\emph{Supporting Information 3}).
 
@@
     Next, we examined the connection between our network-level observations
-    and the plant families present in each community.
+    and the number of species in each plant family present in each community.
     Specifically, we tested the hypothesis that
@@
     a single network). We then related differences in this relationship
-    to differences in the composition of the plant community in each
-    network using a non-parametric permutational multi-variate 
+    to differences in the composition of the plant community (defined as the number of species in each plant family present in each network) using a non-parametric permutational multi-variate 
     analysis of variance (PERMANOVA;~\citealp{Anderson2001}).
@@
     Comparing the results in the observed networks to those obtained after 
-    permuting phylogenetic distances across pairs of plants, the observed 
+    permuting interactions, the observed 
     slope of the relationship between phylogenetic distance and interaction 
@@
     Considering each family separately, the relationship between within-family niche overlap and phylogenetic distance varied widely in both pollination and herbivory networks. 
-    For the 48 families that were well represented in pollination networks, overlap decreased significantly with increasing phylogenetic distance in 12 (Table~\ref{family_slopes_pp}).
+    In pollination networks, overlap decreased significantly with increasing phylogenetic distance in 12 of the 48 well-represented families (Table~\ref{family_slopes_pp}; Fig.~\ref{within_family_regression}).
     There was no significant relationship between overlap and phylogenetic distance in
@@
   \begin{table}[!h]
-  \caption{\small Change in log odds (per million years of phylogenetic distance) of a pair of plants in the same family sharing a herbivore.}
-  % These are from the regressions within each family. P-vals need to be replaced, to come from randomizations. Coefficients should be fine.
-  \label{family_slopes_ph}
-  \begin{tabular}{|l  rr|}
-  \hline
-    Family & Change in log odds & $P$-value \\
-    \hline
-    \emph{Asteraceae} & -1.73 &  0.550 \\
-    \emph{Euphorbiaceae} & -19.2 & \textbf{\textless0.001} \\
-    \emph{Fabaceae} & 18.7 &  \textbf{0.046} \\
-    \emph{Melastomataceae} & -13.2 & \textbf{0.022} \\
-    \emph{Moraceae} & -2.13 & 0.092 \\
-    \emph{Nothofagaceae} & -595 & \textgreater{0.999} \\
-    \emph{Pinaceae} &  -25.8 & 0.733 \\
-    \emph{Poaceae} & -4.50 & \textbf{0.020} \\
-    \emph{Rubiaceae} & -8.16 &  \textbf{0.006} \\
-  \hline
-  \end{tabular}
-  \smallskip
-  \footnotesize
-
-  Nine plant families were sufficiently diverse in our  dataset to permit this analysis
-  (see \emph{Materials \\and Methods} for details). For each pattern of overlap, we show the change
-  in log odds per million years \\and the associated $P$-value. Statistically significant values are
-  indicated in bold. \\
-
-  \end{table}
-
-  \begin{table}[!h]
   \caption{
@@
 
+  \begin{table}[!h]
+  \caption{\small Change in log odds (per million years of phylogenetic distance) of a pair of plants in the same family sharing a herbivore.}
+  % These are from the regressions within each family. P-vals need to be replaced, to come from randomizations. Coefficients should be fine.
+  \label{family_slopes_ph}
+  \begin{tabular}{|l  rr|}
+  \hline
+    Family & Change in log odds & $P$-value \\
+    \hline
+    \emph{Asteraceae} & -1.73 &  0.550 \\
+    \emph{Euphorbiaceae} & -19.2 & \textbf{\textless0.001} \\
+    \emph{Fabaceae} & 18.7 &  \textbf{0.046} \\
+    \emph{Melastomataceae} & -13.2 & \textbf{0.022} \\
+    \emph{Moraceae} & -2.13 & 0.092 \\
+    \emph{Nothofagaceae} & -595 & \textgreater{0.999} \\
+    \emph{Pinaceae} &  -25.8 & 0.733 \\
+    \emph{Poaceae} & -4.50 & \textbf{0.020} \\
+    \emph{Rubiaceae} & -8.16 &  \textbf{0.006} \\
+  \hline
+  \end{tabular}
+  \smallskip
+  \footnotesize
+
+  Nine plant families were sufficiently diverse in our  dataset to permit this analysis
+  (see \emph{Materials \\and Methods} for details). For each pattern of overlap, we show the change
+  in log odds per million years \\and the associated $P$-value. Statistically significant values are
+  indicated in bold. \\
+
+  \end{table}
+
+\clearpage
+
 \section*{Figures}
@@
      networks (bottom; purple). In both network types, the probability of a pair of plants
-     sharing an interaction partner increased with increasing phylogenetic distance (thick,
+     sharing an interaction partner decreased with increasing phylogenetic distance (thick,
      dark lines).
@@
     \end{center}
-     \caption{The slopes of the mixed-effect logistic regression of pairwise niche overlap against phylogenetic distance was signficantly different from 0 for each network.
+     \caption{The slopes of the mixed-effect logistic regression of pairwise niche overlap against phylogenetic distance (representing the change in log odds of a pair of plants sharing an interaction partner) was signficantly different from 0 for each network.
 Here we show the observed slopes for herbivory (green squares) and pollination (purple diamonds) networks.
@@
     \end{center}
-    \caption{Change in the log odds of a pair of plants sharing a pollinator or herbivore as phylogenetic distance between the plants increases.
+    \caption{Change in the log odds of a pair of plants sharing a pollinator or herbivore (i.e., the slopes of the mixed-effect logistic regressions) as phylogenetic distance between the plants increases.
 These values are analogous to the slopes of the regression lines from Eq.
@@
     For clarity, we show only the 15 plant families for which the slope of the regression of the proportion of shared interaction partners against phylogenetic distance was significant in at least one network type.
-    Note that the change in log odds for \emph{Asteraceae} in herbivory networks and \emph{Melastomataceae} and \emph{Poaceae} in pollination networks are not significantly different from zero; we present these values only for comparison across network types.
+    Note that the change in log odds for \emph{Asteraceae} in herbivory networks and \emph{Melastomataceae} in pollination networks are not significantly different from zero; we present these values only for comparison across network types.
 All other plant families were well-represented in only one network type.

### 2019-11-25 manuscript/reply_to_referees_2.tex
more corrections. Nearly done with R4

@@
 
-1. Confusion about description of two dependent variables in analyses
+1. Confusion about description of two dependent variables in analyses [[done]]
 
@@
 The binomial process incorportates both quantities; converting the numbers of shared and unshared interactions to a proportion and weighting the observations by the total number of interactions.
-[[Need to address this in the text]]
+We thank the Referee for pointing out text in the introduction which clarifiedthe purpose of including unshared interactions.
+We have expanded the beginning of this section to explain the logic of our modelling approach in more detail.
+
+	lines XX-XX:
+
+	\begin{quotation}
+
+	    We calculated niche overlap for each pair of plants $i$ and $j$ based on the number of shared interaction
+	    partners ($M_{ij}$) and the number of interaction partners which are not
+	    shared ($U_{ij}$). The number of unshared interaction 
+	    partners gives valuable information about cases where, for example, 
+	    closely-related plants may have experienced disruptive selection, leading to weaker phylogenetic signal.
+The number of shared and unshared interaction partners together indicates the amount of information  provided by each pair of plants: a pair of generalists which share most of their interaction partners gives a stronger indication of phylogenetic signal than a pair of specialists with one common interaction partner.
+
+	\end{quotation}
 
@@
 
-5. Suggestion to consider phylogenetic diversity instead of number of plant pairs
+5. Suggestion to consider phylogenetic diversity instead of number of plant pairs [[done]]
 
@@
 
-	\textbf{R:} Umm... what does this mean? [[Probably going to go with "beyond the scope"]]
+	\textbf{R:} We agree that phylogenetic diversity would be another option for quantifying the 'size' of these networks.
+However, defining the phylogenetic diversity of each network would depend strongly upon the correctness of of base tree.
+As we discuss in the methods, our estimates for non-angiosperms are likely to be fairly rough, and some other species are also only approximately dated.
+Because of this, and because this analysis would more compliment our community-composition analysis than introduce new material, we have opted no to pursue phylogenetic diversity in this manuscript.
+Here, we were more concerned with numbers of plant pairs since numbers of species are known to affect many areas of network structure.
+This did not appear to be a major issue for our analyses.
 

### 2019-11-25 manuscript/phylogenetic_signal_manuscript.tex
more corrections. Nearly done with R4

@@
 
-    We calculated niche overlap for each pair of plants $i$ and $j$ by 
-    combining the number of shared interaction
+    We calculated niche overlap for each pair of plants $i$ and $j$ based on the number of shared interaction
     partners ($M_{ij}$) and the number of interaction partners which are not
-    shared ($U_{ij}$) into a Jaccard index ($J_{ij}$) describing 
+    shared ($U_{ij}$). The number of unshared interaction 
+    partners gives valuable information about cases where, for example, 
+    closely-related plants may have experienced disruptive selection, leading to weaker phylogenetic signal.
+The number of shared and unshared interaction partners together indicates the amount of information  provided by each pair of plants: a pair of generalists which share most of their interaction partners gives a stronger indication of phylogenetic signal than a pair of specialists with one common interaction partner.
+
+    We combined the numbers ofshared and unshared interaction partners
+    into a Jaccard index ($J_{ij}$) describing 
     the proportion of shared interactions. Importantly, we do this while 

### 2019-11-25 manuscript/reply_to_referees_2.tex
more changes. Making progress.

@@
 
+Given the difference of opinion between Referees 1, 3, and 4 and Referee 2, we have prioritised adjusting the manuscript according to the majority view.
+Nevertheless, we have taken care to address each of Referee 2's comments and, where possible, have used them to improve the manuscript.
+
 \closing{Regards,}
@@
 
-	The Referee(s?) seems to view our basic question and analyses positively, but is rather critical of our  writing both in terms of logical clarity and style.
-It is also clear that the Referee is more interested in coevolution than in any purely ecological network patterns.
-We thank the referee for taking the time to provide such extensive feedback and have done our best to incorporate as many of their suggestions as possible, although our ecological focus means that we have not made coevolution a major theme.
-Nevertheless, we now mention the potential for coevolution to affect network structure in the discussion.
-We address each comment in detail below (preceded by \textbf{R:}).
-It appears that the Referee wrote their specific comments before reading the manuscript in its entirety.
-Thus, some of the Referee's objections are in fact addressed at later points.
-In these cases, we have juxtaposed the Referee's comments to demonstrate this.
-
-	1. General criticism of the language of the text
+	The Referee(s?) seems to view our basic question and analyses positively, but is rather bluntly critical of our writing in terms of logical, clarity, and style.
+Some of these criticisms seem to reflect a rather hasty reading of the manuscript, as there are points where the Referee asks why we did not conduct analyses that we did in fact perform or demands that we address biological complications that already appear later in the text.
+In these cases, we point to existing evidence in the manuscript and have tried to make these connections more obvious.
+We address the Referee's other comments in detail below (preceded by \textbf{R:}).
+We hope that this response will clarify the focus and scope of our analyses.
+
+	1. General criticism of the language of the text [[done]]
 
@@
 
-		\textbf{R:} We would like to point out that both the lead and corresponding authors of this manuscript are native English speakers and that Referees 1 and 3 praised the quality of our writing.
-Of course technical correctness does not necessarily imply clarity of expression, and so we have revised the manuscript according to the Referee's suggestions.
-[[Given the Referee's own moderate to poor command of English, this is a hell of a thing to say!!]] If our loquacious verbiage has obfuscated any modicum of information, we apologise.
-
-	2. Title lacks clarity
+		\textbf{R:} As Referees 1 and 3 note, our English is scrupulously correct.
+Of course technical correctness does not necessarily imply clarity of expression, and we apologise if our choice of vocabulary has obfuscated some of the finer points of the manuscript.
+We have endeavoured to clarify the manuscript as the Referee suggests.
+
+	2. Title lacks clarity [[fuck off]]
 
@@
 		\end{refquote}
+
+		\textbf{R:} We have revised the title following a more detailed suggestion by Referee 3 and hope that the new title does not suggest logical inconsistency to this Referee.
 
@@
 
-	18. Critique of manuscript structure [[not sure  how to address]]
+	18. Critique of manuscript structure [[too vague - can't address]]
 
@@
 
-		\textbf{R:} Where, specifically, does the Referee feel that we have included discussion in our results? This vague and somewhat condescending feedback is not helpful.
+		\textbf{R:} Without knowing where, specifically, the Referee feels that we have included discussion in our results there is little we can do to address this complaint.
 
@@
 
-	28. Another complaint about sub-setting the herbivory networks, possibly addressable in text
+	28. Confusing complaint about subsetting herbivory networks or perhaps objection to the claim that oligotrophy is common [[done]]
 
@@
 
-		\textbf{R:}
+		\textbf{R:} We must again point out that subsetting the herbivory networks as we have done was requested during an earlier round of review.
+We are therefore reluctant to reconsider this approach without a very good reason.
+Beyond that, it is very difficult to work out exactly what the Referee objects to in this sentence.
+If the Referee is objecting to our references, note that~\citet{Novotny2005} addresses leaf-chewers as intermediate in their level of specialisation on particular families and emphasises that herbivores in general (regardless of guild) tend to consume a few closely-related hosts.
+They point out the relative rarity of strict specialists compared to specialists on species within a particular genus or family.~\citet{Brandle2006} also found insect herbivores were specialised on a particular genus but consumed multiple species within the genus.
+As~\citet{Brandle2006} focus on phytophagous insects specifically, we feel that this reference addresses our point more directly than~\citet{Yguel2011}.
+We have therefore replaced this reference.
+
+		If the Referee objects to our finding that the herbivores in our networks tended to consume more than one plant species, there is little we can do about it.
+That is simply what our data say.
+We do not feel that it is appropriate to look for explanations in the trends we observe in our networks in other types of networks.
+
+		If the Referee is contending that, because of the multiple herbivore types in~\citet{Novotny2005}, we cannot claim that the herbivores in our dataset are oligotrophs, we can respond with further details.
+The mean number of plants consumed per herbivore ranged between 1.64 and 14.9 across networks, with a mean of 6.36.
+We hope that the Referee will agree that these low mean degrees do suggest that many of the herbivores in our dataset indeed consume only a few plant species.
+Our point therefore stands.
 
@@
 		\textbf{R:}
+
+"At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families.”
+
+- suggests that we focus on broad support. Maybe "Broad conservation of pollinators and herbivores in a global dataset"?
+"Despite variation among families, pollinators and herbivores are broadly conserved among related plants"?
+"Related plants tend to share pollinators and herbivores, but strength of conservation varies among plant families"?
 
@@
 
-6. Request for consideration of multiple testing
+6. Request for consideration of multiple testing [[done]]
 
@@
 
-	\textbf{R:} [[Wasn't this the point of looking at type I errors? Or something?]] [[maybe we talk about this in the discussion?]][[Or I can compare to the permuted networks?]]
+	\textbf{R:} The Referee makes a very good point.
+We had considered these high numbers of significant slopes unlikely to occur by chance, even if we would expect one or two significant results by chance.
+This argument is somewhat difficult to make convincingly and briefly in the middle of the manuscript, however.
+Instead, we apply the sequential correlated Bonferroni test in~\citet{Drezner2016}.
+This development of this test was heavily motivated by the Moran paper you recommend, and we thank the Referee for pointing out this literature.
+We have added tables of the SCBT critical values to Supplemental Information 4 in order to provide readers with a bit more detail.
+
+	Lines XX-XX now read:
+
+	\begin{quotation}
+		 In pollination networks, overlap decreased significantly with increasing phylogenetic distance in 14 of the 48 well-represented families (Table~\ref{family_slopes_pp}; Fig.~\ref{within_family_regression}).
+If we apply the correlated Bonferroni correction to account for multiple testing~\citep{Drezner2016}, all of these slopes remain significant (\emph{Supplemental Information 4}).
+	\end{quotation}
+
+	In responding to this comment, we also noted that the number of significant families in the pollination networks was incorrectly quoted in the main text.
+As shown in Table 1, there are actually 14 significant families in the pollination web.
+We have corrected this error and thank the Referee again for calling our attention to this section of the results.
 

### 2019-11-25 manuscript/phylogenetic_signal_manuscript.tex
more changes. Making progress.

@@
     Considering each family separately, the relationship between within-family niche overlap and phylogenetic distance varied widely in both pollination and herbivory networks. 
-    In pollination networks, overlap decreased significantly with increasing phylogenetic distance in 12 of the 48 well-represented families (Table~\ref{family_slopes_pp}; Fig.~\ref{within_family_regression}).
+    In pollination networks, overlap decreased significantly with increasing phylogenetic distance in 14 of the 48 well-represented families (Table~\ref{family_slopes_pp}; Fig.~\ref{within_family_regression}).
+If we apply the correlated Bonferroni correction to account for multiple testing~\citep{Drezner2016}, all of these slopes remain significant (\emph{Supplemental Information 4}).
     There was no significant relationship between overlap and phylogenetic distance in
@@
     and in one family, \emph{Fabaceae}, overlap of interaction partners increased significantly with 
-    increasing phylogenetic distance.
+    increasing phylogenetic distance. If we again apply the correlated Bonferroni correction, all five significant slopes remain significant  (\emph{Supplemental Information 4}).
 
@@
   oligotrophs which consume only a few closely-related 
-  hosts~\citep{Novotny2005,Yguel2011}.
+  hosts~\citep{Novotny2005,Brandle2006}.
   These oligotrophs may affect overall phylogenetic signal in the same

### 2019-11-25 manuscript/supporting_info.tex
more changes. Making progress.

@@
 
+    To account for multiple testing, we compared the $p$-values of the significant slopes to critical values in a sequential correlated Bonferroni test~\citep{Drezner2016}.
+This test accounts for the increased likelihood of obtaining at least one significant result by chance when conducting multiple hypothesis tests, but is less conservative and less prone to type II errors than the original Bonferroni test.
+All $p$-values remained signficant after applying this test (Table~\ref{SCBT_values}).
+
+    \begin{table}[h!]
+        \caption{
+          Below, we show the ranked $p$-values for the significant slopes in pollination and herbivory networks side-by-side with the critical values from the SCBT.
+Any $p$-value which is less than the corresponding critical value remains significant.
+We obtained critical values separately for the pollination and herbivory networks.
+}
+          \label{SCBT_values}
+        \begin{tabular}{l | l | l l |}
+        Family & Network type & $p$-value & Critical value \\
+        \hline
+        \emph{Apocynaceae}      &   pollination &   0.037   &   0.05000 \\
+        \emph{Rubiaceae}  &   pollination &   0.026   &   0.03952 \\
+        \emph{Amaryllidaceae}   &   pollination &   0.015   &   0.03656 \\
+        \emph{Apiaceae}     &   pollination &   0.006   &   0.03300 \\
+        \emph{Poaceae}    &   pollination &   0.003   &   0.03009 \\
+        \emph{Asteraceae}      &   pollination &   \textless0.001   &   0.02784 \\
+        \emph{Boraginaceae}     &   pollination &   \textless0.001   &   0.02610 \\
+        \emph{Cistaceae}    &   pollination &   \textless0.001   &   0.02473 \\
+        \emph{Fabaceae}    &   pollination &   \textless0.001   &   0.02363 \\
+        \emph{Lamiaceae}    &   pollination &   \textless0.001   &   0.02273 \\
+        \emph{Lauraceae}    &   pollination &   \textless0.001   &   0.02198 \\
+        \emph{Plantaginaceae}  &   pollination &   \textless0.001   &   0.02134 \\
+        \emph{Polygonaceae}    &   pollination &   \textless0.001   &   0.02080 \\
+        \emph{Ranunculaceae}   &   pollination &   \textless0.001   &   0.02033 \\
+        \hline
+        \emph{Moraceae}         &herbivory&  0.046 & 0.05000 \\
+        \emph{Nothofagaceae}    &herbivory&  0.022 & 0.03201 \\
+        \emph{Pinaceae}         &herbivory&  0.020 & 0.02627 \\
+        \emph{Poaceae}          &herbivory&  0.006 & 0.02231 \\
+        \emph{Rubiaceae}        &herbivory&  \textless0.001 & 0.01952 \\
+        \hline
+     \end{tabular}
+    \end{table}
+
 \end{spacing}

### 2019-11-27 manuscript/reply_to_referees_2.tex
think I've finished R2

@@
 
-%\usepackage[britdate]{stockholm-letter}
- \usepackage[britdate,alyssa-signature]{stockholm-letter}
+ \usepackage[britdate]{SU-letter}
 \usepackage{times}
@@
 
+We are pleased to submit a revised version of our manuscript, NPH-MS-2019-30803.
+In response to a suggestion from Referee 3, we have retitled it "".
+We have also taken care to revise our methods section in response to the many helpful suggestions from Referee 4, and hope that our approach is now clearer.
+Finally, we have expanded the discussion to include some additional concepts suggested by Referees 2 and 4, and a possible application of our research suggested by Referee 3.
+
 Given the difference of opinion between Referees 1, 3, and 4 and Referee 2, we have prioritised adjusting the manuscript according to the majority view.
-Nevertheless, we have taken care to address each of Referee 2's comments and, where possible, have used them to improve the manuscript.
+We must also admit to having some difficulty parsing a number of Referee 2's comments in order to find what is being asked/suggestions.
+Nevertheless, we appreciate their time and effort in offering such extensive feedback.
+We have taken care to address each of Referee 2's comments and, where possible, have used them to improve the manuscript.
+
+We appreciate all of the Referee's comments and are confident that our manuscript is all the stronger for responding to them.
 
@@
 
-NPH-MS-2019-30803 At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families.
-by Cirtwill, Alyssa; Dalla Riva, Giulio; Baker, Nick; Ohlsson, Mikael; Norström, Isabelle; Wohlfarth, Inger-Marie; Thia, Josh; Stouffer, Daniel
-
-Dear Dr Cirtwill
-
-I write you in regard to your submitted manuscript, NPH-MS-2019-30803 "At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families.”, which has now been reviewed.
+% NPH-MS-2019-30803 At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families.
+% by Cirtwill, Alyssa; Dalla Riva, Giulio; Baker, Nick; Ohlsson, Mikael; Norström, Isabelle; Wohlfarth, Inger-Marie; Thia, Josh; Stouffer, Daniel
+
+% Dear Dr Cirtwill
+
+% I write you in regard to your submitted manuscript, NPH-MS-2019-30803 "At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families.”, which has now been reviewed.
 We found four reviewers (some original reviewers and some new) and they all generally enjoyed your revised manuscript.
 However, they also provided suggestions for some expanding certain sections and providing additional clarification.
-In particular, Reviewer #2 and #4 provide some detailed suggestions, especially with regard to keeping the aims and logic consistent, that will help strengthen the manuscript.
-
-Although resolving these issues will require some restructuring, I think you should be able to handle these suggestions through revision (see below) and, ultimately, this manuscript will make a nice contribution to the literature.
-
-Please carefully revise your manuscript and resubmit your revised version within 4 weeks. Please also include a summary of how you have incorporated the suggestions of the reviewers.
-
-Thank you for submitting your work to New Phytologist.
-
-Sincerely,
-
-Jana Vamosi
-Editor, New Phytologist
-
-*****************************************************************
-To revise your manuscript please click on the link below
-*** PLEASE NOTE: This is a two-step process. After clicking on the link, you will be directed to a webpage to confirm. ***
-
-https://mc.manuscriptcentral.com/newphytologist?URL_MASK=ebf0a265cb2d423bb35580e635386130
-
-Alternatively log on to New Phytologist ScholarOne Manuscripts:
-http://mc.manuscriptcentral.com/newphytologist
-
-Enter your Author Centre.
-
-Under the ‘My Manuscripts' list click on 'Manuscripts with Decisions'.
-From the list of manuscripts click the ‘create a revision' link, next to the manuscript you wish to submit a revision for.
-From here follow the instructions inputting you responses to the decision letter through to the uploading of your new files.
-
-Please note you will be unable to make your revisions directly on the submitted ScholarOne Manuscripts version of your manuscript.
-Instead, you should revise your original word processor file, and then submit the revised version.
-When revising your manuscript, please prepare two versions: 1) the final revised manuscript and 2) the revised manuscript with revision marks showing.
-The latter file should be designated as a 'document with revision changes highlighted' when uploading.
-
-In any correspondence regarding this manuscript, please include the manuscript reference number and copy the correspondence to New Phytologist Central Office (np-managinged@lancaster.ac.uk).
-*************************************************************
-
-Decision: Accept subject to revision
+In particular, Reviewer \#2 and \#4 provide some detailed suggestions, especially with regard to keeping the aims and logic consistent, that will help strengthen the manuscript.
+
+% Although resolving these issues will require some restructuring, I think you should be able to handle these suggestions through revision (see below) and, ultimately, this manuscript will make a nice contribution to the literature.
+
+% Please carefully revise your manuscript and resubmit your revised version within 4 weeks. Please also include a summary of how you have incorporated the suggestions of the reviewers.
+
+% Thank you for submitting your work to New Phytologist.
+
+% Sincerely,
+
+% Jana Vamosi
+
+% Editor, New Phytologist
+
+% Decision: Accept subject to revision
 
@@
 
-	23. Difference between minimum and maximum slopes not visible
+	23. Difference between minimum and maximum slopes not visible [[done]]
 
@@
 
-		\textbf{R:} [[Check that caption states that min and max are very close together since permutation completely destroyed pattern.]]
+		\textbf{R:} As the caption states, the minimum and maximum slopes were always very close to 0.
+We therefore had to choose between a y-axis scale which would show the observed slopes or one which would show the differences in slopes for the permutations.
+As the  observed slopes are far more important than knowing the exact values of the permutation slopes, we chose to prioritise the former.
 
@@
 
-	26. Blanket demand for more evolution content
+	26. Suggestion to include ideas about evolution and coevolution [[done]]
 
@@
 
-		\textbf{R:} THIS IS NOT AN EVOLUTION PAPER! WE HAVE NO DATA TO INFER ANYTHING ABOUT THE EVOLUTION OF THESE SYSTEMS!
-
-	27. Debate over the meaning of "broad"
+		\textbf{R:} We do include ideas about evolution and coevolution inour discussion.
+We completely agree that, together with ecological processes and environmental filtering, evolution and coevolution are very important in structuring networks.
+However, since we do not have trait or genetic data for our networks, we cannot comment with any certainty on which of our results are due to trait plasticity or environmental influence and which are due to evolution.
+We therefore mention possible evolutionary and ecological explanations together.
+
+		Specialists, for example, could have co-evolved with particular interaction partners.
+They could also, however, be able to interact with more species which simply do not appear in the study site due to competition, unsuitable soil conditions, etc.
+As Referee 4 notes, specialists may also simply be species which were sampled more rarely.
+That is, we may be missing interactions involving these species which actually do occur.
+Please note that the proportion of specialists is a potential explanation for the results we observed and not a key result in itself.
+As such, we feel that spending a great deal of time trying to explain this trend would distract readers from the main message of our paper.
+
+		Some examples of evolutionary ideas in the discussion:
+
+		Lines XX-XX:
+
+		\begin{quotation}
+
+			This relationship between overlap and 
+			phylogenetic distance is consistent with the idea that traits affecting 
+			interactions are heritable and change gradually
+			such that closely related plants resemble their common ancestor--- and
+			  each other ---more than they do distantly related 
+			  plants~\citep{Schemske1999,Gilbert2015,Ponisio2017}. The degree of 
+			  heritability of key traits may, however, differ between families. In
+			  some families, such as \emph{Asteraceae} in pollination networks, 
+			  the positive slope of this relationship was very shallow while in 
+			  others, such as \emph{Melastomataceae} in herbivory networks, the 
+			  positive slope was extremely steep. This could indicate different 
+			  rates of phenotypic drift or evolution in different families. 
+			  In other families, there was no significant relationship between phylogenetic
+			  distance and interaction partner overlap. In these cases, key traits affecting 
+			  plant-insect interactions may not be strongly
+			  conserved. Studies showing a stronger relationship between trait similarity
+			  and shared interaction partners than phylogenetic similarity and shared
+			  interaction partners suggest that traits may indeed be evolutionarily
+			  labile~\citep{Junker2015,Ibanez2016,Endara2017}.
+
+		\end{quotation}
+
+		Lines XX-XX:
+
+		\begin{quotation}
+
+			In other plant families
+			  with more moderate levels of specialisation, it is possible 
+			  that pollination and/or herbivory do not exert large
+			  selection pressures on the plants. If traits affecting pollination
+			  or herbivory are not heritable in these groups [\citealp{Kursar2009}] 
+			  or their phenotypes are constrained by other factors (e.g., 
+			  environmental conditions, trade-offs with other traits, ontogenic
+			  change [\citealp{Karinho2014}]), then we should not expect a relationship 
+			  between phylogenetic distance and overlap of interaction partners.
+
+		\end{quotation}
+
+		See also lines XX-XX, where we discuss constraints on traits. We have lightly revised these lines to reference evolution explicitly.
+
+		\begin{quotation}
+
+		 This may indicate that one type of interaction
+		  places greater evolutionary constraints upon these families than the other, 
+		  similar to the expectation that greater constraints upon consumers 
+		  than upon their resources explains the asymmetry in conservation  
+		  of interaction partners~\citep{Fontaine2015}. Plants
+		  may not be able to respond to selection on both types of interaction
+		  simultaneously because traits affecting pollination can also affect herbivory, and vice
+		  versa~\citep{Strauss1997,Strauss2002,Adler2004,Adler2006,Theis2006}.
+  		\end{quotation}
+
+	27. Objection to the word "broad" [[done]]
 
@@
 This is a very strong sentence that is not supported by your results.
-You found evidence in 55% of plant-pollination networks (almost half of your dataset).
+You found evidence in 55\% of plant-pollination networks (almost half of your dataset).
 In fact, it is interesting to note that even the slope is more pronounced in mutualistic networks you found higher support in herbivory networks, as a higher percentage of networks showed a tendency.
@@
 
-		\textbf{R:}
+		\textbf{R:} Note that 56\% is greater than half, and that when all networks were considered together we also observed the same trends.
+We contend that these two facts do represent broad support for our hypothesis.
+It is not, of course, universal support.
+That is why we A) did not claim universal support and B) provide the numbers of networks.
+Readers are thereby armed with the tools to agree or disagree with our choice of words.
+In case it is the synonymy between broad and general that has perplexed the Referee, we have changed this line to state ''We found \emph{general} support...''.
+We hope that this is clearer.
+
+		With the unbalanced sample sizes of pollination and herbivory networks, we are somewhat reluctant to make much of the difference between 56\% of pollination networks and 64\$ of herbivory networks.
+We consider that the important point here is that networks are more likely than not to show decreasing niche overlap with increasing phylogenetic distance.
 
@@
 		\begin{refquote}
-			351-352 The herbivory networks did not contain as many obligate specialists, but we note that many herbivorous insects are oligotrophs which consume only a few closely-related hosts (Novotny & Basset, 2005; Yguel et al., 2011).
+			351-352 The herbivory networks did not contain as many obligate specialists, but we note that many herbivorous insects are oligotrophs which consume only a few closely-related hosts (Novotny \& Basset, 2005; Yguel et al., 2011).
 This sentence is confuse because you have a subsample of herbivory networks and then this seems to be a by-product of your study design associated with your decision of removing networks that may show strong phylogenetic signal.
@@
 We are therefore reluctant to reconsider this approach without a very good reason.
+
 		Beyond that, it is very difficult to work out exactly what the Referee objects to in this sentence.
@@
 We have therefore replaced this reference.
+We hope that this improved selection of references will help the Referee's confusion.
 
@@
 		If the Referee is contending that, because of the multiple herbivore types in~\citet{Novotny2005}, we cannot claim that the herbivores in our dataset are oligotrophs, we can respond with further details.
-The mean number of plants consumed per herbivore ranged between 1.64 and 14.9 across networks, with a mean of 6.36.
-We hope that the Referee will agree that these low mean degrees do suggest that many of the herbivores in our dataset indeed consume only a few plant species.
+The mean number of plants consumed per herbivore ranged between 1.64 and 14.9 across networks, with a mean of 6.36, and the median ranged bewteen 1 and 11.5 (mean 4.68).
+These measures indicate that many herbivores in our networks do, in fact, consume only a few of the plants available to them.
 Our point therefore stands.
 
-	29. Claims that congeneric species are not closely related
+	29. Claims that congeneric species are not closely related [[No convincing reason to change]]
 
@@
 Without some sources to substantiate this, we find this claim very far-fetched!
-
-	30. Another demand to discuss intimacy [[possibly addressable, since we did add a tiny reference in intro]]
+This is especially surprising given the Referee's insistence that we should expect similar interaction partners within a family.
+We agree that taxonomy is only a proxy for phylogeny, but we are not aware of any evidence that it is a poor proxy.
+We note that across seven other reviews, no other Referee has commented on this.
+Based on this lackof objection and similar language throughout the literature, we have opted not to change this line.
+
+	30. Another demand to discuss intimacy [[done. Look for more places to scattershot Hembry]]
 
@@
 
-		\textbf{R:}
+		\textbf{R:} We do not have any data on interaction intimacy, nor did we test for reciprocal specialisation, so we cannot say how this would influence our results.
+At a guess, we would guess that leaf-chewing herbivory and pollination are both low-herbivory interactions.
+We would therefore naively expect similar trends.
+We note that~\citet{Hembry2018} only study a very small and high-intimacy system (a single genus of brood pollinating moths and their single genus of host plants).
+Their results will therefore not necessarily generlize to the larger, more diverse networks we consider.
+Indeed, had they considered a broader sample of plants and seed predators or herbivores from the same islands, they easily could have found less reciprocal specialisation.
+As a detailed study of this unusual mutualism was the aim in~\citet{Hembry2018} this is not a problem for their work, but we are hesitant to infer too strong a relationship between their findings and ours.
+
+		This reference suggestion is also somewhat confusing as~\citet{Hembry2018} did not find evidence for host-associated differentiation in their moths.
+This would seem to undermine the Referee's fervent belief that evolution/coevolution can explain network structure.
+Moreover, they point out that the support for the intimacy hypothesis  in their system was broad (in the same sense we used the word) but equivocal.
+This exacerbates the difficulty of extrapolating their work to explain our results.
+
+		Given all of the above, it is hard to see how the interaction intimacy hypothesis relates to these lines (which are about whether the number of species in dfferent plant families is related to the strength of phylogenetic signal).
+Instead, we feel that a discussion of the possible effects of intimacy is more relevant later on, where we discuss possible reasons why some families may show different trends.
+Although we cannot test this, some families may interact more intimately with their pollinators/herbivores.
+This could result in more specialised relationships and weaker signal.
+We had mentioned this possibility briefly in lines 406-407 of the previous version, but are happy to expand upon this point somewhat.
+This section (lines XX-XX) now reads:
+
+		\begin{quotation}
+
+			Indeed, animal pollination and seed dispersal have been shown to act
+		  	as filters for several plant clades~\citep{Mayfield2009}, while selection to avoid 
+		  competition and restriction on numbers of interaction partners may lead to
+		  more intimate or specialised interactions~\citep{Ponisio2017}. 
+		  Reciprocal specialisation is particularly expected to occur in highly intimate interactions~\citep{Hembry2018}.
+Although pollination and leaf-chewing herbivory are both relatively low-intimacy interactions, it is still possible that some plant families may tend to have more intimate interactions than others.
+This could result, for example, if a plant is pollinated by an insect which is also a herbivore in its larval stage~\citep{Hembry2018}.
+Testing this possibility is beyond the scope of the present manuscript, but could be interestting for future work.
+
+		\end{quotation}
 
@@
 It is often difficult to see how theoretical work may relate to conservation practice, so we are glad to take the opportunity to make a link here.
-[[Add a bit of this, I think we have room]]
+[[Add a bit of this, I think we have room]] [[May make a good closing line?!?]]
 
@@
 "Despite variation among families, pollinators and herbivores are broadly conserved among related plants"?
-"Related plants tend to share pollinators and herbivores, but strength of conservation varies among plant families"?
+"Related plants tend to share pollinators and herbivores, but strength of phylogenetic signal varies among plant families"?
 
@@
 
-{\Large \bf Reply to Referee 4}
+{\Large \bf Reply to Referee 4} [[done]]
 
@@
 We appreciate that our writing can be dense at times and appreciate the Referee pointing out places where we may clarify our prose.
+We especially appreciate the detailed suggestions for how to improve our second-to-last paragraph, and have followed them to the best of our ability.
 Below, we respond to each comment in detail (preceded by \textbf{R:}).
@@
 			I did not managed to fully grasp the statistical analysis right away (I reckon I'm not a statistical master, but this may be the case of other readers), and I think it was mostly due to the way the methods are described.
-The writing is nice, but some tiny details are missing while they could help the reader to understand more quickly how the authors distinguish the use of the {M_ij, U_ij}-tuple from that of J_ij.
+The writing is nice, but some tiny details are missing while they could help the reader to understand more quickly how the authors distinguish the use of the {M\_ij, U\_ij}-tuple from that of J\_ij.
 			Based on l.
-143-167, I understand that the number of shared interactions M_ij is modelled with a binomial distribution, with the number of trials being M_ij+U_ij, and the probability of success being w_ij (M_ij ~ B(M_ij + U_ij, w_ij)).
-The {M_ij, U_ij}-tuple would appear in R as follows:
-		model ← glm(cbind(M_ij, M_ij+U_ij) ~ d_ij + ..., family = “binomial”)
+143-167, I understand that the number of shared interactions M\_ij is modelled with a binomial distribution, with the number of trials being M\_ij+U\_ij, and the probability of success being w\_ij (M\_ij ~ B(M\_ij + U\_ij, w\_ij)).
+The {M\_ij, U\_ij}-tuple would appear in R as follows:
+			model $\leftarrow$ glm(cbind(M\_ij, M\_ij+U\_ij) \~ d\_ij + ..., family = “binomial”)
 			But, can we actually say that there are two dependent variables?
@@
 			I suppose that the analysis described in paragraph starting from l.
-168 corresponds to actually modelling the Jaccard index (J_ij ~ ...).
+168 corresponds to actually modelling the Jaccard index (J\_ij \~ ...).
 If this is right, I think this should be specified in the second paragraph (no direct mention of the Jaccard index is currently made, except the proportion l.
 170 between brackets although it is not exactly written as in eq.
-(1)), while in the first paragraph, an equation should specify that M_ij ~ B(M_ij + U_ij, w_ij)).
+(1)), while in the first paragraph, an equation should specify that M\_ij ~ B(M\_ij + U\_ij, w\_ij)).
 		\end{refquote}
@@
 			Another point pertains to the definition of “trials” in the binomial-distributed process.
-If I get it right, these correspond to the union of species i and j interactions (of size P_i + P_j -2M_ij = M_ij + U_ij).
+If I get it right, these correspond to the union of species i and j interactions (of size P\_i + P\_j -2M\_ij = M\_ij + U\_ij).
 However, these are not independent for reasons highlighted in the introduction (e.g., competition, facilitation between plants and/or insects).
@@
 However, this leads to multiple testing which is prone to type I errors and I could not find mention of correction for this multiple testing in the text.
-There are actually high chances that there is at least one significant test in each table (1 – (1 – alpha)^N = 0.36 and 0.91 respectively, alpha = 0.05).
+There are actually high chances that there is at least one significant test in each table (1 – (1 – alpha)\^N = 0.36 and 0.91 respectively, alpha = 0.05).
 Yet, the authors can indicate that there are low chances to have that many significant phylogenetic signals (using the probability mass function of the Binomial distribution, see Moran 2003 in Oikos).
@@
 We have added tables of the SCBT critical values to Supplemental Information 4 in order to provide readers with a bit more detail.
+We have also added a few lines to the methods to formally introduce the problem of multiple testing, some of the objections to the strict Bonferroni in~\citet{Moran2003}, and our solution to it.
+
+		Lines XX-XX:
+
+		\begin{quotation}
+
+			By considering each family separately, we do risk obtaining some significant results purely by chance.
+The standard technique for addressing this type of multiple hypothesis testing, the Bonferroni correction, tends to be over-zealous and lead to a failure to reject the null hypothesis even when a large number of significant results before the correction supports the alternative hypothesis~\citep{Moran2003}.
+To account for multiple testing while also allowing the number of families showing significant trends to carry some weight, we use the correlated Bonferroni test introduced in~\citet{Drezler2016} (\emph{Supplemental Information 4}).
+
+		\end{quotation}
 
@@
 
-7. Suggestion to mention sampling completeness as a potential explanation for specialists (discussion)
+	7. Suggestion to mention sampling completeness as a potential explanation for specialists [[done]]
 
@@
 
-		I think that Reviewer #3 made an interesting remark on specialist pollinators, and I agree with the authors on the impossibility to assess sampling completeness on the network of this database.
+			I think that Reviewer \#3 made an interesting remark on specialist pollinators, and I agree with the authors on the impossibility to assess sampling completeness on the network of this database.
 However, I think this should be mentioned in the text, at least to invite future works to provide their sampling effort when publishing new empirical data (hence, helping to improve future analyses).
@@
 
-	\textbf{R:}
-
-8. Discussion of potential tradeoffs between interactions could be sharpened (discussion)
+		\textbf{R:} We share the Referee's desire to prompt researchers to share their sampling effort, and have added a short mention of the possibility  that some of our specialists are actually just rare.
+
+		Lines XX-XX:
+
+		\begin{quotation}
+
+			It is also likely that at least some of the apparent specialists in our dataset are actually rare species for which many interactions have not yet been observed~\citep{Bluthgen2006,Poisot2015}.
+Without information on the sampling completeness of the networks in our dataset, it is difficult to estimate the size of this effect.
+In any case, the degree of phylogenetic conservation of interaction partners may change as we obtain more complete data on rare species.
+
+		\end{quotation}
+
+	8. Discussion of potential tradeoffs between interactions could be sharpened [[done]]
 
@@
 439-442, “Plants may not be able to respond (…).”).
-Strauss & Whitthall’s chapter in the book “Ecology and evolution of flowers” gives a good insight on how these selection pressures can act together or antagonistically in shaping plants phenotypes (and eventually interactions, although not specifically discussed in their chapter).
+Strauss \& Whitthall’s chapter in the book “Ecology and evolution of flowers” gives a good insight on how these selection pressures can act together or antagonistically in shaping plants phenotypes (and eventually interactions, although not specifically discussed in their chapter).
 			Second, the structure of interaction patterns could be discussed with more references than Sauve et al.
@@
 
-	\textbf{R:} - merging interaction types is a good way to bring back to broader context :) - line 439-442 could be clarified based on Strauss & Whitthall (if I can find it) - more references for structure of interaction patterns: e.g., Astegiano et al.
-- be more tentative for dynamical drivers (apparently Sauve et al.
-don't really discuss stability).
-Could be a by-product of assembly process (Maynard et al., 2018)
+		\textbf{R:} We thank the Referee for their suggestions and for the small reading list.
+We have revised this paragraph along the lines above and hope that it is now clearer.
+We have expanded our discussion of (potentially) conflicting selection from different interaction types and removed our brief reference to dynamical drivers.
+We believe that sticking more closely to a single theme has helped to focus this paragraph.
+It now reads:
+
+		\begin{quotation}
+
+			For those few families which were well-represented in \emph{both} pollination
+			and herbivory networks, we can also contrast the 
+			trends in the two network types. Notably, all families except \emph{Asteraceae} 
+			showed different trends in different network types. 
+			This could be because of conflicting selection from pollinators and herbivores,
+			with one type of selection placing greater constraints on plant traits than the other.
+			Multiple types of interactions (e.g., pollination, herbivory, nectar robbing) 
+			and even environmental factors can influence traits such as 
+			flower colour, nectar abundance, and flowering phenology~citep{Strauss2006}. 
+			These influences can act in the same or different directions~\citep{Strauss2006}.
+			Plant phenotypes in turn affect which species participate in both pollination and herbivory~\citep{Strauss1997,Strauss2002,Adler2004,Adler2006,Theis2006}.
+			The interplay between these different selective pressures may mean that plants
+			cannot evolve to respond optimally to both pollinators and herbivores. Put another
+			way, stronger selective pressure from herbivores might cause phenotypic changes
+			that disrupt phylogenetic signal in pollinators, or vice versa. This could result from
+			asymmetric degree distributions: within a single system, most plants tend to interact
+			with many pollinators \emph{or} many herbivores but not both~\citep{Melian2009,Pockock2012,Astegiano2017}.
+			These asymmetric interactions may also affect higher-order network structures such as
+			modularity or nestedness~\citep{Astegiano2017}.
+The nature of the effects of multiple interaction types on both phylogenetic signal in interactions and overall network structure is, however, still an open question deserving of much more research.
+
+		\end{quotation}
 
@@
 » In supporting information, the countries are not indicated in the list.
-Alternatively, and to emphasize on the title following Reviewer #2 suggestion in the previous round of review, a figure showing the spatial distributions of the 59 + 11 network on a world map would be welcome here.
+Alternatively, and to emphasize on the title following Reviewer \#2 suggestion in the previous round of review, a figure showing the spatial distributions of the 59 + 11 network on a world map would be welcome here.
 		\end{refquote}
@@
 7, l.
-125-141 : I think the beginning of this section should be more straightforward and contrast better the information provided by M_ij and U_ij (starting with them) with that of the Jaccard index J_ij.
-In addition, J_ij is never mentioned again as such (but is an estimate of w_ij).
+125-141 : I think the beginning of this section should be more straightforward and contrast better the information provided by M\_ij and U\_ij (starting with them) with that of the Jaccard index J\_ij.
+In addition, J\_ij is never mentioned again as such (but is an estimate of w\_ij).
 		\end{refquote}
@@
 
+	% Check.
 % Astegiano, J., Altermatt, F.
@@
 
-% Maynard, D.S., Serván, C.A. and Allesina, S., 2018. Network spandrels reflect ecological assembly. Ecology letters, 21(3), pp.324-334.
-
-% Melián, C.J., Bascompte, J., Jordano, P. and Krivan, V., 2009. Diversity in a complex ecological network with two interaction types. Oikos, 118(1), pp.122-130.
-
-% Moran, M.D., 2003. Arguments for rejecting the sequential Bonferroni in ecological studies. Oikos, 100(2), pp.403-405.
-
-% Strauss, S.Y. and Whittall, J.B., 2006. Non-pollinator agents of selection on floral traits. Ecology and evolution of flowers, pp.120-138.
+	% Check. % Maynard, D.S., Serván, C.A. and Allesina, S., 2018. Network spandrels reflect ecological assembly. Ecology letters, 21(3), pp.324-334.
+
+	% Check. % Melián, C.J., Bascompte, J., Jordano, P. and Krivan, V., 2009. Diversity in a complex ecological network with two interaction types. Oikos, 118(1), pp.122-130.
+
+	% Check. % Moran, M.D., 2003. Arguments for rejecting the sequential Bonferroni in ecological studies. Oikos, 100(2), pp.403-405.
+
+	% Check. % Strauss, S.Y. and Whittall, J.B., 2006. Non-pollinator agents of selection on floral traits. Ecology and evolution of flowers, pp.120-138.
 

### 2019-11-27 manuscript/phylogenetic_signal_manuscript.tex
think I've finished R2

@@
 In the \emph{Lauraceae}, (represented by four species in one pollination network) and the \emph{Sapindaceae} (represented by five species in one herbivory network and five species in two pollination networks), only one pair of species per network type shared any interaction partners while all other pairs did not share any interaction partners.
+By considering each family separately, we do risk obtaining some significant results purely by chance.
+The standard technique for addressing this type of multiple hypothesis testing, the Bonferroni correction, tends to be over-zealous and lead to a failure to reject the null hypothesis even when a large number of significant results before the correction supports the alternative hypothesis~\citep{Moran2003}.
+To account for multiple testing while also allowing the number of families showing significant trends to carry some weight, we use the correlated Bonferroni test introduced in~\citet{Drezler2016} (\emph{Supplemental Information 4}).
 
@@
 
-  We found broad support for the hypothesis that more
+  We found general support for the hypothesis that more
   closely-related pairs of plants have a higher degree
@@
   The herbivory networks did not contain as many obligate 
-  specialists, but we note that many herbivorous insects are
-  oligotrophs which consume only a few closely-related 
-  hosts~\citep{Novotny2005,Brandle2006}.
+  specialists, but we note that herbivores, as well as pollinators, often interact with only a few closely-related plants~\citep{Novotny2005,Brandle2006,Astegiano2017}.
   These oligotrophs may affect overall phylogenetic signal in the same
-  way as the specialist partners: in both cases plants in different
-  families are unlikely to share interaction partners.
+  way as the strict specialists: in both cases plants in different
+  families are unlikely to share interaction partners since the interaction partners tend to only visit plants within a particular genus.
+It is also likely that at least some of the apparent specialists in our dataset are actually rare species for which many interactions have not yet been observed~\citep{Bluthgen2006,Poisot2015}.
+Without information on the sampling completeness of the networks in our dataset, it is difficult to estimate the size of this effect.
+In any case, the degree of phylogenetic conservation of interaction partners may change as we obtain more complete data on rare species.
 
@@
 
+  [[I don't like this paragraph. Refine?]]
   Moreover, \emph{Polygonaceae} in pollination networks and 
@@
   competition and restriction on numbers of interaction partners may lead to
-  more intimate or specialised interactions~\citep{Ponisio2017}. This is
+  more intimate or specialised interactions~\citep{Ponisio2017}. 
+  Reciprocal specialisation is particularly expected to occur in highly intimate interactions~\citep{Hembry2018}.
+Although pollination and leaf-chewing herbivory are both relatively low-intimacy interactions~\citep{Astegiano2017}, it is still possible that some plant families may tend to have more intimate interactions than others.
+This could result, for example, if a plant is pollinated by an insect which is also a herbivore in its larval stage~\citep{Hembry2018}.
+Testing this possibility is beyond the scope of the present manuscript, but could be interestting for future work.
+  Past selection to avoid competition is 
   consistent with the relatively high proportion of extreme specialists we
@@
   and herbivory networks, we can also contrast the 
-  trends in the two network types. While \emph{Asteraceae} showed the
-  expected decrease in interaction partner overlap with increasing
-  phylogenetic distance, the other families showed different trends in
-  different network types. This may indicate that one type of interaction
-  places greater constraints upon these families than the other, 
-  similar to the expectation that greater constraints upon consumers 
-  than upon their resources explains the asymmetry in conservation  
-  of interaction partners~\citep{Fontaine2015}. Plants
-  may not be able to respond to selection on both types of interaction
-  simultaneously because traits affecting pollination can also affect herbivory, and vice
-  versa~\citep{Strauss1997,Strauss2002,Adler2004,Adler2006,Theis2006}.
-  Associations with pollinators and herbivores may also be constrained by the
-  larger structure of the community. In one recent study, plants which are 
-  visited by many pollinators are also consumed by many herbivores~\citep{Sauve2016}.
-  This may be because pairing antagonistic and mutualistic interactions
-  balances the indirect effects of these interactions, leading to a
-  more stable community~\citep{Sauve2014}. As more networks describing 
-  pollination and herbivory in the same community become available, it 
-  will be interesting to test this hypothesis more thoroughly.
+  trends in the two network types. Notably, all families except \emph{Asteraceae} 
+  showed different trends in different network types. 
+  This could be because of conflicting selection from pollinators and herbivores,
+  with one type of selection placing greater constraints on plant traits than the other.
+  Multiple types of interactions (e.g., pollination, herbivory, nectar robbing) 
+  and even environmental factors can influence traits such as 
+  flower colour, nectar abundance, and flowering phenology~citep{Strauss2006}. 
+  These influences can act in the same or different directions~\citep{Strauss2006}.
+  Plant phenotypes in turn affect which species participate in both pollination and herbivory~\citep{Strauss1997,Strauss2002,Adler2004,Adler2006,Theis2006}.
+  The interplay between these different selective pressures may mean that plants
+  cannot evolve to respond optimally to both pollinators and herbivores. Put another
+  way, stronger selective pressure from herbivores might cause phenotypic changes
+  that disrupt phylogenetic signal in pollinators, or vice versa. This could result from
+  asymmetric degree distributions: within a single system, most plants tend to interact
+  with many pollinators \emph{or} many herbivores but not both~\citep{Melian2009,Pockock2012,Astegiano2017}.
+  These asymmetric interactions may also affect higher-order network structures such as
+  modularity or nestedness~\citep{Astegiano2017}.
+The nature of the effects of multiple interaction types on both phylogenetic signal in interactions and overall network structure is, however, still an open question deserving of much more research.
 
@@
 The maximum and minimum slopes obtained from 999 permutations of each network are depicted by thin, black lines.
-For both network types, the slopes obtained from permuted networks were always very close to 0.}
+For both network types, the slopes obtained from permuted networks were always very close to 0.
+}
     \label{obs_vs_random} 

### 2019-11-27 manuscript/reply_to_referees_2.tex
I like the text but it's too long now

@@
 	The Referee(s?) seems to view our basic question and analyses positively, but is rather bluntly critical of our writing in terms of logical, clarity, and style.
-Some of these criticisms seem to reflect a rather hasty reading of the manuscript, as there are points where the Referee asks why we did not conduct analyses that we did in fact perform or demands that we address biological complications that already appear later in the text.
+Some of these criticisms seem to reflect a rather hasty reading of the manuscript, as there are points where the Referee asks why we did not conduct analyses that we did in fact perform or demands that we address biological concepts that already appeared in the text.
 In these cases, we point to existing evidence in the manuscript and have tried to make these connections more obvious.
-We address the Referee's other comments in detail below (preceded by \textbf{R:}).
-We hope that this response will clarify the focus and scope of our analyses.
+In other cases, we struggled to understand the nature of the Referee's objections.
+We have attempted to address each of the Referee's comments in detail below (preceded by \textbf{R:}).
+We hope that our response will clarify the focus and scope of our analyses and help the Referee to re-think their objections.
 
@@
 
-	2. Title lacks clarity [[fuck off]]
+	2. Title lacks clarity [[done]]
 
@@
 
-		\textbf{R:} We have revised the title following a more detailed suggestion by Referee 3 and hope that the new title does not suggest logical inconsistency to this Referee.
+		\textbf{R:} We have revised the title following a more detailed suggestion by Referee 3 and hope that the new title no longer implies logical inconsistency.
 
@@
 		As we are \emph{not} searching for differences between communities at the family level, but rather at all levels within the angiosperms, a number of the Referee's comments do not apply.
-For example, the comments below:
+We list these below.
+The only bearing this criticism could have is on our choice to use families as a tool to group species for more detailed analyses.
+This decision is based on the fact that many plant families are quite diverse, both in terms of numbers of species and in terms of phenotypes/interaction partners (see e.g., Wilson on plants and insect/bird pollinators).
+Within a single family, plants can show evidence of adaptive radiations, heterogeneous selection, both, or neither.
+The Referee themself points out that some families can show both bird and bee pollination syndromes (see response \#8), and we can also point to papers such as Bernhardt 2000 and Johnson \& Jurgens 2010 which address trait lability, convergent evolution, and adaptive radiation.
+These different possibilities mean that it is not clear whether all families will show phylogenetic conservation of interaction partners.
+This makes families a convenient taxonomic level at which to look for finer-scale phylogenetic trends.
+As we found it difficult to find information on why  different families might show these different trends, we also hope to inspire future research along this  line.
+We have added a summary of this explanation to the methods.
+
+		Lines XX-XX:
+
+		\begin{quotation}
+
+			Finally, we wished to compare the breakdown of overlap of interactions in
+		    different plant families.
+		    Within-family genetic and trait diversity can be high due to adaptive radiations, heterogeneous selection, and other influences on different species.
+Plant families offer a reasonable balance between collecting enough species to identify meaningful trends and maintaining a tractable number of analyses.
+They are therefore the best taxonomic level to investigate phylogenetic conservation in more detail across our large dataset.
+
+		\end{quotation}
+
+		Comments that do seem to not apply:
 
@@
 
+		In addition to the above, we have added another brief discussion of intimacy in the discussion (see response \#28)
+
 	10. Criticisism of methodological changes required by previous reviewers [[done]]
@@
 
-	16. Un-justified request to include connectance [[just address here]]
+	14. Un-justified request to include connectance [[just address here]]
 
@@
 
-	17. Confusion about motivation for community composition analyses [[done]]
+	15. Confusion about motivation for community composition analyses [[done]]
 
@@
 
-	18. Critique of manuscript structure [[too vague - can't address]]
+	16. Critique of manuscript structure [[too vague - can't address]]
 
@@
 
-	19. Incorrect claim that beginning of results is inaccurate [[done]]
+	17. Incorrect claim that beginning of results is inaccurate [[done]]
 
@@
 
-	20. Definition of community composition unclear [[done]]
+	18. Definition of community composition unclear [[done]]
 
@@
 
-	21. Confusion about permutation methodology [[done]]
+	19. Confusion about permutation methodology [[done]]
 
@@
 
-	22. Typo in Fig. 1 caption [[done]]
+	20. Typo in Fig. 1 caption [[done]]
 
@@
 
-	23. Difference between minimum and maximum slopes not visible [[done]]
+	21. Difference between minimum and maximum slopes not visible [[done]]
 
@@
 
-	24. Confusion about line 328 [[done]]
+	22. Confusion about line 328 [[done]]
 
@@
 
-	25. Complaints about table numbering and figure referencing [[done]]
+	23. Complaints about table numbering and figure referencing [[done]]
 
@@
 
-	26. Suggestion to include ideas about evolution and coevolution [[done]]
+	24. Suggestion to include ideas about evolution and coevolution [[done]]
 
@@
 
-	27. Objection to the word "broad" [[done]]
+	25. Objection to the word "broad" [[done]]
 
@@
 
-	28. Confusing complaint about subsetting herbivory networks or perhaps objection to the claim that oligotrophy is common [[done]]
+	26. Confusing complaint about subsetting herbivory networks or perhaps objection to the claim that oligotrophy is common [[done]]
 
@@
 
-	29. Claims that congeneric species are not closely related [[No convincing reason to change]]
+	27. Claims that congeneric species are not closely related [[No convincing reason to change]]
 
@@
 
-	30. Another demand to discuss intimacy [[done. Look for more places to scattershot Hembry]]
+	28. Another demand to discuss intimacy [[done. Look for more places to scattershot Hembry]]
 
@@
 
-{\Large \bf Reply to Referee 3} [[Still to do: title, add a bit about how this could be relevant for conservation.]]
+{\Large \bf Reply to Referee 3} [[Done]]
 
@@
 It is often difficult to see how theoretical work may relate to conservation practice, so we are glad to take the opportunity to make a link here.
-[[Add a bit of this, I think we have room]] [[May make a good closing line?!?]]
-
-	1. Title is confusing
+We have reframed our closing paragraph to introduce the possibilities for using closely-related species in restoration efforts, and believe that it emphasises the importance of continuing research along this line.
+We hope that the Referee agrees that introducing this idea makes for a much stronger conclusion.
+
+	Lines XX-XX:
+
+	\begin{quotation}
+
+		Altogether, our study has revealed general trends for conservation of interaction
+		partners between closely-related species, with some networks and plant 
+		families showing different trends. This overall similarity between closely-related
+		species has a potential application in ecological restoration. Close relatives could
+		be used interchangeably to restore missing interactions and fill ecosystem functions. 
+		This may be advantageous when a target plant is more difficult to establish than its
+		relatives, or if the restoration site is not large enough to support viable populations 
+		of many species. We should urge caution, however, since plants which support the
+		same pollinators may also support similar sets of herbivores. To avoid unwanted 
+		indirect effects, all interactions involving the target species should be considered.
+		 Although here we considered only the presence or absence of interactions,
+		  (i.e., qualitative networks)
+		  recent work also suggests that the phylogenetic composition of a plant
+		  community can also affect the strength of 
+		  interactions, and that the spatial arrangement of plants within a 
+		  community may be particularly important~\citep{Yguel2011,Castagneyrol2014}.
+		These further nuances in the relationship between phylogenetic distance and 
+		niche overlap could also strongly affect the ability of closely-related species to
+		fill the same functions in restoration efforts. This is clearly a topic with many
+		unresolved questions, deserving of further study.
+
+	\end{quotation}
+
+	1. Title is confusing [[done]]
 
@@
 
-		\textbf{R:}
-
-"At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families.”
-
-- suggests that we focus on broad support. Maybe "Broad conservation of pollinators and herbivores in a global dataset"?
-"Despite variation among families, pollinators and herbivores are broadly conserved among related plants"?
-"Related plants tend to share pollinators and herbivores, but strength of phylogenetic signal varies among plant families"?
+		\textbf{R:} We have changed the title to state our main result while also pointing out some of the important variability between networks.
+We do feel that this variability is a major feature of our results, as well as previous studies of phylogenetic signal across systems, and it is too easy to forget if not emphasized.
+We hope that the Referee will agree that our new title, "Related plants tend to share pollinators and herbivores, but strength of phylogenetic signal varies among plant families", strikes a balance between these two considerations.
+
+		% "At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families.”
+
+		% - suggests that we focus on broad support. Maybe "Broad conservation of pollinators and herbivores in a global dataset"?
+		% "Despite variation among families, pollinators and herbivores are broadly conserved among related plants"?
+		% "Related plants tend to share pollinators and herbivores, but strength of phylogenetic signal varies among plant families"?
 

### 2019-11-27 manuscript/phylogenetic_signal_manuscript.tex
I like the text but it's too long now

@@
 
-\title{At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families.}
-[[Title bad, vague, needs replacing.]]
+\title{Related plants tend to share pollinators and herbivores, but strength of phylogenetic signal varies among plant families [[Alternative 1: Broad conservation of pollinators and herbivores in a global dataset]]
+[[Alternative 2: Despite variation among families, pollinators and herbivores are broadly conserved among related plants]]}
 
@@
 
-\section*{Word Counts}
+% \section*{Word Counts}
 
-Main text: 5612 % Limit 6,500
+% Main text: 6719 % Limit 6,500
+% Try to cut methods ... maybe then discussion.
 
-\begin{itemize}
-  \item Introduction: 1074
-  \item Materials and Methods: 2223 
-  \item Results: 890
-  \item Discussion: 1342
-  \item Acknowledgements: 83
-\end{itemize}
+% \begin{itemize}
+%   \item Introduction: 1165 
+%   \item Materials and Methods: 2619 
+%   \item Results: 960
+%   \item Discussion: 1892
+%   \item Acknowledgements: 83
+% \end{itemize}
 
-% Word counts updated July 2, include some comments.
+% \noindent Figures: 3
 
-Figures: 3
+% \noindent Tables: 2
 
-Tables: 2
+% \noindent Supporting information: 1 file containing 4 sections.
 
-Supporting information: 1 file containing 4 sections.
-
-\vspace{0.4 in}
+% \vspace{0.2 in}
 
@@
 \begin{spacing}{1.5}
-% \clearpage
+\clearpage
 
@@
 
-  Several mechanisms that might weaken the conservation of interactions
-  have been identified in the literature. Pollination and herbivory may be affected
+  There are several mechanisms that might weaken the conservation of interaction partners. Pollination and herbivory may be affected
   by a wide variety of traits, and not all of these are likely to be
@@
   floral displays are strongly affected by environmental conditions~\citep{Canto2004}, 
-  then pollinators may not be predicted by plants' phylogenies.
+  then plant phylogeny may not strongly predict pollination.
   Even if the traits affecting pollination and herbivory are
@@
   are attractive to pollinators can also increase 
-  herbivory~\citep{Strauss2002,Adler2004,Theis2006}. 
+  herbivory~\citep{Strauss2002,Adler2004,Strauss2006,Theis2006}. 
   Conversely, herbivory can reduce pollination by inducing chemical 
@@
   There may also be trade-offs between chemical and physical defences, or defences at different life stages, that weaken the overall heritability of plants' sets of herbivores~\citep{Karinho2014,Endara2017}.
-Observed patterns
-  of similarity in plants' interaction partners therefore represent
-  a mixture of environmental effects and various selection pressures as
-  well as plants' shared phylogenetic history.
+  A plant's set of interaction partners therefore reflects a mixture of different envionmental effects and different selection pressures, as well as shared phylogenetic history.
+  If these factors affect closely-related plants differently, then closely-related species may not have more similar interaction partners than distantly-related species.
 
-  A further complication is the possibility that the relationship between
-  plants' relatedness and the similarity of their interaction partners is
-  not constant across plant clades. Closely-related plants
-  in one clade might be under strong selection to favour dissimilar
-  sets of pollinators to avoid exchanging pollen with other
-  species~\citep{Levin1970,Bell2005,Mitchell2009}.
-Similarly, plants may experience disruptive selection on defences against herbivores if congeners tend to grow in the same places such that herbivore able to consume one species could easily spread to close relatives~\citep{Kursar2009}.
-  % Similar pressures  could also affect related plants' defences against herbivores if congeners tend to grow in the same places such that herbivores could easily move between them.  
-  Unrelated plants might also 
-  converge upon similar phenotypes, attracting a particularly 
-  efficient or abundant pollinator~\citep{Ollerton1996,Wilson2007,Ollerton2009,Ibanez2016}. 
+  This variety of different pressures makes it likely that the relationship between plants' relatedness and the similarity of their interaction partners is
+  not constant across plant clades. 
+  Closely-related plants in one clade might be under strong selection to favour dissimilar sets of pollinators to avoid exchanging pollen with other species~\citep{Levin1970,Bell2005,Mitchell2009}, while plants in other clades may be under strong pressure to continue interacting with a common set of partners.
+  Similarly, plants may experience disruptive selection on defences against herbivores if congeners tend to grow in the same places such that herbivore able to consume one species could easily spread to close relatives~\citep{Kursar2009,Yguel2014}.
+  On the other hand, unrelated plants might 
+  converge upon similar phenotypes which attract particularly 
+  efficient or abundant pollinators~\citep{Ollerton1996,Wilson2007,Ollerton2009,Ibanez2016}. 
   Likewise, unrelated plants may converge upon similar defences, leading them to share 
@@
   pairs of plants (henceforth ``niche overlap'') varies over 
-  phylogenetic distance and how this differs between plant families. 
+  phylogenetic distance. 
   Whereas previous 
@@
   relates to network structure.
-As different plant families may have experienced different degrees of coevolution, convergence, etc., we also complement analyses with entire networks with comparisons among plants in the same family within a network.
+As different plant families (which represent tractable clades for analysis) may have experienced different degrees of coevolution, convergence, etc., we also complement analyses with entire networks with comparisons among plants in the same family within a network.
   This novel perspective allows us to investigate the relationship between phylogenetic distance and partner overlap at different scales. 
@@
   phylogenetic distance differs systematically across plant families. 
-  previous studies.
+  This fine-grained approach gives more detailed information than previous studies.
 
-  This fine-grained approach gives more detailed information than 
-% \clearpage
+\clearpage
 
@@
 
-    We combined the numbers ofshared and unshared interaction partners
+    We combined the numbers of shared and unshared interaction partners
     into a Jaccard index ($J_{ij}$) describing 
@@
     weight to species sharing a large number of interaction partners as well as 
-    those sharing a large proportion (i.e., to emphasise pairs of generalists 
-    sharing most of their interaction partners over specialists sharing a single 
-    interaction partner).
+    those sharing a large proportion.
 Note that species sharing a large \emph{number} of interaction partners may not share a large \emph{proportion} of interaction partners if the number of interaction partners that are not shared is also large.
@@
     random intercepts and slopes per network. This expanded regression was fit
-    using the R~\citep{R} function `glmer from package 
+    using the R~\citep{R} function `glmer' from package 
     \emph{lme4}~\citep{lme4} and took the form
@@
     are the change in intercept and slope of the log odds of sharing an 
-    interaction partner, respectively relative to the baseline of 
+    interaction partner, respectively, relative to the baseline of 
     herbivory networks.
 
-    To demonstrate the power of defining $J_{ij}$ as a tuple of $M_{ij}$ and $U_{ij}$, we repeated the above analyses using a Jaccard index based only on the proportion of interaction partners that are shared (i.e., $J_{ij}$ = $M_{ij}$/[$M_{ij}+U_{ij}$]).
+    To demonstrate the power of defining $J_{ij}$ as a tuple of $M_{ij}$ and $U_{ij}$ rather than a single value, we repeated the above analyses using a Jaccard index based only on the proportion of interaction partners that are shared (i.e., $J_{ij}$ = $M_{ij}$/[$M_{ij}+U_{ij}$]).
 Note that while the proportion of shared interaction partners is the same in both cases, the tuple formulation gives more weight to plants with many interaction partners as these provide more information.
@@
 
-  \subsection*{Linking network-level trends and community composition}
+  \subsubsection*{Linking network-level trends and community composition}
 
@@
 
-  \subsection*{Calculating niche overlap within families}
+  \subsubsection*{Calculating niche overlap within families}
 
     Finally, we wished to compare the breakdown of overlap of interactions in
-    different plant families. To do this, we used the same definitions of 
+    different plant families.
+    Within-family genetic and trait diversity can be high due to adaptive radiations, heterogeneous selection, and other influences on different species.
+Plant families offer a reasonable balance between collecting enough species to identify meaningful trends and maintaining a tractable number of analyses.
+They are therefore the best taxonomic level to investigate phylogenetic conservation in more detail across our large dataset.
+     To do this, we used the same definitions of 
     overlap and phylogenetic distance as in the within-network analysis but 
@@
 In the \emph{Lauraceae}, (represented by four species in one pollination network) and the \emph{Sapindaceae} (represented by five species in one herbivory network and five species in two pollination networks), only one pair of species per network type shared any interaction partners while all other pairs did not share any interaction partners.
+
     By considering each family separately, we do risk obtaining some significant results purely by chance.
 The standard technique for addressing this type of multiple hypothesis testing, the Bonferroni correction, tends to be over-zealous and lead to a failure to reject the null hypothesis even when a large number of significant results before the correction supports the alternative hypothesis~\citep{Moran2003}.
-To account for multiple testing while also allowing the number of families showing significant trends to carry some weight, we use the correlated Bonferroni test introduced in~\citet{Drezler2016} (\emph{Supplemental Information 4}).
+To account for multiple testing while also allowing the number of families showing significant trends to carry some weight, we use the correlated Bonferroni test introduced in~\citet{Drezner2016} (\emph{Supplemental Information 4}).
 
-% \clearpage
+\clearpage
 
@@
     partners rather than to the quantitative strength of competition.
+
     As an illustration, a pair
@@
     Taking all families together, the probability of species in the same family sharing interaction partners was not significantly related to phylogenetic distance ($\beta_{distance}$=-6.48, $p$=0.087).
-Pollination networks did not show a significantly different trend from the herbivory networks ($\beta_{distance:pollination}$=1.73, $p$=0.681).
-More closely-related plants in pollination networks did, however, tend to share fewer interaction partners ($\beta_{pollination}$=-0.776, $p$=0.007), similar to our within-network results above.
+Pollination networks did not show a significantly different slope from the herbivory networks ($\beta_{distance:pollination}$=1.73, $p$=0.681).
+Plants in pollination networks did, however, have a lower intercept probability of sharing interaction partners ($\beta_{pollination}$=-0.776, $p$=0.007), similar to our within-network results above.
 
@@
 
-% \clearpage
+\clearpage
 
@@
   positive slope was extremely steep. This could indicate different 
-  rates of phenotypic drift or evolution in different families. 
+  rates of phenotypic drift or evolution in different families (or their interaction partners). 
   In other families, there was no significant relationship between phylogenetic
   distance and interaction partner overlap. In these cases, key traits affecting 
-  plant-insect interactions may not be strongly
-  conserved. Studies showing a stronger relationship between trait similarity
-  and shared interaction partners than phylogenetic similarity and shared
-  interaction partners suggest that traits may indeed be evolutionarily
-  labile~\citep{Junker2015,Ibanez2016,Endara2017}.
+  plant-insect interactions may be highly labile or plastic (environmentally determined).
+These possibilities are supported by several studies showing a stronger relationship between niche overlap and trait similarity than niche overlap and phylogenetic similarity~\citep{Junker2015,Ibanez2016,Endara2017}.
 
-  [[I don't like this paragraph. Refine?]]
-  Moreover, \emph{Polygonaceae} in pollination networks and 
-  \emph{Fabaceae} in herbivory networks showed the opposite 
+  While the majority of plant families in our dataset showed the expected trend, two (\emph{Polygonaceae} in pollination networks and \emph{Fabaceae} in herbivory networks) showed the opposite 
   pattern to what we expected. In these families, closely-related plants had 
@@
   animals have undergone an adaptive radiation to 
-  specialise on their most profitable partner~\citep{Janz2006}. Second, this pattern 
+  specialise on their most profitable partner~\citep{Janz2006}. 
+  Alternatively, it is possible that plants in these families have either undergone convergent evolution or that ancestral traits are commonly preserved.
+Either case would allow distantly-related \emph{Polygonaceae} and \emph{Fabaceae} to
+  interact with the same insects. 
+  Finally, this pattern 
   could be the result of ecological or environmental 
@@
   Indeed, animal pollination and seed dispersal have been shown to act
-  as filters for several plant clades~\citep{Mayfield2009}, while selection to avoid 
+  as filters for several plant clades~\citep{Mayfield2009}, and selection to avoid 
   competition and restriction on numbers of interaction partners may lead to
   more intimate or specialised interactions~\citep{Ponisio2017}. 
-  Reciprocal specialisation is particularly expected to occur in highly intimate interactions~\citep{Hembry2018}.
-Although pollination and leaf-chewing herbivory are both relatively low-intimacy interactions~\citep{Astegiano2017}, it is still possible that some plant families may tend to have more intimate interactions than others.
+  Reciprocal specialisation is particularly expected in highly intimate interactions~\citep{Hembry2018} rather than relatively low-intimacy pollination or leaf-chewing herbivory~\citep{Astegiano2017}.
+  Despite this, it is still possible that some plant families may tend to have more intimate interactions than others.
 This could result, for example, if a plant is pollinated by an insect which is also a herbivore in its larval stage~\citep{Hembry2018}.
-Testing this possibility is beyond the scope of the present manuscript, but could be interestting for future work.
-  Past selection to avoid competition is 
+  Whether or not intimacy plays a role in structuring these interactions, past selection to avoid competition is 
   consistent with the relatively high proportion of extreme specialists we
-  observed in the pollination networks, which likely contributes to the weak
+  observed in the pollination networks. As described above, these specialists likely weaken the relationship between phylogenetic distance and niche overlap. contribute to the weak
   relationships between phylogenetic distance and interaction partner overlap
-  in many networks. Finally, although we do not have information about plants'
-  traits in these networks, it is possible that convergence or a high degree of
-  ancestral trait conservation has occurred
-  allowing distantly-related \emph{Polygonaceae} and \emph{Fabaceae} to
-  interact with the same insects.
+  in many networks.
 
@@
   Alternatively, pollination and/or herbivory might exert large 
-  pressures that maintain the clade within a pollination or 
+  pressures that maintain the clade within a single pollination or 
   defensive syndrome. These syndromes are commonly believed to
@@
   and even environmental factors can influence traits such as 
-  flower colour, nectar abundance, and flowering phenology~citep{Strauss2006}. 
+  flower colour, nectar abundance, and flowering phenology~\citep{Strauss2006}. 
   These influences can act in the same or different directions~\citep{Strauss2006}.
@@
   asymmetric degree distributions: within a single system, most plants tend to interact
-  with many pollinators \emph{or} many herbivores but not both~\citep{Melian2009,Pockock2012,Astegiano2017}.
+  with many pollinators \emph{or} many herbivores but not both~\citep{Melian2009,Pocock2012,Astegiano2017}.
   These asymmetric interactions may also affect higher-order network structures such as
@@
 
-  Altogether, our study has revealed a wide variety of relationships 
-  between overlap of interaction partners and phylogenetic distance 
-  between plants in the same family. Regardless of the precise mechanisms
-  behind these relationships, it is clear
-  that the differences between families can affect the relationship
-  between overlap and phylogenetic distance at the network level.  
+  Altogether, our study has revealed general trends for conservation of interaction
+  partners between closely-related species, with some networks and plant 
+  families showing different trends. This overall similarity between closely-related
+  species has a potential application in ecological restoration. Close relatives could
+  be used interchangeably to restore missing interactions and fill ecosystem functions. 
+  This may be advantageous when a target plant is more difficult to establish than its
+  relatives, or if the restoration site is not large enough to support viable populations 
+  of many species. We should urge caution, however, since plants which support the
+  same pollinators may also support similar sets of herbivores. To avoid unwanted 
+  indirect effects, all interactions involving the target species should be considered.
   Although here we considered only the presence or absence of interactions,
@@
   recent work also suggests that the phylogenetic composition of a plant
-  community can affect the strength of 
+  community can also affect the strength of 
   interactions, and that the spatial arrangement of plants within a 
   community may be particularly important~\citep{Yguel2011,Castagneyrol2014}.
-  If so, then the study of how phylogenetic relationships between plants
-  affect their interactions with animals has only just begun.
-  % This result suggests
-  % that it is not just which plant families are present but the additional 
-  % relationships between the families that affects conservation of
-  % interactions at the network level and is consistent with previous
-  % work showing that the shape of phylogenetic tress, as well as the
-  % phylogenetic distances between species, can affect the strength
-  % of phylogenetic signal~\citep{Chamberlain2014a}.
+  These further nuances in the relationship between phylogenetic distance and 
+  niche overlap could also strongly affect the ability of closely-related species to
+  fill the same functions in restoration efforts. This is clearly a topic with many
+  unresolved questions, deserving of further study.
 
-% \clearpage
+\clearpage
 

### 2019-11-28 manuscript/phylogenetic_signal_manuscript.tex
trimming word count, final read-through before updating reply

@@
 
-% Main text: 6719 % Limit 6,500
+% Main text: 6541 % Limit 6,500 % Can subtract 25 for page numbers
 % Try to cut methods ... maybe then discussion.
@@
 %   \item Introduction: 1165 
-%   \item Materials and Methods: 2619 
+%   \item Materials and Methods: 2470
 %   \item Results: 960
-%   \item Discussion: 1892
+%   \item Discussion: 1863
 %   \item Acknowledgements: 83
@@
     countries (Sweden to New Zealand). The herbivory networks included a 
-    variety of types of herbivores but were dominated by leaf-chewing insects. To ensure that we were analysing interactions 
-    influenced by similar sets of traits across networks, we restricted 
-    our herbivory networks to leaf-chewing insects and excluded 
-    sap-sucking, leaf-mining, and galling insects as well as seed 
-    predators and xylophagous insects; all of these interactions involve 
-    different plant tissues and means of feeding than leaf chewing 
-    and so may be influenced by different plant and insect traits. 
-    Specifically, we removed any non-leaf chewing insects and any 
+    variety of types of herbivores but were dominated by leaf-chewing insects. 
+    Leaf-chewing and other types of herbivory might be affected by different
+    plant traits and therefore cannot be expected to show the same trends
+    with respect to phylogeny. We therefore restricted our networks to
+    leaf-chewing insects by removing any non-leaf chewing insects and any 
     plants which had no interaction partners after removing other types  
-    of herbivores. The adjusted networks range in size between 19 and 
+    of herbivores.
+    The adjusted networks range in size between 19 and 
     997 total species (mean=162, median=97) with between 8 and 132 
@@
     Supporting information 1} for details on the original sources of all 
-    networks. All networks were qualitative, recording the presence or 
-    absence of interactions rather than their strength.
+    networks. All networks were qualitative and did not include interaction strengths.
 
@@
     be assigned to an accepted taxonomic name (e.g., `Unknown Forb') were 
-    discarded, as were those with non-unique common names and no binomial 
-    name given (e.g., `Ragwort) or binomial names that could not be definitively 
+    discarded, as were those with binomial names that could not be definitively 
     linked to higher taxa (e.g., \emph{`Salpiglossus sp.'}). We were left with 
@@
     We then estimated phylogenetic distances between the remaining species. To accomplish 
-    this, we constructed a phylogenetic tree for our dataset based on a dated
-    `mega-tree' of angiosperms~\citep{Zanne2014}. Some species were not included
+    this, we constructed a phylogenetic tree based on a dated
+    `mega-tree' of angiosperms~\citep{Zanne2014}. Some species in our dataset were not included
     in the angiosperm mega-tree. For angiosperms,
@@
     This means that closely-related non-angiosperm species appear to have very long 
-    phylogenetic distances between them. For this reason, we excluded comparisons 
-    between pairs of non-angiosperms from our subsequent analyses. As only two networks (both 
+    phylogenetic distances between them. We therefore excluded comparisons 
+    between pairs of non-angiosperms from our analyses. As only two networks (both 
     herbivory networks) included more than one such species and non-angiosperms
@@
 
-  \subsection*{Calculating niche overlap within communities}
+  \subsection*{Calculating niche overlap}
 
-    We calculated niche overlap for each pair of plants $i$ and $j$ based on the number of shared interaction
-    partners ($M_{ij}$) and the number of interaction partners which are not
-    shared ($U_{ij}$). The number of unshared interaction 
+    We calculated niche overlap for each pair of plants $i$ and $j$ based on the number of shared and unshared interaction partners ($M_{ij}$, $U_{ij}$, respectively). 
+    The number of unshared interaction 
     partners gives valuable information about cases where, for example, 
     closely-related plants may have experienced disruptive selection, leading to weaker phylogenetic signal. 
-The number of shared and unshared interaction partners together indicates the amount of information  provided by each pair of plants: a pair of generalists which share most of their interaction partners gives a stronger indication of phylogenetic signal than a pair of specialists with one common interaction partner.
+    The sum $M_{ij} + U_{ij}$ indicates the amount of information  provided by each pair of plants: a pair of generalists which share most of their interaction partners gives a stronger indication of phylogenetic signal than a pair of extreme specialists with one common interaction partner.
 
-    We combined the numbers of shared and unshared interaction partners
-    into a Jaccard index ($J_{ij}$) describing 
-    the proportion of shared interactions. Importantly, we do this while 
-    preserving the amount of information provided by each pair of plants
-    (indicated by their numbers of interaction partners). $J_{ij}$ is usually defined as: 
-    %
-    \begin{equation}
-      J_{ij} = \frac{M_{ij}}{P_i+P_j-M_{ij}} ,
-    \end{equation}
-    %
-    where $M_{ij}$ is the set of \emph{mutual} (shared) interaction partners of 
-    species $i$ and $j$ and $P_i$ and $P_j$ are the sizes of the sets of interaction 
-    \emph{partners} for species $i$ and $j$ respectively. $J_{ij}$ can also be defined:
-    %
+    Together, $M_{ij}$ and $U_{ij}$ give a Jaccard index ($J_{ij}$) describing 
+    the proportion of shared interactions. $J_{ij}$ is defined: 
+    % %
+    % \begin{equation}
+    %   J_{ij} = \frac{M_{ij}}{P_i+P_j-M_{ij}} ,
+    % \end{equation}
+    % %
+    % where $M_{ij}$ is the set of \emph{mutual} (shared) interaction partners of 
+    % species $i$ and $j$ and $P_i$ and $P_j$ are the sizes of the sets of interaction 
+    % \emph{partners} for species $i$ and $j$ respectively. $J_{ij}$ can also be defined:
+    % %
     \begin{equation}
@@
     %
-    since $U_{ij}$ = $P_{i}$+$P_{j}$-2$M_{ij}$. This second definition more closely
-    relates to our methodology, which used the tuple ($M_{ij}$, $U_{ij}$) as the
-    dependent variable rather than the single value $J_{ij}$. Using this tuple form
-    allows us to give more 
-    weight to species sharing a large number of interaction partners as well as 
-    those sharing a large proportion.
+    where $M_{ij}$ is the set of \emph{mutual} (shared) interaction partners and $U_{ij}$ the set of unshared interaction partners for plants $i$ and $j$.
+    In our statistical analyses (see below), we used the tuple ($M_{ij}$, $U_{ij}$) as the
+    dependent variable rather than the single value $J_{ij}$. 
+    This allows us to preserve information about the amount of information provided by each pair of plants and weight the observations accordingly.
     Note that species sharing a large \emph{number} of interaction partners may not share a large \emph{proportion} of interaction partners if the number of interaction partners that are not shared is also large.
@@
 
-  \subsection*{Statistical analysis}
+  \subsection*{Testing conservation of niche overlap within networks}
 
     We modelled the relationship between niche overlap and phylogenetic 
-    distance using a logistic regression. We used both the numbers of shared 
+    distance using a logistic regression. We used the numbers of shared 
     ($M_{ij}$) and non-shared ($U_{ij}$) partners as dependent variables and 
@@
 
-      Note that pairs of plants are not always independent: the same plant will 
-      appear in many pairs. This violates the assumption of independence used 
+      Note that pairs of plants are not independent: the same plant will 
+      appear in many pairs, and interactions may be influenced by the 
+      overall structure of the community. This violates the assumptions used 
       when calculating the significance of logistic regressions within 
       the R~\citep{R} base package or the package \emph{lme4}~\citep{lme4}. To 
-      calculate significance of the regression coefficients we observed, it was 
+      fairly estimate the significance of our regressions, it was 
       therefore necessary to compare the observed relationships to those in a 
@@
       shuffled interactions among species while preserving row and column 
-      totals. That is, each species retained the same number of interaction 
+      totals. Each species retained the same number of interaction 
       partners as in the observed network but the exact set of partners (and 
@@
       permuted network and, again keeping the observed phylogenetic distances 
-      between plant species, repeated our analyses. We could then determine the 
+      between plant species, repeated our analyses. We then determined the 
       number of permuted networks which appear to have significant 
@@
       of these permuted networks (type I error). Type II error can be determined
-      from the distribution of p-values obtained when comparing the permuted 
+      from the distribution of $p$-values obtained when comparing the permuted 
       networks to permutations of the permuted networks. Although calculating 
       the exact type II error requires a specific alternative hypothesis, the 
-      uniform distribution of p-values we obtained after permuting the permuted 
+      uniform distribution of $p$-values we obtained after permuting the permuted 
       networks means that the type II error would increase linearly as the 
@@
 
-  \subsubsection*{Linking network-level trends and community composition}
+  \subsection*{Linking network-level trends and community composition}
 
@@
     varying relationships between phylogenetic distance and
-    pairwise niche overlap are due to the different distributions 
+    niche overlap are due to the different distributions 
     of families across networks. We defined the relationship between
@@
     a single network). We then related differences in this relationship
-    to differences in the composition of the plant community (defined as the number of species in each plant family present in each network) using a non-parametric permutational multi-variate 
+    to differences in the composition of the plant community 
+    using a non-parametric permutational multi-variate 
     analysis of variance (PERMANOVA;~\citealp{Anderson2001}).
-    As we did not wish to inflate the perceived similarity between
+    To avoid inflating the perceived similarity between
     pairs of networks which did not include many of the same families,
@@
     network could only be exchanged for that of another pollination
-    network. Stratifying the permutations in this way ensures that 
+    network. This stratification procedure ensures that 
     the null distribution used to calculate the $P$-value is not 
@@
 
-    % # This isn't mentioned anywhere else, likely a relic of an older plan.
-    % The PERMANOVA tests whether there is an association between
-    % community composition and network-level patterns but does not
-    % give any information on \emph{which} plant families have the
-    % greatest effects. To address this, we supplemented the 
-    % PERMANOVA with three constrained correspondence analyses (CCAs)
-    % which placed plant families along an axis representing the
-    % change in log odds of sharing an interaction partner.
-    % A correspondence 
-    % analysis (CA) is similar to other multivariate
-    % analyses such as principal components analysis in that it
-    % reduces multivariate data to a set of orthogonal axes. A
-    % subset of axes that explain the majority of variation in 
-    % the data can then be interpreted to elucidate trends that
-    % were difficult to interpret in the full multivariate space.
-    % A constrained correspondence analysis (CCA) creates an extra
-    % axis based on some constraint - in this case, the change in
-    % log odds of sharing an interaction partner.
-
   \subsubsection*{Calculating niche overlap within families}
 
-    Finally, we wished to compare the breakdown of overlap of interactions in
-    different plant families.
+    Finally, we compared the breakdown of niche overlap in different plant families.
     Within-family genetic and trait diversity can be high due to adaptive radiations, heterogeneous selection, and other influences on different species. 
@@
     They are therefore the best taxonomic level to investigate phylogenetic conservation in more detail across our large dataset.
-     To do this, we used the same definitions of 
+    To test whether different families show different conservation of interactions, 
+    we used the same definitions of 
     overlap and phylogenetic distance as in the within-network analysis but 
@@
 
-    For each plant family, within each network type, we then fit one of two 
+    For each plant family, within each network type, we fit one of two 
     similar sets of models. If family $f$ was found in several networks of 
@@
     using the R~\citep{R} function ``glmer'' from package
-     \emph{lme4}~\citep{lme4}. If family $f$ was found in only one network
-    (and therefore only one network type), we omitted the 
+     \emph{lme4}~\citep{lme4}. If family $f$ was found in only one network, we omitted the 
     network-level random effect and fit a logistic regression using the 
@@
     are never shared by more than one plant, a large proportion of specialists
-    would decrease interaction partner overlap.
+    would decrease niche overlap.
 
@@
   closely-related pairs of plants have a higher degree
-  of niche overlap. Using a novel method which considers
-  all pairs of plants together, 
+  of niche overlap. Taking all networks together, 
   the probability of two plants sharing the same animal 
-  interaction partners generally decreased with increasing 
+  interaction partners decreased with increasing 
   phylogenetic distance. Considering networks separately,
-  $\approx$56\%  of the pollination and $\approx$64\% of the 
-  herbivory networks exhibited the expected trend of decreasing 
+  $\approx$56\%  of pollination and $\approx$64\% of
+  herbivory networks showed the expected trend of decreasing 
   overlap with increasing distance. This variation between networks
@@
   networks. The lack of a significant relationship between
-  phylogenetic distance and interaction partner overlap in many
+  phylogenetic distance and niche overlap in many
   networks could be partly due to the large number of extreme
-  specialists, especially among the pollination networks.
+  specialist insects, especially in the pollination networks.
   These species interact with only one plant and
-  therefore weaken any signal of interaction partner overlap.
+  therefore weaken any signal of niche overlap.
   The herbivory networks did not contain as many obligate 
-  specialists, but we note that herbivores, as well as pollinators, often interact with only a few closely-related plants~\citep{Novotny2005,Brandle2006,Astegiano2017}.
+  specialists, but we note that herbivores, like pollinators, often interact with only a few closely-related plants~\citep{Novotny2005,Brandle2006,Astegiano2017}.
   These oligotrophs may affect overall phylogenetic signal in the same
-  way as the strict specialists: in both cases plants in different
-  families are unlikely to share interaction partners since the interaction partners tend to only visit plants within a particular genus.
-It is also likely that at least some of the apparent specialists in our dataset are actually rare species for which many interactions have not yet been observed~\citep{Bluthgen2006,Poisot2015}.
+  way as the strict specialists: in both cases plants that are not very closely related are unlikely to share interaction partners.
+Note that some of the apparent specialists in our dataset may actually be rare species involved in more interactions which have not yet been observed~\citep{Bluthgen2006,Poisot2015}.
 Without information on the sampling completeness of the networks in our dataset, it is difficult to estimate the size of this effect.
-In any case, the degree of phylogenetic conservation of interaction partners may change as we obtain more complete data on rare species.
+  It is possible, however, that we might observe stronger relationships between phylogenetic
+  distance and niche overlap with more complete data on rare species.
 
@@
   was not related to the slope of the relationship between phylogenetic
-  distance and interaction partner overlap. This suggests that 
+  distance and niche overlap. This suggests that 
   conservation of interaction partners among closely related plants
@@
   a network and the relationship between phylogenetic distance and
-  interaction partner overlap in either pollination or herbivory networks,
+  niche overlap in either pollination or herbivory networks,
   the greater importance of shallow phylogeny (as reported for leaf
@@
   were interested in overall structural properties of networks rather
-  than interaction partner overlap, this discrepancy may indicate that
+  than niche overlap, this discrepancy may indicate that
   different aspects of plant-insect interaction networks are influenced
@@
   In other families, there was no significant relationship between phylogenetic
-  distance and interaction partner overlap. In these cases, key traits affecting 
+  distance and niche overlap. In these cases, key traits affecting 
   plant-insect interactions may be highly labile or plastic (environmentally determined).
@@
   observed in the pollination networks. As described above, these specialists likely weaken the relationship between phylogenetic distance and niche overlap. contribute to the weak
-  relationships between phylogenetic distance and interaction partner overlap
+  relationships between phylogenetic distance and niche overlap
   in many networks.

### 2019-11-28 manuscript/phylogenetic_signal_manuscript.tex
trimming done, now to update the reply quotes and add line numbers.

@@
 
-% Main text: 6541 % Limit 6,500 % Can subtract 25 for page numbers
-% Try to cut methods ... maybe then discussion.
+% Main text: 6498 % Limit 6,500 % Can also subtract 25 for page numbers
 
@@
 %   \item Results: 960
-%   \item Discussion: 1863
+%   \item Discussion: 1820
 %   \item Acknowledgements: 83
@@
 
-  We found that the composition of plant families in a network
-  was not related to the slope of the relationship between phylogenetic
-  distance and niche overlap. This suggests that 
-  conservation of interaction partners among closely related plants
-  (e.g., congeners or members of the same subfamilies) is more
+  In our dataset, the slope of the relationship between phylogenetic
+  distance and niche overlap was not related to the composition of the
+  plant community in each network. Combined with the overall trend for
+  conservation of interaction partners above, this suggests that  
+  trends among closely-related plants
+  (e.g., congeners or members of the same subfamilies) are more
   important than phylogenetic signal from deeper within the phylogenetic
@@
   miners and gallers in~\citet{Volf2017}) may be a general 
-  feature of plant-insect interaction networks. This contrasts with
-  the findings of~\citet{Chamberlain2014}, who found that the \emph{shape}
-  of the phylogenetic tree rather than whether speciation was more or
-  less recent had a larger effect on network structure. As~\citet{Chamberlain2014}
+  feature of plant-insect interaction networks. This contrasts 
+  with~\citet{Chamberlain2014}, who found that the \emph{shape}
+  of the phylogenetic tree had a larger effect on network 
+  structure than the timing of speciation. As~\citet{Chamberlain2014}
   were interested in overall structural properties of networks rather
@@
   and the lack of influence of community composition on the strength of 
-  the relationship between phylogenetic distance and interaction partner
-  overlap could be partly due to the different trends within families. 
+  this signal could be partly due to different trends within families. 
   More than half of the plant families in each network type
@@
 
-  While the majority of plant families in our dataset showed the expected trend, two (\emph{Polygonaceae} in pollination networks and \emph{Fabaceae} in herbivory networks) showed the opposite 
-  pattern to what we expected. In these families, closely-related plants had 
+  While the majority of plant families in our dataset showed the 
+  expected trend, two (\emph{Polygonaceae} in pollination networks and \emph{Fabaceae} in herbivory networks) showed the opposite 
+  pattern. In these families, closely-related plants had 
   \emph{lower} overlap than more distantly-related pairs of plants. 
-  There are several possible reasons a plant family might
-  display this pattern. First, part of the family may have recently 
+  There are several possible explanations for this pattern. 
+  First, part of the family may have recently 
   undergone a period of rapid diversification with closely-related species 
-  developing novel phenotypes that attract different animal 
-  interaction partners~\citep{Linder2008,Breitkopf2015}. It is also possible that the
-  animals have undergone an adaptive radiation to 
+  developing novel phenotypes and attracting different  
+  interaction partners~\citep{Linder2008,Breitkopf2015}. Likewise, the
+  animals may have undergone an adaptive radiation to 
   specialise on their most profitable partner~\citep{Janz2006}. 
-  Alternatively, it is possible that plants in these families have either undergone convergent evolution or that ancestral traits are commonly preserved.
-Either case would allow distantly-related \emph{Polygonaceae} and \emph{Fabaceae} to
-  interact with the same insects. 
-  Finally, this pattern 
-  could be the result of ecological or environmental 
+  Alternatively, plants in these families could have undergone convergent evolution or ancestral traits could be strongly preserved. Either case would allow 
+  distantly-related \emph{Polygonaceae} and \emph{Fabaceae} to interact with the same insects. 
+  Finally, this pattern could be the result of ecological or environmental 
   filtering~\citep{Ackerly2003,Mayfield2009}. 
-  Closely-related species which have high degrees of overlap in their interaction 
-  partners might compete too severely to coexist. This is especially likely
+  Closely-related species with strong niche overlap might compete too severely to coexist. 
+  This is especially likely
   for plants sharing pollinators, where the loss of pollen to related species 
@@
   Indeed, animal pollination and seed dispersal have been shown to act
-  as filters for several plant clades~\citep{Mayfield2009}, and selection to avoid 
-  competition and restriction on numbers of interaction partners may lead to
+  as filters for several plant clades~\citep{Mayfield2009}. Selection to avoid 
+  competition and restrict numbers of interaction partners may lead to
   more intimate or specialised interactions~\citep{Ponisio2017}. 
-  Reciprocal specialisation is particularly expected in highly intimate interactions~\citep{Hembry2018} rather than relatively low-intimacy pollination or leaf-chewing herbivory~\citep{Astegiano2017}.
+  Reciprocal specialisation is particularly expected in highly intimate interactions~\citep{Hembry2018} rather than the relatively low-intimacy pollination or leaf-chewing herbivory we consider here~\citep{Astegiano2017}.
   Despite this, it is still possible that some plant families may tend to have more intimate interactions than others.
@@
   consistent with the relatively high proportion of extreme specialists we
-  observed in the pollination networks. As described above, these specialists likely weaken the relationship between phylogenetic distance and niche overlap. contribute to the weak
-  relationships between phylogenetic distance and niche overlap
-  in many networks.
+  observed in the pollination networks. As described above, these specialists likely weaken the relationship between phylogenetic distance and niche overlap.
 
@@
   plants did not vary linearly over phylogenetic distance. Once again, there 
-  are several possible drivers for this trend (or lack thereof). These plants might 
+  are several possible explanations for this result. These plants might 
   be highly specialised on different interaction partners and therefore

### 2019-11-28 manuscript/reply_to_referees_2.tex
spellchecked. Still need to refine reply

@@
 	We are pleased to submit a revised version of our manuscript, NPH-MS-2019-30803.
-In response to a suggestion from Referee 3, we have retitled it "".
+In response to a suggestion from Referee 3, we have re-titled it "".
 We have also taken care to revise our methods section in response to the many helpful suggestions from Referee 4, and hope that our approach is now clearer.
@@
 	Given the difference of opinion between Referees 1, 3, and 4 and Referee 2, we have prioritised adjusting the manuscript according to the majority view.
-We must also admit to having some difficulty parsing a number of Referee 2's comments in order to find what is being asked/suggestions.
-Nevertheless, we appreciate their time and effort in offering such extensive feedback.
-We have taken care to address each of Referee 2's comments and, where possible, have used them to improve the manuscript.
+We must also admit to having some difficulty parsing a number of Referee 2's comments in order to find what is being asked.
+These difficulties mean that we may not have followed as many of Referee 2's suggestions as we have for the other Referees.
+Nevertheless, we do appreciate their time and effort in offering such extensive feedback and have taken care to address each of Referee 2's comments in the hope of clarifying our perspective.
 
@@
 
-		Lines XX-XX:
-
-		\begin{quotation}
-
-			Finally, we wished to compare the breakdown of overlap of interactions in
-		    different plant families.
+		Lines 252-257:
+
+		\begin{quotation}
+
+			Finally, we compared the breakdown of niche overlap in different plant families.
 		    Within-family genetic and trait diversity can be high due to adaptive radiations, heterogeneous selection, and other influences on different species. 
@@
 
-		Lines XX-XX:
+		Lines 11-14:
 
@@
 
-		Lines XX-XX:
+		Lines 29-37:
 
@@
 In antagonistic networks, however, actively-foraging consumers tend to show less phylogenetic signal than their prey~\citep{Ives2006,Cagnolo2011,Naisbit2011,Fontaine2015}.
-In part, this may be related to different degrees of interaction intimacy (dependence of one predator on another), which appears to contribute to network structure in mutualistic, but not antagonistic, networks~\citep{Guimaraes2007,Ponisio2017}.
+In part, this may be related to different degrees of interaction intimacy (dependence of one partner on another), which appears to contribute to network structure in mutualistic, but not antagonistic, networks~\citep{Guimaraes2007,Ponisio2017}.
 
@@
 
-	10. Criticisism of methodological changes required by previous reviewers [[done]]
+	10. Criticism of methodological changes required by previous reviewers [[done]]
 
@@
 We chose this methodology for exactly the reasons the Referee suggests, to give more weight to generalists sharing many interaction partners.
-This is stated in lines XX-XX (quoted below).
-We are glad that the Referee agrees with our choice in methdology.
-
-		\begin{quotation}
-
-			We wished to give more 
-		    weight to species sharing a large number of interaction partners as well as 
-		    those sharing a large proportion (i.e., to emphasise pairs of generalists 
-		    sharing most of their interaction partners over specialists sharing a single 
-		    interaction partner).
-Note that species sharing a large \emph{number} of interaction partners may not share a large \emph{proportion} of interaction partners if the number of interaction partners that are not shared is also large.
+This is stated in lines 138-141 and lines 148-154 (quoted below).
+Note that we have revised these lines somewhat in response to a suggestion from Referee 4, so they do differ somewhat from the previous version.
+We are glad that the Referee agrees with our choice in methodology.
+
+		\begin{quotation}
+
+			Together, $M_{ij}$ and $U_{ij}$ give a Jaccard index ($J_{ij}$) describing 
+			the proportion of shared interactions. $J_{ij}$ is defined:
+
+			\begin{equation}
+			J_{ij} = \frac{M_{ij}}{U_{ij}+M_{ij}} ,
+			\end{equation}
+			%
+			where $M_{ij}$ is the set of \emph{mutual} (shared) interaction partners and $U_{ij}$ the set of unshared interaction partners for plants $i$ and $j$.
+
+		\end{quotation}
+
+		\smallskip
+
+		\begin{quotation}
+
+			We modelled the relationship between niche overlap and phylogenetic 
+			distance using a logistic regression. We used the numbers of shared 
+			($M_{ij}$) and non-shared ($U_{ij}$) partners as dependent variables and 
+			centred, scaled phylogenetic distance as the independent variable. This 
+			approach is conceptually similar to modelling successes and failures in a 
+			binomial-distributed process. Accordingly, we assumed a binomially-distributed error structure and used a logit link function to model the dissimilarity in interaction partners 
+			$J_{ij}$ of plants $i$ and $j$.
 
@@
 
-		Lines XX-XX:
+		Lines 78-86:
 
@@
 			pairs of plants (henceforth ``niche overlap'') varies over 
-		  phylogenetic distance and how this differs between plant families. 
+			phylogenetic distance. 
 			Whereas previous 
@@
 			relates to network structure.
-As different plant families may have experienced different degrees of coevolution, convergence, etc., we also complement analyses with entire networks with comparisons among plants in the same family within a network.
+As different plant families (which represent tractable clades for analysis) may have experienced different degrees of coevolution, convergence, etc., we also complement analyses with entire networks with comparisons among plants in the same family within a network.
 			This novel perspective allows us to investigate the relationship between phylogenetic distance and partner overlap at different scales.
@@
 
-		Lines XX-XX:
+		Lines 224-233:
 
@@
 			varying relationships between phylogenetic distance and
-		    pairwise niche overlap are due to the different distributions 
+			niche overlap are due to the different distributions 
 			of families across networks. We defined the relationship between
@@
 			a single network). We then related differences in this relationship
-		    to differences in the composition of the plant community (defined as the number of species in each plant family present in each network) using a non-parametric permutational multi-variate 
+			to differences in the composition of the plant community 
+			using a non-parametric permutational multi-variate 
 			analysis of variance (PERMANOVA;~\citealp{Anderson2001}).
@@
 
-		Lines XX-XX:
-
-		\begin{quotation}
-
-		In pollination networks, overlap decreased significantly with increasing phylogenetic distance in 12 of the 48 well-represented families
+		Lines 355-356:
+
+		\begin{quotation}
+
+		In pollination networks, overlap decreased significantly with increasing phylogenetic distance in 14 of the 48 well-represented families (Table 1; Fig. 3).
 
@@
 
-		\textbf{R:} We do include ideas about evolution and coevolution inour discussion.
+		\textbf{R:} We do include ideas about evolution and coevolution in our discussion.
 We completely agree that, together with ecological processes and environmental filtering, evolution and coevolution are very important in structuring networks.
@@
 
-		Specialists, for example, could have co-evolved with particular interaction partners.
-They could also, however, be able to interact with more species which simply do not appear in the study site due to competition, unsuitable soil conditions, etc.
-As Referee 4 notes, specialists may also simply be species which were sampled more rarely.
-That is, we may be missing interactions involving these species which actually do occur.
-Please note that the proportion of specialists is a potential explanation for the results we observed and not a key result in itself.
-As such, we feel that spending a great deal of time trying to explain this trend would distract readers from the main message of our paper.
-
 		Some examples of evolutionary ideas in the discussion:
 
-		Lines XX-XX:
+		Lines 413-418:
 
@@
 			plants~\citep{Schemske1999,Gilbert2015,Ponisio2017}. The degree of 
-			  heritability of key traits may, however, differ between families. In
-			  some families, such as \emph{Asteraceae} in pollination networks, 
-			  the positive slope of this relationship was very shallow while in 
-			  others, such as \emph{Melastomataceae} in herbivory networks, the 
-			  positive slope was extremely steep. This could indicate different 
-			  rates of phenotypic drift or evolution in different families. 
+			heritability of key traits may, however, differ between families.
+
+		\end{quotation}
+
+		Lines 420-427:
+
+		\begin{quotation}
+
+			This could indicate different 
+			rates of phenotypic drift or evolution in different families (or their interaction partners). 
 			In other families, there was no significant relationship between phylogenetic
-			  distance and interaction partner overlap. In these cases, key traits affecting 
-			  plant-insect interactions may not be strongly
-			  conserved. Studies showing a stronger relationship between trait similarity
-			  and shared interaction partners than phylogenetic similarity and shared
-			  interaction partners suggest that traits may indeed be evolutionarily
-			  labile~\citep{Junker2015,Ibanez2016,Endara2017}.
-
-		\end{quotation}
-
-		Lines XX-XX:
-
-		\begin{quotation}
-
-			In other plant families
+			distance and niche overlap. In these cases, key traits affecting 
+			plant-insect interactions may be highly labile or plastic (environmentally determined).
+These possibilities are supported by several studies showing a stronger relationship between niche overlap and trait similarity than niche overlap and phylogenetic similarity~\citep{Junker2015,Ibanez2016,Endara2017}.
+
+		\end{quotation}
+
+		Lines 432-437:
+
+		\begin{quotation}
+
+			First, part of the family may have recently 
+			undergone a period of rapid diversification with closely-related species 
+			developing novel phenotypes and attracting different  
+			interaction partners~\citep{Linder2008,Breitkopf2015}. Likewise, the
+			animals may have undergone an adaptive radiation to 
+			specialise on their most profitable partner~\citep{Janz2006}. 
+			Alternatively, plants in these families could have undergone convergent evolution or ancestral traits could be strongly preserved.
+
+		\end{quotation}
+
+		Lines 444-446:
+
+		\begin{quotation}
+
+			Selection to avoid 
+			competition and restrict numbers of interaction partners may lead to
+			more intimate or specialised interactions~\citep{Ponisio2017}.
+
+		\end{quotation}
+
+		Lines 458-466:
+
+		\begin{quotation}
+
+			These plants might 
+			be highly specialised on different interaction partners and therefore
+			have low overlap at all levels of relatedness. In other plant families
 			with more moderate levels of specialisation, it is possible 
@@
 
-		See also lines XX-XX, where we discuss constraints on traits. We have lightly revised these lines to reference evolution explicitly.
-
-		\begin{quotation}
-
-		 This may indicate that one type of interaction
-		  places greater evolutionary constraints upon these families than the other, 
-		  similar to the expectation that greater constraints upon consumers 
-		  than upon their resources explains the asymmetry in conservation  
-		  of interaction partners~\citep{Fontaine2015}. Plants
-		  may not be able to respond to selection on both types of interaction
-		  simultaneously because traits affecting pollination can also affect herbivory, and vice
-		  versa~\citep{Strauss1997,Strauss2002,Adler2004,Adler2006,Theis2006}.
+		Lines 476-482:
+
+		\begin{quotation}
+
+			This could be because of conflicting selection from pollinators and herbivores,
+			with one type of selection placing greater constraints on plant traits than the other.
+			Multiple types of interactions (e.g., pollination, herbivory, nectar robbing) 
+			and even environmental factors can influence traits such as 
+			flower colour, nectar abundance, and flowering phenology~\citep{Strauss2006}. 
+			These influences can act in the same or different directions~\citep{Strauss2006}.
+
 		\end{quotation}
@@
 		If the Referee is contending that, because of the multiple herbivore types in~\citet{Novotny2005}, we cannot claim that the herbivores in our dataset are oligotrophs, we can respond with further details.
-The mean number of plants consumed per herbivore ranged between 1.64 and 14.9 across networks, with a mean of 6.36, and the median ranged bewteen 1 and 11.5 (mean 4.68).
+The mean number of plants consumed per herbivore ranged between 1.64 and 14.9 across networks, with a mean of 6.36, and the median ranged between 1 and 11.5 (mean 4.68).
 These measures indicate that many herbivores in our networks do, in fact, consume only a few of the plants available to them.
@@
 We note that across seven other reviews, no other Referee has commented on this.
-Based on this lackof objection and similar language throughout the literature, we have opted not to change this line.
+Based on this lack of objection and similar language throughout the literature, we have opted not to change this line.
 
@@
 We note that~\citet{Hembry2018} only study a very small and high-intimacy system (a single genus of brood pollinating moths and their single genus of host plants).
-Their results will therefore not necessarily generlize to the larger, more diverse networks we consider.
+Their results will therefore not necessarily generalize to the larger, more diverse networks we consider.
 Indeed, had they considered a broader sample of plants and seed predators or herbivores from the same islands, they easily could have found less reciprocal specialisation.
@@
 
-		Given all of the above, it is hard to see how the interaction intimacy hypothesis relates to these lines (which are about whether the number of species in dfferent plant families is related to the strength of phylogenetic signal).
+		Given all of the above, it is hard to see how the interaction intimacy hypothesis relates to these lines (which are about whether the number of species in different plant families is related to the strength of phylogenetic signal).
 Instead, we feel that a discussion of the possible effects of intimacy is more relevant later on, where we discuss possible reasons why some families may show different trends.
@@
 We had mentioned this possibility briefly in lines 406-407 of the previous version, but are happy to expand upon this point somewhat.
-This section (lines XX-XX) now reads:
+This section (lines 443-454) now reads:
 
@@
 			Indeed, animal pollination and seed dispersal have been shown to act
-		  	as filters for several plant clades~\citep{Mayfield2009}, while selection to avoid 
-		  competition and restriction on numbers of interaction partners may lead to
+			as filters for several plant clades~\citep{Mayfield2009}. Selection to avoid 
+			competition and restrict numbers of interaction partners may lead to
 			more intimate or specialised interactions~\citep{Ponisio2017}. 
-		  Reciprocal specialisation is particularly expected to occur in highly intimate interactions~\citep{Hembry2018}.
-Although pollination and leaf-chewing herbivory are both relatively low-intimacy interactions, it is still possible that some plant families may tend to have more intimate interactions than others.
+			Reciprocal specialisation is particularly expected in highly intimate interactions~\citep{Hembry2018} rather than the relatively low-intimacy pollination or leaf-chewing herbivory we consider here~\citep{Astegiano2017}.
+			Despite this, it is still possible that some plant families may tend to have more intimate interactions than others.
 This could result, for example, if a plant is pollinated by an insect which is also a herbivore in its larval stage~\citep{Hembry2018}.
-Testing this possibility is beyond the scope of the present manuscript, but could be interestting for future work.
+			Whether or not intimacy plays a role in structuring these interactions, past selection to avoid competition is 
+			consistent with the relatively high proportion of extreme specialists we
+			observed in the pollination networks.
 
@@
 
-	Lines XX-XX:
+	Lines 495-511:
 
@@
 
-		Lines XX-XX (methods):
-
-		\begin{quotation}
-
-			All networks were qualitative, recording the presence or 
-		    absence of interactions rather than their strength.
-
-		\end{quotation}
-
-		Lines XX-XX (results):
+		Lines 105-106 (methods):
+
+		\begin{quotation}
+
+			All networks were qualitative and did not include interaction strengths.
+
+		\end{quotation}
+
+		Lines 294-296 (results):
 
@@
 
-    	Lines XX-XX (discussion):
+    	Lines 504-505 (discussion):
 
@@
 		  Although here we considered only the presence or absence of interactions,
-		  (i.e., qualitative networks)
+		  (i.e., qualitative networks) ...
 
@@
 
-		\textbf{R:} We appreciate that this desceription could be unclear, and have revised this line as suggested. It now reads:
-
-		Lines XX-XX:
+		\textbf{R:} We appreciate that this description could be unclear, and have revised this line as suggested. It now reads:
+
+		Lines 326-328:
 
@@
 		\begin{refquote}
-			L322 – how was this result obtained if insect phylogenies were not caclculated? Do you mean “more closely-related plants in pollinator networks”?
+			L322 – how was this result obtained if insect phylogenies were not calculated? Do you mean “more closely-related plants in pollinator networks”?
 		\end{refquote}
@@
 The number of shared variables is indeed the key variable, but the number of unshared interactions is also important as it indicates how extraordinary a particular number of shared interactions is.
-The binomial process incorportates both quantities; converting the numbers of shared and unshared interactions to a proportion and weighting the observations by the total number of interactions.
-We thank the Referee for pointing out text in the introduction which clarifiedthe purpose of including unshared interactions.
+The binomial process incorporates both quantities; converting the numbers of shared and unshared interactions to a proportion and weighting the observations by the total number of interactions.
+We thank the Referee for pointing out text in the introduction which clarified the purpose of including unshared interactions.
 We have expanded the beginning of this section to explain the logic of our modelling approach in more detail.
 
-		lines XX-XX:
-
-		\begin{quotation}
-
-		    We calculated niche overlap for each pair of plants $i$ and $j$ based on the number of shared interaction
-		    partners ($M_{ij}$) and the number of interaction partners which are not
-		    shared ($U_{ij}$). The number of unshared interaction 
+		lines 130-141:
+
+		\begin{quotation}
+
+			We calculated niche overlap for each pair of plants $i$ and $j$ based on the number of shared and unshared interaction partners ($M_{ij}$, $U_{ij}$, respectively). 
+			The number of unshared interaction 
 			partners gives valuable information about cases where, for example, 
 			closely-related plants may have experienced disruptive selection, leading to weaker phylogenetic signal. 
-The number of shared and unshared interaction partners together indicates the amount of information  provided by each pair of plants: a pair of generalists which share most of their interaction partners gives a stronger indication of phylogenetic signal than a pair of specialists with one common interaction partner.
+			The sum $M_{ij} + U_{ij}$ indicates the amount of information  provided by each pair of plants: a pair of generalists which share most of their interaction partners gives a stronger indication of phylogenetic signal than a pair of extreme specialists with one common interaction partner.
+
+			Together, $M_{ij}$ and $U_{ij}$ give a Jaccard index ($J_{ij}$) describing 
+			the proportion of shared interactions. $J_{ij}$ is defined: 
+			\begin{equation}
+			J_{ij} = \frac{M_{ij}}{U_{ij}+M_{ij}} ,
+			\end{equation}
+			where $M_{ij}$ is the set of \emph{mutual} (shared) interaction partners and $U_{ij}$ the set of unshared interaction partners for plants $i$ and $j$.
 
@@
 
-			Lines XX-XX:
-
-			\begin{quotation}
-
-				To demonstrate the power of defining $\omega_{ij}$ as a tuple of $M_{ij}$ and $U_{ij}$, we repeated the above analyses using a Jaccard index based only on the proportion of interaction partners that are shared (i.e., $\omega_{ij}$ = $M_{ij}$/[$M_{ij}+U_{ij}$]).
+			Lines 173-181:
+
+			\begin{quotation}
+
+				To demonstrate the power of defining $J_{ij}$ as a tuple of $M_{ij}$ and $U_{ij}$ rather than a single value, we repeated the above analyses using a Jaccard index based only on the proportion of interaction partners that are shared (i.e., $J_{ij}$ = $M_{ij}$/[$M_{ij}+U_{ij}$]).
 Note that while the proportion of shared interaction partners is the same in both cases, the tuple formulation gives more weight to plants with many interaction partners as these provide more information.
 When comparing the two approaches
-			    we observed similar trends but, notably, the tuple definition of $\omega_{ij}$ had greater power to detect weak relationships (\emph{Supporting information 2}).
-We therefore show only the results when defining $\omega_{ij}$ as a tuple in the main text.
+				we observed similar trends but, notably, the tuple definition of $J_{ij}$ had greater power to detect weak relationships (\emph{Supporting information 2}).
+We therefore show only the results when defining $J_{ij}$ as a tuple in the main text.
 
@@
 
-		Lines XX-XX:
-
-		\begin{quotation}
+		Lines 209-212:
+
+		\begin{quotation}
+
 			This permutation approach also allows us to estimate type I and type II 
@@
 Because the permuted networks should not demonstrate any particular relationship between phylogenetic distance and partner overlap, these slopes should be similar to those obtained after permuting these networks a second time.
+
 		\end{quotation}
@@
 
-		Lines XX-XX:
+		Lines 278-285:
 
@@
 The standard technique for addressing this type of multiple hypothesis testing, the Bonferroni correction, tends to be over-zealous and lead to a failure to reject the null hypothesis even when a large number of significant results before the correction supports the alternative hypothesis~\citep{Moran2003}.
-To account for multiple testing while also allowing the number of families showing significant trends to carry some weight, we use the correlated Bonferroni test introduced in~\citet{Drezler2016} (\emph{Supplemental Information 4}).
-
-		\end{quotation}
-
-		Lines XX-XX now read:
-
-		\begin{quotation}
-			 In pollination networks, overlap decreased significantly with increasing phylogenetic distance in 14 of the 48 well-represented families (Table~\ref{family_slopes_pp}; Fig.~\ref{within_family_regression}).
+To account for multiple testing while also allowing the number of families showing significant trends to carry some weight, we use the correlated Bonferroni test introduced in~\citet{Drezner2016} (\emph{Supplemental Information 4}).
+
+		\end{quotation}
+
+		Lines 355-360 now read:
+
+		\begin{quotation}
+			 In pollination networks, overlap decreased significantly with increasing phylogenetic distance in 14 of the 48 well-represented families (Table 1; Fig.
+3).
 If we apply the correlated Bonferroni correction to account for multiple testing~\citep{Drezner2016}, all of these slopes remain significant (\emph{Supplemental Information 4}).
@@
 
-		Lines XX-XX:
-
-		\begin{quotation}
-
-			It is also likely that at least some of the apparent specialists in our dataset are actually rare species for which many interactions have not yet been observed~\citep{Bluthgen2006,Poisot2015}.
+		Lines 386-391:
+
+		\begin{quotation}
+
+			Note that some of the apparent specialists in our dataset may actually be rare species involved in more interactions which have not yet been observed~\citep{Bluthgen2006,Poisot2015}.
 Without information on the sampling completeness of the networks in our dataset, it is difficult to estimate the size of this effect.
-In any case, the degree of phylogenetic conservation of interaction partners may change as we obtain more complete data on rare species.
+			It is possible, however, that we might observe stronger relationships between phylogenetic
+			distance and niche overlap with more complete data on rare species.
 
@@
 			and even environmental factors can influence traits such as 
-			flower colour, nectar abundance, and flowering phenology~citep{Strauss2006}. 
+			flower colour, nectar abundance, and flowering phenology~\citep{Strauss2006}. 
 			These influences can act in the same or different directions~\citep{Strauss2006}.
@@
 			asymmetric degree distributions: within a single system, most plants tend to interact
-			with many pollinators \emph{or} many herbivores but not both~\citep{Melian2009,Pockock2012,Astegiano2017}.
+			with many pollinators \emph{or} many herbivores but not both~\citep{Melian2009,Pocock2012,Astegiano2017}.
 			These asymmetric interactions may also affect higher-order network structures such as
@@
 
+			\begin{itemize}
 			\item We quantify overlap of interaction partners for all pairs of plants in 59 pollination and 11 herbivory networks based on the numbers of shared and unshared interaction partners (thereby capturing both proportional and absolute overlap).
 We test 1) for relationships between phylogenetic distance and partner overlap within each network, 2) whether these relationships varied with the composition of the plant community, and 3) whether well-represented plant families showed different relationships.
+		\end{itemize}
 
@@
 		\textbf{R:} We do not believe that the original formulation was incorrect, but agree that it was inelegant. We have revised this line to read:
-		\begin{quotation}
-			Plant traits are also likely to determine \emph{which} specific pollinators and herbivores interact with a particular plant.
-	  	\end{quotation}
+
+		\begin{quotation}
+			Plant traits are also likely to determine \emph{which} specific pollinators 
+			  and herbivores interact with a particular plant.
+	  	\end{quotation}
+
 	  	We hope that this revised version reads better.
@@
 
-		\textbf{R:} We had intended these citations to showcase a selection of researchers addressing different aspectsof phylogenetic signal, but appreciate how including them all together could be confusing.
+		\textbf{R:} We had intended these citations to showcase a selection of researchers addressing different aspects of phylogenetic signal, but appreciate how including them all together could be confusing.
 We have removed the large list so as not to distract from the more specific citations in subsequent lines.
@@
 
-		Lines XX-XX:
+		Lines 79-86:
 
@@
 			order to obtain a more detailed picture of how plant phylogeny
-		  relates to network structure. This novel perspective allows us to investigate the relationship between phylogenetic distance and partner overlap at different scales.
+			relates to network structure.
+As different plant families (which represent tractable clades for analysis) may have experienced different degrees of coevolution, convergence, etc., we also complement analyses with entire networks with comparisons among plants in the same family within a network.
+			This novel perspective allows us to investigate the relationship between phylogenetic distance and partner overlap at different scales.
 
@@
 We have also changed all $\omega_{ij}$ to $J_{ij}$ for simplicity.
-This paragraph now reads:
-
-		\begin{quotation}
-		    We calculated niche overlap for each pair of plants $i$ and $j$ by 
-		    combining the number of shared interaction
-		    partners ($M_{ij}$) and the number of interaction partners which are not
-		    shared ($U_{ij}$) into a Jaccard index ($J_{ij}$) describing 
-		    the proportion of shared interactions. Importantly, we do this while 
-		    preserving the amount of information provided by each pair of plants
-		    (indicated by their numbers of interaction partners). $J_{ij}$ is usually defined as: 
-		    %
-		    \begin{equation}
-		      J_{ij} = \frac{M_{ij}}{P_i+P_j-M_{ij}} ,
-		    \end{equation}
-		    %
-		    where $M_{ij}$ is the set of \emph{mutual} (shared) interaction partners of 
-		    species $i$ and $j$ and $P_i$ and $P_j$ are the sizes of the sets of interaction 
-		    \emph{partners} for species $i$ and $j$ respectively. $J_{ij}$ can also be defined:
-		    %
+This paragraph (lines 130-146) now reads:
+
+		\begin{quotation}
+
+			We calculated niche overlap for each pair of plants $i$ and $j$ based on the number of shared and unshared interaction partners ($M_{ij}$, $U_{ij}$, respectively). 
+			The number of unshared interaction 
+			partners gives valuable information about cases where, for example, 
+			closely-related plants may have experienced disruptive selection, leading to weaker phylogenetic signal. 
+			The sum $M_{ij} + U_{ij}$ indicates the amount of information  provided by each pair of plants: a pair of generalists which share most of their interaction partners gives a stronger indication of phylogenetic signal than a pair of extreme specialists with one common interaction partner.
+
+			Together, $M_{ij}$ and $U_{ij}$ give a Jaccard index ($J_{ij}$) describing 
+			the proportion of shared interactions. $J_{ij}$ is defined: 
 			\begin{equation}
@@
 			\end{equation}
-		    %
-		    since $U_{ij}$ = $P_{i}$+$P_{j}$-2$M_{ij}$. This second definition more closely
-		    relates to our methodology, which used the tuple ($M_{ij}$, $U_{ij}$) as the
-		    dependent variable rather than the single value $J_{ij}$. Using this tuple form
-		    allows us to give more 
-		    weight to species sharing a large number of interaction partners as well as 
-		    those sharing a large proportion (i.e., to emphasise pairs of generalists 
-		    sharing most of their interaction partners over specialists sharing a single 
-		    interaction partner).
+			where $M_{ij}$ is the set of \emph{mutual} (shared) interaction partners and $U_{ij}$ the set of unshared interaction partners for plants $i$ and $j$.
+			In our statistical analyses (see below), we used the tuple ($M_{ij}$, $U_{ij}$) as the
+			dependent variable rather than the single value $J_{ij}$. 
+			This allows us to preserve information about the amount of information provided by each pair of plants and weight the observations accordingly.
 			Note that species sharing a large \emph{number} of interaction partners may not share a large \emph{proportion} of interaction partners if the number of interaction partners that are not shared is also large.
-% Added because Josh got confused about the distinction.
+
 		    \end{quotation}
@@
 
-		Lines XX-XX:
-		\begin{quotation}
-			More closely-related plants in pollination networks did, however, tend to share fewer interaction partners ($\beta_{pollination}$=-0.776, $p$=0.007), similar to our within-network results above.
+		Lines 350-352:
+
+		\begin{quotation}
+			Plants in pollination networks did, however, have a lower intercept probability of sharing interaction partners ($\beta_{pollination}$=-0.776, $p$=0.007), similar to our within-network results above.
 		\end{quotation}
@@
 
-	17. A confusing attempt at subtelty [[done]]
+	17. A confusing attempt at subtlety [[done]]
 

### 2019-11-28 manuscript/phylogenetic_signal_manuscript.tex
spellchecked. Still need to refine reply

@@
 \section*{Introduction}
-% \linenumbers
+\linenumbers
 
@@
 In antagonistic networks, however, actively-foraging consumers tend to show less phylogenetic signal than their prey~\citep{Ives2006,Cagnolo2011,Naisbit2011,Fontaine2015}.
-In part, this may be related to different degrees of interaction intimacy (dependence of one predator on another), which appears to contribute to network structure in mutualistic, but not antagonistic, networks~\citep{Guimaraes2007,Ponisio2017}.
+In part, this may be related to different degrees of interaction intimacy (dependence of one partner on another), which appears to contribute to network structure in mutualistic, but not antagonistic, networks~\citep{Guimaraes2007,Ponisio2017}.
 Thus, it is not straightforward to assume that interactions will always be similar among related species.
@@
   There may also be trade-offs between chemical and physical defences, or defences at different life stages, that weaken the overall heritability of plants' sets of herbivores~\citep{Karinho2014,Endara2017}.
-  A plant's set of interaction partners therefore reflects a mixture of different envionmental effects and different selection pressures, as well as shared phylogenetic history.
+  A plant's set of interaction partners therefore reflects a mixture of different environmental effects and different selection pressures, as well as shared phylogenetic history.
   If these factors affect closely-related plants differently, then closely-related species may not have more similar interaction partners than distantly-related species.
@@
     \end{center}
-     \caption{The slopes of the mixed-effect logistic regression of pairwise niche overlap against phylogenetic distance (representing the change in log odds of a pair of plants sharing an interaction partner) was signficantly different from 0 for each network.
+     \caption{The slopes of the mixed-effect logistic regression of pairwise niche overlap against phylogenetic distance (representing the change in log odds of a pair of plants sharing an interaction partner) was significantly different from 0 for each network.
 Here we show the observed slopes for herbivory (green squares) and pollination (purple diamonds) networks.

### 2019-11-28 manuscript/supporting_info.tex
spellchecked. Still need to refine reply

@@
 Thus, while we observed the same trends when treating the response as a proportion and as a tuple, the tuple format displayed these trends more clearly.
-This is likely because of the additional informaion incorporated in the tuple.
+This is likely because of the additional information incorporated in the tuple.
 
@@
 This test accounts for the increased likelihood of obtaining at least one significant result by chance when conducting multiple hypothesis tests, but is less conservative and less prone to type II errors than the original Bonferroni test.
-All $p$-values remained signficant after applying this test (Table~\ref{SCBT_values}).
+All $p$-values remained significant after applying this test (Table~\ref{SCBT_values}).
 

### 2019-11-30 manuscript/reply_to_referees_2.tex
sent off to co-authors

@@
 We must also admit to having some difficulty parsing a number of Referee 2's comments in order to find what is being asked.
+This may be partly because this review came from several people - the Referee refers to themselves as 'we' several times, and the writing appears to be more than usually variable within their comments.
 These difficulties mean that we may not have followed as many of Referee 2's suggestions as we have for the other Referees.
-Nevertheless, we do appreciate their time and effort in offering such extensive feedback and have taken care to address each of Referee 2's comments in the hope of clarifying our perspective.
-
-	We appreciate all of the Referee's comments and are confident that our manuscript is all the stronger for responding to them.
+Nevertheless, we do appreciate their time and effort in offering such extensive feedback and have taken care to address each of Referee 2's comments in the hope of at least clarifying our perspective.
+
+	We appreciate all of the Referees' comments and are confident that our manuscript is all the stronger for responding to them.
 
@@
 
-{\Large \bf Reply to Referee 1} [[done]]
+{\Large \bf Reply to Referee 1}
 
@@
 	\begin{refquote}
-	General comments
+	General comments\\
 
@@
 	The Referee(s?) seems to view our basic question and analyses positively, but is rather bluntly critical of our writing in terms of logical, clarity, and style.
-Some of these criticisms seem to reflect a rather hasty reading of the manuscript, as there are points where the Referee asks why we did not conduct analyses that we did in fact perform or demands that we address biological concepts that already appeared in the text.
+Some of these criticisms seem to reflect a rather hasty reading of the manuscript, as there are points where the Referee asks for analyses or ideas to be included which already appear in the text.
 In these cases, we point to existing evidence in the manuscript and have tried to make these connections more obvious.
-In other cases, we struggled to understand the nature of the Referee's objections.
+In a few cases, we struggled to understand the nature of the Referee's objections.
 We have attempted to address each of the Referee's comments in detail below (preceded by \textbf{R:}).
-We hope that our response will clarify the focus and scope of our analyses and help the Referee to re-think their objections.
-
-	1. General criticism of the language of the text [[done]]
+Wherever possible, we have clarified our text in response to the Referee's comments.
+In particular, we now define community composition more explicitly, have revised the discussion to be more explicit about whether we are referring to overall or within-network trends, and have removed specific phrases that the Referee finds objectionable \emph{prima facie}.
+We hope that these changes and our response will clarify the focus and scope of our analyses.
+
+	1. General criticism of the language of the text
 
@@
 		\textbf{R:} As Referees 1 and 3 note, our English is scrupulously correct.
-Of course technical correctness does not necessarily imply clarity of expression, and we apologise if our choice of vocabulary has obfuscated some of the finer points of the manuscript.
+Of course technical correctness does not necessarily imply clarity of expression, and we apologise if our choice of vocabulary has obfuscated some of the nuances of the manuscript.
 We have endeavoured to clarify the manuscript as the Referee suggests.
 
-	2. Title lacks clarity [[done]]
-
-		\begin{refquote}
-		Specific comments
-		Title
+	2. Title lacks clarity
+
+		\begin{refquote}
+		Specific comments\\
+		Title\\
 		Your title still lacks clarity and does not reflect the main message you state at the beginning of your discussion (in the first sentence of it you state that you found broad support for the hypothesis that more closely related plants tend to have more niche overlap).
@@
 
-	3. Summary too methodologically-oriented in general [[done]]
-
-		\begin{refquote}
-			Summary
-			General comments
+	3. Summary too methodologically-oriented in general
+
+		\begin{refquote}
+			Summary\\
+			General comments\\
 			Your summary is too methodologically-oriented.
@@
 
-	4. Persistent mis-understanding of purpose and scope of within-family analyses [[done]]
+	4. Mis-understanding of purpose and scope of within-family analyses
 
@@
 
-		\textbf{R:} This comment indicates that the Referee has fundamentally misunderstood our manuscript based on the summary.
-Point 2 of the summary lists three separate analyses: testing for relationships between phylogenetic distance and partner overlap in \emph{all pairs of plants in a network, regardless of family}, testing whether the slopes of these whole-network relationships are related to the composition of the plant community in each network, and, as a supplement to these analyses, testing whether the slopes of these relationships differ if we consider only pairs of plants within the same family.
+		\textbf{R:} The Referee is correct about our hypothesis but appears to have assumed that we are \emph{only} searching for conservation of niche overlap within families.
+In fact, point 2 of the summary lists three separate analyses: testing for relationships between phylogenetic distance and partner overlap in \emph{all pairs of plants in a network, regardless of family}, testing whether the slopes of these whole-network relationships are related to the composition of the plant community in each network, and, as a supplement to these analyses, testing whether the slopes of these relationships differ if we consider only pairs of plants within the same family.
 We now number these three different analyses to avoid any further confusion.
 
-		As we are \emph{not} searching for differences between communities at the family level, but rather at all levels within the angiosperms, a number of the Referee's comments do not apply.
-We list these below.
-The only bearing this criticism could have is on our choice to use families as a tool to group species for more detailed analyses.
-This decision is based on the fact that many plant families are quite diverse, both in terms of numbers of species and in terms of phenotypes/interaction partners (see e.g., Wilson on plants and insect/bird pollinators).
+		In this context, checking for different relationships within families is similar to checking for different relationships between networks - an overall trend can mask a great deal of variability, and we wanted to make sure this variability was identified.
+We chose families as the taxonomic level for further analysis because many plant families are quite diverse, both in terms of numbers of species and in terms of phenotypes/interaction partners (see e.g., Wilson on plants and insect/bird pollinators).
 Within a single family, plants can show evidence of adaptive radiations, heterogeneous selection, both, or neither.
@@
 These different possibilities mean that it is not clear whether all families will show phylogenetic conservation of interaction partners.
-This makes families a convenient taxonomic level at which to look for finer-scale phylogenetic trends.
-As we found it difficult to find information on why  different families might show these different trends, we also hope to inspire future research along this  line.
 		We have added a summary of this explanation to the methods.
@@
 
-		Comments that do seem to not apply:
+		As we are \emph{not} searching for differences between communities at the family level, but rather at all levels within the angiosperms, a number of the Referee's comments do not apply.
+We list these below.
 
@@
 
-	5. Very confusing comment complaining about paragraph 4 [[done]]
+	5. Very confusing comment complaining about summary point 4
 
@@
 
-		\textbf{R:} The Referee appears to have some deep-seated objection to any reference to plant families, but has not made the reasons for this objection at all clear.
-As noted above, we do in fact consider relationships between phylogenetic distance and interaction partner overlap at \emph{all} taxonomic levels, not just within families.
-Apart from this, we are confused by the remainder of the Referee's complaint.
-By 'dominant', we mean 'most species-rich in the focal community' rather than any kind of functional interpretation.
-Note that we do not address functions in the rest of the manuscript, so it is not clear why the Referee makes this leap.
+		\textbf{R:} Apart from the Referee's objection to plant families as units for detailed analysis (see respons \#4), this comment seems to demonstrate uncertainty about how we defined the dominant plant families in a community.
+Note that we do not mean to imply any functional argument here, as our manuscript does not address functionality.
+Rather, by 'dominant', we mean 'most species-rich in the focal community'.
 In order to avoid future confusion, we now replace 'dominant families' with 'species-rich groups'.
@@
 
-	6. Complaint about keywords absent from the abstract [[done]]
-
-		\begin{refquote}
-		Keywords
+	6. Complaint about keywords absent from the abstract
+
+		\begin{refquote}
+		Keywords\\
 		Syndrome:  Why you do not mention such theory in your abstract?
@@
 		\textbf{R:} The abstract/summary is under strict word limits, and we did not feel that inserting each keyword without a clear purpose could justify the elimination of other material.
-Given the Referee's confusion regarding our analyses, we are more convinced than ever that our decision to omit some keywords (which do appear in the introduction) in favour of spending more words explaining our methodology was correct.
+Given the Referee's confusion regarding our analyses, we are more convinced than ever that our decision to omit some keywords in favour of spending more words explaining our methodology was correct.
 As we do not directly test pollination or defensive syndromes, we have removed these keywords from the list.
-
-	7. Mistake about the focus of the introduction [[done]]
-
-		\begin{refquote}
-		Introduction
+In response to the Referee's further objections to the syndrome literature, below, we have also removed these terms from the introduction.
+
+	7. Mistake about the focus of the introduction
+
+		\begin{refquote}
+		Introduction\\
 		General. You focus on the compromise between pollination and herbivory interactions but then you do not use this approach in your analyses.
@@
 		\textbf{R:} Potential tradeoffs between encouraging interactions with pollinators and discouraging herbivores are just one of the possible reasons why networks may not display the expected relationship between relatedness and niche overlap.
-Note that we also propose several others in the same paragraph, including convergent evolution or selection to avoid pollen dilution.
+Note that we also propose several others in the same paragraph where trade-offs appear, including convergent evolution or selection to avoid pollen dilution.
 We therefore disagree with the Referee's perception that we focus on compromise between pollination and herbivory.
@@
 
-	8. Deep disagreement with any link between syndromes and conservation of interaction partners [[done]]
+	8. Disagreement with any link between syndromes and conservation of interaction partners
 
@@
 
-		\textbf{R:} As the Referee notes, we do address the possibility of convergence later in our introduction.
+		\textbf{R:} As the Referee notes, we do address the possibility of convergence in our introduction.
 We do not make any claim as to whether the putative pollination syndromes actually reflect plants with common sets of pollinators (the evidence we are aware of is rather mixed).
-Since the Referee appears to object violently to this very common idea in the literature, and because syndromes do not form a major part of our analysis, we have removed it as a keyword and rephrased our introduction.
-It now no longer references pollination syndromes.
-Hopefully this will avoid other readers becoming fixated on the validity or otherwise of the syndrome idea and enable them to take our manuscript on its own merits.
+Since the Referee appears to object to this idea (which we note is quite common in the literature surrounding phylogenetic conservation of interactions), and because syndromes do not form a major part of our analysis, we have removed it as a keyword and rephrased our introduction so that it now no longer references pollination syndromes.
+Hopefully this will help readers to take our manuscript on its own merits rather than those of the syndrome concept.
 
@@
 
-	9. Request to include interaction intimacy [[done]]
+	9. Request to include interaction intimacy
 
@@
 
-		\textbf{R:} We have no information on interaction strengths or intimacies, and so cannot test whether this is affecting our results.
+		\textbf{R:} We have no information on interaction strengths or intimacies, and we note that the interactions we consider are generally low-intimacy.
+We therefore would not expect intimacy to strongly affect these networks.
 However, we are happy to include the idea as yet another reason why plant communities may or may not show conservation of interactions.
@@
 
-	10. Criticism of methodological changes required by previous reviewers [[done]]
-
-		\begin{refquote}
-		Methods
-		Dataset
+	10. Criticism of dataset changes required by previous reviewers
+
+		\begin{refquote}
+		Methods\\
+		Dataset\\
 		Several networks can be reviewed in the literature or are available in different websites.
@@
 
-		\textbf{R:} We restricted our selection of herbivory networks in response to a previous round of review.
+		\textbf{R:} We included all herbivory networks we could find when we began this project, and only restricted our selection of herbivory networks in response to a previous round of review.
 Without more details why (or if) the Referee believes that the herbivory networks we removed should be included, we have opted to continue following that earlier feedback.
-We would have appreciated specific tips for additional herbivory networks, but since the Referee does not provide any specifics there would appear to be little we can do to address this comment.
-
-	11. Request to change "insects consuming leaves" to "chewing insects" [[done]]
+We would have appreciated specific tips for additional herbivory networks, but since the Referee does not provide any specifics we do not feel that conducting an extensive search for additional networks and repeating our analyses is viable within the timeframe given to respond to this review.
+
+	11. Request to change "insects consuming leaves" to "chewing insects"
 
@@
 
-	12. Recommendation to continue using the same methodology [[done]]
-
-		\begin{refquote}
-			Measuring niche overlap
+	12. Recommendation to continue using Jaccard dissimilarity, binomial regression
+
+		\begin{refquote}
+			Measuring niche overlap\\
 			Why you used absolute numbers to measure shared and unshared pollinators and not the Jaccard index?
@@
 
-		\textbf{R:} We did use a Jaccard index, as stated in the first and second sentences under the sub-heading \textbf{Calculating niche overlap between communities}.
+		\textbf{R:} We did use a Jaccard index, as stated in the first  sentence under the sub-heading \textbf{Calculating niche overlap between communities} in the previous revision.
+This line read as follows (emphasis added):
+		\begin{quotation}
+		We calculated niche overlap for each pair of species within a community \emph{using a Jaccard index} to describe the number of shared interaction partners, augmented with the number of interaction partners which were not shared.
+		\end{quotation}
+
 		The Jaccard index is calculated using the number of shared and un-shared interaction partners for a pair of plants, as stated in equation 1.
@@
 
-	13. Request to include plant species as a fixed effect [[done]]
+		As stated in the section on phylogenetic data, we excluded comparisons involving plants for which we could not assign a binomial names (and therefore could not obtain phylogenetic distances) and comparisons between non-angiosperms due to our coarse estimates of their ages.
+This information appeared in lines 107-110 and 118-120 of the previous version and lines 112-115 and 122-124 of the current version.
+
+	13. Request to include plant species as a fixed effect
 
@@
 Due to the fact that species generally appear in few networks (many in only a single network), this would result in near singularity of our models.
-We would therefore be completely unable to observe any patterns as species identity would explain essentially all variation.
+We would therefore be completely unable to observe any patterns as species identity would explain nearly all variation in niche overlap.
 If the Referee is referring to a potential effect of network size, we did in fact test this (see equation 4 and description).
@@
 
-	14. Un-justified request to include connectance [[just address here]]
+	14. Request to include connectance
 
@@
 
-		\textbf{R:} We did not include connectance because we can offer no justification (biological or methodological) why the overall connectance of the network should affect the strength of the relationship between relatedness and niche overlap.
-It is possible that there might be an effect of connectance on the intercept of this relationship (as we would expect higher overlap in general when connectance is high), but we see no particular reason why connectance should change how closely-related species differ from distantly-related species in the same network.
-Since the Referee also does not provide any reasoning behind this request, we have opted to leave our analyses as-is.
-
-		[[Maybe I can add a bit of a biological argument that network size can affect overlap? I'm not sure what methodological but not biological means here.]]
-
-	15. Confusion about motivation for community composition analyses [[done]]
+		\textbf{R:} Our main reason for including network size as a potential effect was methodological rather than biological - slopes for smaller networks are based on smaller sample sizes and therefore may be less robust.
+We do not see either the methodological or biological arguments for including connectance as a predictor.
+We also note that the manuscript is already quite full, so including these new analyses would require us to remove something more important.
+Without a justification from the Referee as to why connectance should affect pairwise niche overlap, we have opted not to add this new thread to the manuscript.
+
+	15. Confusion about motivation for community composition analyses
 
@@
 We now explicitly state this in the introduction.
+Note that we cannot use Shannon diversity within networks as we do not know the abundances of the various plant species.
+All we can do is test the effect of numbers of species as described above.
 
@@
 
-	16. Critique of manuscript structure [[too vague - can't address]]
-
-		\begin{refquote}
-			Results
+	16. Critique of manuscript structure
+
+		\begin{refquote}
+			Results\\
 			General: Please, do not include discussion in your results, it may confound readers.
@@
 
-		\textbf{R:} Without knowing where, specifically, the Referee feels that we have included discussion in our results there is little we can do to address this complaint.
-
-	17. Incorrect claim that beginning of results is inaccurate [[done]]
+		\textbf{R:} We are unsure whether the Referee is giving general advice here or if there is a specific element of the results the Referee feels would fit better in the discussion.
+We thank the Referee for the advice but can take little practical action without more details as to the nature of their objection.
+
+	17. Incorrect claim that beginning of results is inaccurate
 
@@
 
-		\textbf{R:} This comment is in such poor English as to be nearly unintelligible.
-It is not clear whether the Referee is suggesting that we repeat our analyses using half of the pollination networks (without any clear reason as to why) or is simply confused about which analysis these results refer to.
-Since the Referee appears to have assumed that the within-family analyses are the \emph{only} analyses in the manuscript, the latter seems likely.
-
-		Note that the results in lines XX-XX correspond to our first analysis: testing whether niche overlap decreases over increasing phylogenetic
-		distance in a large dataset of pollination and herbivory networks.
-The overall regression did show that partner overlap decreases with increasing phylogenetic distance, so that more distantly-related plants are less likely to share interaction partners (see Fig.
-1).
-The rest of this section gives more details about the differences between pollination and herbivory networks (lines XX-XX) and variation across networks (lines XX-XX), but note that none of these details change the overall regression.
-As this text is correct we have left it unchanged.
-
-	18. Definition of community composition unclear [[done]]
+		\textbf{R:} This comment's somewhat eccentric grammar makes it rather difficult to parse.
+We are guessing that the Referee is confused by the overall trend (more related plants have more similar interaction partners) and the variability of the trends within specific networks.
+To help understand this, note that the structure of the first few lines of the discussion parallel the first few lines of the results.
+First we introduce the overall result, and then we expand upon the details.
+We have lightly edited lines 370-373 to make this clearer:
+
+		\begin{quotation}
+
+			We found general support for the hypothesis that more
+			closely-related pairs of plants have a higher degree
+			of niche overlap. Taking all networks together, 
+			the probability of two plants sharing the same animal 
+			interaction partners decreased with increasing 
+			phylogenetic distance. Considering networks separately ...
+
+		\end{quotation}
+
+	18. Definition of community composition unclear
 
@@
 For tractability, we have summarized community composition as the number of species in each plant family.
-We have added text to the methods to state this more obviously.
+We have added text to the methods to state this explicitly.
 
@@
 
-	19. Confusion about permutation methodology [[done]]
+	19. Confusion about permutation methodology
 
@@
 
-		\textbf{R:} As stated in the methods, we permuted interactions. Note that, in statistical terms, the two approaches are equivalent. We have rephrased the results to match the methods.
-
-	20. Typo in Fig. 1 caption [[done]]
+		\textbf{R:} As stated in the methods, we permuted interactions.
+Note that, in statistical terms, the two approaches are equivalent, but we appreciate that this may not be clear to readers unfamiliar with permutation approaches.
+We have rephrased the results to match the methods.
+
+	20. Typo in Fig. 1 caption
 
@@
 
-	21. Difference between minimum and maximum slopes not visible [[done]]
+	21. Difference between minimum and maximum slopes not visible
 
@@
 
-	22. Confusion about line 328 [[done]]
+	22. Confusion about line 328
 
@@
 
-		\textbf{R:} Yes, 12 is the number of families. We have revised the line to make this more explicit.
+		\textbf{R:} Yes, 12 is the number of families.
+We have revised the line to make this more explicit.
+Note that we have also corrected this line to match Table 1, which includes 14 significant families.
 
@@
 
-	23. Complaints about table numbering and figure referencing [[done]]
+	23. Complaints about table numbering and figure referencing
 
@@
 
-	24. Suggestion to include ideas about evolution and coevolution [[done]]
+	24. Suggestion to include ideas about evolution and coevolution
 
@@
 		\textbf{R:} We do include ideas about evolution and coevolution in our discussion.
-We completely agree that, together with ecological processes and environmental filtering, evolution and coevolution are very important in structuring networks.
+We completely agree that, together with ecological processes and environmental filtering, evolution and coevolution are very important in structuring networks at every level, from pairs of species to entire communities.
 However, since we do not have trait or genetic data for our networks, we cannot comment with any certainty on which of our results are due to trait plasticity or environmental influence and which are due to evolution.
@@
 
-	25. Objection to the word "broad" [[done]]
+	25. Objection to the word "broad"
 
@@
 		\textbf{R:} Note that 56\% is greater than half, and that when all networks were considered together we also observed the same trends.
-We contend that these two facts do represent broad support for our hypothesis.
-It is not, of course, universal support.
-That is why we A) did not claim universal support and B) provide the numbers of networks.
+We contend that these two facts do represent broad support for our hypothesis and note that the Hembry et al reference suggested by the Referee uses the word in a very similar way.
+Broad support is not, of course, universal support.
+That is why we provide the numbers of networks.
 Readers are thereby armed with the tools to agree or disagree with our choice of words.
@@
 
-		With the unbalanced sample sizes of pollination and herbivory networks, we are somewhat reluctant to make much of the difference between 56\% of pollination networks and 64\$ of herbivory networks.
+		We are glad that the Referee finds the greater proportion of significant herbivory networks interesting.
+With the unbalanced sample sizes of pollination and herbivory networks, however, we are somewhat reluctant to make much of the difference between 56\% and 64\%.
 We consider that the important point here is that networks are more likely than not to show decreasing niche overlap with increasing phylogenetic distance.
 
-	26. Confusing complaint about subsetting herbivory networks or perhaps objection to the claim that oligotrophy is common [[done]]
+	26. Confusing complaint about subsetting herbivory networks or perhaps objection to the claim that oligotrophy is common
 
@@
 
-		If the Referee objects to our finding that the herbivores in our networks tended to consume more than one plant species, there is little we can do about it.
-That is simply what our data say.
-We do not feel that it is appropriate to look for explanations in the trends we observe in our networks in other types of networks.
+		If the Referee objects to our finding that the herbivores in our networks tended to consume more than one plant species, there is little we can do about it. That is simply what our data say.
 
@@
 The mean number of plants consumed per herbivore ranged between 1.64 and 14.9 across networks, with a mean of 6.36, and the median ranged between 1 and 11.5 (mean 4.68).
-These measures indicate that many herbivores in our networks do, in fact, consume only a few of the plants available to them.
-Our point therefore stands.
-
-	27. Claims that congeneric species are not closely related [[No convincing reason to change]]
+These measures indicate that many herbivores in our networks do, in fact, consume only a few of the plants available to them (with some highly generalist species increasing the means).
+Our overall point, that oligotrophy may be common in herbivores, therefore stands.
+
+	27. Claims that congeneric species are not closely related
 
@@
 
-		\textbf{R:} Does the Referee really mean to suggest that plants in the same genus are less closely-related than plants in different families?
-Without some sources to substantiate this, we find this claim very far-fetched!
+		\textbf{R:} Does the Referee really mean to suggest that plants in the same genus are generally less closely-related than plants in different families?
+Without some sources to substantiate this, we find this claim very counter-intuitive.
 This is especially surprising given the Referee's insistence that we should expect similar interaction partners within a family.
 We agree that taxonomy is only a proxy for phylogeny, but we are not aware of any evidence that it is a poor proxy.
-We note that across seven other reviews, no other Referee has commented on this.
-Based on this lack of objection and similar language throughout the literature, we have opted not to change this line.
+We also note A) that similar language is quite common in the literature and B) that across seven other reviews, no other Referee has suggested that species in the same taxonomic groups (e.g., genera) are less closely-related than species in different groups.
+Without any evidence to support this claim, we have opted not to change our text.
 
@@
 
-		\textbf{R:} We do not have any data on interaction intimacy, nor did we test for reciprocal specialisation, so we cannot say how this would influence our results.
-At a guess, we would guess that leaf-chewing herbivory and pollination are both low-herbivory interactions.
-We would therefore naively expect similar trends.
-We note that~\citet{Hembry2018} only study a very small and high-intimacy system (a single genus of brood pollinating moths and their single genus of host plants).
+		\textbf{R:} We do not believe that interaction intimacy has a strong effect on our results, as both leaf-chewing herbivory and pollination are low-intimacy interactions~\citep{Astegiano2017}.
+It is possible that there is variation in intimacy within these broad categories, but we do not have data that would allow us to test such a hypothesis.
+We also note that~\citet{Hembry2018} study a very small and high-intimacy system (a single genus of brood pollinating moths and their single genus of host plants).
 Their results will therefore not necessarily generalize to the larger, more diverse networks we consider.
@@
 		This reference suggestion is also somewhat confusing as~\citet{Hembry2018} did not find evidence for host-associated differentiation in their moths.
-This would seem to undermine the Referee's fervent belief that evolution/coevolution can explain network structure.
+This would seem to undermine the idea that evolution/coevolution can explain network structure.
 Moreover, they point out that the support for the intimacy hypothesis  in their system was broad (in the same sense we used the word) but equivocal.
@@
 Instead, we feel that a discussion of the possible effects of intimacy is more relevant later on, where we discuss possible reasons why some families may show different trends.
-Although we cannot test this, some families may interact more intimately with their pollinators/herbivores.
-This could result in more specialised relationships and weaker signal.
-We had mentioned this possibility briefly in lines 406-407 of the previous version, but are happy to expand upon this point somewhat.
 This section (lines 443-454) now reads:
@@
 
-{\Large \bf Reply to Referee 3} [[Done]]
+{\Large \bf Reply to Referee 3}
 
@@
 If closely-related species provide similar functions in ecological networks, they could be used interchangeably to restore ecological interactions/functions.
-This is an exciting potential application of phylogenetic data in biodiversity conservation and restoration, and could be touched upon/discussed in this manuscript..
+This is an exciting potential application of phylogenetic data in biodiversity conservation and restoration, and could be touched upon/discussed in this manuscript.
 		Otherwise, I have only minor comments.
@@
 
-	1. Title is confusing [[done]]
+	1. Title is confusing
 
@@
 
-	2. Request to state that networks are qualitative rather than quantitative [[done]]
+	2. Request to state that networks are qualitative rather than quantitative
 
@@
 
-	3. L298 – Please be careful with use of “lesser/greater” “more negative or positive than expected from permuted networks” [[done]]
+	3. L298 – Please be careful with use of “lesser/greater” “more negative or positive than expected from permuted networks”
 
@@
 
-	4. Typo in line 322 [[done]]
+	4. Typo in line 322
 
@@
 
-{\Large \bf Reply to Referee 4} [[done]]
+{\Large \bf Reply to Referee 4}
 
@@
 
-	\textbf{R:} We thank the Referee for their compliments to our analysis and for taking the time to review our manuscript.
-We appreciate that our writing can be dense at times and appreciate the Referee pointing out places where we may clarify our prose.
+	\textbf{R:} We thank the Referee for their compliments to our analysis and for taking the time to review our manuscript so thoroughly.
+We acknowledge that our writing can be dense at times and appreciate the Referee pointing out places where we may clarify our prose.
 We especially appreciate the detailed suggestions for how to improve our second-to-last paragraph, and have followed them to the best of our ability.
 Below, we respond to each comment in detail (preceded by \textbf{R:}).
-We are confident that revising the manuscript in response to the Referee's comments has improved the manuscript.
-
-	1. Confusion about description of two dependent variables in analyses [[done]]
-
-		\begin{refquote}
-			* Modelling the relationship between niche overlap and phylogenetic distance
+We are confident that revising the manuscript in response to the Referee's comments has significantly improved it.
+
+	1. Confusion about description of tuple-form dependent variable
+
+		\begin{refquote}
+			* Modelling the relationship between niche overlap and phylogenetic distance\\
 			I did not managed to fully grasp the statistical analysis right away (I reckon I'm not a statistical master, but this may be the case of other readers), and I think it was mostly due to the way the methods are described.
@@
 
-		\textbf{R:} The number of shared and unshared interactions are both dependent variables included in the analysis.
-The number of shared variables is indeed the key variable, but the number of unshared interactions is also important as it indicates how extraordinary a particular number of shared interactions is.
+		\textbf{R:} The number of shared and unshared interactions are indeed both dependent variables included in the analysis.
+The number of shared variables is the key variable, but the number of unshared interactions is also important as it indicates how extraordinary a particular number of shared interactions is.
 The binomial process incorporates both quantities; converting the numbers of shared and unshared interactions to a proportion and weighting the observations by the total number of interactions.
-We thank the Referee for pointing out text in the introduction which clarified the purpose of including unshared interactions.
+We thank the Referee for pointing out text in the introduction which clarified the purpose of including unshared interactions, and have used it as the basis for improving the methods.
 We have expanded the beginning of this section to explain the logic of our modelling approach in more detail.
@@
 
-	2. Request to state that we use the Jaccard index more explicitly [[done]]
+	2. Request to state that we use the Jaccard index more explicitly
 
@@
 
-	3. Request to make non-independence of species within each community explicit. [[done]]
+	3. Request to make non-independence of species within each community explicit.
 
@@
 
-	4. Permuting the permuted networks is confusing [[done]]
-
-		\begin{refquote}
-			* Evaluating type I and type II errors: Permutations of permutations
+	4. Permuting the permuted networks is confusing
+
+		\begin{refquote}
+			* Evaluating type I and type II errors: Permutations of permutations\\
 			Paragraph p.
@@
 
-	5. Suggestion to consider phylogenetic diversity instead of number of plant pairs [[done]]
-
-		\begin{refquote}
-			* Testing the effect of network size on the existence of a phylogenetic signal
+	5. Suggestion to consider phylogenetic diversity instead of number of plant pairs
+
+		\begin{refquote}
+			* Testing the effect of network size on the existence of a phylogenetic signal\\
 			Here, it is specifically the number of plant pairs that is studied.
@@
 Because of this, and because this analysis would more compliment our community-composition analysis than introduce new material, we have opted no to pursue phylogenetic diversity in this manuscript.
-Here, we were more concerned with numbers of plant pairs since numbers of species are known to affect many areas of network structure.
-This did not appear to be a major issue for our analyses.
-
-	6. Request for consideration of multiple testing [[done]]
-
-		\begin{refquote}
-			* Testing within-family existence of a phylogenetic signal
+Here, we were more concerned with numbers of plant pairs since numbers of species are known to affect many areas of network structure and because the number of plant pairs is effectively the sample size for our within-network analyses.
+
+	6. Request for consideration of multiple testing
+
+		\begin{refquote}
+			* Testing within-family existence of a phylogenetic signal\\
 			Examining the strength of phylogenetic signal within plant families is an interesting idea.
@@
 This development of this test was heavily motivated by the Moran paper you recommend, and we thank the Referee for pointing out this literature.
-We have added tables of the SCBT critical values to Supplemental Information 4 in order to provide readers with a bit more detail.
+We have added tables of the SCBT critical values to \emph{Supplemental Information 4} in order to provide readers with a bit more detail.
 We have also added a few lines to the methods to formally introduce the problem of multiple testing, some of the objections to the strict Bonferroni in~\citet{Moran2003}, and our solution to it.
@@
 
-	7. Suggestion to mention sampling completeness as a potential explanation for specialists [[done]]
-
-		\begin{refquote}
-			On the effect of specialist pollinators
+	7. Suggestion to mention sampling completeness as a potential explanation for specialists
+
+		\begin{refquote}
+			On the effect of specialist pollinators\\
 
@@
 
-	8. Discussion of potential tradeoffs between interactions could be sharpened [[done]]
-
-		\begin{refquote}
-			On plant families involved in different types of interactions
+	8. Discussion of potential tradeoffs between interactions could be sharpened
+
+		\begin{refquote}
+			On plant families involved in different types of interactions\\
 
@@
 
-	9. Request for additional detail in summary point 2 [[done]]
+	9. Request for additional detail in summary point 2
 
@@
 
-	10. Incorrect referencing of Sauve et al., 2016 [[done]]
+	10. Incorrect referencing of Sauve et al., 2016
 
@@
 
-	11. Possible typo in page 3, lines 9-10 [[done]]
+	11. Possible typo in page 3, lines 9-10
 
@@
 
-	12. ?Suggestion to remove long list of citations in lines 22-25? [[done]]
+	12. Suggestion to remove long list of citations in lines 22-25
 
@@
 
-	11. Better showcase sentence on page 5, lines 78 [[done]]
+	11. Better showcase sentence on page 5, lines 78
 
@@
 
-	12. Suggestion to make a figure showing distribution of webs, or at least to add countries to the list in SI [[done]]
+	12. Suggestion to make a figure showing distribution of webs, or at least to add countries to the list in SI
 
@@
 
-	13. Suggestions to clarify explanation of regressions [[done?]]
+	13. Suggestions to clarify explanation of regressions
 
@@
 
-	14. Rephrasing of permutation strategy confusing [[done]]
+	14. Rephrasing of permutation strategy confusing
 
@@
 
-	15. Typo in page 15, lines 322-324 [[done]]
+	15. Typo in page 15, lines 322-324
 
@@
 
-	16. Fig. 3, Table 2 conflict for Poaceae [[done]]
+	16. Fig. 3, Table 2 conflict for Poaceae
 
@@
 
-	17. A confusing attempt at subtlety [[done]]
+	17. A confusing attempt at subtlety
 
@@
 
-\bibliographystyle{prsb} 
-\bibliography{abbreviated}
+\bibliographystyle{newphy} 
+\renewcommand*{\bibfont}{\raggedright}
+\bibliography{manual}
 

### 2019-12-05 manuscript/supporting_info.tex
checked all refs

@@
     \hline
-    M\_PL\_001  & Pollination & Chile & \citep{Arroyo1982}  \\
-    M\_PL\_002  & Pollination & Chile & \citep{Arroyo1982}  \\
-    M\_PL\_003  & Pollination & Chile & \citep{Arroyo1982}  \\
-    M\_PL\_004  & Pollination & Canada (New Brunswick) & \citep{Barrett1987} \\
-    M\_PL\_005  & Pollination & U.S.A. (Colorado) & \citep{Clements1923}  \\
-    M\_PL\_006  & Pollination & U.K. (Norfolk) & \citep{Dicks2002} \\
-    M\_PL\_007  & Pollination & U.K. (Norfolk) & \citep{Dicks2002} \\
-    M\_PL\_008  & Pollination & Spain (Canary Islands) & \citep{Dupont2003}  \\
-    M\_PL\_009  & Pollination & Sweden & \citep{Elberling1999} \\
+    M\_PL\_001  & Pollination & Chile & \citet{Arroyo1982}  \\
+    M\_PL\_002  & Pollination & Chile & \citet{Arroyo1982}  \\
+    M\_PL\_003  & Pollination & Chile & \citet{Arroyo1982}  \\
+    M\_PL\_004  & Pollination & Canada (New Brunswick) & \citet{Barrett1987} \\
+    M\_PL\_005  & Pollination & U.S.A. (Colorado) & \citet{Clements1923}  \\
+    M\_PL\_006  & Pollination & U.K. (Norfolk) & \citet{Dicks2002} \\
+    M\_PL\_007  & Pollination & U.K. (Norfolk) & \citet{Dicks2002} \\
+    M\_PL\_008  & Pollination & Spain (Canary Islands) & \citet{Dupont2003}  \\
+    M\_PL\_009  & Pollination & Sweden & \citet{Elberling1999} \\
     M\_PL\_010  & Pollination & Denmark (Greenland) & Elberling, H. \& Olesen, J. M. Unpub. \\
-    M\_PL\_011  & Pollination & Mauritius & \citep{Olesen2002a}  \\
-    M\_PL\_012  & Pollination & Portugal (Azores) & \citep{Olesen2002a}  \\
-    M\_PL\_013  & Pollination & South Africa (KwaZulu-Natal) & \citep{Ollerton2003}  \\
-    M\_PL\_014  & Pollination & Canada (N.W.T.) & \citep{Hocking1968} \\
-    M\_PL\_015  & Pollination & Greece (Athens) & \citep{Petanidou1991} \\
-    M\_PL\_016  & Pollination & Spain (Andalucia) & \citep{Herrera1988} \\
-    M\_PL\_017  & Pollination & U.K. (England) & \citep{Memmott2002} \\
+    M\_PL\_011  & Pollination & Mauritius & \citet{Olesen2002a}  \\
+    M\_PL\_012  & Pollination & Portugal (Azores) & \citet{Olesen2002a}  \\
+    M\_PL\_013  & Pollination & South Africa (KwaZulu-Natal) & \citet{Ollerton2003}  \\
+    M\_PL\_014  & Pollination & Canada (N.W.T.) & \citet{Hocking1968} \\
+    M\_PL\_015  & Pollination & Greece (Athens) & \citet{Petanidou1991} \\
+    M\_PL\_016  & Pollination & Spain (Andalucia) & \citet{Herrera1988} \\
+    M\_PL\_017  & Pollination & U.K. (England) & \citet{Memmott2002} \\
     M\_PL\_018  & Pollination & Denmark & Olesen, J. M. Unpublished.  \\
-    M\_PL\_019  & Pollination & U.S.A. (Colorado) & \citep{Inouye1988}  \\
-    M\_PL\_020  & Pollination & Canada (N.W.T.) & \citep{Kevan1970} \\
-    M\_PL\_021  & Pollination & Japan (Kyoto) & \citep{Kato1990}  \\
-    M\_PL\_022  & Pollination & Argentina (Mendoza) & \citep{Medan2002} \\
-    M\_PL\_023  & Pollination & Argentina (Mendoza) & \citep{Medan2002} \\
-    M\_PL\_024  & Pollination & Canada (N.W.T.) & \citep{Mosquin1967} \\
-    M\_PL\_025  & Pollination & U.S.A. (North Carolina) & \citep{Motten1982}  \\
-    M\_PL\_026  & Pollination & Ecuador (Gal\'{a}pagos Islands) & \citep{McMullen1993}  \\
-    M\_PL\_027  & Pollination & New Zealand (South Island) & \citep{Primack1983} \\
-    M\_PL\_028  & Pollination & New Zealand (South Island) & \citep{Primack1983} \\
-    M\_PL\_029  & Pollination & New Zealand (South Island) & \citep{Primack1983} \\
-    M\_PL\_030  & Pollination & Venezuela & \citep{Ramirez1992} \\
-    M\_PL\_031  & Pollination & Venezuela & \citep{Ramirez1989} \\
+    M\_PL\_019  & Pollination & U.S.A. (Colorado) & \citet{Inouye1988}  \\
+    M\_PL\_020  & Pollination & Canada (N.W.T.) & \citet{Kevan1970} \\
+    M\_PL\_021  & Pollination & Japan (Kyoto) & \citet{Kato1990}  \\
+    M\_PL\_022  & Pollination & Argentina (Mendoza) & \citet{Medan2002} \\
+    M\_PL\_023  & Pollination & Argentina (Mendoza) & \citet{Medan2002} \\
+    M\_PL\_024  & Pollination & Canada (N.W.T.) & \citet{Mosquin1967} \\
+    M\_PL\_025  & Pollination & U.S.A. (North Carolina) & \citet{Motten1982}  \\
+    M\_PL\_026  & Pollination & Ecuador (Gal\'{a}pagos Islands) & \citet{McMullen1993}  \\
+    M\_PL\_027  & Pollination & New Zealand (South Island) & \citet{Primack1983} \\
+    M\_PL\_028  & Pollination & New Zealand (South Island) & \citet{Primack1983} \\
+    M\_PL\_029  & Pollination & New Zealand (South Island) & \citet{Primack1983} \\
+    M\_PL\_030  & Pollination & Venezuela & \citet{Ramirez1992} \\
+    M\_PL\_031  & Pollination & Venezuela & \citet{Ramirez1989} \\
     \hline
@@
     \hline
-    M\_PL\_032  & Pollination & U.S.A. (Illinois) & \citep{Schemske1978}  \\
-    M\_PL\_033  & Pollination & Canada (Ontario) & \citep{Small1976} \\
-    M\_PL\_034  & Pollination & Chile & \citep{SmithRamirez2005}  \\
-    M\_PL\_035  & Pollination & Jamaica & \citep{Percival1974}  \\
+    M\_PL\_032  & Pollination & U.S.A. (Illinois) & \citet{Schemske1978}  \\
+    M\_PL\_033  & Pollination & Canada (Ontario) & \citet{Small1976} \\
+    M\_PL\_034  & Pollination & Chile & \citet{SmithRamirez2005}  \\
+    M\_PL\_035  & Pollination & Jamaica & \citet{Percival1974}  \\
     M\_PL\_036  & Pollination & Portugal (Azores) & Olesen, J. M. Unpublished.  \\
-    M\_PL\_037  & Pollination & Denmark & \citep{Montero2005} \\
-    M\_PL\_038  & Pollination & Denmark & \citep{Montero2005} \\
-    M\_PL\_039  & Pollination & Spain (Canary Islands) & \citep{Stald2003} \\
-    M\_PL\_040  & Pollination & Jamaica & \citep{Ingversen2006} \\
-    M\_PL\_041  & Pollination & Dominica & \citep{Ingversen2006} \\
-    M\_PL\_042  & Pollination & Ecuador (Gal\'{a}pagos Islands) & \citep{Philipp2006} \\
-    M\_PL\_043  & Pollination & Denmark & \citep{Montero2005} \\
-    M\_PL\_044  & Pollination & Japan (Amami Islands) & \citep{Kato2000}  \\
-    M\_PL\_045  & Pollination & Denmark (Greenland) & \citep{Lundgren2005}  \\
-    M\_PL\_046  & Pollination & Denmark & \citep{Bundgaard2003} \\
-    M\_PL\_047  & Pollination & Denmark & \citep{Dupont2009a}  \\
-    M\_PL\_048  & Pollination & Denmark & \citep{Dupont2009a}  \\
-    M\_PL\_049  & Pollination & Denmark & \citep{Bek2006}  \\
-    M\_PL\_050  & Pollination & Spain (Canary Islands) & \citep{Stald2003} \\
-    M\_PL\_051  & Pollination & Argentina (R\'{i}o Negro) & \citep{Vazquez2002} \\
-    M\_PL\_052  & Pollination & Denmark (Greenland) & \citep{Witt1998}  \\
-    M\_PL\_053  & Pollination & Japan (Kyusu) & \citep{Yamazaki2003}  \\
-    M\_PL\_054  & Pollination & Japan (Kyoto) & \citep{Kakutani1990}  \\
-    M\_PL\_055  & Pollination & Japan (Fukui Prefacture) & \citep{Kato1996}  \\
-    M\_PL\_056  & Pollination & Japan (Yamanashi) & \citep{Kato1993}  \\
-    M\_PL\_057  & Pollination & Japan (Kibune) & \citep{Inoue1990} \\
-    M\_PL\_058  & Pollination & Spain (Catalonia) & \citep{Bartomeus2008} \\
-    M\_PL\_059  & Pollination & Brazil (Bu\'{i}que) & \citep{Bezerra2009} \\
-    Basset  & Herbivory & Papua New Guinea & \citep{Basset1996}  \\
-    Bl\"{u}thgen  & Herbivory & Malaysia (Sabah) & \citep{Bluthgen2006a}  \\
-    Bodner  & Herbivory & Ecuador & \citep{Bodner2010}  \\
-    Coley & Herbivory & Panama & \citep{Coley2006} \\
-    Ibanez  & Herbivory & France (Central French Alps) & \citep{Ibanez2013}  \\
-    Joern\_altuda  & Herbivory & U.S.A. (Texas) & \citep{Joern1979} \\
-    Joern\_marathon  & Herbivory & U.S.A. (Texas) & \citep{Joern1979} \\
-    Novotny & Herbivory & Papua New Guinea & \citep{Novotny2012} \\
-    Peralta & Herbivory & New Zealand (South Island) & \citep{Peralta2016} \\
-    Sheldon & Herbivory & U.S.A. (Washington) & \citep{Sheldon1978} \\
-    Ueckert & Herbivory & U.S.A. (Colorado) & \citep{Ueckert1971} \\
+    M\_PL\_037  & Pollination & Denmark & \citet{Montero2005} \\
+    M\_PL\_038  & Pollination & Denmark & \citet{Montero2005} \\
+    M\_PL\_039  & Pollination & Spain (Canary Islands) & \citet{Stald2003} \\
+    M\_PL\_040  & Pollination & Jamaica & \citet{Ingversen2006} \\
+    M\_PL\_041  & Pollination & Dominica & \citet{Ingversen2006} \\
+    M\_PL\_042  & Pollination & Ecuador (Gal\'{a}pagos Islands) & \citet{Philipp2006} \\
+    M\_PL\_043  & Pollination & Denmark & \citet{Montero2005} \\
+    M\_PL\_044  & Pollination & Japan (Amami Islands) & \citet{Kato2000}  \\
+    M\_PL\_045  & Pollination & Denmark (Greenland) & \citet{Lundgren2005}  \\
+    M\_PL\_046  & Pollination & Denmark & \citet{Bundgaard2003} \\
+    M\_PL\_047  & Pollination & Denmark & \citet{Dupont2009a}  \\
+    M\_PL\_048  & Pollination & Denmark & \citet{Dupont2009a}  \\
+    M\_PL\_049  & Pollination & Denmark & \citet{Bek2006}  \\
+    M\_PL\_050  & Pollination & Spain (Canary Islands) & \citet{Stald2003} \\
+    M\_PL\_051  & Pollination & Argentina (R\'{i}o Negro) & \citet{Vazquez2002} \\
+    M\_PL\_052  & Pollination & Denmark (Greenland) & \citet{Witt1998}  \\
+    M\_PL\_053  & Pollination & Japan (Kyusu) & \citet{Yamazaki2003}  \\
+    M\_PL\_054  & Pollination & Japan (Kyoto) & \citet{Kakutani1990}  \\
+    M\_PL\_055  & Pollination & Japan (Fukui Prefacture) & \citet{Kato1996}  \\
+    M\_PL\_056  & Pollination & Japan (Yamanashi) & \citet{Kato1993}  \\
+    M\_PL\_057  & Pollination & Japan (Kibune) & \citet{Inoue1990} \\
+    M\_PL\_058  & Pollination & Spain (Catalonia) & \citet{Bartomeus2008} \\
+    M\_PL\_059  & Pollination & Brazil (Bu\'{i}que) & \citet{Bezerra2009} \\
+    Basset  & Herbivory & Papua New Guinea & \citet{Basset1996}  \\
+    Bl\"{u}thgen  & Herbivory & Malaysia (Sabah) & \citet{Bluthgen2006a}  \\
+    Bodner  & Herbivory & Ecuador & \citet{Bodner2010}  \\
+    Coley & Herbivory & Panama & \citet{Coley2006} \\
+    Ibanez  & Herbivory & France (Central French Alps) & \citet{Ibanez2013}  \\
+    Joern\_altuda  & Herbivory & U.S.A. (Texas) & \citet{Joern1979} \\
+    Joern\_marathon  & Herbivory & U.S.A. (Texas) & \citet{Joern1979} \\
+    Novotny & Herbivory & Papua New Guinea & \citet{Novotny2012} \\
+    Peralta & Herbivory & New Zealand (South Island) & \citet{Peralta2016} \\
+    Sheldon & Herbivory & U.S.A. (Washington) & \citet{Sheldon1978} \\
+    Ueckert & Herbivory & U.S.A. (Colorado) & \citet{Ueckert1971} \\
     \hline

### 2019-12-09 manuscript/reply_to_referees_2.tex
trying to be nicer to the idiot reviewer

@@
 	Given the difference of opinion between Referees 1, 3, and 4 and Referee 2, we have prioritised adjusting the manuscript according to the majority view.
-We must also admit to having some difficulty parsing a number of Referee 2's comments in order to find what is being asked.
-This may be partly because this review came from several people - the Referee refers to themselves as 'we' several times, and the writing appears to be more than usually variable within their comments.
-These difficulties mean that we may not have followed as many of Referee 2's suggestions as we have for the other Referees.
-Nevertheless, we do appreciate their time and effort in offering such extensive feedback and have taken care to address each of Referee 2's comments in the hope of at least clarifying our perspective.
+We must also admit to having some difficulty parsing a number of Referee 2's comments in order to find what precisely was being asked.
+This may be partly because this review appears to have come from several people - the Referee refers to themselves as 'we' several times, and the writing appears to be more than usually variable within their comments.
+These difficulties mean that we may not have been able to address Referee 2's comments as fully as we have those of the other Referees.
+Nevertheless, we do appreciate their time and effort in offering feedback.
+In addressing Referee 2's comments to the best of our abilities, we hope that we have at least managed to clarify our perspective.
 
@@
 
-	The Referee(s?) seems to view our basic question and analyses positively, but is rather bluntly critical of our writing in terms of logical, clarity, and style.
-Some of these criticisms seem to reflect a rather hasty reading of the manuscript, as there are points where the Referee asks for analyses or ideas to be included which already appear in the text.
-In these cases, we point to existing evidence in the manuscript and have tried to make these connections more obvious.
-In a few cases, we struggled to understand the nature of the Referee's objections.
-We have attempted to address each of the Referee's comments in detail below (preceded by \textbf{R:}).
-Wherever possible, we have clarified our text in response to the Referee's comments.
-In particular, we now define community composition more explicitly, have revised the discussion to be more explicit about whether we are referring to overall or within-network trends, and have removed specific phrases that the Referee finds objectionable \emph{prima facie}.
-We hope that these changes and our response will clarify the focus and scope of our analyses.
+	The Referee seems to view our basic question and analyses positively, but is rather critical of our writing in terms of logic, clarity, and style.
+We the time the Referee has spent in giving such extensive feedback, and have endeavoured to clarify the manuscript in response.
+In particular, we now define community composition more explicitly, have revised the discussion to be more explicit about whether we are referring to overall or within-network trends, and have removed specific phrases that the Referee found objectionable \emph{prima facie}.
+There are points where the Referee asks for analyses or ideas to be included which we felt already appeared in the text.
+In these cases, we point to the areas in question and have tried to make these connections more apparent.
+	We address each of the Referee's comments in detail below (preceded by \textbf{R:}). We hope that these changes and our response will clarify the focus and purpose of our analyses.
 
@@
 
-		\textbf{R:} As Referees 1 and 3 note, our English is scrupulously correct.
-Of course technical correctness does not necessarily imply clarity of expression, and we apologise if our choice of vocabulary has obfuscated some of the nuances of the manuscript.
-We have endeavoured to clarify the manuscript as the Referee suggests.
+		\textbf{R:} We acknowledge that our choice of vocabulary or phrasing may have obscured some of the finer points of the manuscript.
+We have carefully revised specific passages that this and other Referees have identied as particularly unclear, and attempted to refine the manuscript overall.
+We hope that it is now more clear.
 
@@
 
-		\textbf{R:} We have revised the title following a more detailed suggestion by Referee 3 and hope that the new title no longer implies logical inconsistency.
+		\textbf{R:} We have revised the title following a detailed suggestion by Referee 3 and believe that the new title is a better reflection of the manuscript as a whole.
 
@@
 
-		\textbf{R:} We regret that the Referee finds our summary too methodologically-orientated, but note that Referee 4 has requested that we include further methodological details in the summary.
-Moreover, in a later comment this Referee also requests more methodological details.
-To balance these conflicting comments, we no longer emphasise the methodological novelty of our study but have added the greater detail requested.
-As the other three Referees for this revision did not find the summary overly methodological in its original form, we are confident that the revised summary does not indicate that we lack focus.
-We also note that the extremely tight word limit for the summary does not allow us to explain why we have unbalanced numbers of pollination and herbivory networks.
-This information is contained in the methods.
+		\textbf{R:} We regret that the Referee found our summary too methodologically-orientated.
+We also note, however, that Referee 4 has requested that we include further methodological details in the summary.
+To strike a balance between these perspectives, we no longer emphasise the methodological novelty of our study but have added the greater detail requested.
+In the spirit of not making the summary overly methodological, and because of the extremely tight word limit, we have not attempted to explain the unbalanced numbers of pollination and herbivory networks here.
+This information is contained in the Methods.
 
@@
 
-		\textbf{R:} The Referee is correct about our hypothesis but appears to have assumed that we are \emph{only} searching for conservation of niche overlap within families.
+		\textbf{R:} The Referee is correct about our hypothesis but it appears that our earlier version lead them that we are \emph{only} searching for conservation of niche overlap within families.
 In fact, point 2 of the summary lists three separate analyses: testing for relationships between phylogenetic distance and partner overlap in \emph{all pairs of plants in a network, regardless of family}, testing whether the slopes of these whole-network relationships are related to the composition of the plant community in each network, and, as a supplement to these analyses, testing whether the slopes of these relationships differ if we consider only pairs of plants within the same family.
@@
 
-		In this context, checking for different relationships within families is similar to checking for different relationships between networks - an overall trend can mask a great deal of variability, and we wanted to make sure this variability was identified.
+		In this context, checking for different relationships within families is similar to checking for different relationships between networks - an overall trend can mask a great deal of variability, and we wanted to make sure this variability was described as thoroughly as possible.
 We chose families as the taxonomic level for further analysis because many plant families are quite diverse, both in terms of numbers of species and in terms of phenotypes/interaction partners (see e.g., Wilson on plants and insect/bird pollinators).
 Within a single family, plants can show evidence of adaptive radiations, heterogeneous selection, both, or neither.
-The Referee themself points out that some families can show both bird and bee pollination syndromes (see response \#8), and we can also point to papers such as Bernhardt 2000 and Johnson \& Jurgens 2010 which address trait lability, convergent evolution, and adaptive radiation.
+The Referee themself points out that some families can show both bird and bee pollination syndromes (see response \#7), and we can also point to papers such as Bernhardt 2000 and Johnson \& Jurgens 2010 which address trait lability, convergent evolution, and adaptive radiation.
 These different possibilities mean that it is not clear whether all families will show phylogenetic conservation of interaction partners.
-		We have added a summary of this explanation to the methods.
+		As we seem to have failed to make this point clearly in the earlier version, we have added a summary of this explanation to the methods.
 
@@
 
-		As we are \emph{not} searching for differences between communities at the family level, but rather at all levels within the angiosperms, a number of the Referee's comments do not apply.
-We list these below.
+		As we are not searching for differences between communities at the family level, but rather at all levels within the angiosperms, a number of the Referee's comments did not seem to directly apply.
+Due to their brevity, it is possible that we could not extract the Referee's main point from these comments.
+We list them below in case the Referee wishes to provide further clarification going forward.
 
@@
 
-	5. Very confusing comment complaining about summary point 4
+	5. Comments about summary point 4
 
@@
 
-		\textbf{R:} Apart from the Referee's objection to plant families as units for detailed analysis (see respons \#4), this comment seems to demonstrate uncertainty about how we defined the dominant plant families in a community.
+		\textbf{R:} Apart from the Referee's objection to plant families as units for detailed analysis (see response \#4), this comment seems to demonstrate uncertainty about how we defined the dominant plant families in a community.
 Note that we do not mean to imply any functional argument here, as our manuscript does not address functionality.
@@
 In order to avoid future confusion, we now replace 'dominant families' with 'species-rich groups'.
-We hope that this makes it clear that we are advocating researcher take a finer-scale perspective on phylogenetic signal in ecological networks.
+We hope that this makes it clear that we are advocating that researchers take a finer-scale perspective on phylogenetic signal in ecological networks.
 
@@
 
-	6. Complaint about keywords absent from the abstract
+	6. Comment about the focus of the introduction
+
+		\begin{refquote}
+		Introduction\\
+		General. You focus on the compromise between pollination and herbivory interactions but then you do not use this approach in your analyses.
+		\end{refquote}
+
+		\textbf{R:} Potential tradeoffs between encouraging interactions with pollinators and discouraging herbivores are just one of the possible reasons why networks may not display the expected relationship between relatedness and niche overlap.
+Note that we also propose several others in the same paragraph, including convergent evolution or selection to avoid pollen dilution.
+We therefore disagree with the Referee's perception that our primary focus is on the compromise between pollination and herbivory.
+This material is intended solely as background for readers who may not be familiar with arguments against the phylogenetic conservation of interaction partners.
+We have reviewed the text in question to reassure ourselves that this is the tenor of our introduction.
+
+	7. Disagreement with pollination syndrome discussion
 
@@
 		\end{refquote}
-
-		\textbf{R:} The abstract/summary is under strict word limits, and we did not feel that inserting each keyword without a clear purpose could justify the elimination of other material.
-Given the Referee's confusion regarding our analyses, we are more convinced than ever that our decision to omit some keywords in favour of spending more words explaining our methodology was correct.
-As we do not directly test pollination or defensive syndromes, we have removed these keywords from the list.
-In response to the Referee's further objections to the syndrome literature, below, we have also removed these terms from the introduction.
-
-	7. Mistake about the focus of the introduction
-
-		\begin{refquote}
-		Introduction\\
-		General. You focus on the compromise between pollination and herbivory interactions but then you do not use this approach in your analyses.
-		\end{refquote}
-
-		\textbf{R:} Potential tradeoffs between encouraging interactions with pollinators and discouraging herbivores are just one of the possible reasons why networks may not display the expected relationship between relatedness and niche overlap.
-Note that we also propose several others in the same paragraph where trade-offs appear, including convergent evolution or selection to avoid pollen dilution.
-We therefore disagree with the Referee's perception that we focus on compromise between pollination and herbivory.
-It is beyond the scope of this manuscript to test all possible reasons why closely-related plants might not share interaction partners.
-This material is intended solely as background for readers who may not be familiar with arguments against the phylogenetic conservation of interaction partners.
-
-	8. Disagreement with any link between syndromes and conservation of interaction partners
 
@@
 		\textbf{R:} As the Referee notes, we do address the possibility of convergence in our introduction.
-We do not make any claim as to whether the putative pollination syndromes actually reflect plants with common sets of pollinators (the evidence we are aware of is rather mixed).
-Since the Referee appears to object to this idea (which we note is quite common in the literature surrounding phylogenetic conservation of interactions), and because syndromes do not form a major part of our analysis, we have removed it as a keyword and rephrased our introduction so that it now no longer references pollination syndromes.
-Hopefully this will help readers to take our manuscript on its own merits rather than those of the syndrome concept.
+Note that while we mentioned pollination and defense syndromes as common ideas in the literature, we did not make any claim as to whether these putative syndromes actually reflect plants with common sets of pollinators (the evidence we are aware of is rather mixed).
+Since syndromes do not form a major part of our analysis, we have removed them from the keywords and introduction.
+We hope that these changes will help readers avoid becoming distracted from the main focus of our manuscript (whether phylogenetic distance predicts niche overlap).
 
@@
 
-	9. Request to include interaction intimacy
+	8. Request to include interaction intimacy
 
@@
 
-		\textbf{R:} We have no information on interaction strengths or intimacies, and we note that the interactions we consider are generally low-intimacy.
-We therefore would not expect intimacy to strongly affect these networks.
+		\textbf{R:} We have no information on interaction strengths or intimacies and so cannot test for this possibility.
 However, we are happy to include the idea as yet another reason why plant communities may or may not show conservation of interactions.
@@
 
-		In addition to the above, we have added another brief discussion of intimacy in the discussion (see response \#28)
-
-	10. Criticism of dataset changes required by previous reviewers
+	9. Criticism of methodological changes requested by previous reviewers
 
@@
 
-		\textbf{R:} We included all herbivory networks we could find when we began this project, and only restricted our selection of herbivory networks in response to a previous round of review.
-Without more details why (or if) the Referee believes that the herbivory networks we removed should be included, we have opted to continue following that earlier feedback.
-We would have appreciated specific tips for additional herbivory networks, but since the Referee does not provide any specifics we do not feel that conducting an extensive search for additional networks and repeating our analyses is viable within the timeframe given to respond to this review.
-
-	11. Request to change "insects consuming leaves" to "chewing insects"
+		\textbf{R:} We initially included all herbivory networks which we were able to locate at the beginning of this project (circa 2014).
+Restricting the herbivory networks to only leaf-chewing insects was requested in a previous round of review on the basis that the traits affecting leaf-chewing are likely to be quite different from those affecting gall-forming or other interactions.
+This mix of herbivory types would not necessarily be expected to show the same trends as pollination, which always involves the same plant tissues.
+As this logic seemed reasonable to us and the Editor, and because the networks involving other types of herbivory were too small a part of the dataset to control for such differences statistically, we agreed to remove the non-leaf-chewing networks.
+Without more details as to why (or if) the Referee believes that the herbivory networks we removed should be included, we have decided to continue following that earlier feedback.
+We have revised the Methods section \textbf{Network data} to make the reasons for using a subset of herbivory networks clearer and hope this this addresses the Referee's concerns.
+
+	10. Request to change "insects consuming leaves" to "chewing insects"
 
@@
 
-	12. Recommendation to continue using Jaccard dissimilarity, binomial regression
+	11. Recommendation to continue using the same methodology
 
@@
 
-		\textbf{R:} We did use a Jaccard index, as stated in the first  sentence under the sub-heading \textbf{Calculating niche overlap between communities} in the previous revision.
-This line read as follows (emphasis added):
-		\begin{quotation}
-		We calculated niche overlap for each pair of species within a community \emph{using a Jaccard index} to describe the number of shared interaction partners, augmented with the number of interaction partners which were not shared.
-		\end{quotation}
-
+		\textbf{R:} We apologize for any confusion here, as we do in fact use a Jaccard index, as stated under the sub-heading \textbf{Calculating niche overlap between communities}.
 		The Jaccard index is calculated using the number of shared and un-shared interaction partners for a pair of plants, as stated in equation 1.
-We also did use a generalised linear model with binomial error distribution, as stated in the \textbf{Statistical analysis} section.
+We also use a generalised linear model with binomial error distribution, as stated in the \textbf{Statistical analysis} section.
 We chose this methodology for exactly the reasons the Referee suggests, to give more weight to generalists sharing many interaction partners.
-This is stated in lines 138-141 and lines 148-154 (quoted below).
-Note that we have revised these lines somewhat in response to a suggestion from Referee 4, so they do differ somewhat from the previous version.
+This is stated in lines 137-143 and lines 148-154 (quoted below).
 We are glad that the Referee agrees with our choice in methodology.
+We have revised the Methods section in response to more detailed comments from Referee 4 and have added a brief appendix demonstrating how a tuple can be used as input to a glm in R.
+We hope that these changes make it clear that we are using a Jaccard index in a binomial regression in order to weight our models according to the amount of information provided by each species pair.
 
@@
 			the proportion of shared interactions. $J_{ij}$ is defined: 
-
+			% %
 			\begin{equation}
@@
 			where $M_{ij}$ is the set of \emph{mutual} (shared) interaction partners and $U_{ij}$ the set of unshared interaction partners for plants $i$ and $j$.
+			In our statistical analyses (see below), we used the tuple ($M_{ij}$, $U_{ij}$) as the
+			dependent variable rather than the single value $J_{ij}$. 
+			This allows us to preserve information about the amount of information provided by each pair of plants and weight the observations accordingly.
 
@@
 
-		As stated in the section on phylogenetic data, we excluded comparisons involving plants for which we could not assign a binomial names (and therefore could not obtain phylogenetic distances) and comparisons between non-angiosperms due to our coarse estimates of their ages.
-This information appeared in lines 107-110 and 118-120 of the previous version and lines 112-115 and 122-124 of the current version.
-
-	13. Request to include plant species as a fixed effect
+	12. Request to include plant species as a fixed effect
 
@@
 		\textbf{R:} It sounds as though the Referee would like us to include plant species as a predictor in our regressions.
-Due to the fact that species generally appear in few networks (many in only a single network), this would result in near singularity of our models.
-We would therefore be completely unable to observe any patterns as species identity would explain nearly all variation in niche overlap.
-If the Referee is referring to a potential effect of network size, we did in fact test this (see equation 4 and description).
-If the Referee did not mean either of these possibilities, we apologise but are unable to understand this comment.
-
-	14. Request to include connectance
+Due to the fact that particular species generally appear in few networks (many in only a single network), this would result in near singularity of our models.
+We would therefore be completely unable to observe any patterns as species identity would explain essentially all variation in our regressions.
+Species identity is undoubtedly important for the same reasons we observed different trends in different plant families, but our dataset is unsuited for testing for species-level variation.
+
+	13. Request to include connectance
 
@@
 
-		\textbf{R:} Our main reason for including network size as a potential effect was methodological rather than biological - slopes for smaller networks are based on smaller sample sizes and therefore may be less robust.
-We do not see either the methodological or biological arguments for including connectance as a predictor.
-We also note that the manuscript is already quite full, so including these new analyses would require us to remove something more important.
+		\textbf{R:} Our main reason for including network size as a potential effect was indeed methodological rather than biological - slopes for smaller networks are based on smaller sample sizes and therefore may be less robust.
+		Given the potential for this sample size effect to skew our results, we believe that this methodological/mathematical argument is sufficient to explain why we tested for an effect of network size.
+
+		In contrast, we were unable to determine amongst ourselves what the methodological or biological arguments would be for including connectance as a predictor.
+We also note that the manuscript is already quite full, so including these new analyses would require us to remove something which we and other Referees have regarded as important through the last few revisions.
 Without a justification from the Referee as to why connectance should affect pairwise niche overlap, we have opted not to add this new thread to the manuscript.
 
-	15. Confusion about motivation for community composition analyses
-
-		\begin{refquote}
-			Line 210 Linking network level trends and community composition
+	14. Confusion about motivation for community composition analyses
+
+		\begin{refquote}
+			Line 210 Linking network level trends and community composition\\
 
@@
 We now explicitly state this in the introduction.
-Note that we cannot use Shannon diversity within networks as we do not know the abundances of the various plant species.
-All we can do is test the effect of numbers of species as described above.
+While we agree that testing for an effect of Shannon diversity could be interesting, we cannot include such a test in this manuscript as we do not have information on species abundances.
 
@@
 
-	16. Critique of manuscript structure
+	15. Critique of manuscript structure
 
@@
 
-		\textbf{R:} We are unsure whether the Referee is giving general advice here or if there is a specific element of the results the Referee feels would fit better in the discussion.
-We thank the Referee for the advice but can take little practical action without more details as to the nature of their objection.
-
-	17. Incorrect claim that beginning of results is inaccurate
+		\textbf{R:} We have revised the results as best we can to avoid text which could be misconstrued as discussion.
+
+	16. Confusion about beginning of results
 
@@
 
-		\textbf{R:} This comment's somewhat eccentric grammar makes it rather difficult to parse.
-We are guessing that the Referee is confused by the overall trend (more related plants have more similar interaction partners) and the variability of the trends within specific networks.
-To help understand this, note that the structure of the first few lines of the discussion parallel the first few lines of the results.
+		\textbf{R:} We had some difficulty interpreting this comment but are guessing that the Referee is confused by the transition between the overall trend (more related plants have more similar interaction partners) and the variability of the trends within specific networks.
+To help understand this, note that the structure of the first few lines of the discussion parallels the first few lines of the results.
 First we introduce the overall result, and then we expand upon the details.
-We have lightly edited lines 370-373 to make this clearer:
+We have edited lines 370-373 to make this clearer:
 
@@
 
-	18. Definition of community composition unclear
+	17. Definition of community composition unclear
 
@@
 
-		\textbf{R:} Community composition is the set of plant species that make up a community, as described by the researchers constructing each network.
+		\textbf{R:} We define community composition as the set of plant species that make up a community, as described by the researchers constructing each network.
 For tractability, we have summarized community composition as the number of species in each plant family.
-We have added text to the methods to state this explicitly.
+We have added text to the methods to state this more explicitly.
 
@@
 			Specifically, we tested the hypothesis that
-			varying relationships between phylogenetic distance and
+			varying relationships between phylogenetic distance and pairwise
 			niche overlap are due to the different distributions 
@@
 
-	19. Confusion about permutation methodology
-
-		\begin{refquote}
-			Minor comments on Results
+	18. Confusion about permutation methodology
+
+		\begin{refquote}
+			Minor comments on Results\\
 			297-298 You permuted interactions or phylogenetic distances?
@@
 		\textbf{R:} As stated in the methods, we permuted interactions.
-Note that, in statistical terms, the two approaches are equivalent, but we appreciate that this may not be clear to readers unfamiliar with permutation approaches.
+In statistical terms, the two approaches are equivalent, but we appreciate that this may not be obvious given that permutation approaches are not terribly common.
 We have rephrased the results to match the methods.
 
-	20. Typo in Fig. 1 caption
+	19. Typo in Fig. 1 caption
 
@@
 
-	21. Difference between minimum and maximum slopes not visible
+	20. Difference between minimum and maximum slopes not visible
 
@@
 
-		\textbf{R:} As the caption states, the minimum and maximum slopes were always very close to 0.
-We therefore had to choose between a y-axis scale which would show the observed slopes or one which would show the differences in slopes for the permutations.
-As the observed slopes are far more important than knowing the exact values of the permutation slopes, we chose to prioritise the former.
-
-	22. Confusion about line 328
+		\textbf{R:} As stated in the caption, the minimum and maximum slopes from the permutations are very close to 0.
+The clarify that they are not the same values, we now give the range of slopes (-1.34$\times10^{-12}$ to 9.19$\times10^{-13}$) as in the caption of Fig.
+1.
+We hope that this is now clearer.
+
+	21. Number of families unclear in line 328
 
@@
 
-		\textbf{R:} Yes, 12 is the number of families.
+		\textbf{R:} The Referee is correct; 12 is indeed the number of families.
 We have revised the line to make this more explicit.
@@
 
-	23. Complaints about table numbering and figure referencing
+	22. Table numbering and figure referencing
 
@@
 
-		\textbf{R:} We have reordered the tables and added a redundant reference to Fig. 3.
-
-	24. Suggestion to include ideas about evolution and coevolution
-
-		\begin{refquote}
-			Discussion
-			General
+		\textbf{R:} We have reordered the tables and added a second reference to Fig. 3.
+
+	23. Request for more evolution content
+
+		\begin{refquote}
+			Discussion\\
+			General\\
 			We suggest you include ideas about evolution and coevolution in networks in your discussion.
@@
 
-		\textbf{R:} We do include ideas about evolution and coevolution in our discussion.
-We completely agree that, together with ecological processes and environmental filtering, evolution and coevolution are very important in structuring networks at every level, from pairs of species to entire communities.
+		\textbf{R:} We completely agree that, together with ecological processes and environmental filtering, evolution and coevolution are very important in structuring networks.
 However, since we do not have trait or genetic data for our networks, we cannot comment with any certainty on which of our results are due to trait plasticity or environmental influence and which are due to evolution.
 We therefore mention possible evolutionary and ecological explanations together.
-
-		Some examples of evolutionary ideas in the discussion:
-
-		Lines 413-418:
-
-		\begin{quotation}
-
-			This relationship between overlap and 
-			phylogenetic distance is consistent with the idea that traits affecting 
-			interactions are heritable and change gradually
-			such that closely related plants resemble their common ancestor--- and
-			each other ---more than they do distantly related 
-			plants~\citep{Schemske1999,Gilbert2015,Ponisio2017}. The degree of 
-			heritability of key traits may, however, differ between families.
-
-		\end{quotation}
+This mixture may have led the Referee to miss the evolutionary and coevolutionary ideas which are embedded throughout the discussion.
+We highlight some examples of these ideas below:
 
@@
 			Alternatively, plants in these families could have undergone convergent evolution or ancestral traits could be strongly preserved.
-
-		\end{quotation}
-
-		Lines 444-446:
-
-		\begin{quotation}
-
-			Selection to avoid 
-			competition and restrict numbers of interaction partners may lead to
-			more intimate or specialised interactions~\citep{Ponisio2017}.
 
@@
 
-	25. Objection to the word "broad"
+	24. Objection to claim of "broad support"
 
@@
 
-		\textbf{R:} Note that 56\% is greater than half, and that when all networks were considered together we also observed the same trends.
-We contend that these two facts do represent broad support for our hypothesis and note that the Hembry et al reference suggested by the Referee uses the word in a very similar way.
-Broad support is not, of course, universal support.
-That is why we provide the numbers of networks.
-Readers are thereby armed with the tools to agree or disagree with our choice of words.
-In case it is the synonymy between broad and general that has perplexed the Referee, we have changed this line to state ''We found \emph{general} support...''.
-We hope that this is clearer.
+		\textbf{R:} We found that more closely-related pairs of plants have greater niche overlap when considering all networks together, as well as in the majority of networks considered separetely. 
+		Moreover, the number of networks displaying significant trends (56\% of the pollination networks and 64\% of herbivory networks) is much greater than we would expect to occur purely by chance.
+Putting all of this together, we contend that there is indeed broad (in the sense of 'general' or 'overall') support for our hypothesis.
+In case it is simply the synonymy between broad and general that has perplexed the Referee, we have revised this line to state ''We found \emph{general} support...''.
+We hope that this wording is less contentious when the overall trends and preponderance of within-network results are considered together.
+
+		Nevertheless, we agree with the Referee that we do not have universal support for our hypothesis.
+This is why we provide the numbers of networks which did and did not support our hypothesis immediately after stating the oveerall trend.
+This allows readers to agree or disagree with our choice of words based on their interpretation of the facts.
 
 		We are glad that the Referee finds the greater proportion of significant herbivory networks interesting.
+We also find the possibility of stronger conservation of interaction partners in herbivory networks intriguing.
 		With the unbalanced sample sizes of pollination and herbivory networks, however, we are somewhat reluctant to make much of the difference between 56\% and 64\%.
@@
 
-	26. Confusing complaint about subsetting herbivory networks or perhaps objection to the claim that oligotrophy is common
+	25. Suggestion that low numbers of specialist herbivores are an artefact
 
@@
 
-		Beyond that, it is very difficult to work out exactly what the Referee objects to in this sentence.
-If the Referee is objecting to our references, note that~\citet{Novotny2005} addresses leaf-chewers as intermediate in their level of specialisation on particular families and emphasises that herbivores in general (regardless of guild) tend to consume a few closely-related hosts.
+		Beyond the objection to the dataset, it appears that the Referee is claiming that oligotrophy rather than strict specialisation is an artefact of our dataset rather than a general feature of herbivory networks.
+Note, however, that~\citet{Novotny2005} addresses leaf-chewers as intermediate in their level of specialisation on particular families and emphasises that herbivores in general (regardless of guild) tend to consume a few closely-related hosts.
 They point out the relative rarity of strict specialists compared to specialists on species within a particular genus or family.~\citet{Brandle2006} also found insect herbivores were specialised on a particular genus but consumed multiple species within the genus.
 As~\citet{Brandle2006} focus on phytophagous insects specifically, we feel that this reference addresses our point more directly than~\citet{Yguel2011}.
-We have therefore replaced this reference.
-We hope that this improved selection of references will help the Referee's confusion.
-
-		If the Referee objects to our finding that the herbivores in our networks tended to consume more than one plant species, there is little we can do about it. That is simply what our data say.
-
-		If the Referee is contending that, because of the multiple herbivore types in~\citet{Novotny2005}, we cannot claim that the herbivores in our dataset are oligotrophs, we can respond with further details.
-The mean number of plants consumed per herbivore ranged between 1.64 and 14.9 across networks, with a mean of 6.36, and the median ranged between 1 and 11.5 (mean 4.68).
-These measures indicate that many herbivores in our networks do, in fact, consume only a few of the plants available to them (with some highly generalist species increasing the means).
-Our overall point, that oligotrophy may be common in herbivores, therefore stands.
-
-	27. Claims that congeneric species are not closely related
+We have therefore replaced this reference and hope that this improved support will better demonstrate that the low levels of strict specialist herbivores in our dataset are not artefactual.
+
+	26. Claims that congeneric species are not closely related
 
@@
 
-		\textbf{R:} Does the Referee really mean to suggest that plants in the same genus are generally less closely-related than plants in different families?
-Without some sources to substantiate this, we find this claim very counter-intuitive.
-This is especially surprising given the Referee's insistence that we should expect similar interaction partners within a family.
-We agree that taxonomy is only a proxy for phylogeny, but we are not aware of any evidence that it is a poor proxy.
-We also note A) that similar language is quite common in the literature and B) that across seven other reviews, no other Referee has suggested that species in the same taxonomic groups (e.g., genera) are less closely-related than species in different groups.
-Without any evidence to support this claim, we have opted not to change our text.
-
-	28. Another demand to discuss intimacy [[done. Look for more places to scattershot Hembry]]
+		\textbf{R:} We may have failed to grasp the essence of this comment, as it seems that the Referee is suggesting that plants in the same genus are generally less closely-related than plants in different genera.
+This is quite counter-intuitive.
+We agree that plants within some genera are more closely-related than plants within other genera, but because we always use phylogenetic distance in our analyses, these differences do not influence the slopes we observe.
+Here we are not comparing the divergence times of different genera but referencing the nested nature of phylogenies as a whole.
+Referring to genera and subfamiliees is intended as a guide for readers who may not be expert phylogeneticists and could appreciate a reminder that we are considering branches near the tips of a phylogenetic tree.
+
+		In general, we believe that taxonomy is a reasonable proxy for phylogeny, and that two plants from within a genus will be more closely related than two plants in different genera.
+We are not aware of any evidence to the contrary, but are open to exploring this viewpoint if the Referee would like to provide some citations.
+In the meantime, we have opted not to change our text.
+
+	27. Request to discuss results in terms of intimacy
 
@@
 
-		\textbf{R:} We do not believe that interaction intimacy has a strong effect on our results, as both leaf-chewing herbivory and pollination are low-intimacy interactions~\citep{Astegiano2017}.
-It is possible that there is variation in intimacy within these broad categories, but we do not have data that would allow us to test such a hypothesis.
-We also note that~\citet{Hembry2018} study a very small and high-intimacy system (a single genus of brood pollinating moths and their single genus of host plants).
-Their results will therefore not necessarily generalize to the larger, more diverse networks we consider.
-Indeed, had they considered a broader sample of plants and seed predators or herbivores from the same islands, they easily could have found less reciprocal specialisation.
-As a detailed study of this unusual mutualism was the aim in~\citet{Hembry2018} this is not a problem for their work, but we are hesitant to infer too strong a relationship between their findings and ours.
-
-		This reference suggestion is also somewhat confusing as~\citet{Hembry2018} did not find evidence for host-associated differentiation in their moths.
-This would seem to undermine the idea that evolution/coevolution can explain network structure.
-Moreover, they point out that the support for the intimacy hypothesis  in their system was broad (in the same sense we used the word) but equivocal.
-This exacerbates the difficulty of extrapolating their work to explain our results.
-
-		Given all of the above, it is hard to see how the interaction intimacy hypothesis relates to these lines (which are about whether the number of species in different plant families is related to the strength of phylogenetic signal).
-Instead, we feel that a discussion of the possible effects of intimacy is more relevant later on, where we discuss possible reasons why some families may show different trends.
-This section (lines 443-454) now reads:
-
-		\begin{quotation}
-
-			Indeed, animal pollination and seed dispersal have been shown to act
-			as filters for several plant clades~\citep{Mayfield2009}. Selection to avoid 
+		\textbf{R:} We do not have information about the intimacy of different interactions within our dataset and are reluctant to speculate about what the effects of intimacy might be without data.
+Both leaf-chewing herbivory and pollination are generally low-intimacy interactions~\citep{Astegiano2017}, but there may still be variation in intimacy within these groups.
+Without more detailed information, that is as far as we can comment without pure speculation.
+
+		It is also difficult to compare our work to that of~\citet{Hembry2018} as their small and extremely intimate system is quite different from our larger, more diverse dataset.
+In particular, our pollination and herbivory networks generally describe different systems, so we cannot test whether reciprocal specialisation is more common for plants which interact with the same animals as pollinators and herbivores.
+We agree that this would be interesting, but it is a question best left for future work and a more targetted data set.
+
+		Given all of the above, we do not believe that a detailed discussion of intimacy fits well with our discussion.
+We do want to keep this idea in readers heads, however, and have added a brief description of the idea in lines (lines 443-454):
+
+		\begin{quotation}
+
+			Selection to avoid 
 			competition and restrict numbers of interaction partners may lead to
 			more intimate or specialised interactions~\citep{Ponisio2017}. 
-			Reciprocal specialisation is particularly expected in highly intimate interactions~\citep{Hembry2018} rather than the relatively low-intimacy pollination or leaf-chewing herbivory we consider here~\citep{Astegiano2017}.
-			Despite this, it is still possible that some plant families may tend to have more intimate interactions than others.
-This could result, for example, if a plant is pollinated by an insect which is also a herbivore in its larval stage~\citep{Hembry2018}.
-			Whether or not intimacy plays a role in structuring these interactions, past selection to avoid competition is 
+			This is particularly the case in highly intimate interactions, where both partners may specialise~\citep{Hembry2018}.
+			Past selection to avoid competition is 
 			consistent with the relatively high proportion of extreme specialists we
@@
 We thank the Referee for pointing out text in the introduction which clarified the purpose of including unshared interactions, and have used it as the basis for improving the methods.
-We have expanded the beginning of this section to explain the logic of our modelling approach in more detail.
+We have expanded the beginning of this section to explain the logic of our modelling approach in more detail, and a brief appendix which shows how a tuple can be given as input in a regression model in R.
 
@@
 			\end{equation}
-			where $M_{ij}$ is the set of \emph{mutual} (shared) interaction partners and $U_{ij}$ the set of unshared interaction partners for plants $i$ and $j$.
+			where $M_{ij}$ is the set of \emph{mutual} (shared) interaction partners and $U_{ij}$ the set of unshared interaction partners for plants $i$ and $j$ (see \emph{Supplemental Information 2} for R implementation).
 

### 2019-12-09 manuscript/reply_to_referees_2_dbs.tex
trying to be nicer to the idiot reviewer

--- 2019-11-30 manuscript/reply_to_referees_2.tex
@@
 \location{Private Bag 4800}
-\telephone{+64 3 364 2729}
+% \telephone{+64 3 364 2729}
 \fax{+64 3 364 2590}
@@
 	Given the difference of opinion between Referees 1, 3, and 4 and Referee 2, we have prioritised adjusting the manuscript according to the majority view.
-We must also admit to having some difficulty parsing a number of Referee 2's comments in order to find what is being asked.
+We must also admit to having some difficulty parsing a number of Referee 2's comments in order to find what precisely was being asked.
 This may be partly because this review came from several people - the Referee refers to themselves as 'we' several times, and the writing appears to be more than usually variable within their comments.
 These difficulties mean that we may not have followed as many of Referee 2's suggestions as we have for the other Referees.
-Nevertheless, we do appreciate their time and effort in offering such extensive feedback and have taken care to address each of Referee 2's comments in the hope of at least clarifying our perspective.
+Nevertheless, we do appreciate their time and effort in offering such extensive feedback and have taken care to address each of Referee 2's comments to the best of our abilities in the hope of at least clarifying our perspective.
 
@@
 
-	The Referee(s?) seems to view our basic question and analyses positively, but is rather bluntly critical of our writing in terms of logical, clarity, and style.
-Some of these criticisms seem to reflect a rather hasty reading of the manuscript, as there are points where the Referee asks for analyses or ideas to be included which already appear in the text.
-In these cases, we point to existing evidence in the manuscript and have tried to make these connections more obvious.
-In a few cases, we struggled to understand the nature of the Referee's objections.
+	The Referee seems to view our basic question and analyses positively, but is rather critical of our writing in terms of logical, clarity, and style.
+	%Some of these criticisms seem to reflect a rather hasty reading of the manuscript, as
+	There are points where the Referee asks for analyses or ideas to be included which we felt already appeared in the text.
+	In these cases, we point to the areas in question and have tried to make these connections more apparent.
+	In a few further cases, we were not fully able to identify the core of the Referee's objections.
 We have attempted to address each of the Referee's comments in detail below (preceded by \textbf{R:}).
 Wherever possible, we have clarified our text in response to the Referee's comments.
-In particular, we now define community composition more explicitly, have revised the discussion to be more explicit about whether we are referring to overall or within-network trends, and have removed specific phrases that the Referee finds objectionable \emph{prima facie}.
+In particular, we now define community composition more explicitly, have revised the discussion to be more explicit about whether we are referring to overall or within-network trends, and have removed specific phrases that the Referee found objectionable \emph{prima facie}.
 We hope that these changes and our response will clarify the focus and scope of our analyses.
@@
 
-		\textbf{R:} As Referees 1 and 3 note, our English is scrupulously correct.
+		\textbf{R:} 
+		%As Referees 1 and 3 note, our English is scrupulously correct.
 Of course technical correctness does not necessarily imply clarity of expression, and we apologise if our choice of vocabulary has obfuscated some of the nuances of the manuscript.
 We have endeavoured to clarify the manuscript as the Referee suggests.
+		We are sorry the Referee found the text less clear than we would have desired. We have gone through the latest version very carefully with a focus on the clarity of the text.
 
@@
 
-		\textbf{R:} We have revised the title following a more detailed suggestion by Referee 3 and hope that the new title no longer implies logical inconsistency.
+		\textbf{R:} We have revised the title following a more detailed suggestion by Referee 3 and hope that the new title is a better reflection of the manuscript as a whole.
 
@@
 
-		\textbf{R:} We regret that the Referee finds our summary too methodologically-orientated, but note that Referee 4 has requested that we include further methodological details in the summary.
-Moreover, in a later comment this Referee also requests more methodological details.
-To balance these conflicting comments, we no longer emphasise the methodological novelty of our study but have added the greater detail requested.
-As the other three Referees for this revision did not find the summary overly methodological in its original form, we are confident that the revised summary does not indicate that we lack focus.
-We also note that the extremely tight word limit for the summary does not allow us to explain why we have unbalanced numbers of pollination and herbivory networks.
-This information is contained in the methods.
+		\textbf{R:} We regret that the Referee found our summary too methodologically-orientated.
+We also note that Referee 4 has requested that we include further methodological details in the summary.
+To balance these out, we no longer emphasise the methodological novelty of our study but have added the greater detail requested.
+We also note, however, that the extremely tight word limit for the summary does not allow us to explain why we have unbalanced numbers of pollination and herbivory networks.
+This information is contained in the Methods.
 
@@
 
-		\textbf{R:} The Referee is correct about our hypothesis but appears to have assumed that we are \emph{only} searching for conservation of niche overlap within families.
+		\textbf{R:} The Referee is correct about our hypothesis but it appears that our earlier version lead them to believe that we are \emph{only} searching for conservation of niche overlap within families.
 In fact, point 2 of the summary lists three separate analyses: testing for relationships between phylogenetic distance and partner overlap in \emph{all pairs of plants in a network, regardless of family}, testing whether the slopes of these whole-network relationships are related to the composition of the plant community in each network, and, as a supplement to these analyses, testing whether the slopes of these relationships differ if we consider only pairs of plants within the same family.
@@
 
-		In this context, checking for different relationships within families is similar to checking for different relationships between networks - an overall trend can mask a great deal of variability, and we wanted to make sure this variability was identified.
+		In this context, checking for different relationships within families is similar to checking for different relationships between networks - an overall trend can mask a great deal of variability, and we wanted to make sure this variability was identified as best possible.
 We chose families as the taxonomic level for further analysis because many plant families are quite diverse, both in terms of numbers of species and in terms of phenotypes/interaction partners (see e.g., Wilson on plants and insect/bird pollinators).
@@
 These different possibilities mean that it is not clear whether all families will show phylogenetic conservation of interaction partners.
-		We have added a summary of this explanation to the methods.
+		As we seem to have failed in making this point clearly in the earlier version, we have added a summary of this explanation to the methods.
 
@@
 
-		As we are \emph{not} searching for differences between communities at the family level, but rather at all levels within the angiosperms, a number of the Referee's comments do not apply.
-We list these below.
+		As we are not searching for differences \emph{between} communities at the family level, but rather at all levels within the angiosperms, a number of the Referee's comments did not seem to directly apply.
+I their brevity, it is possible that we were unable to capture the Referee's principle argument, so we list these below in case they prefer greater clarification going forward.
 
@@
 In order to avoid future confusion, we now replace 'dominant families' with 'species-rich groups'.
-We hope that this makes it clear that we are advocating researcher take a finer-scale perspective on phylogenetic signal in ecological networks.
+We hope that this makes it clear that we are advocating researchers take a finer-scale perspective on phylogenetic signal in ecological networks.
 
@@
 		\textbf{R:} The abstract/summary is under strict word limits, and we did not feel that inserting each keyword without a clear purpose could justify the elimination of other material.
-Given the Referee's confusion regarding our analyses, we are more convinced than ever that our decision to omit some keywords in favour of spending more words explaining our methodology was correct.
+		%Given the Referee's confusion regarding our analyses, we are more convinced than ever that our decision to omit some keywords in favour of spending more words explaining our methodology was correct.
 		As we do not directly test pollination or defensive syndromes, we have removed these keywords from the list.
@@
 
-	7. Mistake about the focus of the introduction
+	7. The focus of the introduction
 
@@
 Note that we also propose several others in the same paragraph where trade-offs appear, including convergent evolution or selection to avoid pollen dilution.
-We therefore disagree with the Referee's perception that we focus on compromise between pollination and herbivory.
-It is beyond the scope of this manuscript to test all possible reasons why closely-related plants might not share interaction partners.
+We therefore disagree with the Referee's perception that out primary focus is the compromise between pollination and herbivory.
+		% It is beyond the scope of this manuscript to test all possible reasons why closely-related plants might not share interaction partners.
 		This material is intended solely as background for readers who may not be familiar with arguments against the phylogenetic conservation of interaction partners.
+We have reviewed the text in question to reassure ourselves that this is the tenor of our discussion.
 
@@
 We do not make any claim as to whether the putative pollination syndromes actually reflect plants with common sets of pollinators (the evidence we are aware of is rather mixed).
-Since the Referee appears to object to this idea (which we note is quite common in the literature surrounding phylogenetic conservation of interactions), and because syndromes do not form a major part of our analysis, we have removed it as a keyword and rephrased our introduction so that it now no longer references pollination syndromes.
-Hopefully this will help readers to take our manuscript on its own merits rather than those of the syndrome concept.
+Since the Referee appears to object to this idea (which we nevertheless note is quite common in the literature surrounding phylogenetic conservation of interactions), and because syndromes do not form a major part of our analysis, we have removed it as a keyword and rephrased our introduction so that it now no longer references pollination syndromes.
+Hopefully this will help readers to evaluate our manuscript on its own merits rather than those of the syndrome concept.
 
@@
 
-	10. Criticism of dataset changes required by previous reviewers
+	10. Criticism of dataset %changes required by previous reviewers
 
@@
 		\textbf{R:} We included all herbivory networks we could find when we began this project, and only restricted our selection of herbivory networks in response to a previous round of review.
-Without more details why (or if) the Referee believes that the herbivory networks we removed should be included, we have opted to continue following that earlier feedback.
-We would have appreciated specific tips for additional herbivory networks, but since the Referee does not provide any specifics we do not feel that conducting an extensive search for additional networks and repeating our analyses is viable within the timeframe given to respond to this review.
+Without more details regarding why (or if) the Referee believes that the herbivory networks we removed should be included, we have opted to continue following that earlier feedback.
+We would have appreciated specific tips pointing us toward additional herbivory networks, but lacking this information we concluded that  conducting a further search for additional networks and repeating our analyses was un-viable within the timeframe given to respond to this review.
 
@@
 
-		\textbf{R:} We did use a Jaccard index, as stated in the first  sentence under the sub-heading \textbf{Calculating niche overlap between communities} in the previous revision.
+		\textbf{R:} We apologize for any confusion here, as we did in fact use a Jaccard index, as stated in the first  sentence under the sub-heading \textbf{Calculating niche overlap between communities} in the previous revision.
 This line read as follows (emphasis added):
@@
 
+		%DBS: I think your interpretation is incorrect here.
+I believe that they are referring to the fact that species with many interactions have a greater chance of "strong" overlap than species with few interactions.
+Either way though, I don't think this can be operationalized because each pairwise overlap value is tied to two species and not one (and that isn't tractable, in a way that I can think of...).
+
 		\textbf{R:} It sounds as though the Referee would like us to include plant species as a predictor in our regressions.
@@
 		\textbf{R:} Our main reason for including network size as a potential effect was methodological rather than biological - slopes for smaller networks are based on smaller sample sizes and therefore may be less robust.
-We do not see either the methodological or biological arguments for including connectance as a predictor.
-We also note that the manuscript is already quite full, so including these new analyses would require us to remove something more important.
+In contrast, we were unable to determine among ourselves what the methodological or biological arguments would be for including connectance as a predictor
+		We also note that the manuscript is already quite full, so including these new analyses would require us to remove which we and other Referees have regarded as more important.
 Without a justification from the Referee as to why connectance should affect pairwise niche overlap, we have opted not to add this new thread to the manuscript.
+		% DBS: This probably isn't true. If connectance were 0 there would be no overlap and if it were 1 overlap would be perfect. They probably think it sets a useful baseline. (?)
 
@@
 Note that we cannot use Shannon diversity within networks as we do not know the abundances of the various plant species.
-All we can do is test the effect of numbers of species as described above.
+All we can do is test the effect of richness as described above.
 
@@
 		\textbf{R:} We are unsure whether the Referee is giving general advice here or if there is a specific element of the results the Referee feels would fit better in the discussion.
-We thank the Referee for the advice but can take little practical action without more details as to the nature of their objection.
-
-	17. Incorrect claim that beginning of results is inaccurate
+We have revised the results as best we can to avoid text which could be misconstrued as discussion.
+		%We thank the Referee for the advice but can take little practical action without more details as to the nature of their objection.
+
+	17. Claim  about accuracy of the beginning of results
 
@@
 
-		\textbf{R:} This comment's somewhat eccentric grammar makes it rather difficult to parse.
+		\textbf{R:} We were unclear regarding what and why the Referee made this comment.
 We are guessing that the Referee is confused by the overall trend (more related plants have more similar interaction partners) and the variability of the trends within specific networks.
-To help understand this, note that the structure of the first few lines of the discussion parallel the first few lines of the results.
+To help understand this, note that the structure of the first few lines of the discussion parallels the first few lines of the results.
 First we introduce the overall result, and then we expand upon the details.
@@
 For tractability, we have summarized community composition as the number of species in each plant family.
-We have added text to the methods to state this explicitly.
+We have added text to the methods to state this more explicitly.
 
@@
 
+	    %DBS: To be fair, I think this might still lack detail.
+When we say "differences in the composition" in the last sentence, should be say "beta-diversity metric X comparing the family-wise composition of the two networks?"
+
 	19. Confusion about permutation methodology
@@
 
-		\textbf{R:} We have reordered the tables and added a redundant reference to Fig. 3.
+		\textbf{R:} We have reordered the tables and added a second reference to Fig. 3.
 
@@
 
-		\textbf{R:} We do include ideas about evolution and coevolution in our discussion.
+		\textbf{R:} %We do include ideas about evolution and coevolution in our discussion.
 		We completely agree that, together with ecological processes and environmental filtering, evolution and coevolution are very important in structuring networks at every level, from pairs of species to entire communities.
@@
 		Some examples of evolutionary ideas in the discussion:
+
+		% DBS: Aren't you just beating a dead horse below with all the examples?
+Couldn't a list of the line numbers be sufficient?
+If I were this reviewer, this would piss me off.
+Though you might not like them, I seriously doubt that is the image or result you wish to project...
 
@@
 
-		\textbf{R:} Note that 56\% is greater than half, and that when all networks were considered together we also observed the same trends.
-We contend that these two facts do represent broad support for our hypothesis and note that the Hembry et al reference suggested by the Referee uses the word in a very similar way.
+		% DBS: Again, do you really want to pick a fight that is a matter of splitting hairs? Why die in a ditch over our use of the term broad?
+
+		\textbf{R:} When all networks were considered together, we observed the same trends.
+Moreover, 56\% is both (i) greater than half and (ii) much greater than one would expect if the result occurred purely by chance (5\%).
+Putting this all together, we contend that these two facts do represent broad support for our hypothesis.
+		%and note that the Hembry et al reference suggested by the Referee uses the word in a very similar way.
 		Broad support is not, of course, universal support.
-That is why we provide the numbers of networks.
-Readers are thereby armed with the tools to agree or disagree with our choice of words.
-In case it is the synonymy between broad and general that has perplexed the Referee, we have changed this line to state ''We found \emph{general} support...''.
+This is why we provide the numbers of networks, thereby allowing readers to agree or disagree with our choice of words.
+In case it is the synonymy between broad and unambiguous that has perplexed the Referee, we have changed this line to state ''We found \emph{general} support...''.
 We hope that this is clearer.
+		% DBS: If you want to go down this line of argument, I would just leave it as broad....
 
@@
 
-	26. Confusing complaint about subsetting herbivory networks or perhaps objection to the claim that oligotrophy is common
+	26. Complaint about subsetting herbivory networks or perhaps objection to the claim that oligotrophy is common
 
@@
 These measures indicate that many herbivores in our networks do, in fact, consume only a few of the plants available to them (with some highly generalist species increasing the means).
-Our overall point, that oligotrophy may be common in herbivores, therefore stands.
+Our overall point, that oligotrophy may be common in herbivores, therefore likely stands.
 
@@
 		\end{refquote}
+
+		% DBS: Tone it down!
+There is *nothing* to be gained from the response below.
+It would be easier and more prudent to just say that taxonomy is an imperfect proxy of phylogeney and yes, sometimes taxonomic congeners might actually be more distant phylogenetically though on the whole the match is pretty damn good.
 
@@
 
-	28. Another demand to discuss intimacy [[done. Look for more places to scattershot Hembry]]
+	28. Request to discuss intimacy [[done. Look for more places to scattershot Hembry]]
 
@@
 		\textbf{R:} We do not believe that interaction intimacy has a strong effect on our results, as both leaf-chewing herbivory and pollination are low-intimacy interactions~\citep{Astegiano2017}.
-It is possible that there is variation in intimacy within these broad categories, but we do not have data that would allow us to test such a hypothesis.
+It is possible that there is variation in intimacy within these broad categories, but we unfortunately do not have data that would allow us to test such a hypothesis.
 We also note that~\citet{Hembry2018} study a very small and high-intimacy system (a single genus of brood pollinating moths and their single genus of host plants).
-Their results will therefore not necessarily generalize to the larger, more diverse networks we consider.
+Their results will therefore not necessarily generalize to the larger, more diverse networks we consider here.
 Indeed, had they considered a broader sample of plants and seed predators or herbivores from the same islands, they easily could have found less reciprocal specialisation.
@@
 Moreover, they point out that the support for the intimacy hypothesis  in their system was broad (in the same sense we used the word) but equivocal.
-This exacerbates the difficulty of extrapolating their work to explain our results.
+This exacerbates the difficulty we found in extrapolating their work to explain our results.
 
 		Given all of the above, it is hard to see how the interaction intimacy hypothesis relates to these lines (which are about whether the number of species in different plant families is related to the strength of phylogenetic signal).
-Instead, we feel that a discussion of the possible effects of intimacy is more relevant later on, where we discuss possible reasons why some families may show different trends.
+Instead, we felt that a discussion of the possible effects of intimacy was more relevant later on, where we discuss possible reasons why some families may show different trends.
 This section (lines 443-454) now reads:

### 2019-12-09 manuscript/reply_to_referees_njb_edits.tex
trying to be nicer to the idiot reviewer

--- 2019-11-30 manuscript/reply_to_referees_2.tex
@@
 
-	We are pleased to submit a revised version of our manuscript, NPH-MS-2019-30803.
-In response to a suggestion from Referee 3, we have re-titled it "".
-We have also taken care to revise our methods section in response to the many helpful suggestions from Referee 4, and hope that our approach is now clearer.
-Finally, we have expanded the discussion to include some additional concepts suggested by Referees 2 and 4, and a possible application of our research suggested by Referee 3.
-
 Given the difference of opinion between Referees 1, 3, and 4 and Referee 2, we have prioritised adjusting the manuscript according to the majority view.
-We must also admit to having some difficulty parsing a number of Referee 2's comments in order to find what is being asked.
-This may be partly because this review came from several people - the Referee refers to themselves as 'we' several times, and the writing appears to be more than usually variable within their comments.
-These difficulties mean that we may not have followed as many of Referee 2's suggestions as we have for the other Referees.
-Nevertheless, we do appreciate their time and effort in offering such extensive feedback and have taken care to address each of Referee 2's comments in the hope of at least clarifying our perspective.
-
-	We appreciate all of the Referees' comments and are confident that our manuscript is all the stronger for responding to them.
+Nevertheless, we have taken care to address each of Referee 2's comments and, where possible, have used them to improve the manuscript.
 
@@
 
-% NPH-MS-2019-30803 At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families.
-% by Cirtwill, Alyssa; Dalla Riva, Giulio; Baker, Nick; Ohlsson, Mikael; Norström, Isabelle; Wohlfarth, Inger-Marie; Thia, Josh; Stouffer, Daniel
-
-% Dear Dr Cirtwill
-
-% I write you in regard to your submitted manuscript, NPH-MS-2019-30803 "At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families.”, which has now been reviewed.
+NPH-MS-2019-30803 At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families.
+by Cirtwill, Alyssa; Dalla Riva, Giulio; Baker, Nick; Ohlsson, Mikael; Norström, Isabelle; Wohlfarth, Inger-Marie; Thia, Josh; Stouffer, Daniel
+
+Dear Dr Cirtwill
+
+I write you in regard to your submitted manuscript, NPH-MS-2019-30803 "At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families.”, which has now been reviewed.
 We found four reviewers (some original reviewers and some new) and they all generally enjoyed your revised manuscript.
@@
 
-% Although resolving these issues will require some restructuring, I think you should be able to handle these suggestions through revision (see below) and, ultimately, this manuscript will make a nice contribution to the literature.
-
-% Please carefully revise your manuscript and resubmit your revised version within 4 weeks. Please also include a summary of how you have incorporated the suggestions of the reviewers.
-
-% Thank you for submitting your work to New Phytologist.
-
-% Sincerely,
-
-% Jana Vamosi
-
-% Editor, New Phytologist
-
-% Decision: Accept subject to revision
+Although resolving these issues will require some restructuring, I think you should be able to handle these suggestions through revision (see below) and, ultimately, this manuscript will make a nice contribution to the literature.
+
+Please carefully revise your manuscript and resubmit your revised version within 4 weeks. Please also include a summary of how you have incorporated the suggestions of the reviewers.
+
+Thank you for submitting your work to New Phytologist.
+
+Sincerely,
+
+Jana Vamosi
+
+Editor, New Phytologist
+
+Decision: Accept subject to revision
 
@@
 	\begin{refquote}
-	General comments\\
+	General comments
 
@@
 
-	The Referee(s?) seems to view our basic question and analyses positively, but is rather bluntly critical of our writing in terms of logical, clarity, and style.
-Some of these criticisms seem to reflect a rather hasty reading of the manuscript, as there are points where the Referee asks for analyses or ideas to be included which already appear in the text.
+	The Referee seems to view our basic question and analyses positively, but is critical of our writing in terms of logic, clarity, and style.
+We were confused by some of these criticisms as there are points where the Referee asks why we did not conduct analyses that we did in fact perform or asks that we address biological complications that already appear later in the text.
 In these cases, we point to existing evidence in the manuscript and have tried to make these connections more obvious.
-In a few cases, we struggled to understand the nature of the Referee's objections.
-We have attempted to address each of the Referee's comments in detail below (preceded by \textbf{R:}).
-Wherever possible, we have clarified our text in response to the Referee's comments.
-In particular, we now define community composition more explicitly, have revised the discussion to be more explicit about whether we are referring to overall or within-network trends, and have removed specific phrases that the Referee finds objectionable \emph{prima facie}.
-We hope that these changes and our response will clarify the focus and scope of our analyses.
+We address the Referee's other comments in detail below (preceded by \textbf{R:}).
+We hope that this response will clarify the focus and scope of our analyses.
 
@@
 
-		\textbf{R:} As Referees 1 and 3 note, our English is scrupulously correct.
-Of course technical correctness does not necessarily imply clarity of expression, and we apologise if our choice of vocabulary has obfuscated some of the nuances of the manuscript.
-We have endeavoured to clarify the manuscript as the Referee suggests.
+		\textbf{R:} We acknowledge that our choice of vocabulary or phrasing may have obfuscated some of the finer points of the manuscript.
+As such, we have endeavoured to clarify the manuscript as the Referee suggests.
 
@@
 		\begin{refquote}
-		Specific comments\\
-		Title\\
+		Specific comments
+		Title
 		Your title still lacks clarity and does not reflect the main message you state at the beginning of your discussion (in the first sentence of it you state that you found broad support for the hypothesis that more closely related plants tend to have more niche overlap).
@@
 
-		\textbf{R:} We have revised the title following a more detailed suggestion by Referee 3 and hope that the new title no longer implies logical inconsistency.
+		\textbf{R:} We have revised the title following a more detailed suggestion by Referee 3 and believe that the new title provides additional logical consistency.
 
@@
 		\begin{refquote}
-			Summary\\
-			General comments\\
+			Summary
+			General comments
 			Your summary is too methodologically-oriented.
@@
 
-	4. Mis-understanding of purpose and scope of within-family analyses
+	4. Persistent mis-understanding of purpose and scope of within-family analyses
 
@@
 
-		\textbf{R:} The Referee is correct about our hypothesis but appears to have assumed that we are \emph{only} searching for conservation of niche overlap within families.
-In fact, point 2 of the summary lists three separate analyses: testing for relationships between phylogenetic distance and partner overlap in \emph{all pairs of plants in a network, regardless of family}, testing whether the slopes of these whole-network relationships are related to the composition of the plant community in each network, and, as a supplement to these analyses, testing whether the slopes of these relationships differ if we consider only pairs of plants within the same family.
-We now number these three different analyses to avoid any further confusion.
-
-		In this context, checking for different relationships within families is similar to checking for different relationships between networks - an overall trend can mask a great deal of variability, and we wanted to make sure this variability was identified.
-We chose families as the taxonomic level for further analysis because many plant families are quite diverse, both in terms of numbers of species and in terms of phenotypes/interaction partners (see e.g., Wilson on plants and insect/bird pollinators).
-Within a single family, plants can show evidence of adaptive radiations, heterogeneous selection, both, or neither.
-The Referee themself points out that some families can show both bird and bee pollination syndromes (see response \#8), and we can also point to papers such as Bernhardt 2000 and Johnson \& Jurgens 2010 which address trait lability, convergent evolution, and adaptive radiation.
-These different possibilities mean that it is not clear whether all families will show phylogenetic conservation of interaction partners.
-		We have added a summary of this explanation to the methods.
-
-		Lines 252-257:
-
-		\begin{quotation}
-
-			Finally, we compared the breakdown of niche overlap in different plant families.
-		    Within-family genetic and trait diversity can be high due to adaptive radiations, heterogeneous selection, and other influences on different species. 
-		    Plant families offer a reasonable balance between collecting enough species to identify meaningful trends and maintaining a tractable number of analyses. 
-		    They are therefore the best taxonomic level to investigate phylogenetic conservation in more detail across our large dataset.
-
-		\end{quotation}
+		\textbf{R:} This comment indicates that the Referee has fundamentally misunderstood our manuscript based on the summary.
+Point 2 of the summary lists three separate analyses: testing for relationships between phylogenetic distance and partner overlap in \emph{all pairs of plants in a network, regardless of family}, testing whether the slopes of these whole-network relationships are related to the composition of the plant community in each network, and, as a supplement to these analyses, testing whether the slopes of these relationships differ if we consider only pairs of plants within the same family.
+We now number these three different analyses to avoid confusion.
 
 		As we are \emph{not} searching for differences between communities at the family level, but rather at all levels within the angiosperms, a number of the Referee's comments do not apply.
-We list these below.
+For example, the comments below:
 
@@
 
-	5. Very confusing comment complaining about summary point 4
-
-		\begin{refquote}
-		4st paragraph "Considering factors affecting the dominant plant families within
+	5. Very confusing comment referencing paragraph 4
+
+		\begin{refquote}
+		4th paragraph "Considering factors affecting the dominant plant families within
 		a community may be the key to understanding the distribution of interactions." So, relationships are more functional?
@@
 
-		\textbf{R:} Apart from the Referee's objection to plant families as units for detailed analysis (see respons \#4), this comment seems to demonstrate uncertainty about how we defined the dominant plant families in a community.
-Note that we do not mean to imply any functional argument here, as our manuscript does not address functionality.
-Rather, by 'dominant', we mean 'most species-rich in the focal community'.
+		\textbf{R:} The Referee appears to object to any reference to plant families, but has not made the reasons for this objection clear.
+As noted above, we do in fact consider relationships between phylogenetic distance and interaction partner overlap at \emph{all} taxonomic levels, not just within families.
+Apart from this, we are confused by the remainder of the Referee's comment.
+By 'dominant', we mean 'most species-rich in the focal community' rather than any kind of functional interpretation.
+Note that we do not address functions in the rest of the manuscript, so it is not clear why the Referee makes this leap.
 In order to avoid future confusion, we now replace 'dominant families' with 'species-rich groups'.
-We hope that this makes it clear that we are advocating researcher take a finer-scale perspective on phylogenetic signal in ecological networks.
+We hope that this makes it clear that we are advocating research that takes a finer-scale perspective on phylogenetic signal in ecological networks.
 
@@
 
-	6. Complaint about keywords absent from the abstract
-
-		\begin{refquote}
-		Keywords\\
+	6. Comment about keywords absent from the abstract
+
+		\begin{refquote}
+		Keywords
 		Syndrome:  Why you do not mention such theory in your abstract?
@@
 		\textbf{R:} The abstract/summary is under strict word limits, and we did not feel that inserting each keyword without a clear purpose could justify the elimination of other material.
-Given the Referee's confusion regarding our analyses, we are more convinced than ever that our decision to omit some keywords in favour of spending more words explaining our methodology was correct.
+Given the Referee's confusion regarding our analyses, we are more convinced than ever that our decision to omit some keywords (which do appear in the introduction) in favour of spending more words explaining our methodology was correct.
 As we do not directly test pollination or defensive syndromes, we have removed these keywords from the list.
-In response to the Referee's further objections to the syndrome literature, below, we have also removed these terms from the introduction.
 
@@
 		\begin{refquote}
-		Introduction\\
+		Introduction
 		General. You focus on the compromise between pollination and herbivory interactions but then you do not use this approach in your analyses.
@@
 		\textbf{R:} Potential tradeoffs between encouraging interactions with pollinators and discouraging herbivores are just one of the possible reasons why networks may not display the expected relationship between relatedness and niche overlap.
-Note that we also propose several others in the same paragraph where trade-offs appear, including convergent evolution or selection to avoid pollen dilution.
+Note that we also propose several others in the same paragraph, including convergent evolution or selection to avoid pollen dilution.
 We therefore disagree with the Referee's perception that we focus on compromise between pollination and herbivory.
@@
 
-		\textbf{R:} As the Referee notes, we do address the possibility of convergence in our introduction.
+		\textbf{R:} As the Referee notes, we do address the possibility of convergence later in our introduction.
 We do not make any claim as to whether the putative pollination syndromes actually reflect plants with common sets of pollinators (the evidence we are aware of is rather mixed).
-Since the Referee appears to object to this idea (which we note is quite common in the literature surrounding phylogenetic conservation of interactions), and because syndromes do not form a major part of our analysis, we have removed it as a keyword and rephrased our introduction so that it now no longer references pollination syndromes.
-Hopefully this will help readers to take our manuscript on its own merits rather than those of the syndrome concept.
-
-		Lines 11-14:
+Since the Referee appears to object to this very common idea in the literature, and because syndromes do not form a major part of our analysis, we have removed it as a keyword and rephrased our introduction.
+Our manuscript no longer references pollination syndromes.
+Hopefully this will avoid other readers becoming distracted by the idea of syndromes.
+
+		Lines XX-XX:
 
@@
 
-	9. Request to include interaction intimacy
+	9. Request to include interaction intimacy [[done]]
 
@@
 
-		\textbf{R:} We have no information on interaction strengths or intimacies, and we note that the interactions we consider are generally low-intimacy.
-We therefore would not expect intimacy to strongly affect these networks.
+		\textbf{R:} We have no information on interaction strengths or intimacies, and so cannot test whether this is affecting our results.
 However, we are happy to include the idea as yet another reason why plant communities may or may not show conservation of interactions.
@@
 
-		Lines 29-37:
+		Lines XX-XX:
 
@@
 In antagonistic networks, however, actively-foraging consumers tend to show less phylogenetic signal than their prey~\citep{Ives2006,Cagnolo2011,Naisbit2011,Fontaine2015}.
-In part, this may be related to different degrees of interaction intimacy (dependence of one partner on another), which appears to contribute to network structure in mutualistic, but not antagonistic, networks~\citep{Guimaraes2007,Ponisio2017}.
-
-		\end{quotation}
-
-		In addition to the above, we have added another brief discussion of intimacy in the discussion (see response \#28)
-
-	10. Criticism of dataset changes required by previous reviewers
-
-		\begin{refquote}
-		Methods\\
-		Dataset\\
+In part, this may be related to different degrees of interaction intimacy (dependence of one predator on another), which appears to contribute to network structure in mutualistic, but not antagonistic, networks~\citep{Guimaraes2007,Ponisio2017}.
+
+		\end{quotation}
+
+	10. Criticisism of methodological changes required by previous reviewers
+
+		\begin{refquote}
+			Methods
+			Dataset
 			Several networks can be reviewed in the literature or are available in different websites.
@@
 
-		\textbf{R:} We included all herbivory networks we could find when we began this project, and only restricted our selection of herbivory networks in response to a previous round of review.
-Without more details why (or if) the Referee believes that the herbivory networks we removed should be included, we have opted to continue following that earlier feedback.
-We would have appreciated specific tips for additional herbivory networks, but since the Referee does not provide any specifics we do not feel that conducting an extensive search for additional networks and repeating our analyses is viable within the timeframe given to respond to this review.
-
-	11. Request to change "insects consuming leaves" to "chewing insects"
+		\textbf{R:} We restricted our selection of herbivory networks in response to a previous round of review.
+Without more details on why (or if) the Referee believes that the herbivory networks we removed should be included, we have opted to continue following that earlier feedback.
+We would have appreciated specific examples for additional herbivory networks, but since the Referee does not provide any specifics there is little we can do to address this comment.
+
+	11. Request to change "insects consuming leaves" to "chewing insects" [[done]]
 
@@
 
-	12. Recommendation to continue using Jaccard dissimilarity, binomial regression
-
-		\begin{refquote}
-			Measuring niche overlap\\
+	12. Recommendation to continue using the same methodology
+
+		\begin{refquote}
+			Measuring niche overlap
 			Why you used absolute numbers to measure shared and unshared pollinators and not the Jaccard index?
@@
 
-		\textbf{R:} We did use a Jaccard index, as stated in the first  sentence under the sub-heading \textbf{Calculating niche overlap between communities} in the previous revision.
-This line read as follows (emphasis added):
-		\begin{quotation}
-		We calculated niche overlap for each pair of species within a community \emph{using a Jaccard index} to describe the number of shared interaction partners, augmented with the number of interaction partners which were not shared.
-		\end{quotation}
-
+		\textbf{R:} We did use a Jaccard index, as stated in the first and second sentences under the sub-heading \textbf{Calculating niche overlap between communities}.
 The Jaccard index is calculated using the number of shared and un-shared interaction partners for a pair of plants, as stated in equation 1.
@@
 We chose this methodology for exactly the reasons the Referee suggests, to give more weight to generalists sharing many interaction partners.
-This is stated in lines 138-141 and lines 148-154 (quoted below).
-Note that we have revised these lines somewhat in response to a suggestion from Referee 4, so they do differ somewhat from the previous version.
-We are glad that the Referee agrees with our choice in methodology.
-
-		\begin{quotation}
-
-			Together, $M_{ij}$ and $U_{ij}$ give a Jaccard index ($J_{ij}$) describing 
-			the proportion of shared interactions. $J_{ij}$ is defined:
-
-			\begin{equation}
-			J_{ij} = \frac{M_{ij}}{U_{ij}+M_{ij}} ,
-			\end{equation}
-			%
-			where $M_{ij}$ is the set of \emph{mutual} (shared) interaction partners and $U_{ij}$ the set of unshared interaction partners for plants $i$ and $j$.
-
-		\end{quotation}
-
-		\smallskip
-
-		\begin{quotation}
-
-			We modelled the relationship between niche overlap and phylogenetic 
-			distance using a logistic regression. We used the numbers of shared 
-			($M_{ij}$) and non-shared ($U_{ij}$) partners as dependent variables and 
-			centred, scaled phylogenetic distance as the independent variable. This 
-			approach is conceptually similar to modelling successes and failures in a 
-			binomial-distributed process. Accordingly, we assumed a binomially-distributed error structure and used a logit link function to model the dissimilarity in interaction partners 
-			$J_{ij}$ of plants $i$ and $j$.
-
-		\end{quotation}
-
-		As stated in the section on phylogenetic data, we excluded comparisons involving plants for which we could not assign a binomial names (and therefore could not obtain phylogenetic distances) and comparisons between non-angiosperms due to our coarse estimates of their ages.
-This information appeared in lines 107-110 and 118-120 of the previous version and lines 112-115 and 122-124 of the current version.
-
-	13. Request to include plant species as a fixed effect
+This is stated in lines XX-XX (quoted below).
+We are glad that the Referee agrees with our choice in methdology.
+
+		\begin{quotation}
+
+			We wished to give more 
+		    weight to species sharing a large number of interaction partners as well as 
+		    those sharing a large proportion (i.e., to emphasise pairs of generalists 
+		    sharing most of their interaction partners over specialists sharing a single 
+		    interaction partner).
+Note that species sharing a large \emph{number} of interaction partners may not share a large \emph{proportion} of interaction partners if the number of interaction partners that are not shared is also large.
+
+		\end{quotation}
+
+	13. Request to include plant species as a fixed effect [[done]]
 
@@
 		\textbf{R:} It sounds as though the Referee would like us to include plant species as a predictor in our regressions.
-Due to the fact that species generally appear in few networks (many in only a single network), this would result in near singularity of our models.
-We would therefore be completely unable to observe any patterns as species identity would explain nearly all variation in niche overlap.
+Due to the fact that individual species generally appear in few networks (many in only a single network), this would result in near singularity of our models.
+We would therefore be completely unable to observe any patterns as species identity would explain essentially all variation.
 If the Referee is referring to a potential effect of network size, we did in fact test this (see equation 4 and description).
-If the Referee did not mean either of these possibilities, we apologise but are unable to understand this comment.
-
-	14. Request to include connectance
+
+	16. Un-justified request to include connectance
 
@@
 
-		\textbf{R:} Our main reason for including network size as a potential effect was methodological rather than biological - slopes for smaller networks are based on smaller sample sizes and therefore may be less robust.
-We do not see either the methodological or biological arguments for including connectance as a predictor.
-We also note that the manuscript is already quite full, so including these new analyses would require us to remove something more important.
-Without a justification from the Referee as to why connectance should affect pairwise niche overlap, we have opted not to add this new thread to the manuscript.
-
-	15. Confusion about motivation for community composition analyses
+		\textbf{R:} We did not include connectance because we can offer no justification (biological or methodological) why the overall connectance of the network should affect the strength of the relationship between relatedness and niche overlap.
+It is possible that there might be an effect of connectance on the intercept of this relationship (as we would expect higher overlap in general when connectance is high), but we see no particular reason why connectance should change how closely-related species differ from distantly-related species in the same network.
+Since the Referee also does not provide any reasoning behind this request, we have opted to leave our analyses as-is.
+
+		[[Maybe I can add a bit of a biological argument that network size can affect overlap? I'm not sure what methodological but not biological means here.]]
+
+		\textbf{Nick:} I'm super confused by this comment as well.
+R2 seems to want more information about connectance but then complains about the lack of biological arguments for network size and niche overlap.
+I think if you have something you can mention about the biological argument you can mention it but anything you add here addressing this comment we may need to add to the manuscript unless you can phrase it in a way that indicates its somewhat ridiculous to mention and wouldn't contribute to the paper but still explains why we left it out.
+I was also trying to wrack my brain about connectance affecting the strength of the relationship between relatedness and niche overlap...
+I feel like if we start going into detail about connectance and how that plays you would have a stronger argument talking about modularity / nestedness instead because at least those two measurements indicate differences in interactions; but that is way outside the scope of this paper.
+
+	17. Confusion about motivation for community composition analyses
 
@@
 We now explicitly state this in the introduction.
-Note that we cannot use Shannon diversity within networks as we do not know the abundances of the various plant species.
-All we can do is test the effect of numbers of species as described above.
-
-		Lines 78-86:
+
+		Lines XX-XX:
 
@@
 		  pairs of plants (henceforth ``niche overlap'') varies over 
-			phylogenetic distance. 
+		  phylogenetic distance and how this differs between plant families. 
 		  Whereas previous 
@@
 		  relates to network structure.
-As different plant families (which represent tractable clades for analysis) may have experienced different degrees of coevolution, convergence, etc., we also complement analyses with entire networks with comparisons among plants in the same family within a network.
+As different plant families may have experienced different degrees of coevolution, convergence, etc., we also complement analyses with entire networks with comparisons among plants in the same family within a network.
 		  This novel perspective allows us to investigate the relationship between phylogenetic distance and partner overlap at different scales.
@@
 
-	16. Critique of manuscript structure
-
-		\begin{refquote}
-			Results\\
+	18. Critique of manuscript structure
+
+		\begin{refquote}
+			Results
 			General: Please, do not include discussion in your results, it may confound readers.
@@
 
-		\textbf{R:} We are unsure whether the Referee is giving general advice here or if there is a specific element of the results the Referee feels would fit better in the discussion.
-We thank the Referee for the advice but can take little practical action without more details as to the nature of their objection.
-
-	17. Incorrect claim that beginning of results is inaccurate
+		\textbf{R:} Without knowing where, specifically, the Referee feels that we have included discussion in our results there is little we can do to address this complaint.
+
+	19. Incorrect claim that beginning of results is inaccurate
 
@@
 
-		\textbf{R:} This comment's somewhat eccentric grammar makes it rather difficult to parse.
-We are guessing that the Referee is confused by the overall trend (more related plants have more similar interaction partners) and the variability of the trends within specific networks.
-To help understand this, note that the structure of the first few lines of the discussion parallel the first few lines of the results.
-First we introduce the overall result, and then we expand upon the details.
-We have lightly edited lines 370-373 to make this clearer:
-
-		\begin{quotation}
-
-			We found general support for the hypothesis that more
-			closely-related pairs of plants have a higher degree
-			of niche overlap. Taking all networks together, 
-			the probability of two plants sharing the same animal 
-			interaction partners decreased with increasing 
-			phylogenetic distance. Considering networks separately ...
-
-		\end{quotation}
-
-	18. Definition of community composition unclear
+		\textbf{R:} It is not clear whether the Referee is suggesting that we repeat our analyses using half of the pollination networks (without any clear reason as to why) or is simply confused about which analysis these results refer to.
+Since the Referee appears to have assumed that the within-family analyses are the \emph{only} analyses in the manuscript, the latter seems likely.
+
+		Note that the results in lines XX-XX correspond to our first analysis: testing whether niche overlap decreases over increasing phylogenetic
+		distance in a large dataset of pollination and herbivory networks.
+The overall regression did show that partner overlap decreases with increasing phylogenetic distance, so that more distantly-related plants are less likely to share interaction partners (see Fig.
+1).
+The rest of this section gives more details about the differences between pollination and herbivory networks (lines XX-XX) and variation across networks (lines XX-XX), but note that none of these details change the overall regression.
+As this text is correct we have left it unchanged.
+
+	20. Definition of community composition unclear
 
@@
 For tractability, we have summarized community composition as the number of species in each plant family.
-We have added text to the methods to state this explicitly.
-
-		Lines 224-233:
+We have added text to the methods to state this more obviously.
+
+		Lines XX-XX:
 
@@
 		    varying relationships between phylogenetic distance and
-			niche overlap are due to the different distributions 
+		    pairwise niche overlap are due to the different distributions 
 		    of families across networks. We defined the relationship between
@@
 		    a single network). We then related differences in this relationship
-			to differences in the composition of the plant community 
-			using a non-parametric permutational multi-variate 
+		    to differences in the composition of the plant community (defined as the number of species in each plant family present in each network) using a non-parametric permutational multi-variate 
 		    analysis of variance (PERMANOVA;~\citealp{Anderson2001}).
@@
 
-	19. Confusion about permutation methodology
+	21. Confusion about permutation methodology
 
@@
 
-		\textbf{R:} As stated in the methods, we permuted interactions.
-Note that, in statistical terms, the two approaches are equivalent, but we appreciate that this may not be clear to readers unfamiliar with permutation approaches.
-We have rephrased the results to match the methods.
-
-	20. Typo in Fig. 1 caption
+		\textbf{R:} As stated in the methods, we permuted interactions. Note that, in statistical terms, the two approaches are equivalent. We have rephrased the results to match the methods.
+
+	22. Typo in Fig. 1 caption
 
@@
 
-	21. Difference between minimum and maximum slopes not visible
+	23. Difference between minimum and maximum slopes not visible
 
@@
 
-	22. Confusion about line 328
+	24. Confusion about line 328
 
@@
 
-		\textbf{R:} Yes, 12 is the number of families.
-We have revised the line to make this more explicit.
-Note that we have also corrected this line to match Table 1, which includes 14 significant families.
-
-		Lines 355-356:
-
-		\begin{quotation}
-
-		In pollination networks, overlap decreased significantly with increasing phylogenetic distance in 14 of the 48 well-represented families (Table 1; Fig. 3).
-
-		\end{quotation}
-
-	23. Complaints about table numbering and figure referencing
+		\textbf{R:} The number 12 referred to the number of families. We have revised this line to make this more explicit.
+
+		Lines XX-XX:
+
+		\begin{quotation}
+
+		In pollination networks, overlap decreased significantly with increasing phylogenetic distance in 12 of the 48 well-represented families
+
+		\end{quotation}
+
+	25. Complaints about table numbering and figure referencing
 
@@
 
-	24. Suggestion to include ideas about evolution and coevolution
+	26. Request for more evolution content
 
@@
 		\textbf{R:} We do include ideas about evolution and coevolution in our discussion.
-We completely agree that, together with ecological processes and environmental filtering, evolution and coevolution are very important in structuring networks at every level, from pairs of species to entire communities.
+We agree that, together with ecological processes and environmental filtering, evolution and coevolution are very important in structuring networks.
 However, since we do not have trait or genetic data for our networks, we cannot comment with any certainty on which of our results are due to trait plasticity or environmental influence and which are due to evolution.
-We therefore mention possible evolutionary and ecological explanations together.
-
-		Some examples of evolutionary ideas in the discussion:
-
-		Lines 413-418:
+Specialists, for example, could have co-evolved with particular interaction partners.
+They could also, however, be able to interact with more species which simply do not appear in the study site due to competition, unsuitable soil conditions, etc.
+As Referee 4 notes, specialists may also simply be species which were sampled more rarely.
+That is, we may be missing interactions involving these species which actually do occur.
+Please note that the proportion of specialists is a potential explanation for the results we observed and not a key result in itself.
+As such, we feel that spending a great deal of time trying to explain this trend would distract readers from the main message of our paper.
+
+		Note that the previous version did touch on evolutionary ideas. Some examples:
 
@@
 			  plants~\citep{Schemske1999,Gilbert2015,Ponisio2017}. The degree of 
-			heritability of key traits may, however, differ between families.
-
-		\end{quotation}
-
-		Lines 420-427:
-
-		\begin{quotation}
-
-			This could indicate different 
-			rates of phenotypic drift or evolution in different families (or their interaction partners). 
+			  heritability of key traits may, however, differ between families. In
+			  some families, such as \emph{Asteraceae} in pollination networks, 
+			  the positive slope of this relationship was very shallow while in 
+			  others, such as \emph{Melastomataceae} in herbivory networks, the 
+			  positive slope was extremely steep. This could indicate different 
+			  rates of phenotypic drift or evolution in different families. 
 			  In other families, there was no significant relationship between phylogenetic
-			distance and niche overlap. In these cases, key traits affecting 
-			plant-insect interactions may be highly labile or plastic (environmentally determined).
-These possibilities are supported by several studies showing a stronger relationship between niche overlap and trait similarity than niche overlap and phylogenetic similarity~\citep{Junker2015,Ibanez2016,Endara2017}.
-
-		\end{quotation}
-
-		Lines 432-437:
-
-		\begin{quotation}
-
-			First, part of the family may have recently 
-			undergone a period of rapid diversification with closely-related species 
-			developing novel phenotypes and attracting different  
-			interaction partners~\citep{Linder2008,Breitkopf2015}. Likewise, the
-			animals may have undergone an adaptive radiation to 
-			specialise on their most profitable partner~\citep{Janz2006}. 
-			Alternatively, plants in these families could have undergone convergent evolution or ancestral traits could be strongly preserved.
-
-		\end{quotation}
-
-		Lines 444-446:
-
-		\begin{quotation}
-
-			Selection to avoid 
-			competition and restrict numbers of interaction partners may lead to
-			more intimate or specialised interactions~\citep{Ponisio2017}.
-
-		\end{quotation}
-
-		Lines 458-466:
-
-		\begin{quotation}
-
-			These plants might 
-			be highly specialised on different interaction partners and therefore
-			have low overlap at all levels of relatedness. In other plant families
+			  distance and interaction partner overlap. In these cases, key traits affecting 
+			  plant-insect interactions may not be strongly
+			  conserved. Studies showing a stronger relationship between trait similarity
+			  and shared interaction partners than phylogenetic similarity and shared
+			  interaction partners suggest that traits may indeed be evolutionarily
+			  labile~\citep{Junker2015,Ibanez2016,Endara2017}.
+
+		\end{quotation}
+
+		\begin{quotation}
+
+			In other plant families
 			  with more moderate levels of specialisation, it is possible 
@@
 
-		Lines 476-482:
-
-		\begin{quotation}
-
-			This could be because of conflicting selection from pollinators and herbivores,
-			with one type of selection placing greater constraints on plant traits than the other.
-			Multiple types of interactions (e.g., pollination, herbivory, nectar robbing) 
-			and even environmental factors can influence traits such as 
-			flower colour, nectar abundance, and flowering phenology~\citep{Strauss2006}. 
-			These influences can act in the same or different directions~\citep{Strauss2006}.
-
-		\end{quotation}
-
-	25. Objection to the word "broad"
+		See also lines XX-XX, where we discuss constraints on traits. We have lightly revised these lines to reference evolution explicitly.
+
+		\begin{quotation}
+
+		 This may indicate that one type of interaction
+		  places greater evolutionary constraints upon these families than the other, 
+		  similar to the expectation that greater constraints upon consumers 
+		  than upon their resources explains the asymmetry in conservation  
+		  of interaction partners~\citep{Fontaine2015}. Plants
+		  may not be able to respond to selection on both types of interaction
+		  simultaneously because traits affecting pollination can also affect herbivory, and vice
+		  versa~\citep{Strauss1997,Strauss2002,Adler2004,Adler2006,Theis2006}.
+  		\end{quotation}
+
+	27. Objection to the word "broad"
 
@@
 
-		\textbf{R:} Note that 56\% is greater than half, and that when all networks were considered together we also observed the same trends.
-We contend that these two facts do represent broad support for our hypothesis and note that the Hembry et al reference suggested by the Referee uses the word in a very similar way.
-Broad support is not, of course, universal support.
-That is why we provide the numbers of networks.
+		\textbf{Nick:} I think they are suggesting that our evidence was only in 55(6?)\% of our plant-pollinator networks and not in our other network types, thus ''almost half ''.
+However I agree that our results still show broad support.
+
+		\textbf{R:} We note that 56\% is greater than half of those networks, and that when all networks were considered together we also observed the same trends.
+We contend that these two facts do represent broad support for our hypothesis.
+It is not, of course, universal support.
+That is why we A) did not claim universal support and B) provide the numbers of networks.
 Readers are thereby armed with the tools to agree or disagree with our choice of words.
-In case it is the synonymy between broad and general that has perplexed the Referee, we have changed this line to state ''We found \emph{general} support...''.
+In an effort to be as unbiased as possible while discussing our results, we have changed this line to state ''We found \emph{general} support...''.
 We hope that this is clearer.
 
-		We are glad that the Referee finds the greater proportion of significant herbivory networks interesting.
-With the unbalanced sample sizes of pollination and herbivory networks, however, we are somewhat reluctant to make much of the difference between 56\% and 64\%.
+		With the unbalanced sample sizes of pollination and herbivory networks, we are reluctant to make much of the difference between 56\% of pollination networks and 64\% of herbivory networks.
 We consider that the important point here is that networks are more likely than not to show decreasing niche overlap with increasing phylogenetic distance.
 
-	26. Confusing complaint about subsetting herbivory networks or perhaps objection to the claim that oligotrophy is common
+	28. Question about subsetting herbivory networks or perhaps objection to the claim that oligotrophy is common
 
@@
 We are therefore reluctant to reconsider this approach without a very good reason.
-
 Beyond that, it is very difficult to work out exactly what the Referee objects to in this sentence.
@@
 We have therefore replaced this reference.
-We hope that this improved selection of references will help the Referee's confusion.
-
-		If the Referee objects to our finding that the herbivores in our networks tended to consume more than one plant species, there is little we can do about it. That is simply what our data say.
+
+		If the Referee objects to our finding that the herbivores in our networks tended to consume more than one plant species, there is little we can do about it.
+That is simply what our data say.
+We do not feel that it is appropriate to look for explanations in the trends we observe in our networks in other types of networks.
 
 		If the Referee is contending that, because of the multiple herbivore types in~\citet{Novotny2005}, we cannot claim that the herbivores in our dataset are oligotrophs, we can respond with further details.
-The mean number of plants consumed per herbivore ranged between 1.64 and 14.9 across networks, with a mean of 6.36, and the median ranged between 1 and 11.5 (mean 4.68).
-These measures indicate that many herbivores in our networks do, in fact, consume only a few of the plants available to them (with some highly generalist species increasing the means).
-Our overall point, that oligotrophy may be common in herbivores, therefore stands.
-
-	27. Claims that congeneric species are not closely related
+The mean number of plants consumed per herbivore ranged between 1.64 and 14.9 across networks, with a mean of 6.36, and the median ranged bewteen 1 and 11.5 (mean 4.68).
+These measures indicate that many herbivores in our networks do, in fact, consume only a few of the plants available to them.
+
+	29. Claims that congeneric species are not closely related
 
@@
 
-		\textbf{R:} Does the Referee really mean to suggest that plants in the same genus are generally less closely-related than plants in different families?
-Without some sources to substantiate this, we find this claim very counter-intuitive.
-This is especially surprising given the Referee's insistence that we should expect similar interaction partners within a family.
+		\textbf{Nick:} This seems like a rather unclear argument from the reviewer.
+To state that congeneric species can not be closely related is basically arguing that being closely related taxonomically does not mean that those species are closely related phylogenetically.
+However, I agree that if they are going to make a statement that powerful, they should provide references and a very clear rationale to make the requested change.
+Can we find a reference where someone else talks about taxonomic and phylogenetic relationships as we have?
+Just as a justification tool more than anything?
+
+		\textbf{R:} We are confused by this comment, is the Referee suggesting that plants in the same genus are less closely-related than plants in different families?
+This comment is surprising given the Referee's insistence that we should expect similar interaction partners within a family.
 We agree that taxonomy is only a proxy for phylogeny, but we are not aware of any evidence that it is a poor proxy.
-We also note A) that similar language is quite common in the literature and B) that across seven other reviews, no other Referee has suggested that species in the same taxonomic groups (e.g., genera) are less closely-related than species in different groups.
-Without any evidence to support this claim, we have opted not to change our text.
-
-	28. Another demand to discuss intimacy [[done. Look for more places to scattershot Hembry]]
+We note that across seven other reviews, no other Referee has commented on this.
+Based on this lack of objection and similar language throughout the literature, we have opted not to change this line.
+
+	30. Another demand to discuss intimacy [[possibly addressable, since we did add a tiny reference in intro]]
 
@@
 
-		\textbf{R:} We do not believe that interaction intimacy has a strong effect on our results, as both leaf-chewing herbivory and pollination are low-intimacy interactions~\citep{Astegiano2017}.
-It is possible that there is variation in intimacy within these broad categories, but we do not have data that would allow us to test such a hypothesis.
-We also note that~\citet{Hembry2018} study a very small and high-intimacy system (a single genus of brood pollinating moths and their single genus of host plants).
-Their results will therefore not necessarily generalize to the larger, more diverse networks we consider.
-Indeed, had they considered a broader sample of plants and seed predators or herbivores from the same islands, they easily could have found less reciprocal specialisation.
-As a detailed study of this unusual mutualism was the aim in~\citet{Hembry2018} this is not a problem for their work, but we are hesitant to infer too strong a relationship between their findings and ours.
-
-		This reference suggestion is also somewhat confusing as~\citet{Hembry2018} did not find evidence for host-associated differentiation in their moths.
-This would seem to undermine the idea that evolution/coevolution can explain network structure.
-Moreover, they point out that the support for the intimacy hypothesis  in their system was broad (in the same sense we used the word) but equivocal.
-This exacerbates the difficulty of extrapolating their work to explain our results.
-
-		Given all of the above, it is hard to see how the interaction intimacy hypothesis relates to these lines (which are about whether the number of species in different plant families is related to the strength of phylogenetic signal).
-Instead, we feel that a discussion of the possible effects of intimacy is more relevant later on, where we discuss possible reasons why some families may show different trends.
-This section (lines 443-454) now reads:
-
-		\begin{quotation}
-
-			Indeed, animal pollination and seed dispersal have been shown to act
-			as filters for several plant clades~\citep{Mayfield2009}. Selection to avoid 
-			competition and restrict numbers of interaction partners may lead to
-			more intimate or specialised interactions~\citep{Ponisio2017}. 
-			Reciprocal specialisation is particularly expected in highly intimate interactions~\citep{Hembry2018} rather than the relatively low-intimacy pollination or leaf-chewing herbivory we consider here~\citep{Astegiano2017}.
-			Despite this, it is still possible that some plant families may tend to have more intimate interactions than others.
-This could result, for example, if a plant is pollinated by an insect which is also a herbivore in its larval stage~\citep{Hembry2018}.
-			Whether or not intimacy plays a role in structuring these interactions, past selection to avoid competition is 
-			consistent with the relatively high proportion of extreme specialists we
-			observed in the pollination networks.
-
-		\end{quotation}
+		\textbf{R:} We do not have any data on interaction intimacy, so we cannot say how this would influence our results. [[I'll work on adding some kind of ref to this Hembry thing.]]
 
@@
 If closely-related species provide similar functions in ecological networks, they could be used interchangeably to restore ecological interactions/functions.
-This is an exciting potential application of phylogenetic data in biodiversity conservation and restoration, and could be touched upon/discussed in this manuscript.
+This is an exciting potential application of phylogenetic data in biodiversity conservation and restoration, and could be touched upon/discussed in this manuscript..
 		Otherwise, I have only minor comments.
@@
 It is often difficult to see how theoretical work may relate to conservation practice, so we are glad to take the opportunity to make a link here.
-We have reframed our closing paragraph to introduce the possibilities for using closely-related species in restoration efforts, and believe that it emphasises the importance of continuing research along this line.
-We hope that the Referee agrees that introducing this idea makes for a much stronger conclusion.
-
-	Lines 495-511:
-
-	\begin{quotation}
-
-		Altogether, our study has revealed general trends for conservation of interaction
-		partners between closely-related species, with some networks and plant 
-		families showing different trends. This overall similarity between closely-related
-		species has a potential application in ecological restoration. Close relatives could
-		be used interchangeably to restore missing interactions and fill ecosystem functions. 
-		This may be advantageous when a target plant is more difficult to establish than its
-		relatives, or if the restoration site is not large enough to support viable populations 
-		of many species. We should urge caution, however, since plants which support the
-		same pollinators may also support similar sets of herbivores. To avoid unwanted 
-		indirect effects, all interactions involving the target species should be considered.
-		Although here we considered only the presence or absence of interactions,
-		(i.e., qualitative networks)
-		recent work also suggests that the phylogenetic composition of a plant
-		community can also affect the strength of 
-		interactions, and that the spatial arrangement of plants within a 
-		community may be particularly important~\citep{Yguel2011,Castagneyrol2014}.
-		These further nuances in the relationship between phylogenetic distance and 
-		niche overlap could also strongly affect the ability of closely-related species to
-		fill the same functions in restoration efforts. This is clearly a topic with many
-		unresolved questions, deserving of further study.
-
-	\end{quotation}
+[[Add a bit of this, I think we have room]]
 
@@
 
-		\textbf{R:} We have changed the title to state our main result while also pointing out some of the important variability between networks.
-We do feel that this variability is a major feature of our results, as well as previous studies of phylogenetic signal across systems, and it is too easy to forget if not emphasized.
-We hope that the Referee will agree that our new title, "Related plants tend to share pollinators and herbivores, but strength of phylogenetic signal varies among plant families", strikes a balance between these two considerations.
-
-		% "At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families.”
-
-		% - suggests that we focus on broad support. Maybe "Broad conservation of pollinators and herbivores in a global dataset"?
-		% "Despite variation among families, pollinators and herbivores are broadly conserved among related plants"?
-		% "Related plants tend to share pollinators and herbivores, but strength of phylogenetic signal varies among plant families"?
-
-	2. Request to state that networks are qualitative rather than quantitative
+		\textbf{R:}
+
+"At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families.”
+
+- suggests that we focus on broad support. Maybe "Broad conservation of pollinators and herbivores in a global dataset"?
+"Despite variation among families, pollinators and herbivores are broadly conserved among related plants"?
+"Related plants tend to share pollinators and herbivores, but strength of conservation varies among plant families"?
+
+	2. Request to state that networks are qualitative rather than quantitative [[done]]
 
@@
 
-		Lines 105-106 (methods):
-
-		\begin{quotation}
-
-			All networks were qualitative and did not include interaction strengths.
-
-		\end{quotation}
-
-		Lines 294-296 (results):
+		Lines XX-XX (methods):
+
+		\begin{quotation}
+
+			All networks were qualitative, recording the presence or 
+		    absence of interactions rather than their strength.
+
+		\end{quotation}
+
+		Lines XX-XX (results):
 
@@
 
-    	Lines 504-505 (discussion):
+    	Lines XX-XX (discussion):
 
@@
 		  Although here we considered only the presence or absence of interactions,
-		  (i.e., qualitative networks) ...
-
-    	\end{quotation}
-
-	3. L298 – Please be careful with use of “lesser/greater” “more negative or positive than expected from permuted networks”
-
-		\textbf{R:} We appreciate that this description could be unclear, and have revised this line as suggested. It now reads:
-
-		Lines 326-328:
+		  (i.e., qualitative networks)
+
+    	\end{quotation}
+
+	3. L298 – Please be careful with use of “lesser/greater” “more negative or positive than expected from permuted networks” [[done]]
+
+		\textbf{R:} We appreciate that this desceription could be unclear, and have revised this line as suggested. It now reads:
+
+		Lines XX-XX:
 
@@
 
-	4. Typo in line 322
-
-		\begin{refquote}
-			L322 – how was this result obtained if insect phylogenies were not calculated? Do you mean “more closely-related plants in pollinator networks”?
+	4. Typo in line 322 [[done]]
+
+		\begin{refquote}
+			L322 – how was this result obtained if insect phylogenies were not caclculated? Do you mean “more closely-related plants in pollinator networks”?
 		\end{refquote}
@@
 
-	\textbf{R:} We thank the Referee for their compliments to our analysis and for taking the time to review our manuscript so thoroughly.
-We acknowledge that our writing can be dense at times and appreciate the Referee pointing out places where we may clarify our prose.
-We especially appreciate the detailed suggestions for how to improve our second-to-last paragraph, and have followed them to the best of our ability.
+	\textbf{R:} We thank the Referee for their compliments to our analysis and for taking the time to review our manuscript.
+We appreciate that our writing can be dense at times and appreciate the Referee pointing out places where we may clarify our prose.
 Below, we respond to each comment in detail (preceded by \textbf{R:}).
-We are confident that revising the manuscript in response to the Referee's comments has significantly improved it.
-
-	1. Confusion about description of tuple-form dependent variable
-
-		\begin{refquote}
-			* Modelling the relationship between niche overlap and phylogenetic distance\\
+We are confident that revising the manuscript in response to the Referee's comments has improved the manuscript.
+
+1. Confusion about description of two dependent variables in analyses [[done]]
+
+	\begin{refquote}
+		* Modelling the relationship between niche overlap and phylogenetic distance
 		I did not managed to fully grasp the statistical analysis right away (I reckon I'm not a statistical master, but this may be the case of other readers), and I think it was mostly due to the way the methods are described.
@@
 
-		\textbf{R:} The number of shared and unshared interactions are indeed both dependent variables included in the analysis.
-The number of shared variables is the key variable, but the number of unshared interactions is also important as it indicates how extraordinary a particular number of shared interactions is.
-The binomial process incorporates both quantities; converting the numbers of shared and unshared interactions to a proportion and weighting the observations by the total number of interactions.
-We thank the Referee for pointing out text in the introduction which clarified the purpose of including unshared interactions, and have used it as the basis for improving the methods.
+	\textbf{R:} The number of shared and unshared interactions are both dependent variables included in the analysis.
+The number of shared variables is indeed the key variable, but the number of unshared interactions is also important as it indicates how extraordinary a particular number of shared interactions is.
+The binomial process incorportates both quantities; converting the numbers of shared and unshared interactions to a proportion and weighting the observations by the total number of interactions.
+We thank the Referee for pointing out text in the introduction which clarifiedthe purpose of including unshared interactions.
 We have expanded the beginning of this section to explain the logic of our modelling approach in more detail.
 
-		lines 130-141:
-
-		\begin{quotation}
-
-			We calculated niche overlap for each pair of plants $i$ and $j$ based on the number of shared and unshared interaction partners ($M_{ij}$, $U_{ij}$, respectively). 
-			The number of unshared interaction 
+	lines XX-XX:
+
+	\begin{quotation}
+
+	    We calculated niche overlap for each pair of plants $i$ and $j$ based on the number of shared interaction
+	    partners ($M_{ij}$) and the number of interaction partners which are not
+	    shared ($U_{ij}$). The number of unshared interaction 
 	    partners gives valuable information about cases where, for example, 
 	    closely-related plants may have experienced disruptive selection, leading to weaker phylogenetic signal.
-			The sum $M_{ij} + U_{ij}$ indicates the amount of information  provided by each pair of plants: a pair of generalists which share most of their interaction partners gives a stronger indication of phylogenetic signal than a pair of extreme specialists with one common interaction partner.
-
-			Together, $M_{ij}$ and $U_{ij}$ give a Jaccard index ($J_{ij}$) describing 
-			the proportion of shared interactions. $J_{ij}$ is defined: 
-			\begin{equation}
-			J_{ij} = \frac{M_{ij}}{U_{ij}+M_{ij}} ,
-			\end{equation}
-			where $M_{ij}$ is the set of \emph{mutual} (shared) interaction partners and $U_{ij}$ the set of unshared interaction partners for plants $i$ and $j$.
-
-		\end{quotation}
-
-	2. Request to state that we use the Jaccard index more explicitly
+The number of shared and unshared interaction partners together indicates the amount of information  provided by each pair of plants: a pair of generalists which share most of their interaction partners gives a stronger indication of phylogenetic signal than a pair of specialists with one common interaction partner.
+
+	\end{quotation}
+
+2. Request to state that we use the Jaccard index more explicitly [[done]]
 
@@
 
-			Lines 173-181:
-
-			\begin{quotation}
-
-				To demonstrate the power of defining $J_{ij}$ as a tuple of $M_{ij}$ and $U_{ij}$ rather than a single value, we repeated the above analyses using a Jaccard index based only on the proportion of interaction partners that are shared (i.e., $J_{ij}$ = $M_{ij}$/[$M_{ij}+U_{ij}$]).
+		Lines XX-XX:
+
+		\begin{quotation}
+
+			To demonstrate the power of defining $\omega_{ij}$ as a tuple of $M_{ij}$ and $U_{ij}$, we repeated the above analyses using a Jaccard index based only on the proportion of interaction partners that are shared (i.e., $\omega_{ij}$ = $M_{ij}$/[$M_{ij}+U_{ij}$]).
 Note that while the proportion of shared interaction partners is the same in both cases, the tuple formulation gives more weight to plants with many interaction partners as these provide more information.
 When comparing the two approaches
-				we observed similar trends but, notably, the tuple definition of $J_{ij}$ had greater power to detect weak relationships (\emph{Supporting information 2}).
-We therefore show only the results when defining $J_{ij}$ as a tuple in the main text.
-
-			\end{quotation}
-
-	3. Request to make non-independence of species within each community explicit.
+		    we observed similar trends but, notably, the tuple definition of $\omega_{ij}$ had greater power to detect weak relationships (\emph{Supporting information 2}).
+We therefore show only the results when defining $\omega_{ij}$ as a tuple in the main text.
+
+		\end{quotation}
+
+3. Request to make non-independence of species within each community explicit. [[done]]
 
@@
 
-	4. Permuting the permuted networks is confusing
-
-		\begin{refquote}
-			* Evaluating type I and type II errors: Permutations of permutations\\
+4. Permuting the permuted networks is confusing [[done]]
+
+	\begin{refquote}
+		* Evaluating type I and type II errors: Permutations of permutations
 		Paragraph p.
@@
 
-		Lines 209-212:
-
-		\begin{quotation}
-
+	Lines XX-XX:
+
+	\begin{quotation}
 		This permutation approach also allows us to estimate type I and type II 
@@
 Because the permuted networks should not demonstrate any particular relationship between phylogenetic distance and partner overlap, these slopes should be similar to those obtained after permuting these networks a second time.
-
-		\end{quotation}
-
-	5. Suggestion to consider phylogenetic diversity instead of number of plant pairs
-
-		\begin{refquote}
-			* Testing the effect of network size on the existence of a phylogenetic signal\\
+	\end{quotation}
+
+5. Suggestion to consider phylogenetic diversity instead of number of plant pairs [[done]]
+
+	\begin{refquote}
+		* Testing the effect of network size on the existence of a phylogenetic signal
 		Here, it is specifically the number of plant pairs that is studied.
@@
 Because of this, and because this analysis would more compliment our community-composition analysis than introduce new material, we have opted no to pursue phylogenetic diversity in this manuscript.
-Here, we were more concerned with numbers of plant pairs since numbers of species are known to affect many areas of network structure and because the number of plant pairs is effectively the sample size for our within-network analyses.
-
-	6. Request for consideration of multiple testing
-
-		\begin{refquote}
-			* Testing within-family existence of a phylogenetic signal\\
+Here, we were more concerned with numbers of plant pairs since numbers of species are known to affect many areas of network structure.
+This did not appear to be a major issue for our analyses.
+
+6. Request for consideration of multiple testing [[done]]
+
+	\begin{refquote}
+		* Testing within-family existence of a phylogenetic signal
 		Examining the strength of phylogenetic signal within plant families is an interesting idea.
@@
 This development of this test was heavily motivated by the Moran paper you recommend, and we thank the Referee for pointing out this literature.
-We have added tables of the SCBT critical values to \emph{Supplemental Information 4} in order to provide readers with a bit more detail.
-We have also added a few lines to the methods to formally introduce the problem of multiple testing, some of the objections to the strict Bonferroni in~\citet{Moran2003}, and our solution to it.
-
-		Lines 278-285:
-
-		\begin{quotation}
-
-			By considering each family separately, we do risk obtaining some significant results purely by chance.
-The standard technique for addressing this type of multiple hypothesis testing, the Bonferroni correction, tends to be over-zealous and lead to a failure to reject the null hypothesis even when a large number of significant results before the correction supports the alternative hypothesis~\citep{Moran2003}.
-To account for multiple testing while also allowing the number of families showing significant trends to carry some weight, we use the correlated Bonferroni test introduced in~\citet{Drezner2016} (\emph{Supplemental Information 4}).
-
-		\end{quotation}
-
-		Lines 355-360 now read:
-
-		\begin{quotation}
-			 In pollination networks, overlap decreased significantly with increasing phylogenetic distance in 14 of the 48 well-represented families (Table 1; Fig.
-3).
+We have added tables of the SCBT critical values to Supplemental Information 4 in order to provide readers with a bit more detail.
+
+	Lines XX-XX now read:
+
+	\begin{quotation}
+		 In pollination networks, overlap decreased significantly with increasing phylogenetic distance in 14 of the 48 well-represented families (Table~\ref{family_slopes_pp}; Fig.~\ref{within_family_regression}).
 If we apply the correlated Bonferroni correction to account for multiple testing~\citep{Drezner2016}, all of these slopes remain significant (\emph{Supplemental Information 4}).
@@
 
-	7. Suggestion to mention sampling completeness as a potential explanation for specialists
-
-		\begin{refquote}
-			On the effect of specialist pollinators\\
+7. Suggestion to mention sampling completeness as a potential explanation for specialists [[done]]
+
+	\begin{refquote}
+		On the effect of specialist pollinators
 
@@
 
-		Lines 386-391:
-
-		\begin{quotation}
-
-			Note that some of the apparent specialists in our dataset may actually be rare species involved in more interactions which have not yet been observed~\citep{Bluthgen2006,Poisot2015}.
+	Lines XX-XX:
+
+	\begin{quotation}
+
+		It is also likely that at least some of the apparent specialists in our dataset are actually rare species for which many interactions have not yet been observed~\citep{Bluthgen2006,Poisot2015}.
 Without information on the sampling completeness of the networks in our dataset, it is difficult to estimate the size of this effect.
-			It is possible, however, that we might observe stronger relationships between phylogenetic
-			distance and niche overlap with more complete data on rare species.
-
-		\end{quotation}
-
-	8. Discussion of potential tradeoffs between interactions could be sharpened
-
-		\begin{refquote}
-			On plant families involved in different types of interactions\\
+In any case, the degree of phylogenetic conservation of interaction partners may change as we obtain more complete data on rare species.
+
+	\end{quotation}
+
+8. Discussion of potential tradeoffs between interactions could be sharpened (discussion)
+
+	\begin{refquote}
+		On plant families involved in different types of interactions
 
@@
 
-		\textbf{R:} We thank the Referee for their suggestions and for the small reading list.
-We have revised this paragraph along the lines above and hope that it is now clearer.
-We have expanded our discussion of (potentially) conflicting selection from different interaction types and removed our brief reference to dynamical drivers.
-We believe that sticking more closely to a single theme has helped to focus this paragraph.
-It now reads:
-
-		\begin{quotation}
-
-			For those few families which were well-represented in \emph{both} pollination
-			and herbivory networks, we can also contrast the 
-			trends in the two network types. Notably, all families except \emph{Asteraceae} 
-			showed different trends in different network types. 
-			This could be because of conflicting selection from pollinators and herbivores,
-			with one type of selection placing greater constraints on plant traits than the other.
-			Multiple types of interactions (e.g., pollination, herbivory, nectar robbing) 
-			and even environmental factors can influence traits such as 
-			flower colour, nectar abundance, and flowering phenology~\citep{Strauss2006}. 
-			These influences can act in the same or different directions~\citep{Strauss2006}.
-			Plant phenotypes in turn affect which species participate in both pollination and herbivory~\citep{Strauss1997,Strauss2002,Adler2004,Adler2006,Theis2006}.
-			The interplay between these different selective pressures may mean that plants
-			cannot evolve to respond optimally to both pollinators and herbivores. Put another
-			way, stronger selective pressure from herbivores might cause phenotypic changes
-			that disrupt phylogenetic signal in pollinators, or vice versa. This could result from
-			asymmetric degree distributions: within a single system, most plants tend to interact
-			with many pollinators \emph{or} many herbivores but not both~\citep{Melian2009,Pocock2012,Astegiano2017}.
-			These asymmetric interactions may also affect higher-order network structures such as
-			modularity or nestedness~\citep{Astegiano2017}.
-The nature of the effects of multiple interaction types on both phylogenetic signal in interactions and overall network structure is, however, still an open question deserving of much more research.
-
-		\end{quotation}
+	\textbf{R:} - merging interaction types is a good way to bring back to broader context :) - line 439-442 could be clarified based on Strauss \& Whitthall (if I can find it) - more references for structure of interaction patterns: e.g., Astegiano et al.
+- be more tentative for dynamical drivers (apparently Sauve et al.
+don't really discuss stability).
+Could be a by-product of assembly process (Maynard et al., 2018)
 
@@
 
-	9. Request for additional detail in summary point 2
+9. Request for additional detail in summary point 2 [[done]]
 
@@
 
-			\begin{itemize}
 		\item We quantify overlap of interaction partners for all pairs of plants in 59 pollination and 11 herbivory networks based on the numbers of shared and unshared interaction partners (thereby capturing both proportional and absolute overlap).
 We test 1) for relationships between phylogenetic distance and partner overlap within each network, 2) whether these relationships varied with the composition of the plant community, and 3) whether well-represented plant families showed different relationships.
-		\end{itemize}
-
-		\end{quotation}
-
-	10. Incorrect referencing of Sauve et al., 2016
+
+	\end{quotation}
+
+10. Incorrect referencing of Sauve et al., 2016 [[done]]
 
@@
 
-	11. Possible typo in page 3, lines 9-10
+11. Possible typo in page 3, lines 9-10 [[done]]
 
@@
 	\textbf{R:} We do not believe that the original formulation was incorrect, but agree that it was inelegant. We have revised this line to read:
-
-		\begin{quotation}
-			Plant traits are also likely to determine \emph{which} specific pollinators 
-			  and herbivores interact with a particular plant.
-	  	\end{quotation}
-
+	\begin{quotation}
+		Plant traits are also likely to determine \emph{which} specific pollinators and herbivores interact with a particular plant.
+  	\end{quotation}
   	We hope that this revised version reads better.
 
-	12. Suggestion to remove long list of citations in lines 22-25
+12. ?Suggestion to remove long list of citations in lines 22-25? [[done]]
 
@@
 
-		\textbf{R:} We had intended these citations to showcase a selection of researchers addressing different aspects of phylogenetic signal, but appreciate how including them all together could be confusing.
+	\textbf{R:} We had intended these citations to showcase a selection of researchers addressing different aspectsof phylogenetic signal, but appreciate how including them all together could be confusing.
 We have removed the large list so as not to distract from the more specific citations in subsequent lines.
 
-	11. Better showcase sentence on page 5, lines 78
+11. Better showcase sentence on page 5, lines 78 [[done]]
 
@@
 
-		Lines 79-86:
+	Lines XX-XX:
 
@@
 	  order to obtain a more detailed picture of how plant phylogeny
-			relates to network structure.
-As different plant families (which represent tractable clades for analysis) may have experienced different degrees of coevolution, convergence, etc., we also complement analyses with entire networks with comparisons among plants in the same family within a network.
-			This novel perspective allows us to investigate the relationship between phylogenetic distance and partner overlap at different scales.
-
-		\end{quotation}
-
-	12. Suggestion to make a figure showing distribution of webs, or at least to add countries to the list in SI
+	  relates to network structure. This novel perspective allows us to investigate the relationship between phylogenetic distance and partner overlap at different scales.
+
+	\end{quotation}
+
+12. Suggestion to make a figure showing distribution of webs, or at least to add countries to the list in SI [[done]]
 
@@
 
-	13. Suggestions to clarify explanation of regressions
+13. Suggestions to clarify explanation of regressions [[done?]]
 
@@
 We have also changed all $\omega_{ij}$ to $J_{ij}$ for simplicity.
-This paragraph (lines 130-146) now reads:
-
-		\begin{quotation}
-
-			We calculated niche overlap for each pair of plants $i$ and $j$ based on the number of shared and unshared interaction partners ($M_{ij}$, $U_{ij}$, respectively). 
-			The number of unshared interaction 
-			partners gives valuable information about cases where, for example, 
-			closely-related plants may have experienced disruptive selection, leading to weaker phylogenetic signal. 
-			The sum $M_{ij} + U_{ij}$ indicates the amount of information  provided by each pair of plants: a pair of generalists which share most of their interaction partners gives a stronger indication of phylogenetic signal than a pair of extreme specialists with one common interaction partner.
-
-			Together, $M_{ij}$ and $U_{ij}$ give a Jaccard index ($J_{ij}$) describing 
-			the proportion of shared interactions. $J_{ij}$ is defined: 
+This paragraph now reads:
+
+	\begin{quotation}
+	    We calculated niche overlap for each pair of plants $i$ and $j$ by 
+	    combining the number of shared interaction
+	    partners ($M_{ij}$) and the number of interaction partners which are not
+	    shared ($U_{ij}$) into a Jaccard index ($J_{ij}$) describing 
+	    the proportion of shared interactions. Importantly, we do this while 
+	    preserving the amount of information provided by each pair of plants
+	    (indicated by their numbers of interaction partners). $J_{ij}$ is usually defined as: 
+	    %
+	    \begin{equation}
+	      J_{ij} = \frac{M_{ij}}{P_i+P_j-M_{ij}} ,
+	    \end{equation}
+	    %
+	    where $M_{ij}$ is the set of \emph{mutual} (shared) interaction partners of 
+	    species $i$ and $j$ and $P_i$ and $P_j$ are the sizes of the sets of interaction 
+	    \emph{partners} for species $i$ and $j$ respectively. $J_{ij}$ can also be defined:
+	    %
 	    \begin{equation}
@@
 	    \end{equation}
-			where $M_{ij}$ is the set of \emph{mutual} (shared) interaction partners and $U_{ij}$ the set of unshared interaction partners for plants $i$ and $j$.
-			In our statistical analyses (see below), we used the tuple ($M_{ij}$, $U_{ij}$) as the
-			dependent variable rather than the single value $J_{ij}$. 
-			This allows us to preserve information about the amount of information provided by each pair of plants and weight the observations accordingly.
+	    %
+	    since $U_{ij}$ = $P_{i}$+$P_{j}$-2$M_{ij}$. This second definition more closely
+	    relates to our methodology, which used the tuple ($M_{ij}$, $U_{ij}$) as the
+	    dependent variable rather than the single value $J_{ij}$. Using this tuple form
+	    allows us to give more 
+	    weight to species sharing a large number of interaction partners as well as 
+	    those sharing a large proportion (i.e., to emphasise pairs of generalists 
+	    sharing most of their interaction partners over specialists sharing a single 
+	    interaction partner).
 Note that species sharing a large \emph{number} of interaction partners may not share a large \emph{proportion} of interaction partners if the number of interaction partners that are not shared is also large.
-
-		    \end{quotation}
-
-	14. Rephrasing of permutation strategy confusing
+% Added because Josh got confused about the distinction.
+	    \end{quotation}
+
+14. Rephrasing of permutation strategy confusing [[done]]
 
@@
 
-	15. Typo in page 15, lines 322-324
+15. Typo in page 15, lines 322-324 [[done]]
 
@@
 
-		Lines 350-352:
-
-		\begin{quotation}
-			Plants in pollination networks did, however, have a lower intercept probability of sharing interaction partners ($\beta_{pollination}$=-0.776, $p$=0.007), similar to our within-network results above.
-		\end{quotation}
-
-	16. Fig. 3, Table 2 conflict for Poaceae
+	Lines XX-XX:
+	\begin{quotation}
+		More closely-related plants in pollination networks did, however, tend to share fewer interaction partners ($\beta_{pollination}$=-0.776, $p$=0.007), similar to our within-network results above.
+	\end{quotation}
+
+16. Fig. 3, Table 2 conflict for Poaceae [[done]]
 
@@
 
-	17. A confusing attempt at subtlety
+17. A confusing attempt at subtelty [[done]]
 
@@
 
-	% Check.
 % Astegiano, J., Altermatt, F.
@@
 
-	% Check. % Maynard, D.S., Serván, C.A. and Allesina, S., 2018. Network spandrels reflect ecological assembly. Ecology letters, 21(3), pp.324-334.
-
-	% Check. % Melián, C.J., Bascompte, J., Jordano, P. and Krivan, V., 2009. Diversity in a complex ecological network with two interaction types. Oikos, 118(1), pp.122-130.
-
-	% Check. % Moran, M.D., 2003. Arguments for rejecting the sequential Bonferroni in ecological studies. Oikos, 100(2), pp.403-405.
-
-	% Check. % Strauss, S.Y. and Whittall, J.B., 2006. Non-pollinator agents of selection on floral traits. Ecology and evolution of flowers, pp.120-138.
+% Maynard, D.S., Serván, C.A. and Allesina, S., 2018. Network spandrels reflect ecological assembly. Ecology letters, 21(3), pp.324-334.
+
+% Melián, C.J., Bascompte, J., Jordano, P. and Krivan, V., 2009. Diversity in a complex ecological network with two interaction types. Oikos, 118(1), pp.122-130.
+
+% Moran, M.D., 2003. Arguments for rejecting the sequential Bonferroni in ecological studies. Oikos, 100(2), pp.403-405.
+
+% Strauss, S.Y. and Whittall, J.B., 2006. Non-pollinator agents of selection on floral traits. Ecology and evolution of flowers, pp.120-138.
 
@@
 
-\bibliographystyle{newphy} 
-\renewcommand*{\bibfont}{\raggedright}
-\bibliography{manual}
+\bibliographystyle{prsb} 
+\bibliography{abbreviated}
 

### 2019-12-09 manuscript/phylogenetic_signal_manuscript.tex
trying to be nicer to the idiot reviewer

@@
 
-\title{Related plants tend to share pollinators and herbivores, but strength of phylogenetic signal varies among plant families [[Alternative 1: Broad conservation of pollinators and herbivores in a global dataset]]
-[[Alternative 2: Despite variation among families, pollinators and herbivores are broadly conserved among related plants]]}
+\title{Related plants tend to share pollinators and herbivores, but strength of phylogenetic signal varies among plant families}
 
@@
 
-% \noindent Supporting information: 1 file containing 4 sections.
+% \noindent Supporting information: 1 file containing 5 sections.
 
@@
     where $\delta_{ij}$ is the phylogenetic distance between plants $i$ and 
-    $j$ and $J_{ij}$ is defined by the tuple ($M_{ij}$, $U_{ij}$) . 
+    $j$ and $J_{ij}$ is defined by the tuple ($M_{ij}$, $U_{ij}$) (see \emph{Supplemental Information 2} for R implementation). 
     The fixed effect of distance in this regression, $\beta_{distance}$, 
@@
 When comparing the two approaches
-    we observed similar trends but, notably, the tuple definition of $J_{ij}$ had greater power to detect weak relationships (\emph{Supporting information 2}).
+    we observed similar trends but, notably, the tuple definition of $J_{ij}$ had greater power to detect weak relationships (\emph{Supporting information 3}).
 We therefore show only the results when defining $J_{ij}$ as a tuple in the main text.
@@
     varying relationships between phylogenetic distance and
-    niche overlap are due to the different distributions 
+    pairwise niche overlap are due to the different distributions 
     of families across networks. We defined the relationship between
@@
     0.011 of sharing a given pollinator.
-    These trends may be partly 
-    due to the greater proportion of specialist pollinators than specialist 
-    herbivores. In our dataset, an average of 48\% (+/- 14) of pollinators 
+    These trends may be related to the numbers of extreme specialists in each network. In our dataset, an average of 48\% (+/- 14) of pollinators 
     in a given web were extreme specialists (i.e., visited only one plant 
@@
     $P$\textless0.001 for a binomial regression of specialists and 
-    generalists over network type). As extreme specialists by definition 
-    are never shared by more than one plant, a large proportion of specialists
-    would decrease niche overlap.
+    generalists over network type).
 
@@
     between phylogenetic distance and overlap always had more positive 
-    relationships than the permuted networks. This suggests that even in 
+    relationships than the permuted networks. This indicates that even in 
     the networks with non-significant relationships, the association between niche overlap and 
-    phylogenetic distance was not random. When the slopes of the permuted 
+    phylogenetic distance was not random and confirms that the significant results we observe are not due to non-independence of plants within a network. When the slopes of the permuted 
     networks were compared to those obtained from permutations of the 
-    permuted networks, there was no relationship, which speaks to the robustness of our methodology (\emph{Supporting information 3}).
+    permuted networks, there was no relationship, which speaks to the robustness of our methodology (\emph{Supporting information 4}).
 
@@
 
-    We were interested in whether the slope of the relationship between phylogenetic distance varied with community composition.
+    We were interested in whether the slope of the relationship between phylogenetic distance and niche overlap varied with community composition.
 In a PERMANOVA of slope against community composition, stratified by network type, we did not find a significant relationship between slope and community composition ($F_{1,68}$=1.06, $p$=0.493).
@@
     There was no significant relationship between overlap and phylogenetic distance in
-    a further 34 plant families (see \emph{Supporting information 4} for further 
+    a further 34 plant families (see \emph{Supporting information 5} for further 
     details). Finally, the overlap between pairs of \emph{Apiaceae} and \emph{Poaceae} increased significantly with increasing phylogenetic distance.
 
-    Of the nine plant families that were sufficiently well represented in herbivory 
+    Of the nine plant families that were well-represented in herbivory 
     networks, overlap decreased significantly with increasing phylogenetic distance in four 
@@
   more intimate or specialised interactions~\citep{Ponisio2017}. 
-  Reciprocal specialisation is particularly expected in highly intimate interactions~\citep{Hembry2018} rather than the relatively low-intimacy pollination or leaf-chewing herbivory we consider here~\citep{Astegiano2017}.
-  Despite this, it is still possible that some plant families may tend to have more intimate interactions than others.
-This could result, for example, if a plant is pollinated by an insect which is also a herbivore in its larval stage~\citep{Hembry2018}.
-  Whether or not intimacy plays a role in structuring these interactions, past selection to avoid competition is 
+  This is particularly the case in highly intimate interactions, where both partners may specialise~\citep{Hembry2018}.
+  Past selection to avoid competition is 
   consistent with the relatively high proportion of extreme specialists we
@@
 Thick, dashed lines represent the mean slopes across all networks of each type.
-The maximum and minimum slopes obtained from 999 permutations of each network are depicted by thin, black lines.
+The maximum and minimum slopes obtained from 999 permutations of each network are depicted by thin, black lines (permutation slopes ranged between -1.34$\times10^{-12}$ and 9.19$\times10^{-13}$).
 For both network types, the slopes obtained from permuted networks were always very close to 0.

### 2019-12-09 manuscript/supporting_info.tex
trying to be nicer to the idiot reviewer

@@
 
-\section*{Supporting information 2: Repeating our analyses with proportion of shared partners}
+\section*{Supporting information 2: R implementation of tuple-form regression}
+
+    We first fit a series of regressions (one per network) relating the Jaccard dissimilarity of the interaction partners of plants $i$ and $j$ ($J_{ij}$) to the phylogenetic  distance between them ($\delta_{ij}$), using the form
+    %
+      \begin{equation}
+        {\rm logit}\left(J_{ij}\right) \propto \beta_{distance}\delta_{ij} .
+        \label{basic}
+      \end{equation}
+    %
+    We fit these regressions using the R~\citep{R} base function ``glm'', which will accept $J_{ij}$ formatted as either a single value summarizing the probability of sharing an interaction partner \emph{or} the numbers of shared and un-shared interaction partners ($M_{ij}$ and $U_{ij}$).
+As we wished to use the tuple ($M_{ij}$, $U_{ij}$) as our input, the command in R was:
+
+    \emph{model=glm(cbind(M\_ij,U\_ij) $\sim$ scale(delta\_ij),family="binomial")}.
+
+    We used the same tuple-input form of the binomial regression for all subsequent regressions.
+
+\clearpage
+
+\section*{Supporting information 3: Repeating our analyses with proportion of shared partners}
 
@@
 
-\section*{Supporting information 3: Distributions of $p$-values for permuted networks}
+\section*{Supporting information 4: Distributions of $p$-values for permuted networks}
 
@@
 
-\section*{Supporting information 4: Details of within-family regressions}
+\section*{Supporting information 5: Details of within-family regressions}
 

### 2019-12-09 manuscript/reply_to_referees_2.tex
fixed editor address in reply
adjusted some sticky refs in the diff file, finished editing reply. Very tired of this whole enterprise

@@
 \begin{letter}{\bf Dr. Jana Vamosi\\
-               Editor\\
-               Proceedings of the Royal Society B\\
-               6-9 Carlton House Terrace\\
-               London, UK\\
-               SW1Y 5AG\\
+               Editor, New Phytologist\\
+               University of Calgary\\
+               2500 University Drive NW\\
+               Calgary, Canada\\
+               T2N 1N4\\
                 }
@@
 	We are pleased to submit a revised version of our manuscript, NPH-MS-2019-30803.
-In response to a suggestion from Referee 3, we have re-titled it "".
+In response to a suggestion from Referee 3, we have re-titled it "Related plants tend to share pollinators and herbivores, but strength of phylogenetic signal varies among plant families".
 We have also taken care to revise our methods section in response to the many helpful suggestions from Referee 4, and hope that our approach is now clearer.
@@
 	The Referee seems to view our basic question and analyses positively, but is rather critical of our writing in terms of logic, clarity, and style.
-We the time the Referee has spent in giving such extensive feedback, and have endeavoured to clarify the manuscript in response.
-In particular, we now define community composition more explicitly, have revised the discussion to be more explicit about whether we are referring to overall or within-network trends, and have removed specific phrases that the Referee found objectionable \emph{prima facie}.
+We appreciate the time the Referee has spent in giving such extensive feedback, and have endeavoured to clarify the manuscript in response.
+In particular, we now define community composition more explicitly, have revised the discussion to be clearer about whether we are referring to overall or within-network trends, and have removed specific phrases that the Referee found objectionable \emph{prima facie}.
 There are points where the Referee asks for analyses or ideas to be included which we felt already appeared in the text.
@@
 We have carefully revised specific passages that this and other Referees have identied as particularly unclear, and attempted to refine the manuscript overall.
-We hope that it is now more clear.
+We hope that it is now clearer.
 
@@
 
-		\textbf{R:} The Referee is correct about our hypothesis but it appears that our earlier version lead them that we are \emph{only} searching for conservation of niche overlap within families.
+		\textbf{R:} The Referee is correct about our hypothesis, but it appears that our earlier version lead them that we are \emph{only} searching for conservation of niche overlap within families.
 In fact, point 2 of the summary lists three separate analyses: testing for relationships between phylogenetic distance and partner overlap in \emph{all pairs of plants in a network, regardless of family}, testing whether the slopes of these whole-network relationships are related to the composition of the plant community in each network, and, as a supplement to these analyses, testing whether the slopes of these relationships differ if we consider only pairs of plants within the same family.
@@
 
-		Lines 252-257:
+		Lines 251-256:
 
@@
 		\begin{quotation}
+			\begin{itemize}
 		    \item The variety of relationships between phylogenetic distance and partner overlap in different plant families likely reflects a comparable variety of ecological and evolutionary processes.
-Considering factors affecting particular species-rich groups within a community may be the key to understanding the distribution of interactions.
+Considering factors affecting particular species-rich groups within a community may be the key to understanding the distribution of interactions at the network level.
+			\end{itemize}
 		\end{quotation}
@@
 Without more details as to why (or if) the Referee believes that the herbivory networks we removed should be included, we have decided to continue following that earlier feedback.
-We have revised the Methods section \textbf{Network data} to make the reasons for using a subset of herbivory networks clearer and hope this this addresses the Referee's concerns.
+We have revised the Methods section \textbf{Network data} to make the reasons for using a subset of herbivory networks clearer and hope that this addresses the Referee's concerns.
 
@@
 We chose this methodology for exactly the reasons the Referee suggests, to give more weight to generalists sharing many interaction partners.
-This is stated in lines 137-143 and lines 148-154 (quoted below).
+This is stated in lines 137-143 and lines 147-153 (quoted below).
 We are glad that the Referee agrees with our choice in methodology.
@@
 
-		\textbf{R:} It sounds as though the Referee would like us to include plant species as a predictor in our regressions.
-Due to the fact that particular species generally appear in few networks (many in only a single network), this would result in near singularity of our models.
+		\textbf{R:} Due to the fact that particular species generally appear in few networks (many in only a single network), this would result in near singularity of our models.
 We would therefore be completely unable to observe any patterns as species identity would explain essentially all variation in our regressions.
 Species identity is undoubtedly important for the same reasons we observed different trends in different plant families, but our dataset is unsuited for testing for species-level variation.
+
+		% DBS seems to think it's a generalist/specialist question, but I don't see that reading at all.
+Anyway, we do give more weight to information coming from generalists, but that's a feature not a bug.
+		Another possibility is that the Referee is suggesting that we include species degree (number of interaction partners) rather than species identity.
+We cannot address this possibility in our approach, since all of our analyses are based on species pairs.
+To some extent generalists (particularly when paired with other generalists) \emph{do} have more weight in our analyses, but this is by design.
+Pairs of species with more interaction partners between them give a more reliable picture of their niche overlap than specialists which are only able to share or not share a single partner.
+This idea is discussed in more detail in the Methods.
 
@@
 		In contrast, we were unable to determine amongst ourselves what the methodological or biological arguments would be for including connectance as a predictor.
-We also note that the manuscript is already quite full, so including these new analyses would require us to remove something which we and other Referees have regarded as important through the last few revisions.
-Without a justification from the Referee as to why connectance should affect pairwise niche overlap, we have opted not to add this new thread to the manuscript.
+Nevertheless, in order to assuage the Referee's concerns we have fit a similar model relating regression slopes to connectance instead of species richness.
+All terms in this regression were non-significant.
+We have added this regression in an appendix and hope that by including it the Referee will have more confidence in our results.
+		% Seems like DBS thought he actually had a point here, so I guess I can't get away without doing more analysis.
 
@@
 We want to explore whether more similar networks have more similar slopes of partner overlap against phylogenetic distance.
-Once again, we are pleased that the Referee agrees with our analysis.
 We did this because different plant families likely experienced different levels of convergence, coevolution, have different levels of intimacy with their partners, etc.
@@
 
-		Lines 78-86:
+		Lines 77-85:
 
@@
 First we introduce the overall result, and then we expand upon the details.
-We have edited lines 370-373 to make this clearer:
+We have edited lines 368-371 to make this clearer:
 
@@
 			interaction partners decreased with increasing 
-			phylogenetic distance. Considering networks separately ...
+			phylogenetic distance. Considering networks separately, ...
 
@@
 
-		Lines 224-233:
-
-		\begin{quotation}
+		Lines 225-235:
+
+		\begin{quotation}
+
 			Next, we examined the connection between our network-level observations
@@
 			Specifically, we tested the hypothesis that
-			varying relationships between phylogenetic distance and pairwise
-			niche overlap are due to the different distributions 
+			varying relationships between phylogenetic distance and
+			pairwise niche overlap are due to the different distributions 
 			of families across networks. We defined the relationship between
@@
 			a single network). We then related differences in this relationship
-			to differences in the composition of the plant community 
+			to differences in Bray-Curtis dissimilarity in the family-wise composition of the two plant communities 
 			using a non-parametric permutational multi-variate 
 			analysis of variance (PERMANOVA;~\citealp{Anderson2001}).
+
 	    \end{quotation}
@@
 
-		Lines 355-356:
+		Lines 354-355:
 
@@
 This mixture may have led the Referee to miss the evolutionary and coevolutionary ideas which are embedded throughout the discussion.
-We highlight some examples of these ideas below:
-
-		Lines 420-427:
+We highlight three  examples of these ideas below.
+
+		Lines 418-425:
 
@@
 
-		Lines 432-437:
+		Lines 430-435:
 
@@
 
-		Lines 458-466:
+		Lines 451-459:
 
@@
 
-		Lines 476-482:
-
-		\begin{quotation}
-
-			This could be because of conflicting selection from pollinators and herbivores,
-			with one type of selection placing greater constraints on plant traits than the other.
-			Multiple types of interactions (e.g., pollination, herbivory, nectar robbing) 
-			and even environmental factors can influence traits such as 
-			flower colour, nectar abundance, and flowering phenology~\citep{Strauss2006}. 
-			These influences can act in the same or different directions~\citep{Strauss2006}.
-
-		\end{quotation}
-
 	24. Objection to claim of "broad support"
@@
 
-		\textbf{R:} We found that more closely-related pairs of plants have greater niche overlap when considering all networks together, as well as in the majority of networks considered separetely. 
-		Moreover, the number of networks displaying significant trends (56\% of the pollination networks and 64\% of herbivory networks) is much greater than we would expect to occur purely by chance.
-Putting all of this together, we contend that there is indeed broad (in the sense of 'general' or 'overall') support for our hypothesis.
-In case it is simply the synonymy between broad and general that has perplexed the Referee, we have revised this line to state ''We found \emph{general} support...''.
-We hope that this wording is less contentious when the overall trends and preponderance of within-network results are considered together.
-
-		Nevertheless, we agree with the Referee that we do not have universal support for our hypothesis.
-This is why we provide the numbers of networks which did and did not support our hypothesis immediately after stating the oveerall trend.
-This allows readers to agree or disagree with our choice of words based on their interpretation of the facts.
+		\textbf{R:} We have rephrased this line to read 'We found general support ...'.
+Given the overall trend of increasing niche overlap with decreasing phylogenetic distance, combined with the majority of both pollination and herbivory networks showing significant trends, we believe that there is indeed general support for our hypothesis despite the variability within networks.
 
 		We are glad that the Referee finds the greater proportion of significant herbivory networks interesting.
-We also find the possibility of stronger conservation of interaction partners in herbivory networks intriguing.
 With the unbalanced sample sizes of pollination and herbivory networks, however, we are somewhat reluctant to make much of the difference between 56\% and 64\%.
@@
 
-		\textbf{R:} We may have failed to grasp the essence of this comment, as it seems that the Referee is suggesting that plants in the same genus are generally less closely-related than plants in different genera.
-This is quite counter-intuitive.
-We agree that plants within some genera are more closely-related than plants within other genera, but because we always use phylogenetic distance in our analyses, these differences do not influence the slopes we observe.
-Here we are not comparing the divergence times of different genera but referencing the nested nature of phylogenies as a whole.
-Referring to genera and subfamiliees is intended as a guide for readers who may not be expert phylogeneticists and could appreciate a reminder that we are considering branches near the tips of a phylogenetic tree.
-
-		In general, we believe that taxonomy is a reasonable proxy for phylogeny, and that two plants from within a genus will be more closely related than two plants in different genera.
-We are not aware of any evidence to the contrary, but are open to exploring this viewpoint if the Referee would like to provide some citations.
-In the meantime, we have opted not to change our text.
+		\textbf{R:} We agree that some genera are more closely-related than others and that taxonomy is an imperfect proxy for phylogeny.
+Nevertheless, we believe that the overall correspondence between phylogeny and taxonomy is good enough to use taxonomic labels to indicate the tips of a tree, for illustration purposes.
+In order to refresh the memories of readers who may not be familiar with terminology regarding deep/shallow differentiation, we have kept the reference to genera and subfamilies in this line.
 
@@
 		Given all of the above, we do not believe that a detailed discussion of intimacy fits well with our discussion.
-We do want to keep this idea in readers heads, however, and have added a brief description of the idea in lines (lines 443-454):
+We do want to keep this idea in readers heads, however, and have added a brief description of the idea in lines 442-447:
 
@@
 
-	Lines 495-511:
+	Lines 488-504:
 
@@
 
-		Lines 105-106 (methods):
+		Lines 104-105 (Methods):
 
@@
 
-		Lines 294-296 (results):
+		Lines 293-295 (Results):
 
@@
 
-    	Lines 504-505 (discussion):
+    	Lines 497-498 (Discussion):
 
@@
 
-		Lines 326-328:
+		Lines 323-325:
 
@@
 
-		lines 130-141:
+		lines 129-140:
 
@@
 			the proportion of shared interactions. $J_{ij}$ is defined: 
+			% %
 			\begin{equation}
@@
 			\end{equation}
-			where $M_{ij}$ is the set of \emph{mutual} (shared) interaction partners and $U_{ij}$ the set of unshared interaction partners for plants $i$ and $j$ (see \emph{Supplemental Information 2} for R implementation).
+			%
+			where $M_{ij}$ is the set of \emph{mutual} (shared) interaction partners and $U_{ij}$ the set of unshared interaction partners for plants $i$ and $j$.
 
@@
 
-			Lines 173-181:
+			Lines 172-180:
 
@@
 When comparing the two approaches
-				we observed similar trends but, notably, the tuple definition of $J_{ij}$ had greater power to detect weak relationships (\emph{Supporting information 2}).
+				we observed similar trends but, notably, the tuple definition of $J_{ij}$ had greater power to detect weak relationships (\emph{Supporting information 3}).
 We therefore show only the results when defining $J_{ij}$ as a tuple in the main text.
@@
 
-		Lines 209-212:
+		Lines 210-213:
 
@@
 
-		Lines 278-285:
+		Lines 277-284:
 
@@
 The standard technique for addressing this type of multiple hypothesis testing, the Bonferroni correction, tends to be over-zealous and lead to a failure to reject the null hypothesis even when a large number of significant results before the correction supports the alternative hypothesis~\citep{Moran2003}.
-To account for multiple testing while also allowing the number of families showing significant trends to carry some weight, we use the correlated Bonferroni test introduced in~\citet{Drezner2016} (\emph{Supplemental Information 4}).
-
-		\end{quotation}
-
-		Lines 355-360 now read:
-
-		\begin{quotation}
-			 In pollination networks, overlap decreased significantly with increasing phylogenetic distance in 14 of the 48 well-represented families (Table 1; Fig.
-3).
-If we apply the correlated Bonferroni correction to account for multiple testing~\citep{Drezner2016}, all of these slopes remain significant (\emph{Supplemental Information 4}).
+To account for multiple testing while also allowing the number of families showing significant trends to carry some weight, we use the correlated Bonferroni test introduced in~\citet{Drezner2016} (\emph{Supporting information 6}).
+
+		\end{quotation}
+
+		Lines 354-357 now read:
+
+		\begin{quotation}
+
+			 In pollination networks, overlap decreased significantly with increasing phylogenetic distance in 14 of the 48 well-represented families (Table~\ref{family_slopes_pp}; Fig.~\ref{within_family_regression}).
+If we apply the correlated Bonferroni correction to account for multiple testing~\citep{Drezner2016}, all of these slopes remain significant (\emph{Supporting information 6}).
+
 		\end{quotation}
@@
 
-		Lines 386-391:
+		Lines 384-389:
 
@@
 
-		Lines 79-86:
+		Lines 78-85:
 
@@
 We have also changed all $\omega_{ij}$ to $J_{ij}$ for simplicity.
-This paragraph (lines 130-146) now reads:
+This paragraph (lines 129-145) now reads:
 
@@
 
-		Lines 350-352:
+		Lines 349-351:
 

### 2019-12-09 manuscript/phylogenetic_signal_manuscript.tex
adjusted some sticky refs in the diff file, finished editing reply. Very tired of this whole enterprise

@@
 
-% \section*{Word Counts}
+\clearpage
 
-% Main text: 6498 % Limit 6,500 % Can also subtract 25 for page numbers
+\section*{Word Counts}
 
-% \begin{itemize}
-%   \item Introduction: 1165 
-%   \item Materials and Methods: 2470
-%   \item Results: 960
-%   \item Discussion: 1820
-%   \item Acknowledgements: 83
-% \end{itemize}
+Main text: 6409 % Limit 6,500 %
 
-% \noindent Figures: 3
+\begin{itemize}
+  \item Introduction: 1163
+  \item Materials and Methods: 2469
+  \item Results: 949
+  \item Discussion: 1745
+  \item Acknowledgements: 83
+\end{itemize}
 
-% \noindent Tables: 2
+\noindent Figures: 3
 
-% \noindent Supporting information: 1 file containing 5 sections.
+\noindent Tables: 2
+
+\noindent Supporting information: 1 file containing 6 sections.
+
+\clearpage
 
@@
 In part, this may be related to different degrees of interaction intimacy (dependence of one partner on another), which appears to contribute to network structure in mutualistic, but not antagonistic, networks~\citep{Guimaraes2007,Ponisio2017}.
-Thus, it is not straightforward to assume that interactions will always be similar among related species.
+In any case, it is not straightforward to assume that interactions will always be similar among related species.
 
@@
     Leaf-chewing and other types of herbivory might be affected by different
-    plant traits and therefore cannot be expected to show the same trends
+    plant traits and cannot be expected to show the same trends
     with respect to phylogeny. We therefore restricted our networks to
@@
     Note that species sharing a large \emph{number} of interaction partners may not share a large \emph{proportion} of interaction partners if the number of interaction partners that are not shared is also large.
-% Added because Josh got confused about the distinction.
 
@@
     where $\delta_{ij}$ is the phylogenetic distance between plants $i$ and 
-    $j$ and $J_{ij}$ is defined by the tuple ($M_{ij}$, $U_{ij}$) (see \emph{Supplemental Information 2} for R implementation). 
+    $j$ and $J_{ij}$ is defined by the tuple ($M_{ij}$, $U_{ij}$) (see \emph{Supporting information 2} for R implementation). 
     The fixed effect of distance in this regression, $\beta_{distance}$, 
@@
 Both models were fit using the R~\citep{R} base function ``glm".
+A similar model relating the strength of the relationship between phylogenetic distance and niche overlap to connectance showed no significant trends (\emph{Supporting information 4}).
 
@@
       networks means that the type II error would increase linearly as the 
-      alternative hypothesis was set farther from zero (\emph{Supporting Information 3}).
+      alternative hypothesis was set farther from zero (\emph{Supporting information 5}).
 
@@
     a single network). We then related differences in this relationship
-    to differences in the composition of the plant community 
+    to differences in Bray-Curtis dissimilarity in the family-wise composition of the two plant communities 
     using a non-parametric permutational multi-variate 
     analysis of variance (PERMANOVA;~\citealp{Anderson2001}).
-    To avoid inflating the perceived similarity between
-    pairs of networks which did not include many of the same families,
-    we used Bray-Curtis dissimilarity to define differences in plant
-    community composition. Bray-Curtis dissimilarity considers only
+    Bray-Curtis dissimilarity considers only
     those plant families which appear in at least one of a pair of
@@
 The standard technique for addressing this type of multiple hypothesis testing, the Bonferroni correction, tends to be over-zealous and lead to a failure to reject the null hypothesis even when a large number of significant results before the correction supports the alternative hypothesis~\citep{Moran2003}.
-To account for multiple testing while also allowing the number of families showing significant trends to carry some weight, we use the correlated Bonferroni test introduced in~\citet{Drezner2016} (\emph{Supplemental Information 4}).
+To account for multiple testing while also allowing the number of families showing significant trends to carry some weight, we use the correlated Bonferroni test introduced in~\citet{Drezner2016} (\emph{Supporting information 6}).
 
@@
     networks were compared to those obtained from permutations of the 
-    permuted networks, there was no relationship, which speaks to the robustness of our methodology (\emph{Supporting information 4}).
+    permuted networks, there was no relationship, which speaks to the robustness of our methodology (\emph{Supporting information 5}).
 
@@
     In pollination networks, overlap decreased significantly with increasing phylogenetic distance in 14 of the 48 well-represented families (Table~\ref{family_slopes_pp}; Fig.~\ref{within_family_regression}).
-If we apply the correlated Bonferroni correction to account for multiple testing~\citep{Drezner2016}, all of these slopes remain significant (\emph{Supplemental Information 4}).
+If we apply the correlated Bonferroni correction to account for multiple testing~\citep{Drezner2016}, all of these slopes remain significant (\emph{Supporting information 6}).
     There was no significant relationship between overlap and phylogenetic distance in
-    a further 34 plant families (see \emph{Supporting information 5} for further 
+    a further 34 plant families (see \emph{Supporting information 6} for further 
     details). Finally, the overlap between pairs of \emph{Apiaceae} and \emph{Poaceae} increased significantly with increasing phylogenetic distance.
@@
     and in one family, \emph{Fabaceae}, overlap of interaction partners increased significantly with 
-    increasing phylogenetic distance. If we again apply the correlated Bonferroni correction, all five significant slopes remain significant  (\emph{Supplemental Information 4}).
+    increasing phylogenetic distance. If we again apply the correlated Bonferroni correction, all five significant slopes remain significant  (\emph{Supportin information 6}).
 
@@
 Thick, dashed lines represent the mean slopes across all networks of each type.
-The maximum and minimum slopes obtained from 999 permutations of each network are depicted by thin, black lines (permutation slopes ranged between -1.34$\times10^{-12}$ and 9.19$\times10^{-13}$).
-For both network types, the slopes obtained from permuted networks were always very close to 0.
+The maximum and minimum slopes obtained from 999 permutations of each network are depicted by thin, black lines.
+For both network types, the slopes obtained from permuted networks were always very close to 0 (range -1.34$\times10^{-12}$ to 9.19$\times10^{-13}$).
 }

### 2019-12-09 manuscript/supporting_info.tex
adjusted some sticky refs in the diff file, finished editing reply. Very tired of this whole enterprise

@@
 
+\section*{Supporting information 4: A test of connectance}
+
+    To test whether the relationship between phylogenetic distance and niche overlap depended on connectance, we fit a general linear model for the slope of this relationship inferred from the glm models against connectance (C), network type (again using herbivory networks as a baseline), and their interaction:
+    %
+      \begin{equation}
+        \beta_{distance} \propto \beta_{C} \eta_{N} + \beta_{pollination} I_N + \beta_{C:pollination} \eta_{N} I_N ,
+      \end{equation}
+    %
+    where $\eta_{N}$ is the number of plant pairs in network $N$ for which distances could be calculated, $I_N$ is an indicator equal to 1 if network $N$ is a pollination network and 0 otherwise.
+
+    The strength of the relationship did not depend on network type ($\beta_{pollination}$=-0.015, $p$=0.860), connectance ($\beta_{C}$=-0.652, $p$=0.051), or their interaction ($\beta_{C:pollination}$=0.687, $p$=0.084).
+    If we removed the interaction term and re-fit the model, the strength of the relationships between phylogenetic distance and niche overlap still did not depend on connectance ($\beta_{C}$=-0.169, $p$=0.356).
+We conclude that connectance does not constrain pairwise niche overlap in our dataset.
+
 \clearpage
 
-\section*{Supporting information 4: Distributions of $p$-values for permuted networks}
+\section*{Supporting information 5: Distributions of $p$-values for permuted networks}
 
@@
 
-\section*{Supporting information 5: Details of within-family regressions}
+\section*{Supporting information 6: Details of within-family regressions}
 

### 2019-12-09 code/Jaccard_regressions.R
added that stupid regression against C

@@ -20,7 +20,7 @@ for(n in 1:length(files)){
   size=nrow(netdata)
 
   obs_slopes=c(Jaccard$coefficients['scale(distance)'],summary(Jaccard)$coefficients['scale(distance)',4],Sorenson$coefficients['scale(distance)'],summary(Sorenson)$coefficients['scale(distance)',4])
-  outtab[n,]=c(net,obs_slopes,size)
+  outtab[n,]=c(net,obs_slopes,size,C)
 
   if(n<12){
   	netdata$nettype='ph'
@@ -56,7 +56,12 @@ outtab$nettype=c(rep('PH',11),rep('PP',59))
 outtab$nettype=as.factor(outtab$nettype)
 outtab$n_pairs=as.numeric(as.character(outtab$n_pairs))
 # I think it may be best to make observed slopes, random slopes, and random-random slopes separately?
-
+source('how_many_extreme_specialists.R')
+outtab$network=as.character(droplevels(outtab$network))
+result_table$network=as.character(droplevels(result_table$network))
+outtab<-outtab[order(outtab$network),]
+result_table<-result_table[order(result_table$network),]
+outtab$C=result_table$C
 
 slope_test=with(outtab,glm(Jaccard_slope~nettype*n_pairs))
 pval_test=with(outtab,glm(Jaccard_p~nettype*n_pairs))

### 2019-12-09 code/how_many_extreme_specialists.R

@@ -5,19 +5,21 @@ library(MASS)
 
 phfiles<-as.character(list.files(path="../data/Corrected_Matrices/Plant_herbivore_matrices", full.names=TRUE, pattern="*.csv"))
 ppfiles<-as.character(list.files(path="../data/Corrected_Matrices/Stouffer_Ecology_Matrices", full.names=TRUE, pattern="*.csv"))
-planttree=read.newick("../data/plant_phylogeny/dated_tree.new")
+# planttree=read.newick("../data/plant_phylogeny/dated_tree.new")
 
 #### Directory of species names and networks
-speciesnames=read.table('../data/plant_phylogeny/corrected_names.tsv',header=TRUE,sep=',')
+# speciesnames=read.table('../data/plant_phylogeny/corrected_names.tsv',header=TRUE,sep=',')
 
 # Set up the results storage table
-result_table=matrix(nrow=length(c(phfiles,ppfiles)),ncol=9,data=1000)
-colnames(result_table)=c("network","network_type","spec_plants","spec_animals","gen_plants","gen_animals","n_plants","n_animals","plants_in_tree")
+result_table=matrix(nrow=length(c(phfiles,ppfiles)),ncol=12,data=1000)
+# colnames(result_table)=c("network","network_type","spec_plants","spec_animals","gen_plants","gen_animals","n_plants","n_animals","plants_in_tree")
+colnames(result_table)=c("network","network_type","spec_plants","spec_animals","gen_plants","gen_animals","n_plants","n_animals","mean_deg_insect","mean_deg_plant","median_deg_insect","C")
 
 for(n in 1:length(c(phfiles,ppfiles))){
   file=c(phfiles,ppfiles)[n]
   print(file)
   netname=gsub('../data/Corrected_Matrices/','',file)
+  net=gsub('_corrected.csv',"",netname)
 
   if(file%in%phfiles){
     nettype='ph'} else {
@@ -26,6 +28,9 @@ for(n in 1:length(c(phfiles,ppfiles))){
   network_matrix=read.csv(file,header=TRUE,sep=',',row.names=1)
   if('X'%in%colnames(network_matrix)){          # Trim any superfluous columns
     network_matrix$X=NULL    }
+  if('X.1'%in%colnames(network_matrix)){          # Trim any superfluous columns
+    network_matrix$X.1=NULL    }
+
 
[…]

### 2019-12-09 code/Jaccard_regressions.R
missed something

@@ -71,3 +71,5 @@ PP_slope_test=with(pptab,glm(Jaccard_slope~n_pairs))
 PP_pval_test=with(pptab,glm(Jaccard_p~n_pairs))
 
 
+stupidCtest=with(outtab,glm(Jaccard_slope~nettype*C))
+

### 2019-12-09 code/how_many_extreme_specialists.R

@@ -19,7 +19,7 @@ for(n in 1:length(c(phfiles,ppfiles))){
   file=c(phfiles,ppfiles)[n]
   print(file)
   netname=gsub('../data/Corrected_Matrices/','',file)
-  net=gsub('_corrected.csv',"",netname)
+  net=gsub('_corrected.csv','',netname)
 
   if(file%in%phfiles){
     nettype='ph'} else {

### 2019-12-19 manuscript/reply_to_referees_2.tex
addressing cosmetic changes from New Phy

@@
 We must also admit to having some difficulty parsing a number of Referee 2's comments in order to find what precisely was being asked.
-This may be partly because this review appears to have come from several people - the Referee refers to themselves as 'we' several times, and the writing appears to be more than usually variable within their comments.
 These difficulties mean that we may not have been able to address Referee 2's comments as fully as we have those of the other Referees.
@@
 In the spirit of not making the summary overly methodological, and because of the extremely tight word limit, we have not attempted to explain the unbalanced numbers of pollination and herbivory networks here.
-This information is contained in the Methods.
-
-	4. Mis-understanding of purpose and scope of within-family analyses
+As before, this information is contained in the Methods.
+
+	4. Misunderstanding of purpose and scope of within-family analyses
 
@@
 In fact, point 2 of the summary lists three separate analyses: testing for relationships between phylogenetic distance and partner overlap in \emph{all pairs of plants in a network, regardless of family}, testing whether the slopes of these whole-network relationships are related to the composition of the plant community in each network, and, as a supplement to these analyses, testing whether the slopes of these relationships differ if we consider only pairs of plants within the same family.
-We now number these three different analyses to avoid any further confusion.
+We now enumerate these three different analyses to avoid any further confusion.
 
@@
 
-		\textbf{R:} Potential tradeoffs between encouraging interactions with pollinators and discouraging herbivores are just one of the possible reasons why networks may not display the expected relationship between relatedness and niche overlap.
+		\textbf{R:} Potential trade-offs between encouraging interactions with pollinators and discouraging herbivores are just one of the possible reasons why networks may not display the expected relationship between relatedness and niche overlap.
 Note that we also propose several others in the same paragraph, including convergent evolution or selection to avoid pollen dilution.
@@
 Note that while we mentioned pollination and defense syndromes as common ideas in the literature, we did not make any claim as to whether these putative syndromes actually reflect plants with common sets of pollinators (the evidence we are aware of is rather mixed).
-Since syndromes do not form a major part of our analysis, we have removed them from the keywords and introduction.
+Since syndromes themselves do not form a major part of our analysis, we have removed them from the keywords and introduction.
 We hope that these changes will help readers avoid becoming distracted from the main focus of our manuscript (whether phylogenetic distance predicts niche overlap).
@@
 
-		\textbf{R:} We have no information on interaction strengths or intimacies and so cannot test for this possibility.
+		\textbf{R:} Unfortunately, we have no information on interaction strengths or intimacies and so cannot test for this possibility.
 However, we are happy to include the idea as yet another reason why plant communities may or may not show conservation of interactions.
@@
 
-		\textbf{R:} The term "insects consuming leaves" was recommended by an earlier reviewer, but we agree that leaf mining also constitutes leaf consumption (this is not necessarily the case for sap-sucking and galling, which is less leaf-specific).
+		\textbf{R:} The exact phrase "insects consuming leaves" was recommended by an earlier reviewer, but we agree that leaf mining also constitutes leaf consumption (this is not necessarily the case for sap-sucking and galling, which is less leaf-specific).
 We have changed these lines as suggested.
@@
 		\textbf{R:} The Referee was correct with their first idea.
-We want to explore whether more similar networks have more similar slopes of partner overlap against phylogenetic distance.
+We want to explore whether more compositionally similar networks have more similar slopes of partner overlap against phylogenetic distance.
 We did this because different plant families likely experienced different levels of convergence, coevolution, have different levels of intimacy with their partners, etc.
@@
 		\textbf{R:} As stated in the caption, the minimum and maximum slopes from the permutations are very close to 0.
-The clarify that they are not the same values, we now give the range of slopes (-1.34$\times10^{-12}$ to 9.19$\times10^{-13}$) as in the caption of Fig.
+To clarify that they are not the same values, we now give the range of slopes (-1.34$\times10^{-12}$ to 9.19$\times10^{-13}$) as in the caption of Fig.
 1.
@@
 
-	23. Request for more evolution content
+	23. Request for more evolutionary content
 
@@
 		We are glad that the Referee finds the greater proportion of significant herbivory networks interesting.
-With the unbalanced sample sizes of pollination and herbivory networks, however, we are somewhat reluctant to make much of the difference between 56\% and 64\%.
+With the unbalanced sample sizes of pollination and herbivory networks, however, we are reluctant to make much of the difference between 56\% and 64\%.
 We consider that the important point here is that networks are more likely than not to show decreasing niche overlap with increasing phylogenetic distance.
@@
 		\textbf{R:} We must again point out that subsetting the herbivory networks as we have done was requested during an earlier round of review.
-We are therefore reluctant to reconsider this approach without a very good reason.
+We are therefore reluctant to reconsider this approach without a very compelling reason to do so.
 
@@
 
-		\textbf{R:} We do not have information about the intimacy of different interactions within our dataset and are reluctant to speculate about what the effects of intimacy might be without data.
+		\textbf{R:} As noted above, we do not have information about the intimacy of different interactions within our dataset and are reluctant to delve too deeply into what the effects of intimacy might be without data to back up our ideas.
 Both leaf-chewing herbivory and pollination are generally low-intimacy interactions~\citep{Astegiano2017}, but there may still be variation in intimacy within these groups.

### 2019-12-19 manuscript/phylogenetic_signal_manuscript.tex
addressing cosmetic changes from New Phy

@@
 \usepackage{setspace}
+\usepackage{multicol}
 
@@
 
-\author{Alyssa R. Cirtwill$^{1,2}$, Giulio V. Dalla Riva$^{3}$, Nick J. Baker$^{1}$,\\
-Mikael Ohlsson$^{4}$, Isabelle Norstr\"{o}m$^{4}$, Inger-Marie Wohlfarth$^{4}$,\\ % All confirmed to submit
-Joshua A. Thia$^{1,5}$, % Confirmed to submit
-% Christie J. Webber$^{1}$, % Christie has confirmed that she'd rather be in the acknowledgements than an author
-Daniel B. Stouffer$^{1}$}
-\date{\small$^1$Centre for Integrative Ecology, School of Biological Sciences\\University of Canterbury\\Private Bag 4800\\
+\author{Alyssa R. Cirtwill$^{\dagger1,2}$, Giulio V. Dalla Riva$^{3}$, Nick J. Baker$^{1}$, Mikael Ohlsson$^{4}$,\\ 
+Isabelle Norstr\"{o}m$^{4}$, Inger-Marie Wohlfarth$^{4}$, Joshua A. Thia$^{1}$, Daniel B. Stouffer$^{1}$}
+\date{
+\begin{multicols}{2}
+\small
+$\dagger$ Corresponding author: alyssa.cirtwill@gmail.com; +46 8 16 20 00\\
+\medskip$^1$Centre for Integrative Ecology, School of Biological Sciences\\University of Canterbury\\Private Bag 4800\\
 Christchurch 8140, New Zealand\\
@@
 Christchurch 8140, New Zealand\\
-\medskip$^4$Department of Physics, Chemistry, and Biology (IFM)\\ Link\"{o}ping University\\ 581 83 Link\"{o}ping, Sweden\\
-\medskip$^5$Present Address: School of Biological Sciences\\
-The University of Queensland\\Brisbane, QLD 4072, Australia }
+\bigskip\bigskip$^4$Department of Physics, Chemistry, and Biology (IFM)\\ Link\"{o}ping University\\ 581 83 Link\"{o}ping, Sweden\\ \medskip
+\end{multicols}}
 
@@
 \maketitle
+
 \baselineskip=8.5mm
@@
 
-\clearpage
+% \clearpage
+\vspace{-0.5in}
+\section*{ORCID IDs}
+\noindent Alyssa Cirtwill: https://orcid.org/0000-0002-1772-3868\\
+\noindent Giulio V. Dalla Riva: https://orcid.org/0000-0002-3454-0633\\
+\noindent Joshua A. Thia: https://orcid.org/0000-0001-9084-0959\\
+\noindent Daniel B. Stouffer: https://orcid.org/0000-0001-9436-9674\\
 
+\vspace{-0.25in}
 \section*{Word Counts}
+\begin{multicols}{2}
 
 Main text: 6409 % Limit 6,500 % 
-
+\vspace{-5pt}
 \begin{itemize}
+  \setlength\itemsep{-0.1em}
   \item Introduction: 1163
@@
 
-\noindent Figures: 3
+\noindent Figures: 3\\
+\noindent Tables: 2\\
+\noindent Notes: 1 file, 6 sections.
+\end{multicols}
 
-\noindent Tables: 2
+\vspace{-0.25in}
+\begin{multicols}{2}
+\section*{Social media}
+@acirtwill; @stoufferlab\\
 
-\noindent Supporting information: 1 file containing 6 sections.
+\section*{Header}
 
@@
 
-\clearpage
+% \clearpage
 
@@
     plant species (mean=39.1, median=29.5). See \emph{Table S1, 
-    Supporting information 1} for details on the original sources of all 
+    Notes S1} for details on the original sources of all 
     networks. All networks were qualitative and did not include interaction strengths.
@@
     where $\delta_{ij}$ is the phylogenetic distance between plants $i$ and 
-    $j$ and $J_{ij}$ is defined by the tuple ($M_{ij}$, $U_{ij}$) (see \emph{Supporting information 2} for R implementation). 
+    $j$ and $J_{ij}$ is defined by the tuple ($M_{ij}$, $U_{ij}$) (see \emph{Notes S2} for R implementation). 
     The fixed effect of distance in this regression, $\beta_{distance}$, 
@@
 When comparing the two approaches
-    we observed similar trends but, notably, the tuple definition of $J_{ij}$ had greater power to detect weak relationships (\emph{Supporting information 3}).
+    we observed similar trends but, notably, the tuple definition of $J_{ij}$ had greater power to detect weak relationships (\emph{Notes S3}).
 We therefore show only the results when defining $J_{ij}$ as a tuple in the main text.
@@
 Both models were fit using the R~\citep{R} base function ``glm".
-A similar model relating the strength of the relationship between phylogenetic distance and niche overlap to connectance showed no significant trends (\emph{Supporting information 4}).
+A similar model relating the strength of the relationship between phylogenetic distance and niche overlap to connectance showed no significant trends (\emph{Notes S4}).
 
@@
       networks means that the type II error would increase linearly as the 
-      alternative hypothesis was set farther from zero (\emph{Supporting information 5}).
+      alternative hypothesis was set farther from zero (\emph{Notes S5}).
 
@@
 The standard technique for addressing this type of multiple hypothesis testing, the Bonferroni correction, tends to be over-zealous and lead to a failure to reject the null hypothesis even when a large number of significant results before the correction supports the alternative hypothesis~\citep{Moran2003}.
-To account for multiple testing while also allowing the number of families showing significant trends to carry some weight, we use the correlated Bonferroni test introduced in~\citet{Drezner2016} (\emph{Supporting information 6}).
+To account for multiple testing while also allowing the number of families showing significant trends to carry some weight, we use the correlated Bonferroni test introduced in~\citet{Drezner2016} (\emph{Notes S6}).
 
-\clearpage
+% \clearpage
 
@@
     networks were compared to those obtained from permutations of the 
-    permuted networks, there was no relationship, which speaks to the robustness of our methodology (\emph{Supporting information 5}).
+    permuted networks, there was no relationship, which speaks to the robustness of our methodology (\emph{Notes S5}).
 
@@
     In pollination networks, overlap decreased significantly with increasing phylogenetic distance in 14 of the 48 well-represented families (Table~\ref{family_slopes_pp}; Fig.~\ref{within_family_regression}).
-If we apply the correlated Bonferroni correction to account for multiple testing~\citep{Drezner2016}, all of these slopes remain significant (\emph{Supporting information 6}).
+If we apply the correlated Bonferroni correction to account for multiple testing~\citep{Drezner2016}, all of these slopes remain significant (\emph{Notes S6}).
     There was no significant relationship between overlap and phylogenetic distance in
-    a further 34 plant families (see \emph{Supporting information 6} for further 
+    a further 34 plant families (see \emph{Notes S6} for further 
     details). Finally, the overlap between pairs of \emph{Apiaceae} and \emph{Poaceae} increased significantly with increasing phylogenetic distance.
@@
 
+\section*{Notes legends}
+
+\noindent Notes 1: Sources for networks. Original sources for all networks used in this study.\\
+
+\noindent Notes 2: R implementation of tuple-form regression. Further details and R code for our statistical model.\\
+
+\noindent Notes 3: Repeating our analyses with proportion of shared partners.
+Results when niche overlap is defined as the proportion of shared interaction partners rather than by a tuple of shared and unshared partners.\\
+
+\noindent Notes 4: A test of connectance. Methods and results for a test as to whether the connectance of a network affects the relationship between phylogenetic distance and niche overlap.\\
+
+\noindent Notes 5: Distributions of $p$-values for permuted networks. Figures showing the distributions of $p$-values in permuted networks referenced in Figs. 1-2.\\
+
+\noindent Notes 6: Details of within-family regressions.
+Supplemental results for within-family regressions, including a comparison of $p$-values and critical values for the sequential correlated Bonferroni test.\\
+
 \newpage
@@
   \caption{
-  \small Change in log odds (per million years of phylogenetic distance) of a pair of plants in the same family sharing a pollinator.}
+  \small Change ($\Delta$) in log odds (per million years of phylogenetic distance) of a pair of plants in the same family sharing a pollinator.}
   % These are from the regressions within each family. P-vals need to be replaced, to come from randomizations. Coefficients should be fine.
@@
     \hline
-    Family  & Change in log odds & $P$-value & Family  & Change in log odds & $P$-value \\
+    Family  & $\Delta$ log odds & $P$-value & Family  & $\Delta$ log odds & $P$-value \\
     \hline
@@
   \begin{table}[!h]
-  \caption{\small Change in log odds (per million years of phylogenetic distance) of a pair of plants in the same family sharing a herbivore.}
+  \caption{\small Change ($\Delta$) in log odds (per million years of phylogenetic distance) of a pair of plants in the same family sharing a herbivore.}
   % These are from the regressions within each family. P-vals need to be replaced, to come from randomizations. Coefficients should be fine.
@@
   \hline
-    Family & Change in log odds & $P$-value \\
+    Family & $\Delta$ log odds & $P$-value \\
     \hline
@@
     \begin{center}
-      \centerline{\includegraphics*[height=.62\textheight]{Figures/dataplots/Family/allfams_full.eps}}
+      \centerline{\includegraphics*[height=.58\textheight]{Figures/dataplots/Family/allfams_full.eps}}
     \end{center}

### 2019-12-19 manuscript/supporting_info.tex
addressing cosmetic changes from New Phy

@@
 
-\author{Alyssa R. Cirtwill$^{1,2}$, Giulio V. Dalla Riva$^{3}$, Nick J. Baker$^{1}$,\\
-Mikael Ohlsson$^{4}$, Isabelle Norstr\"{o}m$^{4}$, Inger-Marie Wohlfarth$^{4}$,\\
-Joshua A. Thia$^{1,5}$, 
-% Christie J. Webber$^{1}$, 
-Daniel B. Stouffer$^{1}$}
-\date{\small$^1$Centre for Integrative Ecology, School of Biological Sciences\\
-\medskip$^2$Present address: Department of Ecology,\\
-Environment, and Plant Sciences (DEEP)\\
-Stockholm University\\
-114 19 Stockholm, Sweden\\
-\medskip$^3$Biomathematics Research Centre, School of Mathematics and Statistics\\
-University of Canterbury\\Private Bag 4800\\
-Christchurch 8140, New Zealand\\
-\medskip$^4$Department of Physics, Chemistry, and Biology (IFM)\\ Link\"{o}ping University\\ 581 83 Link\"{o}ping, Sweden\\
-\medskip$^5$Present Address: School of Biological Sciences\\
-The University of Queensland\\Brisbane, QLD 4072, Australia }
+\author{Alyssa R. Cirtwill, Giulio V. Dalla Riva, Nick J. Baker,\\
+Mikael Ohlsson, Isabelle Norstr\"{o}m, Inger-Marie Wohlfarth,\\
+Joshua A. Thia, Daniel B. Stouffer}
+\date{Article accepted: December 13, 2019}
 
@@
 
-\linenumbers
+% \linenumbers
 \beginsupplement
@@
 
-\section*{Supporting information 1: Sources for networks}
+\section*{Notes S1: Sources for networks}
   \begin{table}[!h]
@@
 
-\section*{Supporting information 2: R implementation of tuple-form regression}
+\section*{Notes S2: R implementation of tuple-form regression}
 
@@
 
-\section*{Supporting information 3: Repeating our analyses with proportion of shared partners}
+\section*{Notes S3: Repeating our analyses with proportion of shared partners}
 
@@
 
-\section*{Supporting information 4: A test of connectance}
+\section*{Notes S4: A test of connectance}
 
@@
 
-\section*{Supporting information 5: Distributions of $p$-values for permuted networks}
+\section*{Notes S5: Distributions of $p$-values for permuted networks}
 
@@
 
-\section*{Supporting information 6: Details of within-family regressions}
+\section*{Notes S6: Details of within-family regressions}
 

### 2019-12-24 manuscript/supporting_info.tex
proofs changes

@@
 
-\title{At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families - Supporting Information}
+\title{At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families\\ Supporting Information}
 
@@
 Mikael Ohlsson, Isabelle Norstr\"{o}m, Inger-Marie Wohlfarth,\\
-Joshua A. Thia, Daniel B. Stouffer}
+Joshua A. Thia, \& Daniel B. Stouffer}
 \date{Article accepted: December 13, 2019}
@@
     \begin{center}
-    \begin{tabular}{|l l l m{8cm} |}
+    \begin{tabular}{|l l l m{7cm} |}
     \hline

### 2020-01-09 manuscript/accpeted_manuscript.tex
creating submitted and accepted versions for proper legal archiving

--- 2019-12-19 manuscript/phylogenetic_signal_manuscript.tex
@@
 \usepackage{multicol}
+\usepackage{fancyhdr}
 
@@
 
+\lhead{Accepted manuscript}
+
 \title{Related plants tend to share pollinators and herbivores, but strength of phylogenetic signal varies among plant families}
@@
 \author{Alyssa R. Cirtwill$^{\dagger1,2}$, Giulio V. Dalla Riva$^{3}$, Nick J. Baker$^{1}$, Mikael Ohlsson$^{4}$,\\ 
-Isabelle Norstr\"{o}m$^{4}$, Inger-Marie Wohlfarth$^{4}$, Joshua A. Thia$^{1}$, Daniel B. Stouffer$^{1}$}
+Isabelle Norstr\"{o}m$^{4}$, Inger-Marie Wohlfarth$^{4}$, Joshua A. Thia$^{1}$, \& Daniel B. Stouffer$^{1}$}
 \date{
@@
 
-% \clearpage
-\vspace{-0.5in}
-\section*{ORCID IDs}
-\noindent Alyssa Cirtwill: https://orcid.org/0000-0002-1772-3868\\
-\noindent Giulio V. Dalla Riva: https://orcid.org/0000-0002-3454-0633\\
-\noindent Joshua A. Thia: https://orcid.org/0000-0001-9084-0959\\
-\noindent Daniel B. Stouffer: https://orcid.org/0000-0001-9436-9674\\
+\noindent This is the accepted version of the following article: \\
+\smallskip
+Cirtwill, A. R., Dalla Riva, G. V., Baker, N. J., Ohlsson, M.,
+Norstr\"{o}m$^{4}$, I., Wohlfarth, I.
+M., Thia, J.
+A., Stouffer, D.
+B.
+(2020) \emph{Related plants tend to share pollinators and herbivores, but strength of phylogenetic signal varies among plant families}.
+\textbf{New Phytologist}: in press, which has been published in final form at \emph{link to paper}.\\
+\smallskip
+This article may be used for
+non-commercial purposes in accordance with the Wiley Self-Archiving Policy [http://www.wileyauthors.com/self-archiving].
 
-\vspace{-0.25in}
-\section*{Word Counts}
-\begin{multicols}{2}
+% % \clearpage
+% \vspace{-0.25in}
+% \small{
+% \noindent\textbf{ORCID IDs}\\
+% \noindent Alyssa Cirtwill: https://orcid.org/0000-0002-1772-3868\\
+% \noindent Giulio V. Dalla Riva: https://orcid.org/0000-0002-3454-0633\\
+% \noindent Joshua A. Thia: https://orcid.org/0000-0001-9084-0959\\
+% \noindent Daniel B. Stouffer: https://orcid.org/0000-0001-9436-9674\\
 
-Main text: 6409 % Limit 6,500 % 
-\vspace{-5pt}
-\begin{itemize}
-  \setlength\itemsep{-0.1em}
-  \item Introduction: 1163
-  \item Materials and Methods: 2469
-  \item Results: 949
-  \item Discussion: 1745
-  \item Acknowledgements: 83
-\end{itemize}
+% \medskip
+% \noindent\textbf{Social media}: 
+% @acirtwill; @stoufferlab\\
+% \medskip
+% \noindent\textbf{Header}: 
+% Phylogenetic distance \& niche overlap
+% }
 
-\noindent Figures: 3\\
-\noindent Tables: 2\\
-\noindent Notes: 1 file, 6 sections.
-\end{multicols}
+% \noindent\small\textbf{Word Counts}
+% \begin{multicols}{2}
+% \small{
+% Main text: 6409 % Limit 6,500 % 
+% \vspace{-5pt}
+% \begin{itemize}
+%   \setlength\itemsep{-0.1em}
+%   \item Introduction: 1163
+%   \item Materials and Methods: 2469
+%   \item Results: 949
+%   \item Discussion: 1745
+%   \item Acknowledgements: 83
+% \end{itemize}
+% \bigskip
+% \bigskip
+% \bigskip
 
-\vspace{-0.25in}
-\begin{multicols}{2}
-\section*{Social media}
-@acirtwill; @stoufferlab\\
-
-\section*{Header}
+% \noindent Figures: 3\\
+% \noindent Tables: 2\\
+% \noindent Notes: 1 file, 6 sections.}
+% \end{multicols}
 
@@
 
-\end{spacing}
-\begin{spacing}{1.5}
+% \end{spa cing}
+% \begin{spacing}{1.5}
 \clearpage
@@
 
+\newpage
+
 \section*{Notes legends}

### 2020-01-09 manuscript/second_submission.tex
creating submitted and accepted versions for proper legal archiving

--- 2019-12-09 manuscript/phylogenetic_signal_manuscript.tex
@@
 % make Figure 1 etc bold
+\usepackage{fancyhdr}
 \usepackage[labelfont=bf]{caption}
@@
 
-\title{Related plants tend to share pollinators and herbivores, but strength of phylogenetic signal varies among plant families}
+\lhead{Submitted version}
+
+\title{At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families.}
 
@@
 
-\clearpage
+\noindent This is the submitted version of the following article: \\
+\smallskip
+Cirtwill, A. R., Dalla Riva, G. V., Baker, N. J., Ohlsson, M.,
+Norstr\"{o}m$^{4}$, I., Wohlfarth, I.
+M., Thia, J.
+A., Stouffer, D.
+B.
+(2020) \emph{Related plants tend to share pollinators and herbivores, but strength of phylogenetic signal varies among plant families}.
+\textbf{New Phytologist}: in press.\\
 
-\section*{Word Counts}
+% \section*{Word Counts}
 
-Main text: 6409 % Limit 6,500 %
+% Main text: 5612 % Limit 6,500
+
+% \begin{itemize}
+%   \item Introduction: 1074
+%   \item Materials and Methods: 2223 
+%   \item Results: 890
+%   \item Discussion: 1342
+%   \item Acknowledgements: 83
+% \end{itemize}
+
+% % Word counts updated July 2, include some comments.
+
+% Figures: 3
+
+% Tables: 2
+
+% Supporting information: 1 file containing 4 sections.
+
+\vspace{0.4 in}
+
+\section*{Summary} % Must be <200 words. Currently 199
 
   \begin{itemize}
-  \item Introduction: 1163
-  \item Materials and Methods: 2469
-  \item Results: 949
-  \item Discussion: 1745
-  \item Acknowledgements: 83
-\end{itemize}
+    \item Related plants are often hypothesised to interact with similar sets of pollinators and herbivores, but empirical support for this idea is mixed.
+We argue that this may be because plant families vary in their tendency to share interaction partners.
 
-\noindent Figures: 3
+    \item We introduce a novel way to quantify overlap of interaction partners for each pair of plants in 59 pollination and 11 herbivory networks based on the numbers of shared and unshared interaction partners.
+We test for relationships between phylogenetic distance and partner overlap within each network, and whether these relationships varied with the composition of the plant community.
+Finally, we test for different relationships within well-represented plant families.
 
-\noindent Tables: 2
-
-\noindent Supporting information: 1 file containing 6 sections.
-
-\clearpage
-
-% \vspace{0.2 in}
-
-\section*{Summary} % Must be <200 words. Currently 200.
-
-  \begin{itemize}
-    \item Related plants are often hypothesised to interact with similar sets of pollinators and herbivores, but this idea has only mixed empirical support.
-This may be because plant families vary in their tendency to share interaction partners.
-
-    \item We quantify overlap of interaction partners for all pairs of plants in 59 pollination and 11 herbivory networks based on the numbers of shared and unshared interaction partners (thereby capturing both proportional and absolute overlap).
-We test 1) for relationships between phylogenetic distance and partner overlap within each network, 2) whether these relationships varied with the composition of the plant community, and 3) whether well-represented plant families showed different relationships.
-
-    \item Across all networks, more closely-related plants tended to have greater overlap.
-The strength of this relationship within a network was unrelated to the composition of the network's plant component, but, when considered separately, different plant families showed different relationships between phylogenetic distance and overlap of interaction partners.
+    \item Across all networks, more closely-related plants tended to have greater overlap, especially in herbivory networks.
+The strength of this relationship within a network was unrelated to the composition of the network's plant component, but different plant families showed different relationships between phylogenetic distance and overlap of interaction partners.
 
     \item The variety of relationships between phylogenetic distance and partner overlap in different plant families likely reflects a comparable variety of ecological and evolutionary processes.
-Considering factors affecting particular species-rich groups within a community may be the key to understanding the distribution of interactions at the network level.
+Considering factors affecting the dominant plant families within a community may be the key to understanding the distribution of interactions.
 
@@
 
-ecological networks, herbivory, niche overlap, phylogenetic signal, pollination, specialisation
+defensive syndrome, ecological networks, herbivory, niche overlap, phylogenetic signal, pollination, pollination syndrome, specialisation
 
-\end{spacing}
-\begin{spacing}{1.5}
+% \end{spacing}
+% \begin{spacing}{1.5}
 \clearpage
@@
 \section*{Introduction}
-\linenumbers
+% \linenumbers
 
   Interactions with animals affect plants' life cycles in several critical
-  ways~\citep{Mayr2001}. On one hand,
+  ways~\citep{Mayr2001,Sauve2016}. On one hand,
   pollination and other mutualistic interactions contribute
@@
   secondary metabolites may have fewer herbivores~\citep{Johnson2014}. 
-  Plant traits are also likely to determine \emph{which} specific pollinators 
-  and herbivores interact with a particular plant. Plants with different defences 
+  A plant's traits are also likely to determine \emph{which} specific pollinators 
+  and herbivores interact with that plant. Plants with different defences 
   (e.g., thorns vs. chemical defences) may deter different groups of 
-  herbivores~\citep{Ehrlich1964,Johnson2014}, and pollinators with similar traits are often expected to attract similar sets of pollinators~\citep{Waser1996,Fenster2004,Ollerton2009}.
+  herbivores~\citep{Ehrlich1964,Johnson2014}, and the concept of 
+  pollination syndromes has often been used to group plants into phenotypic
+  classes believed to attract certain groups of pollinators~\citep{Waser1996,Fenster2004,Ollerton2009}.
 
@@
   Recent studies that have investigated this question at the level of whole
-  communities, however, have yielded mixed results.
+  communities, however, have yielded mixed results~\citep{Rezende2007a,Gomez2010,Rohr2014a,Fontaine2015,Lind2015,Ibanez2016,Bergamini2017,Sydenham2017,Volf2017,Hutchinson2017}.
   In particular, significant phylogenetic signal in plants' sets of interaction partners tends to be rare in empirical networks (\citealp{Rezende2007a,Lind2015,Ibanez2016}; but see~\citealp{Elias2013,Fontaine2015,Hutchinson2017}).
@@
 In antagonistic networks, however, actively-foraging consumers tend to show less phylogenetic signal than their prey~\citep{Ives2006,Cagnolo2011,Naisbit2011,Fontaine2015}.
-In part, this may be related to different degrees of interaction intimacy (dependence of one partner on another), which appears to contribute to network structure in mutualistic, but not antagonistic, networks~\citep{Guimaraes2007,Ponisio2017}.
-In any case, it is not straightforward to assume that interactions will always be similar among related species.
+Thus, it is not straightforward to assume that interactions will always be similar among related species.
 
-  There are several mechanisms that might weaken the conservation of interaction partners. Pollination and herbivory may be affected
+  Several mechanisms that might weaken the conservation of interactions
+  have been identified in the literature. Pollination and herbivory may be affected
   by a wide variety of traits, and not all of these are likely to be
@@
   floral displays are strongly affected by environmental conditions~\citep{Canto2004}, 
-  then plant phylogeny may not strongly predict pollination.
+  then pollinators may not be predicted by plants' phylogenies.
   Even if the traits affecting pollination and herbivory are
@@
   are attractive to pollinators can also increase 
-  herbivory~\citep{Strauss2002,Adler2004,Strauss2006,Theis2006}. 
+  herbivory~\citep{Strauss2002,Adler2004,Theis2006}. 
   Conversely, herbivory can reduce pollination by inducing chemical 
@@
 There may also be trade-offs between chemical and physical defences, or defences at different life stages, that weaken the overall heritability of plants' sets of herbivores~\citep{Karinho2014,Endara2017}.
-  A plant's set of interaction partners therefore reflects a mixture of different environmental effects and different selection pressures, as well as shared phylogenetic history.
-  If these factors affect closely-related plants differently, then closely-related species may not have more similar interaction partners than distantly-related species.
+Observed patterns
+  of similarity in plants' interaction partners therefore represent
+  a mixture of environmental effects and various selection pressures as
+  well as plants' shared phylogenetic history.
 
-  This variety of different pressures makes it likely that the relationship between plants' relatedness and the similarity of their interaction partners is
-  not constant across plant clades. 
-  Closely-related plants in one clade might be under strong selection to favour dissimilar sets of pollinators to avoid exchanging pollen with other species~\citep{Levin1970,Bell2005,Mitchell2009}, while plants in other clades may be under strong pressure to continue interacting with a common set of partners.
-  Similarly, plants may experience disruptive selection on defences against herbivores if congeners tend to grow in the same places such that herbivore able to consume one species could easily spread to close relatives~\citep{Kursar2009,Yguel2014}.
-  On the other hand, unrelated plants might 
-  converge upon similar phenotypes which attract particularly 
-  efficient or abundant pollinators~\citep{Ollerton1996,Wilson2007,Ollerton2009,Ibanez2016}. 
+  A further complication is the possibility that the relationship between
+  plants' relatedness and the similarity of their interaction partners is
+  not constant across plant clades. Closely-related plants
+  in one clade might be under strong selection to favour dissimilar
+  sets of pollinators to avoid exchanging pollen with other
+  species~\citep{Levin1970,Bell2005,Mitchell2009}.
+Similarly, plants may experience disruptive selection on defences against herbivores if congeners tend to grow in the same places such that herbivore able to consume one species could easily spread to close relatives~\citep{Kursar2009}.
+  % Similar pressures  could also affect related plants' defences against herbivores if congeners tend to grow in the same places such that herbivores could easily move between them.  
+  Unrelated plants might also 
+  converge upon similar phenotypes, attracting a particularly 
+  efficient or abundant pollinator~\citep{Ollerton1996,Wilson2007,Ollerton2009,Ibanez2016}. 
   Likewise, unrelated plants may converge upon similar defences, leading them to share 
@@
   pairs of plants (henceforth ``niche overlap'') varies over 
-  phylogenetic distance. 
+  phylogenetic distance and how this differs between plant families. 
   Whereas previous 
@@
   order to obtain a more detailed picture of how plant phylogeny
-  relates to network structure.
-As different plant families (which represent tractable clades for analysis) may have experienced different degrees of coevolution, convergence, etc., we also complement analyses with entire networks with comparisons among plants in the same family within a network.
-  This novel perspective allows us to investigate the relationship between phylogenetic distance and partner overlap at different scales. 
-  Specifically,
+  relates to network structure. Specifically,
   we test 1) whether niche overlap decreases over increasing phylogenetic
@@
   phylogenetic distance differs systematically across plant families.
-  This fine-grained approach gives more detailed information than previous studies.
+  This fine-grained approach gives more detailed information than 
+  previous studies.
 
-\clearpage
+% \clearpage
 
@@
     set of 59 pollination and 11 herbivory networks. These networks span 
-    a range of biomes (desert to grassland to tundra) and 
-    countries (Sweden to New Zealand). The herbivory networks included a 
-    variety of types of herbivores but were dominated by leaf-chewing insects. 
-    Leaf-chewing and other types of herbivory might be affected by different
-    plant traits and cannot be expected to show the same trends
-    with respect to phylogeny. We therefore restricted our networks to
-    leaf-chewing insects by removing any non-leaf chewing insects and any 
+    a range of biomes (desert to scrub forest to grassland) and 
+    countries (Sweden to Australia). The herbivory networks included a 
+    variety of types of herbivores but were dominated by insects 
+    consuming leaves. To ensure that we were analysing interactions 
+    influenced by similar sets of traits across networks, we restricted 
+    our herbivory networks to insects consuming leaves and excluded 
+    sap-sucking, leaf-mining, and galling insects as well as seed 
+    predators and xylophagous insects; all of these interactions involve 
+    different plant tissues and means of feeding than leaf consumption 
+    and so may be influenced by different plant and insect traits. 
+    Specifically, we removed any non-leaf consuming insects and any 
     plants which had no interaction partners after removing other types  
-    of herbivores.
-    The adjusted networks range in size between 19 and 
+    of herbivores. The adjusted networks range in size between 19 and 
     997 total species (mean=162, median=97) with between 8 and 132 
@@
     Supporting information 1} for details on the original sources of all 
-    networks. All networks were qualitative and did not include interaction strengths.
+    networks.
 
@@
     be assigned to an accepted taxonomic name (e.g., `Unknown Forb') were 
-    discarded, as were those with binomial names that could not be definitively 
+    discarded, as were those with non-unique common names and no binomial 
+    name given (e.g., `Ragwort) or binomial names that could not be definitively 
     linked to  higher taxa (e.g., \emph{`Salpiglossus sp.'}). We were left with 
@@
     We then estimated phylogenetic distances between the remaining species. To accomplish 
-    this, we constructed a phylogenetic tree based on a dated
-    `mega-tree' of angiosperms~\citep{Zanne2014}. Some species in our dataset were not included
+    this, we constructed a phylogenetic tree for our dataset based on a dated
+    `mega-tree' of angiosperms~\citep{Zanne2014}. Some species were not included
     in the angiosperm mega-tree. For angiosperms,
@@
     This means that closely-related non-angiosperm species appear to have very long 
-    phylogenetic distances between them. We therefore excluded comparisons 
-    between pairs of non-angiosperms from our analyses. As only two networks (both 
+    phylogenetic distances between them. For this reason, we excluded comparisons 
+    between pairs of non-angiosperms from our subsequent analyses. As only two networks (both 
     herbivory networks) included more than one such species and non-angiosperms
@@
 
-  \subsection*{Calculating niche overlap}
+  \subsection*{Calculating niche overlap within communities}
 
-    We calculated niche overlap for each pair of plants $i$ and $j$ based on the number of shared and unshared interaction partners ($M_{ij}$, $U_{ij}$, respectively). 
-    The number of unshared interaction 
-    partners gives valuable information about cases where, for example, 
-    closely-related plants may have experienced disruptive selection, leading to weaker phylogenetic signal. 
-    The sum $M_{ij} + U_{ij}$ indicates the amount of information  provided by each pair of plants: a pair of generalists which share most of their interaction partners gives a stronger indication of phylogenetic signal than a pair of extreme specialists with one common interaction partner.
-
-    Together, $M_{ij}$ and $U_{ij}$ give a Jaccard index ($J_{ij}$) describing 
-    the proportion of shared interactions. $J_{ij}$ is defined: 
-    % %
-    % \begin{equation}
-    %   J_{ij} = \frac{M_{ij}}{P_i+P_j-M_{ij}} ,
-    % \end{equation}
-    % %
-    % where $M_{ij}$ is the set of \emph{mutual} (shared) interaction partners of 
-    % species $i$ and $j$ and $P_i$ and $P_j$ are the sizes of the sets of interaction 
-    % \emph{partners} for species $i$ and $j$ respectively. $J_{ij}$ can also be defined:
-    % %
+    We calculated niche overlap for each pair of species within a community 
+    using a Jaccard index to describe the number of shared interaction 
+    partners, augmented with the number of interaction partners which were 
+    not shared. The Jaccard index $J_{ij}$ describes the proportion of 
+    shared interaction partners for species $i$ and $j$ and is defined as: 
+  %
     \begin{equation}
-      J_{ij} = \frac{M_{ij}}{U_{ij}+M_{ij}} ,
+      J_{ij} = \frac{M_{ij}}{P_i+P_j-M_{ij}} ,
     \end{equation}
   %
-    where $M_{ij}$ is the set of \emph{mutual} (shared) interaction partners and $U_{ij}$ the set of unshared interaction partners for plants $i$ and $j$.
-    In our statistical analyses (see below), we used the tuple ($M_{ij}$, $U_{ij}$) as the
-    dependent variable rather than the single value $J_{ij}$. 
-    This allows us to preserve information about the amount of information provided by each pair of plants and weight the observations accordingly.
+    where $M_{ij}$ is the set of \emph{mutual} (shared) interaction partners of 
+    species $i$ and $j$ and $P_i$ and $P_j$ are the sizes of the sets of interaction 
+    \emph{partners} for species $i$ and $j$ respectively. We wished to give more 
+    weight to species sharing a large number of interaction partners as well as 
+    those sharing a large proportion (i.e., to emphasise pairs of generalists 
+    sharing most of their interaction partners over specialists sharing a single 
+    interaction partner).
 Note that species sharing a large \emph{number} of interaction partners may not share a large \emph{proportion} of interaction partners if the number of interaction partners that are not shared is also large.
+% Added because Josh got confused about the distinction.
+    To capture all of this information for each species pair, we therefore recorded the number of 
+    shared interaction partners ($M_{ij}$) and the number of interaction partners 
+    that were not shared 
+    ($U_{ij}$ = $P_{i}$+$P_{j}$-2$M_{ij}$). Instead of a single index $J_{ij}$, 
+    we thus kept track of the full information needed to compute
+    niche overlap between species $i$ and $j$ as a tuple: ($M_{ij}$, $U_{ij}$).
 
-  \subsection*{Testing conservation of niche overlap within networks}
+  \subsection*{Statistical analysis}
 
     We modelled the relationship between niche overlap and phylogenetic 
-    distance using a logistic regression. We used the numbers of shared 
+    distance using a logistic regression. We used both the numbers of shared 
     ($M_{ij}$) and non-shared ($U_{ij}$) partners as dependent variables and 
@@
     approach is conceptually similar to modelling successes and failures in a 
-    binomial-distributed process. Accordingly, we assumed a binomially-distributed error structure and used a logit link function to model the dissimilarity in interaction partners 
-    $J_{ij}$ of plants $i$ and $j$. Regressions of niche overlap and 
-    phylogenetic distance within 
+    binomial-distributed process. Accordingly, we assumed a binomially-distributed error structure and used a logit link function to model the 
+    probability $\omega_{ij}$ of plants $i$ and $j$ sharing an interaction 
+    partner. Regressions of niche overlap and phylogenetic distance within 
     each network were fit using the R~\citep{R} base function ``glm'' and 
@@
       \begin{equation}
-        {\rm logit}\left(J_{ij}\right) \propto \beta_{distance}\delta_{ij} ,
+        {\rm logit}\left(\omega_{ij}\right) \propto \beta_{distance}\delta_{ij} ,
         \label{basic}
@@
     where $\delta_{ij}$ is the phylogenetic distance between plants $i$ and 
-    $j$ and $J_{ij}$ is defined by the tuple ($M_{ij}$, $U_{ij}$) (see \emph{Supporting information 2} for R implementation). 
-    The fixed effect of distance in this regression, $\beta_{distance}$, 
+    $j$. The fixed effect of distance in this regression, $\beta_{distance}$, 
     can be understood as the change in log odds of sharing an interaction 
@@
     random intercepts and slopes per network. This expanded regression was fit
-    using the R~\citep{R} function `glmer' from package 
+    using the R~\citep{R} function `glmer from package 
     \emph{lme4}~\citep{lme4} and took the form
@@
       \begin{equation}
-        {\rm logit}\left(J_{ij}\right) \propto \beta_{distance} \delta_{ij} + \beta_{pollination} I_{ij} + \beta_{distance:pollination} \delta_{ij} I_{ij} ,
+        {\rm logit}\left(\omega_{ij}\right) \propto \beta_{distance} \delta_{ij} + \beta_{pollination} I_{ij} + \beta_{distance:pollination} \delta_{ij} I_{ij} ,
       \end{equation}
@@
     are the change in intercept and slope of the log odds of sharing an 
-    interaction partner, respectively, relative to the baseline of 
+    interaction partner, respectively relative to the baseline of 
     herbivory networks.
 
-    To demonstrate the power of defining $J_{ij}$ as a tuple of $M_{ij}$ and $U_{ij}$ rather than a single value, we repeated the above analyses using a Jaccard index based only on the proportion of interaction partners that are shared (i.e., $J_{ij}$ = $M_{ij}$/[$M_{ij}+U_{ij}$]).
-Note that while the proportion of shared interaction partners is the same in both cases, the tuple formulation gives more weight to plants with many interaction partners as these provide more information.
-When comparing the two approaches
-    we observed similar trends but, notably, the tuple definition of $J_{ij}$ had greater power to detect weak relationships (\emph{Supporting information 3}).
-We therefore show only the results when defining $J_{ij}$ as a tuple in the main text.
+    To demonstrate the power of defining $\omega_{ij}$ as a tuple of $M_{ij}$ and $U_{ij}$, we repeated the above analyses instead defining $\omega_{ij}$ as the proportion of interaction partners that are shared (i.e., $M_{ij}$/[$M_{ij}+U_{ij}$]).
+We observed similar trends but, notably, the tuple definition of $\omega_{ij}$ had greater power to detect weak relationships (\emph{Supporting information 2}).
+We therefore show only the results when defining $\omega_{ij}$ as a tuple in the main text.
+
+    Note that pairs of plants are not always independent: the same plant will 
+    appear in many pairs. This violates the assumption of independence used 
+    when calculating the significance of logistic regressions within 
+    the R~\citep{R} base package or the package \emph{lme4}~\citep{lme4}. To 
+    calculate significance of the regression coefficients we observed, it was 
+    therefore necessary to compare the observed relationships to those in a 
+    suite of appropriately permuted networks. To create these networks, we 
+    shuffled interactions among species while preserving row and column 
+    totals. That is, each species retained the same number of interaction 
+    partners as in the observed network but the exact set of partners (and 
+    therefore niche overlaps with all other species) varied across permuted 
+    networks. We preserved the observed phylogenetic relationships between 
+    species in all cases. For each observed network, we created 999 such 
+    permuted networks and calculated the relationship between niche overlap 
+    and phylogenetic distance. This gave us a null distribution for each 
+    observed network with which to determine the significance of the observed 
+    relationship.
+
+    This permutation approach also allows us to estimate type I and type II 
+    error for our analysis. To do this, we created 500 permutations of each 
+    permuted network and, again keeping the observed phylogenetic distances 
+    between plant species, repeated our analyses. We can then determine the 
+    number of permuted networks which appear to have significant 
+    overlap-phylogenetic distance relationships relative to the permutations 
+    of these permuted networks (type I error). Type II error can be determined
+    from the distribution of p-values obtained when comparing the permuted 
+    networks to permutations of the permuted networks. Although calculating 
+    the exact type II error requires a specific alternative hypothesis, the 
+    uniform distribution of p-values we obtained after permuting the permuted 
+    networks means that the type II error would increase linearly as the 
+    alternative hypothesis was set farther from zero.
 
@@
 Both models were fit using the R~\citep{R} base function ``glm".
-A similar model relating the strength of the relationship between phylogenetic distance and niche overlap to connectance showed no significant trends (\emph{Supporting information 4}).
-
-    \subsubsection*{Accounting for non-independence}
-
-      Note that pairs of plants are not independent: the same plant will 
-      appear in many pairs, and interactions may be influenced by the 
-      overall structure of the community. This violates the assumptions used 
-      when calculating the significance of logistic regressions within 
-      the R~\citep{R} base package or the package \emph{lme4}~\citep{lme4}. To 
-      fairly estimate the significance of our regressions, it was 
-      therefore necessary to compare the observed relationships to those in a 
-      suite of appropriately permuted networks. To create these networks, we 
-      shuffled interactions among species while preserving row and column 
-      totals. Each species retained the same number of interaction 
-      partners as in the observed network but the exact set of partners (and 
-      therefore niche overlaps with all other species) varied across permuted 
-      networks. We preserved the observed phylogenetic relationships between 
-      species in all cases. For each observed network, we created 999 such 
-      permuted networks and calculated the relationship between niche overlap 
-      and phylogenetic distance. This gave us a null distribution for each 
-      observed network with which to determine the significance of the observed 
-      relationship.
-
-      This permutation approach also allows us to estimate type I and type II 
-      error for our analysis.
-Because the permuted networks should not demonstrate any particular relationship between phylogenetic distance and partner overlap, these slopes should be similar to those obtained after permuting these networks a second time.
-      To estimate type I and type II errors, we created 500 permutations of each 
-      permuted network and, again keeping the observed phylogenetic distances 
-      between plant species, repeated our analyses. We then determined the 
-      number of permuted networks which appear to have significant 
-      overlap-phylogenetic distance relationships relative to the permutations 
-      of these permuted networks (type I error). Type II error can be determined
-      from the distribution of $p$-values obtained when comparing the permuted 
-      networks to permutations of the permuted networks. Although calculating 
-      the exact type II error requires a specific alternative hypothesis, the 
-      uniform distribution of $p$-values we obtained after permuting the permuted 
-      networks means that the type II error would increase linearly as the 
-      alternative hypothesis was set farther from zero (\emph{Supporting information 5}).
 
@@
     Next, we examined the connection between our network-level observations
-    and the number of species in each plant family present in each community.
+    and the plant families present in each community.
     Specifically, we tested the hypothesis that
@@
     a single network). We then related differences in this relationship
-    to differences in Bray-Curtis dissimilarity in the family-wise composition of the two plant communities 
-    using a non-parametric permutational multi-variate 
+    to differences in the composition of the plant community in each
+    network using a non-parametric permutational multi-variate 
     analysis of variance (PERMANOVA;~\citealp{Anderson2001}).
-    Bray-Curtis dissimilarity considers only
+    As we did not wish to inflate the perceived similarity between
+    pairs of networks which did not include many of the same families,
+    we used Bray-Curtis dissimilarity to define differences in plant
+    community composition. Bray-Curtis dissimilarity considers only
     those plant families which appear in at least one of a pair of
@@
     network could only be exchanged for that of another pollination
-    network. This stratification procedure ensures that 
+    network. Stratifying the permutations in this way ensures that 
     the null distribution used to calculate the $P$-value is not 
@@
 
-  \subsubsection*{Calculating niche overlap within families}
+    % # This isn't mentioned anywhere else, likely a relic of an older plan.
+    % The PERMANOVA tests whether there is an association between
+    % community composition and network-level patterns but does not
+    % give any information on \emph{which} plant families have the
+    % greatest effects. To address this, we supplemented the 
+    % PERMANOVA with three constrained correspondence analyses (CCAs)
+    % which placed plant families along an axis representing the
+    % change in log odds of sharing an interaction partner.
+    % A correspondence 
+    % analysis (CA) is similar to other multivariate
+    % analyses such as principal components analysis in that it
+    % reduces multivariate data to a set of orthogonal axes. A
+    % subset of axes that explain the majority of variation in 
+    % the data can then be interpreted to elucidate trends that
+    % were difficult to interpret in the full multivariate space.
+    % A constrained correspondence analysis (CCA) creates an extra
+    % axis based on some constraint - in this case, the change in
+    % log odds of sharing an interaction partner.
 
-    Finally, we compared the breakdown of niche overlap in different plant families.
-    Within-family genetic and trait diversity can be high due to adaptive radiations, heterogeneous selection, and other influences on different species. 
-    Plant families offer a reasonable balance between collecting enough species to identify meaningful trends and maintaining a tractable number of analyses. 
-    They are therefore the best taxonomic level to investigate phylogenetic conservation in more detail across our large dataset.
-    To test whether different families show different conservation of interactions, 
-    we used the same definitions of 
+  \subsection*{Calculating niche overlap within families}
+
+    Finally, we wished to compare the breakdown of overlap of interactions in
+    different plant families. To do this, we used the same definitions of 
     overlap and phylogenetic distance as in the within-network analysis but 
@@
 
-    For each plant family, within each network type, we fit one of two 
+    For each plant family, within each network type, we then fit one of two 
     similar sets of models. If family $f$ was found in several networks of 
@@
     using the R~\citep{R} function ``glmer'' from package
-     \emph{lme4}~\citep{lme4}. If family $f$ was found in only one network, we omitted the 
+     \emph{lme4}~\citep{lme4}. If family $f$ was found in only one network
+    (and therefore only one network type), we omitted the 
     network-level random effect and fit a logistic regression using the 
@@
 
-    By considering each family separately, we do risk obtaining some significant results purely by chance.
-The standard technique for addressing this type of multiple hypothesis testing, the Bonferroni correction, tends to be over-zealous and lead to a failure to reject the null hypothesis even when a large number of significant results before the correction supports the alternative hypothesis~\citep{Moran2003}.
-To account for multiple testing while also allowing the number of families showing significant trends to carry some weight, we use the correlated Bonferroni test introduced in~\citet{Drezner2016} (\emph{Supporting information 6}).
-
-\clearpage
+% \clearpage
 
@@
     types of networks, but a pair of congeners would be less likely to 
-    share pollinators than to share herbivores. Note that, as our networks 
-    are qualitative, these results refer only to the number of shared interaction
-    partners rather than to the quantitative strength of competition.
-
-    As an illustration, a pair
+    share pollinators than to share herbivores. As an illustration, a pair
     of plants which diverged 10mya would have a probability of 0.202 of sharing
@@
     0.011 of sharing a given pollinator.
-    These trends may be related to the numbers of extreme specialists in each network. In our dataset, an average of 48\% (+/- 14) of pollinators 
+    These trends may be partly 
+    due to the greater proportion of specialist pollinators than specialist 
+    herbivores. In our dataset, an average of 48\% (+/- 14) of pollinators 
     in a given web were extreme specialists (i.e., visited only one plant 
@@
     Comparing the results in the observed networks to those obtained after 
-    permuting interactions, the observed 
+    permuting phylogenetic distances across pairs of plants, the observed 
     slope of the relationship between phylogenetic distance and interaction 
-    partner overlap was always more extreme (i.e., always more negative or 
-    always more positive) than that obtained in the permuted networks (Fig.~\ref{obs_vs_random}).
+    partner overlap was always more extreme (i.e., always lesser or always 
+    greater) than that obtained in the permuted networks (Fig.~\ref{obs_vs_random}).
     Observed networks with a negative relationship between phylogenetic distance 
@@
     between phylogenetic distance and overlap always had more positive 
-    relationships than the permuted networks. This indicates that even in 
+    relationships than the permuted networks. This suggests that even in 
     the networks with non-significant relationships, the association between niche overlap and 
-    phylogenetic distance was not random and confirms that the significant results we observe are not due to non-independence of plants within a network. When the slopes of the permuted 
+    phylogenetic distance was not random. When the slopes of the permuted 
     networks were compared to those obtained from permutations of the 
-    permuted networks, there was no relationship, which speaks to the robustness of our methodology (\emph{Supporting information 5}).
+    permuted networks, there was no relationship, which speaks to the robustness of our methodology (\emph{Supporting information 3}).
 
@@
 
-    We were interested in whether the slope of the relationship between phylogenetic distance and niche overlap varied with community composition.
+    We were interested in whether the slope of the relationship between phylogenetic distance varied with community composition.
 In a PERMANOVA of slope against community composition, stratified by network type, we did not find a significant relationship between slope and community composition ($F_{1,68}$=1.06, $p$=0.493).
@@
     Taking all families together, the probability of species in the same family sharing interaction partners was not significantly related to phylogenetic distance ($\beta_{distance}$=-6.48, $p$=0.087).
-Pollination networks did not show a significantly different slope from the herbivory networks ($\beta_{distance:pollination}$=1.73, $p$=0.681).
-Plants in pollination networks did, however, have a lower intercept probability of sharing interaction partners ($\beta_{pollination}$=-0.776, $p$=0.007), similar to our within-network results above.
+Pollination networks did not show a significantly different trend from the herbivory networks ($\beta_{distance:pollination}$=1.73, $p$=0.681).
+More closely-related pollinators did, however, tend to share fewer interaction partners ($\beta_{pollination}$=-0.776, $p$=0.007), similar to our within-network results above.
 
     Considering each family separately, the relationship between within-family niche overlap and phylogenetic distance varied widely in both pollination and herbivory networks. 
-    In pollination networks, overlap decreased significantly with increasing phylogenetic distance in 14 of the 48 well-represented families (Table~\ref{family_slopes_pp}; Fig.~\ref{within_family_regression}).
-If we apply the correlated Bonferroni correction to account for multiple testing~\citep{Drezner2016}, all of these slopes remain significant (\emph{Supporting information 6}).
+    For the 48 families that were well represented in pollination networks, overlap decreased significantly with increasing phylogenetic distance in 12 (Table~\ref{family_slopes_pp}).
     There was no significant relationship between overlap and phylogenetic distance in
-    a further 34 plant families (see \emph{Supporting information 6} for further 
+    a further 34 plant families (see \emph{Supporting information 4} for further 
     details). Finally, the overlap between pairs of \emph{Apiaceae} and \emph{Poaceae} increased significantly with increasing phylogenetic distance.
 
-    Of the nine plant families that were well-represented in herbivory 
+    Of the nine plant families that were sufficiently well represented in herbivory 
     networks, overlap decreased significantly with increasing phylogenetic distance in four 
@@
     and in one family, \emph{Fabaceae}, overlap of interaction partners increased significantly with 
-    increasing phylogenetic distance. If we again apply the correlated Bonferroni correction, all five significant slopes remain significant  (\emph{Supportin information 6}).
+    increasing phylogenetic distance.
 
-\clearpage
+% \clearpage
 
@@
 
-  We found general support for the hypothesis that more
+  We found broad support for the hypothesis that more
   closely-related pairs of plants have a higher degree
-  of niche overlap. Taking all networks together, 
+  of niche overlap. Using a novel method which considers
+  all pairs of plants together, 
   the probability of two plants sharing the same animal 
-  interaction partners decreased with increasing 
+  interaction partners generally decreased with increasing 
   phylogenetic distance. Considering networks separately,
-  $\approx$56\%  of pollination and $\approx$64\% of
-  herbivory networks showed the expected trend of decreasing 
+  $\approx$56\%  of the pollination and $\approx$64\% of the 
+  herbivory networks exhibited the expected trend of decreasing 
   overlap with increasing distance. This variation between networks
@@
   networks. The lack of a significant relationship between
-  phylogenetic distance and niche overlap in many
+  phylogenetic distance and interaction partner overlap in many
   networks could be partly due to the large number of extreme
-  specialist insects, especially in the pollination networks.
+  specialists, especially among the pollination networks.
   These species interact with only one plant and
-  therefore weaken any signal of niche overlap.
+  therefore weaken any signal of interaction partner overlap.
   The herbivory networks did not contain as many obligate 
-  specialists, but we note that herbivores, like pollinators, often interact with only a few closely-related plants~\citep{Novotny2005,Brandle2006,Astegiano2017}.
+  specialists, but we note that many herbivorous insects are
+  oligotrophs which consume only a few closely-related 
+  hosts~\citep{Novotny2005,Yguel2011}.
   These oligotrophs may affect overall phylogenetic signal in the same
-  way as the strict specialists: in both cases plants that are not very closely related are unlikely to share interaction partners.
-Note that some of the apparent specialists in our dataset may actually be rare species involved in more interactions which have not yet been observed~\citep{Bluthgen2006,Poisot2015}.
-Without information on the sampling completeness of the networks in our dataset, it is difficult to estimate the size of this effect.
-  It is possible, however, that we might observe stronger relationships between phylogenetic
-  distance and niche overlap with more complete data on rare species.
+  way as the specialist partners: in both cases plants in different
+  families are unlikely to share interaction partners.
 
-  In our dataset, the slope of the relationship between phylogenetic
-  distance and niche overlap was not related to the composition of the
-  plant community in each network. Combined with the overall trend for
-  conservation of interaction partners above, this suggests that  
-  trends among closely-related plants
-  (e.g., congeners or members of the same subfamilies) are more
+  We found that the composition of plant families in a network
+  was not related to the slope of the relationship between phylogenetic
+  distance and interaction partner overlap. This suggests that 
+  conservation of interaction partners among closely related plants
+  (e.g., congeners or members of the same subfamilies) is more
   important than phylogenetic signal from deeper within the phylogenetic
@@
   a network and the relationship between phylogenetic distance and
-  niche overlap in either pollination or herbivory networks,
+  interaction partner overlap in either pollination or herbivory networks,
   the greater importance of shallow phylogeny (as reported for leaf
   miners and gallers in~\citet{Volf2017}) may be a general 
-  feature of plant-insect interaction networks. This contrasts 
-  with~\citet{Chamberlain2014}, who found that the \emph{shape}
-  of the phylogenetic tree had a larger effect on network 
-  structure than the timing of speciation. As~\citet{Chamberlain2014}
+  feature of plant-insect interaction networks. This contrasts with
+  the findings of~\citet{Chamberlain2014}, who found that the \emph{shape}
+  of the phylogenetic tree rather than whether speciation was more or
+  less recent had a larger effect on network structure. As~\citet{Chamberlain2014}
   were interested in overall structural properties of networks rather
-  than niche overlap, this discrepancy may indicate that
+  than interaction partner overlap, this discrepancy may indicate that
   different aspects of plant-insect interaction networks are influenced
@@
   and the lack of influence of community composition on the strength of 
-  this signal could be partly due to different trends within families. 
+  the relationship between phylogenetic distance and interaction partner
+  overlap could be partly due to the different trends within families. 
   More than half of the plant families in each network type
@@
   positive slope was extremely steep. This could indicate different 
-  rates of phenotypic drift or evolution in different families (or their interaction partners). 
+  rates of phenotypic drift or evolution in different families. 
   In other families, there was no significant relationship between phylogenetic
-  distance and niche overlap. In these cases, key traits affecting 
-  plant-insect interactions may be highly labile or plastic (environmentally determined).
-These possibilities are supported by several studies showing a stronger relationship between niche overlap and trait similarity than niche overlap and phylogenetic similarity~\citep{Junker2015,Ibanez2016,Endara2017}.
+  distance and interaction partner overlap. In these cases, key traits affecting 
+  plant-insect interactions may not be strongly
+  conserved. Studies showing a stronger relationship between trait similarity
+  and shared interaction partners than phylogenetic similarity and shared
+  interaction partners suggest that traits may indeed be evolutionarily
+  labile~\citep{Junker2015,Ibanez2016,Endara2017}.
 
-  While the majority of plant families in our dataset showed the 
-  expected trend, two (\emph{Polygonaceae} in pollination networks and \emph{Fabaceae} in herbivory networks) showed the opposite 
-  pattern. In these families, closely-related plants had 
+  Moreover, \emph{Polygonaceae} in pollination networks and 
+  \emph{Fabaceae} in herbivory networks showed the opposite 
+  pattern to what we expected. In these families, closely-related plants had 
   \emph{lower} overlap than more distantly-related pairs of plants. 
-  There are several possible explanations for this pattern. 
-  First, part of the family may have recently 
+  There are several possible reasons a plant family might
+  display this pattern. First, part of the family may have recently 
   undergone a period of rapid diversification with closely-related species 
-  developing novel phenotypes and attracting different  
-  interaction partners~\citep{Linder2008,Breitkopf2015}. Likewise, the
-  animals may have undergone an adaptive radiation to 
-  specialise on their most profitable partner~\citep{Janz2006}. 
-  Alternatively, plants in these families could have undergone convergent evolution or ancestral traits could be strongly preserved. Either case would allow 
-  distantly-related \emph{Polygonaceae} and \emph{Fabaceae} to interact with the same insects. 
-  Finally, this pattern could be the result of ecological or environmental 
+  developing novel phenotypes that attract different animal 
+  interaction partners~\citep{Linder2008,Breitkopf2015}. It is also possible that the
+  animals have undergone an adaptive radiation to 
+  specialise on their most profitable partner~\citep{Janz2006}. Second, this pattern 
+  could be the result of ecological or environmental 
   filtering~\citep{Ackerly2003,Mayfield2009}. 
-  Closely-related species with strong niche overlap might compete too severely to coexist. 
-  This is especially likely
+  Closely-related species which have high degrees of overlap in their interaction 
+  partners might compete too severely to coexist. This is especially likely
   for plants sharing pollinators, where the loss of pollen to related species 
@@
   Indeed, animal pollination and seed dispersal have been shown to act
-  as filters for several plant clades~\citep{Mayfield2009}. Selection to avoid 
-  competition and restrict numbers of interaction partners may lead to
-  more intimate or specialised interactions~\citep{Ponisio2017}. 
-  This is particularly the case in highly intimate interactions, where both partners may specialise~\citep{Hembry2018}.
-  Past selection to avoid competition is 
+  as filters for several plant clades~\citep{Mayfield2009}, while selection to avoid 
+  competition and restriction on numbers of interaction partners may lead to
+  more intimate or specialised interactions~\citep{Ponisio2017}. This is
   consistent with the relatively high proportion of extreme specialists we
-  observed in the pollination networks. As described above, these specialists likely weaken the relationship between phylogenetic distance and niche overlap.
+  observed in the pollination networks, which likely contributes to the weak
+  relationships between phylogenetic distance and interaction partner overlap
+  in many networks. Finally, although we do not have information about plants'
+  traits in these networks, it is possible that convergence or a high degree of
+  ancestral trait conservation has occurred
+  allowing distantly-related \emph{Polygonaceae} and \emph{Fabaceae} to
+  interact with the same insects.
 
@@
   plants did not vary linearly over phylogenetic distance. Once again, there 
-  are several possible explanations for this result. These plants might 
+  are several possible drivers for this trend (or lack thereof). These plants might 
   be highly specialised on different interaction partners and therefore
@@
   Alternatively, pollination and/or herbivory might exert large 
-  pressures that maintain the clade within a single pollination or 
+  pressures that maintain the clade within a pollination or 
   defensive syndrome. These syndromes are commonly believed to
@@
   and herbivory networks, we can also contrast the 
-  trends in the two network types. Notably, all families except \emph{Asteraceae} 
-  showed different trends in different network types. 
-  This could be because of conflicting selection from pollinators and herbivores,
-  with one type of selection placing greater constraints on plant traits than the other.
-  Multiple types of interactions (e.g., pollination, herbivory, nectar robbing) 
-  and even environmental factors can influence traits such as 
-  flower colour, nectar abundance, and flowering phenology~\citep{Strauss2006}. 
-  These influences can act in the same or different directions~\citep{Strauss2006}.
-  Plant phenotypes in turn affect which species participate in both pollination and herbivory~\citep{Strauss1997,Strauss2002,Adler2004,Adler2006,Theis2006}.
-  The interplay between these different selective pressures may mean that plants
-  cannot evolve to respond optimally to both pollinators and herbivores. Put another
-  way, stronger selective pressure from herbivores might cause phenotypic changes
-  that disrupt phylogenetic signal in pollinators, or vice versa. This could result from
-  asymmetric degree distributions: within a single system, most plants tend to interact
-  with many pollinators \emph{or} many herbivores but not both~\citep{Melian2009,Pocock2012,Astegiano2017}.
-  These asymmetric interactions may also affect higher-order network structures such as
-  modularity or nestedness~\citep{Astegiano2017}.
-The nature of the effects of multiple interaction types on both phylogenetic signal in interactions and overall network structure is, however, still an open question deserving of much more research.
+  trends in the two network types. While \emph{Asteraceae} showed the
+  expected decrease in interaction partner overlap with increasing
+  phylogenetic distance, the other families showed different trends in
+  different network types. This may indicate that one type of interaction
+  places greater constraints upon these families than the other, 
+  similar to the expectation that greater constraints upon consumers 
+  than upon their resources explains the asymmetry in conservation  
+  of interaction partners~\citep{Fontaine2015}. Plants
+  may not be able to respond to selection on both types of interaction
+  simultaneously because traits affecting pollination can also affect herbivory, and vice
+  versa~\citep{Strauss1997,Strauss2002,Adler2004,Adler2006,Theis2006}.
+  Associations with pollinators and herbivores may also be constrained by the
+  larger structure of the community. In one recent study, plants which are 
+  visited by many pollinators are also consumed by many herbivores~\citep{Sauve2016}.
+  This may be because pairing antagonistic and mutualistic interactions
+  balances the indirect effects of these interactions, leading to a
+  more stable community~\citep{Sauve2014}. As more networks describing 
+  pollination and herbivory in the same community become available, it 
+  will be interesting to test this hypothesis more thoroughly.
 
-  Altogether, our study has revealed general trends for conservation of interaction
-  partners between closely-related species, with some networks and plant 
-  families showing different trends. This overall similarity between closely-related
-  species has a potential application in ecological restoration. Close relatives could
-  be used interchangeably to restore missing interactions and fill ecosystem functions. 
-  This may be advantageous when a target plant is more difficult to establish than its
-  relatives, or if the restoration site is not large enough to support viable populations 
-  of many species. We should urge caution, however, since plants which support the
-  same pollinators may also support similar sets of herbivores. To avoid unwanted 
-  indirect effects, all interactions involving the target species should be considered.
+  Altogether, our study has revealed a wide variety of relationships 
+  between overlap of interaction partners and phylogenetic distance 
+  between plants in the same family. Regardless of the precise mechanisms
+  behind these relationships, it is clear
+  that the differences between families can affect the relationship
+  between overlap and phylogenetic distance at the network level.  
   Although here we considered only the presence or absence of interactions,
-  (i.e., qualitative networks)
   recent work also suggests that the phylogenetic composition of a plant
-  community can also affect the strength of 
+  community can affect the strength of 
   interactions, and that the spatial arrangement of plants within a 
   community may be particularly important~\citep{Yguel2011,Castagneyrol2014}.
-  These further nuances in the relationship between phylogenetic distance and 
-  niche overlap could also strongly affect the ability of closely-related species to
-  fill the same functions in restoration efforts. This is clearly a topic with many
-  unresolved questions, deserving of further study.
+  If so, then the study of how phylogenetic relationships between plants
+  affect their interactions with animals has only just begun.
+  % This result suggests
+  % that it is not just which plant families are present but the additional 
+  % relationships between the families that affects conservation of
+  % interactions at the network level and is consistent with previous
+  % work showing that the shape of phylogenetic tress, as well as the
+  % phylogenetic distances between species, can affect the strength
+  % of phylogenetic signal~\citep{Chamberlain2014a}.
 
-\clearpage
+% \clearpage
 
@@
 \section*{Tables}
+
+  \begin{table}[!h]
+  \caption{\small Change in log odds (per million years of phylogenetic distance) of a pair of plants in the same family sharing a herbivore.}
+  % These are from the regressions within each family. P-vals need to be replaced, to come from randomizations. Coefficients should be fine.
+  \label{family_slopes_ph}
+  \begin{tabular}{|l  rr|}
+  \hline
+    Family & Change in log odds & $P$-value \\
+    \hline
+    \emph{Asteraceae} & -1.73 &  0.550 \\
+    \emph{Euphorbiaceae} & -19.2 & \textbf{\textless0.001} \\
+    \emph{Fabaceae} & 18.7 &  \textbf{0.046} \\
+    \emph{Melastomataceae} & -13.2 & \textbf{0.022} \\
+    \emph{Moraceae} & -2.13 & 0.092 \\
+    \emph{Nothofagaceae} & -595 & \textgreater{0.999} \\
+    \emph{Pinaceae} &  -25.8 & 0.733 \\
+    \emph{Poaceae} & -4.50 & \textbf{0.020} \\
+    \emph{Rubiaceae} & -8.16 &  \textbf{0.006} \\
+  \hline
+  \end{tabular}
+  \smallskip
+  \footnotesize
+
+  Nine plant families were sufficiently diverse in our  dataset to permit this analysis
+  (see \emph{Materials \\and Methods} for details). For each pattern of overlap, we show the change
+  in log odds per million years \\and the associated $P$-value. Statistically significant values are
+  indicated in bold. \\
+
+  \end{table}
 
@@
 
-  \begin{table}[!h]
-  \caption{\small Change in log odds (per million years of phylogenetic distance) of a pair of plants in the same family sharing a herbivore.}
-  % These are from the regressions within each family. P-vals need to be replaced, to come from randomizations. Coefficients should be fine.
-  \label{family_slopes_ph}
-  \begin{tabular}{|l  rr|}
-  \hline
-    Family & Change in log odds & $P$-value \\
-    \hline
-    \emph{Asteraceae} & -1.73 &  0.550 \\
-    \emph{Euphorbiaceae} & -19.2 & \textbf{\textless0.001} \\
-    \emph{Fabaceae} & 18.7 &  \textbf{0.046} \\
-    \emph{Melastomataceae} & -13.2 & \textbf{0.022} \\
-    \emph{Moraceae} & -2.13 & 0.092 \\
-    \emph{Nothofagaceae} & -595 & \textgreater{0.999} \\
-    \emph{Pinaceae} &  -25.8 & 0.733 \\
-    \emph{Poaceae} & -4.50 & \textbf{0.020} \\
-    \emph{Rubiaceae} & -8.16 &  \textbf{0.006} \\
-  \hline
-  \end{tabular}
-  \smallskip
-  \footnotesize
-
-  Nine plant families were sufficiently diverse in our  dataset to permit this analysis
-  (see \emph{Materials \\and Methods} for details). For each pattern of overlap, we show the change
-  in log odds per million years \\and the associated $P$-value. Statistically significant values are
-  indicated in bold. \\
-
-  \end{table}
-
-\clearpage
-
 \section*{Figures}
@@
      networks (bottom; purple). In both network types, the probability of a pair of plants
-     sharing an interaction partner decreased with increasing phylogenetic distance (thick,
+     sharing an interaction partner increased with increasing phylogenetic distance (thick,
      dark lines).
@@
     \end{center}
-     \caption{The slopes of the mixed-effect logistic regression of pairwise niche overlap against phylogenetic distance (representing the change in log odds of a pair of plants sharing an interaction partner) was significantly different from 0 for each network.
+     \caption{The slopes of the mixed-effect logistic regression of pairwise niche overlap against phylogenetic distance was signficantly different from 0 for each network.
 Here we show the observed slopes for herbivory (green squares) and pollination (purple diamonds) networks.
@@
 The maximum and minimum slopes obtained from 999 permutations of each network are depicted by thin, black lines.
-For both network types, the slopes obtained from permuted networks were always very close to 0 (range -1.34$\times10^{-12}$ to 9.19$\times10^{-13}$).
-}
+For both network types, the slopes obtained from permuted networks were always very close to 0.}
     \label{obs_vs_random} 
@@
     \end{center}
-    \caption{Change in the log odds of a pair of plants sharing a pollinator or herbivore (i.e., the slopes of the mixed-effect logistic regressions) as phylogenetic distance between the plants increases.
+    \caption{Change in the log odds of a pair of plants sharing a pollinator or herbivore as phylogenetic distance between the plants increases.
 These values are analogous to the slopes of the regression lines from Eq.
@@
     For clarity, we show only the 15 plant families for which the slope of the regression of the proportion of shared interaction partners against phylogenetic distance was significant in at least one network type.
-    Note that the change in log odds for \emph{Asteraceae} in herbivory networks and \emph{Melastomataceae} in pollination networks are not significantly different from zero; we present these values only for comparison across network types.
+    Note that the change in log odds for \emph{Asteraceae} in herbivory networks and \emph{Melastomataceae} and \emph{Poaceae} in pollination networks are not significantly different from zero; we present these values only for comparison across network types.
 All other plant families were well-represented in only one network type.
